### 2014-07-16 paper.tex
first commit

% \documentclass[a4paper,11pt]{article}
% \documentclass[a4paper,10pt,draftcls,journal]{IEEEtran}
\documentclass[a4paper,10pt,journal]{IEEEtran}
% \usepackage{times}
\usepackage{graphicx} \usepackage[cmex10]{amsmath}
\usepackage{amssymb} \usepackage{fancybox} \usepackage{alltt}
\usepackage{soul} \usepackage{color} \usepackage{verbatim}
\usepackage{xcolor} \usepackage{colortbl,hhline}
%\usepackage{algorithm2e}
% \usepackage{algorithm}
\usepackage[ruled,vlined]{algorithm2e} \usepackage{framed}
\usepackage{amsthm} \usepackage{fancyref}
\usepackage{amsmath,amsfonts,amssymb, amsthm} \usepackage{textcomp}
\newtheorem*{remark}{Remark}

% \usepackage{natbib}
% \bibpunct{[}{]}{;}{a}{,}{,}

\def \lb {{\langle}} \def \rb {{\rangle}}
\newcommand{\fro}[1]{\|#1\|_2}
\newcommand{\theHalgorithm}{\arabic{algorithm}}

\newcommand{\argmin}{\mathop{\mathrm{argmin}}}

\usepackage{hyperref}

\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}

\newcommand{\prox}{\textrm{pr ox} } \newcommand{\grad}{\textrm{grad} }
\newcommand{\dive}{\textrm{div} }

\pagenumbering{gobble}

\begin{document}
%\onecolumn
\title{Primal-dual algorithm for computing best response against the unplanned mixed strategies of an opponent in two-person zero-sum sequential games}

\author{\IEEEauthorblockN{Elvis D. DOHMATOB}}

\maketitle

\begin{abstract}
% LESS THAN 200 WORDS !!!!!
% 
% While medical imaging typically provides massive amounts of
% data, the extraction of relevant information in a given
% applicative context remains a difficult challenge.

% XXX : don't call it SPM but just "predictive regions or predictive
% maps"
In this manuscript, we consider the problem of computing the best response against the  unplanned mixed strategies of an opponent
in two-player zero-sum sequential games. An unplanned mixed strategy is simply a strategy chosen from a probability simplex.
The proposed technique employs the primal-dual scheme of A. Chambolle and T. Pock to solve the corresponding saddle-point problem.
The resulting algorithm is simple (all resolvent operators can be effectively computed quasi closed-form, using only elementary algebraic operations)
 and is orders of magnitude more efficient than state-of-the-art algorithms like those based on Linear Programming, Interior-Point methods,
and more recently, the Nesterov Excessive Gap Technique. The problem considered here encompasses the problem of computing the best response against an opponent's fixed strategy.
We conclude by exhibiting results on Texas Hold'em Poker.
\end{abstract}

\begin{IEEEkeywords}
  game theory; two-person zero-sum sequential game; best response; mixed strategy; simplex; convex-optimization; saddle-point problem; primal-dual scheme
\end{IEEEkeywords}

\section{Introduction: Statement of the problem}
\label{sec:intro}
%% Let $A \in \mathbb{R}^{m,n}$ be the payoff matrix; let $E \in \mathbb{R}^{r,n}$ and $e \in \mathbb{R}^r$ be a matrix so that player 1 wishes only to use those strategies  $x \in \mathbb{R}_{+}^n$ for which $Ex = e$, i.e $x \in \mathbb{R}_{+}^n$
%%  %% from player \textbf{row} perspective, so that player \textbf{row} gains $A_{i,j}$ and player \textbf{column} forfeits $A_{i,j}$ euros if the former plays the $i$th row and the former players the $j$th column.

%% We denote by $\mathbf{y} \in \mathbb{R}^{n}$ the targets to
%% be predicted, and $\mathbf{X}\in\mathbb{R}^{n \times p}$ the
%% brain images related to the presentation of different
%% stimuli. $p$ is the number of voxels and $n$ the number of
%% samples (images). Typically, $p \sim 10^3-10^5$ (for a whole volume),
%% while $n \sim 10-10^3$.  Let $\Omega \subset \mathbb{R}^3$ be
%% the 3D image domain, discretized on a finite grid. The coefficients
%% $\mathbf{w}$ define a spatial map in $\mathbb{R}^p$. Its gradient at a
%% voxel $j \in \Omega $ reads\footnote{Where it is understood that the feature vector $w$ is ``unmasked''
%% into a full 3D volume before the spatial operators are applied.}:
%% \begin{eqnarray}
%%   \mathbf{\nabla} w(j) := [\nabla_{x} w(j),
%%     \nabla_{y} w(j), \nabla_{z} w(j)] \in
%%   \mathbb{R}^3,
%% \end{eqnarray}
%% where $\nabla_{u}$ is the spatial difference operator along
%% the $u$-axis. Thus $\mathbf{\nabla}$
%% is a linear operator $\in \mathbb{R}^{3p \times
%%   p}$ with adjoint $\mathbf{\nabla} ^T = -\dive \in \mathbb{R}^{p
%%   \times 3p}$. Let $\tilde{\nabla} := [(1 - \rho)\nabla^T, \rho I]^T$ be the identity-augmented spatial gradient operator. Finally, let us recall the definition of the $(q, 1)$ mixed-norm\footnote{Where $q$ itself is allowed to be a mixed-norm.}:
%% \begin{equation}
%% \|v\|_{q, 1} := \sum_{j}{\|v_{j}\|_{q}}
%% \end{equation}

Consider a two-person zero-sum sequential game with payoff matrix $A \in \mathbb{R}^{m,n}$. Consider the problem of
finding the best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$ for player 1, given a fixed
(possibly mixed) strategy $y_0$ for player 2, where $E \in \{-1, 0, +1\}^{r,n}$ and $(1, 0, 0, ..., 0) =: e \in \mathbb{R}^r$ encode player
1's game plan, consistent with the rules of the game. In the language of convex-optimization, one can readily give the following saddle-point formulation for this problem. Viz,

\begin{equation}
  \underset{x \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})}{min}\text{ }\underset{y \in \Delta_{m}^0}{max}\text{ }y^TAx
\end{equation}

where $\Delta_{m}^0$ is the singleton $\{y_0\}$ if $y_0$ is known, otherwise it is the $m-$dimensional probability simplex $\Delta_{m} := \{x \in \mathbb{R}_{+}^m \text{ s.t }\textbf{1}^Tx = 1\}$.\\\\
Noting that $i_{E^{-1}(\{e\})}(x) = \underset{\eta \in \mathbb{R}^r}{max}\text{ }\eta^T(e - Ex)$, one can re-write (1) as:
\begin{equation}
  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m, \eta \in \mathbb{R}^r}{max}\text{ }[y,\eta]^T\left[ \begin{array}{@{}cc@{}}
    A \\ \hline
    -E
    \end{array} \right]x + G(x) - F^*(y, \eta)
\end{equation}
where:
\begin{equation}
  \begin{aligned}
    G:=i_{\mathbb{R}_{+}^n}\\
    F^*: (y, \eta) \mapsto (i_{\Delta_{m}^0}(y) + e^T\eta)
  \end{aligned}
\end{equation}
with resolvent operators given by
\begin{equation}
  \begin{aligned}
    (1 + \tau \partial G)^{-1}: x \mapsto \Pi_{\mathbb{R}_{+}^n}(x) = (x)_+\\
    (1 + \sigma \partial F^*)^{-1}: (y, \eta) \mapsto (\Pi_{\Delta_{m}^0}(y), \eta - \sigma e)% (z, \eta) \mapsto \bigl(y, \frac{\eta}{1 + \sigma}\bigr)
  \end{aligned}
\end{equation}
This way, we obtain following algorithm which solves (2).

\begin{algorithm}[htb]
\caption{Primal-dual algorithm for computing best response against on plained mixed strategies of opponent}%%  \textbf{Let}
\textbf{Initialize} $\tilde{x}^{(0)} = x^{(0)} \in \mathbb{R}^n$; $y^{(0)} \in \mathbb{R}^{m}$; $\eta^{(0)} \in \mathbb{R}^{m}$;
$\tau, \sigma > 0 \text{ s.t. }\tau\sigma (\|A\|^2 + \|E\|^2) \le 1$; $k = 0$.\\
\Repeat{
  convergence}{
  \begin{eqnarray*}
    y^{(k+1)} &\leftarrow& \Pi_{\Delta_{m}^0}\bigl(y^{(k)} + \sigma A \tilde{x}^{(k)}\bigr)\\
    \eta^{(k+1)} &\leftarrow& \eta^{(k)} - \sigma E \tilde{x}^{(k)} - \sigma e\\
    x^{(k+1)} &\leftarrow& (x^{(k)} - \tau A^Ty^{(k+1)} + E^T\eta^{(k+1)})_+\\
    \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
    k &\leftarrow& k + 1
  \end{eqnarray*}
} \Return $x^{(k)}$
\label{Tab:pseudocode_lbfgs}
\end{algorithm}

%\begin{remark}
%% Due to the independence of $(1 + \sigma \partial F^*)^{-1}$ on $\sigma$, we can always choose the pair
%% $(\tau, \sigma)$ , such that $\tau\sigma \|\tilde{\nabla}\|^2 \le 1$ and $\tau \rho(X^TX) \le \alpha$.
% \end{remark}
%% We note that if the pair $(\tau, \sigma)$ is chosen such that $\tau \rho(X^TX) < \alpha$,
%% then (6) can be approximated by
%% \begin{equation}
%% (1 + \tau \partial G)^{-1}(w) \approx (1 - \frac{\tau}{\alpha}X^TX)(w - \frac{\tau}{\alpha} X^Ty)
%% \end{equation}

%% Prediction of external variates from brain images has seen an
%% explosion of interest in the past decade, in cognitive neurosciences
%% to predict cognitive content from functional imaging data such as fMRI
%% \cite{haxby2001,kamitani2005,haynes2006} or for medical diagnosis
%% purposes \cite{fan2008}. Given that brain images are
%% high-dimensional objects --composed of many voxels-- and the
%% number of samples is limited by the cost of acquisition, the
%% estimation of a multivariate predictive model is ill-posed and calls
%% for regularization. This regularization is central as it encodes the
%% practicioner's priors on the spatial maps. For brain mapping, it has
%% been shown that regularization schemes based on sparsity (Lasso or
%% $\ell_1$ family of models) \cite{carroll2009} or Total Variation (TV),
%% that promotes spatial contiguity \cite{michel2011}, perform well for
%% prediction. The combination of these, hereafter dubbed
%% ``TV$-\ell_{1}$'', extracts spatially-informed %% --and thus, more
%% %% interpretable-- 
%% brain maps that are more stable \cite{baldassarre2012}
%% and recover better the predictive regions
%% \cite{gramfort-etal:2013a}. In addition, this prior leads to
%% state-of-the-art methods for extraction of brain atlases
%% \cite{abraham2013}.

%% However, the corresponding optimization problem is
%% intrinsically hard to solve. The reason for this is two-fold. First and
%% foremost, in fMRI studies, the design matrix $\mathbf{X}$ is ``fat''
%% ($n \ll p$), dense, ill-conditioned with little algebraic structure to be
%% exploited, making the optimization problem ill-conditioned. Second, the
%% penalty is not smooth, and while the $\ell_{1}$ term is \emph{proximable}
%% (via \emph{soft-thresholding}), the TV term does not admit a closed-form proximal
%% operator. Thus neither gradient-based methods (like Newton, BFGS, etc.) nor proximal methods (like
%% ISTA~\cite{daubechies2004}, FISTA~\cite{beck2009a}) can be used in the
%% traditional way.

%% While the quality of the optimization may sound as a minor
%% technical problem to the practitioner, the sharpening effect of TV and the
%% sparsity-inducing effect of $\ell_1$ come into play only for
%% well-optimized solutions. As a result, the brain maps extracted vary
%% significantly as a function of the tolerance on the solver (see
%% Fig.\,\ref{fig:maps_tolerance}).

%% \begin{figure*}
%% \includegraphics[width=.32\linewidth]{maps/face_vs_house_tol_0_1.pdf}%
%% \llap{\color{white}\raisebox{.17\linewidth}{\rlap{\sffamily Stopping:
%%       $\Delta E < 10^{-1}$}}\hspace*{.315\linewidth}}\hfill%
%% \includegraphics[width=.32\linewidth]{maps/face_vs_house_tol_0_001.pdf}%
%% \llap{\color{white}\raisebox{.17\linewidth}{\rlap{\sffamily Stopping:
%%       $\Delta E < 10^{-3}$}}\hspace*{.315\linewidth}}\hfill%
%% \includegraphics[width=.32\linewidth]{maps/face_vs_house_tol_1e-05.pdf}%
%% \llap{\color{white}\raisebox{.17\linewidth}{\rlap{\sffamily Stopping:
%%       $\Delta E < 10^{-5}$}}\hspace*{.315\linewidth}}%

%% \caption{TV$-\ell_1$ maps for the face-house discrimination task on
%%   the visual recognition dataset, with regularization parameters chosen by
%%   cross-validation, for different stopping criteria.
%%   Note that
%%   the stopping criterion is defined as a threshold on the energy
%%   decrease per one iteration of the algorithm, and thus differs from
%%   the tolerance displayed in figure \ref{Fig:MSEtimes}.  This figure shows
%%   the importance of convergence for problem \eqref{eq:opt_pb}, and motivates
%%   the need for a fast solver.}%
%% \label{fig:maps_tolerance}
%% \end{figure*}

%% In this contribution, we compare a comprehensive list of
%% solvers, all implemented with great care, for solving TV$-\ell_1$
%% regression with a focus on convergence time. First we state the formal
%% problem solved.
%% In section \ref{sec:algos}
%% we present the various algorithms. Experiments done and the results obtained are presented in secions
%%  \ref{sec:experiments} and \ref{sec:results}
%% respectively. Section \ref{sec:discusion} concludes the paper with
%% general recommendations.

%% \section{Formal problem statement and notations}

%% \label{sec:problem_statement}

%% We denote by $\mathbf{y} \in \mathbb{R}^{n}$ the targets to
%% be predicted, and $\mathbf{X}\in\mathbb{R}^{n \times p}$ the
%% brain images related to the presentation of different
%% stimuli. $p$ is the number of voxels and $n$ the number of
%% samples (images). Typically, $p \sim 10^3-10^5$ (for a whole volume),
%% while $n \sim 10-10^3$.  Let $\Omega \subset \mathbb{R}^3$ be
%% the 3D image domain, discretized on a finite grid. The coefficients
%% $\mathbf{w}$ define a spatial map in $\mathbb{R}^p$. Its gradient at a
%% voxel $\omega \in \Omega $ reads:
%% \begin{eqnarray}
%%   \mathbf{\nabla} \mathbf{w}(\omega) := [\nabla_{x} \mathbf{w}(\omega),
%%     \nabla_{y} \mathbf{w}(\omega), \nabla_{z} \mathbf{w}(\omega)] \in
%%   \mathbb{R}^3,
%% \end{eqnarray}
%% where $\nabla_{u}$ is the spatial difference operator along
%% the $u$-axis. Thus $\mathbf{\nabla}$
%% is a linear operator $\in \mathbb{R}^{3p \times
%%   p}$ with adjoint $\mathbf{\nabla} ^T = -\dive \in \mathbb{R}^{p
%%   \times 3p}$. $\Delta := \nabla ^T \nabla \in
%% \mathbb{R}^{p \times p}$ is the Laplace operator.

%% TV$-\ell_1$ regression leads to the following non-smooth convex
%% optimization problem \cite{gramfort-etal:2013a}:
%% \begin{eqnarray}
%%   \mathbf{\hat{w}} := \argmin_{\mathbf{w}}\;\{E(\mathbf{w}) :=
%%   \mathcal{L}(\mathbf{y}, \mathbf{X}, \mathbf{w}) + \alpha
%%   J(\mathbf{w})\},
%%   \label{eq:opt_pb}
%% \end{eqnarray}
%% where $J(\mathbf{w}) := \theta\|\mathbf{w}\|_{\ell_{1}} + (1 -
%% \theta)\|\mathbf{w}\|_{TV}$ is the regularization and $\alpha \ge 0$
%% controls the amount of regularization. The
%% parameter $\theta \in [0, 1]$, also known as the $\ell_{1}$ \textit{ratio}, is the trade-off between the
%% sparsity-inducing penalty $\ell_{1}$ (Lasso) and TV (isotropic Total
%% Variation):
%% % also known as the $\ell_{1}$\emph{-ratio},
%% % XXX = $\ell_{1}$\emph{-ratio} is sklearn jargon
%% \begin{eqnarray}
%% \|\mathbf{w}\|_{\ell_{1}} := \sum_{\omega \in
%%   \Omega}|\mathbf{w}(\omega)|;\;\;\textbf{ }\|\mathbf{w}\|_{TV} :=
%% \sum_{\omega \in \Omega} \|\nabla \mathbf{w}(\omega)\|_{2} \enspace .
%% %% \\
%% %% &=& \sum_{\omega \in
%% %% \Omega}
%% %% \sqrt{\nabla_{x} \mathbf{w}(\omega)^2 + \nabla_{y} \mathbf{w}(\omega)^2 +
%% %%   \nabla_{z}\mathbf{w}(\omega)^2}\\
%% \end{eqnarray}
%% $\mathcal{L}(\mathbf{y}, \mathbf{X}, \mathbf{w})$
%% is the loss function. Here, we focus on the squared loss
%% and the logistic loss, defined \emph{e.g.} in \cite{michel2011}. The
%% squared loss is natural for regression settings, where $\mathbf{y}$ is a
%% continuous variable, but it may also be used for classification
%% \cite{suykens2002}. The logistic loss is harder to optimize, but
%% more natural for classification settings.

%% \section{Algorithms}
%% \label{sec:algos}

%% In this section, we present the algorithms we benchmarked for solving
%% problem \eqref{eq:opt_pb}.

%% \paragraph{ISTA/FISTA}
%% ISTA~\cite{daubechies2004}, and its accelerated variant
%% FISTA~\cite{beck2009a}, are proximal gradient approaches: the go-to
%% methods for non-smooth optimization. In their seminal introduction of TV
%% for fMRI, Michel \emph{et al.} \cite{michel2011} relied on ISTA.
%% The challenge of these methods for TV is that the proximal operator
%% %% \footnote{The proximal operator (or prox for short) can be seen as a generalization of projection unto convex set.}
%%   of TV
%% cannot be computed exactly; we approximate it in an inner FISTA loop
%% \cite{beck2009b,michel2011}.
%% % , \cite{gramfort-etal:2013a}.
%% %%  and must itself be solved by a
%% %% FISTA\footnote{Note that solving TV and TV$-\ell_1$ are formally very
%% %% close \cite{gramfort-etal:2013a}.
%% % }
%% % \cite{beck2009b,michel2011}. 
%% Here, for all FISTA implementations we use
%% the faster monotonous FISTA variant \cite{beck2009b}. We control the
%% optimality of the TV proximal via its dual gap \cite{michel2011} and
%% use a line-search strategy in the monotonous FISTA to decrease the
%% tolerance as the algorithm progresses, ensuring convergence of the
%% TV-$\ell_1$ regression with good accuracy.

%% \paragraph{ISTA/FISTA with backtracking}
%% A key ingredient in FISTA's convergence is the Lipschitz
%% constant $L(\mathcal{L})$, of the derivative of smooth part of the objective function
%% . The tighter the upper bound used for this constant,
%% the faster the resulting FISTA algorithm. In FISTA, the main use of 
%% $L(\mathcal{L})$ is the fact that: for any
%% stepsize $0 < t \le 1/L(\mathcal{L})$ and for any point $\mathbf{z}$,
%% \begin{equation}%
%%   \begin{gathered}
%%     \mathcal{L}(\mathbf{p}_{t}(\mathbf{z})) \le
%%     \mathcal{L}(\mathbf{z}) + \mathbf{r}_{t}^T\nabla
%%     \mathcal{L}(\mathbf{z}) + \frac{1}{2t} \|\mathbf{r}_{t}\|_{2}^2,
%%     \text{  where} \quad\\
%%     \mathbf{p}_{t}(\mathbf{z}) := \textrm{prox}_{\alpha t J}(\mathbf{z} - t
%%     \nabla \mathcal{L}(\mathbf{z})) \,\text{  and  }\,
%%     \mathbf{r}_{t} :=
%%     \mathbf{p}_{t}(\mathbf{z}) - \mathbf{z} \quad
%%   \end{gathered}
%%   \label{eq:fista_ineq}
%% \end{equation}
%% In least-squares regression, $L(\mathcal{L})$ is precisely the largest
%% singular value of the design matrix $\mathbf{X}$.
%% For logistic
%% regression however, the tightest known upper bound for
%% $L(\mathcal{L})$ is $\|\mathbf{X}\|\|\mathbf{X}^T\|$ (for example see Appendix A of
%% \cite{yuan2012}), which performs
%% very poorly locally (i.e, stepsizes $\sim 1 / L(\mathcal{L})$ are
%% sub-optimal locally). A way to circumvent this difficulty is
%% \emph{backtracking line search} \cite{beck2009a}, where one tunes the
%% stepsize $t$ to satisfy inequality \eqref{eq:fista_ineq} locally at
%% point $\mathbf{z}$.

%% \paragraph{ADMM: Alternating Direction Method of Multipliers}
%% ADMM is a Bregman Operator Splitting primal-dual method for
%% solving convex-optimization problems by splitting the
%% objective function in two convex terms which are functions of linearly-related auxiliary variables
%% \cite{boyd2010}.  ADMM is particularly appealing for problems such as TV
%% regression: using the variable split $\mathbf{z}
%% \leftarrow \nabla \mathbf{w}$, the regularization is a simple $\ell_{1}/\ell_2$
%% norm on $\mathbf{z}$ for which the proximal is exact and computationally
%% cheap. However, in our settings, limitations of ADMM are:
%% \begin{itemize}
%% \item the $\mathbf{w}$-update involves the inversion of a large ($p \times p$)
%%   ill-conditioned linear operator (precisely a weighted sum of
%%   $\mathbf{X}^T\mathbf{X}$, the laplacian $\Delta$, and the identity
%%   operator).
%% \item the $\rho$ parameter for penalizing the split
%%   residual $\mathbf{z} - \nabla \mathbf{w}$ is hard to set (this is still an
%%   open problem), and though under mild conditions ADMM
%%   converges for any value of $\rho$, the convergence rate depends
%%   on $\rho$.
%% \end{itemize}

%% \paragraph{Primal-Dual algorithm of Chambolle and Pock \cite{chambolle2010}}
%% this scheme is another method based on operator splitting.
%% Used for fMRI TV regression by \cite{gramfort-etal:2013a},
%% it does not require setting a hyperparameter.  % XXX : this is wrong you have the tau / sigma
%% However it is a first-order single-step method and is thus more impacted by the
%% conditioning of the problem. Note that here we explore this primal-dual
%% method only in the squared loss setting, in which the algorithm can be accelerated by
%% precomputing the SVD of $\mathbf{X}$ \cite{gramfort-etal:2013a}
%% .

%% \paragraph{HANSO \cite{lewis2008}}
%% a modified LBFGS scheme based on gradient 
%% sampling methods \cite{burke2005} and inexact
%% line-search. For non-smooth problems as in our case, the algorithm relies on
%% random initialization, to avoid singularities with high probability. 
%% Here, we used the original authors' implementation.

%% \paragraph{Uniform approximation by smooth convex surrogates}
%% $\ell_{1}$ (resp. TV) is differentiable almost everywhere,
%% with gradient $\bigl(\textbf{w}(\omega)/|\textbf{w}(\omega|))_{\omega
%%   \in \Omega}$ (resp. $-\dive (\nabla \mathbf{w}/\|\nabla
%% \mathbf{w}\|_2)$), except at voxels $\omega$ of the weights map where
%% \textbf{w}$(\omega) = 0$ (resp. $\|\nabla \mathbf{w}(\omega)\|_{2} =
%% 0$), corresponding to black spots (resp. edges).  A convenient
%% approach (see for example \cite{NESTA, nesterov2005a, nesterov2005b,
%%   beck2012}) for dealing with such singularities is to uniformly
%% approximate the offending function with smooth surrogates that
%% preserve its convexity. Given  % I removed "and other important properties"
%% a smoothing parameter $\mu > 0$, we define \emph{smoothed} versions
%% of $\ell_1$ and TV:
%% %
%% \begin{eqnarray}
%%   \left.
%%   \begin{aligned}
%%     \|\mathbf{w}\|_{\ell_{1},\mu} &:= \sum_{\omega \in \Omega}
%%     \sqrt{\mathbf{w}(\omega)^2 + \mu^2} \quad\\
%%     \|\mathbf{w}\|_{TV, \mu} &:=
%%     \sum_{\omega \in \Omega} \sqrt{\|\nabla \mathbf{w}(\omega)\|_{2}^2 +
%%     \mu^2} \quad
%%     \end{aligned}
%%     \right\}
%% \end{eqnarray}
%% These surrogate upper-bounds are convex and everywhere-differentiable
%% with gradients that are Lipschitz-continuous with constants $1/\mu$ and
%% $\|\nabla\|^2(1/\mu) = 12 / \mu$ respectively.
%% %
%% They lead to smoothed versions of problem \eqref{eq:opt_pb}:
%% \begin{align}
%%   \mathbf{\hat{w}}_{\mu} := \argmin_{\mathbf{w}}\;
%%   \{E_{\mu}(\mathbf{w}) := \mathcal{L}(\mathbf{y}, \mathbf{X}, \mathbf{w}) + \alpha
%%     J_{\mu}(\mathbf{w})\},
%%   \label{eq:sopt_pb}
%% \\
%%     \text{where} \quad
%%     J_{\mu}(\mathbf{w}) :=\theta \|\mathbf{w}\|_{\ell_{1},\mu} +
%%     (1 - \theta)\|\mathbf{w}\|_{TV, \mu} \quad
%% \end{align}

%% To solve \eqref{eq:opt_pb}, we consider problems of the form
%% \eqref{eq:sopt_pb} with $\mu \rightarrow 0^+$: we start with a coarse
%% $\mu$ ($= 10^{-2}$, \emph{e.g}) and cheaply solve the $\mu$-smoothed problem
%% \eqref{eq:sopt_pb} to a precision $\sim \mu$ using a fast
%% iterative oracle like the LBFGS \cite{ciyou1994}; we
%% obtain a better estimate for the solution; then we decrease $\mu$ by a fixed factor,
%% and restart the solver on problem \eqref{eq:sopt_pb} with this solution; and so on, in a 
%% \emph{continuation} process~\cite{NESTA} detailed in Alg.
%% \ref{Tab:pseudocode_lbfgs}.

%% \begin{algorithm}[htb]
%% \caption{LBFGS algorithm with continuation} \textbf{Let}
%% $\epsilon > 0$ be the desired precision, $\beta$ ($0 < \beta <
%% 1$) be the rate of decay of the smoothing parameter $\mu$, and $\gamma > 0$ be a constant.  Finally,
%% let LBFGS: $(E_\mu, \mathbf{w}^{(0)}, \epsilon) \mapsto \mathbf{w}$ be
%% an oracle which when warm-started with an initial guess
%% $\mathbf{w}^{(0)}$, returns an $\epsilon$-optimal
%% solution (i.e $E_\mu(\mathbf{w}) - E_\mu^{*} < \epsilon$) for problem \eqref{eq:sopt_pb}.\\
%% \textbf{Initialize} $ 0 < \mu^{(0)}$ ($= 10^{-2}$, \emph{e.g}),
%% $\mathbf{w}^{(0)}\in \mathbb{R}^p$, and $k = 0$.\\
%% \Repeat{$\gamma\mu^{(k)}
%%   < \epsilon$}{
%%   \begin{eqnarray*}
%%     \mathbf{w}^{(k + 1)} &\leftarrow& \mbox{LBFGS}(E_{\mu^{(k)}},
%%     \mathbf{w}^{(k)}, \gamma\mu^{(k)})\\
%%     \mu^{(k + 1)} &\leftarrow& \beta \mu^{(k)} \\
%%     k &\leftarrow& k + 1
%%   \end{eqnarray*}
%% } \Return $\mathbf{w}^{(k)}$
%% \label{Tab:pseudocode_lbfgs}
%% \end{algorithm}

%% This algorithm is not faster than
%% $\mathcal{O}(1/\epsilon)$: indeed a good optimization algorithm
%% for the sub-problem \eqref{eq:sopt_pb} is $\mathcal{O}(\sqrt{L_{\mu}/\epsilon})$
%% \cite{nesterov1983}, and $L_{\mu} \sim 1 / \mu \sim 1 / \epsilon$. We
%% believe that this bound is tight but a detailed analysis is
%% beyond the scope of this paper.

%% \section{Experiments on fMRI datasets}
%% \label{sec:experiments}
%% We now detail experiments done on publicly available
%% data. All experiments were run full-brain without spatial smoothing.

%% \paragraph{Visual recognition}
%% \label{subsec:haxby}
%% Our first benchmark dataset is a popular block-design fMRI dataset from a study on face and
%% object representation in human ventral temporal cortex  \cite{haxby2001}.
%% It consists of
%% 6 subjects with 12 runs per subject. In each run, the subjects
%% passively viewed images of eight object categories, grouped
%% in 24-second blocks separated by intermittent rest periods. This
%% experiment is a classification task: predicting the object category. We use a
%% two-class prediction target: $\mathbf{y}$ encodes faces versus houses.
%% The design matrix $\mathbf{X}$ is made of
%% time-series from the full-brain mask of $p = 23\,707$ voxels over $n =
%% 216$ TRs, of a single subject (subj1).

%% \paragraph{Mixed Gambles}
%% Our second benchmark dataset is a study in which
%% subjects were presented with mixed (gain/loss) gambles, and decided
%% whether they would accept each gamble \cite{mixedgambles2007}.  No outcomes of these gambles
%% were presented during scanning, but after the scan three gambles were
%% selected at random and played for real money. The prediction task here is
%% to predict the magnitude of the gain and thus a regression on a
%% continuous variable \cite{jimura2012}. The data is pooled across
%% subjects, resulting in 768 samples, each an image of 33\,177 voxels.

%% % We validate our algorithms on both simulated and real data.
%% \smallskip

%% We study the convergence of the algorithms for parameters close to the
%% optimal parameters set by 10-fold cross-validation to maximize prediction
%% accuracy.

%% \begin{figure*}
%% % generate with: ipython ../wip/tv_l1_solver/plot_parallel_plots.py bench/haxby_lr_11th.json .9 --pdb
%% \hspace*{-.01\linewidth}%
%% \includegraphics[width=.6\linewidth]{bench/haxby_lr_energy.pdf}
%% \hspace*{-.09\linewidth}%
%% \includegraphics[width=.6\linewidth]{bench/haxby_lr.pdf}%
%% % \vspace{-2ex}
%% \caption{TV$-\ell_1$ penalized Logistic Regression on the visual
%% recognition face-house
%%   discrimination task. \textbf{Left}: excess energy $E(\mathbf{w}_t) -
%% E(\mathbf{w}_{t})_{t \rightarrow \infty}$ as a function 
%% of time.
%% \textbf{Right}: convergence time of the various solvers for different
%% choice of regularization parameters.
%% Broken lines correspond to a tolerance of $10^{0}$,
%%   whilst full-lines correspond to $10^{-2}$.  The thick vertical line
%% indicates the best model selected by cross-validation.}
%% \label{Fig:HaxbyLR}
%% \end{figure*}

%% %% \paragraph{Haxby 2001: TV$-\ell_{1}$ penalized Least-Squares Regression}
%% %% See figure \ref{Fig:HaxbyMSE}
%% \begin{figure*}
%% % generate with: ipython ../wip/tv_l1_solver/plot_parallel_plots.py bench/haxby_mse_10th.json 1e-2 --pdb
%% \includegraphics[width=.6\linewidth]{bench/haxby_mse.pdf}%
%% \hspace{-.09\linewidth}%
%% % generate with: ipython ../wip/tv_l1_solver/plot_parallel_plots.py bench/poldrack_mse_12th.json 2e1 --pdb
%% \includegraphics[width=.6\linewidth]{bench/poldrack_mse.pdf}
%% % \vspace{-2ex}
%% \caption{TV$-\ell_1$ penalized Least-Squares Regression. \textbf{Left}:
%%   on the visual recognition  face-house discrimination task; \textbf{Right}: on the
%%   Mixed gambles dataset. Broken lines correspond to a tolerance of $10^{0}$,
%%   whilst full-lines correspond to $10^{-2}$. The thick vertical line
%% indicates the best model selected by cross-validation.}
%% \label{Fig:MSEtimes}
%% \end{figure*}

%% \section{Results: convergence times}
%% \label{sec:results}
%% Here, we present benchmark results for our experiments. Figure
%% \ref{Fig:HaxbyLR} gives results for the logistic regression run on the
%% visual recognition dataset: convergence plots of energy as a function of
%% time show that all methods are asymptotically decreasing. Figure
%% \ref{Fig:HaxbyLR} left, shows the time required to give a convergence
%% threshold, defined as a given excess energy compared to the lowest energy
%% achieved by all methods, for different choices of regularization
%% parameters. Similarly, figure \ref{Fig:MSEtimes} shows convergence times
%% for squared loss on both datasets. For these figures,
%% each solver was run for a maximum of 1 hour per problem. Solvers that do
%% not appear on a plot did not converge for the corresponding
%% tolerance and time budget.

%% For logistic loss, the most serious contender is
%% algorithm \ref{Tab:pseudocode_lbfgs}, LBFGS applied on a smooth
%% surrogate, followed by ADMM, however ADMM performance
%% varies markedly depending on the choice of $\rho$. For the squared loss
%% FISTA and algorithm \ref{Tab:pseudocode_lbfgs} are the best performers,
%% with FISTA achieving a clear lead for the larger mixed-gambles dataset.
%% Note that in the case of strong regularization the problem is better
%% conditioned, and first-order methods such as the
%% primal-dual approach can perform well.

%% %% \paragraph{Haxby: TV$-\ell_{1}$ penalized Logistic Regression}
%% %% TV$-\ell_{1}$ penalized Logistic Regression...See figure \ref{Fig:HaxbyLR}

%% \section{Conclusions: approaches to prefer}
%% \label{sec:discusion}

%% TV$-\ell_{1}$ penalized regression for brain imaging leads to
%% very high-dimensional, non-smooth and very ill-conditioned optimization
%% problems. We have presented a comprehensive comparison of state-of-the-art
%% solvers in these setting. Solvers were implemented with all known
%% algorithmic improvements and implementation were carefully profiled and
%% optimized.

%% Our results outline best strategies: monotonous FISTA with a adaptive
%% control of the tolerance of the TV proximal operator, in the case of
%% squared loss; smoothed quasi-newton based on surrogate upper-bounds of
%% the non-smooth norms for logistic loss. While these algorithms are
%% variants of existing approaches, we present here novel additions useful
%% for the TV or TV$-\ell_1$ settings. The fact that the smooth approaches emerge
%% as fast solvers on these non-smooth problems is not unexpected as
%% \emph{i)} the amount of regularization is small \emph{ii)} the prevailing
%% term is smooth and very ill conditioned, thus calling for second-order
%% methods such as Newton or quasi-Newton.

%% For neuroimaging applications, our study has highlighted the need to
%% converge to a good tolerance and the corresponding difficulties. Lack of
%% good solver and explicit control of tolerance can lead to brain maps and
%% conclusions that reflect properties of the solver more than of the
%% TV$-\ell_1$ solution.

%% %\section{Acknowledgements}
%% %% \label{subsec:acknowledgements}
%% %This work was supported by the  Human Brain Project.

%% \medskip \noindent
%% \textbf{Acknowledgments:}
%% This work was supported by the  Human Brain Project.

%% % ==========
%% % = biblio =
%% % ==========
%% % {\small
%% \bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv}
\end{document}

%
%

### 2014-07-16 matrix_games.py

@@ -1,0 +1,61 @@
+# Author: DOHMATOB Elvis Dopgima <gmdopp@gmail.com>
+
+from math import sqrt
+import numpy as np
+from scipy import linalg
+
+
+def proj_simplex(v, z=1.):
+    """Euclidean projection onto a simplex."""
+    v = np.array(v)
+    assert v.ndim == 1
+    n = len(v)
+    u = v.copy()
+    u.sort()
+    u = u[::-1]
+    cs = np.cumsum(u)
+    cs -= z
+    cs /= np.arange(1., n + 1)
+    rho = np.nonzero(u - cs > 0.)[0][-1]
+    theta = cs[rho]
+    return np.maximum(v - theta, 0.)
+
+
+def solve_matrix_game(A, max_iter=1000, tol=1e-6, verbose=1):
+    """Solve matrix game using Chambolle-Pock algorithm."""
+    A = np.array(A)
+    n, m = A.shape
+    x = np.zeros(m)
+    y = np.zeros(n)
+    xbar = x.copy()
+    L = linalg.svdvals(A)[0] ** 2
+    tau = sigma = .99 / sqrt(L)
+    assert tau * sigma * L <= 1.
+    theta = 1.
+    old_value = np.inf
+    for k in xrange(max_iter):
+        old_x = x.copy()
+        y += sigma * np.dot(A, xbar)
+        y = proj_simplex(y)
+        Aty = np.dot(A.T, y)
+        value = np.dot(x, Aty)
+        value_delta = old_value - value
+        old_value = value
+        if verbose:
+            print "Iteration %03i/%03i: value=%g, change=%g" % (
+                k + 1, max_iter, value, value_delta)
+        value_delta = abs(value_delta)
+        if value_delta < tol:
+            if verbose:
+                print "Converged after %i iterations (|change| < %g)." % (
+                    k + 1, tol)
+            break
+        x -= tau * Aty
+        x = proj_simplex(x)
+        xbar = x + theta * (x - old_x)
+
+    return x, y
+
+
+if __name__ == "__main__":
+    print solve_matrix_game(10 * np.random.randn(250, 150))

### 2014-07-23 paper.tex
typos

@@
 finding the best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$ for player 1, given a fixed
-(possibly mixed) strategy $y_0$ for player 2, where $E \in \{-1, 0, +1\}^{r,n}$ and $(1, 0, 0, ..., 0) =: e \in \mathbb{R}^r$ encode player
+(possibly mixed) strategy $y_0$ for player 2, where $E \in \{-1, 0, +1\}^{r,n}$ and $e \in \mathbb{R}^r$ encode player
 1's game plan, consistent with the rules of the game. In the language of convex-optimization, one can readily give the following saddle-point formulation for this problem. Viz,
@@
     G:=i_{\mathbb{R}_{+}^n}\\
-    F^*: (y, \eta) \mapsto (i_{\Delta_{m}^0}(y) + e^T\eta)
+    F^*: (y, \eta) \mapsto (i_{\Delta_{m}^0}(y) - e^T\eta)
   \end{aligned}
@@
     (1 + \tau \partial G)^{-1}: x \mapsto \Pi_{\mathbb{R}_{+}^n}(x) = (x)_+\\
-    (1 + \sigma \partial F^*)^{-1}: (y, \eta) \mapsto (\Pi_{\Delta_{m}^0}(y), \eta - \sigma e)% (z, \eta) \mapsto \bigl(y, \frac{\eta}{1 + \sigma}\bigr)
+    (1 + \sigma \partial F^*)^{-1}: (y, \eta) \mapsto (\Pi_{\Delta_{m}^0}(y), \eta + \sigma e)% (z, \eta) \mapsto \bigl(y, \frac{\eta}{1 + \sigma}\bigr)
   \end{aligned}
@@
 \begin{algorithm}[htb]
-\caption{Primal-dual algorithm for computing best response against on plained mixed strategies of opponent}%%  \textbf{Let}
+\caption{Primal-dual algorithm for computing best response against unplained mixed strategies of opponent}%%  \textbf{Let}
 \textbf{Initialize} $\tilde{x}^{(0)} = x^{(0)} \in \mathbb{R}^n$; $y^{(0)} \in \mathbb{R}^{m}$; $\eta^{(0)} \in \mathbb{R}^{m}$;
@@
     y^{(k+1)} &\leftarrow& \Pi_{\Delta_{m}^0}\bigl(y^{(k)} + \sigma A \tilde{x}^{(k)}\bigr)\\
-    \eta^{(k+1)} &\leftarrow& \eta^{(k)} - \sigma E \tilde{x}^{(k)} - \sigma e\\
+    \eta^{(k+1)} &\leftarrow& \eta^{(k)} - \sigma E \tilde{x}^{(k)} + \sigma e\\
     x^{(k+1)} &\leftarrow& (x^{(k)} - \tau A^Ty^{(k+1)} + E^T\eta^{(k+1)})_+\\

### 2014-07-23 paper.tex
typos
more typos
comestics

@@
 %\onecolumn
-\title{Primal-dual algorithm for computing best response against the unplanned mixed strategies of an opponent in two-person zero-sum sequential games}
+\title{A fast algorithm for computing the best response against the unplanned mixed strategies of an opponent in two-person zero-sum sequential games}
 
@@
 % applicative context remains a difficult challenge.
-
 % XXX : don't call it SPM but just "predictive regions or predictive
@@
 In this manuscript, we consider the problem of computing the best response against the  unplanned mixed strategies of an opponent
-in two-player zero-sum sequential games. An unplanned mixed strategy is simply a strategy chosen from a probability simplex.
+in two-player zero-sum sequential games. The problem considered here encompasses the problem of computing the best response against an opponent's fixed strategy.
+The problem considered here encompasses the problem of computing the best response against an opponent's fixed strategy.
+An unplanned mixed strategy is simply a strategy chosen from a probability simplex.
 The proposed technique employs the primal-dual scheme of A. Chambolle and T. Pock to solve the corresponding saddle-point problem.
-The resulting algorithm is simple (all resolvent operators can be effectively computed quasi closed-form, using only elementary algebraic operations)
- and is orders of magnitude more efficient than state-of-the-art algorithms like those based on Linear Programming, Interior-Point methods,
-and more recently, the Nesterov Excessive Gap Technique. The problem considered here encompasses the problem of computing the best response against an opponent's fixed strategy.
-We conclude by exhibiting results on Texas Hold'em Poker.
+The resulting algorithm is simple: all resolvent operators can be effectively computed quasi closed-form, using only elementary algebraic operations.
+%%  and is orders of magnitude more efficient than state-of-the-art algorithms like those based on Linear Programming, Interior-Point methods,
+%% and more recently, the Nesterov Excessive Gap Technique.
+By way of example, we conclude by exhibiting results on Texas Hold'em Poker.
 \end{abstract}
@@
 \label{sec:intro}
-%% Let $A \in \mathbb{R}^{m,n}$ be the payoff matrix; let $E \in \mathbb{R}^{r,n}$ and $e \in \mathbb{R}^r$ be a matrix so that player 1 wishes only to use those strategies  $x \in \mathbb{R}_{+}^n$ for which $Ex = e$, i.e $x \in \mathbb{R}_{+}^n$
-%%  %% from player \textbf{row} perspective, so that player \textbf{row} gains $A_{i,j}$ and player \textbf{column} forfeits $A_{i,j}$ euros if the former plays the $i$th row and the former players the $j$th column.
 
-%% We denote by $\mathbf{y} \in \mathbb{R}^{n}$ the targets to
-%% be predicted, and $\mathbf{X}\in\mathbb{R}^{n \times p}$ the
-%% brain images related to the presentation of different
-%% stimuli. $p$ is the number of voxels and $n$ the number of
-%% samples (images). Typically, $p \sim 10^3-10^5$ (for a whole volume),
-%% while $n \sim 10-10^3$.  Let $\Omega \subset \mathbb{R}^3$ be
-%% the 3D image domain, discretized on a finite grid. The coefficients
-%% $\mathbf{w}$ define a spatial map in $\mathbb{R}^p$. Its gradient at a
-%% voxel $j \in \Omega $ reads\footnote{Where it is understood that the feature vector $w$ is ``unmasked''
-%% into a full 3D volume before the spatial operators are applied.}:
-%% \begin{eqnarray}
-%%   \mathbf{\nabla} w(j) := [\nabla_{x} w(j),
-%%     \nabla_{y} w(j), \nabla_{z} w(j)] \in
-%%   \mathbb{R}^3,
-%% \end{eqnarray}
-%% where $\nabla_{u}$ is the spatial difference operator along
-%% the $u$-axis. Thus $\mathbf{\nabla}$
-%% is a linear operator $\in \mathbb{R}^{3p \times
-%%   p}$ with adjoint $\mathbf{\nabla} ^T = -\dive \in \mathbb{R}^{p
-%%   \times 3p}$.
-Let $\tilde{\nabla} := [(1 - \rho)\nabla^T, \rho I]^T$ be the identity-augmented spatial gradient operator.
-Finally, let us recall the definition of the $(q, 1)$ mixed-norm\footnote{Where $q$ itself is allowed to be a mixed-norm.}:
-%% \begin{equation}
-%% \|v\|_{q, 1} := \sum_{j}{\|v_{j}\|_{q}}
-%% \end{equation}
-
-Consider a two-person zero-sum sequential game with payoff matrix $A \in \mathbb{R}^{m,n}$. Consider the problem of
+To begin, let us introduce some technical vocabulary we will be using in this paper. The reader should lookup any standard textbook
+on convex optimization for a tutorial introduction to these notions. Viz,\\
+$\mathbb{R}_+$: \quad \textit{the nonnegative part of the real-line $\mathbb{R}$}\\
+$(x)_+$: \quad \textit{the component-wise maximum of the vector $x$ and 0}\\
+$\Delta_{m}$: \quad \textit{the $m-$dimensional probability simplex
+%$\{x \in \mathbb{R}_{+}^m\text{ }| \text{ }\textbf{1}^Tx = 1\}$
+}\\
+$\Pi_C$: \quad \textit{the euclidean projector onto the convex set $C$}\\
+$\|K\|$: \quad \textit{the operator norm of a matrix $K$}\\
+$F^*$: \quad \textit{the Fenchel transform of a convex l.s.c\footnote{lower semi-contnuous} function $F$}\\
+$E^{-1}(U)$: \quad \textit{the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{r,n}$, namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$}\\\\
+Now, consider a two-person zero-sum sequential game with payoff matrix $A \in \mathbb{R}^{m,n}$. We are interested in the problem of
 finding the best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$ for player 1, given a fixed
@@
 
-where $\Delta_{m}^0$ is the singleton $\{y_0\}$ if $y_0$ is known, otherwise it is the $m-$dimensional probability simplex $\Delta_{m} := \{x \in \mathbb{R}_{+}^m \text{ s.t }\textbf{1}^Tx = 1\}$.\\\\
-Noting that $i_{E^{-1}(\{e\})}(x) = \underset{\eta \in \mathbb{R}^r}{max}\text{ }\eta^T(e - Ex)$, one can re-write (1) as:
+where $\Delta_{m}^0$ is $\Delta_{m}$ if $y_0$ is known, otherwise it is the singleton
+%% \footnote{Note that the origin $\textbf{0} \in \mathbb{R}^m$ can be seen a degenerate simplex with radius $0^+$,
+%% whilst a singleton  $\{y_0\}$ can be seen as a $y_0-$translation of this simplex.}
+$\{y_0\}$.\\\\
+
+In section II, we give a brief overview of existing methods for solving (1). We elaborate our proposed primal-dual algorithm in section III.
+
+\section{Related work}
+pending...
+
+\section{The algorithm}
+Noting that $i_{E^{-1}(\{e\})}(x) = \underset{\theta \in \mathbb{R}^r}{max}\text{ }\theta^T(e - Ex)$, one can re-write (1) as:
 \begin{equation}
-  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m, \eta \in \mathbb{R}^r}{max}\text{ }[y,\eta]^T\left[ \begin{array}{@{}cc@{}}
-    A \\ \hline
-    -E
-    \end{array} \right]x + G(x) - F^*(y, \eta)
+  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m, \theta \in \mathbb{R}^r}{max}\text{ }
+  \left[\begin{array}{@{}cc@{}}y\\\theta\end{array}\right]^TKx + G(x) - F^*(y, \theta)
 \end{equation}
@@
 \begin{equation}
+  \left.
   \begin{aligned}
+    K := \left[\begin{array}{@{}cc@{}}A\\-E\end{array}\right]\\
     G:=i_{\mathbb{R}_{+}^n}\\
-    F^*: (y, \eta) \mapsto (i_{\Delta_{m}^0}(y) - e^T\eta)
+    F^*: (y, \theta) \mapsto (i_{\Delta_{m}^0}(y) - e^T\theta)
   \end{aligned}
+  \right\}
 \end{equation}
-with resolvent operators given by
+
+Furthermore, $F^*$ and $G$ have resolvent (a.k.a \textit{proximity}) operators given by the simple formulae:
 \begin{equation}
+  \left.
   \begin{aligned}
     (1 + \tau \partial G)^{-1}: x \mapsto \Pi_{\mathbb{R}_{+}^n}(x) = (x)_+\\
-    (1 + \sigma \partial F^*)^{-1}: (y, \eta) \mapsto (\Pi_{\Delta_{m}^0}(y), \eta + \sigma e)% (z, \eta) \mapsto \bigl(y, \frac{\eta}{1 + \sigma}\bigr)
+    (1 + \sigma \partial F^*)^{-1}: (y, \theta) \mapsto (\Pi_{\Delta_{m}^0}(y), \theta + \sigma e)% (z, \theta) \mapsto \bigl(y, \frac{\theta}{1 + \sigma}\bigr)
   \end{aligned}
+  \right\}
 \end{equation}
-This way, we obtain following algorithm which solves (2).
+This way, we obtain following primal-dual algorithm for solving (2).
 
@@
 \caption{Primal-dual algorithm for computing best response against unplained mixed strategies of opponent}%%  \textbf{Let}
-\textbf{Initialize} $\tilde{x}^{(0)} = x^{(0)} \in \mathbb{R}^n$; $y^{(0)} \in \mathbb{R}^{m}$; $\eta^{(0)} \in \mathbb{R}^{m}$;
-$\tau, \sigma > 0 \text{ s.t. }\tau\sigma (\|A\|^2 + \|E\|^2) \le 1$; $k = 0$.\\
+\textbf{Initialize} $\tilde{x}^{(0)} = x^{(0)} \in \mathbb{R}^n$; $y^{(0)} \in \mathbb{R}^{m}$; $\theta^{(0)} \in \mathbb{R}^{r}$;
+$\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 \le 1$; $k = 0$.\\
 \Repeat{
@@
     y^{(k+1)} &\leftarrow& \Pi_{\Delta_{m}^0}\bigl(y^{(k)} + \sigma A \tilde{x}^{(k)}\bigr)\\
-    \eta^{(k+1)} &\leftarrow& \eta^{(k)} - \sigma E \tilde{x}^{(k)} + \sigma e\\
-    x^{(k+1)} &\leftarrow& (x^{(k)} - \tau A^Ty^{(k+1)} + E^T\eta^{(k+1)})_+\\
+    \theta^{(k+1)} &\leftarrow& \theta^{(k)} - \sigma E \tilde{x}^{(k)} + \sigma e\\
+    x^{(k+1)} &\leftarrow& \bigl(x^{(k)} - \tau A^Ty^{(k+1)} + E^T\theta^{(k+1)}\bigr)_+\\
     \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\

### 2014-07-25 paper.tex
implemented primal-dual algo for computing best response strategy

@@
 %\onecolumn
-\title{A fast algorithm for computing the best response against the unplanned mixed strategies of an opponent in two-person zero-sum sequential games}
+\title{A fast algorithm for computing best response behaviour strategies in two-person sequential games}
 
@@
 % maps"
-In this manuscript, we consider the problem of computing the best response against the  unplanned mixed strategies of an opponent
-in two-player zero-sum sequential games. The problem considered here encompasses the problem of computing the best response against an opponent's fixed strategy.
-The problem considered here encompasses the problem of computing the best response against an opponent's fixed strategy.
-An unplanned mixed strategy is simply a strategy chosen from a probability simplex.
-The proposed technique employs the primal-dual scheme of A. Chambolle and T. Pock to solve the corresponding saddle-point problem.
-The resulting algorithm is simple: all resolvent operators can be effectively computed quasi closed-form, using only elementary algebraic operations.
+In this manuscript, we consider the problem of computing the best response against an opponent's realization plan in two-person sequential games.
+The proposed technique employs the primal-dual scheme of A. Chambolle and T. Pock to solve the corresponding contrained convex-optimization problem.
+The resulting algorithm is simple: all resolvent operators can be effectively computed in closed-form, using only elementary algebraic operations.
 %%  and is orders of magnitude more efficient than state-of-the-art algorithms like those based on Linear Programming, Interior-Point methods,
@@
 \begin{IEEEkeywords}
-  game theory; two-person zero-sum sequential game; best response; mixed strategy; simplex; convex-optimization; saddle-point problem; primal-dual scheme
+  game theory; two-person sequential game; best response; convex-optimization; contraint; primal-dual scheme
 \end{IEEEkeywords}
 
-\section{Introduction: Statement of the problem}
+\section{Introduction}
 \label{sec:intro}
+\subsection{Notation and Terminology}
+To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
+(for example \cite{sboyd}) on convex optimization for a tutorial introduction to these notions. Viz,\\
+\textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
+$\mathbb{R}_+$: \quad \textit{nonnegative part of the real-line $\mathbb{R}$}\\
+$i_C$: \quad \textit{indicator function of the convex set $C$}\\
+$\Pi_C$: \quad \textit{euclidean projector onto the convex set $C$}\\
+$(x)_+$: \quad \textit{component-wise maximum of the vector $x$ and 0}\\
+$\|K\|$: \quad \textit{operator norm of the matrix $K$}\\
+$F^*$: \quad \textit{Fenchel transform of the convex l.s.c function $F$}\\
+$E^{-1}(U)$: \quad \textit{pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
+namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$}
 
-To begin, let us introduce some technical vocabulary we will be using in this paper. The reader should lookup any standard textbook
-on convex optimization for a tutorial introduction to these notions. Viz,\\
-$\mathbb{R}_+$: \quad \textit{the nonnegative part of the real-line $\mathbb{R}$}\\
-$(x)_+$: \quad \textit{the component-wise maximum of the vector $x$ and 0}\\
-$\Delta_{m}$: \quad \textit{the $m-$dimensional probability simplex
-%$\{x \in \mathbb{R}_{+}^m\text{ }| \text{ }\textbf{1}^Tx = 1\}$
-}\\
-$\Pi_C$: \quad \textit{the euclidean projector onto the convex set $C$}\\
-$\|K\|$: \quad \textit{the operator norm of a matrix $K$}\\
-$F^*$: \quad \textit{the Fenchel transform of a convex l.s.c\footnote{lower semi-contnuous} function $F$}\\
-$E^{-1}(U)$: \quad \textit{the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{r,n}$, namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$}\\\\
-Now, consider a two-person zero-sum sequential game with payoff matrix $A \in \mathbb{R}^{m,n}$. We are interested in the problem of
-finding the best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$ for player 1, given a fixed
-(possibly mixed) strategy $y_0$ for player 2, where $E \in \{-1, 0, +1\}^{r,n}$ and $e \in \mathbb{R}^r$ encode player
-1's game plan, consistent with the rules of the game. In the language of convex-optimization, one can readily give the following saddle-point formulation for this problem. Viz,
+\subsection{Statement of the problem}
+Consider a two-person zero-sum sequential game with payoff matrix $A \in \mathbb{R}^{m,n}$. We are interested in the problem of
+finding the best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$ for player 2, given a fixed
+(possibly mixed) strategy $y_0$ for player 1, where $E \in \{-1, 0, +1\}^{p,n}$ and $(1, 0, 0, ..., 0) =: e \in \mathbb{R}^p$.
+Recall that $E$ and $e$ encode linear constraints on player 1's ``admissible'' realization plans $x$, in the sequential form representation
+of the game (See \cite{bernhard-1996, benhard-agt} for theory on \textit{sequential-form representation}). In the language of convex-optimization,
+one can readily give the following saddle-point formulation for this problem. Viz,
 
 \begin{equation}
-  \underset{x \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})}{min}\text{ }\underset{y \in \Delta_{m}^0}{max}\text{ }y^TAx
+  \underset{x \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})}{min}\text{ }-y_0^TAx
 \end{equation}
 
-where $\Delta_{m}^0$ is $\Delta_{m}$ if $y_0$ is known, otherwise it is the singleton
-%% \footnote{Note that the origin $\textbf{0} \in \mathbb{R}^m$ can be seen a degenerate simplex with radius $0^+$,
-%% whilst a singleton  $\{y_0\}$ can be seen as a $y_0-$translation of this simplex.}
-$\{y_0\}$.\\\\
-
-In section II, we give a brief overview of existing methods for solving (1). We elaborate our proposed primal-dual algorithm in section III.
+In section II, we give a brief overview of existing methods for solving (1). We elaborate our proposed algorithm in section III.
 
 \section{Related work}
-pending...
+Pending...
 
-\section{The algorithm}
-Noting that $i_{E^{-1}(\{e\})}(x) = \underset{\theta \in \mathbb{R}^r}{max}\text{ }\theta^T(e - Ex)$, one can re-write (1) as:
+\section{The proposed algorithm}
+In this section we present the algorithm which is the purpose of this paper, namely an algorithm for solving (1).
+
+\subsection{Derivation of the algorithm}
+First observe that (1) can be re-written in the form:
 \begin{equation}
-  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m, \theta \in \mathbb{R}^r}{max}\text{ }
-  \left[\begin{array}{@{}cc@{}}y\\\theta\end{array}\right]^TKx + G(x) - F^*(y, \theta)
+  \underset{x \in \mathbb{R}^n}{min}\text{ }{f(-Ax) + g(x)}
+\end{equation}
+where:\\
+\begin{equation}
+  \left.
+  \begin{aligned}
+    g := i_{E^{-1}(\{b\})} + i_{\mathbb{R}_{+}^m}\\
+    f: z \mapsto y_0^Tz
+    \end{aligned}
+  \right\}
+\end{equation}
+
+Finally, the primal-dual formulation of this problem is:
+\begin{equation}
+  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m}{max}\text{ }{y^T(-A)x_0 + g(x) - f^*(y))}
+\end{equation}
+
+Now, let's observe that $i_{E^{-1}(\{e\})}(x) = \underset{\zeta \in \mathbb{R}^q}{max}\text{ }\zeta^T(e - Ex)$, and so one can re-write (2) as:
+\begin{equation}
+  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m, \zeta \in \mathbb{R}^p}{max}\text{ }
+  \begin{bmatrix}y\\\zeta\end{bmatrix}^TKx + G(x) - F^*(y, \zeta)
 \end{equation}
@@
   \begin{aligned}
-    K := \left[\begin{array}{@{}cc@{}}A\\-E\end{array}\right]\\
-    G:=i_{\mathbb{R}_{+}^n}\\
-    F^*: (y, \theta) \mapsto (i_{\Delta_{m}^0}(y) - e^T\theta)
+    K := -\begin{bmatrix}A\\E\end{bmatrix}\\
+    G := i_{\mathbb{R}_{+}^n}\\
+    F^*: (y, \zeta) \mapsto (i_{\{y_0\}} - \zeta^Te)
   \end{aligned}
@@
   \begin{aligned}
-    (1 + \tau \partial G)^{-1}: x \mapsto \Pi_{\mathbb{R}_{+}^n}(x) = (x)_+\\
-    (1 + \sigma \partial F^*)^{-1}: (y, \theta) \mapsto (\Pi_{\Delta_{m}^0}(y), \theta + \sigma e)% (z, \theta) \mapsto \bigl(y, \frac{\theta}{1 + \sigma}\bigr)
+    (1 + \tau \partial G)^{-1} = \Pi_{\mathbb{R}_+^n}: x \mapsto (x)_+\\
+    (1 + \sigma \partial F^*)^{-1}: (y, \zeta) \mapsto (y_0, \zeta + \sigma e)
   \end{aligned}
@@
 \begin{algorithm}[htb]
-\caption{Primal-dual algorithm for computing best response against unplained mixed strategies of opponent}%%  \textbf{Let}
-\textbf{Initialize} $\tilde{x}^{(0)} = x^{(0)} \in \mathbb{R}^n$; $y^{(0)} \in \mathbb{R}^{m}$; $\theta^{(0)} \in \mathbb{R}^{r}$;
-$\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 \le 1$; $k = 0$.\\
+\caption{Primal-dual algorithm for computing best response against opponent's realization plan $y$}%%  \textbf{Let}
+\textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
+$\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$; $k = 0$.\\
+\textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
 \Repeat{
@@
   \begin{eqnarray*}
-    y^{(k+1)} &\leftarrow& \Pi_{\Delta_{m}^0}\bigl(y^{(k)} + \sigma A \tilde{x}^{(k)}\bigr)\\
-    \theta^{(k+1)} &\leftarrow& \theta^{(k)} - \sigma E \tilde{x}^{(k)} + \sigma e\\
-    x^{(k+1)} &\leftarrow& \bigl(x^{(k)} - \tau A^Ty^{(k+1)} + E^T\theta^{(k+1)}\bigr)_+\\
+    \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma (e - E\tilde{x}^{(k)})\\
+    x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
     \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
@@
   \end{eqnarray*}
-} \Return $x^{(k)}$
+} \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
 \label{Tab:pseudocode_lbfgs}
 \end{algorithm}
+
+\subsection{Primal-dual gap stopping-criterion and convergence of the algorithm}
+Pending...
 
@@
 %% \end{eqnarray}
-%% where $J(\mathbf{w}) := \theta\|\mathbf{w}\|_{\ell_{1}} + (1 -
-%% \theta)\|\mathbf{w}\|_{TV}$ is the regularization and $\alpha \ge 0$
+%% where $J(\mathbf{w}) := \zeta\|\mathbf{w}\|_{\ell_{1}} + (1 -
+%% \zeta)\|\mathbf{w}\|_{TV}$ is the regularization and $\alpha \ge 0$
 %% controls the amount of regularization. The
-%% parameter $\theta \in [0, 1]$, also known as the $\ell_{1}$ \textit{ratio}, is the trade-off between the
+%% parameter $\zeta \in [0, 1]$, also known as the $\ell_{1}$ \textit{ratio}, is the trade-off between the
 %% sparsity-inducing penalty $\ell_{1}$ (Lasso) and TV (isotropic Total
@@
 %%     \text{where} \quad
-%%     J_{\mu}(\mathbf{w}) :=\theta \|\mathbf{w}\|_{\ell_{1},\mu} +
-%%     (1 - \theta)\|\mathbf{w}\|_{TV, \mu} \quad
+%%     J_{\mu}(\mathbf{w}) :=\zeta \|\mathbf{w}\|_{\ell_{1},\mu} +
+%%     (1 - \zeta)\|\mathbf{w}\|_{TV, \mu} \quad
 %% \end{align}

### 2014-07-25 best_response.py

@@ -1,0 +1,66 @@
+import numpy as np
+from scipy import linalg
+
+
+def best_response(A, E, e, y0, max_iter=1000, tol=1e-4):
+    """Computes best response to an opponent's realization plan in a two-person
+    sequential game.
+
+    Parameters
+    ----------
+    A: 2D array of size (m, n)
+        Payoff matrix.
+
+    E: 2D array of shape (p, n)
+        Constraints matrix for our realization plans (x)
+
+    e: 1D array of length p
+        Our realization plans are constrained like so: Ex = e, x>=0.
+
+    y0: 1D array of length m
+        Fixed realization plan of opponent (player 2).
+
+    """
+
+    _, n = A.shape
+    assert E.shape[1] == n
+    p, _ = E.shape
+    x = np.zeros(n)
+    xbar = x.copy()
+    zeta = np.zeros(p)
+    old_gain = np.inf
+    L = linalg.svdvals(np.vstack((A, E)))[0]
+    tau = sigma = .99 / L
+    assert tau * sigma * L * L < 1.
+    const = tau * A.T.dot(y0)
+    for k in xrange(max_iter):
+        old_x = x.copy()
+        gain = -np.dot(x.T, const) / tau
+        gain_delta = old_gain - gain
+        old_gain = gain
+        print "Iteration %03i/%03i: gain=%g, change=%g" % (
+            k + 1, max_iter, gain, gain_delta)
+        gain_delta = abs(gain_delta)
+        if gain_delta < tol:
+            print "Converged (gain delta < %g)" % tol
+            break
+        zeta += sigma * (e - E.dot(xbar))
+        x += const + E.T.dot(zeta)
+
+        x = np.maximum(x, 0.)
+
+        xbar = 2 * x - old_x
+
+    return x
+
+
+if __name__ == "__main__":
+    A = np.zeros((5, 3))
+    A[2:4, 1:] = [[1, -1], [-2, 4]]
+    A[-1, 0] = 1
+    A = A.T
+    E = np.array([[1, 0, 0, 0, 0], [-1, 1, 1, 0, 0], [-1, 0, 0, 1, 1]])
+    e = np.eye(E.shape[0])[0]
+    y0 = np.array([1, .66, .33])
+    xstar = best_response(A, E, e, y0, tol=1e-4)
+    print "x* =", xstar

### 2014-07-25 paper.tex
more

@@
 To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
-(for example \cite{sboyd}) on convex optimization for a tutorial introduction to these notions. Viz,\\
+(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,\\
 \textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
@@
   \underset{x \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})}{min}\text{ }-y_0^TAx
+  \label{eq:opt_pb}
 \end{equation}
 
-In section II, we give a brief overview of existing methods for solving (1). We elaborate our proposed algorithm in section III.
+In section II, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}. We elaborate our proposed algorithm in section III.
 
@@
 \section{The proposed algorithm}
-In this section we present the algorithm which is the purpose of this paper, namely an algorithm for solving (1).
+\label{sec:algo}
+In this section we present the algorithm which is the purpose of this paper, namely an algorithm for solving \eqref{eq:opt_pb}.
+Our algorithm (Alg.\ref{Tab:pseudocode_pb}) is a use-case of the generic primal-dual algorithm of A.
+Chambolle and T.
+Pock, namely Algorithmic 1 of \cite{chambolle2010}.
 
@@
   \begin{bmatrix}y\\\zeta\end{bmatrix}^TKx + G(x) - F^*(y, \zeta)
+  \label{eq:pd_opt}
 \end{equation}
@@
 \end{equation}
-This way, we obtain following primal-dual algorithm for solving (2).
+
+Using these ingredients, we obtain the primal-dual algorithm given in Alg.\ref{Tab:pseudocode_pb}, 
+for solving \eqref{eq:pd_opt}, and thus \eqref{eq:opt_pb}.
 
@@
 } \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
-\label{Tab:pseudocode_lbfgs}
+\label{Tab:pseudocode_pb}
 \end{algorithm}
@@
 
-%\begin{remark}
-%% Due to the independence of $(1 + \sigma \partial F^*)^{-1}$ on $\sigma$, we can always choose the pair
-%% $(\tau, \sigma)$ , such that $\tau\sigma \|\tilde{\nabla}\|^2 \le 1$ and $\tau \rho(X^TX) \le \alpha$.
-% \end{remark}
-%% We note that if the pair $(\tau, \sigma)$ is chosen such that $\tau \rho(X^TX) < \alpha$,
-%% then (6) can be approximated by
-%% \begin{equation}
-%% (1 + \tau \partial G)^{-1}(w) \approx (1 - \frac{\tau}{\alpha}X^TX)(w - \frac{\tau}{\alpha} X^Ty)
-%% \end{equation}
+\medskip \noindent
+\textbf{Acknowledgments:}
+This work was supported by the  Human Brain Project.
 
-%% Prediction of external variates from brain images has seen an
-%% explosion of interest in the past decade, in cognitive neurosciences
-%% to predict cognitive content from functional imaging data such as fMRI
-%% \cite{haxby2001,kamitani2005,haynes2006} or for medical diagnosis
-%% purposes \cite{fan2008}. Given that brain images are
-%% high-dimensional objects --composed of many voxels-- and the
-%% number of samples is limited by the cost of acquisition, the
-%% estimation of a multivariate predictive model is ill-posed and calls
-%% for regularization. This regularization is central as it encodes the
-%% practicioner's priors on the spatial maps. For brain mapping, it has
-%% been shown that regularization schemes based on sparsity (Lasso or
-%% $\ell_1$ family of models) \cite{carroll2009} or Total Variation (TV),
-%% that promotes spatial contiguity \cite{michel2011}, perform well for
-%% prediction. The combination of these, hereafter dubbed
-%% ``TV$-\ell_{1}$'', extracts spatially-informed %% --and thus, more
-%% %% interpretable-- 
-%% brain maps that are more stable \cite{baldassarre2012}
-%% and recover better the predictive regions
-%% \cite{gramfort-etal:2013a}. In addition, this prior leads to
-%% state-of-the-art methods for extraction of brain atlases
-%% \cite{abraham2013}.
-
-%% However, the corresponding optimization problem is
-%% intrinsically hard to solve. The reason for this is two-fold. First and
-%% foremost, in fMRI studies, the design matrix $\mathbf{X}$ is ``fat''
-%% ($n \ll p$), dense, ill-conditioned with little algebraic structure to be
-%% exploited, making the optimization problem ill-conditioned. Second, the
-%% penalty is not smooth, and while the $\ell_{1}$ term is \emph{proximable}
-%% (via \emph{soft-thresholding}), the TV term does not admit a closed-form proximal
-%% operator. Thus neither gradient-based methods (like Newton, BFGS, etc.) nor proximal methods (like
-%% ISTA~\cite{daubechies2004}, FISTA~\cite{beck2009a}) can be used in the
-%% traditional way.
-
-%% While the quality of the optimization may sound as a minor
-%% technical problem to the practitioner, the sharpening effect of TV and the
-%% sparsity-inducing effect of $\ell_1$ come into play only for
-%% well-optimized solutions. As a result, the brain maps extracted vary
-%% significantly as a function of the tolerance on the solver (see
-%% Fig.\,\ref{fig:maps_tolerance}).
-
-%% \begin{figure*}
-%% \includegraphics[width=.32\linewidth]{maps/face_vs_house_tol_0_1.pdf}%
-%% \llap{\color{white}\raisebox{.17\linewidth}{\rlap{\sffamily Stopping:
-%%       $\Delta E < 10^{-1}$}}\hspace*{.315\linewidth}}\hfill%
-%% \includegraphics[width=.32\linewidth]{maps/face_vs_house_tol_0_001.pdf}%
-%% \llap{\color{white}\raisebox{.17\linewidth}{\rlap{\sffamily Stopping:
-%%       $\Delta E < 10^{-3}$}}\hspace*{.315\linewidth}}\hfill%
-%% \includegraphics[width=.32\linewidth]{maps/face_vs_house_tol_1e-05.pdf}%
-%% \llap{\color{white}\raisebox{.17\linewidth}{\rlap{\sffamily Stopping:
-%%       $\Delta E < 10^{-5}$}}\hspace*{.315\linewidth}}%
-
-%% \caption{TV$-\ell_1$ maps for the face-house discrimination task on
-%%   the visual recognition dataset, with regularization parameters chosen by
-%%   cross-validation, for different stopping criteria.
-%%   Note that
-%%   the stopping criterion is defined as a threshold on the energy
-%%   decrease per one iteration of the algorithm, and thus differs from
-%%   the tolerance displayed in figure \ref{Fig:MSEtimes}.  This figure shows
-%%   the importance of convergence for problem \eqref{eq:opt_pb}, and motivates
-%%   the need for a fast solver.}%
-%% \label{fig:maps_tolerance}
-%% \end{figure*}
-
-%% In this contribution, we compare a comprehensive list of
-%% solvers, all implemented with great care, for solving TV$-\ell_1$
-%% regression with a focus on convergence time. First we state the formal
-%% problem solved.
-%% In section \ref{sec:algos}
-%% we present the various algorithms. Experiments done and the results obtained are presented in secions
-%%  \ref{sec:experiments} and \ref{sec:results}
-%% respectively. Section \ref{sec:discusion} concludes the paper with
-%% general recommendations.
-
-%% \section{Formal problem statement and notations}
-
-%% \label{sec:problem_statement}
-
-%% We denote by $\mathbf{y} \in \mathbb{R}^{n}$ the targets to
-%% be predicted, and $\mathbf{X}\in\mathbb{R}^{n \times p}$ the
-%% brain images related to the presentation of different
-%% stimuli. $p$ is the number of voxels and $n$ the number of
-%% samples (images). Typically, $p \sim 10^3-10^5$ (for a whole volume),
-%% while $n \sim 10-10^3$.  Let $\Omega \subset \mathbb{R}^3$ be
-%% the 3D image domain, discretized on a finite grid. The coefficients
-%% $\mathbf{w}$ define a spatial map in $\mathbb{R}^p$. Its gradient at a
-%% voxel $\omega \in \Omega $ reads:
-%% \begin{eqnarray}
-%%   \mathbf{\nabla} \mathbf{w}(\omega) := [\nabla_{x} \mathbf{w}(\omega),
-%%     \nabla_{y} \mathbf{w}(\omega), \nabla_{z} \mathbf{w}(\omega)] \in
-%%   \mathbb{R}^3,
-%% \end{eqnarray}
-%% where $\nabla_{u}$ is the spatial difference operator along
-%% the $u$-axis. Thus $\mathbf{\nabla}$
-%% is a linear operator $\in \mathbb{R}^{3p \times
-%%   p}$ with adjoint $\mathbf{\nabla} ^T = -\dive \in \mathbb{R}^{p
-%%   \times 3p}$. $\Delta := \nabla ^T \nabla \in
-%% \mathbb{R}^{p \times p}$ is the Laplace operator.
-
-%% TV$-\ell_1$ regression leads to the following non-smooth convex
-%% optimization problem \cite{gramfort-etal:2013a}:
-%% \begin{eqnarray}
-%%   \mathbf{\hat{w}} := \argmin_{\mathbf{w}}\;\{E(\mathbf{w}) :=
-%%   \mathcal{L}(\mathbf{y}, \mathbf{X}, \mathbf{w}) + \alpha
-%%   J(\mathbf{w})\},
-%%   \label{eq:opt_pb}
-%% \end{eqnarray}
-%% where $J(\mathbf{w}) := \zeta\|\mathbf{w}\|_{\ell_{1}} + (1 -
-%% \zeta)\|\mathbf{w}\|_{TV}$ is the regularization and $\alpha \ge 0$
-%% controls the amount of regularization. The
-%% parameter $\zeta \in [0, 1]$, also known as the $\ell_{1}$ \textit{ratio}, is the trade-off between the
-%% sparsity-inducing penalty $\ell_{1}$ (Lasso) and TV (isotropic Total
-%% Variation):
-%% % also known as the $\ell_{1}$\emph{-ratio},
-%% % XXX = $\ell_{1}$\emph{-ratio} is sklearn jargon
-%% \begin{eqnarray}
-%% \|\mathbf{w}\|_{\ell_{1}} := \sum_{\omega \in
-%%   \Omega}|\mathbf{w}(\omega)|;\;\;\textbf{ }\|\mathbf{w}\|_{TV} :=
-%% \sum_{\omega \in \Omega} \|\nabla \mathbf{w}(\omega)\|_{2} \enspace .
-%% %% \\
-%% %% &=& \sum_{\omega \in
-%% %% \Omega}
-%% %% \sqrt{\nabla_{x} \mathbf{w}(\omega)^2 + \nabla_{y} \mathbf{w}(\omega)^2 +
-%% %%   \nabla_{z}\mathbf{w}(\omega)^2}\\
-%% \end{eqnarray}
-%% $\mathcal{L}(\mathbf{y}, \mathbf{X}, \mathbf{w})$
-%% is the loss function. Here, we focus on the squared loss
-%% and the logistic loss, defined \emph{e.g.} in \cite{michel2011}. The
-%% squared loss is natural for regression settings, where $\mathbf{y}$ is a
-%% continuous variable, but it may also be used for classification
-%% \cite{suykens2002}. The logistic loss is harder to optimize, but
-%% more natural for classification settings.
-
-%% \section{Algorithms}
-%% \label{sec:algos}
-
-%% In this section, we present the algorithms we benchmarked for solving
-%% problem \eqref{eq:opt_pb}.
-
-%% \paragraph{ISTA/FISTA}
-%% ISTA~\cite{daubechies2004}, and its accelerated variant
-%% FISTA~\cite{beck2009a}, are proximal gradient approaches: the go-to
-%% methods for non-smooth optimization. In their seminal introduction of TV
-%% for fMRI, Michel \emph{et al.} \cite{michel2011} relied on ISTA.
-%% The challenge of these methods for TV is that the proximal operator
-%% %% \footnote{The proximal operator (or prox for short) can be seen as a generalization of projection unto convex set.}
-%%   of TV
-%% cannot be computed exactly; we approximate it in an inner FISTA loop
-%% \cite{beck2009b,michel2011}.
-%% % , \cite{gramfort-etal:2013a}.
-%% %%  and must itself be solved by a
-%% %% FISTA\footnote{Note that solving TV and TV$-\ell_1$ are formally very
-%% %% close \cite{gramfort-etal:2013a}.
-%% % }
-%% % \cite{beck2009b,michel2011}. 
-%% Here, for all FISTA implementations we use
-%% the faster monotonous FISTA variant \cite{beck2009b}. We control the
-%% optimality of the TV proximal via its dual gap \cite{michel2011} and
-%% use a line-search strategy in the monotonous FISTA to decrease the
-%% tolerance as the algorithm progresses, ensuring convergence of the
-%% TV-$\ell_1$ regression with good accuracy.
-
-%% \paragraph{ISTA/FISTA with backtracking}
-%% A key ingredient in FISTA's convergence is the Lipschitz
-%% constant $L(\mathcal{L})$, of the derivative of smooth part of the objective function
-%% . The tighter the upper bound used for this constant,
-%% the faster the resulting FISTA algorithm. In FISTA, the main use of 
-%% $L(\mathcal{L})$ is the fact that: for any
-%% stepsize $0 < t \le 1/L(\mathcal{L})$ and for any point $\mathbf{z}$,
-%% \begin{equation}%
-%%   \begin{gathered}
-%%     \mathcal{L}(\mathbf{p}_{t}(\mathbf{z})) \le
-%%     \mathcal{L}(\mathbf{z}) + \mathbf{r}_{t}^T\nabla
-%%     \mathcal{L}(\mathbf{z}) + \frac{1}{2t} \|\mathbf{r}_{t}\|_{2}^2,
-%%     \text{  where} \quad\\
-%%     \mathbf{p}_{t}(\mathbf{z}) := \textrm{prox}_{\alpha t J}(\mathbf{z} - t
-%%     \nabla \mathcal{L}(\mathbf{z})) \,\text{  and  }\,
-%%     \mathbf{r}_{t} :=
-%%     \mathbf{p}_{t}(\mathbf{z}) - \mathbf{z} \quad
-%%   \end{gathered}
-%%   \label{eq:fista_ineq}
-%% \end{equation}
-%% In least-squares regression, $L(\mathcal{L})$ is precisely the largest
-%% singular value of the design matrix $\mathbf{X}$.
-%% For logistic
-%% regression however, the tightest known upper bound for
-%% $L(\mathcal{L})$ is $\|\mathbf{X}\|\|\mathbf{X}^T\|$ (for example see Appendix A of
-%% \cite{yuan2012}), which performs
-%% very poorly locally (i.e, stepsizes $\sim 1 / L(\mathcal{L})$ are
-%% sub-optimal locally). A way to circumvent this difficulty is
-%% \emph{backtracking line search} \cite{beck2009a}, where one tunes the
-%% stepsize $t$ to satisfy inequality \eqref{eq:fista_ineq} locally at
-%% point $\mathbf{z}$.
-
-%% \paragraph{ADMM: Alternating Direction Method of Multipliers}
-%% ADMM is a Bregman Operator Splitting primal-dual method for
-%% solving convex-optimization problems by splitting the
-%% objective function in two convex terms which are functions of linearly-related auxiliary variables
-%% \cite{boyd2010}.  ADMM is particularly appealing for problems such as TV
-%% regression: using the variable split $\mathbf{z}
-%% \leftarrow \nabla \mathbf{w}$, the regularization is a simple $\ell_{1}/\ell_2$
-%% norm on $\mathbf{z}$ for which the proximal is exact and computationally
-%% cheap. However, in our settings, limitations of ADMM are:
-%% \begin{itemize}
-%% \item the $\mathbf{w}$-update involves the inversion of a large ($p \times p$)
-%%   ill-conditioned linear operator (precisely a weighted sum of
-%%   $\mathbf{X}^T\mathbf{X}$, the laplacian $\Delta$, and the identity
-%%   operator).
-%% \item the $\rho$ parameter for penalizing the split
-%%   residual $\mathbf{z} - \nabla \mathbf{w}$ is hard to set (this is still an
-%%   open problem), and though under mild conditions ADMM
-%%   converges for any value of $\rho$, the convergence rate depends
-%%   on $\rho$.
-%% \end{itemize}
-
-%% \paragraph{Primal-Dual algorithm of Chambolle and Pock \cite{chambolle2010}}
-%% this scheme is another method based on operator splitting.
-%% Used for fMRI TV regression by \cite{gramfort-etal:2013a},
-%% it does not require setting a hyperparameter.  % XXX : this is wrong you have the tau / sigma
-%% However it is a first-order single-step method and is thus more impacted by the
-%% conditioning of the problem. Note that here we explore this primal-dual
-%% method only in the squared loss setting, in which the algorithm can be accelerated by
-%% precomputing the SVD of $\mathbf{X}$ \cite{gramfort-etal:2013a}
-%% .
-
-%% \paragraph{HANSO \cite{lewis2008}}
-%% a modified LBFGS scheme based on gradient 
-%% sampling methods \cite{burke2005} and inexact
-%% line-search. For non-smooth problems as in our case, the algorithm relies on
-%% random initialization, to avoid singularities with high probability. 
-%% Here, we used the original authors' implementation.
-
-%% \paragraph{Uniform approximation by smooth convex surrogates}
-%% $\ell_{1}$ (resp. TV) is differentiable almost everywhere,
-%% with gradient $\bigl(\textbf{w}(\omega)/|\textbf{w}(\omega|))_{\omega
-%%   \in \Omega}$ (resp. $-\dive (\nabla \mathbf{w}/\|\nabla
-%% \mathbf{w}\|_2)$), except at voxels $\omega$ of the weights map where
-%% \textbf{w}$(\omega) = 0$ (resp. $\|\nabla \mathbf{w}(\omega)\|_{2} =
-%% 0$), corresponding to black spots (resp. edges).  A convenient
-%% approach (see for example \cite{NESTA, nesterov2005a, nesterov2005b,
-%%   beck2012}) for dealing with such singularities is to uniformly
-%% approximate the offending function with smooth surrogates that
-%% preserve its convexity. Given  % I removed "and other important properties"
-%% a smoothing parameter $\mu > 0$, we define \emph{smoothed} versions
-%% of $\ell_1$ and TV:
-%% %
-%% \begin{eqnarray}
-%%   \left.
-%%   \begin{aligned}
-%%     \|\mathbf{w}\|_{\ell_{1},\mu} &:= \sum_{\omega \in \Omega}
-%%     \sqrt{\mathbf{w}(\omega)^2 + \mu^2} \quad\\
-%%     \|\mathbf{w}\|_{TV, \mu} &:=
-%%     \sum_{\omega \in \Omega} \sqrt{\|\nabla \mathbf{w}(\omega)\|_{2}^2 +
-%%     \mu^2} \quad
-%%     \end{aligned}
-%%     \right\}
-%% \end{eqnarray}
-%% These surrogate upper-bounds are convex and everywhere-differentiable
-%% with gradients that are Lipschitz-continuous with constants $1/\mu$ and
-%% $\|\nabla\|^2(1/\mu) = 12 / \mu$ respectively.
-%% %
-%% They lead to smoothed versions of problem \eqref{eq:opt_pb}:
-%% \begin{align}
-%%   \mathbf{\hat{w}}_{\mu} := \argmin_{\mathbf{w}}\;
-%%   \{E_{\mu}(\mathbf{w}) := \mathcal{L}(\mathbf{y}, \mathbf{X}, \mathbf{w}) + \alpha
-%%     J_{\mu}(\mathbf{w})\},
-%%   \label{eq:sopt_pb}
-%% \\
-%%     \text{where} \quad
-%%     J_{\mu}(\mathbf{w}) :=\zeta \|\mathbf{w}\|_{\ell_{1},\mu} +
-%%     (1 - \zeta)\|\mathbf{w}\|_{TV, \mu} \quad
-%% \end{align}
-
-%% To solve \eqref{eq:opt_pb}, we consider problems of the form
-%% \eqref{eq:sopt_pb} with $\mu \rightarrow 0^+$: we start with a coarse
-%% $\mu$ ($= 10^{-2}$, \emph{e.g}) and cheaply solve the $\mu$-smoothed problem
-%% \eqref{eq:sopt_pb} to a precision $\sim \mu$ using a fast
-%% iterative oracle like the LBFGS \cite{ciyou1994}; we
-%% obtain a better estimate for the solution; then we decrease $\mu$ by a fixed factor,
-%% and restart the solver on problem \eqref{eq:sopt_pb} with this solution; and so on, in a 
-%% \emph{continuation} process~\cite{NESTA} detailed in Alg.
-%% \ref{Tab:pseudocode_lbfgs}.
-
-%% \begin{algorithm}[htb]
-%% \caption{LBFGS algorithm with continuation} \textbf{Let}
-%% $\epsilon > 0$ be the desired precision, $\beta$ ($0 < \beta <
-%% 1$) be the rate of decay of the smoothing parameter $\mu$, and $\gamma > 0$ be a constant.  Finally,
-%% let LBFGS: $(E_\mu, \mathbf{w}^{(0)}, \epsilon) \mapsto \mathbf{w}$ be
-%% an oracle which when warm-started with an initial guess
-%% $\mathbf{w}^{(0)}$, returns an $\epsilon$-optimal
-%% solution (i.e $E_\mu(\mathbf{w}) - E_\mu^{*} < \epsilon$) for problem \eqref{eq:sopt_pb}.\\
-%% \textbf{Initialize} $ 0 < \mu^{(0)}$ ($= 10^{-2}$, \emph{e.g}),
-%% $\mathbf{w}^{(0)}\in \mathbb{R}^p$, and $k = 0$.\\
-%% \Repeat{$\gamma\mu^{(k)}
-%%   < \epsilon$}{
-%%   \begin{eqnarray*}
-%%     \mathbf{w}^{(k + 1)} &\leftarrow& \mbox{LBFGS}(E_{\mu^{(k)}},
-%%     \mathbf{w}^{(k)}, \gamma\mu^{(k)})\\
-%%     \mu^{(k + 1)} &\leftarrow& \beta \mu^{(k)} \\
-%%     k &\leftarrow& k + 1
-%%   \end{eqnarray*}
-%% } \Return $\mathbf{w}^{(k)}$
-%% \label{Tab:pseudocode_lbfgs}
-%% \end{algorithm}
-
-%% This algorithm is not faster than
-%% $\mathcal{O}(1/\epsilon)$: indeed a good optimization algorithm
-%% for the sub-problem \eqref{eq:sopt_pb} is $\mathcal{O}(\sqrt{L_{\mu}/\epsilon})$
-%% \cite{nesterov1983}, and $L_{\mu} \sim 1 / \mu \sim 1 / \epsilon$. We
-%% believe that this bound is tight but a detailed analysis is
-%% beyond the scope of this paper.
-
-%% \section{Experiments on fMRI datasets}
-%% \label{sec:experiments}
-%% We now detail experiments done on publicly available
-%% data. All experiments were run full-brain without spatial smoothing.
-
-%% \paragraph{Visual recognition}
-%% \label{subsec:haxby}
-%% Our first benchmark dataset is a popular block-design fMRI dataset from a study on face and
-%% object representation in human ventral temporal cortex  \cite{haxby2001}.
-%% It consists of
-%% 6 subjects with 12 runs per subject. In each run, the subjects
-%% passively viewed images of eight object categories, grouped
-%% in 24-second blocks separated by intermittent rest periods. This
-%% experiment is a classification task: predicting the object category. We use a
-%% two-class prediction target: $\mathbf{y}$ encodes faces versus houses.
-%% The design matrix $\mathbf{X}$ is made of
-%% time-series from the full-brain mask of $p = 23\,707$ voxels over $n =
-%% 216$ TRs, of a single subject (subj1).
-
-%% \paragraph{Mixed Gambles}
-%% Our second benchmark dataset is a study in which
-%% subjects were presented with mixed (gain/loss) gambles, and decided
-%% whether they would accept each gamble \cite{mixedgambles2007}.  No outcomes of these gambles
-%% were presented during scanning, but after the scan three gambles were
-%% selected at random and played for real money. The prediction task here is
-%% to predict the magnitude of the gain and thus a regression on a
-%% continuous variable \cite{jimura2012}. The data is pooled across
-%% subjects, resulting in 768 samples, each an image of 33\,177 voxels.
-
-%% % We validate our algorithms on both simulated and real data.
-%% \smallskip
-
-%% We study the convergence of the algorithms for parameters close to the
-%% optimal parameters set by 10-fold cross-validation to maximize prediction
-%% accuracy.
-
-%% \begin{figure*}
-%% % generate with: ipython ../wip/tv_l1_solver/plot_parallel_plots.py bench/haxby_lr_11th.json .9 --pdb
-%% \hspace*{-.01\linewidth}%
-%% \includegraphics[width=.6\linewidth]{bench/haxby_lr_energy.pdf}
-%% \hspace*{-.09\linewidth}%
-%% \includegraphics[width=.6\linewidth]{bench/haxby_lr.pdf}%
-%% % \vspace{-2ex}
-%% \caption{TV$-\ell_1$ penalized Logistic Regression on the visual
-%% recognition face-house
-%%   discrimination task. \textbf{Left}: excess energy $E(\mathbf{w}_t) -
-%% E(\mathbf{w}_{t})_{t \rightarrow \infty}$ as a function 
-%% of time.
-%% \textbf{Right}: convergence time of the various solvers for different
-%% choice of regularization parameters.
-%% Broken lines correspond to a tolerance of $10^{0}$,
-%%   whilst full-lines correspond to $10^{-2}$.  The thick vertical line
-%% indicates the best model selected by cross-validation.}
-%% \label{Fig:HaxbyLR}
-%% \end{figure*}
-
-%% %% \paragraph{Haxby 2001: TV$-\ell_{1}$ penalized Least-Squares Regression}
-%% %% See figure \ref{Fig:HaxbyMSE}
-%% \begin{figure*}
-%% % generate with: ipython ../wip/tv_l1_solver/plot_parallel_plots.py bench/haxby_mse_10th.json 1e-2 --pdb
-%% \includegraphics[width=.6\linewidth]{bench/haxby_mse.pdf}%
-%% \hspace{-.09\linewidth}%
-%% % generate with: ipython ../wip/tv_l1_solver/plot_parallel_plots.py bench/poldrack_mse_12th.json 2e1 --pdb
-%% \includegraphics[width=.6\linewidth]{bench/poldrack_mse.pdf}
-%% % \vspace{-2ex}
-%% \caption{TV$-\ell_1$ penalized Least-Squares Regression. \textbf{Left}:
-%%   on the visual recognition  face-house discrimination task; \textbf{Right}: on the
-%%   Mixed gambles dataset. Broken lines correspond to a tolerance of $10^{0}$,
-%%   whilst full-lines correspond to $10^{-2}$. The thick vertical line
-%% indicates the best model selected by cross-validation.}
-%% \label{Fig:MSEtimes}
-%% \end{figure*}
-
-%% \section{Results: convergence times}
-%% \label{sec:results}
-%% Here, we present benchmark results for our experiments. Figure
-%% \ref{Fig:HaxbyLR} gives results for the logistic regression run on the
-%% visual recognition dataset: convergence plots of energy as a function of
-%% time show that all methods are asymptotically decreasing. Figure
-%% \ref{Fig:HaxbyLR} left, shows the time required to give a convergence
-%% threshold, defined as a given excess energy compared to the lowest energy
-%% achieved by all methods, for different choices of regularization
-%% parameters. Similarly, figure \ref{Fig:MSEtimes} shows convergence times
-%% for squared loss on both datasets. For these figures,
-%% each solver was run for a maximum of 1 hour per problem. Solvers that do
-%% not appear on a plot did not converge for the corresponding
-%% tolerance and time budget.
-
-%% For logistic loss, the most serious contender is
-%% algorithm \ref{Tab:pseudocode_lbfgs}, LBFGS applied on a smooth
-%% surrogate, followed by ADMM, however ADMM performance
-%% varies markedly depending on the choice of $\rho$. For the squared loss
-%% FISTA and algorithm \ref{Tab:pseudocode_lbfgs} are the best performers,
-%% with FISTA achieving a clear lead for the larger mixed-gambles dataset.
-%% Note that in the case of strong regularization the problem is better
-%% conditioned, and first-order methods such as the
-%% primal-dual approach can perform well.
-
-%% %% \paragraph{Haxby: TV$-\ell_{1}$ penalized Logistic Regression}
-%% %% TV$-\ell_{1}$ penalized Logistic Regression...See figure \ref{Fig:HaxbyLR}
-
-%% \section{Conclusions: approaches to prefer}
-%% \label{sec:discusion}
-
-%% TV$-\ell_{1}$ penalized regression for brain imaging leads to
-%% very high-dimensional, non-smooth and very ill-conditioned optimization
-%% problems. We have presented a comprehensive comparison of state-of-the-art
-%% solvers in these setting. Solvers were implemented with all known
-%% algorithmic improvements and implementation were carefully profiled and
-%% optimized.
-
-%% Our results outline best strategies: monotonous FISTA with a adaptive
-%% control of the tolerance of the TV proximal operator, in the case of
-%% squared loss; smoothed quasi-newton based on surrogate upper-bounds of
-%% the non-smooth norms for logistic loss. While these algorithms are
-%% variants of existing approaches, we present here novel additions useful
-%% for the TV or TV$-\ell_1$ settings. The fact that the smooth approaches emerge
-%% as fast solvers on these non-smooth problems is not unexpected as
-%% \emph{i)} the amount of regularization is small \emph{ii)} the prevailing
-%% term is smooth and very ill conditioned, thus calling for second-order
-%% methods such as Newton or quasi-Newton.
-
-%% For neuroimaging applications, our study has highlighted the need to
-%% converge to a good tolerance and the corresponding difficulties. Lack of
-%% good solver and explicit control of tolerance can lead to brain maps and
-%% conclusions that reflect properties of the solver more than of the
-%% TV$-\ell_1$ solution.
-
-%% %\section{Acknowledgements}
-%% %% \label{subsec:acknowledgements}
-%% %This work was supported by the  Human Brain Project.
-
-%% \medskip \noindent
-%% \textbf{Acknowledgments:}
-%% This work was supported by the  Human Brain Project.
-
-%% % ==========
-%% % = biblio =
-%% % ==========
-%% % {\small
-%% \bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv}
+% ==========
+% = biblio =
+% ==========
+% {\small
+\bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv}
 \end{document}

### 2014-07-26 paper.tex
more

@@
-% \documentclass[a4paper,11pt]{article}
-% \documentclass[a4paper,10pt,draftcls,journal]{IEEEtran}
 \documentclass[a4paper,10pt,journal]{IEEEtran}
-% \usepackage{times}
 \usepackage{graphicx} \usepackage[cmex10]{amsmath}
@@
 \usepackage{xcolor} \usepackage{colortbl,hhline}
-%\usepackage{algorithm2e}
-% \usepackage{algorithm}
 \usepackage[ruled,vlined]{algorithm2e} \usepackage{framed}
@@
 \usepackage{amsmath,amsfonts,amssymb, amsthm} \usepackage{textcomp}
-\newtheorem*{remark}{Remark}
 
-% \usepackage{natbib}
-% \bibpunct{[}{]}{;}{a}{,}{,}
+\newtheorem{remark}{Remark}
 
@@
 \begin{document}
-%\onecolumn
-\title{A fast algorithm for computing best response behaviour strategies in two-person sequential games}
+\onecolumn
+\title{A fast algorithm for computing best response strategies in two-person sequential games}
 
@@
 % maps"
-In this manuscript, we consider the problem of computing the best response against an opponent's realization plan in two-person sequential games.
-The proposed technique employs the primal-dual scheme of A. Chambolle and T. Pock to solve the corresponding contrained convex-optimization problem.
-The resulting algorithm is simple: all resolvent operators can be effectively computed in closed-form, using only elementary algebraic operations.
+In this manuscript, we consider the problem of computing a best response against an opponent's realization plan in two-person sequential games.
+The proposed algorithm for solving the corresponding contrained convex-optimization problem, derives from the primal-dual scheme of A. Chambolle and T. Pock.
+Our algorithm is simple: all resolvent operators can be effectively computed in closed-form, using only elementary algebraic operations.
 %%  and is orders of magnitude more efficient than state-of-the-art algorithms like those based on Linear Programming, Interior-Point methods,
@@
 \section{Introduction}
-\label{sec:intro}
+%\label{sec:intro}
 \subsection{Notation and Terminology}
@@
 \textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
-$\mathbb{R}_+$: \quad \textit{nonnegative part of the real-line $\mathbb{R}$}\\
-$i_C$: \quad \textit{indicator function of the convex set $C$}\\
-$\Pi_C$: \quad \textit{euclidean projector onto the convex set $C$}\\
-$(x)_+$: \quad \textit{component-wise maximum of the vector $x$ and 0}\\
-$\|K\|$: \quad \textit{operator norm of the matrix $K$}\\
-$F^*$: \quad \textit{Fenchel transform of the convex l.s.c function $F$}\\
-$E^{-1}(U)$: \quad \textit{pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
+$\mathbb{R}_+$: \quad \textit{the nonnegative part of the real-line $\mathbb{R}$}\\
+$i_C$: \quad \textit{the indicator function of the convex set $C$}\\
+$\Pi_C$: \quad \textit{the euclidean projector onto the convex set $C$}\\
+$(x)_+$: \quad \textit{the component-wise maximum of the vector $x$ and 0}\\
+$\|K\|_2$: \quad \textit{the matrix 2-norm of the matrix $K$}\\
+$f^*$: \quad \textit{the Fenchel transform of the convex l.s.c function $f$}\\
+$E^{-1}(U)$: \quad \textit{the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
 namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$}
@@
 \subsection{Statement of the problem}
-Consider a two-person zero-sum sequential game with payoff matrix $A \in \mathbb{R}^{m,n}$. We are interested in the problem of
-finding the best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$ for player 2, given a fixed
-(possibly mixed) strategy $y_0$ for player 1, where $E \in \{-1, 0, +1\}^{p,n}$ and $(1, 0, 0, ..., 0) =: e \in \mathbb{R}^p$.
-Recall that $E$ and $e$ encode linear constraints on player 1's ``admissible'' realization plans $x$, in the sequential form representation
-of the game (See \cite{bernhard-1996, benhard-agt} for theory on \textit{sequential-form representation}). In the language of convex-optimization,
+Consider a two-person sequential game\footnote{In a sequential game, players take turns in play, one after the other,
+as opposed to simultaneous play.} in \textit{sequential-form} (See for example, page 2 of \cite{koller-1995},
+for theory on sequential-form representation), and let $A \in \mathbb{R}^{m,n}$ be our payoff matrix.
+We will be referring to the other player as ``the opponent''. We are interested in the problem of
+finding a best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$, given a fixed
+(possibly mixed) strategy $y_0$ for the opponent, where $E$ is a sparse $p$-by-$n$ matrix whose entries are $-1$, $0$, or $+1$,
+and $(1, 0, 0, ..., 0) =: e \in \mathbb{R}^p$. Recall that $E$ and $e$ encode linear constraints on our ``admissible''
+realization plans\footnote{In games in sequential form, the terms ``strategy'' and ``realization plan''
+mean thesame thing.} $x$, in the sequential form representation of the game.
+In the language of convex-optimization,
 one can readily give the following saddle-point formulation for this problem. Viz,
@@
 
-In section II, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}. We elaborate our proposed algorithm in section III.
+A solution $x^*$ to problem \eqref{eq:opt_pb} is called a \textit{best response} strategy against the opponent's fixed strategy $y_0$.
+
+\begin{remark}
+Of course $y_0$ is not necessarily an optimal strategy for the opponent. In case it is, the pair $(x^*, y_0)$ is a Nash equilibrium for the game.
+\end{remark}
+
+\begin{remark}
+  In practice, $A$ and $E$ are very sparse as a game will typically have very few leafs
+(i.e terminal states). This sparsity should be thoroughly exploited by a solver for problem \eqref{eq:opt_pb}.
+\end{remark}
+
+In section II, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}.
+We elaborate our proposed algorithm in section III.
 
@@
 \label{sec:algo}
-In this section we present the algorithm which is the purpose of this paper, namely an algorithm for solving \eqref{eq:opt_pb}.
-Our algorithm (Alg.\ref{Tab:pseudocode_pb}) is a use-case of the generic primal-dual algorithm of A.
-Chambolle and T.
-Pock, namely Algorithmic 1 of \cite{chambolle2010}.
+In this section we present the algorithm which is the purpose of this paper, namely an algorithm
+for solving \eqref{eq:opt_pb}. Our algorithm (Alg.\ref{Tab:pseudocode_pb}) is a use-case of
+the generic primal-dual algorithm of A. Chambolle and T. Pock, namely Algorithm 1 of \cite{chambolle2010}.
 
@@
   \begin{aligned}
-    g := i_{E^{-1}(\{b\})} + i_{\mathbb{R}_{+}^m}\\
+    g := i_{E^{-1}(\{e\})} + i_{\mathbb{R}_{+}^m}\\
     f: z \mapsto y_0^Tz
@@
 
-Finally, the primal-dual formulation of this problem is:
+Finally, the primal-dual formulation of this problem (which can be easily obtained using
+\textit{Fenchel-Rockafellar duality}, for example) is:
 \begin{equation}
-  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m}{max}\text{ }{y^T(-A)x_0 + g(x) - f^*(y))}
+  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m}{max}\text{ }{y^T(-A)x_0 + g(x) - f^*(y)}
 \end{equation}
 
-Now, let's observe that $i_{E^{-1}(\{e\})}(x) = \underset{\zeta \in \mathbb{R}^q}{max}\text{ }\zeta^T(e - Ex)$, and so one can re-write (2) as:
+Now, let's observe that $i_{E^{-1}(\{e\})}(x) = \underset{\zeta \in \mathbb{R}^p}{max}\text{ }\zeta^T(e - Ex)$, and so one can re-write (2) as:
 \begin{equation}
@@
 \end{equation}
-where:
+where we've defined:
 \begin{equation}
@@
     K := -\begin{bmatrix}A\\E\end{bmatrix}\\
-    G := i_{\mathbb{R}_{+}^n}\\
-    F^*: (y, \zeta) \mapsto (i_{\{y_0\}} - \zeta^Te)
+    G := g - i_{E^{-1}(\{b\})} = i_{\mathbb{R}_{+}^n}\\
+    F^*: (y, \zeta) \mapsto (f^*(y) - \zeta^Te) = (i_{\{y_0\}}(y) - \zeta^Te)
   \end{aligned}
@@
 
-Furthermore, $F^*$ and $G$ have resolvent (a.k.a \textit{proximity}) operators given by the simple formulae:
+Furthermore, $F^*$ and $G$ are convex l.s.c, with resolvent (a.k.a \textit{proximity}) operators given by the simple formulae:
 \begin{equation}
@@
 
-Using these ingredients, we obtain the primal-dual algorithm given in Alg.\ref{Tab:pseudocode_pb}, 
+Using these ingredients, we derive the primal-dual algorithm given in Alg.\ref{Tab:pseudocode_pb}, 
 for solving \eqref{eq:pd_opt}, and thus \eqref{eq:opt_pb}.
@@
 \begin{algorithm}[htb]
-\caption{Primal-dual algorithm for computing best response against opponent's realization plan $y$}%%  \textbf{Let}
+\caption{Primal-dual algorithm for computing best response against opponent's realization plan $y_0$}
 \textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
-$\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$; $k = 0$.\\
+$\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
 \textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
@@
   \begin{eqnarray*}
-    \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma (e - E\tilde{x}^{(k)})\\
+    \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
     x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
@@
 \textbf{Acknowledgments:}
-This work was supported by the  Human Brain Project.
+Pending...
 

### 2014-07-26 best_response.py

@@ -35,6 +35,7 @@ def best_response(A, E, e, y0, max_iter=1000, tol=1e-6):
     const = tau * A.T.dot(y0)
     for k in xrange(max_iter):
         old_x = x.copy()
+        residue = e - E.dot(xbar)
         gain = -np.dot(x.T, const) / tau
         gain_delta = old_gain - gain
         old_gain = gain
@@ -44,7 +45,7 @@ def best_response(A, E, e, y0, max_iter=1000, tol=1e-6):
         if gain_delta < tol:
             print "Converged (gain delta < %g)" % tol
             break
-        zeta += sigma * (e - E.dot(xbar))
+        zeta += sigma * (residue)
         x += const + E.T.dot(zeta)
 
         x = np.maximum(x, 0.)

### 2014-07-26 paper.tex
more
new bib file (for game theory citing)

@@
 \begin{document}
-\onecolumn
+%\onecolumn
 \title{A fast algorithm for computing best response strategies in two-person sequential games}
@@
 Consider a two-person sequential game\footnote{In a sequential game, players take turns in play, one after the other,
-as opposed to simultaneous play.} in \textit{sequential-form} (See for example, page 2 of \cite{koller-1995},
+as opposed to simultaneous play.} in \textit{sequential-form} (See for example, \cite{von1996efficient} and \cite{koller1996efficient} 
 for theory on sequential-form representation), and let $A \in \mathbb{R}^{m,n}$ be our payoff matrix.
@@
 
+\begin{definition}
 A solution $x^*$ to problem \eqref{eq:opt_pb} is called a \textit{best response} strategy against the opponent's fixed strategy $y_0$.
+\end{definition}
 
@@
 
-In section II, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}.
-We elaborate our proposed algorithm in section III.
+In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}.
+We elaborate our proposed algorithm in section \ref{sec:algo}.
 
 \section{Related work}
+\label{sec:related_work}
+
 Pending...
@@
 
-\subsection{Primal-dual gap stopping-criterion and convergence of the algorithm}
+\subsection{Convergence of the algorithm and practical stopping-criteria}
 Pending...
@@
 % {\small
-\bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv}
+\bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv.bib,agt.bib}
 \end{document}

### 2014-07-26 paper.tex
more

@@
 
-Furthermore, $F^*$ and $G$ are convex l.s.c, with resolvent (a.k.a \textit{proximity}) operators given by the simple formulae:
+Furthermore, one easily checks that $F^*$ and $G$ are \textit{proper} convex l.s.c, with resolvent
+(a.k.a \textit{proximity}) operators given by the simple formulae:
 \begin{equation}
@@
 \end{equation}
+
+\begin{remark}
+Equation \eqref{eq:pd_opt} is the form of equation (2) in \cite{chambolle2010} if we take $X := \mathbb{R}^n$ and
+$Y := \mathbb{R}^m \times \mathbb{R}^p$.
+\end{remark}
 

### 2014-07-26 paper.tex
more

@@
 \begin{remark}
-Equation \eqref{eq:pd_opt} is the form of equation (2) in \cite{chambolle2010} if we take $X := \mathbb{R}^n$ and
+Equation \eqref{eq:pd_opt} is in the form of equation (2) in \cite{chambolle2010} if we take $X := \mathbb{R}^n$ and
 $Y := \mathbb{R}^m \times \mathbb{R}^p$.

### 2014-07-26 paper.tex
more

@@
 
+Using these ingredients, we derive the primal-dual algorithm given in Alg.\ref{Tab:pseudocode_pb}, 
+for solving \eqref{eq:pd_opt}, and thus \eqref{eq:opt_pb}.
+
 \begin{remark}
@@
 
-Using these ingredients, we derive the primal-dual algorithm given in Alg.\ref{Tab:pseudocode_pb}, 
-for solving \eqref{eq:pd_opt}, and thus \eqref{eq:opt_pb}.
+\begin{remark}
+The derivation above reveals that in equation \eqref{eq:opt_pb} above, if the constraint ``$x \ge 0$'' is replaced by
+a constraint ``$x \in C$'' (thus obtaining a new problem) where $C$ is a convex set onto which euclidean projections
+can be easily computed (for example, a probability simplex), then we simply need to replace the operator ``$(.)_+$''
+with ``$\Pi_C$'' in the equations to obtain a corresponding algorithm.
+\end{remark}
 

### 2014-07-26 paper.tex
'running average ||e - Exk||_2' stopping criterion

--- 2014-07-26 paper.tex
@@
 To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
-(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,\\
-\textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
+(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,\\\\
+$a^Tb$: \quad \textit{the dot product of two vectors $a$ and $b$}\\
 $\mathbb{R}_+$: \quad \textit{the nonnegative part of the real-line $\mathbb{R}$}\\
+$(x)_+$: \quad \textit{the component-wise maximum of the vector $x$ and 0}\\
 $i_C$: \quad \textit{the indicator function of the convex set $C$}\\
 $\Pi_C$: \quad \textit{the euclidean projector onto the convex set $C$}\\
-$(x)_+$: \quad \textit{the component-wise maximum of the vector $x$ and 0}\\
 $\|K\|_2$: \quad \textit{the matrix 2-norm of the matrix $K$}\\
 $f^*$: \quad \textit{the Fenchel transform of the convex l.s.c function $f$}\\
+\textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
 $E^{-1}(U)$: \quad \textit{the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
@@
     G := g - i_{E^{-1}(\{b\})} = i_{\mathbb{R}_{+}^n}\\
-    F^*: (y, \zeta) \mapsto (f^*(y) - \zeta^Te) = (i_{\{y_0\}}(y) - \zeta^Te)
+    F^*: (y, \zeta) \mapsto (f^*(y) - \zeta^Te) = (i_{\{y_0\}}(y) - e^T\zeta)
   \end{aligned}
@@
 
-Using these ingredients, we derive the primal-dual algorithm given in Alg.\ref{Tab:pseudocode_pb}, 
-for solving \eqref{eq:pd_opt}, and thus \eqref{eq:opt_pb}.
+\begin{remark}
+The derivation above reveals that in equation \eqref{eq:opt_pb} above, if the constraint ``$x \ge 0$'' is replaced by
+a constraint ``$x \in C$'' (thus obtaining a new problem) where $C$ is a convex set
+%% onto which euclidean projections
+%% can be easily computed (for example, a probability simplex)
+, then we simply need to replace the operator ``$(.)_+$''
+with ``$\Pi_C$'' in the equations to obtain a corresponding algorithm. Of course, this is because $i_C^* = \Pi_C$.
+\end{remark}
 
@@
 \caption{Primal-dual algorithm for computing best response against opponent's realization plan $y_0$}
+\textbf{Let} $\epsilon > 0$ be a given tolerance.\\
 \textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
@@
 \Repeat{
-  convergence}{
+  $\frac{1}{k + 1}\sum_{j=0}^{k}{\|e - E\tilde{x}^{(j)}\|^2_2} < \epsilon$}{
   \begin{eqnarray*}
@@
 
-\subsection{Convergence of the algorithm and practical stopping-criteria}
+\subsection{Convergence analysis of the algorithm}
 Pending...

### 2014-07-26 best_response.py

@@ -2,7 +2,7 @@ import numpy as np
 from scipy import linalg
 
 
-def best_response(A, E, e, y0, max_iter=1000, tol=1e-6):
+def best_response(A, E, e, y0, max_iter=1000, tol=1e-2):
     """Computes best response to an opponent's realization plan in a two-person
     sequential game.
 
@@ -28,22 +28,21 @@ def best_response(A, E, e, y0, max_iter=1000, tol=1e-6):
     x = np.zeros(n)
     xbar = x.copy()
     zeta = np.zeros(p)
-    old_gain = np.inf
     L = linalg.svdvals(np.vstack((A, E)))[0]
     tau = sigma = .99 / L
     assert tau * sigma * L * L < 1.
     const = tau * A.T.dot(y0)
+    r = 0
+    history = []
     for k in xrange(max_iter):
         old_x = x.copy()
         residue = e - E.dot(xbar)
-        gain = -np.dot(x.T, const) / tau
-        gain_delta = old_gain - gain
-        old_gain = gain
-        print "Iteration %03i/%03i: gain=%g, change=%g" % (
-            k + 1, max_iter, gain, gain_delta)
-        gain_delta = abs(gain_delta)
-        if gain_delta < tol:
-            print "Converged (gain delta < %g)" % tol
+        r = (k * r + np.dot(residue, residue)) / (k + 1.)
+        history.append(r)
+        print "Iteration %03i/%03i: running average ||e - Exk||^2 = %g" % (
+            k + 1, max_iter, r)
+        if r < tol:
+            print "Converged (running average ||e - Exk||^2 < %g)" % tol
             break
         zeta += sigma * (residue)
         x += const + E.T.dot(zeta)
@@ -52,7 +51,7 @@ def best_response(A, E, e, y0, max_iter=1000, tol=1e-6):
 
         xbar = 2 * x - old_x
 
-    return x
+    return x, history
 
 
 if __name__ == "__main__":
@@ -63,6 +62,14 @@ if __name__ == "__main__":
     E = np.array([[1, 0, 0, 0, 0], [-1, 1, 1, 0, 0], [-1, 0, 0, 1, 1]])
     e = np.eye(E.shape[0])[0]
     y0 = np.array([1, .66, .33])
-    xstar = best_response(A, E, e, y0)
+    xstar, history = best_response(A, E, e, y0)
     print "x* =", xstar
     print E.dot(xstar) - e
+
+    import pylab as pl
[…]

### 2014-07-26 best_response.py
ENH: better convergence criterion

@@ -32,26 +32,31 @@ def best_response(A, E, e, y0, max_iter=1000, tol=1e-2):
     tau = sigma = .99 / L
     assert tau * sigma * L * L < 1.
     const = tau * A.T.dot(y0)
-    r = 0
-    history = []
+    average_error = 0
+    average_errors = []
     for k in xrange(max_iter):
         old_x = x.copy()
-        residue = e - E.dot(xbar)
-        r = (k * r + np.dot(residue, residue)) / (k + 1.)
-        history.append(r)
-        print "Iteration %03i/%03i: running average ||e - Exk||^2 = %g" % (
-            k + 1, max_iter, r)
-        if r < tol:
-            print "Converged (running average ||e - Exk||^2 < %g)" % tol
-            break
-        zeta += sigma * (residue)
+        old_zeta = zeta.copy()
+        zeta += sigma * (e - E.dot(xbar))
         x += const + E.T.dot(zeta)
 
         x = np.maximum(x, 0.)
-
         xbar = 2 * x - old_x
 
-    return x, history
+        a = x - old_x
+        b = zeta - old_zeta
+        average_error = (k * average_error + .5 * (np.dot(a, a) / tau + np.dot(
+                    b, b) / sigma))  / (k + 1.)
+        average_errors.append(average_error)
+        print ("Iteration %04i/%04i: .5 * (||x^(k+1) - "
+               "x^(k)||^2" " / tau + ||zeta^(k+1) - zeta^(k)||^2 / sigma) "
+               "= %.3e" % (k + 1, max_iter, average_error))
+        if average_error < tol:
+            print ("Converged (.5 * (||x^(k+1) - x^(k)||^2 / tau + "
+                   "||zeta^(k+1) - zeta^(k)||^2 / sigma) < %g)" % tol)
+            break
+
+    return x, average_errors
 
 
 if __name__ == "__main__":
@@ -62,14 +67,15 @@ if __name__ == "__main__":
     E = np.array([[1, 0, 0, 0, 0], [-1, 1, 1, 0, 0], [-1, 0, 0, 1, 1]])
     e = np.eye(E.shape[0])[0]
     y0 = np.array([1, .66, .33])
-    xstar, history = best_response(A, E, e, y0)
+    xstar, average_errors = best_response(A, E, e, y0)
     print "x* =", xstar
     print E.dot(xstar) - e
 
     import pylab as pl
-    history = np.array(history)
[…]

### 2014-07-26 paper.tex
ENH: better convergence criterion
cosmetic

@@
 %\onecolumn
-\title{A fast algorithm for computing best response strategies in two-person sequential games}
+\title{A fast primal-dual algorithm for computing best response strategies in two-person sequential games}
 
@@
 (for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,\\\\
-$a^Tb$: \quad \textit{the dot product of two vectors $a$ and $b$}\\
+$u^Tv$: \quad \textit{the dot product of two vectors $u$ and $v$}\\
 $\mathbb{R}_+$: \quad \textit{the nonnegative part of the real-line $\mathbb{R}$}\\
@@
 \begin{remark}
-The derivation above reveals that in equation \eqref{eq:opt_pb} above, if the constraint ``$x \ge 0$'' is replaced by
-a constraint ``$x \in C$'' (thus obtaining a new problem) where $C$ is a convex set
-%% onto which euclidean projections
-%% can be easily computed (for example, a probability simplex)
-, then we simply need to replace the operator ``$(.)_+$''
-with ``$\Pi_C$'' in the equations to obtain a corresponding algorithm. Of course, this is because $i_C^* = \Pi_C$.
+Neither $G$ nor $F^*$ is strongly convex and so Alg.\ref{Tab:pseudocode_pb} cannot be accelerated in the sense of algorithm 39 of \cite{chambolle2010}.
 \end{remark}
@@
   \caption{Primal-dual algorithm for computing best response against opponent's realization plan $y_0$}
-\textbf{Let} $\epsilon > 0$ be a given tolerance.\\
+  \textbf{Given} Tolerance $\epsilon > 0$.\\
   \textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
-$\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
+  $d^{(0)} = 0$; $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
   \textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
   \Repeat{
-  $\frac{1}{k + 1}\sum_{j=0}^{k}{\|e - E\tilde{x}^{(j)}\|^2_2} < \epsilon$}{
+    $d^{(k)} < \epsilon$}{
     \begin{eqnarray*}
-    \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
+      r^{(k)} &\leftarrow& e - E\tilde{x}^{(k)}\\ 
+    \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma r^{(k)}\\
     x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
     \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
+    d^{(k+1)} &\leftarrow& max(d^{(k)}, \frac{\|x^{(k+1)} - x^{(k)}\|^2_2}{2\tau} + \frac{\|r^{(k)}\|^2_2}{2})\\
     k &\leftarrow& k + 1
@@
 Pending...
+
+\begin{remark}
+The derivation above reveals that in equation \eqref{eq:opt_pb} above, if the constraint ``$x \ge 0$'' is replaced by
+a constraint ``$x \in C$'' (thus obtaining a new problem) where $C$ is a convex set
+%% onto which euclidean projections
+%% can be easily computed (for example, a probability simplex)
+, then we simply need to replace the operator ``$(.)_+$''
+with ``$\Pi_C$'' in the equations to obtain a corresponding algorithm. Of course, this is because $i_C^* = \Pi_C$.
+\end{remark}
 

### 2014-07-26 best_response.py

@@ -37,23 +37,27 @@ def best_response(A, E, e, y0, max_iter=1000, tol=1e-2):
     for k in xrange(max_iter):
         old_x = x.copy()
         old_zeta = zeta.copy()
+
+        # dual update
         zeta += sigma * (e - E.dot(xbar))
         x += const + E.T.dot(zeta)
 
+        # primal update
         x = np.maximum(x, 0.)
         xbar = 2 * x - old_x
 
+        # check primal-dual convergence
         a = x - old_x
         b = zeta - old_zeta
         average_error = (k * average_error + .5 * (np.dot(a, a) / tau + np.dot(
                     b, b) / sigma))  / (k + 1.)
         average_errors.append(average_error)
-        print ("Iteration %04i/%04i: .5 * (||x^(k+1) - "
+        print ("Iteration %04i/%04i: running average .5 * (||x^(k+1) - "
                "x^(k)||^2" " / tau + ||zeta^(k+1) - zeta^(k)||^2 / sigma) "
                "= %.3e" % (k + 1, max_iter, average_error))
         if average_error < tol:
-            print ("Converged (.5 * (||x^(k+1) - x^(k)||^2 / tau + "
-                   "||zeta^(k+1) - zeta^(k)||^2 / sigma) < %g)" % tol)
+            print ("Converged (running average .5 * (||x^(k+1) - x^(k)||^2"
+                   " / tau + ||zeta^(k+1) - zeta^(k)||^2 / sigma) < %g)" % tol)
             break
 
     return x, average_errors
@@ -72,10 +76,8 @@ if __name__ == "__main__":
     print E.dot(xstar) - e
 
     import pylab as pl
-    average_errors = np.array(average_errors)
-    average_errors -= average_errors.min()
-    pl.loglog(average_errors)
-    pl.ylabel("(excess) running average .5 * (||x^(k+1) - x^(k)||^2 / tau + "
+    pl.semilogx(average_errors, linewidth=3)
+    pl.ylabel("running average .5 * (||x^(k+1) - x^(k)||^2 / tau + "
               "||zeta^(k+1) - zeta^(k)||^2 / sigma)")
     pl.xlabel("k")
     pl.show()

### 2014-07-26 best_response.py
better stopping criterion

@@ -2,7 +2,7 @@ import numpy as np
 from scipy import linalg
 
 
-def best_response(A, E, e, y0, max_iter=1000, tol=1e-2):
+def best_response(A, E, e, y0, max_iter=1000, tol=1e-2, callback=None):
     """Computes best response to an opponent's realization plan in a two-person
     sequential game.
 
@@ -35,6 +35,9 @@ def best_response(A, E, e, y0, max_iter=1000, tol=1e-2):
     average_error = 0
     average_errors = []
     for k in xrange(max_iter):
+        if callback:
+            callback(locals())
+
         old_x = x.copy()
         old_zeta = zeta.copy()
 
@@ -49,8 +52,8 @@ def best_response(A, E, e, y0, max_iter=1000, tol=1e-2):
         # check primal-dual convergence
         a = x - old_x
         b = zeta - old_zeta
-        average_error = (k * average_error + .5 * (np.dot(a, a) / tau + np.dot(
-                    b, b) / sigma))  / (k + 1.)
+        average_error = .5 * (np.dot(a, a) / tau + np.dot(
+                    b, b) / sigma)
         average_errors.append(average_error)
         print ("Iteration %04i/%04i: running average .5 * (||x^(k+1) - "
                "x^(k)||^2" " / tau + ||zeta^(k+1) - zeta^(k)||^2 / sigma) "
@@ -71,11 +74,26 @@ if __name__ == "__main__":
     E = np.array([[1, 0, 0, 0, 0], [-1, 1, 1, 0, 0], [-1, 0, 0, 1, 1]])
     e = np.eye(E.shape[0])[0]
     y0 = np.array([1, .66, .33])
-    xstar, average_errors = best_response(A, E, e, y0)
+
+    import pylab as pl
+
+    def cb(env):
+        pl.scatter(env['x'][0], env['zeta'][0], marker="*")
+        pl.draw()
+
+    fig = pl.figure(figsize=(13, 13))
+    pl.grid("on")
+    pl.xlim(0., 2.)
+    pl.ylim(-1., 1.)
+    pl.xlabel("xk")
+    pl.ylabel("yk")
+    pl.ion()
+
+    xstar, average_errors = best_response(A, E, e, y0, callback=cb, tol=1e-4)
     print "x* =", xstar
     print E.dot(xstar) - e
 
-    import pylab as pl
+    pl.figure()
     pl.semilogx(average_errors, linewidth=3)
[…]

### 2014-07-27 paper.tex
better stopping criterion
looks much better

--- 2014-07-26 paper.tex
@@
 To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
-(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,\\\\
-$a^Tb$: \quad \textit{the dot product of two vectors $a$ and $b$}\\
-$\mathbb{R}_+$: \quad \textit{the nonnegative part of the real-line $\mathbb{R}$}\\
-$(x)_+$: \quad \textit{the component-wise maximum of the vector $x$ and 0}\\
-$i_C$: \quad \textit{the indicator function of the convex set $C$}\\
-$\Pi_C$: \quad \textit{the euclidean projector onto the convex set $C$}\\
-$\|K\|_2$: \quad \textit{the matrix 2-norm of the matrix $K$}\\
-$f^*$: \quad \textit{the Fenchel transform of the convex l.s.c function $f$}\\
-\textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
-$E^{-1}(U)$: \quad \textit{the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
-namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$}
+(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,
+\begin{itemize}
+\item $A^T$: \quad transpose of the matrix $A$;
+\item $\begin{bmatrix}A\\B\end{bmatrix}$: vertical stacking of the matrices $A$ and $B$;
+\item $v_j$: \quad $j$th component of the vector $v$;
+\item $u^Tv$: \quad the dot product of two vectors $u$ and $v$;
+\item $\mathbb{R}_+$: \quad the nonnegative part of the real-line $\mathbb{R}$;
+\item $(x)_+$: \quad the component-wise maximum of the vector $x$ and 0;
+\item $i_C$: \quad the indicator function of the convex set $C$;
+\item $\Pi_C$: \quad the euclidean projector onto the convex set $C$;
+\item $\|K\|_2$: \quad the matrix 2-norm of the matrix $K$;
+\item $f^*$: \quad the Fenchel transform of the convex l.s.c function $f$;
+\item \textit{l.s.c}: \quad acronyme for ``lower semi-continuous'';
+\item $E^{-1}(U)$: \quad the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
+namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
+\end{itemize}
 
@@
 In this section we present the algorithm which is the purpose of this paper, namely an algorithm
-for solving \eqref{eq:opt_pb}. Our algorithm (Alg.\ref{Tab:pseudocode_pb}) is a use-case of
+for solving \eqref{eq:opt_pb}. Our algorithm (Alg.\ref{Tab:algo}) is a use-case of
 the generic primal-dual algorithm of A. Chambolle and T. Pock, namely Algorithm 1 of \cite{chambolle2010}.
@@
 
-Using these ingredients, we derive the primal-dual algorithm given in Alg.\ref{Tab:pseudocode_pb}, 
+Using these ingredients, we derive the primal-dual algorithm given in Alg.\ref{Tab:algo}, 
 for solving \eqref{eq:pd_opt}, and thus \eqref{eq:opt_pb}.
@@
 \end{remark}
+
+\begin{remark}
+Neither $G$ nor $F^*$ is strongly convex and so Alg.\ref{Tab:algo} cannot be accelerated in the sense of algorithm 39 of \cite{chambolle2010}.
+\end{remark}
+
+\begin{algorithm}[htb]
+  \caption{Primal-dual algorithm for computing best response against opponent's realization plan $y_0$}
+  \textbf{Given} Tolerance $\epsilon > 0$.\\
+  \textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
+  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
+  \textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
+  \Repeat{
+    $\frac{\|x^{(k+1)} - x^{(k)}\|^2_2}{2\tau} + \frac{\|\zeta^{(k+1)} - \zeta^{(k)}\|^2_2}{2\sigma} < \epsilon$}{
+    \begin{eqnarray*}
+      \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
+      x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
+      \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
+      k &\leftarrow& k + 1
+    \end{eqnarray*}
+  } \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
+  \label{Tab:algo}
+\end{algorithm}
+
+\subsection{Convergence analysis of the algorithm}
+Pending...
 
@@
 \end{remark}
-
-\begin{algorithm}[htb]
-\caption{Primal-dual algorithm for computing best response against opponent's realization plan $y_0$}
-\textbf{Let} $\epsilon > 0$ be a given tolerance.\\
-\textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
-$\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
-\textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
-\Repeat{
-  $\frac{1}{k + 1}\sum_{j=0}^{k}{\|e - E\tilde{x}^{(j)}\|^2_2} < \epsilon$}{
-  \begin{eqnarray*}
-    \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
-    x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
-    \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
-    k &\leftarrow& k + 1
-  \end{eqnarray*}
-} \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
-\label{Tab:pseudocode_pb}
-\end{algorithm}
-
-\subsection{Convergence analysis of the algorithm}
-Pending...
 

### 2014-07-27 paper.tex
paper improved

@@
 \begin{itemize}
-\item $A^T$: \quad transpose of the matrix $A$;
-\item $\begin{bmatrix}A\\B\end{bmatrix}$: vertical stacking of the matrices $A$ and $B$;
-\item $v_j$: \quad $j$th component of the vector $v$;
+\item $\mathbb{R}^{m, n}$ \quad the space of all $m$-by-$p$ real matrices;
+\item $E^{-1}(U)$: \quad the pre-image of $U \subset \mathbb{R}^n$ under the matrix $E \in \mathbb{R}^{p,n}$,
+namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
+\item $A^T$: \quad the transpose of the matrix $A$;
+\item $\begin{bmatrix}A\\B\end{bmatrix}$: \quad the vertical stacking of the matrices $A$ and $B$;
+\item $v_j$: \quad the $j$th component of the vector $v$;
 \item $u^Tv$: \quad the dot product of two vectors $u$ and $v$;
@@
 \item $\|K\|_2$: \quad the matrix 2-norm of the matrix $K$;
+\item \textit{l.s.c}: \quad acronym for \textit{lower semi-continuous};
 \item $f^*$: \quad the Fenchel transform of the convex l.s.c function $f$;
-\item \textit{l.s.c}: \quad acronyme for ``lower semi-continuous'';
-\item $E^{-1}(U)$: \quad the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
-namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
 \end{itemize}

### 2014-07-27 best_response.py

@@ -34,8 +34,8 @@ def best_response(A, E, e, y0, max_iter=1000, tol=1e-2, theta=1.,
     tau = sigma = .99 / L
     assert tau * sigma * L * L < 1.
     const = tau * A.T.dot(y0)
-    average_error = 0
-    average_errors = []
+    error = 0
+    errors = []
     for k in xrange(max_iter):
         old_x = x.copy()
         old_zeta = zeta.copy()

### 2014-08-08 paper.tex
yet another endeavor towards game tree abstraction

--- 2014-07-27 paper.tex
@@
-\documentclass[a4paper,10pt,journal]{IEEEtran}
+\documentclass[a4paper,9pt,journal]{IEEEtran}
 \usepackage{graphicx} \usepackage[cmex10]{amsmath}
@@
 %\onecolumn
-\title{A fast primal-dual algorithm for computing best response strategies in two-person sequential games}
+\title{A fast primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum sequential games}
 
@@
 %% and more recently, the Nesterov Excessive Gap Technique.
-By way of example, we conclude by exhibiting results on Texas Hold'em Poker.
+% By way of example, we conclude by exhibiting results on Texas Hold'em Poker.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-  game theory; two-person sequential game; best response; convex-optimization; contraint; primal-dual scheme
+  game theory; two-person sequential game; Nash equilibria; best response; convex-optimization; contraint; primal-dual scheme
 \end{IEEEkeywords}
@@
 \begin{itemize}
-\item $A^T$: \quad transpose of the matrix $A$;
-\item $\begin{bmatrix}A\\B\end{bmatrix}$: vertical stacking of the matrices $A$ and $B$;
-\item $v_j$: \quad $j$th component of the vector $v$;
-\item $u^Tv$: \quad the dot product of two vectors $u$ and $v$;
-\item $\mathbb{R}_+$: \quad the nonnegative part of the real-line $\mathbb{R}$;
-\item $(x)_+$: \quad the component-wise maximum of the vector $x$ and 0;
-\item $i_C$: \quad the indicator function of the convex set $C$;
-\item $\Pi_C$: \quad the euclidean projector onto the convex set $C$;
-\item $\|K\|_2$: \quad the matrix 2-norm of the matrix $K$;
-\item $f^*$: \quad the Fenchel transform of the convex l.s.c function $f$;
-\item \textit{l.s.c}: \quad acronyme for ``lower semi-continuous'';
-\item $E^{-1}(U)$: \quad the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
+\item $\mathbb{R}^{m, n}$ \quad space of all $m$-by-$p$ real matrices;
+\item $E^{-1}(U)$: \quad pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
 namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
+\item $A^T$: \quad transpose of a matrix $A$;
+\item $\begin{bmatrix}A\\B\end{bmatrix}$: \quad vertical stacking of two matrices $A$ and $B$;
+\item $v_j$: \quad $j$th component of  a vector $v$;
+\item $u^Tv$: \quad dot product of two vectors $u$ and $v$;
+\item $\mathbb{R}^n_+$: \quad the $n$-dimensional nonnegative orthant;
+\item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
+\item $i_C$: \quad indicator function of a convex set $C$;
+\item $\Pi_C$: \quad euclidean projector onto a convex set $C$;
+\item $\|K\|_2$: \quad matrix 2-norm of a matrix $K$;
+\item \textit{p.c.l.s.c}: \quad acronym for \textit{proper convex lower semi-continuous};
+\item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{p.c.l.s.c} function $f$;
+\item $(1 + \sigma \partial f)^{-1}$: resolvent (a.k.a proximal) operator of a \textit{p.c.l.s.c} function $f$, for a given stepsize $\sigma > 0$
 \end{itemize}
@@
 Consider a two-person sequential game\footnote{In a sequential game, players take turns in play, one after the other,
-as opposed to simultaneous play.} in \textit{sequential-form} (See for example, \cite{von1996efficient} and \cite{koller1996efficient} 
+as opposed to simultaneous play.} in \textit{sequential-form} (See for example, \cite{von1996efficient}
+and \cite{koller1996efficient} 
 for theory on sequential-form representation), and let $A \in \mathbb{R}^{m,n}$ be our payoff matrix.
@@
 finding a best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$, given a fixed
-(possibly mixed) strategy $y_0$ for the opponent, where $E$ is a sparse $p$-by-$n$ matrix whose entries are $-1$, $0$, or $+1$,
-and $(1, 0, 0, ..., 0) =: e \in \mathbb{R}^p$. Recall that $E$ and $e$ encode linear constraints on our ``admissible''
-realization plans\footnote{In games in sequential form, the terms ``strategy'' and ``realization plan''
-mean thesame thing.} $x$, in the sequential form representation of the game.
-In the language of convex-optimization,
+behavioral strategy $y_0$ for the opponent, where $E$ is a sparse $p$-by-$n$ matrix whose
+entries are $-1$, $0$, or $+1$, and $(1, 0, 0, ..., 0) =: e \in \mathbb{R}^p$. Recall that $E$
+and $e$ encode linear constraints on our ``admissible'' realization plans\footnote{In games
+in sequential form, the terms ``strategy'' and ``realization plan'' mean thesame thing.} $x$,
+in the sequential form representation of the game. In the language of convex-optimization,
 one can readily give the following saddle-point formulation for this problem. Viz,
@@
 \begin{definition}
-A solution $x^*$ to problem \eqref{eq:opt_pb} is called a \textit{best response} strategy against the opponent's fixed strategy $y_0$.
+A solution $x^*$ to problem \eqref{eq:opt_pb} is called a \textit{best response} strategy against
+the opponent's fixed strategy $y_0$.
 \end{definition}
@@
 \begin{remark}
-Of course $y_0$ is not necessarily an optimal strategy for the opponent. In case it is, the pair $(x^*, y_0)$ is a Nash equilibrium for the game.
+Of course $y_0$ is not necessarily an optimal strategy for the opponent. In case it is, the pair $(x^*, y_0)$
+is a Nash equilibrium for the game.
 \end{remark}
@@
 \begin{remark}
-  In practice, $A$ and $E$ are very sparse as a game will typically have very few leafs
-(i.e terminal states). This sparsity should be thoroughly exploited by a solver for problem \eqref{eq:opt_pb}.
+  In practice, $A$, $E$, and $F$ are very sparse: $A$ will be sparse because a concrete sequential game will
+typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
+combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
+$E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
+zig-zag between only a limited number of the player's information sets so that a move at an information set will
+rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
+This sparsity should be thoroughly exploited\footnote{For example when
+multiplying vectors with these matrices.} by a solver for problem \eqref{eq:opt_pb}.
 \end{remark}
@@
 \section{The proposed algorithm}
-\label{sec:algo}
+0\label{sec:algo}
 In this section we present the algorithm which is the purpose of this paper, namely an algorithm
@@
 
-Furthermore, one easily checks that $F^*$ and $G$ are \textit{proper} convex l.s.c, with resolvent
+Furthermore, one easily checks that $F^*$ and $G$ are \textit{p.c.l.s.c} with resolvent
 (a.k.a \textit{proximity}) operators given by the simple formulae:
@@
 \begin{algorithm}[htb]
-  \caption{Primal-dual algorithm for computing best response against opponent's realization plan $y_0$}
+  \caption{Primal-dual algorithm for computing best response against opponent's fixed realization plan $y_0$}
   \textbf{Given} Tolerance $\epsilon > 0$.\\

### 2014-08-08 abstractions.py

@@ -1,0 +1,294 @@
+import itertools
+import re
+import networkx as nx
+from nose.tools import assert_true, assert_equal, assert_false
+import numpy as np
+
+
+class Game(object):
+    """Implementation of KUHN(3, 1, 1, 2) 1-card poker."""
+
+    def __init__(self):
+        self.tree = nx.DiGraph()
+        self.edge_labels = {}
+        self.infosets = {}
+        self.sequences = {}
+        self.constraints = {}
+        self.player_choices = {0: list(itertools.permutations('123', 2)),
+                               1: 'CFKR', 2: 'cfkr'}
+        self.build_tree()
+        self.build_infosets()
+
+    def _add_labelled_edge(self, x, y, move, **kwargs):
+        """Adds a labelled edge to the tree."""
+        self.tree.add_node(y, **kwargs)
+        self.tree.add_edge(x, y)
+        self.edge_labels[(x, y)] = move
+
+    def build_tree(self):
+        """Builds the tree (nx.DiGraph object)."""
+        proba = "1/6"
+        for perm in itertools.permutations('123', 2):
+            self._add_labelled_edge('/', '/.%s' % ''.join(perm), proba,
+                                    player=0, proba=eval("1. * %s" % proba))
+            for a in 'CR':
+                self._add_labelled_edge('/.%s' % ''.join(perm), '/.%s.%s' % (
+                        ''.join(perm), a), a, player=1)
+                if a == 'C':  # check
+                    for b in 'cr':
+                        dst = '/.%s.%s.%s' % (''.join(perm), a, b)
+                        self._add_labelled_edge('/.%s.%s' % (''.join(perm), a),
+                                           dst, b, player=2)
+                        if b == "c":
+                            self.tree.add_node(dst, player=2,
+                                               payoff=cmp(*perm))
+                        else:  # raise
+                            for x in 'FK':
+                                dst = '/.%s.%s.%s.%s' % (
+                                    ''.join(perm), a, b, x)
+                                self._add_labelled_edge(
+                                    '/.%s.%s.%s' % (''.join(perm), a, b),
+                                    dst, x, player=1)
+                                if x == "F":  # fold
+                                    self.tree.add_node(dst, player=1,
+                                                       payoff=-1)
+                                else:  # call
+                                    self.tree.add_node(dst, player=1,
+                                               payoff=2 * cmp(*perm))
[…]

### 2014-08-08 occam.py

@@ -1,121 +1,322 @@
 # Author: DOHMATOB Elvis Dopgima <gmdopp@gmail.com>
 
 import itertools
+import re
+from nose.tools import assert_true, assert_equal
 import numpy as np
 import pylab as pl
 import networkx as nx
 
 
-def kuhn3112_gametree():
-    """Function to generate KUHN(3, 1, 1, 2) poker game tree."""
-    G = nx.DiGraph()
-    G.add_node('/', player=None)
-    edge_labels = {}
+class Kurn3112GameTree(object):
+    """Implementation of kuhn(3, 1, 1, 2) poker game tree."""
 
-    def _add_labelled_edge(x, y, move, **kwargs):
-        G.add_node(y, **kwargs)
-        G.add_edge(x, y)
-        edge_labels[(x, y)] = move
+    def __init__(self):
+        self.tree = nx.DiGraph()
+        self.edge_labels = {}
 
-    for perm in itertools.permutations('123', 2):
-        _add_labelled_edge('/', '/.%s' % ''.join(perm), '1/6', player=0)
-        for a in 'CR':
-            _add_labelled_edge('/.%s' % ''.join(perm), '/.%s.%s' % (
-                    ''.join(perm), a), a, player=1)
-            if a == 'C':  # check
-                for b in 'cr':
-                    dst = '/.%s.%s.%s' % (''.join(perm), a, b)
-                    _add_labelled_edge('/.%s.%s' % (''.join(perm), a),
-                                       dst, b, player=2)
-                    if b == "c":
-                        G.add_node(dst, player=2, payoff=cmp(*perm))
-                    else:  # raise
-                        for x in 'FK':
-                            dst = '/.%s.%s.%s.%s' % (''.join(perm), a, b, x)
-                            _add_labelled_edge(
-                                '/.%s.%s.%s' % (''.join(perm), a, b),
-                                dst, x, player=1)
-                            if x == "F":  # fold
-                                G.add_node(dst, player=1, payoff=-1)
-                            else:  # call
-                                G.add_node(dst, player=1,
-                                           payoff=2 * cmp(*perm))
-            else:  # raise
-                for b in "fk":
-                    dst = '/.%s.%s.%s' % (''.join(perm), a, b)
-                    _add_labelled_edge('/.%s.%s' % (''.join(perm), a),
-                                       dst, b, player=2)
-                    if b == "f":  # fold
-                        G.add_node(dst, player=2, payoff=1.)
[…]

### 2014-08-08 paper.tex
computing best response strategy using preconditioned primal-dual algorithm

@@
 \begin{itemize}
-\item $\mathbb{R}^{m, n}$ \quad space of all $m$-by-$p$ real matrices;
+\item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$p$ real matrices;
 \item $E^{-1}(U)$: \quad pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
@@
 \item $\|K\|_2$: \quad matrix 2-norm of a matrix $K$;
-\item \textit{p.c.l.s.c}: \quad acronym for \textit{proper convex lower semi-continuous};
-\item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{p.c.l.s.c} function $f$;
-\item $(1 + \sigma \partial f)^{-1}$: resolvent (a.k.a proximal) operator of a \textit{p.c.l.s.c} function $f$, for a given stepsize $\sigma > 0$
+\item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
+\item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
+\item $(1 + \sigma \partial f)^{-1}$: resolvent (a.k.a proximal) operator of a \textit{l.s.c.p.c} function $f$, for a given stepsize $\sigma > 0$
 \end{itemize}
@@
 
-Furthermore, one easily checks that $F^*$ and $G$ are \textit{p.c.l.s.c} with resolvent
+Furthermore, one easily checks that $F^*$ and $G$ are \textit{l.s.c.p.c} with resolvent
 (a.k.a \textit{proximity}) operators given by the simple formulae:

### 2014-08-08 best_response.py

@@ -3,6 +3,52 @@ import numpy as np
 from scipy import linalg
 
 
+def best(A, E, e, y0, max_iter=1000, tol=1e-2, callback=None, **kwargs):
+    c = -A.T.dot(y0)
+    m, n = E.shape
+    alpha = 1.
+    tau = np.reciprocal([(np.abs(col) ** (2. - alpha)).sum() for col in E.T])
+    sigma = np.reciprocal([(np.abs(row) ** alpha).sum() for row in E])
+    x = np.zeros(n)
+    zeta = np.zeros(m)
+    old_value = np.inf
+    values = []
+    for k in xrange(max_iter):
+        old_x = x.copy()
+        old_zeta = zeta.copy()
+        x -= tau * (E.T.dot(zeta) + c)
+        x = np.maximum(x, 0.)
+        value = c.T.dot(x)
+        values.append(value)
+        change = old_value - value
+        old_value = value
+        zeta += sigma * (E.dot(2. * x - old_x) - e)
+        if callback:
+            callback(locals())
+
+        print "Iteration %03i/%03i: value=%5.2e, change=%5.2e" % (
+            k + 1, max_iter, value, change)
+        change = abs(change)
+        if change < tol:
+            print "Converged (|change| < %5.2e)." % tol
+            break
+
+    import pylab as pl
+    values = -np.array(values)
+    value *= -1.
+    pl.plot(values)
+    pl.axhline(value, linestyle="--", c="r",
+               label="value of game (= %g)" % value)
+    pl.ylabel("primal objective at kth iteration")
+    pl.xlabel("k")
+    pl.legend(loc="best")
+    pl.title(
+        ("Computing best response strategy in sequence-form game using "
+         "diagonally preconditioned primal-dual algorithm of Chambolle-Pock"))
+    pl.show()
+    return x, zeta, None
+
+
 def best_response(A, E, e, y0, max_iter=1000, tol=1e-2, theta=1.,
                   callback=None):
     """Computes best response to an opponent's realization plan in a two-person
@@ -36,6 +82,7 @@ def best_response(A, E, e, y0, max_iter=1000, tol=1e-2, theta=1.,
     const = tau * A.T.dot(y0)
     error = 0
     errors = []
+    values = []
     for k in xrange(max_iter):
         old_x = x.copy()
         old_zeta = zeta.copy()
[…]

### 2014-08-13 paper.tex
refactor

@@
 \begin{remark}
-  In practice, $A$, $E$, and $F$ are very sparse: $A$ will be sparse because a concrete sequential game will
-typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
-combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
-$E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
-zig-zag between only a limited number of the player's information sets so that a move at an information set will
-rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
+  In practice, $A$, $E$, and $F$ are very sparse.
+%% : $A$ will be sparse because a concrete sequential game will
+%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
+%% combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
+%% $E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
+%% zig-zag between only a limited number of the player's information sets so that a move at an information set will
+%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
 This sparsity should be thoroughly exploited\footnote{For example when
@@
 \section{The proposed algorithm}
-0\label{sec:algo}
+\label{sec:algo}
 In this section we present the algorithm which is the purpose of this paper, namely an algorithm

### 2014-08-13 abstractions.py

@@ -1,3 +1,9 @@
+"""
+References
+----------
+[1] Bernhard von Stengel, "Efficient Computation of Behavior Strategies"
+
+"""
 # Author: DOHMATOB Elvis Dopgima
 
 import re
@@ -6,19 +12,10 @@ import numpy as np
 from nose.tools import assert_equal, assert_true, assert_false
 
 
-class Kuhn3112(object):
-    """
-    Proof-of-Concept for sequence-form representation (@ la BvS) poker.
-
-    References
-    ----------
-    [1] Bernhard von Stengel, "Efficient Computation of Behavior Strategies"
-
-    """
+class Game(object):
+    player_choices = None
 
     def __init__(self):
-        self.player_choices = {0: ['12', '13', '21', '23', '31', '32'],
-                               1: list('CFKR'), 2: list('cfkr')}
         self.tree = nx.DiGraph()
         self.edge_labels = {}
         self.infosets = {}
@@ -31,58 +28,16 @@ class Kuhn3112(object):
         self.build_strategy_constraints()
         self.build_payoff_matrix()
 
-    def add_labelled_edge(self, x, y, move, **kwargs):
+    def build_tree(self):
+        raise NotImplementedError
+
+    def add_labelled_edge(self, x, choice, **kwargs):
         """Adds a labelled edge to the tree."""
+        y = ".".join([x, choice])
         self.tree.add_node(y, **kwargs)
         self.tree.add_edge(x, y)
-        self.edge_labels[(x, y)] = move
-
-    def cmp_cards(self, a, b):
-        return cmp(int(a), int(b))
-
-    def build_tree(self):
-        """Builds the tree (nx.DiGraph object)."""
-        for perm, proba in zip(['12', '13', '21', '23', '31', '32'],
-                               [1. / 6] * 6):
-            self.add_labelled_edge('/', '/.%s' % ''.join(perm), proba,
-                                   player=0, proba=eval("1. * %s" % proba))
-            for a in 'CR':
-                self.add_labelled_edge('/.%s' % ''.join(perm), '/.%s.%s' % (
-                        ''.join(perm), a), a, player=1)
-                if a == 'C':  # check
-                    for b in 'cr':
-                        dst = '/.%s.%s.%s' % (''.join(perm), a, b)
-                        self.add_labelled_edge('/.%s.%s' % (''.join(perm), a),
-                                           dst, b, player=2)
-                        if b == "c":
-                            self.tree.add_node(dst, player=2, proba=proba,
[…]

### 2014-08-18 paper.tex
more

@@
 \begin{document}
-%\onecolumn
+\onecolumn
 \title{A fast primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum sequential games}
@@
 \begin{itemize}
+\item $\mathcal{P}(S)$: \quad set of all the subsets of $S$;
+\item $\mathcal{P}_k(S)$: \quad set of all the subsets of $S$ which have exactly $k$ elements;
 \item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$p$ real matrices;
 \item $E^{-1}(U)$: \quad pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
-namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
+namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$;
 \item $A^T$: \quad transpose of a matrix $A$;
@@
 \end{itemize}
+
+\subsection{Generating the Texas Hold'em Poker game tree}
+Let $a := (a_1, a_2, a_3, a_4) \in 
+\mathbb{R}\times\mathbb{R}\times\mathbb{R}^2\times\mathbb{R}^2$ hold the accounting info, where:
+\begin{itemize}
+\item $a_1\in\mathbb{R}$ is the running bet size,
+\item $a_2\in\mathbb{R}$ is the running total amount in the pot,
+\item $a_3\in\mathbb{R}^2$ is a vector showing what each player has put into the pot sofar, and
+\item $a_4\in\mathbb{R}^2$ is a vector showing running capital of each player.
+\end{itemize}
+Let $ok(a, L)$ be a flag which is true iff the bet size $a_1$ has not exceeded the limit $L$ and each player's running credit is nonnegative.
+For any round $t\in\mathbb{N}$, let $p(t)$ be the player to begin and $\Sigma(t)$ be the set of all signals that can be emitted by the chance player.
+\definition{
+A signal is simply any part of the information needed at shutdown to score the player's hands.
+}
+\remark{
+An emitted signal can be fully observable (for example, community cards), or only partially observable (for example when private / hole / pocket cards are delt, players can only see their own hole cards given to them; they can't see another player's hole cards).
+}
+
+\begin{equation}
+  \gamma(t, T, a, L) = \begin{cases} 
+    \mathcal{P}_1(\Sigma(t)), &\mbox{if } (t < T) \land ok(a, L) \land (p(t) = 0);\\
+            {\{\textbf{F}_{p(t)}\} \cup \textbf{C}_{p(t)}\gamma(t + 1, T, a, L) \cup \textbf{K}_{p(t)}\lambda(t, T, g(a, \textbf{K}_{p(t)}), L)},&\mbox{if } (t < T) \land ok(a, L) \land (p(t) > 0);\\
+            \emptyset, &\mbox{if } t \ge T \lor \neg ok(a, L) .\end{cases}
+\end{equation}
+where the auxiliary function $\lambda$ is defined by:
+\begin{equation}
+  \left.
+  \begin{aligned}
+    \lambda(t, T, a, L) := \cup_{n=0}^\infty\alpha_1^{(n)}(t, T, a, L) \cup \cup_{n=0}^\infty\alpha_2^{(n)}(t, T, a, L)\\
+    \alpha_1^{(n)}(t, T, a, L) := (\textbf{R}_{p(t)'}\textbf{R}_{p(t)})^n\mathcal{P}_1(\{\textbf{F}_{p(t)'}, \textbf{K}_{p(t)'}\})\gamma(t + 1, T, g(a, (\textbf{R}_{p(t)'}\textbf{R}_{p(t)})^n\mathcal{P}_1(\{\textbf{F}_{p(t)'}, \textbf{K}_{p(t)'}\})), L)\\
+    \alpha_2^{(n)}(t, T, a, L) := (\textbf{R}_{p(t)'}\textbf{R}_{p(t)})^n\textbf{R}_{p(t)'}\mathcal{P}_1(\{\textbf{F}_{p(t)}, \textbf{K}_{p(t)}\})\gamma(t + 1, T, g(a, (\textbf{R}_{p(t)'}\textbf{R}_{p(t)})^n\textbf{R}_{p(t)'}\mathcal{P}_1(\{\textbf{F}_{p(t)}, \textbf{K}_{p(t)}\})), L)
+    %% \lambda_{1}(t, T, a, L) := \cup_{n=0}^\infty\alpha_1^{(n)}(t, T, a, L)\\
+    %% \lambda_{2}(t, T, a) := \cup_{n=0}^\infty\\
+    \end{aligned}
+  \right\}
+\end{equation}
 

### 2014-08-18 basic.py

@@ -1,0 +1,114 @@
+from nose.tools import assert_equal
+
+MOVES = ['fold', 'check', 'call', 'raise']
+CHANCE_MOVES = ['JJ', 'JQ', 'QJ', 'QQ']
+
+
+def init_state(player=0, pot=0, bet_size=1., accounts={1: 10., 2: 10},
+               middle=False, potted={1: 0, 2: 0}, move=None, norminal=1,
+               stage=0, max_stages=1):
+    return dict(player=player, pot=pot, bet_size=bet_size, move=move,
+                accounts=accounts.copy(), middle=middle, stage=stage,
+                potted=potted.copy(), norminal=norminal,
+                max_stages=max_stages)
+
+
+def dead(state):
+    if state["move"] == "fold":
+        return True
+    if state['stage'] == state['max_stages']:
+        return True
+
+
+def can(state, move):
+    if state['player'] == 0:
+        return move in CHANCE_MOVES
+    if move == "fold":
+        return True
+    if move == "call":
+        return state["accounts"][state["player"]] >= state['bet_size']
+    if move == "raise":
+        return state["accounts"][state["player"]] >= 2 * state['bet_size']
+    if move == "check":
+        if state["player"] != state["norminal"]:
+            return False
+        if state["middle"]:
+            return False
+        return True
+    else:
+        assert 0
+
+
+def end_stage(state):
+    state['stage_ended'] = True
+    state['stage'] += 1
+
+
+def moves(state):
+    if state['player'] > 0:
+        return [move for move in MOVES if can(state, move)]
+    else:
+        assert 0
+
+
+def handle_fold(state):
+    pass
+
+
+def handle_check(state):
+    end_stage(state)
+
+
+def handle_call(state):
+    state['pot'] += state['bet_size']
+    state['potted'][state['player']] += state['bet_size']
+    state['accounts'][state['player']] -= state['bet_size']
+
+
+def handle_raise(state):
+    state['bet_size'] *= 2.
+    handle_call(state)
+
+
+def next_player(state):
+    if state['player'] == 0:
+        state['player'] = state["norminal"]
+    else:
+        state['player'] = 1 + state["player"] % 2
+
+
+def handle_move(state, move):
+    if not can(state, move):
+        return False
+    state['move'] = move
+    eval("handle_%s" % move)(state)
+    next_player(state)
+    return True
+
+
+def play(state):
+    for move in moves(state):
[…]

### 2014-08-18 bones.py

@@ -1,0 +1,89 @@
+"""
+Basic heads-up limit Texas Hold'em
+
+The game has a maximum of 2 rounds. In each round, some public signals
+(possible no signal, in a non-final round) are revealed by the dealer
+and a stage game played. Let's first define the following betting
+actions:
+
+----------------------------------------------------------------------
+| ACTION |            DESCRIPTION                |   WHEN POSSIBLE   |
+|--------------------------------------------------------------------|
+| fold   | throwaway one's cards, thus  ending   | always            |
+|        | the game with th opponent as winner   |                   |
+|--------------------------------------------------------------------|
+| call   | bet the same amount as the running    | always            |
+|        | bet amount                            |                   |
+|--------------------------------------------------------------------|
+| raise  | increase the running bet amount by 1  | if new bet would  |
+|        | and bet the result                    | be less than some |
+|        |                                       | hard-limit        |
+|--------------------------------------------------------------------|
+| check  | bet nothing and move to the next      | if first player   |
+|        |                                       | for this  round   |
+----------------------------------------------------------------------
+
+"""
+
+MOVES = ['fold', 'kall', 'check', 'raise']
+
+
+def can(move, info):
+    if move == "fold":
+        return True
+    elif move == "kall":
+        return True
+    elif move == "raise":
+        return info['bet'] + 1. <= info['limit']
+    elif move == "check":
+        return not (info["stage_started"] or info['last_stage'])
+    else:
+        assert 0
+
+
+def get_moves(info):
+    return [move for move in MOVES if can(move, info)]
+
+
+def do_move(move, info):
+    if move == "fold":
+        info["stage_ended"] = True
+        info["game_ended"] = True
+    elif move == "kall":
+        info["pot"] += info["bet"]
+        if info["stage_started"]:
+            info["stage_ended"] = True
+    elif move == "raise":
+        info['bet'] += 1
+        info["pot"] += info["bet"]
+    elif move == "check":
+        info['stage_ended'] = True
+    else:
+        assert 0
+
+
+def go(info):
+    if not info['stage_started']:
+        print " ."
+    info['player'] = 1 - info['player']
+    moves = get_moves(info)
+    info['padding'] += " "
+    for cnt, move in enumerate(moves):
+        info_ = info.copy()
+        info_['stage_started'] = True
+        print info_['padding'] + "|"
+        if cnt == len(moves) - 1:
+            info_['padding'] += " "
[…]

### 2014-08-18 chambolle_pock.py

@@ -1,0 +1,128 @@
+import numpy as np
+
+
+proj_interval_a_b = lambda a, b, y: (a <= y) * (y <= b) * y + b * (
+    y >= b) + a * (y <= a)
+
+
+def averaged_projections(proj_C, proj_D, y, max_iter=100, callback=None,
+                         verbose=0):
+    """Averaged projections algorithm.
+
+    Projects a point onto the intersection of two sets C and D. It is
+    assumed that the euclidean projections onto C and D can be effectively
+    computed separately.
+    """
+    for k in xrange(max_iter):
+        if callback:
+            old_y = y.copy()
+        if verbose or 1:
+            print "Iteration: %03i/%03i: proj=%s" % (k + 1, max_iter, y)
+
+        # project
+        y = .5 * (proj_C(y) + proj_D(y))
+
+        # check convergence
+        if callback:
+            if callback(old_y, y):
+                return y
+    return y
+
+
+def prox_l1(x, tau):
+    d = np.abs(x)
+    nz = d.nonzero()
+    x[nz] *= np.maximum(1. - tau / d[nz], 0.)
+    return x
+
+
+def prox_conjugate(prox_f, x, tau):
+    if tau == 0.:
+        return x
+    x /= tau
+    x -= prox_f(x, 1. / tau)
+    return x
+
+
+def chambolle_pock(K, KT, prox_G, prox_Fstar, x0, y0, max_iter=100,
+                   callback=None, theta=1., tol=1e-4):
+    tau = sigma = .99 / K.L
+    assert tau * sigma * K.L * K.L < 1.
+    x = np.array(x0)
+    y = np.array(y0)
+    xbar = x.copy()
+    for k in xrange(max_iter):
+        old_x = x.copy()
+        old_y = y.copy()
+        y += sigma * K(xbar)
+        y = prox_Fstar(y, sigma)
+        x -= tau * KT(y)
+        x = prox_G(x, tau)
+        xbar = x + theta * (x - old_x)
+
+        if callback:
+            callback(locals())
+
+        a = x - old_x
+        b = y - old_y
+        error = .5 * (np.dot(a, a) / tau + np.dot(b, b) / sigma)
+        print "Iteration %04i/%04i: error=%.3e" % (k + 1, max_iter, error)
+        if error < tol:
+            break
+
+    return x, y
+
+if __name__ == "__main__":
+
+    """
+    This example finds the point in an interval [a, b] with the smallest
[…]

### 2014-08-18 dop.py

@@ -1,0 +1,83 @@
+import numpy as np
+
+move_id = lambda move, p: move.upper() if p == 1 else move.lower()
+norminal = lambda t: 1 + t % 2
+opponent = lambda p: 1 + p % 2
+whose = lambda move: 1 if move == move.upper() else 2
+
+
+def chance(t):
+    if t == 0:
+        for perm in ['JJ', 'JQ', 'QJ', 'QQ']:
+            yield perm
+    else:
+        yield ""
+
+
+def ok(a, L):
+    """Checks that the bank is still sane."""
+    return a and a[0] <= L and np.all(a[3] >= .0)
+
+
+def do_call(a, p):
+    """Executes a "call" action."""
+    a[1] += a[0]
+    a[2][p - 1] += a[0]
+    a[3][p - 1] -= a[0]
+    return a
+
+
+def do_raise(a, p):
+    """Executes a "raise" action."""
+    a[0] *= 2.
+    return do_call(a, p)
+
+
+def copy_a(a):
+    """Copies / clones a banks HD."""
+    return [a[0], a[1], a[2].copy(), a[3].copy()]
+
+
+def u(a, cmd):
+    """Executes a cmd and updates the bank info."""
+    cmd = cmd.split(".")[-1]
+    if cmd.lower() in ['', 'f']:
+        return a
+    elif cmd[0].lower() == "k":
+        do_call(a, whose(cmd[0]))
+    elif cmd[0].lower() == "r":
+        do_raise(a, whose(cmd[0]))
+    return u(a, cmd[1:])
+
+
+def gamma(t, T, a, L):
+    """Generates all (admissible) nodes of the game tree."""
+    if t < T and ok(a, L):
+        p = norminal(t)
+        q = opponent(p)
+        for perm in chance(t):
+            yield perm + move_id("f", p)
+            c = move_id("c", p)
+            a[0] = 1
+            for x in gamma(t + 1, T, a, L):
+                yield perm + c + "." + x
+            k = move_id("k", p)
+            token = move_id("r", q) + move_id("r", p)
+            for o, last_sip in zip([p, q], ['', move_id("r", q)]):
+                for end in [move_id('f', o), move_id('k', o)]:
+                    rep = ""
+                    x = perm + k + rep + last_sip + end
+                    a_ = u(copy_a(a), x)
+                    while ok(a_, L):
+                        yield x
+                        for y in gamma(t + 1, T, a_, L):
+                            yield x + "." + y
[…]

### 2014-08-18 ellipsoid.py

@@ -1,0 +1,189 @@
+from math import sqrt
+import numpy as np
+from scipy.sparse.linalg import LinearOperator
+from nose.tools import assert_true
+from nilearn.decoding.sparse_models.common import (
+    gradient_id, div_id, _unmask)
+
+
+def power(A, p, max_iter=1000):
+    """Power iteration to estimate the dorminant eigval of an operator."""
+    b = np.random.randn(p)
+    for _ in xrange(max_iter):
+        b = A(b)
+        b /= sqrt((b ** 2).sum())
+    lambd = np.dot(b, A(b)) / np.dot(b, b)
+    return lambd
+
+
+def diagonal_preconditioners(X, shape, l1_ratio, alpha=1.,
+                            salt=1e-6):
+    """Computes diagonal preconditioners for sparse-variation model."""
+    shape_ = [len(shape) + 1] + list(shape)
+    p = np.prod(shape)
+    beta = 2. - alpha
+
+    # compute \Tau and \Sigma_2
+    linop = LinearOperator(
+        (4 * p, p),
+        lambda w: gradient_id(w.reshape(shape),
+                              l1_ratio=l1_ratio).ravel(),
+        dtype=X.dtype)
+
+    tau = np.array([(np.abs(c) ** alpha).sum()
+                    for c in X.T])
+    sigma2 = [1. / (np.abs(r) ** beta).sum() for r in X]
+    e = np.zeros(p)
+    for j in xrange(linop.shape[1]):
+        e *= 0
+        e[j] = 1
+        tau[j] += (np.abs(linop(e)) ** alpha).sum()
+    tau = np.reciprocal(tau)
+
+    # compute \Sigma_1
+    sigma1 = np.zeros(4 * p)
+    linop = LinearOperator(
+        (p, (len(shape) + 1) * p),
+        lambda w: -div_id(w.reshape(shape_),
+                          l1_ratio=l1_ratio).ravel(),
+        dtype=X.dtype)
+    e = np.zeros(linop.shape[1])
+    for j in xrange(linop.shape[1]):
+        e *= 0
+        e[j] = 1
+        sigma1[j] += 1. / ((np.abs(linop(e)) + salt) ** alpha).sum()
+    sigma1 = sigma1.reshape((-1, p))
+    return tau, sigma1, sigma2
+
+
+class DiagonallyPreconditionedStack(object):
+    """Diagonally precondioned operator and resolvents for primal-dual.
+
+    Notes
[…]

### 2014-08-18 g.py

@@ -1,0 +1,59 @@
+from copy import deepcopy
+import numpy as np
+
+move_id = lambda move, p: move.upper() if p == 1 else move.lower()
+other_player = lambda p: 1 + p % 2
+whose = lambda m: 1 if m == m.upper() else 2
+
+
+def clone(obj):
+    """Quick and dirty technology for cloning an object instance."""
+    c = object.__new__(obj.__class__)
+    c.__dict__ = deepcopy(obj.__dict__)
+    return c
+
+
+class Treasury(object):
+    def __init__(self, capitals, bet_size=1, limit=np.inf):
+        self.limit = limit
+        self.bet_size = bet_size
+        self.pot = 0.
+        self.potted = np.zeros(2)
+        self.accounts = np.array(capitals)
+
+    def do_call(self, p):
+        self.pot += self.bet_size
+        self.potted[p - 1] += self.bet_size
+        self.accounts[p - 1] -= self.bet_size
+        # if np.any(self.accounts < 0.):
+        #     raise RuntimeError("Some players have negative accounts!")
+        assert self.potted.sum() == self.pot
+
+    def do_raise(self, p):
+        self.bet_size *= 2
+        # if self.bet_size > self.limit:
+        #     raise RuntimeError(
+        #         "bet_size exceeded limmit of %g$" % self.limit)
+        self.do_call(p)
+
+    def __dict__(self):
+        return dict((k, getattr(self, k))
+                    for k in ["bet_size", "pot", "potted", "accounts"])
+
+    def __repr__(self):
+        return str(self.__dict__())
+
+
+def g(treasury, cmd):
+    if np.any(treasury.accounts <= 0) or treasury.bet_size > treasury.limit:
+        return None
+    elif not cmd or cmd[0].lower() == "f":
+        return treasury
+    elif cmd[0].lower() == "k":
+        treasury.do_call(whose(cmd[0]))
+        return g(treasury, cmd[1:])
+    elif cmd[0].lower() == "r":
+        treasury.do_raise(whose(cmd[0]))
+        return g(treasury, cmd[1:])
+    else:
+        assert 0

### 2014-08-18 game_abstraction.py

@@ -15,7 +15,7 @@ class PokerTree:
     def init_state(self, **kwargs):
         """Creates game state, overriding defaults with kwargs."""
         state = {}
-        state["player"] = kwargs.get('player', 0)
+        state["player"] = kwargs.get('player', 1)
         state["bet_size"] = kwargs.get('bet_size', 1)
         state["pot"] = kwargs.get('pot', 0)
         state["middle"] = kwargs.get('middle', False)
@@ -51,6 +51,12 @@ class PokerTree:
         self.end_round(state)
         state['hand_ended'] = True
 
+    def set_next_player(self, state):
+        if state['player'] == 0:
+            state['player'] = 1
+        else:
+            state['player'] = 1 + state['player'] % 2
+
     def handle_move(self, state, move):
         """Updates game state by effecting the given move."""
         if move == "check":
@@ -62,13 +68,13 @@ class PokerTree:
         elif move == "fold":
             self.end_hand(state)
         elif move == "raise":
-            state['bet_size'] += 1
+            state['bet_size'] *= 2
             state['pot'] += state['bet_size']
         else:
             assert 0
 
         state['middle'] = True
-        state['player'] = 1 - state['player']
+        self.set_next_player(state)
 
     def can_check(self, state):
         """Checks whether current player can "check" in given state."""
@@ -87,7 +93,7 @@ class PokerTree:
     def can_raise(self, state):
         """Checks whether current player can "raise" in given state."""
         # can raise if and only if new bet would not exceed limit
-        return state["bet_size"] + 1 <= self.limit
+        return 2 * state["bet_size"] <= self.limit
 
     def can_call(self, state):
         """Checks whether current player can "call" in given state."""
@@ -109,7 +115,7 @@ class PokerTree:
             move = "kall"
         if state['player'] == 1:  # XXX swapped with 0
             move = move.upper()
-        elif state['player'] == 0:
+        elif state['player'] == 2:
             move = move.lower()
         else:
             assert 0
@@ -135,10 +141,11 @@ class PokerTree:
             self.node_count += 1
             state_['node_id'] = self.node_count
             print state_['padding'][:-1] + (
-                "+-" + "%s(node_id=%i,round=%i,bet_size=%g$,pot=%g$)%s" % (
-                    mid, state_['node_id'], state_["round"],
-                    state_['bet_size'],
[…]

### 2014-08-18 grail.py

@@ -1,0 +1,237 @@
+from nose.tools import assert_true, assert_false, assert_equal
+
+MOVES = ['fold', 'check', 'call', 'raise']
+
+
+def init_state(**kwargs):
+    state = {}
+    state = state.copy()
+    state["player"] = kwargs.get('player', 0)
+    state["bet"] = kwargs.get('bet', 1)
+    state["pot"] = kwargs.get('pot', 0)
+    state["limit"] = kwargs.get('limit', 4)
+    state["middle"] = kwargs.get('middle', False)
+    state["stage_ended"] = kwargs.get('stage_ended', False)
+    state["game_ended"] = kwargs.get('game_ended', False)
+    state["stage"] = kwargs.get('stage', 0)
+    state["padding"] = kwargs.get('padding', "")
+    return state
+
+
+def end_stage(state):
+    state['stage_ended'] = True
+    state['stage'] += 1
+
+
+def end_game(state):
+    end_stage(state)
+    state['game_ended'] = True
+
+
+def handle_move(state, move):
+    if move == "check":
+        end_stage(state)
+    elif move == "call":
+        state['pot'] += state['bet']
+        if state["middle"]:
+            end_stage(state)
+    elif move == "fold":
+        end_game(state)
+    elif move == "raise":
+        state['bet'] += 1
+        state['pot'] += state['bet']
+    else:
+        assert 0
+
+    state['middle'] = True
+    state['player'] = 1 - state['player']
+
+
+def can_check(state):
+    if state['stage'] == 1:
+        # can only "check" in first round
+        return False
+    elif state['stage'] == 0:
+        # can't "check" in the middle of a round
+        return not state['middle']
+    else:
+        assert 0
+
+
+def can_fold(state):
+    # can always fold
+    return True
+
+
+def can_raise(state):
+    # can raise if and only if new bet would not exceed limit
+    return state["bet"] + 1 <= state['limit']
+
+
+def can_call(state):
+    assert state['bet'] <= state['limit']  # ensure game is not garbage
+    # can always call
+    return True
+
+
+def can(state, move):
+    return eval("can_%s(state)" % move)
+
+
+def get_moves(state):
+    return [move for move in MOVES if can(state, move)]
+
+
+def get_move_id(state, move):
+    if move == "call":
+        move = "kall"
+    if state['player'] == 1:  # XXX swapped with 0
+        move = move.upper()
+    elif state['player'] == 0:
+        move = move.lower()
[…]

### 2014-08-18 info.py

@@ -1,0 +1,87 @@
+import itertools
+import networkx as nx
+from nose.tools import assert_true, assert_equal
+
+
+def kuhn3112_gametree():
+    """Function to generate KUHN(3, 1, 1, 2) poker game tree."""
+    T = nx.DiGraph()
+    T.add_node('/', player=None)
+    edge_labels = {}
+
+    def _add_labelled_edge(x, y, move, **kwargs):
+        T.add_node(y, **kwargs)
+        T.add_edge(x, y)
+        edge_labels[(x, y)] = move
+
+    proba = "1/6"
+    for perm in itertools.permutations('123', 2):
+        _add_labelled_edge('/', '/.%s' % ''.join(perm), proba, player=0,
+                           proba=eval("1. * %s" % proba))
+        for a in 'CR':
+            _add_labelled_edge('/.%s' % ''.join(perm), '/.%s.%s' % (
+                    ''.join(perm), a), a, player=1)
+            if a == 'C':  # check
+                for b in 'cr':
+                    dst = '/.%s.%s.%s' % (''.join(perm), a, b)
+                    _add_labelled_edge('/.%s.%s' % (''.join(perm), a),
+                                       dst, b, player=2)
+                    if b == "c":
+                        T.add_node(dst, player=2, payoff=cmp(*perm))
+                    else:  # raise
+                        for x in 'FK':
+                            dst = '/.%s.%s.%s.%s' % (''.join(perm), a, b, x)
+                            _add_labelled_edge(
+                                '/.%s.%s.%s' % (''.join(perm), a, b),
+                                dst, x, player=1)
+                            if x == "F":  # fold
+                                T.add_node(dst, player=1, payoff=-1)
+                            else:  # call
+                                T.add_node(dst, player=1,
+                                           payoff=2 * cmp(*perm))
+            else:  # raise
+                for b in "fk":
+                    dst = '/.%s.%s.%s' % (''.join(perm), a, b)
+                    _add_labelled_edge('/.%s.%s' % (''.join(perm), a),
+                                       dst, b, player=2)
+                    if b == "f":  # fold
+                        T.add_node(dst, player=2, payoff=1.)
+                    else:  # call
+                        T.add_node(dst, player=2, payoff=2 * cmp(*perm))
+
+    return T, edge_labels
+
+
+def player_moves(player):
[…]

### 2014-08-18 kuhn.py

@@ -1,21 +1,15 @@
-"""
-References
-----------
-[1] Bernhard von Stengel, "Efficient Computation of Behavior Strategies"
-
-"""
-# Author: DOHMATOB Elvis Dopgima
-
 import re
 import networkx as nx
 import numpy as np
 from nose.tools import assert_equal, assert_true, assert_false
 
+CARD_RANDKINS = {'3': 1, '2': 2, '1': 3}
 
-class Game(object):
-    player_choices = None
 
+class Poker(object):
     def __init__(self):
+        self.player_choices = {0: ['12', '13', '21', '23', '31', '32'],
+                               1: list('CFKR'), 2: list('cfkr')}
         self.tree = nx.DiGraph()
         self.edge_labels = {}
         self.infosets = {}
@@ -28,16 +22,58 @@ class Game(object):
         self.build_strategy_constraints()
         self.build_payoff_matrix()
 
-    def build_tree(self):
-        raise NotImplementedError
-
-    def add_labelled_edge(self, x, choice, **kwargs):
+    def _add_labelled_edge(self, x, y, move, **kwargs):
         """Adds a labelled edge to the tree."""
-        y = ".".join([x, choice])
         self.tree.add_node(y, **kwargs)
         self.tree.add_edge(x, y)
-        self.edge_labels[(x, y)] = choice
-        return y
+        self.edge_labels[(x, y)] = move
+
+    def cmp_cards(self, a, b):
+        return cmp(CARD_RANDKINS[b], CARD_RANDKINS[a])
+
+    def build_tree(self):
+        """Builds the tree (nx.DiGraph object)."""
+        for perm, proba in zip(self.player_choices[0],
+                               [1. / 6] * 6):
+            self._add_labelled_edge('/', '/.%s' % ''.join(perm), proba,
+                                    player=0, proba=eval("1. * %s" % proba))
+            for a in 'CR':
+                self._add_labelled_edge('/.%s' % ''.join(perm), '/.%s.%s' % (
+                        ''.join(perm), a), a, player=1)
+                if a == 'C':  # check
+                    for b in 'cr':
+                        dst = '/.%s.%s.%s' % (''.join(perm), a, b)
+                        self._add_labelled_edge('/.%s.%s' % (''.join(perm), a),
+                                           dst, b, player=2)
+                        if b == "c":
+                            self.tree.add_node(dst, player=2, proba=proba,
+                                               payoff=self.cmp_cards(*perm))
+                        else:  # raise
[…]

### 2014-08-18 last.py

@@ -1,0 +1,118 @@
+import itertools
+import numpy as np
+from nose.tools import assert_equal, assert_true, assert_false
+
+norminal = lambda t: 1 + t % 2
+opponent = lambda p: 1 + p % 2
+move_id = lambda move, p: move.upper() if p == 1 else move.lower()
+singletons = lambda x: itertools.combinations(x, 1)
+whose = lambda m: 1 if m == m.upper() else 2
+
+
+def chance(t):
+    if t == 0:
+        for perm in itertools.product("JQ", "JQ"):
+            yield perm
+
+
+def ok(a, L):
+    return a and a[0] <= L and np.all(a[3] >= .0)
+
+
+def do_call(a, p):
+    a[1] += a[0]
+    a[2][p - 1] += a[0]
+    a[3][p - 1] -= a[0]
+    return a
+
+
+def do_raise(a, p):
+    a[0] *= 2.
+    return do_call(a, p)
+
+
+def copy_a(a):
+    return [a[0], a[1], a[2].copy(), a[3].copy()]
+
+
+def u(a, cmd):
+    if cmd.lower() in ['', 'f']:
+        return a
+    elif cmd[0].lower() == "k":
+        do_call(a, whose(cmd[0]))
+        return u(a, cmd[1:])
+    elif cmd[0].lower() == "r":
+        do_raise(a, whose(cmd[0]))
+        return u(a, cmd[1:])
+    else:
+        assert 0
+
+
+def test_u():
+    a = [1, 0., np.array([0, 0]), np.array([100, 100])]
+    u(a, "rRrRrRf")
+    assert_equal(a[2].sum(), a[1])
+    assert_equal(a[0], 64.)
+    a = [1, 0., np.array([0, 0]), np.array([100, 100])]
+    u(a, "rRrRrRk")
+    assert_equal(a[1], 126 + 64)
+    assert_equal(a[0], 64.)
+
+
+def test_opponent():
+    assert_equal(opponent(1), 2)
+    assert_equal(opponent(2), 1)
+
+
+def alpha1(t, T, a, L, rep=""):
+    if t < T and ok(a, L):
+        p = norminal(t)
+        q = opponent(p)
+        token = move_id("r", q) + move_id("r", p)
+        while True:
+            for end in singletons([move_id('f', q), move_id('k', q)]):
+                end = end[0]
+                x = rep + end
+                a_ = u(copy_a(a), x)
+                if ok(a_, L):
+                    return set().union(
[…]

### 2014-08-18 magic.py

@@ -1,0 +1,34 @@
+def move_id(move, norminal):
+    if norminal == 1:
+        return move.upper()
+    else:
+        return move.lower()
+
+
+def everythx(rnd=0, limit=2, consumed_limit=0, norminal=1, max_rnds=1):
+    assert norminal > 0
+    if rnd >= max_rnds:
+        yield ""
+        return
+    yield move_id("f", norminal)
+    if rnd < max_rnds - 1:
+        for s in everythx(rnd=rnd + 1, limit=limit, norminal=1 + norminal % 2,
+                          max_rnds=max_rnds, consumed_limit=consumed_limit):
+            yield move_id("c", norminal) + ("." + s if s else "")
+    for n in xrange(limit - consumed_limit):
+        start = "K" if norminal == 1 else "k"
+        middle = "rR" if norminal == 1 else "Rr"
+        for end in "fk":
+            aux = start + middle * n + end
+            if not end[-1].lower() == 'f':
+                for s in everythx(rnd=rnd + 1, limit=limit,
+                                  consumed_limit=consumed_limit + n,
+                                  norminal=1 + norminal % 2,
+                                  max_rnds=max_rnds):
+                    yield aux + ("." + s if s else "")
+            else:
+                yield aux
+
+
+for s in everythx(limit=2, max_rnds=2):
+    print s

### 2014-08-18 plane_geo.py

@@ -1,0 +1,82 @@
+from math import sqrt
+import numpy as np
+
+
+def dist_from_plane(unit_normal, intercept, point):
+    """Perpendicular distance of a point from a plane (or line)."""
+    return abs(np.dot(unit_normal, point) + intercept)
+
+
+def projection_onto_plane(unit_normal, intercept, point):
+    """Euclidean projection of a point onto a plane (or line)."""
+    d = dist_from_plane(unit_normal, intercept, point)
+    return point - d * unit_normal
+
+
+def proj(unit_normals, intercepts, point, max_iter=100, verbose=1.,
+         tol=1e-10):
+    """Euclidean projection of a point onto the intersection of
+    the nonnegative orthant and a set of hyperplanes."""
+    x = point
+    error = np.inf
+    for k in xrange(max_iter):
+        old_x = x.copy()
+
+        if verbose:
+            print "Iteration %03i/%03i: x=%s, ||dx||=%5.2e" % (
+                k + 1, max_iter, x, error)
+        if error < tol:
+            if verbose:
+                print "Converged."
+            break
+
+        for unit_normal, intercept in zip(unit_normals, intercepts):
+            x = projection_onto_plane(unit_normal, intercept, x)
+        x = np.maximum(x, 0.)
+        error = sqrt(((x - old_x) ** 2).sum())
+    return x
+
+
+def evil(L, r, z, proj_C=lambda v: np.maximum(v, 0.), L_norm=None,
+         max_iter=100, verbose=1, tol=1e-4):
+    """Projects the point z onto the intersection of the hyperplane "Ex=r" and
+    the convex set C.
+    """
+    from scipy import linalg
+    if L_norm is None:
+        L_norm = linalg.svdvals(L)[0]
+    gamma = 1.99 / L_norm ** 2
+    v = np.zeros(L.shape[0])
+    x = np.zeros(L.shape[1])
+    b = 1
+    for k in xrange(max_iter):
+        old_x = x.copy()
+        x = proj_C(z - L.T.dot(v)) + b
+        v += gamma * (L.dot(x) - r)
+        b *= .5  # we want: \sum_{k}{b_k} < \infty
+        error = sqrt(((x - old_x) ** 2).sum())
+        if verbose:
+            print "\tIteration %03i/%03i: x=%s, error=%5.2e" % (
+                x, k + 1, max_iter, error)
+        if error < tol:
+            if verbose:
[…]

### 2014-08-18 poker.py

@@ -228,10 +228,13 @@ class Poker(object):
         pass
 
     def handle_call(self, p):
-        pass
+        assert self.can_call(p)
+        self.debit(p, self.bet)
 
     def handle_raise(self, p):
-        pass
+        assert self.can_raise(p)
+        self.bet *= 2
+        self.handle_call(p)
 
     def do_flop(self):
         pass

### 2014-08-18 projections.py

@@ -1,0 +1,192 @@
+from math import sqrt
+import numpy as np
+from scipy import linalg
+
+
+def devil(L, r, z, max_iter=100, verbose=0, tol=1e-4):
+    q, n = L.shape
+    l = linalg.svdvals(np.vstack((np.eye(n), L)))[0]
+    sigma = tau = .99 / l
+    assert sigma * tau * l * l < 1.
+    x = np.zeros(n)
+    xbar = x.copy()
+    v = np.zeros(n)
+    zeta = np.zeros(q)
+    for k in xrange(max_iter):
+        old_x = x.copy()
+        old_v = v.copy()
+        old_zeta = zeta.copy()
+
+        v += sigma * (xbar - z)
+        v /= (1. + sigma)
+        zeta += sigma * (L.dot(xbar) - r)
+        x -= tau * (v + L.T.dot(zeta))
+        x = np.maximum(x, 0.)
+        xbar = 2 * x - old_x
+
+        error = .5 * (((x - old_x) ** 2).sum() / tau + (
+                ((v - old_v) ** 2).sum() + (
+                    (zeta - old_zeta) ** 2).sum()) / sigma)
+        if verbose:
+            print "\tIteration: %03i/%03i: error=%g" % (k + 1, max_iter, error)
+
+        if error < tol:
+            if verbose:
+                print "\tConverged after %i iterations." % (k + 1)
+            break
+
+    return x
+
+
+def general_condat(L, grad_F, beta, prox_G, prox_Hstar, norm_L=None,
+                   max_iter=100, verbose=0, tol=1e-4):
+
+    if norm_L is None:
+        norm_L = linalg.svdvals(L)[0]
+    sigma = .99 / norm_L
+    tau = .9 / (sigma * norm_L * norm_L + .5 * beta)
+    assert 1. / tau - sigma * norm_L * norm_L >= beta * .5
+    print norm_L, beta, sigma, tau
+    x = np.zeros(A.shape[1])
+    y = np.zeros(A.shape[0])
+    ybar = y.copy()
+    delta = 2. - .5 * beta / (1. / tau - sigma * norm_L * norm_L)
+    assert 1. <= delta <= 2.
+    rho = .99 * delta
+    for _ in xrange(max_iter):
+        old_x = x.copy()
+        old_y = y.copy()
+
+        xbar = x - tau * (grad_F(x) + A.T.dot(y))
+        xbar = prox_G(xbar, tau)
[…]

### 2014-08-18 pypoker.py

@@ -1,0 +1,279 @@
+#!/usr/bin/env python
+from pokerengine.pokergame import PokerGameServer
+from pokerengine.pokerchips import PokerChips
+from random import choice
+from getopt import getopt, GetoptError
+from sys import argv, exit, stderr
+from string import join
+import gettext
+gettext.install('textpoker', '.')
+
+self_voicing = False
+autoPlay = False
+
+try:
+    from speechd.client import SSIPClient
+    speechd = SSIPClient("textpoker")
+    def info(text):
+        if self_voicing:
+            speechd.speak(text)
+        print text
+except:
+    def info(text):
+        print text
+
+players = 5
+game = None
+mySerial = 0
+
+def serial2name(serial):
+    global mySerial
+    if serial == mySerial:
+        return "you"
+    else:
+        return "Player %d" % serial
+
+def setupGame(argv):
+    """Process command line arguments and setup game"""
+
+    def usage():
+        print >>stderr, "Usage: %s [-a] [-n PLAYERS] [-s]" % argv[0]
+
+    global autoPlay, players, game, mySerial, self_voicing
+    try:
+        opts, args = getopt(argv[1:], "an:s", ["help"])
+    except GetoptError:
+        usage()
+        exit(2)
+    for opt, arg in opts:
+        if opt == "-a":
+            autoPlay = True
+        elif opt == "--help":
+            usage()
+            exit()
+        elif opt == "-n":
+            try:
+                players = int(arg)
+            except:
+                print >>stderr, "%s is not a valid argument for %s" % (arg, opt)
+                usage()
+                exit(3)
+        elif opt == "-s":
+            self_voicing = True
+    game = PokerGameServer("poker.%s.xml", ['/etc/poker-engine'])
+    game.verbose = 0
+    game.setVariant("holdem")
+    game.setBettingStructure("10-15-pot-limit")
+    serials = [n+1 for n in range(players)]
+    if not autoPlay:
+        mySerial = choice(serials)
+    game.registerCallback(pokerEvent)
+    for serial in serials:
+        game.addPlayer(serial)
+        game.payBuyIn(serial, 1500*100)
+        game.sit(serial)
+        if serial == mySerial and not autoPlay:
+            game.autoBlindAnte(serial)
+        else:
+            game.botPlayer(serial)
+
+def pokerEvent(id, type, *args):
+    global game, mySerial
+    if type == "all-in":
+        if args[0] == mySerial:
[…]

### 2014-08-18 rules.py

@@ -1,0 +1,40 @@
+def gen_stage_seqs(limit=2):
+    yield ''
+    yield 'c'
+    for k in ['', 'k']:
+        for n in xrange(limit):
+            for c in ['f', 'k']:
+                yield k + 'r' * n + c
+
+
+def _gen_game_seqs(max_stages, limit=2):
+    if max_stages == 1:
+        for sigma in gen_stage_seqs(limit=limit):
+            yield sigma
+    elif max_stages > 1:
+        for sigma in _gen_game_seqs(max_stages - 1, limit=limit):
+            yield sigma
+            if sigma and sigma[-1] not in ['f', 'c']:
+                for future in gen_stage_seqs(limit=limit):
+                    if future:
+                        yield sigma + "." + future
+
+
+def gen_game_seqs(*args, **kwargs):
+    for seq in _gen_game_seqs(*args, **kwargs):
+        if not (len(seq) > 1 and seq.endswith('c')):
+            yield seq
+
+
+def count(s, l):
+    if s > 1:
+        return 2 * (2 * l * ((2 * l) ** (s - 1) + 1) + 1)
+    else:
+        return 4 * l + 2
+
+s, l = (2, 4)
+seqs = gen_game_seqs(s, limit=l)
+for sigma in seqs:
+    print "'%s'" % sigma
+# assert len(seqs) == len(set(seqs)) == count(s, l)
+print count(s, l)

### 2014-08-18 smug.py

@@ -1,0 +1,62 @@
+import itertools
+import pylab as pl
+import networkx as nx
+
+T = nx.DiGraph()
+edge_labels = {}
+
+
+def is_leaf(T, node):
+    """Checks whether given node is leaf / terminal."""
+    return T.out_degree(node) == 0.
+
+
+def _add_labelled_edge(x, y, **kwargs):
+    move = y.split(".")[-1]
+    T.add_node(y, **kwargs)
+    T.add_edge(x, y)
+    edge_labels[(x, y)] = move
+
+proba = "1/6"
+for z in itertools.permutations('123', 2):
+    _add_labelled_edge('/', '/.%s' % ''.join(z), proba=proba)
+
+pos = nx.graphviz_layout(T, prog='dot')
+
+
+# BFS"
+info = {1: {}, 2: {}}
+source = "/"
+info[1] = {}
+
+for node in T.nodes_iter():
+    if node == "/" or is_leaf(T, node):
+        continue
+    if node[-1] in '123cfkr':
+        player = 1
+    else:
+        player = 2
+    signal = re.match('^/\.(.)', node).group(1)
+    skeleton = project_seq_onto_player(node,
+                                       player_moves(player))
+    moves = sorted([succ[-1] for succ in T.successors(node)])
+    key = signal, tuple(skeleton), tuple(moves)
+    if not key in info[player]:
+        info[player][key] = dict(nodes=[])
+    info[player][key]['nodes'].append(node)
+
+for z in '123':
+    print [node for node in nodes if node.startswith('/.%s' % z)]
+
+# leaf (terminal) nodes
+nx.draw_networkx_nodes(T, pos, nodelist=[n for n in T.nodes(
+            ) if is_leaf(T, n)], node_shape='s')
+
+# decision nodes
+nx.draw_networkx_nodes(T, pos, nodelist=[n for n in T.nodes(
+            ) if not is_leaf(T, n)], node_shape='o')
+
+# labelled edges
+nx.draw_networkx_edges(T, pos, arrows=False)
+nx.draw_networkx_edge_labels(T, pos, edge_labels=edge_labels)
+pl.show()

### 2014-08-18 tex.py

@@ -1,0 +1,7 @@
+from nose.tools import assert_true, assert_equal, assert_false
+
+
+def test_preflop():
+    players = [Player(), Player()]
+    poker = Poker(norminal=1)
+    poker.do_round()

### 2014-08-18 texas.py

@@ -1,0 +1,229 @@
+import random
+import numpy as np
+
+
+class Player(object):
+    def __init__(self):
+        self.card = None  # private (hidden) card
+        self.flop_card = None  # public hard to be made known by dealer
+        self.norminal = False
+
+    def take_card(self, card):
+        """Take "hole" (face-down) card from dealer."""
+        self.card = card
+
+    def see_flop(self, flop_card):
+        """See flop unrevealed by dealer to everybody."""
+        self.flop_card = flop_card
+
+    def show_card(self):
+        """Reveal the hidden (private) card."""
+        return self.card
+
+    def act(self, env):
+        return "flop"
+
+    def new_round(self, norminal=False):
+        self.norminal = norminal
+
+    def can_check(self, env):
+        return env["rnd"] == 1 and self.norminal
+
+
+class Dull(Player):
+    def act(self, env):
+        if self.can_check(env):
+            return "check"
+        else:
+            return "call"
+
+
+class Crazy(Player):
+    def act(self, _):
+        p = random.random()
+        return "call" if p < .6 else ("raise" if p < .8 else "fold")
+
+
+class Poker(object):
+    """Simplified Texas Hold'em Poker as explained in the article:
+    http://www.contrib.andrew.cmu.edu/~qihangl/firstsummerpaper_finaldraft.pdf,
+    page 2.
+
+    """
+
+    def __init__(self, player1, player2, capital=100., n_games=1):
+        self.players = [player1, player2]
+        self.n_games = n_games
+        self.capital = capital  # initial capital of each player
+        self.pot = 0.
+        self.accounts = np.ones(len(self.players)) * capital
+        self.norminal_player = 0
+        self.potted = np.zeros_like(self.accounts)
+        self.winner = None  # who won last game
+        self.net_winner = None  # who walks out the house with net profit
+        self.bet = 1.  # current bet
+        self.rnd = 0  # round #
+        self.cards = list('JJQQ')  # deck
+        random.shuffle(self.cards)
+
+        # deal
+        for player in self.players:
+            player.take_card(self.cards[-1])
+            self.cards = self.cards[:-1]
+        assert len(self.cards) == 2, self.cards
+        self.flop_card = self.cards[-2]
+        self.final_card = self.cards[-1]
+
+    def new_round(self):
+        """Starts a new round of betting."""
+        # everybody puts 1$ into pot
+        self.accounts -= 1.
+        self.potted += 1.
+        self.pot += 2.
+
+        self.rnd += 1
[…]

### 2014-08-18 tree.py

@@ -1,0 +1,13 @@
+from nose.tools import assert_equal
+import re
+
+
+def get_children(key, tree):
+    return dict((k, v) for k, v in tree.iteritems()
+                if re.match('^%s.$' % key, k))
+
+
+def test_get_children():
+    tree = {'': None, 'a': 1, 'a1': 4, 'a2': ['hey', None], 'b': 5}
+    assert_equal(get_children('a', tree), {'a2': ['hey', None], 'a1': 4})
+    assert_equal(get_children('b', tree), {})

### 2014-08-18 warmachine.py

@@ -1,0 +1,212 @@
+from copy import deepcopy
+import re
+import networkx as nx
+import numpy as np
+
+other_player = lambda p: 1 + p % 2
+player = lambda rnd: 1 + rnd % 2
+move_id = lambda move, p: move.upper() if p == 1 else move.lower()
+whose = lambda m: 1 if m == m.upper() else 2
+
+
+def clone(obj):
+    """Quick and dirty technology for cloning an object instance."""
+    c = object.__new__(obj.__class__)
+    c.__dict__ = deepcopy(obj.__dict__)
+    return c
+
+
+class Treasury(object):
+    def __init__(self, capitals, bet_size=1, limit=np.inf):
+        self.limit = limit
+        self.bet_size = bet_size
+        self.pot = 0.
+        self.potted = np.zeros(2)
+        self.accounts = np.array(capitals)
+
+    def do_call(self, p):
+        self.pot += self.bet_size
+        self.potted[p - 1] += self.bet_size
+        self.accounts[p - 1] -= self.bet_size
+        # if np.any(self.accounts < 0.):
+        #     raise RuntimeError("Some players have negative accounts!")
+        assert self.potted.sum() == self.pot
+
+    def do_raise(self, p):
+        self.bet_size *= 2
+        # if self.bet_size > self.limit:
+        #     raise RuntimeError(
+        #         "bet_size exceeded limmit of %g$" % self.limit)
+        self.do_call(p)
+
+    def __dict__(self):
+        return dict((k, getattr(self, k))
+                    for k in ["bet_size", "pot", "potted", "accounts"])
+
+    def __repr__(self):
+        return str(self.__dict__())
+
+    def ok(self, limit):
+        if np.any(self.accounts <= 0.):
+            return False
+        elif self.bet_size > limit:
+            return False
+        else:
+            return True
+
+    def copy(self):
+        t = Treasury(self.accounts.copy(), bet_size=self.bet_size)
+        t.potted = self.potted.copy()
+        t.pot = self.pot
+        return t
+
+
+def g(treasury, cmd):
+    treasury = treasury.copy()
+    if np.any(treasury.accounts <= 0) or treasury.bet_size > treasury.limit:
+        return None
+    elif not cmd or cmd[0].lower() == "f":
+        return treasury
+    elif cmd[0].lower() == "k":
+        treasury.do_call(whose(cmd[0]))
+        return g(treasury, cmd[1:])
+    elif cmd[0].lower() == "r":
[…]

### 2014-10-29 neurobreakfast.tex
added .tex for neurobreakfast

%-----------------------------------------------------
%----- Setup -----------------------------------------
%-----------------------------------------------------
% for normal version
\documentclass[xcolor=dvipsnames]{beamer}
% for trans version
%\documentclass[xcolor=dvipsnames, trans]{beamer}
%\usepackage{pgfpages}
%\pgfpagesuselayout{2 on 1}[a4paper,border shrink=10mm]

%-----------------------------------------------------
%----- Document begins
%-----------------------------------------------------
\usetheme{Warsaw}
\setbeamertemplate{navigation symbols}{}

\usepackage[T1]{fontenc}
%\usepackage[utf-8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}

\usepackage{mathpazo}
\usepackage{graphicx}
\usepackage[labelformat=empty, labelsep=none,
  font=footnotesize]{caption}
\usepackage{sidecap}
\usecolortheme[named=Bittersweet]{structure}
\usepackage{array}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{stmaryrd}

\usepackage{bm}
\setbeamercovered{transparent}

% Shorthand for bold math
\def\B#1{\bm{#1}}
% Matrix transpose
\def\trans{^\mathsf{T}}
% A compact fraction
\def\slantfrac#1#2{\kern.1em^{#1}\kern-.1em/\kern-.1em_{#2}}
% "off" indice
\def\off{\text{off}}
% cholesky decomposition
\def\chol{\text{chol}}

\title[NeuroBreakfast - \today\hspace{\stretch{1}}
  (\insertframenumber{}/\inserttotalframenumber{})]{Solving two-person zero-sum sequential games
via efficient computaion of Nash equilibria: proof-of-concept on Kuhn's 3-card Poker}
\author{DOHMATOB Elvis \inst{1,2}}
\institute{
  \inst{1}Parietal Team, INRIA\\\inst{2}Universit\'e Paris-Sud}

\date{} \selectlanguage{english}
\begin{document}

\begin{frame}
\maketitle
\end{frame}

%\logo{\includegraphics[scale=0.1]{img/logo_parietal.png}}
\begin{frame}
  \frametitle{Problem}
  Given a \textcolor{orange}{sequential two-person zero-sum game} (e.g Texas Hold'em Poker), construct an \textcolor{orange}{optimal player}.
  %% Approximate the population covariance matrix $\Sigma$ from $n$ samples.
  %% \begin{itemize}
  %% \item $\B{S}$ is the $p \times p$ sample covariance
  %%   matrix.\\
  %%   $\B{S} = \frac{1}{n}\sum^n_{i=1}x_ix_i\trans$. $\mathbb{E}[S] = \Sigma$.
  %% \item Largest (resp. smallest) eigenvalue of $S$ is biased upwards
  %%   (resp. downwards)
  %% \item $\Rightarrow$ Shrinkage: pushing up (resp. pulling down) the
  %%   largest (resp. smallest) eigenvalue. \textcolor{gray}{(Stein
  %%     1976)}.
  %% \end{itemize}

  %% \vfill

  %% Ledoit-Wolf problem:\\
  %% \begin{itemize}
  %% \item $\underset{\hat{\B{\Sigma}}}{\min} \,
  %%   \mathbb{E}\left\{\|\hat{\B{\Sigma}}(\{x_i\}^n_{i=1}) - \B{\Sigma}\|^2_F\right\}$ with $\|\B{A}\|_F = \sqrt{\text{Tr}(\B{A}\B{A}\trans)/p}$
  %% \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Two-person zero sum Sequential games}
  \uncover<1->{
  \begin{itemize}[<+->]
      \item There are 3 players: \textcolor{blue}{nature (player 0)}, \textcolor{red}{Alice (player 1)}, and \textcolor{green}{Bob (player 2)}.}
    \item Players take turns in making moves
    \item Set of moves of any two distinct players don't
      overlap (i.e \textcolor{red}{$A_p \cap A_q = \emptyset$ if $p \ne q$})
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Minimax NE problem for general sequential game}
  \begin{equation}
    \underset{x \in Q_1}{maximize}\text{ }\underset{y \in \mathbb{R}_+^m, Fy=f}{minimize}\text{ }y^TAx,
  \end{equation}

\uncover<2>{
  where:
  \begin{equation}
    \left .
    \begin{split}
      Q_1 &:= \{x \in \mathbb{R}_+^n\text{ }|\text{ }Ex=e\} \text{ is \textcolor{blue}{Alice's complex}, and}\\
      Q_2 &:= \{y \in \mathbb{R}_+^m\text{ }|\text{ }Fy=f\} \text{ is \textcolor{red}{Bob's complex}.}
    \end{split}
    \right\}
  \end{equation}
}
\end{frame}

\begin{frame}
  \frametitle{Two-person zero sum Sequential games}
    The game tree T (from Alice's perspective) is defined as follows.
    T has a set V(T) of nodes (aka vertices) and a set E(T) of edges.
\end{frame}

\begin{frame}
  \frametitle{Non-Linear Ledoit-Wolf: Why? How?}

  \begin{itemize}
  \item ($p/n$ large) or ($\Sigma$ eigenvalues close to one another)
    $\Rightarrow$ linear shrinkage OK.\\($p/n$ small) or ($\Sigma$
    eigenvalues dispersed) $\Rightarrow$ non-linear shrinkage better.
  \item Mar\v{c}enko-Pastur equation: relationship between $\B{S}$ and
    $\B{\Sigma}$ eigenvalues under large-dimensional asymptotics.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Non-Linear Ledoit-Wolf: deeper into the "how?"}

  \begin{itemize}
  \item $H_n$ empirical d.f. of sample ($\B{S}_n$) eigenvalues $\B{\tau}_n$.\\
    $H_n(\B{\tau}) \equiv
    \frac{1}{p}\sum^p_{i=1}\mathbb{1}_{[\tau_i,+\infty[}(\tau)$
  \item $F_n$ e.d.f. of population ($\B{\Sigma}_n$) eigenvalues
    $\B{\lambda}_n$.\\$\B{Y}_n = \B{X}_n\B{\Sigma}^{1/2}_n$, $\B{X}_n
    \sim \mathcal{N}(\B{0},\text{Id})$
  \item $F_n$ (resp. $H_n$) converges almost surely to $F$ (resp. $H$).
  \item Stieltjes transform of a non-decreasing function $G$:
     $\forall z \in \mathbb{C}^+, m_G(z) \equiv
     \int^{+\infty}_{-\infty}\frac{1}{u - z}dG(u)$
   \item Mar\v{c}enko-Pastur equation: $\forall z \in \mathbb{C}^+,
     m_F(z) = \int^{+\infty}_{-\infty}\frac{1}{\tau[1-\frac{p}{n}-\frac{p}{n}zm_F(z)] - z}dH(\tau)$
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Non-Linear Ledoit-Wolf: Implementation\ldots}

  \begin{equation*}
    \begin{split}
      \textcolor{red}{Q_{n,p}}: & [0, \infty[^p \rightarrow [0,\infty[^p \\
              & \B{t} \equiv (t_1,\ldots,t_p)\trans
              \mapsto Q_{n,p}(\B{t}) \equiv
              (q^1_{n,p}(t),\ldots,q^p_{n,p}(t))\trans
    \end{split}
  \end{equation*}

  \vfill
  \hrule{}
  \vfill

  $\textcolor{blue}{\hat{\B{\tau}}_n} = \underset{\B{t} \in [0, \infty[^p}{\text{argmin}} 
      \frac{1}{p} \sum^p_{i=1}[\textcolor{red}{q^i_{n,p}(}\B{t}\textcolor{red}{)} - \lambda_{n,i}]^2$

  \vfill
  \hrule{}
  \vfill

  $\textcolor{PineGreen}{\overset{\smile}{m}^{\hat{\B{\tau}}_n}_{n,p}(}\lambda_i\textcolor{PineGreen}{)} \simeq \frac{n-p}{p\lambda_i} - \frac{n}{p}\frac{1}{\textcolor{blue}{\hat{\B{\tau}}_{n,i}}\lambda_i}$

  \vfill
  \hrule{}
  \vfill

  $\textcolor{purple}{\hat{d}_i^*} = \frac{\lambda_i}{|1 - \frac{p}{n} - \frac{p}{n}|^2\textcolor{PineGreen}{\overset{\smile}{m}^{\hat{\B{\tau}}_n}_{n,p}(}\lambda_i\textcolor{PineGreen}{)}}$; {\scriptsize Covariance:} $S_n^*\B{U}_n\textcolor{purple}{\hat{\B{D}}^*_n}\B{U}_n\trans${\scriptsize , with }$\B{S}_n=\B{U}_n\B{D}_n\B{U}_n\trans$

\end{frame}

\begin{frame}
  \frametitle{About the $Q_{n,p}$ function}

  \begin{equation*}
    \begin{split}
      Q_{n,p}: & [0, \infty[^p \rightarrow [0,\infty[^p \\
              & \B{t} \equiv (t_1,\ldots,t_p)\trans
              \mapsto Q_{n,p}(\B{t}) \equiv
              (\textcolor{red}{q^1_{n,p}(}t\textcolor{red}{)},\ldots,\textcolor{red}{q^p_{n,p}(}t\textcolor{red}{)})\trans
    \end{split}
  \end{equation*}

  \vfill
  \hrule{}
  \vfill

  $\forall i = 1, \ldots, p \quad \textcolor{red}{q^i_{n,p}(}t\textcolor{red}{)} \equiv
  p\int_{(i-1)/p}^{i/p}\textcolor{blue}{(F^{\B{t}}_{n,p})^{-1}(}u\textcolor{blue}{)}du$

  \vfill
  \hrule{}
  \vfill

  $\textcolor{blue}{(F^{\B{t}}_{n,p})^{-1}(}u\textcolor{blue}{)} \equiv \sup\{x \in \mathbb{R}: \textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \leq u\}$

  \vfill
  \hrule{}
  \vfill

  $\textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \equiv \max \left\{1 - \frac{n}{p}, \frac{1}{p}\sum^p_{i=1}\mathbb{1}_{\{t_i = 0\}}\right\}$ if $x = 0$, $\textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \equiv \underset{\eta \rightarrow 0^+}{\lim}\frac{1}{\pi}\int^{+\infty}_{-\infty}\text{Im}\left[\textcolor{purple}{m^{\B{t}}_{n,p}(}\zeta + i\,\eta\textcolor{purple}{)}\right]d\zeta$ otherwise

  \vfill
  \hrule{}
  \vfill

  $m \equiv \textcolor{purple}{m^{\B{t}}_{n,p}(}z\textcolor{purple}{)}$ sol. in $\left\{m \in \mathbb{C}: -\frac{n-p}{nz} + \frac{p}{n}\right\}$ of $\textcolor{purple}{m} = \frac{1}{p}\sum^p_{i=1}\frac{1}{t_i(1 - \frac{p}{n} - \frac{p}{n}z\textcolor{purple}{m}) - z}$

\end{frame}

\end{document}

### 2014-10-30 neurobreakfast.tex
more tex

@@
 \usepackage{stmaryrd}
-
+\usepackage{graphicx}
 \usepackage{bm}
@@
   (\insertframenumber{}/\inserttotalframenumber{})]{Solving two-person zero-sum sequential games
-via efficient computaion of Nash equilibria: proof-of-concept on Kuhn's 3-card Poker}
+via efficient computation of Nash equilibria: proof-of-concept on Kuhn's 3-card Poker}
 \author{DOHMATOB Elvis \inst{1,2}}
@@
     \item Players take turns in making moves
-    \item Set of moves of any two distinct players don't
+    \item Sets of moves of any two distinct players don't
       overlap (i.e \textcolor{red}{$A_p \cap A_q = \emptyset$ if $p \ne q$})
@@
 \begin{frame}
-  \frametitle{Minimax NE problem for general sequential game}
+\frametitle{Strategy profiles, simplexes and complexes}
+\begin{definition}
+  \begin{itemize}[<+->]
+    \item The \textcolor{blue}{$n$-\textit{simplex}}, denoted $\Delta_n$, is the subset of $\mathbb{R}^{n+1}$ defined by
       \begin{equation}
-    \underset{x \in Q_1}{maximize}\text{ }\underset{y \in \mathbb{R}_+^m, Fy=f}{minimize}\text{ }y^TAx,
+        \Delta_n := \left\{x \in \mathbb{R}^{n+1}\text{ }|\text{ } x_i \ge 0\text{ } \forall i, \text{ and } \sum_{i=1}^{n+1}{x_i} = 1\right\}
+      \end{equation}
+    \item Each kink $\delta_i := (0, ..., 0,1,0, ...,0)$ of $\Delta_n$ represents a \textit{\textcolor{blue}{pure-strategy}}.
+      Any non-kink point $x$ of $\Delta_n$ represents a
+      \textit{\textcolor{blue}{mixed-strategy}}. Thus $\Delta_n$ is simply the \textit{convex hall} of $(n+1)$-dimensional pure strategies $\delta_i$.
+    \item A \textit{\textcolor{blue}{complex}} is an abstract \textit{\textcolor{blue}{polyhedron}} whose kinks are themselves simplexes. Points on
+      a complex correspond to \textit{\textcolor{blue}{behavioural strategies}}.
+  \end{itemize}
+\end{definition}
+\end{frame}
+
+\begin{frame}
+\frametitle{Simplexes and complexes (examples of)}
+\begin{figure}
+  \includegraphics[width=3cm]{simplex.png}
+  \includegraphics[width=3cm]{7-simplex.png}
+  \includegraphics[width=3cm]{10-simplex.png}
+  \caption{\textbf{Left}: 2-simplex \textbf{Middle}: 7-simplex \textbf{Right}: 10-simplex}
+\end{figure}
+\end{frame}
+
+\begin{frame}
+  \frametitle{NE minimax and best-response in sequential-games}
+Thanks to the sequence-form representation, we have:
+\begin{itemize}[<+->]
+\item NE problem for Alice and Bob is the the \textit{\textcolor{blue}{saddle-point problem}}
+  \begin{equation}
+    \underset{x \in Q_1}{maximize}\text{ }\underset{y \in Q_2}{minimize}\text{ }y^TAx,
+    \label{eq:minimax_stengel}
   \end{equation}
@@
      \begin{split}
-      Q_1 &:= \{x \in \mathbb{R}_+^n\text{ }|\text{ }Ex=e\} \text{ is \textcolor{blue}{Alice's complex}, and}\\
+       Q_1 &:= \{x \in \mathbb{R}_+^n\text{ }|\text{ }Ex=e\} \text{ is \textcolor{blue}{Alice's complex, and}}\\
        Q_2 &:= \{y \in \mathbb{R}_+^m\text{ }|\text{ }Fy=f\} \text{ is \textcolor{red}{Bob's complex}.}
@@
    \end{equation}
+   A saddle-point $(x^*, y^*)$ corresponds to a NE for the game.
+   \item Given a fixed behavioural strategy $y_0 \in Q_2$ for Bob, a \textit{\textcolor{blue}{best-response}} behavioural strategy $x_0$ for Alice
+     \footnote{Of course, there is an analogous concept for Bob.}
+    is a solution to the LCP
+    \begin{equation}
+      \underset{x\in Q_1}{maximize}\text{ }{y_0^TAx}
+    \end{equation}
 }
+  \end{itemize}
 \end{frame}

### 2014-10-30 simple.py

@@ -402,7 +402,7 @@ class Game(object):
                     row[i] = -1.
                     row[where] = 1.
                     E.append(row)
-            # right handside
+            # right handside, e
             e = np.zeros(len(self.infosets[player]) + 1)
             e[0] = 1.
             self.constraints[player] = np.array(E), e
@@ -419,7 +419,7 @@ class Game(object):
         Use tricks in equation (38) of "Smoothing Techniques for Computing Nash
         Equilibria of Sequential Games" http://repository.cmu.edu/cgi
         /viewcontent.cgi?article=2442&context=compsci to compute the payoff
-        matrix as a block diagonal matrix whose blocs are sums of Kronecker
+        matrix as a block diagonal matrix whose blocks are sums of Kronecker
         products of sparse matrices. This can be done by appropriately
         permuting the list of sequences of each (non-chance) player.
         """
@@ -655,6 +655,7 @@ class NashPlayer(Player):
     def __init__(self, name, player, game):
         super(NashPlayer, self).__init__(name, player, game)
         self.game = game
+        self.sequences = self.game.sequences[self.player]
         self.compute_optimal_rplan()
         self.location = "(/,0)"
 
@@ -669,7 +670,6 @@ class NashPlayer(Player):
         A = self.game.payoff_matrix
         x, y, _ = compute_ne(A, E, F, e, f, tol=0, max_iter=100)
         self.rplan = np.array([x, y][self.player - 1])
-        self.sequences = self.game.sequences[self.player]
 
     def choice(self, choices):
         """Makes a choice at give node, according to our optimal realization

### 2014-10-30 neurobreakfast.tex
more tex

@@
 \frametitle{Simplexes and complexes (examples of)}
-\begin{figure}
-  \includegraphics[width=3cm]{simplex.png}
-  \includegraphics[width=3cm]{7-simplex.png}
-  \includegraphics[width=3cm]{10-simplex.png}
-  \caption{\textbf{Left}: 2-simplex \textbf{Middle}: 7-simplex \textbf{Right}: 10-simplex}
-\end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=3cm]{simplex.png}
+%%   \includegraphics[width=3cm]{7-simplex.png}
+%%   \includegraphics[width=3cm]{10-simplex.png}
+%%   \caption{\textbf{Left}: 2-simplex \textbf{Middle}: 7-simplex \textbf{Right}: 10-simplex}
+%% \end{figure}
 \end{frame}
@@
 
-  \uncover<2>{
     where:
@@
     \end{equation}
-}
   \end{itemize}
@@
   \frametitle{Two-person zero sum Sequential games}
-    The game tree T (from Alice's perspective) is defined as follows.
-    T has a set V(T) of nodes (aka vertices) and a set E(T) of edges.
+  \begin{itemize}[<+->]
+    \item The game tree $T$ (from Alice's perspective) is defined as follows.
+    $T$ has a set $V(T)$ of nodes (aka vertices) and a set $E(T)$ of edges.
+    \item Each node $v$ belongs to a single player, $p(v)$, called "\textcolor{blue}{the player to act
+    at $v$}"; $p(v) := 3$ if $v$ is a leaf node. At node $v$, the player $p(v)$ has a set
+    $C(v) \subset A_p$ of possible moves.
+    \item For each player $p \in \{0, 1, 2\}$,
+      the set of all nodes at which $p$ acts is called the nodes of $p$,
+    denoted $V_p(T)$.% Thus $v(0)$, $v(1)$, and $v(2)$ form a partition of $V(T)$.
+  \item There are two kinds of nodes: the \textcolor{blue}{leaf nodes} $L(T)$, at which the game must
+    end and \textcolor{blue}{decision nodes} $D(T)$, at which the player to act must make a move.
+    \textcolor{orange}{For example in Poker,
+    a leaf node is reached at countdown, or when a player folds, or when the
+    player runs out of money.}
+    \item  There is a special node \textcolor{blue}{root}(T) defined by $root(T) := (/, p_0)$,
+
+    \item In accordance with the rules of the game, every other node
+      $y \in V(T)-\{root(T)\}$ is of the form $y = v.(c, p(v))$
+
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Sequences and payoff matrix}
+  \begin{itemize}[<+->]
+    \item Let $S_p$ be the sequences of moves for player $p$.
+Then any $\sigma \in S_p$ is either the empty sequence $\empty$ set or can be written as $\sigma_{h_p} c$ where $h_p$ is an information set of $p$ and $c$ is a choice at $h_p$.
+      \item Precisely,
+        \begin{equation}
+          S_p = \{\emptyset\} \cup \{\sigma_{h}c\text{ }|\text{ }h \in H_{p}, c \in C_h\}
+        \end{equation}
+        \item The payoff matrix $A = (a_{\sigma,\tau})$ by
+          \begin{equation}
+            a_{\sigma,\tau} := \sum_{\text{leaf }t:\text{ } \sigma_1(t) = \sigma, \sigma_2(t) = \tau}\beta_0(\sigma_0(t))a(t)
+            \end{equation}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{NE computation Kuhn's Poker}
+  \[   E = \left( \begin{array}{ccccccccccccc}
+1&0&0&0&0&0&0&0&0&0&0&0&0\\-1&0&0&0&0&0&0&0&0&1&0&0&1\\-1&1&0&0&1&0&0&0&0&0&0&0&0\\-1&0&0&0&0&1&0&0&1&0&0&0&0\\0&-1&1&1&0&0&0&0&0&0&0&0&0\\0&0&0&0&0&-1&1&1&0&0&0&0&0\\0&0&0&0&0&0&0&0&0&-1&1&1&0
+\end{array} \right),\]
+  $e = (1, 0, 0, 0, 0, 0, 0)$
+
+  %% \begin{figure}
+  %%   \includegraphics[width=7cm]{Kuhn3112_NE.pdf}
+  %%   \includegraphics[width=5cm]{Kuhn3112_payoff.pdf}
+  %%   \caption{\textbf{Left}: 2-simplex \textbf{Middle}: 7-simplex \textbf{Right}: 10-simplex}
+  %% \end{figure}
 \end{frame}

### 2014-10-30 simple.py

@@ -903,16 +903,24 @@ if __name__ == "__main__":
         print "Nash Equilibrium:"
         print "x* = ", x
         print "y* =", y
-        plt.figure()
-        plt.semilogx(values)
+        plt.figure(figsize=(13.5, 10))
+        plt.semilogx(values, linewidth=4)
         value = values[-1]
         plt.axhline(value, linestyle="--",
-                   label="value of the game: %5.2e" % value)
-        plt.xlabel("k")
-        plt.ylabel("value of game after k iterations")
-        plt.legend(loc="best")
-        plt.title("%s: Sequence-form NE computation" % (
-                game.__class__.__name__))
+                   label="value of the game: %5.2e" % value, linewidth=4,
+                    color="k")
+        plt.xlabel("k", fontsize=25)
+        plt.ylabel("value of game after k iterations", fontsize=25)
+        plt.legend(loc="best", prop=dict(size=25))
+        # plt.title("%s: Sequence-form NE computation" % (
+        #         game.__class__.__name__))
+        plt.tick_params(axis='both', which='major', labelsize=20)
+        plt.savefig("%s_NE.pdf" % game.__class__.__name__)
+
+        tmpfig = plt.figure(figsize=(13.5, 10))
+        plt.matshow(game.payoff_matrix, fignum=tmpfig.number)
+        plt.axis("off")
+        plt.savefig("%s_payoff.pdf" % game.__class__.__name__)
 
         plt.figure()
         game.draw()

### 2014-10-30 neurobreakfast.tex
new files

@@
 
+\begin{frame}
+\frametitle{Some necessary history ...}
+\begin{itemize}[<+->]
+  \item Blaise Pascal, and other giants ($\sim 1623$)...
+    \item Zemelo 1913 (subgame perfect equilibrium, backward induction)
+    \item Von Neumann and Oskar Morgenstern (Cooperative Games, \textit{Theory of Games and Economic Behavior, 1944}),
+    \item John F. Nash (Non-cooperative games, Nash Equilibrium)
+    \item L. Shapley (concept of value for bargaining games, etc.),
+    \item Tucker, Kuhn, and co. (equivalence between LCP and problem of computation of Nash Equilibria;
+      subgame perfect equilibrium again).
+\end{itemize}
+\end{frame}
+
 %\logo{\includegraphics[scale=0.1]{img/logo_parietal.png}}
@@
   Given a \textcolor{orange}{sequential two-person zero-sum game} (e.g Texas Hold'em Poker), construct an \textcolor{orange}{optimal player}.
+
   %% Approximate the population covariance matrix $\Sigma$ from $n$ samples.
@@
     \begin{frame}
+  \frametitle{Two-person zero sum Sequential games}
+  \begin{itemize}[<+->]
+    \item The game tree $T$ (from Alice's perspective) is defined as follows.
+    $T$ has a set $V(T)$ of nodes (aka vertices) and a set $E(T)$ of edges.
+    \item Each node $v$ belongs to a single player, $p(v)$, called "\textcolor{blue}{the player to act
+    at $v$}"; $p(v) := 3$ if $v$ is a leaf node. At node $v$, the player $p(v)$ has a set
+    $C(v) \subset A_p$ of possible moves.
+    \item For each player $p \in \{0, 1, 2\}$,
+      the set of all nodes at which $p$ acts is called the nodes of $p$,
+    denoted $V_p(T)$.% Thus $v(0)$, $v(1)$, and $v(2)$ form a partition of $V(T)$.
+  \item There are two kinds of nodes: the \textcolor{blue}{leaf nodes} $L(T)$, at which the game must
+    end and \textcolor{blue}{decision nodes} $D(T)$, at which the player to act must make a move.
+    \textcolor{orange}{For example in Poker,
+    a leaf node is reached at countdown, or when a player folds, or when the
+    player runs out of money.}
+    \item  There is a special node \textcolor{blue}{root}(T) defined by $root(T) := (/, p_0)$,
+
+    \item In accordance with the rules of the game, every other node
+      $y \in V(T)-\{root(T)\}$ is of the form $y = v.(c, p(v))$
+
+  \end{itemize}
+\end{frame}
+
+%% \begin{frame}
+%%   \frametitle{Game tree (T) for Kuhn's 3-card Poker}
+%%       \begin{figure}
+%%         \includegraphics[width=12cm]{Kuhn3112_gt.png}
+%%       \end{figure}
+%% \end{frame}
+
+\begin{frame}
 \frametitle{Strategy profiles, simplexes and complexes}
@@
     \item A \textit{\textcolor{blue}{complex}} is an abstract \textit{\textcolor{blue}{polyhedron}} whose kinks are themselves simplexes. Points on
-      a complex correspond to \textit{\textcolor{blue}{behavioural strategies}}.
+      a complex correspond to \textit{\textcolor{blue}{realization plans}}.
   \end{itemize}
@@
 \frametitle{Simplexes and complexes (examples of)}
+\begin{figure}
+  \includegraphics[width=3cm]{simplex.png}
+  \includegraphics[width=3cm]{7-simplex.png}
+  \includegraphics[width=3cm]{10-simplex.png}
+  \caption{\textbf{Left}: 2-simplex \textbf{Middle}: 7-simplex \textbf{Right}: 10-simplex}
+\end{figure}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Sequences and payoff matrix}
+  \begin{definition}
+    Given a node $t \in V(T)$, and a player $p \in \{0, 1, 2\}$, let $\sigma_p(t)$ be the sequence of player $p$'s moves along the path from the root node \ to $t$.
+\end{definition}
+
+  \begin{itemize}[<+->]
+    \item Let $S_p$ be the sequences of moves for player $p$.
+Then any $\sigma \in S_p$ is either the empty sequence $\empty$ set or can be written as $\sigma_{h_p} c$ where $h_p$ is an information set of $p$ and $c$ is a choice at $h_p$.
+    \item Precisely,
+      \begin{equation}
+        S_p = \{\emptyset\} \cup \{\sigma_{h}c\text{ }|\text{ }h \in H_{p}, c \in C_h\}
+        \end{equation}
+\item The payoff matrix $A = (a_{\sigma,\tau})$ by
+  \begin{equation}
+    a_{\sigma,\tau} := \sum_{\text{leaf }t:\text{ } \sigma_1(t) = \sigma, \sigma_2(t) = \tau}\beta_0(\sigma_0(t))a(t)
+  \end{equation}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Example of sequence-form representation}
+  \begin{itemize}[<+->]
+    \item \textcolor{blue}{$S_1 = [[],[(\{'chance': ('A',), 'choices': ('(B,2)', '(F,3)'), 'sigma': ''\}, '(B,2)')],
+ [(\{'chance': ('A',), 'choices': ('(B,2)', '(F,3)'), 'sigma': ''\}, '(F,3)')],
+ [(\{'chance': ('K',), 'choices': ('(B,2)', '(F,3)'), 'sigma': ''\}, '(B,2)')],
+ [(\{'chance': ('K',), 'choices': ('(B,2)', '(F,3)'), 'sigma': ''\}, '(F,3)')]]$}
+\item \textcolor{green}{$I_1 = \{(('A',), '', ('(B,2)', '(F,3)')): ['(/,0).(w,1)', '(/,0).(x,1)'],
+  (('K',), '', ('(B,2)', '(F,3)')): ['(/,0).(u,1)', '(/,0).(v,1)']\}$}
+\item \textcolor{red}{$E = \left( \begin{array}{ccccc}
+    1&0&0&0&0\\-1&1&1&0&0\\-1&0&0&1&1
+    \end{array} \right)$,
+$e=(1, 0, 0)$,
+$A = \left( \begin{array}{ccccc}
+0&0&0&0&0\\0&0&0&1&0\\0&0&0&0&0\\0&-1&0&0&0\\0&0&0&0&0
+\end{array}\right)$
+}
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Kuhn's Poker sequence-form representation}
+  \[   E = \left( \begin{array}{ccccccccccccc}
+1&0&0&0&0&0&0&0&0&0&0&0&0\\-1&0&0&0&0&0&0&0&0&1&0&0&1\\-1&1&0&0&1&0&0&0&0&0&0&0&0\\-1&0&0&0&0&1&0&0&1&0&0&0&0\\0&-1&1&1&0&0&0&0&0&0&0&0&0\\0&0&0&0&0&-1&1&1&0&0&0&0&0\\0&0&0&0&0&0&0&0&0&-1&1&1&0
+\end{array} \right),\]
+  $e = (1, 0, 0, 0, 0, 0, 0)$
+
   %% \begin{figure}
-%%   \includegraphics[width=3cm]{simplex.png}
-%%   \includegraphics[width=3cm]{7-simplex.png}
-%%   \includegraphics[width=3cm]{10-simplex.png}
+  %%   \includegraphics[width=7cm]{Kuhn3112_NE.pdf}
+  %%   \includegraphics[width=5cm]{Kuhn3112_payoff.pdf}
   %%   \caption{\textbf{Left}: 2-simplex \textbf{Middle}: 7-simplex \textbf{Right}: 10-simplex}
@@
 \begin{frame}
-  \frametitle{Two-person zero sum Sequential games}
-  \begin{itemize}[<+->]
-    \item The game tree $T$ (from Alice's perspective) is defined as follows.
-    $T$ has a set $V(T)$ of nodes (aka vertices) and a set $E(T)$ of edges.
-    \item Each node $v$ belongs to a single player, $p(v)$, called "\textcolor{blue}{the player to act
-    at $v$}"; $p(v) := 3$ if $v$ is a leaf node. At node $v$, the player $p(v)$ has a set
-    $C(v) \subset A_p$ of possible moves.
-    \item For each player $p \in \{0, 1, 2\}$,
-      the set of all nodes at which $p$ acts is called the nodes of $p$,
-    denoted $V_p(T)$.% Thus $v(0)$, $v(1)$, and $v(2)$ form a partition of $V(T)$.
-  \item There are two kinds of nodes: the \textcolor{blue}{leaf nodes} $L(T)$, at which the game must
-    end and \textcolor{blue}{decision nodes} $D(T)$, at which the player to act must make a move.
-    \textcolor{orange}{For example in Poker,
-    a leaf node is reached at countdown, or when a player folds, or when the
-    player runs out of money.}
-    \item  There is a special node \textcolor{blue}{root}(T) defined by $root(T) := (/, p_0)$,
-
-    \item In accordance with the rules of the game, every other node
-      $y \in V(T)-\{root(T)\}$ is of the form $y = v.(c, p(v))$
-
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Sequences and payoff matrix}
-  \begin{itemize}[<+->]
-    \item Let $S_p$ be the sequences of moves for player $p$.
-Then any $\sigma \in S_p$ is either the empty sequence $\empty$ set or can be written as $\sigma_{h_p} c$ where $h_p$ is an information set of $p$ and $c$ is a choice at $h_p$.
-      \item Precisely,
-        \begin{equation}
-          S_p = \{\emptyset\} \cup \{\sigma_{h}c\text{ }|\text{ }h \in H_{p}, c \in C_h\}
-        \end{equation}
-        \item The payoff matrix $A = (a_{\sigma,\tau})$ by
-          \begin{equation}
-            a_{\sigma,\tau} := \sum_{\text{leaf }t:\text{ } \sigma_1(t) = \sigma, \sigma_2(t) = \tau}\beta_0(\sigma_0(t))a(t)
-            \end{equation}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
   \frametitle{NE computation Kuhn's Poker}
@@
 \begin{frame}
-  \frametitle{Non-Linear Ledoit-Wolf: Why? How?}
+  \frametitle{Practical considerations}
+  In practice, the \textcolor{orange}{payoff matrix $A$ will be very huge} (\textcolor{green}{for example $18 x 10^9$ rows by $18 x 10^9$ columns for Texas Hold'em!}) but \textcolor{blue}{sparse, with a nice block structure}
 
-  \begin{itemize}
-  \item ($p/n$ large) or ($\Sigma$ eigenvalues close to one another)
-    $\Rightarrow$ linear shrinkage OK.\\($p/n$ small) or ($\Sigma$
-    eigenvalues dispersed) $\Rightarrow$ non-linear shrinkage better.
-  \item Mar\v{c}enko-Pastur equation: relationship between $\B{S}$ and
-    $\B{\Sigma}$ eigenvalues under large-dimensional asymptotics.
-  \end{itemize}
+\begin{equation}
+  A = \begin{bmatrix}A_1\text{ }0 \text{ }0\\ 0\text{ }A_2\text{ }0 \\0 \text{ } 0\text{ }A_3\end{bmatrix}
+\end{equation}
+
+where (for some ``small'' (worst case $\sim 100$ by $100$) sparse matrices $F_1$, ..., $B_2$, ..., $S$, $W$):
+\begin{equation}
+  \left .
+  \begin{split}
+    A_1 := F_1 \otimes B_1\\
+    A_2 := F_2 \otimes B_2\\
+    A_3 := F_3 \otimes B_3 + S \otimes W,
+  \end{split}
+  \right\}
+\end{equation}
 \end{frame}
 
-\begin{frame}
-  \frametitle{Non-Linear Ledoit-Wolf: deeper into the "how?"}
+%% \begin{frame}
+%%   \frametitle{Non-Linear Ledoit-Wolf: Why? How?}
 
-  \begin{itemize}
-  \item $H_n$ empirical d.f. of sample ($\B{S}_n$) eigenvalues $\B{\tau}_n$.\\
-    $H_n(\B{\tau}) \equiv
-    \frac{1}{p}\sum^p_{i=1}\mathbb{1}_{[\tau_i,+\infty[}(\tau)$
-  \item $F_n$ e.d.f. of population ($\B{\Sigma}_n$) eigenvalues
-    $\B{\lambda}_n$.\\$\B{Y}_n = \B{X}_n\B{\Sigma}^{1/2}_n$, $\B{X}_n
-    \sim \mathcal{N}(\B{0},\text{Id})$
-  \item $F_n$ (resp. $H_n$) converges almost surely to $F$ (resp. $H$).
-  \item Stieltjes transform of a non-decreasing function $G$:
-     $\forall z \in \mathbb{C}^+, m_G(z) \equiv
-     \int^{+\infty}_{-\infty}\frac{1}{u - z}dG(u)$
-   \item Mar\v{c}enko-Pastur equation: $\forall z \in \mathbb{C}^+,
-     m_F(z) = \int^{+\infty}_{-\infty}\frac{1}{\tau[1-\frac{p}{n}-\frac{p}{n}zm_F(z)] - z}dH(\tau)$
-  \end{itemize}
-\end{frame}
+%%   \begin{itemize}
+%%   \item ($p/n$ large) or ($\Sigma$ eigenvalues close to one another)
+%%     $\Rightarrow$ linear shrinkage OK.\\($p/n$ small) or ($\Sigma$
+%%     eigenvalues dispersed) $\Rightarrow$ non-linear shrinkage better.
+%%   \item Mar\v{c}enko-Pastur equation: relationship between $\B{S}$ and
+%%     $\B{\Sigma}$ eigenvalues under large-dimensional asymptotics.
+%%   \end{itemize}
+%% \end{frame}
 
-\begin{frame}
-  \frametitle{Non-Linear Ledoit-Wolf: Implementation\ldots}
+%% \begin{frame}
+%%   \frametitle{Non-Linear Ledoit-Wolf: deeper into the "how?"}
 
-  \begin{equation*}
-    \begin{split}
-      \textcolor{red}{Q_{n,p}}: & [0, \infty[^p \rightarrow [0,\infty[^p \\
-              & \B{t} \equiv (t_1,\ldots,t_p)\trans
-              \mapsto Q_{n,p}(\B{t}) \equiv
-              (q^1_{n,p}(t),\ldots,q^p_{n,p}(t))\trans
-    \end{split}
-  \end{equation*}
+%%   \begin{itemize}
+%%   \item $H_n$ empirical d.f. of sample ($\B{S}_n$) eigenvalues $\B{\tau}_n$.\\
+%%     $H_n(\B{\tau}) \equiv
+%%     \frac{1}{p}\sum^p_{i=1}\mathbb{1}_{[\tau_i,+\infty[}(\tau)$
+%%   \item $F_n$ e.d.f. of population ($\B{\Sigma}_n$) eigenvalues
+%%     $\B{\lambda}_n$.\\$\B{Y}_n = \B{X}_n\B{\Sigma}^{1/2}_n$, $\B{X}_n
+%%     \sim \mathcal{N}(\B{0},\text{Id})$
+%%   \item $F_n$ (resp. $H_n$) converges almost surely to $F$ (resp. $H$).
+%%   \item Stieltjes transform of a non-decreasing function $G$:
+%%      $\forall z \in \mathbb{C}^+, m_G(z) \equiv
+%%      \int^{+\infty}_{-\infty}\frac{1}{u - z}dG(u)$
+%%    \item Mar\v{c}enko-Pastur equation: $\forall z \in \mathbb{C}^+,
+%%      m_F(z) = \int^{+\infty}_{-\infty}\frac{1}{\tau[1-\frac{p}{n}-\frac{p}{n}zm_F(z)] - z}dH(\tau)$
+%%   \end{itemize}
+%% \end{frame}
 
-  \vfill
-  \hrule{}
-  \vfill
+%% \begin{frame}
+%%   \frametitle{Non-Linear Ledoit-Wolf: Implementation\ldots}
 
-  $\textcolor{blue}{\hat{\B{\tau}}_n} = \underset{\B{t} \in [0, \infty[^p}{\text{argmin}} 
-      \frac{1}{p} \sum^p_{i=1}[\textcolor{red}{q^i_{n,p}(}\B{t}\textcolor{red}{)} - \lambda_{n,i}]^2$
+%%   \begin{equation*}
+%%     \begin{split}
+%%       \textcolor{red}{Q_{n,p}}: & [0, \infty[^p \rightarrow [0,\infty[^p \\
+%%               & \B{t} \equiv (t_1,\ldots,t_p)\trans
+%%               \mapsto Q_{n,p}(\B{t}) \equiv
+%%               (q^1_{n,p}(t),\ldots,q^p_{n,p}(t))\trans
+%%     \end{split}
+%%   \end{equation*}
 
-  \vfill
-  \hrule{}
-  \vfill
+%%   \vfill
+%%   \hrule{}
+%%   \vfill
 
-  $\textcolor{PineGreen}{\overset{\smile}{m}^{\hat{\B{\tau}}_n}_{n,p}(}\lambda_i\textcolor{PineGreen}{)} \simeq \frac{n-p}{p\lambda_i} - \frac{n}{p}\frac{1}{\textcolor{blue}{\hat{\B{\tau}}_{n,i}}\lambda_i}$
+%%   $\textcolor{blue}{\hat{\B{\tau}}_n} = \underset{\B{t} \in [0, \infty[^p}{\text{argmin}} 
+%%       \frac{1}{p} \sum^p_{i=1}[\textcolor{red}{q^i_{n,p}(}\B{t}\textcolor{red}{)} - \lambda_{n,i}]^2$
 
-  \vfill
-  \hrule{}
-  \vfill
+%%   \vfill
+%%   \hrule{}
+%%   \vfill
 
-  $\textcolor{purple}{\hat{d}_i^*} = \frac{\lambda_i}{|1 - \frac{p}{n} - \frac{p}{n}|^2\textcolor{PineGreen}{\overset{\smile}{m}^{\hat{\B{\tau}}_n}_{n,p}(}\lambda_i\textcolor{PineGreen}{)}}$; {\scriptsize Covariance:} $S_n^*\B{U}_n\textcolor{purple}{\hat{\B{D}}^*_n}\B{U}_n\trans${\scriptsize , with }$\B{S}_n=\B{U}_n\B{D}_n\B{U}_n\trans$
+%%   $\textcolor{PineGreen}{\overset{\smile}{m}^{\hat{\B{\tau}}_n}_{n,p}(}\lambda_i\textcolor{PineGreen}{)} \simeq \frac{n-p}{p\lambda_i} - \frac{n}{p}\frac{1}{\textcolor{blue}{\hat{\B{\tau}}_{n,i}}\lambda_i}$
 
-\end{frame}
+%%   \vfill
+%%   \hrule{}
+%%   \vfill
 
-\begin{frame}
-  \frametitle{About the $Q_{n,p}$ function}
+%%   $\textcolor{purple}{\hat{d}_i^*} = \frac{\lambda_i}{|1 - \frac{p}{n} - \frac{p}{n}|^2\textcolor{PineGreen}{\overset{\smile}{m}^{\hat{\B{\tau}}_n}_{n,p}(}\lambda_i\textcolor{PineGreen}{)}}$; {\scriptsize Covariance:} $S_n^*\B{U}_n\textcolor{purple}{\hat{\B{D}}^*_n}\B{U}_n\trans${\scriptsize , with }$\B{S}_n=\B{U}_n\B{D}_n\B{U}_n\trans$
 
-  \begin{equation*}
-    \begin{split}
-      Q_{n,p}: & [0, \infty[^p \rightarrow [0,\infty[^p \\
-              & \B{t} \equiv (t_1,\ldots,t_p)\trans
-              \mapsto Q_{n,p}(\B{t}) \equiv
-              (\textcolor{red}{q^1_{n,p}(}t\textcolor{red}{)},\ldots,\textcolor{red}{q^p_{n,p}(}t\textcolor{red}{)})\trans
-    \end{split}
-  \end{equation*}
+%% \end{frame}
 
-  \vfill
-  \hrule{}
-  \vfill
+%% \begin{frame}
+%%   \frametitle{About the $Q_{n,p}$ function}
 
-  $\forall i = 1, \ldots, p \quad \textcolor{red}{q^i_{n,p}(}t\textcolor{red}{)} \equiv
-  p\int_{(i-1)/p}^{i/p}\textcolor{blue}{(F^{\B{t}}_{n,p})^{-1}(}u\textcolor{blue}{)}du$
+%%   \begin{equation*}
+%%     \begin{split}
+%%       Q_{n,p}: & [0, \infty[^p \rightarrow [0,\infty[^p \\
+%%               & \B{t} \equiv (t_1,\ldots,t_p)\trans
+%%               \mapsto Q_{n,p}(\B{t}) \equiv
+%%               (\textcolor{red}{q^1_{n,p}(}t\textcolor{red}{)},\ldots,\textcolor{red}{q^p_{n,p}(}t\textcolor{red}{)})\trans
+%%     \end{split}
+%%   \end{equation*}
 
-  \vfill
-  \hrule{}
-  \vfill
+%%   \vfill
+%%   \hrule{}
+%%   \vfill
 
-  $\textcolor{blue}{(F^{\B{t}}_{n,p})^{-1}(}u\textcolor{blue}{)} \equiv \sup\{x \in \mathbb{R}: \textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \leq u\}$
+%%   $\forall i = 1, \ldots, p \quad \textcolor{red}{q^i_{n,p}(}t\textcolor{red}{)} \equiv
+%%   p\int_{(i-1)/p}^{i/p}\textcolor{blue}{(F^{\B{t}}_{n,p})^{-1}(}u\textcolor{blue}{)}du$
 
-  \vfill
-  \hrule{}
-  \vfill
+%%   \vfill
+%%   \hrule{}
+%%   \vfill
 
-  $\textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \equiv \max \left\{1 - \frac{n}{p}, \frac{1}{p}\sum^p_{i=1}\mathbb{1}_{\{t_i = 0\}}\right\}$ if $x = 0$, $\textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \equiv \underset{\eta \rightarrow 0^+}{\lim}\frac{1}{\pi}\int^{+\infty}_{-\infty}\text{Im}\left[\textcolor{purple}{m^{\B{t}}_{n,p}(}\zeta + i\,\eta\textcolor{purple}{)}\right]d\zeta$ otherwise
+%%   $\textcolor{blue}{(F^{\B{t}}_{n,p})^{-1}(}u\textcolor{blue}{)} \equiv \sup\{x \in \mathbb{R}: \textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \leq u\}$
 
-  \vfill
-  \hrule{}
-  \vfill
+%%   \vfill
+%%   \hrule{}
+%%   \vfill
 
-  $m \equiv \textcolor{purple}{m^{\B{t}}_{n,p}(}z\textcolor{purple}{)}$ sol.
+%%   $\textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \equiv \max \left\{1 - \frac{n}{p}, \frac{1}{p}\sum^p_{i=1}\mathbb{1}_{\{t_i = 0\}}\right\}$ if $x = 0$, $\textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \equiv \underset{\eta \rightarrow 0^+}{\lim}\frac{1}{\pi}\int^{+\infty}_{-\infty}\text{Im}\left[\textcolor{purple}{m^{\B{t}}_{n,p}(}\zeta + i\,\eta\textcolor{purple}{)}\right]d\zeta$ otherwise
+
+%%   \vfill
+%%   \hrule{}
+%%   \vfill
+
+%%   $m \equiv \textcolor{purple}{m^{\B{t}}_{n,p}(}z\textcolor{purple}{)}$ sol.
 in $\left\{m \in \mathbb{C}: -\frac{n-p}{nz} + \frac{p}{n}\right\}$ of $\textcolor{purple}{m} = \frac{1}{p}\sum^p_{i=1}\frac{1}{t_i(1 - \frac{p}{n} - \frac{p}{n}z\textcolor{purple}{m}) - z}$
 
-\end{frame}
+%% \end{frame}
 

### 2014-11-29 onepage.tex
dualized NE problem for sequential games :)

\documentclass[a4paper,9pt,journal]{IEEEtran}
\usepackage{graphicx} \usepackage[cmex10]{amsmath}
\usepackage{amssymb} \usepackage{fancybox} \usepackage{alltt}
\usepackage{soul} \usepackage{color} \usepackage{verbatim}
\usepackage{xcolor} \usepackage{colortbl,hhline}
\usepackage[ruled,vlined]{algorithm2e} \usepackage{framed}
\usepackage{amsthm} \usepackage{fancyref}
\usepackage{amsmath,amsfonts,amssymb, amsthm} \usepackage{textcomp}

\newtheorem{remark}{Remark}

\def \lb {{\langle}} \def \rb {{\rangle}}
\newcommand{\fro}[1]{\|#1\|_2}
\newcommand{\theHalgorithm}{\arabic{algorithm}}

\newcommand{\argmin}{\mathop{\mathrm{argmin}}}

\usepackage{hyperref}

\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}

\newcommand{\prox}{\textrm{pr ox} } \newcommand{\grad}{\textrm{grad} }
\newcommand{\dive}{\textrm{div} }

\pagenumbering{gobble}

\begin{document}
\onecolumn
\title{A fast and simple primal-dual algorithm for computing Nash equilibria and best response strategies
  in two-person zero-sum sequential games with imcomplete information}

\author{\IEEEauthorblockN{DOHMATOB Elvis}}

\maketitle

\begin{abstract}
% LESS THAN 200 WORDS !!!!!
% 
% While medical imaging typically provides massive amounts of
% data, the extraction of relevant information in a given
% applicative context remains a difficult challenge.
% XXX : don't call it SPM but just "predictive regions or predictive
% maps"
In this manuscript we present a simple primal-dual algorithm for computing Nash equilibria and best reponse strategies in  sequential games with
imcomplete information and perfect recall. The proposed algorithm derives from the primal-dual scheme of A. Chambolle and T. Pock, applied to the
equilibrium and best response strategy problems for the sequence form representation of the game. We use a dualization trick to render all
proximity operators computable in closed-form.

%% In this manuscript, we consider the problem of computing a best response against an opponent's realization plan in two-person sequential games.
%% The proposed algorithm for solving the corresponding contrained convex-optimization problem, derives from the primal-dual scheme of A. Chambolle and T. Pock.
%% Our algorithm is simple: all resolvent operators can be effectively computed in closed-form, using only elementary algebraic operations.
%%  and is orders of magnitude more efficient than state-of-the-art algorithms like those based on Linear Programming, Interior-Point methods,
%% and more recently, the Nesterov Excessive Gap Technique.
% By way of example, we conclude by exhibiting results on Texas Hold'em Poker.
\end{abstract}

\begin{IEEEkeywords}
  game theory; Nash equilibrium; two-person sequential game; imcomplete information; perfect recall; sequence-form representaion; best response strategy;
  convex-optimization; dualization; primal-dual algorithms
\end{IEEEkeywords}

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
Give positive integers $m$ and $n$, $\mathbb{R}^{n}$ denotes the $n$-dimensional real vector space, and $\mathbb{R}^{m \times n}$
the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
$\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_j \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegati
ve orthant}.
For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
$(x)_+$ denotes its point-wise maximum with 0. Note that $(x)_+ \in \mathbb{R}^n_+$.
For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$, denoted $\|K\|$, is defined by
$\|K\| := \underset{x \ne 0}{max}\text{ }\frac{\|Kx\|}{\|x\|}$. Equivalently, $\|K\|$ is the largest \textit{singular value} of $K$, i.e the largest
\textit{eigen-value} of $K^TK$. Given a convex subset $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
$i_C(x) = 0$ if $x \in C$ and $i_C(x) = +\infty$ otherwise. Finally, given a \textit{proper} convex function (i.e a convex function which takes a finite
value at least a one point) $f : \mathbb{R}^n \rightarrow [0, +\infty]$, and a positive real number $\tau$, the \textit{proximal operator} of $f$ of rank $\tau$,
denoted $\text{prox}_{\tau f}$ is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) solution of the problem
\begin{equation}
  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
\end{equation}

%% We will be needing the following notation: %%  The reader should lookup any standard textbook
%% %% (for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions.
%% Viz,
%% \begin{itemize}
%% \item $\mathbb{R}^n$: $n$-dimensional real vector space;
%% \item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$n$ real matrices;
%% \item $0_{m,n}$: $m$-by-$n$ matrix of zeros;
%% \item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
%% \item $\mathbb{R}^n_+$: \quad $\{x \in \mathbb{R}^n|x = (x)_+\}$, the $n$-dimensional nonnegative orthant 
%% \item $i_C$: \quad indicator function of a convex set $C$;
%% % \item $\Pi_C$: \quad euclidean projector onto a convex set $C$;
%% \item $\|K\|_2$: \quad spectral norm of a matrix $K$
%% % \item $F^*$: the convex conjugate of a convex function $F$.
%% %% \item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
%% %% \item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
%% \end{itemize}

\subsection{Statement of the problem}
We are interested in the problem of computing a Nash equilibrium for a two-person zero-sum sequential game with imcomplete information
and perfect recall (e.g Texas Hold'em Poker, etc.). In the \textit{sequence-form representation} of the game, the problem has the following saddle-point formulation
\begin{equation}
  \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{y^TAx}
  \label{eq:opt_pb}
\end{equation}

where $Q_j := \{z \in \mathbb{R}_+^{n_j}|E_jz=e_j\}$, for $j \in \{1, 2\}$. As usual, the ``minimize-maximize'' notation in problem
\eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
\begin{equation}
  {y^*}^TAx \le y^TAx \le y^TAx^*, \forall (x, y) \in Q_1 \times Q_2
\end{equation}
Such pairs correspond to the Nash equilibria of the game.

We recall that $E_j$ is a $p_j$-by-$n_j$ matrix whose
entries are $-1$, $0$, or $+1$, and $e_j := (1, 0, 0, ..., 0)$ is a vector of length $p_j$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
encode linear constraints on our (resp. the opponent's)  ``admissible'' realization $x$ (resp. $y$). $A$ is the payoff matrix, of size $n_2 \times n_1$.

\begin{remark}
  In practice, the matrices $A$, $E_1$, and $E_2$ are large but very sparse too.
%% : $A$ will be sparse because a concrete sequential game will
%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
%% combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
%% $E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
%% zig-zag between only a limited number of the player's information sets so that a move at an information set will
%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
This sparsity should be thoroughly exploited by a solver for problem \eqref{eq:opt_pb}.
\end{remark}

%% In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}.
%% We elaborate our proposed algorithm in section \ref{sec:algo}.

%% \section{Related work}
%% \label{sec:related_work}

%% Pending...

\section{The proposed algorithm}
We preprose to solve problem \eqref{eq:opt_pb} using the primal-dual scheme of A. Chambolle and T. Pock.
Though this scheme has recently gained considerable popularity in the signal processing community, to the best of our knowledge,
this is the first time it is being applied to game theoretic problems.

%% \label{sec:algo}
%% In this section we present the algorithm which is the purpose of this paper, namely an algorithm
%% for solving \eqref{eq:opt_pb}. Our algorithm (Alg.\ref{Tab:algo}) is a use-case of
%% the generic primal-dual algorithm of A. Chambolle and T. Pock, namely Algorithm 1 of \cite{chambolle2010}.

Now, observe that
\begin{eqnarray*}
  i_{Q_j}(z) = i_{\mathbb{R}^{n_j}_+}(z) + \underset{w \in \mathbb{R}^{n_j}}{max}\text{}{w^T(E_jz - e_j)}, \forall z \in \mathbb{R}^{n_j},
\end{eqnarray*}
and so problem \eqref{eq:opt_pb} can be re-written as

\begin{equation}
  \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{p_1}}{minimize}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{p_2}}{maximize}
           {\begin{bmatrix}y\\v\end{bmatrix}^TK\begin{bmatrix}x\\u\end{bmatrix} + G(y, v) - F(x, u)}
  \label{eq:my_opt_pb}
\end{equation}

where:
\begin{equation}
  \left .
  \begin{split}
    K :=
    \left[
      \begin{array}{c|c}
        A & E_1^T \\ \hline
        E_2 & 0_{p_2, p_1}
      \end{array}
      \right] \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)} \\
    %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)}\\
      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{\mathbb{R}^{n_2}_+}(y) - v^Te_1\\
      F: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{\mathbb{R}^{n_1}_+}(x) - u^Te_2
  \end{split}
  \right\}
\end{equation}

It is clear that $G$ and $F$ are proper convex lower semi-continuous and a straightforward computation reveals that their proximal operators are given by
\begin{equation}
  \left .
  \begin{split}
    (1 + \tau \partial G)^{-1}: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{p_1}, (y, v) \mapsto ((y)_+, v + \tau e_1)\\
    (1 + \sigma \partial F)^{-1}: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{p_2}, (x, u) \mapsto ((x)_+, u + \sigma e_2)
  \end{split}
  \right\}
\end{equation}

%% \begin{algorithm}[htb]
%%   \caption{Primal-dual algorithm for computing best response against opponent's fixed realization plan $y_0$}
%%   \textbf{Given} Tolerance $\epsilon > 0$.\\
%%   \textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
%%   $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
%%   \textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
%%   \Repeat{
%%     $\frac{\|x^{(k+1)} - x^{(k)}\|^2_2}{2\tau} + \frac{\|\zeta^{(k+1)} - \zeta^{(k)}\|^2_2}{2\sigma} < \epsilon$}{
%%     \begin{eqnarray*}
%%       \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
%%       x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
%%       \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
%%       k &\leftarrow& k + 1
%%     \end{eqnarray*}
%%   } \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
%%   \label{Tab:algo}
%% \end{algorithm}

%% \subsection{Convergence analysis of the algorithm}
%% Pending...

%% \begin{remark}
%% The derivation above reveals that in equation \eqref{eq:opt_pb} above, if the constraint ``$x \ge 0$'' is replaced by
%% a constraint ``$x \in C$'' (thus obtaining a new problem) where $C$ is a convex set
%% %% onto which euclidean projections
%% %% can be easily computed (for example, a probability simplex)
%% , then we simply need to replace the operator ``$(.)_+$''
%% with ``$\Pi_C$'' in the equations to obtain a corresponding algorithm. Of course, this is because $i_C^* = \Pi_C$.
%% \end{remark}

%% \medskip \noindent
%% \textbf{Acknowledgments:}
%% Pending...

% ==========
% = biblio =
% ==========
% {\small
\bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv.bib,agt.bib}
\end{document}

%
%

### 2014-11-29 sequential_games.py

@@ -271,12 +271,12 @@ if __name__ == "__main__":
     """
 
     ### Load the game tree ###################################################
-    import scipy.io
-    game = scipy.io.loadmat('game.mat')
-    A, P, Q, a, b = [game[key] for key in "APQab"]
-    A = A.T
-    a = a.ravel()
-    b = b.ravel()
+    # import scipy.io
+    # game = scipy.io.loadmat('game.mat')
+    # A, P, Q, a, b = [game[key] for key in "APQab"]
+    # A = A.T
+    # a = a.ravel()
+    # b = b.ravel()
     A = np.zeros((5, 3))
     A[2:4, 1:] = [[1, -1], [-2, 4]]
     A[-1, 0] = 1

### 2014-11-29 onepage.tex
ehn

@@
 % maps"
-In this manuscript we present a simple primal-dual algorithm for computing Nash equilibria and best reponse strategies in  sequential games with
+In this manuscript, we present a simple primal-dual algorithm for computing Nash equilibria and best reponse strategies in  sequential games with
 imcomplete information and perfect recall. The proposed algorithm derives from the primal-dual scheme of A. Chambolle and T. Pock, applied to the
-equilibrium and best response strategy problems for the sequence form representation of the game. We use a dualization trick to render all
-proximity operators computable in closed-form.
+equilibrium and best response strategy problems in the sequence-form representation of the game. Our technique is to use a dualization
+trick and unconstrain the saddle-point problem. All proximal operators in the resulting primal-dual algorithm are simple,
+only involving nonnegative thresholding and translations.
+The convergence and convergence rate of our algorithm derive explicitly from the general Chambolle-Pock primal-dual scheme.
 
@@
 \begin{IEEEkeywords}
-  game theory; Nash equilibrium; two-person sequential game; imcomplete information; perfect recall; sequence-form representaion; best response strategy;
-  convex-optimization; dualization; primal-dual algorithms
+  game theory; Nash equilibrium; two-person zero-sum game; sequential game; imcomplete information; perfect recall; sequence-form representaion;
+  best response strategy; convex-optimization; dualization; proximal operator; primal-dual algorithms
 \end{IEEEkeywords}
@@
 %\label{sec:intro}
-\subsection{Notation and Terminology}
-Give positive integers $m$ and $n$, $\mathbb{R}^{n}$ denotes the $n$-dimensional real vector space, and $\mathbb{R}^{m \times n}$
-the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
-$\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_j \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegati
-ve orthant}.
-For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
-$(x)_+$ denotes its point-wise maximum with 0. Note that $(x)_+ \in \mathbb{R}^n_+$.
-For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$, denoted $\|K\|$, is defined by
-$\|K\| := \underset{x \ne 0}{max}\text{ }\frac{\|Kx\|}{\|x\|}$. Equivalently, $\|K\|$ is the largest \textit{singular value} of $K$, i.e the largest
-\textit{eigen-value} of $K^TK$. Given a convex subset $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
-$i_C(x) = 0$ if $x \in C$ and $i_C(x) = +\infty$ otherwise. Finally, given a \textit{proper} convex function (i.e a convex function which takes a finite
-value at least a one point) $f : \mathbb{R}^n \rightarrow [0, +\infty]$, and a positive real number $\tau$, the \textit{proximal operator} of $f$ of rank $\tau$,
-denoted $\text{prox}_{\tau f}$ is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) solution of the problem
-\begin{equation}
-  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
-\end{equation}
 
@@
 \begin{equation}
-  \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{y^TAx}
+  \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
   \label{eq:opt_pb}
@@
 
-where $Q_j := \{z \in \mathbb{R}_+^{n_j}|E_jz=e_j\}$, for $j \in \{1, 2\}$. As usual, the ``minimize-maximize'' notation in problem
+where $Q_j := \{z \in \mathbb{R}^{n_j}|z \ge 0, E_jz=e_j\}$, for $j \in \{1, 2\}$. As usual, the ``minimize-maximize'' notation in problem
 \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
@@
 entries are $-1$, $0$, or $+1$, and $e_j := (1, 0, 0, ..., 0)$ is a vector of length $p_j$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
-encode linear constraints on our (resp. the opponent's)  ``admissible'' realization $x$ (resp. $y$). $A$ is the payoff matrix, of size $n_2 \times n_1$.
+encode linear constraints on our (resp. the opponent's)  ``admissible'' realization $x$ (resp. $y$). $A$ is the payoff matrix, of size $n_1 \times n_2$.
 
@@
 Though this scheme has recently gained considerable popularity in the signal processing community, to the best of our knowledge,
-this is the first time it is being applied to game theoretic problems.
+this is the first time it is being applied to compute Nash equilibria.
+
+We first introduce some fundamental notations, and then proceed to derive the algorithm. The convergence and convergence rate
+of our algorithm derive explicitly from the general Chambolle-Pock primal-dual scheme.
+
+\subsection{Notation and Terminology}
+Give positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
+the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
+$\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_j \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegative orthant}.
+For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
+$(x)_+$ denotes its point-wise maximum with 0. Note that $(x)_+ \in \mathbb{R}^n_+$.
+For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$, denoted $\|K\|$, is defined by
+\footnote{Equivalently, $\|K\|$ is the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$.}
+$\|K\| := \underset{x \ne 0}{max}\text{ }\frac{\|Kx\|}{\|x\|}$.
+
+Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
+$i_C(x) = 0$ if $x \in C$ and $i_C(x) = +\infty$ otherwise. Note that $i_{C \cap D} = i_C + i_D$. Finally, given a \textit{proper convex
+function} (i.e a convex function which takes a finite
+value at least a one point) $f : \mathbb{R}^n \rightarrow [0, +\infty]$, and a positive real number $\tau$, the \textit{proximal operator} of $f$ of rank $\tau$,
+denoted $\text{prox}_{\tau f}$ is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) solution of the problem
+\begin{equation}
+  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
+\end{equation}
 
@@
 
-Now, observe that
-\begin{eqnarray*}
-  i_{Q_j}(z) = i_{\mathbb{R}^{n_j}_+}(z) + \underset{w \in \mathbb{R}^{n_j}}{max}\text{}{w^T(E_jz - e_j)}, \forall z \in \mathbb{R}^{n_j},
-\end{eqnarray*}
+\subsection{Derivation of the algorithm}
+Observe that $i_{Q_j}(z) = i_{\mathbb{R}^{n_j}_+}(z) + \underset{w \in \mathbb{R}^{n_j}}{max}\text{}{w^T(E_jz - e_j)}, \forall z \in \mathbb{R}^{n_j}$,
 and so problem \eqref{eq:opt_pb} can be re-written as
@@
   \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{p_1}}{minimize}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{p_2}}{maximize}
-           {\begin{bmatrix}y\\v\end{bmatrix}^TK\begin{bmatrix}x\\u\end{bmatrix} + G(y, v) - F(x, u)}
+           {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - F(x, u)}
   \label{eq:my_opt_pb}
@@
       \end{array}
-      \right] \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)} \\
+      \right] \in \mathbb{R}^{(n_1 + p_2) \times (n_2 + p_1)} \\
     %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)}\\

### 2014-11-30 onepage.tex
ehn
code and paper.tex are in phase

@@
 \begin{document}
-\onecolumn
-\title{A fast and simple primal-dual algorithm for computing Nash equilibria and best response strategies
-  in two-person zero-sum sequential games with imcomplete information}
+%\onecolumn
+\title{A fast and simple primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum games}
 
@@
 $\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_j \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegative orthant}.
+
 For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
@@
 Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
-$i_C(x) = 0$ if $x \in C$ and $i_C(x) = +\infty$ otherwise. Note that $i_{C \cap D} = i_C + i_D$. Finally, given a \textit{proper convex
-function} (i.e a convex function which takes a finite
-value at least a one point) $f : \mathbb{R}^n \rightarrow [0, +\infty]$, and a positive real number $\tau$, the \textit{proximal operator} of $f$ of rank $\tau$,
+$i_C(x) = 0$ if $x \in C$ and $i_C(x) = +\infty$ otherwise. Note that $i_{C \cap D} = i_C + i_D$. Finally, given a \textit{proper convex lower semi-continous
+function} (\textit{p.c.l.s.c} for short) $f : \mathbb{R}^n \rightarrow [0, +\infty]$, and a positive real number $\tau$, the \textit{proximal operator} of $f$ of rank $\tau$,
 denoted $\text{prox}_{\tau f}$ is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) solution of the problem
@@
 \subsection{Derivation of the algorithm}
-Observe that $i_{Q_j}(z) = i_{\mathbb{R}^{n_j}_+}(z) + \underset{w \in \mathbb{R}^{n_j}}{max}\text{}{w^T(E_jz - e_j)}, \forall z \in \mathbb{R}^{n_j}$,
-and so problem \eqref{eq:opt_pb} can be re-written as
+Observe that $\forall (x, y) \in \mathbb{R}^{n_1} \times \mathbb{R}^{n_2}$, we have
+\begin{equation}
+  \left .
+  \begin{split}
+    -i_{Q_1}(x) &= -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)}\\
+  i_{Q_2}(y) &= i_{\mathbb{R}^{n_2}_+}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}
+  \end{split}
+  \right\}
+\end{equation}
+and so problem \eqref{eq:opt_pb} can be re-written in the unconstrained form
 
@@
 
-where:
+where $v \in \mathbb{R}^{p_1}$ and $u \in \mathbb{R}^{p_2}$ are auxiliary dual variables and 
 \begin{equation}
@@
       \begin{array}{c|c}
-        A & E_1^T \\ \hline
+        A & -E_1^T \\ \hline
         E_2 & 0_{p_2, p_1}
@@
     %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)}\\
-      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{\mathbb{R}^{n_2}_+}(y) - v^Te_1\\
-      F: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{\mathbb{R}^{n_1}_+}(x) - u^Te_2
+      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tv\\
+      F: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tu
   \end{split}
@@
 
-It is clear that $G$ and $F$ are proper convex lower semi-continuous and a straightforward computation reveals that their proximal operators are given by
+It is clear that $G$ and $F$ are \textit{p.c.l.s.c} and a straightforward computation reveals that their proximal operators are given by
 \begin{equation}
@@
   \begin{split}
-    (1 + \tau \partial G)^{-1}: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{p_1}, (y, v) \mapsto ((y)_+, v + \tau e_1)\\
-    (1 + \sigma \partial F)^{-1}: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{p_2}, (x, u) \mapsto ((x)_+, u + \sigma e_2)
+    \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{p_1}\\
+    (y, v) &\mapsto ((y)_+, v - \tau e_1)\\
   \end{split}
@@
 
-%% \begin{algorithm}[htb]
-%%   \caption{Primal-dual algorithm for computing best response against opponent's fixed realization plan $y_0$}
-%%   \textbf{Given} Tolerance $\epsilon > 0$.\\
-%%   \textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
-%%   $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
-%%   \textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
-%%   \Repeat{
-%%     $\frac{\|x^{(k+1)} - x^{(k)}\|^2_2}{2\tau} + \frac{\|\zeta^{(k+1)} - \zeta^{(k)}\|^2_2}{2\sigma} < \epsilon$}{
-%%     \begin{eqnarray*}
-%%       \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
-%%       x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
-%%       \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
-%%       k &\leftarrow& k + 1
-%%     \end{eqnarray*}
-%%   } \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
-%%   \label{Tab:algo}
-%% \end{algorithm}
+and
+\begin{equation}
+  \left .
+  \begin{split}
+    \text{prox}_{\sigma F}: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{p_2}\\
+    (x, u) &\mapsto ((x)_+, u - \sigma e_2)
+  \end{split}
+  \right\}
+\end{equation}
+
+Putting everything together, we obtain Algorithm \ref{Tab:algo}.
+
+\begin{algorithm}[htb]
+  \caption{Primal-dual algorithm for computing a Nash equilibrium of a two-person zero-sum game}
+  \textbf{initialize}
+  $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{p_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{p_2}$; 
+  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$ (for example take $\tau = \sigma = \frac{.99}{\|K\|}$); $k = 0$.\\
+  \Repeat{Convergence}{
+    \begin{eqnarray*}
+      x^{(k+1)} &\leftarrow& \left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)_+\\
+      u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
+      y^{(k+1)} &\leftarrow& \left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)_+\\
+      v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
+      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
+      \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
+      k &\leftarrow& k + 1
+    \end{eqnarray*}
+  } \Return $x^{(k)}$, $y^{(k)}$
+  \label{Tab:algo}
+\end{algorithm}
 

### 2014-11-30 sequential_games.py

@@ -310,6 +310,8 @@ if __name__ == "__main__":
     print "Nash Equilibrium:"
     print "x* = ", x
     print "y* =", y
+    print "Px^* - a = %s" % (P.dot(x) - a)
+    print "Qy^* - b = %s" % (Q.dot(y) - b)
 
     pl.figure()
     pl.plot(values, 's-')

### 2014-12-01 onepage.tex
cosmetics
better .tex + figures

@@
 \begin{document}
-%\onecolumn
+\onecolumn
 \title{A fast and simple primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum games}
@@
 where $Q_j := \{z \in \mathbb{R}^{n_j}|z \ge 0, E_jz=e_j\}$, for $j \in \{1, 2\}$. As usual, the ``minimize-maximize'' notation in problem
-\eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
+\eqref{eq:opt_pb} means that a pair $(\hat{x}, \hat{y}) \in Q_1 \times Q_2$ is a solution iff
 \begin{equation}
-  {y^*}^TAx \le y^TAx \le y^TAx^*, \forall (x, y) \in Q_1 \times Q_2
+  x^TA\hat{y} \le x^TAy \le {\hat{x}}^TAy, \forall (x, y) \in Q_1 \times Q_2
 \end{equation}
-Such pairs correspond to the Nash equilibria of the game.
+Such pairs $(\hat{x}, \hat{y})$ correspond to the Nash equilibria of the game, and ${\hat{x}}^TA\hat{y}$ is the \textit{value}\footnote{This value is the same for every equilibrium pair $(\hat{x}, \hat{y})$.} of the game.
 
@@
 encode linear constraints on our (resp. the opponent's)  ``admissible'' realization $x$ (resp. $y$). $A$ is the payoff matrix, of size $n_1 \times n_2$.
+
+For example, the pair $(\hat{x}, \hat{y})$ given by\\
+$\hat{x} = (1, .478, .522, .174, .826)$ and
+$\hat{y} = (1, 1/2, 1/2)$ is a Nash equilibrium for the sequence-form game given by\\
+$A = \left(\begin{array}{ccc}
+0 & 0 & 0\\
+0 & 0 & 0\\
+0 & 1 & -1\\
+0 & -2 & 4\\
+1 & 0 & 0
+\end{array}\right)$, $E_1 = \left(\begin{array}{ccccc}
+  1 & 0 & 0 & 0 & 0\\
+  -1 & 1 & 1 & 0 & 0\\
+  -1 & 0 & 0 & 1 & 1
+\end{array}\right)$,
+$e_1 = (1, 0, 0)$, $E_2 = \left(\begin{array}{ccc}
+  1 & 0 & 0\\
+  -1 & 1 & 1
+\end{array}\right)$, and $e_2 = (1, 0)$.
 
@@
   \caption{Primal-dual algorithm for computing a Nash equilibrium of a two-person zero-sum game}
+  \textbf{require} the specification of a game $(A, E_1, E_2, e_1, e_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
+  $E_1 \in \mathbb{R}^{p_1 \times n_1}$, $E_2 \in \mathbb{R}^{p_2 \times n_2}$, $e_1 \in \mathbb{R}^{p_1}$, $e_2 \in \mathbb{R}^{p_2}$;
+  a tolerance level $\epsilon > 0$.\\
   \textbf{initialize}
@@
   $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$ (for example take $\tau = \sigma = \frac{.99}{\|K\|}$); $k = 0$.\\
-  \Repeat{Convergence}{
+  \Repeat{$\frac{\|\Delta x^{(k)}\|^2 + \|\Delta v^{(k)}\|^2}{\sigma} + \frac{\|\Delta y^{(k)}\|^2 + \|\Delta u^{(k)}\|^2}{\tau} < \epsilon$}{
     \begin{eqnarray*}
@@
 \end{algorithm}
+
+\section{Application to Poker}
+\subsection{Kuhn Poker}
+The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
+$E_1 = \left(\begin{array}{ccccccccccccc}
+1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
+-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
+  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
+  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
+  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
+\end{array}\right)  \in \mathbb{R}^{7 \times 13}$, $e_1 = e_2 = (1, 0, 0, 0, 0, 0, 0) \in \mathbb{R}^7$,\\
+$E_2 = \left(\begin{array}{ccccccccccccc}
+1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
+-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
+-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
+\end{array}\right)  \in \mathbb{R}^{7 \times 13}$, and\\
+$A = \left(\begin{array}{ccccccccccccc}
+  &   &   &   &   &   &   &   &   &   &   &   &  \\
+  &   &   &   &   &   &   & -0.167 &   &   &   & -0.167 &  \\
+  &   &   &   &   &   &   &   & -0.167 &   &   &   & -0.167\\
+  &   &   &   &   &   &   &   & -0.333 &   &   &   & -0.333\\
+  &   &   &   &   & 0.167 & -0.333 &   &   & 0.167 & -0.333 &   &  \\
+  &   &   & 0.167 &   &   &   &   &   &   &   & -0.167 &  \\
+  &   &   &   & -0.167 &   &   &   &   &   &   &   & -0.167\\
+  &   &   &   & 0.333 &   &   &   &   &   &   &   & -0.333\\
+  & 0.167 & 0.333 &   &   &   &   &   &   & 0.167 & -0.333 &   &  \\
+  &   &   & 0.167 &   &   &   & 0.167 &   &   &   &   &  \\
+  &   &   &   & -0.167 &   &   &   & -0.167 &   &   &   &  \\
+  &   &   &   & 0.333 &   &   &   & 0.333 &   &   &   &  \\
+  & 0.167 & 0.333 &   &   & 0.167 & 0.333 &   &   &   &   &   &  
+\end{array}\right)
+ \in \mathbb{R}^{13 \times 13}$.\\
+The pair $(\hat{x}, \hat{y}) \in \mathbb{R}^{13}_+ \times \mathbb{R}^{13}_+$ of realization plans given by $\hat{x} = (1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725)$ and\\
+$\hat{y} = (1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1)$ is a Nash equlibrium for the game, computed using Algorithm  \ref{Tab:algo}.
+The convergence curve is shown in Fig \ref{Tab:conv_curves}.
+One easy checks that this equilibrium is feasible.
+Indeed,  $E_1\hat{x} - e_1 = (4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, -8.62 \times 10^{-7}, -1.96 \times 10^{-5})$ and $E_2\hat{y} - e_2 = (-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6}, 2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7})$.
+Finally, $\hat{x}^TA\hat{y} = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by Kuhn in his 1954 paper.
+
+\begin{figure}
+  \includegraphics[width=.5\linewidth]{Kuhn3112_NE.pdf}
+  \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
+  \caption{Convergence curves of Algorithm \ref{Tab:algo} on simplified variants of Poker. \textbf{Left}: Kuhn Poker. \textbf{Right}: Another simplified Poker variant}.
+  \label{Tab:conv_curves}
+\end{figure}
 

### 2014-12-01 primal_dual.py

@@ -92,6 +92,53 @@ def primal_dual_ne(A, E1, E2, e1, e2, L=None, max_iter=10000, tol=1e-4):
             break
     return x, y, values
 
+
+def array2tex(x, bars=False, brace="(", form=None, col_names=None,
+              row_names=None, omit_zero=False):
+    def _omit_zero(a):
+        return " " if omit_zero and float(a) == 0. else a
+
+    from math import floor
+    if not col_names is None:
+        bars = True
+        col_names = " & ".join([str(cn) for cn in col_names])
+    if row_names is None and not col_names is None:
+        row_names = [""] * len(x)
+    if form is None:
+        form = "%s"
+    if brace == "(":
+        closing_brace = ")"
+    elif brace == "[":
+        closing_brace = "]"
+    cline = "c" * x.shape[1]
+    if bars:
+        cline = "|%s|" % ("|".join(cline))
+    if col_names:
+        cline  = "c%s" % cline
+    out = "%s\\begin{array}{%s}\n" % ("\\left" + brace if brace else "", cline)
+    if not col_names is None:
+        out += "%s\\\\%s\n" % (col_names, "\\hline" if bars else "")
+    out += ("\\\\%s\n" % ("\\hline" if bars else "")).join(
+        [" & ".join([_omit_zero(str(int(a)) if floor(a) == a else
+                                ("%s" % form) % a) for a in y]) for y in x])
+    if not row_names is None:
+        tmp = out.split("\n")
+        out = "\n".join(tmp[:2] + ["%s & %s" % (row_name, o)
+                                   for row_name, o in zip(row_names, tmp[2:])])
+    elif not col_names is None:
+        out = "\n".join(["& %s" % o for o in out.split("\n")])
+    out += "\n\\end{array}%s\n" % (
+        "\\right%s" % closing_brace if brace else "")
+    return out
+
+
+def scientific2tex(x):
+    if not isinstance(x, basestring):
+        x = "%.2e" % x
+    tmp = x.split("e")
+    assert len(tmp) == 2
+    return "%s \\times 10^{%d}" % (tmp[0], int(tmp[1]))
+
 if __name__ == "__main__":
     import matplotlib.pyplot as plt
     # build the game

### 2014-12-01 simple.py

@@ -905,10 +905,10 @@ def test_nash_player():
 if __name__ == "__main__":
     for game_cls in [SimplifiedPoker, Kuhn3112]:
         game = game_cls()
-        E, e = game.constraints[1]
-        F, f = game.constraints[2]
+        E1, e1 = game.constraints[1]
+        E2, e2 = game.constraints[2]
         A = game.payoff_matrix
-        x, y, values = primal_dual_ne(A, E, F, e, f)
+        x, y, values = primal_dual_ne(A, E1, E2, e1, e2)
         print
         print "Nash Equilibrium:"
         print "x* = ", x
@@ -916,9 +916,12 @@ if __name__ == "__main__":
         plt.figure(figsize=(13.5, 10))
         plt.semilogx(values, linewidth=4)
         value = values[-1]
-        plt.axhline(value, linestyle="--",
-                   label="value of the game: %5.2e" % value, linewidth=4,
-                    color="k")
+        plt.axhline(-1. / 18. if isinstance(game, Kuhn3112) else value,
+                    linestyle="--",
+                    label="true value of the game: %s" % (
+                        "-1 / 18" if isinstance(game, Kuhn3112) else
+                        ("-1 / 4" if isinstance(game, SimplifiedPoker)
+                         else "%.2e" % value)), linewidth=4, color="k")
         plt.xlabel("k", fontsize=25)
         plt.ylabel("value of game after k iterations", fontsize=25)
         plt.legend(loc="best", prop=dict(size=25))

### 2014-12-04 onepage.tex
better algo .tex
more

--- 2014-11-30 onepage.tex
@@
 \documentclass[a4paper,9pt,journal]{IEEEtran}
-\usepackage{graphicx} \usepackage[cmex10]{amsmath}
+\usepackage{graphicx}
+\usepackage[cmex10]{amsmath}
 \usepackage{amssymb} \usepackage{fancybox} \usepackage{alltt}
@@
 \begin{document}
-%\onecolumn
-\title{A fast and simple primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum games}
+\onecolumn
+\title{A fast and simple primal-dual algorithm for computing Nash equilibria in two-person zero-sum games}
 
@@
 \section{Introduction}
-%\label{sec:intro}
+\label{sec:intro}
 
@@
 
+\subsection{Notation and Terminology}
+\label{sec:notation}
+We will need the following notations and definitions in the sequel. Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
+the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros and $1_{m,n}$ denotes the $m$-by-$n$ matrix of ones.
+$\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_j \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegative orthant}.
+
+For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
+$(x)_+$ denotes its point-wise maximum with 0. Note that $(x)_+ \in \mathbb{R}^n_+$.
+For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$,
+denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).
+
+Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
+$i_C(x) = 0$ if $x \in C$ and $i_C(x) = +\infty$ otherwise. Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projector} onto $C$, denoted $\Pi_C$ is the function
+$\Pi: \mathbb{R}^n \mapsto C$, which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closed to $x$. Precisely,
+\begin{equation}
+  \Pi_C(x) := \underset{c \in C}{argimin}\text{ }\|c - x\|^2
+\end{equation}
+For example, $\Pi_{\mathbb{R}^n_+}(x) = (x)_+, \forall x \in \mathbb{R}^n$.
+
+Let $f : \mathbb{R}^n \rightarrow [0, +\infty]$ be a \textit{proper convex lower semi-continous function} (\textit{p.c.l.s.c} for short), and a positive real number $\tau$, the \textit{proximal operator} of $f$ of rank $\tau$,
+denoted $\text{prox}_{\tau f}$ is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) solution of the problem
+\begin{equation}
+  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
+\end{equation}
+
+It is easy to see that if $f$ is the indicator function of a convex set $C$, then $\text{prox}_{\tau f} = \Pi_C, \forall \tau > 0$. In this sense, proximal operators can be seen
+as a generalization of euclidean projection operators.
 \subsection{Statement of the problem}
-We are interested in the problem of computing a Nash equilibrium for a two-person zero-sum sequential game with imcomplete information
-and perfect recall (e.g Texas Hold'em Poker, etc.). In the \textit{sequence-form representation} of the game, the problem has the following saddle-point formulation
+We are interested in \textit{two-person zero-sum} games for which the \textit{Nash Equilibrium Problem (NEP)} can be formulated as
 \begin{equation}
@@
 
-where $Q_j := \{z \in \mathbb{R}^{n_j}|z \ge 0, E_jz=e_j\}$, for $j \in \{1, 2\}$. As usual, the ``minimize-maximize'' notation in problem
-\eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
+where \textit{feasibility sets} $Q_j$ have the form
 \begin{equation}
-  {y^*}^TAx \le y^TAx \le y^TAx^*, \forall (x, y) \in Q_1 \times Q_2
+  Q_j := \{z \in C_j|E_jz = e_j\},\text{ for some convex subset $C_j$ of a euclidean space $\mathbb{R}^{n_j}$, and some vector $e_j \in \mathbb{R}^{p_j}$}
 \end{equation}
-Such pairs correspond to the Nash equilibria of the game.
+$Q_j$ is the \textit{strategy portfolio} for player $j$. $A$ is the \textit{payoff matrix} from player 1's perspective of the game: if player 1 players strategy
+$x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money (and can be in fact negative!, in which case this represents a loss for player 1).
+We will assume that the convex sets $C_j$ are simple enough so that the eucliean projectors $\Pi_{C_j}$ can be cheaply computed.
+Typically, $C_j = \mathbb{R}^{p_j}_+$, and encodes a nonnegativity constraint; in this case, $\Pi_{C_j}(z) \equiv (z)_+$ as seen in subsection \ref{sec:notation}.
+As usual, the ``minimize-maximize'' notation in problem \eqref{eq:opt_pb} means that a pair $(\hat{x}, \hat{y}) \in Q_1 \times Q_2$ is a solution iff
+\begin{equation}
+  x^TA\hat{y} \le x^TAy \le {\hat{x}}^TAy, \forall (x, y) \in Q_1 \times Q_2
+\end{equation}
+Such pairs $(\hat{x}, \hat{y})$ correspond to the Nash equilibria of the game, and ${\hat{x}}^TA\hat{y}$ is the \textit{value}
+\footnote{This value is the same for every equilibrium pair $(\hat{x}, \hat{y})$.} of the game.
 
-We recall that $E_j$ is a $p_j$-by-$n_j$ matrix whose
-entries are $-1$, $0$, or $+1$, and $e_j := (1, 0, 0, ..., 0)$ is a vector of length $p_j$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
-encode linear constraints on our (resp. the opponent's)  ``admissible'' realization $x$ (resp. $y$). $A$ is the payoff matrix, of size $n_1 \times n_2$.
+\subsection{Examples}
+\label{subsec:example_games}
+\begin{itemize}
+\item[{\textit{(a)}}] \textit{Simultaneous two-person zero-sum games}\\
+  Here, the NEP takes the form of problem \eqref{eq:opt_pb} with $p_j = 1$, $C_j = \mathbb{R}^{p_j}_+$, $E_j = 1_{1, n_j}$,
+  and $e_j = 1$, so that $Q_j$ is simply the probabability $n_j$-simplex $\Delta_{n_j}$. Each point in $\Delta_{n_j}$ corresponds to a \textit{mixed-strategy} for player $j$,
+and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_j}$).
+\item[{\textit{(b)}}] \textit{Two-person zero-sum sequential games with imcomplete information and perfect recall}\\
+It is now known, thanks to the \textit{sequence-form representaion}, that the NEP for such games takes the form of problem \eqref{eq:opt_pb}
+
+We recall that in the sequence-form representation of such games,  $E_j$ is a matrix whose
+entries are $-1$, $0$, or $+1$, and $e_j := (1, 0, 0, ..., 0)$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
+encode linear constraints player 1's (resp. player 2's)  ``admissible'' \textit{realization plans} $x$ (resp. $y$).
+
+As an illustration, the pair $(\hat{x}, \hat{y})$ given by
+$\hat{x} = (1, .478, .522, .174, .826)$ and
+$\hat{y} = (1, 1/2, 1/2)$ is a Nash equilibrium for the sequence-form game given by\\
+$A = \left(\begin{array}{ccc}
+0 & 0 & 0\\
+0 & 0 & 0\\
+0 & 1 & -1\\
+0 & -2 & 4\\
+1 & 0 & 0
+\end{array}\right)$, $E_1 = \left(\begin{array}{ccccc}
+  1 & 0 & 0 & 0 & 0\\
+  -1 & 1 & 1 & 0 & 0\\
+  -1 & 0 & 0 & 1 & 1
+\end{array}\right)$,
+$e_1 = (1, 0, 0)$, $E_2 = \left(\begin{array}{ccc}
+  1 & 0 & 0\\
+  -1 & 1 & 1
+\end{array}\right)$, and $e_2 = (1, 0)$.
+\end{itemize}
 
 \begin{remark}
-  In practice, the matrices $A$, $E_1$, and $E_2$ are large but very sparse too.
+  At least for sequential games, the matrices $A$, $E_1$, and $E_2$ are very large (can have upto billions of rows and columns) but very sparse too.
 %% : $A$ will be sparse because a concrete sequential game will
@@
 
-We first introduce some fundamental notations, and then proceed to derive the algorithm. The convergence and convergence rate
+We now detail the proposed algorithm for solving the saddle-point problem \eqref{eq:opt_pb}. The convergence and convergence rate
 of our algorithm derive explicitly from the general Chambolle-Pock primal-dual scheme.
-
-\subsection{Notation and Terminology}
-Give positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
-the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
-$\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_j \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegative orthant}.
-
-For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
-$(x)_+$ denotes its point-wise maximum with 0. Note that $(x)_+ \in \mathbb{R}^n_+$.
-For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$, denoted $\|K\|$, is defined by
-\footnote{Equivalently, $\|K\|$ is the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$.}
-$\|K\| := \underset{x \ne 0}{max}\text{ }\frac{\|Kx\|}{\|x\|}$.
-
-Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
-$i_C(x) = 0$ if $x \in C$ and $i_C(x) = +\infty$ otherwise. Note that $i_{C \cap D} = i_C + i_D$. Finally, given a \textit{proper convex lower semi-continous
-function} (\textit{p.c.l.s.c} for short) $f : \mathbb{R}^n \rightarrow [0, +\infty]$, and a positive real number $\tau$, the \textit{proximal operator} of $f$ of rank $\tau$,
-denoted $\text{prox}_{\tau f}$ is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) solution of the problem
-\begin{equation}
-  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
-\end{equation}
 
@@
   \begin{split}
-    -i_{Q_1}(x) &= -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)}\\
-  i_{Q_2}(y) &= i_{\mathbb{R}^{n_2}_+}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}
+    -i_{Q_1}(x) &= -i_{C_1}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)}\\
+  i_{Q_2}(y) &= i_{C_2}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}
   \end{split}
@@
     %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)}\\
-      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tv\\
-      F: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tu
+      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{C_2}(y) + e_1^Tv\\
+      F: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{C_1}(x) + e_2^Tu
   \end{split}
   \right\}
+  \label{eq:unconstrained_pb}
 \end{equation}
@@
     \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{p_1}\\
-    (y, v) &\mapsto ((y)_+, v - \tau e_1)\\
+    (y, v) &\mapsto (\Pi_{C_2}(y), v - \tau e_1)\\
   \end{split}
@@
     \text{prox}_{\sigma F}: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{p_2}\\
-    (x, u) &\mapsto ((x)_+, u - \sigma e_2)
+    (x, u) &\mapsto (\Pi_{C_1}(x), u - \sigma e_2)
   \end{split}
@@
 \begin{algorithm}[htb]
-  \caption{Primal-dual algorithm for computing a Nash equilibrium of a two-person zero-sum game}
+  \caption{Primal-dual algorithm so solving the saddle-point problem \eqref{eq:opt_pb}}
+  \textbf{require}
+  \begin{itemize}
+    \item the specification of a game $(A, E_1, E_2, e_1, e_2, C_1, C_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
+  $E_1 \in \mathbb{R}^{p_1 \times n_1}$, $E_2 \in \mathbb{R}^{p_2 \times n_2}$, $e_1 \in \mathbb{R}^{p_1}$, $e_2 \in \mathbb{R}^{p_2}$, $C_j$ is a convex subset of $\mathbb{R}^{n_j}$;
+      \item a tolerance level $\epsilon > 0$
+  \end{itemize}
+  \textbf{precompute} $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
   \textbf{initialize}
@@
   $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$ (for example take $\tau = \sigma = \frac{.99}{\|K\|}$); $k = 0$.\\
-  \Repeat{Convergence}{
+  \Repeat{$\frac{\|\Delta x^{(k)}\|^2 + \|\Delta v^{(k)}\|^2}{\sigma} + \frac{\|\Delta y^{(k)}\|^2 + \|\Delta u^{(k)}\|^2}{\tau} < \epsilon$}{
+    \begin{eqnarray*}
+      x^{(k+1)} &\leftarrow& \Pi_{C_1}\left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)\\
+      u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
+      y^{(k+1)} &\leftarrow& \Pi_{C_2}\left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)\\
+      v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
+      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
+      \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
+      k &\leftarrow& k + 1
+    \end{eqnarray*}
+  } \Return $x^{(k)}$, $y^{(k)}$
+  \label{Tab:algo}
+\end{algorithm}
+
+\subsubsection{Special case: $C_j = \mathbb{R}^{n_j}_+$} As discussed in subsection \ref{subsec:example_games},
+the NEP for two-person zero-sum simultaneous games and two-person zero-sum sequential games with imcomplete
+information and perfect admits the formulation \eqref{eq:opt_pb}, with $C_j = \mathbb{R}^{n_j}_+$ (coding for nonnegativity constraints).
+In such situations, $\Pi_{C_j}(z) \equiv (z)_+$ as already mentioned in \ref{sec:notation}, and Algorithm \ref{Tab:algo} reduces to the simpler Algorithm \ref{Tab:algo_simplified}.
+
+\begin{algorithm}[htb]
+  \caption{Primal-dual algorithm so solving the saddle-point problem \eqref{eq:opt_pb}, with nonnegativity constraints $C_j = \mathbb{R}^{n_j}_+$}
+  \textbf{require}
+  \begin{itemize}
+    \item the specification of a game $(A, E_1, E_2, e_1, e_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
+  $E_1 \in \mathbb{R}^{p_1 \times n_1}$, $E_2 \in \mathbb{R}^{p_2 \times n_2}$, $e_1 \in \mathbb{R}^{p_1}$, $e_2 \in \mathbb{R}^{p_2}$;
+      \item a tolerance level $\epsilon > 0$
+  \end{itemize}
+  \textbf{precompute} $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
+  \textbf{initialize}
+  $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{p_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{p_2}$; 
+  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$ (for example take $\tau = \sigma = \frac{.99}{\|K\|}$); $k = 0$.\\
+  \Repeat{$\frac{\|\Delta x^{(k)}\|^2 + \|\Delta v^{(k)}\|^2}{\sigma} + \frac{\|\Delta y^{(k)}\|^2 + \|\Delta u^{(k)}\|^2}{\tau} < \epsilon$}{
     \begin{eqnarray*}
@@
   } \Return $x^{(k)}$, $y^{(k)}$
-  \label{Tab:algo}
+  \label{Tab:algo_simplified}
 \end{algorithm}
+
+\section{Application to Poker}
+\subsection{Kuhn Poker}
+The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
+$A = \left(\begin{array}{ccccccccccccc}
+  &   &   &   &   &   &   &   &   &   &   &   &  \\
+  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
+  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
+  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
+  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
+  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
+  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
+  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
+  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
+  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
+  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
+  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
+  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
+\end{array}\right)
+ \in \mathbb{R}^{13 \times 13}$,\\
+$E_1 = \left(\begin{array}{ccccccccccccc}
+1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
+-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
+  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
+  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
+  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
+\end{array}\right)  \in \mathbb{R}^{7 \times 13}$, $e_1 = e_2 = (1, 0, 0, 0, 0, 0, 0) \in \mathbb{R}^7$,\\
+$E_2 = \left(\begin{array}{ccccccccccccc}
+1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
+-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
+-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
+\end{array}\right)  \in \mathbb{R}^{7 \times 13}$.\\
+The pair $(\hat{x}, \hat{y}) \in \mathbb{R}^{13}_+ \times \mathbb{R}^{13}_+$ of realization plans given by $\hat{x} = (1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725)$ and\\
+$\hat{y} = (1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1)$ is a Nash equlibrium for the game, computed using Algorithm  \ref{Tab:algo_simplified}.
+The convergence curve is shown in Fig \ref{Tab:conv_curves}.
+One easy checks that this equilibrium is feasible.
+Indeed,  $E_1\hat{x} - e_1 = (4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, -8.62 \times 10^{-7}, -1.96 \times 10^{-5})$ and $E_2\hat{y} - e_2 = (-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6}, 2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7})$.
+Finally, $\hat{x}^TA\hat{y} = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by Kuhn in his 1954 paper.
+
+\begin{figure}
+  \includegraphics[width=.5\linewidth]{Kuhn3112_NE.pdf}
+  \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
+  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} on simplified variants of Poker. \textbf{Left}: Kuhn Poker. \textbf{Right}: Another simplified Poker variant}.
+  \label{Tab:conv_curves}
+\end{figure}
 

### 2014-12-04 primal_dual.py

@@ -21,11 +21,13 @@ def power(A, p, max_iter=100, **kwargs):
     return lambd
 
 
-def primal_dual_ne(A, E1, E2, e1, e2, L=None, max_iter=10000, tol=1e-4):
+def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
+                   proj_C2=lambda y: np.maximum(y, 0.),
+                   L=None, max_iter=1500, tol=1e-4):
     """Primal-Dual algorithm for computing Nash equlibrium for two-person
     zero-sum game with payoff matrix A and contraint sets
 
-        Qj := {z | z = (z)_+, Ejz = ej
+        Qj := {z in Cj | Ejz = ej}
 
     The formal problem is:
 
@@ -67,12 +69,12 @@ def primal_dual_ne(A, E1, E2, e1, e2, L=None, max_iter=10000, tol=1e-4):
 
         # update x and u
         x += tau * (A.dot(ytilde) - E1.T.dot(vtilde))
-        x = np.maximum(x, 0.)
+        x = proj_C1(x)
         u += tau * (E2.dot(ytilde) - e2)
 
         # update y and v
         y -= sigma * (A.T.dot(x) + E2.T.dot(u))
-        y = np.maximum(y, 0.)
+        y = proj_C2(y)
         v -= sigma * (e1 - E1.dot(x))
 
         # update ytilde and vtilde
@@ -90,6 +92,7 @@ def primal_dual_ne(A, E1, E2, e1, e2, L=None, max_iter=10000, tol=1e-4):
         if error < tol:
             print "\tConverged after %i iterations." % (k + 1)
             break
+
     return x, y, values
 
 

### 2014-12-04 simple.py

@@ -930,13 +930,13 @@ if __name__ == "__main__":
         plt.tick_params(axis='both', which='major', labelsize=20)
         plt.savefig("%s_NE.pdf" % game.__class__.__name__)
 
-        tmpfig = plt.figure(figsize=(13.5, 10))
-        plt.matshow(game.payoff_matrix, fignum=tmpfig.number)
-        plt.axis("off")
-        plt.savefig("%s_payoff.pdf" % game.__class__.__name__)
+        # tmpfig = plt.figure(figsize=(13.5, 10))
+        # plt.matshow(game.payoff_matrix, fignum=tmpfig.number)
+        # plt.axis("off")
+        # plt.savefig("%s_payoff.pdf" % game.__class__.__name__)
 
-        plt.figure()
-        game.draw()
-        plt.title("Game tree (T) for %s" % game.__class__.__name__)
+        # plt.figure()
+        # game.draw()
+        # plt.title("Game tree (T) for %s" % game.__class__.__name__)
 
     plt.show()

### 2014-12-04 nips2015.tex
omitted files

\documentclass{article} % For LaTeX2e
%\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}

\usepackage{graphicx}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09

\usepackage{bm}
\def\B#1{\bm{#1}}
%\def\B#1{\mathbf{#1}}
\def\trans{\mathsf{T}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author{
DOHMATOB Elvis \inst[1]}
%% \institute{Parietal team, Inria Saclay Ile-de-France\\
%% Saclay, France\\

\title{A fast and simple primal-dual algorithm for computing Nash equilibria in two-person zero-sum games}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\DeclareMathOperator{\prox}{prox}
\DeclareMathOperator{\im}{im}

\newtheorem{remark}{Remark}

\def \lb {{\langle}} \def \rb {{\rangle}}
\newcommand{\fro}[1]{\|#1\|_2}
\newcommand{\theHalgorithm}{\arabic{algorithm}}

\newcommand{\argmin}{\mathop{\mathrm{argmin}}}

\usepackage{hyperref}

\usepackage[ruled,vlined]{algorithm2e} \usepackage{framed}
\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}

%\nipsfinalcopy % Uncomment for camera-ready version
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\begin{abstract}
We present a simple $\mathcal{O}(1/\epsilon)$ primal-dual algorithm with a low cost per iteration, for computing Nash equilibria in two-person zero-sum games. Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}. Our algorithm derives from the primal-dual algorithm developed by Chambolle and Pock in \cite{chambolle2010}, which has gained considerable success in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria, since the strategy profiles of players are sufficiently complex
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to prevent easy computation 
% (i.e using non-iterative procedures, etc.)
of euclidean
% (metric)%
 projections thereupon (the proximal operators).
Our technique is to dualize the constraints in the Nash equilibrium problem, thus effectively unconstraining the problem. The resulting algorithm is simple, only involving matrix-vector multiplications
% (without any matrix inversions, etc.)
and nonnegative clipping.
% (taking point-wise max of a vector and 0)
The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}. As proof of concept, we apply our algorithm to solve Kuhn Poker.
\end{abstract}

\section{Introduction}
\label{sec:intro}
Though \textit{Nash equilibrium} has become a novel way for solving two-person zero-sum games, the problem of computing Nash equilibria for large-scale two-person zero-sum games is still largely unsolved. Even though this problem is, in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle.
%% We will be needing the following notation: %%  The reader should lookup any standard textbook
%% %% (for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions.
%% Viz,
%% \begin{itemize}
%% \item $\mathbb{R}^n$: $n$-dimensional real vector space;
%% \item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$n$ real matrices;
%% \item $0_{m,n}$: $m$-by-$n$ matrix of zeros;
%% \item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
%% \item $\mathbb{R}^n_+$: \quad $\{x \in \mathbb{R}^n|x = (x)_+\}$, the $n$-dimensional nonnegative orthant 
%% \item $i_C$: \quad indicator function of a convex set $C$;
%% % \item $\Pi_C$: \quad euclidean projection operator onto a convex set $C$;
%% \item $\|K\|_2$: \quad spectral norm of a matrix $K$
%% % \item $F^*$: the convex conjugate of a convex function $F$.
%% %% \item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
%% %% \item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
%% \end{itemize}

\section{Statement of the problem}
We are interested in computing Nash equilibria for \textit{two-person zero-sum} games. The problem takes the well-known \textit{minimax} form
\begin{equation}
  \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
  \label{eq:opt_pb}
\end{equation}

where \textit{feasibility sets} $Q_j$ have the form
\begin{equation}
  Q_j := \{z \in C_j|E_jz = e_j\}
\end{equation}
for some convex subset $C_j$ of a euclidean space $\mathbb{R}^{n_j}$, and some vector $e_j \in \mathbb{R}^{p_j}$.
$Q_j$ is the \textit{strategy portfolio} for player $j$. $A$ is the \textit{payoff matrix} from player 1's perspective of the game: if player 1 players strategy
$x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
We will assume that the convex sets $C_j$ are simple enough so that the eucliean projection operators $\Pi_{C_j}$ can be cheaply computed.
Typically, $C_j = \mathbb{R}^{p_j}_+ := \{x \in \mathbb{R}^n|x_j \ge 0\}$, the \textit{the nonnegative orthant}, and encodes a nonnegativity constraint. %% in this case, $\Pi_{C_j}(z) \equiv (z)_+$ as seen in subsection \ref{sec:notation}.
As usual, the ``minimax'' notation in problem \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
\begin{equation}
  x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
\end{equation}
Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
\footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.

We can distinguish two categories of such games, in terms of (non-)simultaneity of play.
\paragraph{Simultaneous two-person zero-sum games}
\label{subsec:example_games}
Here, the Nash equilibrium problem takes the form \eqref{eq:opt_pb} with $p_j = 1$, $C_j = \mathbb{R}^{p_j}_+$, $E_j = 1_{1, n_j}$,
  and $e_j = 1$, so that $Q_j$ is simply the probabability $n_j$-simplex $\Delta_{n_j}$. Each point in $\Delta_{n_j}$ corresponds to a \textit{mixed-strategy} for player $j$,
and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_j}$).

\paragraph{Two-person zero-sum sequential games with imcomplete information and perfect recall}
It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:opt_pb}.

We recall that in the sequence-form representation of such games,  $E_j$ is a matrix whose
entries are $-1$, $0$, or $+1$, and $e_j := (1, 0, 0, ..., 0)$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
encode linear constraints player 1's (resp. player 2's)  ``admissible'' \textit{realization plans} $x$ (resp. $y$).

\paragraph{Example of Nash equilibirum}
As an illustration, the pair $(x^*, y^*)$ given by
$x^* = (1, .478, .522, .174, .826)$ and
$y^* = (1, 1/2, 1/2)$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
$A = \left(\begin{array}{ccc}
  &   &  \\
  &   &  \\
  & 1 & -1\\
  & -2 & 4\\
1 &   &  
\end{array}\right)$, $E_1 = \left(\begin{array}{ccccc}
  1 &   &   &   &  \\
  -1 & 1 & 1 &   &  \\
  -1 &   &   & 1 & 1
\end{array}\right)$,
$E_2 = \left(\begin{array}{ccc}
  1 &   &  \\
  -1 & 1 & 1
\end{array}\right)$, $e_1 = (1, 0, 0)$, and $e_2 = (1, 0)$.

\begin{remark}
  At least for sequential games, the matrices $A$, $E_1$, and $E_2$ are very large (can have upto billions of rows and columns) but very sparse too.
%% : $A$ will be sparse because a concrete sequential game will
%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
%% combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
%% $E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
%% zig-zag between only a limited number of the player's information sets so that a move at an information set will
%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
This sparsity should be thoroughly exploited by a solver for problem \eqref{eq:opt_pb}.
\end{remark}

%% In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}.
%% We elaborate our proposed algorithm in section \ref{sec:algo}.

\section{Related work}
\label{sec:related_work}

Pending...

\section{Some prerequisite notions from convex analysis}
\label{sec:notation}
We will need the following notations and definitions in the sequel. Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros and $1_{m,n}$ denotes the $m$-by-$n$ matrix of ones.
%% $\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_j \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegative orthant}.

For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
$(x)_+$ denotes its point-wise maximum with 0. Note that $(x)_+ \in \mathbb{R}^n_+$.
For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$,
denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).

Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
$i_C(x) = 0$ if $x \in C$ and $i_C(x) = +\infty$ otherwise. Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection operator} onto $C$, denoted $\Pi_C$ is the function
$\Pi: \mathbb{R}^n \mapsto C$, which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closed to $x$. Precisely,
\begin{equation}
  \Pi_C(x) := \underset{c \in C}{argimin}\text{ }\|c - x\|^2
\end{equation}
For example, $\Pi_{\mathbb{R}^n_+}(x) = (x)_+, \forall x \in \mathbb{R}^n$.

Let $f : \mathbb{R}^n \rightarrow [0, +\infty]$ be a \textit{proper convex lower semi-continous function} (\textit{p.c.l.s.c} for short), and $\tau$ a positive real number. The \textit{proximal operator} of $f$ of rank $\tau$,
denoted $\text{prox}_{\tau f}$ is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) solution of the problem
\begin{equation}
  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
\end{equation}

It is easy to see that if $f$ is the indicator function of a convex set $C$, then $\text{prox}_{\tau f} = \Pi_C, \forall \tau > 0$. In this sense, proximal operators can be seen
as a generalization of euclidean projection operators.

\section{The algorithm}
We now derive our primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}. The algorithm can is an application of the general primal-dual algorithm proposed in \cite{chambolle2010}. Though this scheme has recently gained considerable popularity in the signal processing community \cite{gramfort-etal:2013a, dohmatob2014benchmarking}, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.

\begin{theorem}
  The Nash equilibrium problem \eqref{eq:opt_pb} can be re-written in the equivalent unconstrained form

  \begin{equation}
    \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{p_1}}{minimize}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{p_2}}{maximize}
           {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}
           \label{eq:unconstrained_pb}
  \end{equation}

  where $v \in \mathbb{R}^{p_1}$ and $u \in \mathbb{R}^{p_2}$ are auxiliary variables and 
  \begin{equation}
    \left .
    \begin{split}
      K :=
      \left[
        \begin{array}{c|c}
          A & -E_1^T \\ \hline
          E_2 & 0_{p_2, p_1}
        \end{array}
        \right] \in \mathbb{R}^{(n_1 + p_2) \times (n_2 + p_1)} \\
      %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)}\\
      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{C_2}(y) + e_1^Tv\\
      H: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{C_1}(x) + e_2^Tu
    \end{split}
    \right\}
    \label{eq:things}
  \end{equation}

  Moreover, $G$ and $H$ are \textit{p.c.l.s.c} and their proximal operators are given by
  \begin{equation}
    \left .
    \begin{split}
      \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{p_1}\\
      (y, v) &\mapsto (\Pi_{C_2}(y), v - \tau e_1)\\
    \end{split}
    \right\}
  \end{equation}

  and
  \begin{equation}
    \left .
    \begin{split}
      \text{prox}_{\sigma F}: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{p_2}\\
      (x, u) &\mapsto (\Pi_{C_1}(x), u - \sigma e_2)
    \end{split}
    \right\}
  \end{equation}
  \label{thm:pd}
\end{theorem}

%% Theorem \ref{thm:pd}, can be interpreted as follows: 2 players $x$ (player 1)  and $y$ (player 2) go heads-on in a zero-sum game with payoff matrix $A$. Their strategy, profiles are $Q_1$ and $Q_2$ respectively, meaning that if player $j$ players a strategy which is outside $Q_j$ then they are panalized by inflicting an infinite loss yupon them. To remedy this, they recruit assistants $u$ and $v$, whose sole goal is to preven the ...
\begin{proof} First observe that $\forall (x, y) \in \mathbb{R}^{n_1} \times \mathbb{R}^{n_2}$, we have
  \begin{eqnarray*}
      -i_{Q_1}(x) = -i_{C_1}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)},
      \end{eqnarray*}
  and
\begin{eqnarray*}
  i_{Q_2}(y) = i_{C_2}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}
\end{eqnarray*}
  Thus,% problem \eqref{eq:opt_pb} is equivalent to
  \begin{eqnarray*}
    \begin{split}
      x^TAy - i_{Q_1}(x) + i_{Q_2}(y) &= x^TAy -i_{C_1}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)} + i_{C_2}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}\\
      &= \underset{v \in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{min}\text{ }x^TAy - x^TE_1^Tv + u^TE_2y + i_{C_2}(y) + e_1^Tv -(i_{C_1}(x) + e_2^Tu)\\
      &= \underset{v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{max}
      {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)},
    \end{split}
  \end{eqnarray*}
where $K$, $G$, and $H$ are as given in \eqref{eq:things}.

Hence,
\begin{eqnarray*}
  \begin{split}
    \underset{y \in Q_2}{min}\text{ }\underset{x \in Q_1}{max}\text{ }x^TAy &=
    \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }x^TAy - i_{Q_1}(x) + i_{Q_2}(y)\\
    &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }
\underset{v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{max}
      {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}\\
    &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }
\underset{u \in \mathbb{R}^{p_2}}{max}
      {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}\\
      &=     \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{p_2}}{max}
           {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}
  \end{split}
\end{eqnarray*}
Thus problem \eqref{eq:opt_pb} is equivalent to problem \eqref{eq:unconstrained_pb} as claimed.

About the proximal operators, indeed both $G$ and $F$ are separable sums of the indicator function of a convex set, whose prox is simply the euclidean projection operator onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox, at rank $\tau$, is simply $z \mapsto z - \tau a$.
\end{proof}
Now applying Algorithm 39 of \cite{chambolle2010} with $F := H^*$ (the \textit{convex conjugate} of $H$)
 to problem \eqref{eq:unconstrained_pb}, we Algorithm \ref{Tab:algo} for solving the original problem \eqref{eq:opt_pb}. The $\mathcal{O}(1/\epsilon)$ convergence rate of Algorothm \ref{Tab:algo} hails directly from Theorem 1 of \cite{chambolle2010}. Note that this convergence rate cannot be improved in the framework of \cite{chambolle2010}, since neither $G$ nor $H$ is \textit{uniformly convex}.

\begin{algorithm}[htb]
  \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}}
  \textbf{require}
  \begin{itemize}
    \item the specification of a game $(A, E_1, E_2, e_1, e_2, C_1, C_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
  $E_1 \in \mathbb{R}^{p_1 \times n_1}$, $E_2 \in \mathbb{R}^{p_2 \times n_2}$, $e_1 \in \mathbb{R}^{p_1}$, $e_2 \in \mathbb{R}^{p_2}$, $C_j$ is a convex subset of $\mathbb{R}^{n_j}$;
      \item a tolerance level $\epsilon > 0$, on the duality gap
  \end{itemize}
  \textbf{precompute} $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
  \textbf{initialize}
  $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{p_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{p_2}$; 
  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
  \Repeat{$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$}{
    \begin{eqnarray*}
      x^{(k+1)} &\leftarrow& \Pi_{C_1}\left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)\\
      u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
      y^{(k+1)} &\leftarrow& \Pi_{C_2}\left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)\\
      v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
      \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
      k &\leftarrow& k + 1
    \end{eqnarray*}
  } \Return $x^{(k)}$, $y^{(k)}$
  \label{Tab:algo}
\end{algorithm}

\subsection{Special case: $C_j = \mathbb{R}^{n_j}_+$} As discussed in subsection \ref{subsec:example_games},
the Nash equilibrium problem for two-person zero-sum simultaneous games and two-person zero-sum sequential games with imcomplete
information and perfect recall admits the formulation \eqref{eq:opt_pb}, with $C_j = \mathbb{R}^{n_j}_+$ (coding for nonnegativity constraints).
In such situations, $\Pi_{C_j}(z) \equiv (z)_+$ as already mentioned in \ref{sec:notation}, and Algorithm \ref{Tab:algo} reduces to the simpler Algorithm \ref{Tab:algo_simplified}.

\begin{algorithm}[htb]
  \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}, with nonnegativity constraints $C_j = \mathbb{R}^{n_j}_+$}
  \textbf{require}
  \begin{itemize}
    \item the specification of a game $(A, E_1, E_2, e_1, e_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
  $E_1 \in \mathbb{R}^{p_1 \times n_1}$, $E_2 \in \mathbb{R}^{p_2 \times n_2}$, $e_1 \in \mathbb{R}^{p_1}$, $e_2 \in \mathbb{R}^{p_2}$;
      \item a tolerance level $\epsilon > 0$
  \end{itemize}
  \textbf{precompute} $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
  \textbf{initialize}
  $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{p_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{p_2}$; 
  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
  \Repeat{$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$}{
    \begin{eqnarray*}
      x^{(k+1)} &\leftarrow& \left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)_+\\
      u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
      y^{(k+1)} &\leftarrow& \left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)_+\\
      v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
      \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
      k &\leftarrow& k + 1
    \end{eqnarray*}
  } \Return $x^{(k)}$, $y^{(k)}$
  \label{Tab:algo_simplified}
\end{algorithm}

\section{Application to Poker: Kuhn Poker}
The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
$A = \left(\begin{array}{ccccccccccccc}
  &   &   &   &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
\end{array}\right)$,\\
$E_1 = \left(\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
\end{array}\right)$, $e_1 = e_2 = (1, 0, 0, 0, 0, 0, 0)$,\\
and $E_2 = \left(\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
\end{array}\right)$.\\
The pair $(x^*, y^*)$ of realization plans given by\\
$x^* = (1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725)$ and
$y^* = (1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1)$ is a Nash equlibrium for the game, computed using Algorithm  \ref{Tab:algo_simplified}. The convergence curve is shown in Fig \ref{Tab:conv_curves}. One easy checks that this equilibrium is feasible. Indeed,  $E_1x^* - e_1 = (4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, -8.62 \times 10^{-7}, -1.96 \times 10^{-5})$ and $E_2y^* - e_2 = (-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6}, 2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7})$. Finally, $x^*TAy^* = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by Kuhn in his 1954 paper.

\begin{figure}
  \includegraphics[width=.5\linewidth]{Kuhn3112_NE.pdf}
  \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} on simplified variants of Poker. \textbf{Left}: Kuhn Poker. \textbf{Right}: Another simplified Poker variant}.
  \label{Tab:conv_curves}
\end{figure}

\small
\bibliographystyle{ieeetr}
\bibliography{bib}

\end{document}

### 2014-12-12 nips2015.tex
more
wip

@@
 \documentclass{article} % For LaTeX2e
-%\usepackage{nips14submit_e,times}
+\usepackage{nips14submit_e,times}
 \usepackage{hyperref}
@@
 \author{
-DOHMATOB Elvis \inst[1]}
+DOHMATOB Elvis}
 %% \institute{Parietal team, Inria Saclay Ile-de-France\\
@@
 
-\title{A fast and simple primal-dual algorithm for computing Nash equilibria in two-person zero-sum games}
+\title{Primal-dual algorithm for computing Nash equilibria in
+% two-person zero-sum
+sequential games
+% with imcomplete information and perfect recall
+}
 
@@
 \begin{abstract}
-We present a simple $\mathcal{O}(1/\epsilon)$ primal-dual algorithm with a low cost per iteration, for computing Nash equilibria in two-person zero-sum games.
-Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall.
-The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}.
-Our algorithm derives from the primal-dual algorithm developed by Chambolle and Pock in \cite{chambolle2010}, which has gained considerable success in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria, since the strategy profiles of players are sufficiently complex
+We present a simple $\mathcal{O}(1/\epsilon)$ primal-dual algorithm with a low cost per iteration, for computing Nash equilibria in two-person zero-sum sequential games like Texas Hold'em Poker.
+%% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall.
+The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}
+Our algorithm derives from the primal-dual algorithm developed
+% by Chambolle and Pock
+in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria.
+This limitation is due to the fact that the strategy profiles (polytopes) of players are sufficiently complex
 % (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
@@
  projections thereupon (the proximal operators).
-Our technique is to dualize the constraints in the Nash equilibrium problem, thus effectively unconstraining the problem.
+Our technique is to dualize the linear constraints that form part of the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme.
 The resulting algorithm is simple, only involving matrix-vector multiplications
@@
 The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}.
+Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing}, our algorithm has a cheap and constant cost per iteration.
 As proof of concept, we apply our algorithm to solve Kuhn Poker.
@@
 \label{sec:intro}
-Though \textit{Nash equilibrium} has become a novel way for solving two-person zero-sum games, the problem of computing Nash equilibria for large-scale two-person zero-sum games is still largely unsolved.
+For sequential games with imcomplete information and perfect recall like Texas Hold'em Poker, von Stengel and co-workers have developed the \textit{sequence-form} representation (see \cite{von1996efficient} and references therewithin), whose size is linear in the size of the game tree, in contrast with the \textit{strategic-form} representation which is exponential in the size of the game tree.
+
+%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:opt_pb}.
+
+%%%
+\paragraph{Sequence-form representaion}
+The game consists of three players:
+\begin{itemize}
+\item player 1 (Alice),
+\item player 2 (Bob), and
+\item player 0, a special player called \textit{chance}, who plays a publicly known \textit{mixed strategy} $\beta_0$ (more on this later),
+\end{itemize}
+who take turns to play, according to the rules of the game.
+The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of moves) in the former.
+The sequence-form representation for such a game is a quintuplet $(A, E_1, E_2, e_1, e_1)$, where
+\begin{itemize}
+\item For each \textit{information set} $h$ of player $k$, $\sigma_h$ is the sequence of moves to $h$.
+$C_h$ is the set of choices at $h$.
+$\mathcal{I}_k$ is the set of all information sets of player $k$, and the set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by
+\begin{equation}
+\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
+\end{equation}
+Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the moves of all other players (the other player, and the \textit{chance} player, aka \textit{nature}) deleted.
+Such a sequence represents a possible sequence of moves made by player $k$ in the game, from start to finish.
+\item Given a node $t$
+  \begin{itemize}
+  \item $a(t)$ is the payoff received by player $1$ at $t$. Note that $a(t)$ is $0$ for all nonleaf nodes.
+  \item $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to a path in the game tree, by including the moves of the other players;
+  \item $\beta_0(t)$ is the product of the probabilities of the moves made by the chance player along $\sigma_0(t)$.
+  \end{itemize}
+
+\item Besides nonnegativity, the \textit{realization plans} $z$ of each play $k$ have linear contraints of the form
+\begin{equation}
+    z_{\emptyset} = 1 \text{ and }
+    z_{\sigma_h} = \sum_{c \in C_h}{z_{\sigma_h c}}\text{, } \forall h \in \mathcal{I}_k
+  \label{eq:lin}
+\end{equation}
+
+These linear constraints \eqref{eq:lin} can be written in the form
+\begin{equation}
+  E_k z = e_k
+\end{equation}
+
+where $E_k$ a matrix with $p_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $p_k$-dimensional vector of the form $(1, 0, ..., 0)$.
+The \textit{strategy profile} of player $k$ is then the $n_k$-dimensional polytope
+\begin{equation}
+  Q_k := \{z \in \mathbb{R}^{n_k}| z \ge 0\text{ and }E_kz = e_k\}
+  \label{eq:poly}
+\end{equation}
+
+Player $k$'s \textit{pure} strategies correspond to their sequences $\mathcal{S}_k$, and a realization plan is simply a randomization on these pure strategies.
+
+\item $A$, an $n_1$-by-$n_2$ matrix, is the \textit{payoff matrix} from player 1's perspective of the game. Formally $A = (A_{\sigma,\tau})$, where
+  \begin{equation}
+    A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
+  \end{equation}
+
+If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
+
+\end{itemize}
+
+\paragraph{Nash equilibrium problem in sequence-form representaion}
+In sequence-form representation, the Nash equilibrium problem is
+\begin{equation}
+  \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
+  \label{eq:opt_pb}
+\end{equation}
+As usual, the ``minimax'' notation in problem \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
+\begin{equation}
+  x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
+\end{equation}
+Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
+\footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
+
+Even though problem \eqref{eq:opt_pb} is, in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle.
+
+%% Though \textit{Nash equilibrium} has become a novel way for solving two-person zero-sum games, the problem of computing Nash equilibria for large-scale two-person zero-sum games is still largely unsolved.
 Even though this problem is, in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle.
@@
 
-\section{Statement of the problem}
-We are interested in computing Nash equilibria for \textit{two-person zero-sum} games. The problem takes the well-known \textit{minimax} form
-\begin{equation}
-  \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
-  \label{eq:opt_pb}
-\end{equation}
+%% \section{Statement of the problem}
+%% The Nash equilibrium problem for a two-person zero-sum sequential game with imcomplete information and perfect recall is a the saddle-point problem
+%% \begin{equation}
+%%   \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
+%%   \label{eq:opt_pb}
+%% \end{equation}
 
-where \textit{feasibility sets} $Q_j$ have the form
-\begin{equation}
-  Q_j := \{z \in C_j|E_jz = e_j\}
-\end{equation}
-for some convex subset $C_j$ of a euclidean space $\mathbb{R}^{n_j}$, and some vector $e_j \in \mathbb{R}^{p_j}$.
-$Q_j$ is the \textit{strategy portfolio} for player $j$. $A$ is the \textit{payoff matrix} from player 1's perspective of the game: if player 1 players strategy
-$x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
-We will assume that the convex sets $C_j$ are simple enough so that the eucliean projection operators $\Pi_{C_j}$ can be cheaply computed.
-Typically, $C_j = \mathbb{R}^{p_j}_+ := \{x \in \mathbb{R}^n|x_j \ge 0\}$, the \textit{the nonnegative orthant}, and encodes a nonnegativity constraint.
-%% in this case, $\Pi_{C_j}(z) \equiv (z)_+$ as seen in subsection \ref{sec:notation}.
-As usual, the ``minimax'' notation in problem \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
-\begin{equation}
-  x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
-\end{equation}
-Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
-\footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
+%% where player $k$'s \textit{strategy profile} $Q_k$ is the polytope
+%% \begin{equation}
+%%   Q_k := \{z \in \mathbb{R}^{n_k}| E_kz = e_k\text{ and } z_j \ge 0 \text{ }\forall j\}
+%% \end{equation}
+%% for %% some convex subset $C_k$ of a euclidean space $\mathbb{R}^{n_k}$, and 
+%% some $p_k$-by-$n_k$ matrix $E_k$ and $p_k$-dimensional vector $e_k$. $A$ is the \textit{payoff matrix} from player 1's perspective of the game: if player 1 players strategy
+%% $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
+%% %% We will assume that the convex sets $C_k$ are simple enough so that the eucliean projection operators $\Pi_{C_k}$ can be cheaply computed.
+%% Typically, $C_k = \mathbb{R}^{p_k}_+ := \{x \in \mathbb{R}^n|x_k \ge 0\}$, the \textit{the nonnegative orthant}, and encodes a nonnegativity constraint.
+%% in this case, $\Pi_{C_k}(z) \equiv (z)_+$ as seen in subsection \ref{sec:notation}.
+%% As usual, the ``minimax'' notation in problem \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
+%% \begin{equation}
+%%   x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
+%% \end{equation}
+%% Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
+%% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
 
-We can distinguish two categories of such games, in terms of (non-)simultaneity of play.
-\paragraph{Simultaneous two-person zero-sum games}
-\label{subsec:example_games}
-Here, the Nash equilibrium problem takes the form \eqref{eq:opt_pb} with $p_j = 1$, $C_j = \mathbb{R}^{p_j}_+$, $E_j = 1_{1, n_j}$,
-  and $e_j = 1$, so that $Q_j$ is simply the probabability $n_j$-simplex $\Delta_{n_j}$. Each point in $\Delta_{n_j}$ corresponds to a \textit{mixed-strategy} for player $j$,
-and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_j}$).
+%% We can distinguish two categories of such games, in terms of (non-)simultaneity of play.
+%% \paragraph{Simultaneous two-person zero-sum games}
+%% \label{subsec:example_games}
+%% Here, the Nash equilibrium problem takes the form \eqref{eq:opt_pb} with $p_k = 1$, $C_k = \mathbb{R}^{p_k}_+$, $E_k = 1_{1, n_k}$,
+%%   and $e_k = 1$, so that $Q_k$ is simply the probabability $n_k$-simplex $\Delta_{n_k}$. Each point in $\Delta_{n_k}$ corresponds to a \textit{mixed-strategy} for player $j$,
+%% and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_k}$).
 
-\paragraph{Two-person zero-sum sequential games with imcomplete information and perfect recall}
-It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:opt_pb}.
+%% \paragraph{Two-person zero-sum sequential games with imcomplete information and perfect recall}
+%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:opt_pb}.
 
-We recall that in the sequence-form representation of such games,  $E_j$ is a matrix whose
-entries are $-1$, $0$, or $+1$, and $e_j := (1, 0, 0, ..., 0)$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
-encode linear constraints player 1's (resp. player 2's)  ``admissible'' \textit{realization plans} $x$ (resp. $y$).
+%% We recall that in the sequence-form representation of such games,  $E_k$ is a matrix whose
+%% entries are $-1$, $0$, or $+1$, and $e_k := (1, 0, 0, ..., 0)$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
+%% encode linear constraints player 1's (resp. player 2's)  ``admissible'' \textit{realization plans} $x$ (resp. $y$).
 
@@
 
-\section{Some prerequisite notions from convex analysis}
+\section{Useful convex analysis}
 \label{sec:notation}
@@
 the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros and $1_{m,n}$ denotes the $m$-by-$n$ matrix of ones.
-%% $\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_j \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegative orthant}.
+%% $\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_k \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegative orthant}.
 
@@
 We now derive our primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}.
-The algorithm can is an application of the general primal-dual algorithm proposed in \cite{chambolle2010}.
-Though this scheme has recently gained considerable popularity in the signal processing community \cite{gramfort-etal:2013a, dohmatob2014benchmarking}, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.
+The algorithm is derived from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}.
+Though this scheme has recently gained considerable popularity in the signal processing community \cite{gramfort-etal:2013a}, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.
+
+It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:opt_pb} lies in the difficulty of effectively computing the metric projections $\Pi_{Q_k}$.
+Theorem \ref{thm:pd} provides a trick to effectively evade this difficulty.
 
@@
       %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)}\\
-      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{C_2}(y) + e_1^Tv\\
-      H: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{C_1}(x) + e_2^Tu
+      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tv\\
+      H: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tu
     \end{split}
@@
       \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{p_1}\\
-      (y, v) &\mapsto (\Pi_{C_2}(y), v - \tau e_1)\\
+      (y, v) &\mapsto ((y)_+, v - \tau e_1)\\
     \end{split}
@@
       \text{prox}_{\sigma F}: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{p_2}\\
-      (x, u) &\mapsto (\Pi_{C_1}(x), u - \sigma e_2)
+      (x, u) &\mapsto ((x)_+, u - \sigma e_2)
     \end{split}
@@
 %% Theorem \ref{thm:pd}, can be interpreted as follows: 2 players $x$ (player 1)  and $y$ (player 2) go heads-on in a zero-sum game with payoff matrix $A$.
-Their strategy, profiles are $Q_1$ and $Q_2$ respectively, meaning that if player $j$ players a strategy which is outside $Q_j$ then they are panalized by inflicting an infinite loss yupon them.
+Their strategy, profiles are $Q_1$ and $Q_2$ respectively, meaning that if player $j$ players a strategy which is outside $Q_k$ then they are panalized by inflicting an infinite loss yupon them.
 To remedy this, they recruit assistants $u$ and $v$, whose sole goal is to preven the ...
@@
   \begin{eqnarray*}
-      -i_{Q_1}(x) = -i_{C_1}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)},
+   -i_{Q_1}(x) = -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)},
       \end{eqnarray*}
@@
 \begin{eqnarray*}
-  i_{Q_2}(y) = i_{C_2}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}
+  i_{Q_2}(y) = i_{\mathbb{R}^{n_2}_+}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}
 \end{eqnarray*}
@@
     \begin{split}
-      x^TAy - i_{Q_1}(x) + i_{Q_2}(y) &= x^TAy -i_{C_1}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)} + i_{C_2}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}\\
-      &= \underset{v \in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{min}\text{ }x^TAy - x^TE_1^Tv + u^TE_2y + i_{C_2}(y) + e_1^Tv -(i_{C_1}(x) + e_2^Tu)\\
-      &= \underset{v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{max}
-      {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)},
-    \end{split}
-  \end{eqnarray*}
-where $K$, $G$, and $H$ are as given in \eqref{eq:things}.
-
-Hence,
-\begin{eqnarray*}
-  \begin{split}
-    \underset{y \in Q_2}{min}\text{ }\underset{x \in Q_1}{max}\text{ }x^TAy &=
-    \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }x^TAy - i_{Q_1}(x) + i_{Q_2}(y)\\
-    &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }
-\underset{v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{max}
+  \underset{y \in Q_2}{min}\text{ }\underset{x \in Q_1}{max}\text{ }{x^TAy} &=
+  \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\left(\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }
+x^TAy - i_{Q_1}(x)\right) + i_{Q_2}(y) \\
+&= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }x^TAy -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)} + i_{\mathbb{R}^{n_2}_+}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}\\
+      &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }\underset{v \in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{min}\text{ }x^TAy - x^TE_1^Tv + u^TE_2y + i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tv -(i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tu)\\
+      &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ } \underset{v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{max}
       {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}\\
@@
   \end{eqnarray*}
+where $K$, $G$, and $H$ are as given in \eqref{eq:things}.
+
 Thus problem \eqref{eq:opt_pb} is equivalent to problem \eqref{eq:unconstrained_pb} as claimed.
@@
 Now applying Algorithm 39 of \cite{chambolle2010} with $F := H^*$ (the \textit{convex conjugate} of $H$)
- to problem \eqref{eq:unconstrained_pb}, we Algorithm \ref{Tab:algo} for solving the original problem \eqref{eq:opt_pb}.
-The $\mathcal{O}(1/\epsilon)$ convergence rate of Algorothm \ref{Tab:algo} hails directly from Theorem 1 of \cite{chambolle2010}.
+ to problem \eqref{eq:unconstrained_pb}, we obtain Algorithm \ref{Tab:algo_simplified} for solving the original problem \eqref{eq:opt_pb}.
+The $\mathcal{O}(1/\epsilon)$ convergence rate of Algorothm \ref{Tab:algo_simplified} hails directly from Theorem 1 of \cite{chambolle2010}.
 Note that this convergence rate cannot be improved in the framework of \cite{chambolle2010}, since neither $G$ nor $H$ is \textit{uniformly convex}.
+
+%% \subsection{Special case: $C_k = \mathbb{R}^{n_k}_+$} As discussed in subsection \ref{subsec:example_games},
+%% the Nash equilibrium problem for two-person zero-sum simultaneous games and two-person zero-sum sequential games with imcomplete
+%% information and perfect recall admits the formulation \eqref{eq:opt_pb}, with $C_k = \mathbb{R}^{n_k}_+$ (coding for nonnegativity constraints).
+%% In such situations, $\Pi_{C_k}(z) \equiv (z)_+$ as already mentioned in \ref{sec:notation}, and Algorithm \ref{Tab:algo} reduces to the simpler Algorithm \ref{Tab:algo_simplified}.
 
@@
   \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}}
-  \textbf{require}
-  \begin{itemize}
-    \item the specification of a game $(A, E_1, E_2, e_1, e_2, C_1, C_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
-  $E_1 \in \mathbb{R}^{p_1 \times n_1}$, $E_2 \in \mathbb{R}^{p_2 \times n_2}$, $e_1 \in \mathbb{R}^{p_1}$, $e_2 \in \mathbb{R}^{p_2}$, $C_j$ is a convex subset of $\mathbb{R}^{n_j}$;
-      \item a tolerance level $\epsilon > 0$, on the duality gap
-  \end{itemize}
-  \textbf{precompute} $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
-  \textbf{initialize}
-  $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{p_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{p_2}$; 
-  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
-  \Repeat{$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$}{
-    \begin{eqnarray*}
-      x^{(k+1)} &\leftarrow& \Pi_{C_1}\left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)\\
-      u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
-      y^{(k+1)} &\leftarrow& \Pi_{C_2}\left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)\\
-      v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
-      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
-      \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
-      k &\leftarrow& k + 1
-    \end{eqnarray*}
-  } \Return $x^{(k)}$, $y^{(k)}$
-  \label{Tab:algo}
-\end{algorithm}
-
-\subsection{Special case: $C_j = \mathbb{R}^{n_j}_+$} As discussed in subsection \ref{subsec:example_games},
-the Nash equilibrium problem for two-person zero-sum simultaneous games and two-person zero-sum sequential games with imcomplete
-information and perfect recall admits the formulation \eqref{eq:opt_pb}, with $C_j = \mathbb{R}^{n_j}_+$ (coding for nonnegativity constraints).
-In such situations, $\Pi_{C_j}(z) \equiv (z)_+$ as already mentioned in \ref{sec:notation}, and Algorithm \ref{Tab:algo} reduces to the simpler Algorithm \ref{Tab:algo_simplified}.
-
-\begin{algorithm}[htb]
-  \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}, with nonnegativity constraints $C_j = \mathbb{R}^{n_j}_+$}
   \textbf{require}
@@
 \begin{figure}
-  \includegraphics[width=.5\linewidth]{Kuhn3112_NE.pdf}
-  \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
-  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} on simplified variants of Poker. \textbf{Left}: Kuhn Poker. \textbf{Right}: Another simplified Poker variant}.
+  \includegraphics[width=1\linewidth]{Kuhn3112_NE.pdf}
+  % \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
+  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} on Kuhn Poker}
   \label{Tab:conv_curves}
@@
 
+\section{Generalization to general strategy profiles of a similar type}
+Notice tha in \eqref{eq:poly}, the strategy profile of player $k$ can be factored as
+\begin{equation}
+  Q_k := \{z \in \mathbb{R}^{n_k}_+| E_kz = e_k\text\}
+\end{equation}
+
+The framework presented sofar only demanded we be able to efficiently compute metric projections onto the nonnegative orthant $\mathbb{R}^{n_k}_+$ (nonnegative clipping).
+If we now consider general strategy profiles of the form
+\begin{equation}
+  Q_k := \{z \in C_k| E_kz = e_k\text\}
+\end{equation}
+where the $C_k$ are arbitrary convex sets for which the metric projections $\Pi_{C_k}$ can be effectively computed ...
 \small

### 2014-12-12 primal_dual.py

@@ -96,6 +96,14 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
     return x, y, values
 
 
+def primal_dual_sg_ne(A):
+    n1, n2 = A.shape
+    E1 = np.ones((1, n1))
+    E2 = np.ones((1, n2))
+    e1 = e2 = 1.
+    return primal_dual_ne(A, E1, E2, e1, e2)[:2]
+
+
 def array2tex(x, bars=False, brace="(", form=None, col_names=None,
               row_names=None, omit_zero=False):
     def _omit_zero(a):

### 2014-12-12 simple.py

@@ -918,12 +918,12 @@ if __name__ == "__main__":
         value = values[-1]
         plt.axhline(-1. / 18. if isinstance(game, Kuhn3112) else value,
                     linestyle="--",
-                    label="true value of the game: %s" % (
+                    label="true value of the game: $%s$" % (
                         "-1 / 18" if isinstance(game, Kuhn3112) else
                         ("-1 / 4" if isinstance(game, SimplifiedPoker)
                          else "%.2e" % value)), linewidth=4, color="k")
-        plt.xlabel("k", fontsize=25)
-        plt.ylabel("value of game after k iterations", fontsize=25)
+        plt.xlabel("$k$", fontsize=25)
+        plt.ylabel("value of game after $k$ iterations", fontsize=25)
         plt.legend(loc="best", prop=dict(size=25))
         # plt.title("%s: Sequence-form NE computation" % (
         #         game.__class__.__name__))

### 2014-12-15 nips2015.tex
more enh

@@
 \author{
-DOHMATOB Elvis}
-%% \institute{Parietal team, Inria Saclay Ile-de-France\\
-%% Saclay, France\\
+Elvis DOHMATOB
+\\
+Parietal team, Inria Saclay Ile-de-France\\
+Saclay, France\\
+\textit{email}: firstname.lastname@inria.fr}
 
@@
 % two-person zero-sum
-sequential games
+sequential games with imcomplete information
 % with imcomplete information and perfect recall
@@
 The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}
-Our algorithm derives from the primal-dual algorithm developed
+Our algorithm derives from the general primal-dual algorithm developed
 % by Chambolle and Pock
-in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria.
-This limitation is due to the fact that the strategy profiles (polytopes) of players are sufficiently complex
+in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria since the strategy profiles (polytopes) of players are so complex that it is not possible
 % (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
- to prevent easy computation 
+ to analytically compute
 % (i.e using non-iterative procedures, etc.)
-of euclidean
+euclidean
 % (metric)%
- projections thereupon (the proximal operators).
-Our technique is to dualize the linear constraints that form part of the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme.
+ projections (the proximal operators) thereupon.
+Our technique is to dualize the linear constraints that form part of the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme, without any additional overhead.
 The resulting algorithm is simple, only involving matrix-vector multiplications
@@
 %%%
-\paragraph{Sequence-form representaion}
-The game consists of three players:
-\begin{itemize}
-\item player 1 (Alice),
-\item player 2 (Bob), and
-\item player 0, a special player called \textit{chance}, who plays a publicly known \textit{mixed strategy} $\beta_0$ (more on this later),
-\end{itemize}
-who take turns to play, according to the rules of the game.
-The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of moves) in the former.
+\paragraph{From extensive-form to Sequence-form representaion}
+The game consists of three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}, who plays a publicly known \textit{mixed strategy} $\beta_0$ (more on this later).
+All three players are treated symmetrically.
+The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops.
+The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered moves) in the former.
 The sequence-form representation for such a game is a quintuplet $(A, E_1, E_2, e_1, e_1)$, where
 \begin{itemize}
-\item For each \textit{information set} $h$ of player $k$, $\sigma_h$ is the sequence of moves to $h$.
+\item At each node of the \textit{game tree}, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node.
+This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts.
+\item Due to imcompleted information, each player's nodes are grouped into equivalent classes of strategically indistinguishable nodes called \textit{information sets}.
+$\mathcal{I}_k$ is the set of all information sets of player $k$.
+If each information set is a singleton, then the game reduces to a game complete information.
+\item For each information set $h$ of player $k$, $\sigma_h$ is the sequence of moves to $h$.
 $C_h$ is the set of choices at $h$.
-$\mathcal{I}_k$ is the set of all information sets of player $k$, and the set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by
+The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by
 \begin{equation}
@@
   \begin{itemize}
-  \item $a(t)$ is the payoff received by player $1$ at $t$. Note that $a(t)$ is $0$ for all nonleaf nodes.
-  \item $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to a path in the game tree, by including the moves of the other players;
+  \item $a(t)$ is the payoff received by player $1$ at node $t$. That the game is zero-sum means that player 2 receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes.
+  \item $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the moves of the other players;
   \item $\beta_0(t)$ is the product of the probabilities of the moves made by the chance player along $\sigma_0(t)$.
@@
 
-\item Besides nonnegativity, the \textit{realization plans} $z$ of each play $k$ have linear contraints of the form
+\item Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
 \begin{equation}
-    z_{\emptyset} = 1 \text{ and }
-    z_{\sigma_h} = \sum_{c \in C_h}{z_{\sigma_h c}}\text{, } \forall h \in \mathcal{I}_k
+    z(\emptyset) = 1 \text{ and }
+    z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
   \label{eq:lin}
@@
 where $E_k$ a matrix with $p_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $p_k$-dimensional vector of the form $(1, 0, ..., 0)$.
+
+A realization plan $z$ for a player $k$ induces a behavioral strategy $\beta_k$ defined by
+\begin{equation}
+  \beta_k(c) := z(\sigma_hc)/z(\sigma_h)
+\end{equation}
+where $h \in \mathcal{I}_k$ and $c \in \mathcal{C}_h$, and $\beta_k(c)$ is the probability to play $c$ given that the player is at information set $h$.
+
 The \textit{strategy profile} of player $k$ is then the $n_k$-dimensional polytope
+
 \begin{equation}
@@
 As an illustration, the pair $(x^*, y^*)$ given by
-$x^* = (1, .478, .522, .174, .826)$ and
-$y^* = (1, 1/2, 1/2)$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
-$A = \left(\begin{array}{ccc}
+$x^* = [1, .478, .522, .174, .826]^T$ and
+$y^* = [1, 1/2, 1/2]^T$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
+$A = \left[\begin{array}{ccc}
   &   &  \\
@@
 1 &   &  
-\end{array}\right)$, $E_1 = \left(\begin{array}{ccccc}
+\end{array}\right]$, $E_1 = \left[\begin{array}{ccccc}
   1 &   &   &   &  \\
@@
   -1 &   &   & 1 & 1
-\end{array}\right)$,
-$E_2 = \left(\begin{array}{ccc}
+\end{array}\right]$,
+$E_2 = \left[\begin{array}{ccc}
   1 &   &  \\
   -1 & 1 & 1
-\end{array}\right)$, $e_1 = (1, 0, 0)$, and $e_2 = (1, 0)$.
+\end{array}\right]$, $e_1 = [1, 0, 0]^T$, and $e_2 = [1, 0]^T$.
 
 \begin{remark}
-  At least for sequential games, the matrices $A$, $E_1$, and $E_2$ are very large (can have upto billions of rows and columns) but very sparse too.
+  The matrices $A$, $E_1$, and $E_2$ are very large (can have upto billions of rows and columns) but very sparse too.
 %% : $A$ will be sparse because a concrete sequential game will
@@
 \label{sec:related_work}
-
-Pending...
+EGT used in \cite{hoda2010smoothing}...
 
@@
 The algorithm is derived from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}.
-Though this scheme has recently gained considerable popularity in the signal processing community \cite{gramfort-etal:2013a}, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.
+Though this scheme has recently gained considerable popularity in the signal processing community
+%\cite{gramfort-etal:2013a}
+, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.
 
@@
   \end{eqnarray*}
-where $K$, $G$, and $H$ are as given in \eqref{eq:things}.
-
-Thus problem \eqref{eq:opt_pb} is equivalent to problem \eqref{eq:unconstrained_pb} as claimed.
+where $K$, $G$, and $H$ are as given in \eqref{eq:things}. Thus problem \eqref{eq:opt_pb} is equivalent to problem \eqref{eq:unconstrained_pb} as claimed.
 
@@
 The $\mathcal{O}(1/\epsilon)$ convergence rate of Algorothm \ref{Tab:algo_simplified} hails directly from Theorem 1 of \cite{chambolle2010}.
-Note that this convergence rate cannot be improved in the framework of \cite{chambolle2010}, since neither $G$ nor $H$ is \textit{uniformly convex}.
+\begin{remark}
+  Note that the convergence rate of $\mathcal{O}(1/\epsilon)$ cannot be improved in the framework of \cite{chambolle2010}, since neither $G$ nor $H$ is \textit{uniformly convex}.
+\end{remark}
 
@@
 The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
-$A = \left(\begin{array}{ccccccccccccc}
+$A = \left[\begin{array}{ccccccccccccc}
   &   &   &   &   &   &   &   &   &   &   &   &  \\
@@
   & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
-\end{array}\right)$,\\
-$E_1 = \left(\begin{array}{ccccccccccccc}
+\end{array}\right]$,\\
+$E_1 = \left[\begin{array}{ccccccccccccc}
 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
@@
   &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
-\end{array}\right)$, $e_1 = e_2 = (1, 0, 0, 0, 0, 0, 0)$,\\
-and $E_2 = \left(\begin{array}{ccccccccccccc}
+\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
+and $E_2 = \left[\begin{array}{ccccccccccccc}
 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
@@
 -1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
-\end{array}\right)$.\\
+\end{array}\right]$.\\
 The pair $(x^*, y^*)$ of realization plans given by\\
-$x^* = (1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725)$ and
-$y^* = (1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1)$ is a Nash equlibrium for the game, computed using Algorithm  \ref{Tab:algo_simplified}.
+$x^* = [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T$ and
+$y^* = [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash equlibrium for the game, computed using Algorithm  \ref{Tab:algo_simplified}.
 The convergence curve is shown in Fig \ref{Tab:conv_curves}.
 One easy checks that this equilibrium is feasible.
-Indeed,  $E_1x^* - e_1 = (4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, -8.62 \times 10^{-7}, -1.96 \times 10^{-5})$ and $E_2y^* - e_2 = (-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6}, 2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7})$.
+Indeed,  $E_1x^* - e_1 = [4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T$ and $E_2y^* - e_2 = [-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6}, 2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7}]^T$.
 Finally, $x^*TAy^* = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by Kuhn in his 1954 paper.
@@
 
-\section{Generalization to general strategy profiles of a similar type}
+\section{Extending to games with more general strategy profiles of a similar type}
 Notice tha in \eqref{eq:poly}, the strategy profile of player $k$ can be factored as
@@
 
-The framework presented sofar only demanded we be able to efficiently compute metric projections onto the nonnegative orthant $\mathbb{R}^{n_k}_+$ (nonnegative clipping).
-If we now consider general strategy profiles of the form
+The framework presented sofar only demanded we be able to efficiently compute metric projections onto the nonnegative orthant $\mathbb{R}^{n_k}_+$, namely nonnegative clipping.
+This opens perspectives to envisage general two-person zero sum games for which the players' strategy profiles are of the form
 \begin{equation}
   Q_k := \{z \in C_k| E_kz = e_k\text\}
+  \label{eq:q_gen}
 \end{equation}
-where the $C_k$ are arbitrary convex sets for which the metric projections $\Pi_{C_k}$ can be effectively computed ...
+where the $C_k$ are arbitrary convex sets for which the metric projections $\Pi_{C_k}$ can be effectively computed.
+% \paragraph{Example: Computing best response strategies}
+
+As a motivating example, suppose Alice knows a prior that Bob is playing given realization plan $y_0 \in Q_2$ (for example, take $y_0 = [1, 0, ..., 0]^T \in \mathbb{R}^{n_2}$).
+Alice seeks a \textit{best response strategy}, namely a strategy $x^* \in Q_1$ such that
+\begin{equation}
+  x^TAy_0 \le {x^*}^TAy_0,\text{ } \forall x \in Q_1
+\end{equation}
+
+One observes that this problem is an instance of problem \eqref{eq:opt_pb} with
+$Q_2 = \{y_0\} = \{z \in C_2| E_2z = e_2\text\}$ and $C_2 = \{y_0\}$. Of course the metric projection on $C_2$ is simply the constant map $y \mapsto y_0$.
+
+As another motivating example, suppose we know the support ...
+We have the following generalization of Theorem \ref{thm:pd}.
+
+\begin{theorem}
+  The Nash equilibrium problem \eqref{eq:opt_pb} with strategy profiles given by  equation \eqref{eq:q_gen}, can be re-written in the equivalent unconstrained form
+
+  \begin{equation}
+    \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{p_1}}{minimize}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{p_2}}{maximize}
+           {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}
+           \label{eq:unconstrained_pb}
+  \end{equation}
+
+  where $v \in \mathbb{R}^{p_1}$ and $u \in \mathbb{R}^{p_2}$ are auxiliary variables and 
+  \begin{equation}
+    \left .
+    \begin{split}
+      K :=
+      \left[
+        \begin{array}{c|c}
+          A & -E_1^T \\ \hline
+          E_2 & 0_{p_2, p_1}
+        \end{array}
+        \right] \in \mathbb{R}^{(n_1 + p_2) \times (n_2 + p_1)} \\
+      %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)}\\
+      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [-\infty, +\infty], (y, v) \mapsto i_{C_2}(y) + e_1^Tv\\
+      H: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [-\infty, +\infty], (x, u) \mapsto i_{C_1}(x) + e_2^Tu
+    \end{split}
+    \right\}
+    \label{eq:things}
+  \end{equation}
+
+  Moreover, $G$ and $H$ are \textit{p.c.l.s.c} and their proximal operators are given by
+  \begin{equation}
+    \left .
+    \begin{split}
+      \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{p_1}\\
+      (y, v) &\mapsto (\Pi_{C_2}(y), v - \tau e_1)\\
+    \end{split}
+    \right\}
+  \end{equation}
+
+  and
+  \begin{equation}
+    \left .
+    \begin{split}
+      \text{prox}_{\sigma F}: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{p_2}\\
+      (x, u) &\mapsto (\Pi_{C_1}(x), u - \sigma e_2)
+    \end{split}
+    \right\}
+  \end{equation}
+  \label{thm:pd_gen}
+\end{theorem}
+
+\begin{proof}
+Totally analogous to the proof of Theorem \ref{thm:pd} with $\mathbb{R}^{n_k}_+$ replaced with $C_k$,
+$i_{\mathbb{R}^{n_k}_+}$ replaced with $i_{C_k}$, and $\Pi_{\mathbb{R}^{n_k}_+}$ replaced with $\Pi_{C_k}$.
+\end{proof}
+
+%\paragraph{$\mathcal{O}(1/\epsilon)$ primal-dual algorithm for general problems}
+Analogous to Algorithm \ref{Tab:algo_simplified}, we obtain Algorithm \ref{Tab:algo} for solving the Nash equilibrium problem \ref{eq:opt_pb} with the general strategy profiles $Q_k$ defined in \eqref{eq:q_gen}.
+Just like Algorithm \ref{Tab:algo_simplified}, Algorithm \ref{Tab:algo} has a $\mathcal{O}(1/\epsilon)$ convergence rate.
+
+\begin{algorithm}[htb]
+  \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}, with general strategy profiles as defined in \eqref{eq:q_gen}}
+  \textbf{require}
+  \begin{itemize}
+    \item the specification of a game $(A, E_1, E_2, e_1, e_2, C_1, C_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
+  $E_1 \in \mathbb{R}^{p_1 \times n_1}$, $E_2 \in \mathbb{R}^{p_2 \times n_2}$, $e_1 \in \mathbb{R}^{p_1}$, $e_2 \in \mathbb{R}^{p_2}$, each $C_k$ is a convex subset of $\mathbb{R}^{n_k}$, as in the definition of the strategy profiles $Q_k$ in equation \eqref{eq:q_gen};
+      \item a tolerance level $\epsilon > 0$
+  \end{itemize}
+  \textbf{precompute} $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
+  \textbf{initialize}
+  $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{p_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{p_2}$; 
+  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
+  \Repeat{$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$}{
+    \begin{eqnarray*}
+      x^{(k+1)} &\leftarrow& \Pi_{C_1}\left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)\\
+      u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
+      y^{(k+1)} &\leftarrow& \Pi_{C_2}\left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)\\
+      v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
+      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
+      \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
+      k &\leftarrow& k + 1
+    \end{eqnarray*}
+  } \Return $x^{(k)}$, $y^{(k)}$
+  \label{Tab:algo}
+\end{algorithm}
+
+\section{Conclusion}
+\medskip \noindent
+\textbf{Acknowledgments:}
+Pending...
+
 \small

### 2014-12-15 primal_dual.py

@@ -75,6 +75,8 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
         # update y and v
         y -= sigma * (A.T.dot(x) + E2.T.dot(u))
         y = proj_C2(y)
+        if len(y) > 10:
+            y[[2, 8, 9]] = 0
         v -= sigma * (e1 - E1.dot(x))
 
         # update ytilde and vtilde

### 2014-12-15 nips2015.tex
more enh

@@
 %%%
-\paragraph{From extensive-form to Sequence-form representaion}
-The game consists of three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}, who plays a publicly known \textit{mixed strategy} $\beta_0$ (more on this later).
-All three players are treated symmetrically.
+\paragraph{Extensive-form representation}
+The game consists of three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}. All three players are treated symmetrically.
 The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops.
-The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered moves) in the former.
-The sequence-form representation for such a game is a quintuplet $(A, E_1, E_2, e_1, e_1)$, where
-\begin{itemize}
-\item At each node of the \textit{game tree}, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node.
+%% The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
+
+At each node $t$ of the \textit{game tree}, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node.
 This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts.
-\item Due to imcompleted information, each player's nodes are grouped into equivalent classes of strategically indistinguishable nodes called \textit{information sets}.
-$\mathcal{I}_k$ is the set of all information sets of player $k$.
+Due to imcompleted information, each player's nodes are grouped into equivalent classes of \textit{strategically indistinguishable} nodes called \textit{information sets}; $\mathcal{I}_k$ is the set of all information sets of player $k$.
 If each information set is a singleton, then the game reduces to a game complete information.
-\item For each information set $h$ of player $k$, $\sigma_h$ is the sequence of moves to $h$.
+
+$a(t)$ is the payoff received by player $1$ at node $t$. That the game is zero-sum means that player 2 receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes.
+
+A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts.
+The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.
+
+\paragraph{From extensive-form to sequence-form representation}
+For each information set $h$ of player $k$, $\sigma_h$ is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players.
+\textit{Perfect recall} means that a player cannot get additional information on the game treee by remembering their earlier choices.
 $C_h$ is the set of choices at $h$.
@@
 \end{equation}
-Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the moves of all other players (the other player, and the \textit{chance} player, aka \textit{nature}) deleted.
-Such a sequence represents a possible sequence of moves made by player $k$ in the game, from start to finish.
-\item Given a node $t$
-  \begin{itemize}
-  \item $a(t)$ is the payoff received by player $1$ at node $t$. That the game is zero-sum means that player 2 receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes.
-  \item $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the moves of the other players;
-  \item $\beta_0(t)$ is the product of the probabilities of the moves made by the chance player along $\sigma_0(t)$.
-  \end{itemize}
+Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players (the other player, and the \textit{chance} player, aka \textit{nature}) deleted.
+Such a sequence represents a possible sequence of choices made by player $k$ in the game, from start to finish.
 
-\item Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
+$\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
+$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.
+
+Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
 \begin{equation}
@@
 \end{equation}
+
+A realization plan $z$ for a player $k$ induces a \textit{behavioural-strategy} $\beta_k$ defined by
+\begin{equation}
+  \beta_k(c) := \begin{cases}
+    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
+    0, &\mbox{Otherwise}.
+  \end{cases}
+\end{equation}
+
+where $h \in \mathcal{I}_k$ and $c \in \mathcal{C}_h$, and $\beta_k(c)$ is the probability to play $c$ given that the player is at information set $h$.
+From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.
 
@@
 where $E_k$ a matrix with $p_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $p_k$-dimensional vector of the form $(1, 0, ..., 0)$.
-
-A realization plan $z$ for a player $k$ induces a behavioral strategy $\beta_k$ defined by
-\begin{equation}
-  \beta_k(c) := z(\sigma_hc)/z(\sigma_h)
-\end{equation}
-where $h \in \mathcal{I}_k$ and $c \in \mathcal{C}_h$, and $\beta_k(c)$ is the probability to play $c$ given that the player is at information set $h$.
 
@@
 
-\item $A$, an $n_1$-by-$n_2$ matrix, is the \textit{payoff matrix} from player 1's perspective of the game. Formally $A = (A_{\sigma,\tau})$, where
+$A$, an $n_1$-by-$n_2$ matrix, is the \textit{payoff matrix} from player 1's perspective of the game. Formally $A = (A_{\sigma,\tau})$, where
   \begin{equation}
@@
 
-\end{itemize}
+The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form.
+However, since were are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all required information, as we will see in the next section.
 
 \paragraph{Nash equilibrium problem in sequence-form representaion}
-In sequence-form representation, the Nash equilibrium problem is
+In sequence-form representation, the Nash equilibrium problem is (see \cite{von1996efficient})
 \begin{equation}
@@
 
-Even though problem \eqref{eq:opt_pb} is, in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle.
+Even though problem \eqref{eq:opt_pb} is in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
 
@@
 %% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
-%% combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
-%% $E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
-%% zig-zag between only a limited number of the player's information sets so that a move at an information set will
+%% combinations of sequences of choices of the players, will actually lead to a leaf (i.e. end the game);
+%% $E$ and $F$ will be sparse because the kinks of possible sequences of choices of each player will
+%% zig-zag between only a limited number of the player's information sets so that a choice at an information set will
 %% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
@@
 Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
-$i_C(x) = 0$ if $x \in C$ and $i_C(x) = +\infty$ otherwise. Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection operator} onto $C$, denoted $\Pi_C$ is the function
+\begin{equation}
+  i_C(x) = \begin{cases}
+    0, &\mbox{if } x \in C\\
+    +\infty, &\mbox{otherwise}.
+    \end{cases}
+  \end{equation}
+
+Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection operator} onto $C$, denoted $\Pi_C$ is the function
 $\Pi: \mathbb{R}^n \mapsto C$, which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closed to $x$. Precisely,
@@
 As another motivating example, suppose we know the support ...
+
 We have the following generalization of Theorem \ref{thm:pd}.

### 2014-12-16 nips2015.tex
more enh wip

@@
 As proof of concept, we apply our algorithm to solve Kuhn Poker.
+We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with general convex sets.
 \end{abstract}
@@
 \label{sec:intro}
-For sequential games with imcomplete information and perfect recall like Texas Hold'em Poker, von Stengel and co-workers have developed the \textit{sequence-form} representation (see \cite{von1996efficient} and references therewithin), whose size is linear in the size of the game tree, in contrast with the \textit{strategic-form} representation which is exponential in the size of the game tree.
+For sequential games with imcomplete information and perfect recall like Texas Hold'em Poker, von Stengel and co-workers have developed the \textit{sequence-form} representation (see \cite{von1996efficient} and references therewithin), whose size is linear in the size of the game tree, in contrast with the \textit{strategic-form} representation which is exponential.
+The goal of this paper is to develop a fast and simple primal-dual algorithm for computing Nash equilibria for such games, using this representation.
+
+\paragraph{Plan}
+We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation.
+Then we state the Nash equilibrium problem for the sequence-form representation.
+In section \ref{sec:algo} we derive the proposed algorithm for solving this problem and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.
+This is followed by a demonstration on Kuhn Poker in section \ref{sec:kuhn}.
+In section \ref{sec:algo_gen}, we extend  the algorithm to problems with more general strategy profiles, and exhibit thesame convergence properties.
 
@@
 %% The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
-
 At each node $t$ of the \textit{game tree}, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node.
@@
 For each information set $h$ of player $k$, $\sigma_h$ is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players.
-\textit{Perfect recall} means that a player cannot get additional information on the game treee by remembering their earlier choices.
 $C_h$ is the set of choices at $h$.
+\textit{Perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices.
 The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by
@@
 \end{equation}
-Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players (the other player, and the \textit{chance} player, aka \textit{nature}) deleted.
-Such a sequence represents a possible sequence of choices made by player $k$ in the game, from start to finish.
-
+Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish.
 $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
@@
 
-Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
+Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$, and their \textit{mixed-strategies} are randomizations on these pure-strategies.
+In sequence-form, the strategy profile $Q_k$ of player $k \ge 1$ is the polytope of $n_k$-dimensional nonnegative vectors satisying
+% Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
 \begin{equation}
@@
 
-A realization plan $z$ for a player $k$ induces a \textit{behavioural-strategy} $\beta_k$ defined by
-\begin{equation}
-  \beta_k(c) := \begin{cases}
-    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
-    0, &\mbox{Otherwise}.
-  \end{cases}
-\end{equation}
-
-where $h \in \mathcal{I}_k$ and $c \in \mathcal{C}_h$, and $\beta_k(c)$ is the probability to play $c$ given that the player is at information set $h$.
-From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.
-
-These linear constraints \eqref{eq:lin} can be written in the form
-\begin{equation}
-  E_k z = e_k
-\end{equation}
-
-where $E_k$ a matrix with $p_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $p_k$-dimensional vector of the form $(1, 0, ..., 0)$.
-
-The \textit{strategy profile} of player $k$ is then the $n_k$-dimensional polytope
+These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
+where $E_k$ is a matrix with $p_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $p_k$-dimensional vector of the form $(1, 0, ..., 0)$.
+Thus we can re-write
 
@@
 
-Player $k$'s \textit{pure} strategies correspond to their sequences $\mathcal{S}_k$, and a realization plan is simply a randomization on these pure strategies.
+Each point $z \in Q_k$ are called \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
+\begin{equation}
+  \beta_k(h, c) := \begin{cases}
+    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
+    0, &\mbox{Otherwise}.
+  \end{cases}
+\end{equation}
 
-$A$, an $n_1$-by-$n_2$ matrix, is the \textit{payoff matrix} from player 1's perspective of the game. Formally $A = (A_{\sigma,\tau})$, where
+From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.
+
+The \textit{payoff matrix} from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
 \begin{equation}
@@
 The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form.
-However, since were are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all required information, as we will see in the next section.
+However, since are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.
 
-\paragraph{Nash equilibrium problem in sequence-form representaion}
+\paragraph{Statement of the problem: Nash equilibrium problem in sequence-form}
 In sequence-form representation, the Nash equilibrium problem is (see \cite{von1996efficient})
@@
 \end{equation}
-As usual, the ``minimax'' notation in problem \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
+As usual, the ``minimax'' notation in problem \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution if (and only if)
 \begin{equation}
@@
 \section{The algorithm}
+\label{sec:algo}
 We now derive our primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}.
@@
 \section{Application to Poker: Kuhn Poker}
+\label{sec:kuhn}
 The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
@@
 
-\section{Extending to games with more general strategy profiles of a similar type}
+\section{Extending to games with more general strategy profiles}
+\label{sec:algo_gen}
 Notice tha in \eqref{eq:poly}, the strategy profile of player $k$ can be factored as
@@
 
-As a motivating example, suppose Alice knows a prior that Bob is playing given realization plan $y_0 \in Q_2$ (for example, take $y_0 = [1, 0, ..., 0]^T \in \mathbb{R}^{n_2}$).
+As a motivating example, suppose Alice knows a priori that Bob is playing a given realization plan $y_0 \in Q_2$ (for example, take $y_0 = [1, 0, ..., 0]^T \in \mathbb{R}^{n_2}$).
 Alice seeks a \textit{best response strategy}, namely a strategy $x^* \in Q_1$ such that
@@
 Totally analogous to the proof of Theorem \ref{thm:pd} with $\mathbb{R}^{n_k}_+$ replaced with $C_k$,
-$i_{\mathbb{R}^{n_k}_+}$ replaced with $i_{C_k}$, and $\Pi_{\mathbb{R}^{n_k}_+}$ replaced with $\Pi_{C_k}$.
+$i_{\mathbb{R}^{n_k}_+}$ replaced with $i_{C_k}$, and $\Pi_{\mathbb{R}^{n_k}_+}$ (nonnegative clipping) replaced with $\Pi_{C_k}$.
 \end{proof}

### 2014-12-16 simple.py

@@ -443,8 +443,9 @@ class Game(object):
             self.payoff_matrix[i, j] += data['payoff'] * data['proba']
         return self.payoff_matrix
 
-    def draw(self):
+    def draw(self, figsize=None):
         """Draw game tree."""
+        plt.figure(figsize=figsize)
         pos = nx.graphviz_layout(self.tree, prog='dot')
 
         # leaf (terminal) nodes
@@ -464,6 +465,8 @@ class Game(object):
         nx.draw_networkx_edges(self.tree, pos, arrows=False)
         nx.draw_networkx_edge_labels(self.tree, pos,
                                      edge_labels=self.edge_labels)
+
+        # plt.axis("off")
 
 
 class Kuhn3112(Game):
@@ -929,6 +932,8 @@ if __name__ == "__main__":
         #         game.__class__.__name__))
         plt.tick_params(axis='both', which='major', labelsize=20)
         plt.savefig("%s_NE.pdf" % game.__class__.__name__)
+        game.draw(figsize=(13.5, 7))
+        plt.savefig("%s_gt.pdf" % game.__class__.__name__)
 
         # tmpfig = plt.figure(figsize=(13.5, 10))
         # plt.matshow(game.payoff_matrix, fignum=tmpfig.number)

### 2014-12-16 nips2015.tex
more enh wip

@@
 
-Each point $z \in Q_k$ are called \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
+Each point $z \in Q_k$ are called \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
 \begin{equation}

### 2014-12-17 nips2015.tex
wip

@@
 
-$a(t)$ is the payoff received by player $1$ at node $t$. That the game is zero-sum means that player 2 receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes.
+$a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
+receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
+The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
+We will assume implicitly that each (non-chance) player is rational.
 
@@
 
-Each point $z \in Q_k$ are called \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
+Each point $z \in Q_k$ is called a \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
 \begin{equation}
@@
 However, since are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.
+
+\paragraph{Example: Sequence-form representation of Kuhn Poker}
+\label{sec:kuhn_sf}
+The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
+$A = \left[\begin{array}{ccccccccccccc}
+  &   &   &   &   &   &   &   &   &   &   &   &  \\
+  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
+  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
+  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
+  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
+  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
+  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
+  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
+  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
+  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
+  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
+  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
+  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
+\end{array}\right]$,\\
+$E_1 = \left[\begin{array}{ccccccccccccc}
+1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
+-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
+  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
+  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
+  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
+\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
+and $E_2 = \left[\begin{array}{ccccccccccccc}
+1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
+-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
+-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
+\end{array}\right]$.\\
 
@@
 
-\paragraph{Example of Nash equilibirum}
-As an illustration, the pair $(x^*, y^*)$ given by
-$x^* = [1, .478, .522, .174, .826]^T$ and
-$y^* = [1, 1/2, 1/2]^T$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
-$A = \left[\begin{array}{ccc}
-  &   &  \\
-  &   &  \\
-  & 1 & -1\\
-  & -2 & 4\\
-1 &   &  
-\end{array}\right]$, $E_1 = \left[\begin{array}{ccccc}
-  1 &   &   &   &  \\
-  -1 & 1 & 1 &   &  \\
-  -1 &   &   & 1 & 1
-\end{array}\right]$,
-$E_2 = \left[\begin{array}{ccc}
-  1 &   &  \\
-  -1 & 1 & 1
-\end{array}\right]$, $e_1 = [1, 0, 0]^T$, and $e_2 = [1, 0]^T$.
+%% \paragraph{Example of Nash equilibirum}
+%% As an illustration, the pair $(x^*, y^*)$ given by
+%% $x^* = [1, .478, .522, .174, .826]^T$ and
+%% $y^* = [1, 1/2, 1/2]^T$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
+%% $A = \left[\begin{array}{ccc}
+%%   &   &  \\
+%%   &   &  \\
+%%   & 1 & -1\\
+%%   & -2 & 4\\
+%% 1 &   &  
+%% \end{array}\right]$, $E_1 = \left[\begin{array}{ccccc}
+%%   1 &   &   &   &  \\
+%%   -1 & 1 & 1 &   &  \\
+%%   -1 &   &   & 1 & 1
+%% \end{array}\right]$,
+%% $E_2 = \left[\begin{array}{ccc}
+%%   1 &   &  \\
+%%   -1 & 1 & 1
+%% \end{array}\right]$, $e_1 = [1, 0, 0]^T$, and $e_2 = [1, 0]^T$.
 
@@
 \end{equation}
-For example, $\Pi_{\mathbb{R}^n_+}(x) = (x)_+, \forall x \in \mathbb{R}^n$.
+For example, the metric projections onto the nonnegative orthant and the closed unit-disk $\bar{\Delta}$
+% := \{x|\|x\| \le 1\}$
+are $\Pi_{\mathbb{R}^n_+}(x) \equiv (x)_+$ and $\Pi_{\bar{\Delta}}(z) \equiv \dfrac{z}{max(\|z\|, 1)}$ respectively.
 
-Let $f : \mathbb{R}^n \rightarrow [0, +\infty]$ be a \textit{proper convex lower semi-continous function} (\textit{p.c.l.s.c} for short), and $\tau$ a positive real number.
-The \textit{proximal operator} of $f$ of rank $\tau$,
-denoted $\text{prox}_{\tau f}$ is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) solution of the problem
+Let $f : \mathbb{R}^n \rightarrow [0, +\infty]$ be a \textit{proper convex lower semi-continous function}
+(\textit{p.c.l.s.c} for short), and $\tau$ a positive real number. The \textit{proximal operator} of $f$ of rank
+$\tau$, denoted $\text{prox}_{\tau f}$ is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
+unique) solution of the problem
 \begin{equation}
@@
 \begin{proof} First observe that $\forall (x, y) \in \mathbb{R}^{n_1} \times \mathbb{R}^{n_2}$, we have
-  \begin{eqnarray*}
-   -i_{Q_1}(x) = -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)},
-      \end{eqnarray*}
-  and
-\begin{eqnarray*}
+  \begin{eqnarray}
+    \left.
+    \begin{split}
+      -i_{Q_1}(x) = -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)}\\
       i_{Q_2}(y) = i_{\mathbb{R}^{n_2}_+}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}
-\end{eqnarray*}
+      \end{split}
+    \right\}
+  \end{eqnarray}
   Thus,% problem \eqref{eq:opt_pb} is equivalent to
@@
 \label{sec:kuhn}
-The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
-$A = \left[\begin{array}{ccccccccccccc}
-  &   &   &   &   &   &   &   &   &   &   &   &  \\
-  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
-  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
-  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
-  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
-  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
-  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
-  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
-  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
-  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
-  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
-  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
-  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
-\end{array}\right]$,\\
-$E_1 = \left[\begin{array}{ccccccccccccc}
-1 &   &   &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
--1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
-  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
-  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
-  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
-\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
-and $E_2 = \left[\begin{array}{ccccccccccccc}
-1 &   &   &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
--1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
--1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
-\end{array}\right]$.\\
 The pair $(x^*, y^*)$ of realization plans given by\\
 $x^* = [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T$ and
-$y^* = [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash equlibrium for the game, computed using Algorithm  \ref{Tab:algo_simplified}.
+$y^* = [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash equlibrium for the Kuhn Poker presented in \ref{sec:kuhn_sf}, computed using Algorithm  \ref{Tab:algo_simplified}.
 The convergence curve is shown in Fig \ref{Tab:conv_curves}.

### 2015-01-06 nips2015.tex
ENH: formula for dual gap

@@
 \usepackage{amsmath,amsfonts,amsthm}
+\usepackage{qtree}
 
@@
 
-\usepackage[ruled,vlined]{algorithm2e} \usepackage{framed}
+\usepackage[ruled,vlined]{algorithm2e}
+\usepackage{framed}
 \newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
@@
 \begin{abstract}
-We present a simple $\mathcal{O}(1/\epsilon)$ primal-dual algorithm with a low cost per iteration, for computing Nash equilibria in two-person zero-sum sequential games like Texas Hold'em Poker.
+We present a simple primal-dual algorithm with a low cost per iteration, for computing Nash $\epsilon$-equilibria for two-person zero-sum sequential games like Texas Hold'em Poker, in $\mathcal{O}(1/\epsilon)$ iterations.
 %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall.
@@
 As proof of concept, we apply our algorithm to solve Kuhn Poker.
-We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with general convex sets.
+%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
 \end{abstract}
@@
 
-\paragraph{Plan}
-We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation.
+\paragraph{Nash equilibrium problem in sequence-form}
+In \cite{von1996efficient, vonequilibrium}, it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exists sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}, E_1 \in \mathbb{R}^{l_1 \times n_1}, E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to points $(x, y)$ which solve the primal LCP (Linear Constrained Programming) problem
+\begin{equation}
+  \begin{aligned}
+    & \underset{y,p}{\text{minimize}}
+    & & e_1^Tp \\
+    & \text{subject to}
+    & & -Ay + E_1^Tp \geq 0,\\
+    &&& E_2y = e_2,\\
+    &&& y \ge 0
+  \end{aligned}
+  \label{eq:primal_pb}
+\end{equation}
+
+and the dual LCP problem
+\begin{equation}
+  \begin{aligned}
+    & \underset{x,q}{\text{maximize}}
+    & & -e_2^Tq \\
+    & \text{subject to}
+    & & -A^Tx + E_2^Tq \leq 0,\\
+    &&& E_1x = e_1,\\
+    &&& x \ge 0
+  \end{aligned}
+  \label{eq:dual_pb}
+\end{equation}
+
+with duality gap given by
+\begin{equation}
+  \mathcal{G}(p, q) := e_1^Tp - (-e_2^Tq) = e_1^Tp + e_2^Tq
+  \label{eq:dgap}
+\end{equation}
+
+$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and $e_k$ is a vector of the form $[1, 0, ..., 0]$.
+In this representation (called the \textit{sequence-form}), the strategy profile of player $k$ is the polytope
+\begin{equation}
+  Q_k := \{z \ge 0\text{ }|\text{ }E_kz = e_k\} \subseteq \mathbb{R}^{n_k}
+\end{equation}
+
+Of course by \textit{weak duality} in problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb},, it holds that
+\begin{equation}
+  \mathcal{G}(p, q) \geq 0
+\end{equation}
+for any fixed pair $(x, y)$ of realization plans and admissible dual pair $(p,q)$ in problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb}.
+
+It was also shown (for example, Theorem 3.14 of \cite{vonequilibrium}) that a $(x, y)$ is a solution to the primal-dual problem \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff there exists vectors $p$ and $q$ such that
+\begin{equation}
+  \begin{split}
+    E_1x = e_1,\text{ }x \geq 0,\hspace{1em} E_2y = e_2,\text{ }y \geq 0\\
+    -Ay + E_1^Tp \geq 0,\hspace{1em}-A^Tx + E_2^Tq \leq 0
+    \end{split}
+\end{equation}
+
+Moreover, in this case \textit{strong duality} holds and the value of the game equals $e_1^Tp = -e_2^Tq$,
+In this case, the duality gap defined in \eqref{eq:dgap} vanishes.
+
+%% As usual, the ``minimax'' notation in problem \eqref{eq:primal_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution if (and only if)
+%% \begin{equation}
+%%   x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
+%% \label{eq:nash_ineq}
+%% \end{equation}
+%% Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
+%% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
+
+\begin{remark}  
+  Even though problem \eqref{eq:primal_pb} is in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
+\end{remark}
+
+% For the purpose of completeness we will cover the sequence-form representation in \ref{sec:rep}.
+
+%% Though \textit{Nash equilibrium} has become a novel way for solving two-person zero-sum games, the problem of computing Nash equilibria for large-scale two-person zero-sum games is still largely unsolved.
+Even though this problem is, in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle.
+%% We will be needing the following notation: %%  The reader should lookup any standard textbook
+%% %% (for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions.
+%% Viz,
+%% \begin{itemize}
+%% \item $\mathbb{R}^n$: $n$-dimensional real vector space;
+%% \item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$n$ real matrices;
+%% \item $0_{m,n}$: $m$-by-$n$ matrix of zeros;
+%% \item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
+%% \item $\mathbb{R}^n_+$: \quad $\{x \in \mathbb{R}^n|x = (x)_+\}$, the $n$-dimensional nonnegative orthant 
+%% \item $i_C$: \quad indicator function of a convex set $C$;
+%% % \item $\Pi_C$: \quad euclidean projection operator onto a convex set $C$;
+%% \item $\|K\|_2$: \quad spectral norm of a matrix $K$
+%% % \item $F^*$: the convex conjugate of a convex function $F$.
+%% %% \item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
+%% %% \item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
+%% \end{itemize}
+
+%% \section{Statement of the problem}
+%% The Nash equilibrium problem for a two-person zero-sum sequential game with imcomplete information and perfect recall is a the saddle-point problem
+%% \begin{equation}
+%%   \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
+%%   \label{eq:primal_pb}
+%% \end{equation}
+
+%% where player $k$'s \textit{strategy profile} $Q_k$ is the polytope
+%% \begin{equation}
+%%   Q_k := \{z \in \mathbb{R}^{n_k}| E_kz = e_k\text{ and } z_j \ge 0 \text{ }\forall j\}
+%% \end{equation}
+%% for %% some convex subset $C_k$ of a euclidean space $\mathbb{R}^{n_k}$, and 
+%% some $l_k$-by-$n_k$ matrix $E_k$ and $l_k$-dimensional vector $e_k$. $A$ is the \textit{payoff matrix} from player 1's perspective of the game: if player 1 players strategy
+%% $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
+%% %% We will assume that the convex sets $C_k$ are simple enough so that the eucliean projection operators $\Pi_{C_k}$ can be cheaply computed.
+%% Typically, $C_k = \mathbb{R}^{l_k}_+ := \{x \in \mathbb{R}^n|x_k \ge 0\}$, the \textit{the nonnegative orthant}, and encodes a nonnegativity constraint.
+%% in this case, $\Pi_{C_k}(z) \equiv (z)_+$ as seen in subsection \ref{sec:notation}.
+%% As usual, the ``minimax'' notation in problem \eqref{eq:primal_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
+%% \begin{equation}
+%%   x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
+%% \end{equation}
+%% Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
+%% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
+
+%% We can distinguish two categories of such games, in terms of (non-)simultaneity of play.
+%% \paragraph{Simultaneous two-person zero-sum games}
+%% \label{subsec:example_games}
+%% Here, the Nash equilibrium problem takes the form \eqref{eq:primal_pb} with $l_k = 1$, $C_k = \mathbb{R}^{l_k}_+$, $E_k = 1_{1, n_k}$,
+%%   and $e_k = 1$, so that $Q_k$ is simply the probabability $n_k$-simplex $\Delta_{n_k}$. Each point in $\Delta_{n_k}$ corresponds to a \textit{mixed-strategy} for player $j$,
+%% and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_k}$).
+
+%% \paragraph{Two-person zero-sum sequential games with imcomplete information and perfect recall}
+%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:primal_pb}.
+
+%% We recall that in the sequence-form representation of such games,  $E_k$ is a matrix whose
+%% entries are $-1$, $0$, or $+1$, and $e_k := (1, 0, 0, ..., 0)$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
+%% encode linear constraints player 1's (resp. player 2's)  ``admissible'' \textit{realization plans} $x$ (resp. $y$).
+
+%% \paragraph{Example of Nash equilibirum}
+%% As an illustration, the pair $(x^*, y^*)$ given by
+%% $x^* = [1, .478, .522, .174, .826]^T$ and
+%% $y^* = [1, 1/2, 1/2]^T$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
+%% $A = \left[\begin{array}{ccc}
+%%   &   &  \\
+%%   &   &  \\
+%%   & 1 & -1\\
+%%   & -2 & 4\\
+%% 1 &   &  
+%% \end{array}\right]$, $E_1 = \left[\begin{array}{ccccc}
+%%   1 &   &   &   &  \\
+%%   -1 & 1 & 1 &   &  \\
+%%   -1 &   &   & 1 & 1
+%% \end{array}\right]$,
+%% $E_2 = \left[\begin{array}{ccc}
+%%   1 &   &  \\
+%%   -1 & 1 & 1
+%% \end{array}\right]$, $e_1 = [1, 0, 0]^T$, and $e_2 = [1, 0]^T$.
+
+Solving problem \eqref{eq:primal_pb} exactly is impossible in practice, and such a precision doesn't have any fundamental advantage.
+Instead, it is customary compute so-called Nash $\epsilon$-equlibria
+
+\begin{definition}(\textbf{Nash $\epsilon$-equilibria})
+Given a margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists admissible vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} satisfying
+\begin{equation}
+  0 \le \mathcal{G}(p^*, q^*) \le \epsilon
+\label{eq:approx_pb}
+\end{equation}
+\end{definition}
+
+\paragraph{Outline of article}
+The goal of this article is to device a simple algorithm which produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations%We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation.
 Then we state the Nash equilibrium problem for the sequence-form representation.
+Then in
+In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:approx_pb}.
 In section \ref{sec:algo} we derive the proposed algorithm for solving this problem and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.
@@
 
-%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:opt_pb}.
+%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:primal_pb}.
 
 %%%
-\paragraph{Extensive-form representation}
-The game consists of three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}. All three players are treated symmetrically.
-The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops.
+%% \section{The sequence-form representation}
+%% \label{sec:rep}
+%% \paragraph{Recap: Extensive-form representation} The game tree $\mathcal{T}$ is defined as follows.
+There are three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}.
+All three players are treated symmetrically.
+Nodes of the game tree $\mathcal{T}$ are identified with states of the game, and actions taken by players correspond to edges of $\mathcal{T}$.
+%% The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops.
 %% The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
-At each node $t$ of the \textit{game tree}, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node.
+%% At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node.
 This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts.
@@
 
-$a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
-receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
-The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
-We will assume implicitly that each (non-chance) player is rational.
+%% $a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
+%% receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
+%% The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
+%% We will assume implicitly that each (non-chance) player is rational.
 
-A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts.
+%% A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts.
 The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.
 
-\paragraph{From extensive-form to sequence-form representation}
-For each information set $h$ of player $k$, $\sigma_h$ is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players.
+%% \paragraph{From extensive-form to sequence-form representation}
+%% For each information set $h$ of player $k$, $\sigma_h$ (unique and well-defined, by the  is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players.
+\textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined.
 $C_h$ is the set of choices at $h$.
-\textit{Perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices.
 The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by
-\begin{equation}
-\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
-\end{equation}
-Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish.
+%% \begin{equation}
+%% \mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
+%% \end{equation}
+%% Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish.
 $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
-$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.
+%% $\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.
 
-Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$, and their \textit{mixed-strategies} are randomizations on these pure-strategies.
+%% Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$, and their \textit{mixed-strategies} are randomizations on these pure-strategies.
 In sequence-form, the strategy profile $Q_k$ of player $k \ge 1$ is the polytope of $n_k$-dimensional nonnegative vectors satisying
-% Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
-\begin{equation}
-    z(\emptyset) = 1 \text{ and }
-    z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
-  \label{eq:lin}
-\end{equation}
+%% % Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
+%% \begin{equation}
+%%     z(\emptyset) = 1 \text{ and }
+%%     z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
+%%   \label{eq:lin}
+%% \end{equation}
 
-These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
-where $E_k$ is a matrix with $p_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $p_k$-dimensional vector of the form $(1, 0, ..., 0)$.
+%% These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
+%% where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$.
 Thus we can re-write
 
+%% \begin{equation}
+%%   Q_k := \{z \in \mathbb{R}^{n_k}| z \ge 0\text{ and }E_kz = e_k\}
+%%   \label{eq:poly}
+%% \end{equation}
+
+%% Each point $z \in Q_k$ is called a \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
+%% \begin{equation}
+%%   \beta_k(h, c) := \begin{cases}
+%%     z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
+%%     0, &\mbox{Otherwise}.
+%%   \end{cases}
+%% \end{equation}
+
+%% From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.
+
+%% The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
+%% \begin{equation}
+%%     A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
+%%   \end{equation}
+
+%% If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
+
+%% The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form.
+However, since are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.
+
+%% \paragraph{Example: Sequence-form representation of Kuhn Poker}
+%% \label{sec:kuhn_sf}
+%% The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
+%% $A = \left[\begin{array}{ccccccccccccc}
+%%   &   &   &   &   &   &   &   &   &   &   &   &  \\
+%%   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
+%%   &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
+%%   &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
+%%   &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
+%%   &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
+%%   &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
+%%   &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
+%%   & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
+%%   &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
+%%   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
+%%   &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
+%%   & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
+%% \end{array}\right]$,\\
+%% $E_1 = \left[\begin{array}{ccccccccccccc}
+%% 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+%% -1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
+%% -1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
+%% -1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
+%%   & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
+%%   &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
+%%   &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
+%% \end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
+%% and $E_2 = \left[\begin{array}{ccccccccccccc}
+%% 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+%% -1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
+%% -1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
+%% -1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
+%% -1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
+%% -1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
+%% -1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
+%% \end{array}\right]$.\\
+
+\section{Related work}
+\label{sec:related_work}
+EGT used in \cite{hoda2010smoothing}...
+
+\section{Useful convex analysis}
+\label{sec:notation}
+We will need the following notations and definitions in the sequel. Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
+the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros and $1_{m,n}$ denotes the $m$-by-$n$ matrix of ones.
+%% $\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_k \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegative orthant}.
+
+For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
+$(x)_+$ denotes its point-wise maximum with 0. Note that $(x)_+ \in \mathbb{R}^n_+$.
+For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$,
+denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).
+
+Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
 \begin{equation}
-  Q_k := \{z \in \mathbb{R}^{n_k}| z \ge 0\text{ and }E_kz = e_k\}
-  \label{eq:poly}
-\end{equation}
-
-Each point $z \in Q_k$ is called a \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
-\begin{equation}
-  \beta_k(h, c) := \begin{cases}
-    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
-    0, &\mbox{Otherwise}.
+  i_C(x) = \begin{cases}
+    0, &\mbox{if } x \in C\\
+    +\infty, &\mbox{otherwise}.
     \end{cases}
@@
 
-From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.
+Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection operator} onto $C$, denoted $\Pi_C$ is the function
+$\Pi: \mathbb{R}^n \mapsto C$, which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closed to $x$. Precisely,
+\begin{equation}
+  \Pi_C(x) := \underset{c \in C}{argimin}\text{ }\|c - x\|^2
+\end{equation}
+For example, the metric projections onto the nonnegative orthant and the closed unit-disk $\bar{\Delta}$
+% := \{x|\|x\| \le 1\}$
+are $\Pi_{\mathbb{R}^n_+}(x) \equiv (x)_+$ and $\Pi_{\bar{\Delta}}(z) \equiv \dfrac{z}{max(\|z\|, 1)}$ respectively.
 
-The \textit{payoff matrix} from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
+Let $f : \mathbb{R}^n \rightarrow [-\infty, +\infty]$ be a \textit{proper convex lower semi-continous function}
+(\textit{p.c.l.s.c} for short). The \textit{convex conjugate} of $f$ is the function $f^*: \mathbb{R}^n \rightarrow [-\infty, +\infty]$ is defined by
 \begin{equation}
-    A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
+  f^*(x) := \underset{z \in \mathbb{R}^n}{\text{max}}\text{ }z^Tx - f(x)
 \end{equation}
 
-If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
+Given $\tau > 0$, the \textit{proximal operator} of $f$ of rank
+$\tau$, denoted $\text{prox}_{\tau f}$, is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
+unique) solution of the problem
+\begin{equation}
+  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
+\end{equation}
 
-The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form.
-However, since are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.
+It is easy to see that if $f$ is the indicator function of a convex set $C$, then $\text{prox}_{\tau f} = \Pi_C, \forall \tau > 0$. In this sense, proximal operators can be seen
+as a generalization of euclidean projection operators.
 
-\paragraph{Example: Sequence-form representation of Kuhn Poker}
-\label{sec:kuhn_sf}
-The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
+\section{The proposed algorithm}
+\label{sec:algo}
+We now derive our primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:primal_pb}.
+The algorithm is derived from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}.
+Though this scheme has recently gained considerable popularity in the signal processing community
+%\cite{gramfort-etal:2013a}
+, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.
+
+It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing the metric projections $\Pi_{Q_k}$.
+Theorem \ref{thm:pd} provides a trick to effectively evade this difficulty.
+
+\begin{theorem}
+  The Nash equilibrium LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} can be re-written in the saddle-point form
+
+  \begin{equation}
+    \underset{y, v}{minimize}\text{ }\underset{x, u}{maximize}
+           {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}
+           \label{eq:unconstrained_pb}
+  \end{equation}
+
+  where
+  \begin{equation}
+    \left .
+    \begin{split}
+      K :=
+      \left[
+        \begin{array}{c|c}
+          A & -E_1^T \\ \hline
+          E_2 & 0_{l_2, l_1}
+        \end{array}
+        \right] \in \mathbb{R}^{(n_1 + l_2) \times (n_2 + l_1)} \\
+      %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + l_1) \times (n_1 + l_2)}\\
+      G: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tv\\
+      H: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tu
+    \end{split}
+    \right\}
+    \label{eq:things}
+  \end{equation}
+
+  %% Moreover, if $\mathcal{G}'$ denotes the dual-gap function of problem $\eqref{eq:unconstrained_pb}$ and as before, $\mathcal{G}$ denotes the dual-gap function of problem \eqref{eq:primal_pb}, then we have the bound
+  %% \begin{equation}
+  %%   \mathcal{G}(x, y) \le \mathcal{G}'(x, u, y, v), \forall (x, u, y, v) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \times \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}
+  %%   \end{equation}
+
+  \label{thm:pd}
+\end{theorem}
+
+%% Theorem \ref{thm:pd}, can be interpreted as follows: 2 players $x$ (player 1)  and $y$ (player 2) go heads-on in a zero-sum game with payoff matrix $A$.
+Their strategy, profiles are $Q_1$ and $Q_2$ respectively, meaning that if player $j$ players a strategy which is outside $Q_k$ then they are panalized by inflicting an infinite loss yupon them.
+To remedy this, they recruit assistants $u$ and $v$, whose sole goal is to preven the ...
+\begin{proof}
+  The LCP problem \eqref{eq:primal_pb} simplified as follows
+\begin{equation}
+  \begin{aligned}
+    \underset{y,p}{\text{min}}\text{ }e_1^Tp + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2) + i_{\mathbb{R}^{n_2}_+}(y)\\
+    = \underset{y,p}{\text{min}}\text{ }G(y,p) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e2)
+  \end{aligned}
+  \label{eq:a}
+\end{equation}
+
+Now,
+\begin{equation}
+  \begin{split}
+    H^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right) := \underset{x,q}{\text{max}}\text{ }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} - H(x, q) &= \underset{x, q}{\text{max}}\text{ }x^T(Ay - E_1^Tp) - i_{\mathbb{R}^{n_1}_+}(x) + q^TE_2y - f^Tq\\
+      &= \underset{x \geq 0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) + \underset{q}{\text{max}}\text{ }q^TE_2y - f^Tq\\
+      &= i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)
+  \end{split}
+  \label{eq:b}
+\end{equation}
+Combining equations \eqref{eq:a} and \eqref{eq:b}, it follows that the LCP problem \eqref{eq:primal_pb} can be written as 
+\begin{equation}
+  \underset{y,p}{\text{minimize}}\text{ }G(y,p) + H^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
+\end{equation}
+
+Similarly, one shows that the LCP problem \eqref{eq:dual_pb} is equivalent to
+\begin{equation}
+  \underset{x,q}{\text{minimize}}\text{ }-G^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right) - H(x, q)\
+\end{equation}
+
+But this two last equations are simply the primal and dual formulations of the saddle-point problem \eqref{eq:unconstrained_pb}, and we are done.
+
+%% For the dual-gap bound, note that $\forall (x', u', y', v') \in \mathbb{R}^{n_1}_+ \times \mathbb{R}^{l_2} \times \mathbb{R}^{n_2}_+ \times \mathbb{R}^{l_1}$, one has
+%% \begin{eqnarray*}
+%%   \begin{split}
+%%     \underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{l_2}}{max}\text{ }\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y'\\v'\end{bmatrix} + G(y', v') - H(x, u)
+%%       &= \underset{x \in \mathbb{R}^{n_1}_+, u \in \mathbb{R}^{l_2}}{max}\text{ }x^TAy' - v'^T(E_1x - e_1) + u^T(E_2y' - e_2)\\
+%%       &\ge \underset{x \in \mathbb{R}^{n_1}_+}{max}\text{ }x^TAy' - v'^T(E_1x - e_1) + \underset{u \in \mathbb{R}^{l_2}}{max}\text{ }u^T(E_2y' - e_2)\\
+%%       &\ge \underset{x \in Q_1}{max}\text{ }x^TAy + \underset{u \in \mathbb{R}^{l_2}}{max}\text{ }u^T(E_2y' - e_2)
+%%   \end{split}
+%% \end{eqnarray*}
+
+%% and
+%% \begin{eqnarray*}
+%%   \begin{split}
+%%     \underset{y \in \mathbb{R}^{n_2}, v \in \mathbb{R}^{l_1}}{min}\text{ }\begin{bmatrix}x'\\u'\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x', u')
+%%       &= \underset{y \in \mathbb{R}^{n_2}_+, v \in \mathbb{R}^{l_1}}{min}\text{ }x'^TAy - v^T(E_1x' - e_1) + u'^T(E_2y - e_2)\\
+%%       &\le \underset{y \in \mathbb{R}^{n_2}_+}{min}\text{ }x'^TAy + u'^T(E_2y - e_2) - v^T(E_1x' - e_1)
+%%   \end{split}
+%% \end{eqnarray*}
+\end{proof}
+
+The rest of this section is concerned with applying Algorithm 39 of \cite{chambolle2010} to solve problem
+\eqref{eq:unconstrained_pb} and therefore by Theorem \ref{thm:pd}, the Nash equilibrium problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb}.
+
+Now,
+$G$ and $H$ are \textit{p.c.l.s.c} and their proximal operators are given by
+  \begin{equation}
+    \left .
+    \begin{split}
+      \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\\
+      (y, v) &\mapsto ((y)_+, v - \tau e_1)\\
+    \end{split}
+    \right\}
+  \end{equation}
+
+  and
+  \begin{equation}
+    \left .
+    \begin{split}
+      \text{prox}_{\sigma H}: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}\\
+      (x, u) &\mapsto ((x)_+, u - \sigma e_2)
+    \end{split}
+    \right\}
+  \end{equation}
+
+Indeed both $G$ and $F$ are separable sums of the indicator function of a convex set, whose prox is simply the euclidean projection operator onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox, at rank $\tau$, is simply $z \mapsto z - \tau a$.
+
+So, applying Algorithm 39 of \cite{chambolle2010} with $F := H^*$
+ to problem \eqref{eq:unconstrained_pb}, we obtain Algorithm \ref{Tab:algo_simplified} for solving the original problem \eqref{eq:primal_pb}.
+The $\mathcal{O}(1/\epsilon)$ convergence rate of Algorothm \ref{Tab:algo_simplified} hails directly from Theorem 1 of \cite{chambolle2010}.
+\begin{remark}
+  Note that the convergence rate of $\mathcal{O}(1/\epsilon)$ cannot be improved in the framework of \cite{chambolle2010}, since neither $G$ nor $H$ is \textit{uniformly convex}.
+\end{remark}
+
+%% \subsection{Special case: $C_k = \mathbb{R}^{n_k}_+$} As discussed in subsection \ref{subsec:example_games},
+%% the Nash equilibrium problem for two-person zero-sum simultaneous games and two-person zero-sum sequential games with imcomplete
+%% information and perfect recall admits the formulation \eqref{eq:primal_pb}, with $C_k = \mathbb{R}^{n_k}_+$ (coding for nonnegativity constraints).
+%% In such situations, $\Pi_{C_k}(z) \equiv (z)_+$ as already mentioned in \ref{sec:notation}, and Algorithm \ref{Tab:algo} reduces to the simpler Algorithm \ref{Tab:algo_simplified}.
+
+\begin{algorithm}[H]
+  \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for finding a Nash $\epsilon$-equilibrium for a sequential two-person zero-sum game with imcomplete information and perfect recall}
+  \KwIn{sequence-form specification of the game: $(A, E_1, E_2, e_1, e_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
+  $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, $e_1 \in \mathbb{R}^{l_1}$, $e_2 \in \mathbb{R}^{l_2}$}
+  \KwOut{Nash $\epsilon-$equilibrium pair $(x^{(k)}$, $y^{(k)})$ of realization plans}
+  \textbf{Precompute}: $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
+  \textbf{Initialize}:
+  $x^{(0)} \in \mathbb{R}^{n_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $p \in \mathbb{R}^{l_1}$; $q^{(0)} \in \mathbb{R}^{l_2}$; 
+  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
+  \While{
+%$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$
+$|e_1^Tp^{(k)} - e_2^Tq^{(k)}| \geq \epsilon$}{
+    \begin{eqnarray*}
+      x^{(k+1)} &\leftarrow& \left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{p}^{(k)}\right)\right)_+\\
+      q^{(k+1)} &\leftarrow& q^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
+      y^{(k+1)} &\leftarrow& \left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tq^{(k + 1)}\right)\right)_+\\
+      p^{(k+1)} &\leftarrow& p^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
+      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
+      \tilde{q}^{(k+1)} &\leftarrow& 2q^{(k+1)} - q^{(k)}\\
+      k &\leftarrow& k + 1
+    \end{eqnarray*}
+  }
+  \label{Tab:algo_simplified}
+\end{algorithm}
+
+\begin{remark}
+It's possible to do over-relaxation and inertial iterates...
+\end{remark}
+
+\section{Results}
+\paragraph{Simulated game}
+See Figure \ref{Tab:sim_dgap_curve}.
+
+\begin{figure}
+  \includegraphics[width=1\linewidth]{simplex_dgap.pdf}
+  \includegraphics[width=1\linewidth]{simplex_NE.pdf}
+  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} random $1000 \times 1000$ matrix game (on simplexes)}
+  \label{Tab:sim_dgap_curve}
+\end{figure}
+
+\paragraph{Real-world game: Kuhn 3-card Poker}
+For this game, the sequence-form representation is given by (not showing zero entries)\\
 $A = \left[\begin{array}{ccccccccccccc}
@@
 
-\paragraph{Statement of the problem: Nash equilibrium problem in sequence-form}
-In sequence-form representation, the Nash equilibrium problem is (see \cite{von1996efficient})
-\begin{equation}
-  \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
-  \label{eq:opt_pb}
-\end{equation}
-As usual, the ``minimax'' notation in problem \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution if (and only if)
-\begin{equation}
-  x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
-\end{equation}
-Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
-\footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
-
-Even though problem \eqref{eq:opt_pb} is in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
-
-%% Though \textit{Nash equilibrium} has become a novel way for solving two-person zero-sum games, the problem of computing Nash equilibria for large-scale two-person zero-sum games is still largely unsolved.
-Even though this problem is, in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle.
-%% We will be needing the following notation: %%  The reader should lookup any standard textbook
-%% %% (for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions.
-%% Viz,
-%% \begin{itemize}
-%% \item $\mathbb{R}^n$: $n$-dimensional real vector space;
-%% \item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$n$ real matrices;
-%% \item $0_{m,n}$: $m$-by-$n$ matrix of zeros;
-%% \item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
-%% \item $\mathbb{R}^n_+$: \quad $\{x \in \mathbb{R}^n|x = (x)_+\}$, the $n$-dimensional nonnegative orthant 
-%% \item $i_C$: \quad indicator function of a convex set $C$;
-%% % \item $\Pi_C$: \quad euclidean projection operator onto a convex set $C$;
-%% \item $\|K\|_2$: \quad spectral norm of a matrix $K$
-%% % \item $F^*$: the convex conjugate of a convex function $F$.
-%% %% \item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
-%% %% \item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
-%% \end{itemize}
-
-%% \section{Statement of the problem}
-%% The Nash equilibrium problem for a two-person zero-sum sequential game with imcomplete information and perfect recall is a the saddle-point problem
-%% \begin{equation}
-%%   \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
-%%   \label{eq:opt_pb}
-%% \end{equation}
-
-%% where player $k$'s \textit{strategy profile} $Q_k$ is the polytope
-%% \begin{equation}
-%%   Q_k := \{z \in \mathbb{R}^{n_k}| E_kz = e_k\text{ and } z_j \ge 0 \text{ }\forall j\}
-%% \end{equation}
-%% for %% some convex subset $C_k$ of a euclidean space $\mathbb{R}^{n_k}$, and 
-%% some $p_k$-by-$n_k$ matrix $E_k$ and $p_k$-dimensional vector $e_k$. $A$ is the \textit{payoff matrix} from player 1's perspective of the game: if player 1 players strategy
-%% $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
-%% %% We will assume that the convex sets $C_k$ are simple enough so that the eucliean projection operators $\Pi_{C_k}$ can be cheaply computed.
-%% Typically, $C_k = \mathbb{R}^{p_k}_+ := \{x \in \mathbb{R}^n|x_k \ge 0\}$, the \textit{the nonnegative orthant}, and encodes a nonnegativity constraint.
-%% in this case, $\Pi_{C_k}(z) \equiv (z)_+$ as seen in subsection \ref{sec:notation}.
-%% As usual, the ``minimax'' notation in problem \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
-%% \begin{equation}
-%%   x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
-%% \end{equation}
-%% Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
-%% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
-
-%% We can distinguish two categories of such games, in terms of (non-)simultaneity of play.
-%% \paragraph{Simultaneous two-person zero-sum games}
-%% \label{subsec:example_games}
-%% Here, the Nash equilibrium problem takes the form \eqref{eq:opt_pb} with $p_k = 1$, $C_k = \mathbb{R}^{p_k}_+$, $E_k = 1_{1, n_k}$,
-%%   and $e_k = 1$, so that $Q_k$ is simply the probabability $n_k$-simplex $\Delta_{n_k}$. Each point in $\Delta_{n_k}$ corresponds to a \textit{mixed-strategy} for player $j$,
-%% and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_k}$).
-
-%% \paragraph{Two-person zero-sum sequential games with imcomplete information and perfect recall}
-%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:opt_pb}.
-
-%% We recall that in the sequence-form representation of such games,  $E_k$ is a matrix whose
-%% entries are $-1$, $0$, or $+1$, and $e_k := (1, 0, 0, ..., 0)$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
-%% encode linear constraints player 1's (resp. player 2's)  ``admissible'' \textit{realization plans} $x$ (resp. $y$).
-
-%% \paragraph{Example of Nash equilibirum}
-%% As an illustration, the pair $(x^*, y^*)$ given by
-%% $x^* = [1, .478, .522, .174, .826]^T$ and
-%% $y^* = [1, 1/2, 1/2]^T$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
-%% $A = \left[\begin{array}{ccc}
-%%   &   &  \\
-%%   &   &  \\
-%%   & 1 & -1\\
-%%   & -2 & 4\\
-%% 1 &   &  
-%% \end{array}\right]$, $E_1 = \left[\begin{array}{ccccc}
-%%   1 &   &   &   &  \\
-%%   -1 & 1 & 1 &   &  \\
-%%   -1 &   &   & 1 & 1
-%% \end{array}\right]$,
-%% $E_2 = \left[\begin{array}{ccc}
-%%   1 &   &  \\
-%%   -1 & 1 & 1
-%% \end{array}\right]$, $e_1 = [1, 0, 0]^T$, and $e_2 = [1, 0]^T$.
-
-\begin{remark}
-  The matrices $A$, $E_1$, and $E_2$ are very large (can have upto billions of rows and columns) but very sparse too.
-%% : $A$ will be sparse because a concrete sequential game will
-%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
-%% combinations of sequences of choices of the players, will actually lead to a leaf (i.e. end the game);
-%% $E$ and $F$ will be sparse because the kinks of possible sequences of choices of each player will
-%% zig-zag between only a limited number of the player's information sets so that a choice at an information set will
-%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
-This sparsity should be thoroughly exploited by a solver for problem \eqref{eq:opt_pb}.
-\end{remark}
-
-%% In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}.
-%% We elaborate our proposed algorithm in section \ref{sec:algo}.
-
-\section{Related work}
-\label{sec:related_work}
-EGT used in \cite{hoda2010smoothing}...
-
-\section{Useful convex analysis}
-\label{sec:notation}
-We will need the following notations and definitions in the sequel. Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
-the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros and $1_{m,n}$ denotes the $m$-by-$n$ matrix of ones.
-%% $\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_k \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegative orthant}.
-
-For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
-$(x)_+$ denotes its point-wise maximum with 0. Note that $(x)_+ \in \mathbb{R}^n_+$.
-For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$,
-denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).
-
-Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
-\begin{equation}
-  i_C(x) = \begin{cases}
-    0, &\mbox{if } x \in C\\
-    +\infty, &\mbox{otherwise}.
-    \end{cases}
-  \end{equation}
-
-Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection operator} onto $C$, denoted $\Pi_C$ is the function
-$\Pi: \mathbb{R}^n \mapsto C$, which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closed to $x$. Precisely,
-\begin{equation}
-  \Pi_C(x) := \underset{c \in C}{argimin}\text{ }\|c - x\|^2
-\end{equation}
-For example, the metric projections onto the nonnegative orthant and the closed unit-disk $\bar{\Delta}$
-% := \{x|\|x\| \le 1\}$
-are $\Pi_{\mathbb{R}^n_+}(x) \equiv (x)_+$ and $\Pi_{\bar{\Delta}}(z) \equiv \dfrac{z}{max(\|z\|, 1)}$ respectively.
-
-Let $f : \mathbb{R}^n \rightarrow [0, +\infty]$ be a \textit{proper convex lower semi-continous function}
-(\textit{p.c.l.s.c} for short), and $\tau$ a positive real number. The \textit{proximal operator} of $f$ of rank
-$\tau$, denoted $\text{prox}_{\tau f}$ is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
-unique) solution of the problem
-\begin{equation}
-  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
-\end{equation}
-
-It is easy to see that if $f$ is the indicator function of a convex set $C$, then $\text{prox}_{\tau f} = \Pi_C, \forall \tau > 0$. In this sense, proximal operators can be seen
-as a generalization of euclidean projection operators.
-
-\section{The algorithm}
-\label{sec:algo}
-We now derive our primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}.
-The algorithm is derived from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}.
-Though this scheme has recently gained considerable popularity in the signal processing community
-%\cite{gramfort-etal:2013a}
-, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.
-
-It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:opt_pb} lies in the difficulty of effectively computing the metric projections $\Pi_{Q_k}$.
-Theorem \ref{thm:pd} provides a trick to effectively evade this difficulty.
-
-\begin{theorem}
-  The Nash equilibrium problem \eqref{eq:opt_pb} can be re-written in the equivalent unconstrained form
-
-  \begin{equation}
-    \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{p_1}}{minimize}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{p_2}}{maximize}
-           {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}
-           \label{eq:unconstrained_pb}
-  \end{equation}
-
-  where $v \in \mathbb{R}^{p_1}$ and $u \in \mathbb{R}^{p_2}$ are auxiliary variables and 
-  \begin{equation}
-    \left .
-    \begin{split}
-      K :=
-      \left[
-        \begin{array}{c|c}
-          A & -E_1^T \\ \hline
-          E_2 & 0_{p_2, p_1}
-        \end{array}
-        \right] \in \mathbb{R}^{(n_1 + p_2) \times (n_2 + p_1)} \\
-      %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)}\\
-      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tv\\
-      H: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tu
-    \end{split}
-    \right\}
-    \label{eq:things}
-  \end{equation}
-
-  Moreover, $G$ and $H$ are \textit{p.c.l.s.c} and their proximal operators are given by
-  \begin{equation}
-    \left .
-    \begin{split}
-      \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{p_1}\\
-      (y, v) &\mapsto ((y)_+, v - \tau e_1)\\
-    \end{split}
-    \right\}
-  \end{equation}
-
-  and
-  \begin{equation}
-    \left .
-    \begin{split}
-      \text{prox}_{\sigma F}: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{p_2}\\
-      (x, u) &\mapsto ((x)_+, u - \sigma e_2)
-    \end{split}
-    \right\}
-  \end{equation}
-  \label{thm:pd}
-\end{theorem}
-
-%% Theorem \ref{thm:pd}, can be interpreted as follows: 2 players $x$ (player 1)  and $y$ (player 2) go heads-on in a zero-sum game with payoff matrix $A$.
-Their strategy, profiles are $Q_1$ and $Q_2$ respectively, meaning that if player $j$ players a strategy which is outside $Q_k$ then they are panalized by inflicting an infinite loss yupon them.
-To remedy this, they recruit assistants $u$ and $v$, whose sole goal is to preven the ...
-\begin{proof} First observe that $\forall (x, y) \in \mathbb{R}^{n_1} \times \mathbb{R}^{n_2}$, we have
-  \begin{eqnarray}
-    \left.
-    \begin{split}
-      -i_{Q_1}(x) = -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)}\\
-      i_{Q_2}(y) = i_{\mathbb{R}^{n_2}_+}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}
-      \end{split}
-    \right\}
-  \end{eqnarray}
-  Thus,% problem \eqref{eq:opt_pb} is equivalent to
-  \begin{eqnarray*}
-    \begin{split}
-  \underset{y \in Q_2}{min}\text{ }\underset{x \in Q_1}{max}\text{ }{x^TAy} &=
-  \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\left(\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }
-x^TAy - i_{Q_1}(x)\right) + i_{Q_2}(y) \\
-&= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }x^TAy -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)} + i_{\mathbb{R}^{n_2}_+}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}\\
-      &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }\underset{v \in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{min}\text{ }x^TAy - x^TE_1^Tv + u^TE_2y + i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tv -(i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tu)\\
-      &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ } \underset{v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{max}
-      {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}\\
-      &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }
-\underset{u \in \mathbb{R}^{p_2}}{max}
-      {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}\\
-      &=     \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{p_2}}{max}
-           {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}
-    \end{split}
-  \end{eqnarray*}
-where $K$, $G$, and $H$ are as given in \eqref{eq:things}. Thus problem \eqref{eq:opt_pb} is equivalent to problem \eqref{eq:unconstrained_pb} as claimed.
-
-About the proximal operators, indeed both $G$ and $F$ are separable sums of the indicator function of a convex set, whose prox is simply the euclidean projection operator onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox, at rank $\tau$, is simply $z \mapsto z - \tau a$.
-\end{proof}
-Now applying Algorithm 39 of \cite{chambolle2010} with $F := H^*$ (the \textit{convex conjugate} of $H$)
- to problem \eqref{eq:unconstrained_pb}, we obtain Algorithm \ref{Tab:algo_simplified} for solving the original problem \eqref{eq:opt_pb}.
-The $\mathcal{O}(1/\epsilon)$ convergence rate of Algorothm \ref{Tab:algo_simplified} hails directly from Theorem 1 of \cite{chambolle2010}.
-\begin{remark}
-  Note that the convergence rate of $\mathcal{O}(1/\epsilon)$ cannot be improved in the framework of \cite{chambolle2010}, since neither $G$ nor $H$ is \textit{uniformly convex}.
-\end{remark}
-
-%% \subsection{Special case: $C_k = \mathbb{R}^{n_k}_+$} As discussed in subsection \ref{subsec:example_games},
-%% the Nash equilibrium problem for two-person zero-sum simultaneous games and two-person zero-sum sequential games with imcomplete
-%% information and perfect recall admits the formulation \eqref{eq:opt_pb}, with $C_k = \mathbb{R}^{n_k}_+$ (coding for nonnegativity constraints).
-%% In such situations, $\Pi_{C_k}(z) \equiv (z)_+$ as already mentioned in \ref{sec:notation}, and Algorithm \ref{Tab:algo} reduces to the simpler Algorithm \ref{Tab:algo_simplified}.
-
-\begin{algorithm}[htb]
-  \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}}
-  \textbf{require}
-  \begin{itemize}
-    \item the specification of a game $(A, E_1, E_2, e_1, e_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
-  $E_1 \in \mathbb{R}^{p_1 \times n_1}$, $E_2 \in \mathbb{R}^{p_2 \times n_2}$, $e_1 \in \mathbb{R}^{p_1}$, $e_2 \in \mathbb{R}^{p_2}$;
-      \item a tolerance level $\epsilon > 0$
-  \end{itemize}
-  \textbf{precompute} $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
-  \textbf{initialize}
-  $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{p_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{p_2}$; 
-  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
-  \Repeat{$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$}{
-    \begin{eqnarray*}
-      x^{(k+1)} &\leftarrow& \left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)_+\\
-      u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
-      y^{(k+1)} &\leftarrow& \left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)_+\\
-      v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
-      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
-      \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
-      k &\leftarrow& k + 1
-    \end{eqnarray*}
-  } \Return $x^{(k)}$, $y^{(k)}$
-  \label{Tab:algo_simplified}
-\end{algorithm}
-
-\section{Application to Poker: Kuhn Poker}
-\label{sec:kuhn}
+\paragraph{Solution}
 The pair $(x^*, y^*)$ of realization plans given by\\
 $x^* = [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T$ and
-$y^* = [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash equlibrium for the Kuhn Poker presented in \ref{sec:kuhn_sf}, computed using Algorithm  \ref{Tab:algo_simplified}.
-The convergence curve is shown in Fig \ref{Tab:conv_curves}.
+$y^* = [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash $10^{-4}$-equlibrium.
+computed by Algorithm  \ref{Tab:algo_simplified}.
+The convergence curve is shown in Fig \ref{Tab:dgap_curve}.
 One easy checks that this equilibrium is feasible.
@@
 
+The evolution of the dual gap and the expected value of the game across iterations is shown in Figure \ref{Tab:dgap_curve}.
+These figures validates the theoritically established $\mathcal{O}(1/\epsilon)$ convergence rate of the Algorithm.
+
 \begin{figure}
+  \includegraphics[width=1\linewidth]{Kuhn3112_dgap.pdf}
   \includegraphics[width=1\linewidth]{Kuhn3112_NE.pdf}
-  % \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
-  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} on Kuhn Poker}
-  \label{Tab:conv_curves}
+  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} on Kuhn 3-card Poker}
+  \label{Tab:dgap_curve}
 \end{figure}
 
-\section{Extending to games with more general strategy profiles}
-\label{sec:algo_gen}
-Notice tha in \eqref{eq:poly}, the strategy profile of player $k$ can be factored as
-\begin{equation}
-  Q_k := \{z \in \mathbb{R}^{n_k}_+| E_kz = e_k\text\}
-\end{equation}
+%% \section{Extending to games with more general strategy profiles}
+%% \label{sec:algo_gen}
+%% Notice tha in \eqref{eq:poly}, the strategy profile of player $k$ can be factored as
+%% \begin{equation}
+%%   Q_k := \{z \in \mathbb{R}^{n_k}_+| E_kz = e_k\text\}
+%% \end{equation}
 
-The framework presented sofar only demanded we be able to efficiently compute metric projections onto the nonnegative orthant $\mathbb{R}^{n_k}_+$, namely nonnegative clipping.
+%% The framework presented sofar only demanded we be able to efficiently compute metric projections onto the nonnegative orthant $\mathbb{R}^{n_k}_+$, namely nonnegative clipping.
 This opens perspectives to envisage general two-person zero sum games for which the players' strategy profiles are of the form
-\begin{equation}
-  Q_k := \{z \in C_k| E_kz = e_k\text\}
-  \label{eq:q_gen}
-\end{equation}
-where the $C_k$ are arbitrary convex sets for which the metric projections $\Pi_{C_k}$ can be effectively computed.
-% \paragraph{Example: Computing best response strategies}
+%% \begin{equation}
+%%   Q_k := \{z \in C_k| E_kz = e_k\text\}
+%%   \label{eq:q_gen}
+%% \end{equation}
+%% where the $C_k$ are arbitrary convex sets for which the metric projections $\Pi_{C_k}$ can be effectively computed.
+%% % \paragraph{Example: Computing best response strategies}
 
-As a motivating example, suppose Alice knows a priori that Bob is playing a given realization plan $y_0 \in Q_2$ (for example, take $y_0 = [1, 0, ..., 0]^T \in \mathbb{R}^{n_2}$).
+%% As a motivating example, suppose Alice knows a priori that Bob is playing a given realization plan $y_0 \in Q_2$ (for example, take $y_0 = [1, 0, ..., 0]^T \in \mathbb{R}^{n_2}$).
 Alice seeks a \textit{best response strategy}, namely a strategy $x^* \in Q_1$ such that
-\begin{equation}
-  x^TAy_0 \le {x^*}^TAy_0,\text{ } \forall x \in Q_1
-\end{equation}
+%% \begin{equation}
+%%   x^TAy_0 \le {x^*}^TAy_0,\text{ } \forall x \in Q_1
+%% \end{equation}
 
-One observes that this problem is an instance of problem \eqref{eq:opt_pb} with
-$Q_2 = \{y_0\} = \{z \in C_2| E_2z = e_2\text\}$ and $C_2 = \{y_0\}$. Of course the metric projection on $C_2$ is simply the constant map $y \mapsto y_0$.
+%% One observes that this problem is an instance of problem \eqref{eq:primal_pb} with
+%% $Q_2 = \{y_0\} = \{z \in C_2| E_2z = e_2\text\}$ and $C_2 = \{y_0\}$. Of course the metric projection on $C_2$ is simply the constant map $y \mapsto y_0$.
 
-As another motivating example, suppose we know the support ...
+%% As another motivating example, suppose we know the support ...
 
-We have the following generalization of Theorem \ref{thm:pd}.
+%% Indeed we have the following generalization of Theorem \ref{thm:pd} for Nash equilibrium problems in which the strategy  profiles have the generic form \eqref{eq:q_gen}.
+%% \begin{theorem}
+%%   The Nash equilibrium problem \eqref{eq:primal_pb} with strategy profiles given by  equation \eqref{eq:q_gen}, can be re-written in the equivalent unconstrained form
 
-\begin{theorem}
-  The Nash equilibrium problem \eqref{eq:opt_pb} with strategy profiles given by  equation \eqref{eq:q_gen}, can be re-written in the equivalent unconstrained form
+%%   \begin{equation}
+%%     \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{l_1}}{minimize}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{l_2}}{maximize}
+%%            {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}
+%%            \label{eq:unconstrained_gen_pb}
+%%   \end{equation}
 
-  \begin{equation}
-    \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{p_1}}{minimize}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{p_2}}{maximize}
-           {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}
-           \label{eq:unconstrained_pb}
-  \end{equation}
+%%   where $v \in \mathbb{R}^{l_1}$ and $u \in \mathbb{R}^{l_2}$ are auxiliary variables and 
+%%   \begin{equation}
+%%     \left .
+%%     \begin{split}
+%%       K :=
+%%       \left[
+%%         \begin{array}{c|c}
+%%           A & -E_1^T \\ \hline
+%%           E_2 & 0_{l_2, l_1}
+%%         \end{array}
+%%         \right] \in \mathbb{R}^{(n_1 + l_2) \times (n_2 + l_1)} \\
+%%       %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + l_1) \times (n_1 + l_2)}\\
+%%       G: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow [-\infty, +\infty], (y, v) \mapsto i_{C_2}(y) + e_1^Tv\\
+%%       H: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow [-\infty, +\infty], (x, u) \mapsto i_{C_1}(x) + e_2^Tu
+%%     \end{split}
+%%     \right\}
+%%     \label{eq:things}
+%%   \end{equation}
 
-  where $v \in \mathbb{R}^{p_1}$ and $u \in \mathbb{R}^{p_2}$ are auxiliary variables and 
-  \begin{equation}
-    \left .
-    \begin{split}
-      K :=
-      \left[
-        \begin{array}{c|c}
-          A & -E_1^T \\ \hline
-          E_2 & 0_{p_2, p_1}
-        \end{array}
-        \right] \in \mathbb{R}^{(n_1 + p_2) \times (n_2 + p_1)} \\
-      %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)}\\
-      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [-\infty, +\infty], (y, v) \mapsto i_{C_2}(y) + e_1^Tv\\
-      H: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [-\infty, +\infty], (x, u) \mapsto i_{C_1}(x) + e_2^Tu
-    \end{split}
-    \right\}
-    \label{eq:things}
-  \end{equation}
+%%   Moreover, $G$ and $H$ are \textit{p.c.l.s.c} and their proximal operators are given by
+%%   \begin{equation}
+%%     \left .
+%%     \begin{split}
+%%       \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\\
+%%       (y, v) &\mapsto (\Pi_{C_2}(y), v - \tau e_1)\\
+%%     \end{split}
+%%     \right\}
+%%   \end{equation}
 
-  Moreover, $G$ and $H$ are \textit{p.c.l.s.c} and their proximal operators are given by
-  \begin{equation}
-    \left .
-    \begin{split}
-      \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{p_1}\\
-      (y, v) &\mapsto (\Pi_{C_2}(y), v - \tau e_1)\\
-    \end{split}
-    \right\}
-  \end{equation}
+%%   and
+%%   \begin{equation}
+%%     \left .
+%%     \begin{split}
+%%       \text{prox}_{\sigma F}: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}\\
+%%       (x, u) &\mapsto (\Pi_{C_1}(x), u - \sigma e_2)
+%%     \end{split}
+%%     \right\}
+%%   \end{equation}
+%%   \label{thm:pd_gen}
+%% \end{theorem}
 
-  and
-  \begin{equation}
-    \left .
-    \begin{split}
-      \text{prox}_{\sigma F}: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{p_2}\\
-      (x, u) &\mapsto (\Pi_{C_1}(x), u - \sigma e_2)
-    \end{split}
-    \right\}
-  \end{equation}
-  \label{thm:pd_gen}
-\end{theorem}
+%% \begin{proof}
+%% Totally analogous to the proof of Theorem \ref{thm:pd} with $\mathbb{R}^{n_k}_+$ replaced with $C_k$,
+%% $i_{\mathbb{R}^{n_k}_+}$ replaced with $i_{C_k}$, and $\Pi_{\mathbb{R}^{n_k}_+}$ (nonnegative clipping) replaced with $\Pi_{C_k}$.
+%% \end{proof}
 
-\begin{proof}
-Totally analogous to the proof of Theorem \ref{thm:pd} with $\mathbb{R}^{n_k}_+$ replaced with $C_k$,
-$i_{\mathbb{R}^{n_k}_+}$ replaced with $i_{C_k}$, and $\Pi_{\mathbb{R}^{n_k}_+}$ (nonnegative clipping) replaced with $\Pi_{C_k}$.
-\end{proof}
-
-%\paragraph{$\mathcal{O}(1/\epsilon)$ primal-dual algorithm for general problems}
-Analogous to Algorithm \ref{Tab:algo_simplified}, we obtain Algorithm \ref{Tab:algo} for solving the Nash equilibrium problem \ref{eq:opt_pb} with the general strategy profiles $Q_k$ defined in \eqref{eq:q_gen}.
+%% %\paragraph{$\mathcal{O}(1/\epsilon)$ primal-dual algorithm for general problems}
+%% Analogous to Algorithm \ref{Tab:algo_simplified}, we obtain Algorithm \ref{Tab:algo} for solving the Nash equilibrium problem \ref{eq:primal_pb} with the general strategy profiles $Q_k$ defined in \eqref{eq:q_gen}.
 Just like Algorithm \ref{Tab:algo_simplified}, Algorithm \ref{Tab:algo} has a $\mathcal{O}(1/\epsilon)$ convergence rate.
 
-\begin{algorithm}[htb]
-  \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}, with general strategy profiles as defined in \eqref{eq:q_gen}}
-  \textbf{require}
-  \begin{itemize}
-    \item the specification of a game $(A, E_1, E_2, e_1, e_2, C_1, C_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
-  $E_1 \in \mathbb{R}^{p_1 \times n_1}$, $E_2 \in \mathbb{R}^{p_2 \times n_2}$, $e_1 \in \mathbb{R}^{p_1}$, $e_2 \in \mathbb{R}^{p_2}$, each $C_k$ is a convex subset of $\mathbb{R}^{n_k}$, as in the definition of the strategy profiles $Q_k$ in equation \eqref{eq:q_gen};
-      \item a tolerance level $\epsilon > 0$
-  \end{itemize}
-  \textbf{precompute} $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
-  \textbf{initialize}
-  $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{p_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{p_2}$; 
-  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
-  \Repeat{$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$}{
-    \begin{eqnarray*}
-      x^{(k+1)} &\leftarrow& \Pi_{C_1}\left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)\\
-      u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
-      y^{(k+1)} &\leftarrow& \Pi_{C_2}\left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)\\
-      v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
-      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
-      \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
-      k &\leftarrow& k + 1
-    \end{eqnarray*}
-  } \Return $x^{(k)}$, $y^{(k)}$
-  \label{Tab:algo}
-\end{algorithm}
+%% \begin{algorithm}[H]
+%%   \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:primal_pb}, with general strategy profiles as defined in \eqref{eq:q_gen}}
+%%   \KwIn{specification of a game $(A, E_1, E_2, e_1, e_2, C_1, C_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
+%%       $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, $e_1 \in \mathbb{R}^{l_1}$, $e_2 \in \mathbb{R}^{l_2}$, each $C_k$ is a convex subset of $\mathbb{R}^{n_k}$, as in the definition of the strategy profiles $Q_k$ in equation \eqref{eq:q_gen}}
+%%   \KwOut{Nash $\epsilon-$equilibrium pair $x^{(k)}$, $y^{(k)}$}
+%%   \textbf{Precompute}: $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
+%%   \textbf{Initialize}:
+%%   $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{l_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{l_2}$; 
+%%   $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
+%%   \While{
+%% %$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$
+%% $|e_1^Tp^{(k)} - e_2^Tq^{(k)}| \geq \epsilon$}{
+%%     \begin{eqnarray*}
+%%       x^{(k+1)} &\leftarrow& \Pi_{C_1}\left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)\\
+%%       u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
+%%       y^{(k+1)} &\leftarrow& \Pi_{C_2}\left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)\\
+%%       v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
+%%       \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
+%%       \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
+%%       k &\leftarrow& k + 1
+%%     \end{eqnarray*}
+%%   }
+%%   \label{Tab:algo}
+%% \end{algorithm}
 
@@
 \textbf{Acknowledgments:}
-Pending...
-
 \small

### 2015-01-06 primal_dual.py

@@ -3,8 +3,10 @@
 #
 # author: DOHMATOB Elvis
 
+import warnings
 from math import sqrt
 import numpy as np
+from scipy import linalg
 
 
 def power(A, p, max_iter=100, **kwargs):
@@ -21,9 +23,41 @@ def power(A, p, max_iter=100, **kwargs):
     return lambd
 
 
+def evil(L, r, z, proj_C=lambda v: np.maximum(v, 0.), L_norm=None,
+         max_iter=100, verbose=1, tol=1e-4):
+    """Projects the point z onto the intersection of the polyhedron "Lx=r"
+    and the convex set C.
+
+    References
+    ----------
+    P. Combettes et al, "Dualization of Signal Recovery Problems", p.17
+    """
+    if L_norm is None:
+        L_norm = linalg.svdvals(L)[0]
+    gamma = .99 / L_norm ** 2
+    v = np.zeros(L.shape[0])
+    x = np.zeros(L.shape[1])
+    salt = 1e-4
+    for k in xrange(max_iter):
+        old_x = x.copy()
+        x = proj_C(z - L.T.dot(v)) + salt
+        v += gamma * (L.dot(x) - r + salt)
+        salt *= .5  # we want: \sum_{k}{salt_k} < \infty
+        error = sqrt(((x - old_x) ** 2).sum())
+        if verbose:
+            print "\tIteration %03i/%03i: x=%s, error=%5.2e" % (
+                k + 1, max_iter, x, error)
+        if error < tol and 1:
+            if verbose:
+                print "\tConverged after %i iterations." % (k + 1)
+            break
+    return x
+
+
 def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
-                   proj_C2=lambda y: np.maximum(y, 0.),
-                   L=None, max_iter=1500, tol=1e-4):
+                   proj_C2=lambda y: np.maximum(y, 0.), init=None,
+                   tol=1e-8, max_iter=10000, inertia=None, rho=None,
+                   good_init=False):
     """Primal-Dual algorithm for computing Nash equlibrium for two-person
     zero-sum game with payoff matrix A and contraint sets
 
@@ -34,76 +68,137 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
         minimize maximize <x, Ay>
         y in Q2  x in Q1
     """
+    # sanitize rho and inertia
[…]

### 2015-01-06 simple.py

@@ -5,8 +5,7 @@ from nose.tools import assert_equal, assert_true
 import networkx as nx
 import numpy as np
 import matplotlib.pyplot as plt
-# from sequential_games import compute_ne
-from primal_dual import primal_dual_ne
+from primal_dual import primal_dual_ne, primal_dual_sg_ne
 
 
 class Game(object):
@@ -451,7 +450,7 @@ class Game(object):
         # leaf (terminal) nodes
         leaf_nodes = [node for node in self.tree.nodes() if self.is_leaf(node)]
         nx.draw_networkx_nodes(self.tree, pos, nodelist=leaf_nodes,
-                               node_shape='s', node_color="k")
+                               enode_shape='s', node_color="k")
 
         # decision nodes
         dec_nodes = [node
@@ -906,16 +905,26 @@ def test_nash_player():
 
 
 if __name__ == "__main__":
-    for game_cls in [SimplifiedPoker, Kuhn3112]:
-        game = game_cls()
-        E1, e1 = game.constraints[1]
-        E2, e2 = game.constraints[2]
-        A = game.payoff_matrix
-        x, y, values = primal_dual_ne(A, E1, E2, e1, e2)
+    for game_cls in [SimplifiedPoker, Kuhn3112, "simplex"][1:]:
+        if game_cls == "simplex":
+            game = None
+            name = game_cls
+            A = np.random.uniform(-1, 1, size=(1000, 1000))
+            x, y, values, dgaps = primal_dual_sg_ne(A)
+        else:
+            game = game_cls()
+            name = game.__class__.__name__
+            E1, e1 = game.constraints[1]
+            E2, e2 = game.constraints[2]
+            A = game.payoff_matrix
+            args = (A, E1, E2, e1, e2)
+            x, y, values, dgaps = primal_dual_ne(A, E1, E2, e1, e2)
         print
         print "Nash Equilibrium:"
         print "x* = ", x
         print "y* =", y
+
+        # plot evoluation of game value
         plt.figure(figsize=(13.5, 10))
         plt.semilogx(values, linewidth=4)
         value = values[-1]
@@ -931,9 +940,25 @@ if __name__ == "__main__":
         # plt.title("%s: Sequence-form NE computation" % (
         #         game.__class__.__name__))
         plt.tick_params(axis='both', which='major', labelsize=20)
[…]

### 2015-01-06 simple.py
typos

@@ -949,7 +949,7 @@ if __name__ == "__main__":
         plt.loglog(np.abs(dgaps), label="Primal-Dual", linewidth=4)
         plt.xlabel("$k$", fontsize=25)
         plt.ylabel(
-            "Duality gap $|e_1^Tp^{(k)} - e_2^Tq^{(k)}|$",
+            "Duality gap $|e_1^Tp^{(k)} + e_2^Tq^{(k)}|$",
             fontsize=25)
         plt.legend(loc="best", prop=dict(size=25))
         plt.tick_params(axis='both', which='major', labelsize=20)

### 2015-01-08 nips2015.tex
typos
WIP

@@
 
-\paragraph{Nash equilibrium problem in sequence-form}
-In \cite{von1996efficient, vonequilibrium}, it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exists sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}, E_1 \in \mathbb{R}^{l_1 \times n_1}, E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to points $(x, y)$ which solve the primal LCP (Linear Constrained Programming) problem
+In \cite{von1996efficient, vonequilibrium}, it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}, E_1 \in \mathbb{R}^{l_1 \times n_1}, E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to pairs $(x, y)$ of \textit{realization plans} which solve the primal LCP (Linear Constrained Programming) problem
 \begin{equation}
@@
 
-with duality gap given by
+with \textit{duality gap} given by
 \begin{equation}
@@
 
-Of course by \textit{weak duality} in problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb},, it holds that
+Of course by \textit{weak duality} in problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb}, it holds that
 \begin{equation}
@@
 
-It was also shown (for example, Theorem 3.14 of \cite{vonequilibrium}) that a $(x, y)$ is a solution to the primal-dual problem \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff there exists vectors $p$ and $q$ such that
+It was also shown (for example, Theorem 3.14 of \cite{vonequilibrium}) that a $(x, y)$ is a solution to the primal-dual problem \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff there exist vectors $p$ and $q$ such that
 \begin{equation}
@@
 
-Moreover, in this case \textit{strong duality} holds and the value of the game equals $e_1^Tp = -e_2^Tq$,
-In this case, the duality gap defined in \eqref{eq:dgap} vanishes.
+Moreover, in this case \textit{strong duality} holds and the value of the game equals $e_1^Tp = -e_2^Tq$; thus the duality gap $\mathcal{G}(p, q)$ defined in \eqref{eq:dgap} vanishes.
 
@@
 In section \ref{sec:algo} we derive the proposed algorithm for solving this problem and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.
-This is followed by a demonstration on Kuhn Poker in section \ref{sec:kuhn}.
-In section \ref{sec:algo_gen}, we extend  the algorithm to problems with more general strategy profiles, and exhibit thesame convergence properties.
+With construct with a demonstration on Kuhn 3-card Poker.
 
@@
 \label{sec:related_work}
-EGT used in \cite{hoda2010smoothing}...
+In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique \cite{nesterov2005excessive} was used to to solve the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form
+
+\begin{equation}
+  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in Q_1}{\text{maximize}}\text{ }x^TAy
+\end{equation}
+
+They authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate (which derives from the general EGT theory) for the outer-most iteration loop, though the cost of an iteration is presumably heavy since it entails computing a $softmax$ at each iteration.
 
@@
 \label{sec:notation}
-We will need the following notations and definitions in the sequel. Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
+We will need the following notations in the sequel. Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
 the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros and $1_{m,n}$ denotes the $m$-by-$n$ matrix of ones.
@@
 
-Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection operator} onto $C$, denoted $\Pi_C$ is the function
-$\Pi: \mathbb{R}^n \mapsto C$, which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closed to $x$. Precisely,
+Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection operator} onto $C$, denoted $\Pi_C$, is the function
+$\Pi: \mathbb{R}^n \mapsto C$ which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closest to $x$. Precisely,
 \begin{equation}
@@
 \end{equation}
-For example, the metric projections onto the nonnegative orthant and the closed unit-disk $\bar{\Delta}$
+For example, the euclidean projections onto the nonnegative orthant and the closed unit-disk $\bar{\Delta}$
 % := \{x|\|x\| \le 1\}$
@@
 \begin{equation}
-  f^*(x) := \underset{z \in \mathbb{R}^n}{\text{max}}\text{ }z^Tx - f(x)
+  x \mapsto f^*(x) := \underset{z \in \mathbb{R}^n}{\text{max}}\text{ }z^Tx - f(x)
 \end{equation}
+
+For example $i_{\mathbb{R}^{n}_+}^*(x) \equiv i_{\mathbb{R}^{n}_+}(-x)$; $(a^Tx)^* \equiv i_{\{0\}}(x - a)$; and $(\frac{1}{2}\|x\|^2)^* \equiv \frac{1}{2}\|x\|^2$.
+One easily verifies that $f^{**} = f$.
 
@@
 We now derive our primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:primal_pb}.
-The algorithm is derived from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}.
+The algorithm is obtained from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}.
 Though this scheme has recently gained considerable popularity in the signal processing community
@@
 
-It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing the metric projections $\Pi_{Q_k}$.
+It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing the euclidean projections $\Pi_{Q_k}$.
 Theorem \ref{thm:pd} provides a trick to effectively evade this difficulty.
@@
 \begin{theorem}
-  The Nash equilibrium LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} can be re-written in the saddle-point form
+  The Nash equilibrium LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} can be re-written in the saddle-point convex-concove form
 
@@
 
-Now,
+Now, one computes
 \begin{equation}
   \begin{split}
-    H^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right) := \underset{x,q}{\text{max}}\text{ }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} - H(x, q) &= \underset{x, q}{\text{max}}\text{ }x^T(Ay - E_1^Tp) - i_{\mathbb{R}^{n_1}_+}(x) + q^TE_2y - f^Tq\\
-      &= \underset{x \geq 0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) + \underset{q}{\text{max}}\text{ }q^TE_2y - f^Tq\\
+    H^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right) &= \underset{x,q}{\text{max}}\text{ }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} - H(x, q) \\
+      &= \underset{x, q}{\text{max}}\text{ }x^T(Ay - E_1^Tp) - i_{\mathbb{R}^{n_1}_+}(x) + q^TE_2y - f^Tq\\
+      &= \underset{x \geq 0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) + \underset{q}{\text{max}}\text{ }q^T(E_2y - f)\\
       &= i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)
@@
 
-But this two last equations are simply the primal and dual formulations of the saddle-point problem \eqref{eq:unconstrained_pb}, and we are done.
+But these last two equations are simply the primal and dual formulations of the saddle-point problem \eqref{eq:unconstrained_pb}, and we are done.
 
@@
 %$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$
-$|e_1^Tp^{(k)} - e_2^Tq^{(k)}| \geq \epsilon$}{
+$|e_1^Tp^{(k)} + e_2^Tq^{(k)}| \geq \epsilon$}{
     \begin{eqnarray*}
@@
 \section{Results}
-\paragraph{Simulated game}
+\paragraph{Simulated game: matrix game on simplexes}
+Any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a 
+As in \textbf{nesterov, c-p, etc.}, we generate a $1000 \times 1000$ random matrix whose entries are uniformly identically distributed in the closed interval $[-1, 1]$.
 See Figure \ref{Tab:sim_dgap_curve}.
@@
 
-%% The framework presented sofar only demanded we be able to efficiently compute metric projections onto the nonnegative orthant $\mathbb{R}^{n_k}_+$, namely nonnegative clipping.
+%% The framework presented sofar only demanded we be able to efficiently compute euclidean projections onto the nonnegative orthant $\mathbb{R}^{n_k}_+$, namely nonnegative clipping.
 This opens perspectives to envisage general two-person zero sum games for which the players' strategy profiles are of the form
@@
 %% \end{equation}
-%% where the $C_k$ are arbitrary convex sets for which the metric projections $\Pi_{C_k}$ can be effectively computed.
+%% where the $C_k$ are arbitrary convex sets for which the euclidean projections $\Pi_{C_k}$ can be effectively computed.
 %% % \paragraph{Example: Computing best response strategies}
@@
 %% One observes that this problem is an instance of problem \eqref{eq:primal_pb} with
-%% $Q_2 = \{y_0\} = \{z \in C_2| E_2z = e_2\text\}$ and $C_2 = \{y_0\}$. Of course the metric projection on $C_2$ is simply the constant map $y \mapsto y_0$.
+%% $Q_2 = \{y_0\} = \{z \in C_2| E_2z = e_2\text\}$ and $C_2 = \{y_0\}$. Of course the euclidean projection on $C_2$ is simply the constant map $y \mapsto y_0$.
 

### 2015-01-08 simple.py

@@ -969,4 +969,4 @@ if __name__ == "__main__":
         # game.draw()
         # plt.title("Game tree (T) for %s" % game.__class__.__name__)
 
-    # plt.show()
+    plt.show()

### 2015-01-11 nips2015.tex
ENH: getting ready for arxiv

@@
 \begin{abstract}
-We present a simple primal-dual algorithm with a low cost per iteration, for computing Nash $\epsilon$-equilibria for two-person zero-sum sequential games like Texas Hold'em Poker, in $\mathcal{O}(1/\epsilon)$ iterations.
+We present a simple primal-dual algorithm with a low cost per iteration, for computing Nash $\epsilon$-equilibria for two-person zero-sum sequential games like Texas Hold'em Poker, which converges --in duality gap-- after $\mathcal{O}(1/\epsilon)$ basic iterations (i.e iterations only involving basic operations like matvec, clipping, etc., and no calls to external oracles).
 %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall.
@@
  projections (the proximal operators) thereupon.
-Our technique is to dualize the linear constraints that form part of the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme, without any additional overhead.
+Our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme, without any additional overhead.
 The resulting algorithm is simple, only involving matrix-vector multiplications
@@
 Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing}, our algorithm has a cheap and constant cost per iteration.
-As proof of concept, we apply our algorithm to solve Kuhn Poker.
+As proof of concept, we apply our algorithm to solve Kuhn 3-card Poker \cite{kuhn}.
 %% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
@@
 For sequential games with imcomplete information and perfect recall like Texas Hold'em Poker, von Stengel and co-workers have developed the \textit{sequence-form} representation (see \cite{von1996efficient} and references therewithin), whose size is linear in the size of the game tree, in contrast with the \textit{strategic-form} representation which is exponential.
-The goal of this paper is to develop a fast and simple primal-dual algorithm for computing Nash equilibria for such games, using this representation.
+The goal of this paper is to develop a fast and simple primal-dual algorithm for computing  Nash $\epsilon$-equilibria for such games, using this representation.
 
+\subsection{Context}
 In \cite{von1996efficient, vonequilibrium}, it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}, E_1 \in \mathbb{R}^{l_1 \times n_1}, E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to pairs $(x, y)$ of \textit{realization plans} which solve the primal LCP (Linear Constrained Programming) problem
@@
 
-with \textit{duality gap} given by
+with \textit{duality gap} given by\footnote{The last inequality being due to \textit{week duality}.}
 \begin{equation}
-  \mathcal{G}(p, q) := e_1^Tp - (-e_2^Tq) = e_1^Tp + e_2^Tq
+  \mathcal{G}(p, q) := e_1^Tp - (-e_2^Tq) = e_1^Tp + e_2^Tq \geq 0
   \label{eq:dgap}
@@
   Q_k := \{z \ge 0\text{ }|\text{ }E_kz = e_k\} \subseteq \mathbb{R}^{n_k}
+\label{eq:polytope}
 \end{equation}
-
-Of course by \textit{weak duality} in problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb}, it holds that
-\begin{equation}
-  \mathcal{G}(p, q) \geq 0
-\end{equation}
-for any fixed pair $(x, y)$ of realization plans and admissible dual pair $(p,q)$ in problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb}.
 
@@
 %% We can distinguish two categories of such games, in terms of (non-)simultaneity of play.
-%% \paragraph{Simultaneous two-person zero-sum games}
+%% \subsection{Simultaneous two-person zero-sum games}
 %% \label{subsec:example_games}
@@
 
-%% \paragraph{Two-person zero-sum sequential games with imcomplete information and perfect recall}
+%% \subsection{Two-person zero-sum sequential games with imcomplete information and perfect recall}
 %% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:primal_pb}.
@@
 
-%% \paragraph{Example of Nash equilibirum}
+%% \subsection{Example of Nash equilibirum}
 %% As an illustration, the pair $(x^*, y^*)$ given by
@@
 
+\subsection{Statement of the problem}
 Solving problem \eqref{eq:primal_pb} exactly is impossible in practice, and such a precision doesn't have any fundamental advantage.
@@
 
-\paragraph{Outline of article}
 The goal of this article is to device a simple algorithm which produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations%We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation.
@@
 Then in
-In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:approx_pb}.
+
+\subsection{Outline of the article}
+In section \ref{sec:rep} we briefly review the sequence-form representation.
+In section \ref{sec:related_work}, we give a brief overview of existing methods for computing Nash $\epsilon$-equilibria.
+Section \ref{sec:notation} features useful notions of convex optimization (proximal operators, convex conjugates, etc.).
 In section \ref{sec:algo} we derive the proposed algorithm for solving this problem and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.
-With construct with a demonstration on Kuhn 3-card Poker.
+We conclude with a demonstration on Kuhn 3-card Poker \cite{kuhn}.
 
@@
 
-%%%
-%% \section{The sequence-form representation}
-%% \label{sec:rep}
-%% \paragraph{Recap: Extensive-form representation} The game tree $\mathcal{T}$ is defined as follows.
+\section{The sequence-form representation}
+\label{sec:rep}
+In this section, we briefly recall the sequence-form representation of sequential games with imcomplete information and perfect recall.
+A complete overview of the subject can be found in the pioneering work \cite{von1996efficient}.
+\subsection{Recap: Extensive-form representation} The game tree $\mathcal{T}$ is defined as follows.
 There are three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}.
@@
 Nodes of the game tree $\mathcal{T}$ are identified with states of the game, and actions taken by players correspond to edges of $\mathcal{T}$.
-%% The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops.
+The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops.
 %% The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
-%% At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node.
+At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node.
 This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts.
@@
 
-%% $a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
-%% receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
-%% The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
-%% We will assume implicitly that each (non-chance) player is rational.
+$a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
+receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
+The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
+We will assume implicitly that each (non-chance) player is rational.
 
-%% A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts.
+A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts.
 The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.
 
-%% \paragraph{From extensive-form to sequence-form representation}
-%% For each information set $h$ of player $k$, $\sigma_h$ (unique and well-defined, by the  is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players.
+\subsection{From extensive-form to sequence-form representation}
+For each information set $h$ of player $k$, $\sigma_h$ (unique and well-defined, by the  is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players.
 \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined.
@@
 The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by
-%% \begin{equation}
-%% \mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
-%% \end{equation}
-%% Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish.
+\begin{equation}
+\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
+\end{equation}
+Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish.
 $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
-%% $\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.
+$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.
 
-%% Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$, and their \textit{mixed-strategies} are randomizations on these pure-strategies.
-In sequence-form, the strategy profile $Q_k$ of player $k \ge 1$ is the polytope of $n_k$-dimensional nonnegative vectors satisying
-%% % Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
-%% \begin{equation}
-%%     z(\emptyset) = 1 \text{ and }
-%%     z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
-%%   \label{eq:lin}
-%% \end{equation}
+Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$, and their \textit{mixed-strategies} are randomizations on these pure-strategies.
+In sequence-form, the strategy profile of player $k \ge 1$ is the polytope of $n_k$-dimensional nonnegative vectors $z$ (a realization plan) satisfying
+% Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
+\begin{equation}
+  z \geq 0,\hspace{1em}z(\emptyset) = 1,\hspace{1em}
+    z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
+  \label{eq:lin}
+\end{equation}
 
-%% These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
-%% where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$.
-Thus we can re-write
+These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
+where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$.
+The polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}.
+Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
+\begin{equation}
+  \beta_k(h, c) := \begin{cases}
+    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
+    0, &\mbox{Otherwise}.
+  \end{cases}
+\end{equation}
 
-%% \begin{equation}
-%%   Q_k := \{z \in \mathbb{R}^{n_k}| z \ge 0\text{ and }E_kz = e_k\}
-%%   \label{eq:poly}
-%% \end{equation}
+From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.
 
-%% Each point $z \in Q_k$ is called a \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
-%% \begin{equation}
-%%   \beta_k(h, c) := \begin{cases}
-%%     z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
-%%     0, &\mbox{Otherwise}.
-%%   \end{cases}
-%% \end{equation}
+The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
+\begin{equation}
+    A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
+  \end{equation}
 
-%% From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.
+If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
 
-%% The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
-%% \begin{equation}
-%%     A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
-%%   \end{equation}
-
-%% If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
-
-%% The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form.
+The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form and the LCP problems correspond to the Nash \textit{minimax} problem for such games.
 However, since are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.
 
-%% \paragraph{Example: Sequence-form representation of Kuhn Poker}
-%% \label{sec:kuhn_sf}
-%% The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
-%% $A = \left[\begin{array}{ccccccccccccc}
-%%   &   &   &   &   &   &   &   &   &   &   &   &  \\
-%%   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
-%%   &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
-%%   &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
-%%   &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
-%%   &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
-%%   &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
-%%   &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
-%%   & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
-%%   &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
-%%   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
-%%   &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
-%%   & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
-%% \end{array}\right]$,\\
-%% $E_1 = \left[\begin{array}{ccccccccccccc}
-%% 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-%% -1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
-%% -1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
-%% -1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
-%%   & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
-%%   &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
-%%   &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
-%% \end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
-%% and $E_2 = \left[\begin{array}{ccccccccccccc}
-%% 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-%% -1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
-%% -1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
-%% -1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
-%% -1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
-%% -1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
-%% -1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
-%% \end{array}\right]$.\\
+\subsection{Example: Sequence-form representation of Kuhn Poker}
+\label{sec:kuhn_sf}
+The Kuhn 3-card Poker \cite{kuhn} has sequence-form specification given by (not showing zero entries)\\
+$A = \left[\begin{array}{ccccccccccccc}
+  &   &   &   &   &   &   &   &   &   &   &   &  \\
+  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
+  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
+  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
+  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
+  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
+  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
+  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
+  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
+  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
+  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
+  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
+  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
+\end{array}\right]$,\\
+$E_1 = \left[\begin{array}{ccccccccccccc}
+1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
+-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
+  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
+  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
+  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
+\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
+and $E_2 = \left[\begin{array}{ccccccccccccc}
+1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
+-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
+-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
+\end{array}\right]$.\\
 
@@
 \label{sec:related_work}
+\paragraph{Smoothing methods}
 In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique \cite{nesterov2005excessive} was used to to solve the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form
@@
   \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in Q_1}{\text{maximize}}\text{ }x^TAy
+  \label{eq:gilpin}
 \end{equation}
@@
 They authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate (which derives from the general EGT theory) for the outer-most iteration loop, though the cost of an iteration is presumably heavy since it entails computing a $softmax$ at each iteration.
+
+In \cite{gilpinfirst}, a modified verson of the technqiues of \cite{hoda2010smoothing} was developed.
+The authors proved a $\mathcal{O}\left(\left(\|A\| / \delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in terms of the number of calls made to a first-order oracle (for example, Nesterov's optimal gradient \cite{nesterov1983}).
+Here $\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a \textit{condition number} for the given game.
+It should be noted however that
+\begin{itemize}
+\item Though the authors in \cite{gilpinfirst} proved that $\delta > 0$ always, this constant can be arbitrarily small.\item The reported linear convergence rate is not in terms of basic operations (addition, multiplication, matvec, clipping, etc.), but in terms of number of calls to a first-order oracle.
+%% Thus the algorithm developed in \cite{gilpinfirst} doesn't have linear convergence rate in terms of fundamental operations (addition, multiplication, matvec, clipping, etc.).
+  \item Of course, the existence of a linear algorithm for solving \eqref{eq:gilpin} is improbable, as the usual strong-convexity conditions are absent.
+\end{itemize}
+
+\paragraph{CounterFactual Regret minimization}
+More recently, the primal-dual algorithm was applied to matrix games (on simplexes) in \cite{chambolle2014ergodic}.
+Sampling techniques like the CFR (CounterFactual Regret minimization) and its many variants \cite{MartinZinkevichNIPS2007, lanctot2009monte} are also becoming popular...
 
@@
 \label{sec:algo}
-We now derive our primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:primal_pb}.
+We now present our main contribution, namely an $\mathcal{O}(1/\epsilon)$ primal-dual algorithm for computing Nash $\epsilon$-equilibria for sequential two-person zero-sum games with imcomplete information and perfect recall.
 The algorithm is obtained from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}.
-Though this scheme has recently gained considerable popularity in the signal processing community
-%\cite{gramfort-etal:2013a}
-, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.
 
+\subsection{Reformulating the problem}
 It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing the euclidean projections $\Pi_{Q_k}$.
@@
   \begin{equation}
-    \underset{y, v}{minimize}\text{ }\underset{x, u}{maximize}
-           {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}
+    \underset{y, p}{minimize}\text{ }\underset{x, q}{maximize}
+           {\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} + G_2(y, p) - G_2(x, q)}
            \label{eq:unconstrained_pb}
@@
       %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + l_1) \times (n_1 + l_2)}\\
-      G: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tv\\
-      H: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tu
+      G_1: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow [0, +\infty], (y, p) \mapsto i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tp\\
+      G_2: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow [0, +\infty], (x, q) \mapsto i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tq
     \end{split}
@@
 
-  %% Moreover, if $\mathcal{G}'$ denotes the dual-gap function of problem $\eqref{eq:unconstrained_pb}$ and as before, $\mathcal{G}$ denotes the dual-gap function of problem \eqref{eq:primal_pb}, then we have the bound
+  %% Moreover, if $\mathcal{G_1}'$ denotes the dual-gap function of problem $\eqref{eq:unconstrained_pb}$ and as before, $\mathcal{G_1}$ denotes the dual-gap function of problem \eqref{eq:primal_pb}, then we have the bound
   %% \begin{equation}
-  %%   \mathcal{G}(x, y) \le \mathcal{G}'(x, u, y, v), \forall (x, u, y, v) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \times \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}
+  %%   \mathcal{G_1}(x, y) \le \mathcal{G_1}'(x, u, y, v), \forall (x, u, y, v) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \times \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}
   %%   \end{equation}
@@
     \underset{y,p}{\text{min}}\text{ }e_1^Tp + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2) + i_{\mathbb{R}^{n_2}_+}(y)\\
-    = \underset{y,p}{\text{min}}\text{ }G(y,p) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e2)
+    = \underset{y,p}{\text{min}}\text{ }G_1(y,p) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e2)
   \end{aligned}
@@
   \begin{split}
-    H^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right) &= \underset{x,q}{\text{max}}\text{ }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} - H(x, q) \\
-      &= \underset{x, q}{\text{max}}\text{ }x^T(Ay - E_1^Tp) - i_{\mathbb{R}^{n_1}_+}(x) + q^TE_2y - f^Tq\\
-      &= \underset{x \geq 0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) + \underset{q}{\text{max}}\text{ }q^T(E_2y - f)\\
+    G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right) &= \underset{x,q}{\text{max}}\text{ }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} - G_2(x, q) \\
+      &= \underset{x, q}{\text{max}}\text{ }x^T(Ay - E_1^Tp) - i_{\mathbb{R}^{n_1}_+}(x) + q^TE_2y - e_2^Tq\\
+      &= \underset{x \geq 0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) + \underset{q}{\text{max}}\text{ }q^T(E_2y - e_2)\\
       &= i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)
@@
 \begin{equation}
-  \underset{y,p}{\text{minimize}}\text{ }G(y,p) + H^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
+  \underset{y,p}{\text{minimize}}\text{ }G_1(y,p) + G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
 \end{equation}
 
-Similarly, one shows that the LCP problem \eqref{eq:dual_pb} is equivalent to
+By a similarly calculation, one shows that the LCP problem \eqref{eq:dual_pb} is equivalent to
 \begin{equation}
-  \underset{x,q}{\text{minimize}}\text{ }-G^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right) - H(x, q)\
+  \underset{x,q}{\text{minimize}}\text{ }-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right) - G_2(x, q)\
 \end{equation}
@@
 %%   \begin{split}
-%%     \underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{l_2}}{max}\text{ }\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y'\\v'\end{bmatrix} + G(y', v') - H(x, u)
+%%     \underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{l_2}}{max}\text{ }\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y'\\v'\end{bmatrix} + G_1(y', v') - G_2(x, u)
 %%       &= \underset{x \in \mathbb{R}^{n_1}_+, u \in \mathbb{R}^{l_2}}{max}\text{ }x^TAy' - v'^T(E_1x - e_1) + u^T(E_2y' - e_2)\\
@@
 %%   \begin{split}
-%%     \underset{y \in \mathbb{R}^{n_2}, v \in \mathbb{R}^{l_1}}{min}\text{ }\begin{bmatrix}x'\\u'\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x', u')
+%%     \underset{y \in \mathbb{R}^{n_2}, v \in \mathbb{R}^{l_1}}{min}\text{ }\begin{bmatrix}x'\\u'\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G_1(y, v) - G_2(x', u')
 %%       &= \underset{y \in \mathbb{R}^{n_2}_+, v \in \mathbb{R}^{l_1}}{min}\text{ }x'^TAy - v^T(E_1x' - e_1) + u'^T(E_2y - e_2)\\
@@
 
-Now,
-$G$ and $H$ are \textit{p.c.l.s.c} and their proximal operators are given by
+\subsection{The algorithm proper}
+In order to apply Algorithm 39 of \cite{chambolle2010}, we need the proximal operators of
+$G_1$ and $G_2$. Now, both functions are \textit{p.c.l.s.c} and their proximal operators are given by
   \begin{equation}
@@
     \begin{split}
-      \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\\
-      (y, v) &\mapsto ((y)_+, v - \tau e_1)\\
+      \text{prox}_{\tau G_1} : \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\\
+      (y, p) &\mapsto ((y)_+, p - \tau e_1)\\
     \end{split}
@@
     \begin{split}
-      \text{prox}_{\sigma H}: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}\\
-      (x, u) &\mapsto ((x)_+, u - \sigma e_2)
+      \text{prox}_{\sigma G_2}: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}\\
+      (x, q) &\mapsto ((x)_+, q - \sigma e_2)
     \end{split}
@@
 
-Indeed both $G$ and $F$ are separable sums of the indicator function of a convex set, whose prox is simply the euclidean projection operator onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox, at rank $\tau$, is simply $z \mapsto z - \tau a$.
+Indeed both $G_1$ and $F$ are separable sums of the indicator function of a convex set, whose prox is simply the euclidean projection operator onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox, at rank $\tau$, is simply $z \mapsto z - \tau a$.
 
-So, applying Algorithm 39 of \cite{chambolle2010} with $F := H^*$
+Applying Algorithm 39 of \cite{chambolle2010} with $F := G_2^*$
  to problem \eqref{eq:unconstrained_pb}, we obtain Algorithm \ref{Tab:algo_simplified} for solving the original problem \eqref{eq:primal_pb}.
 The $\mathcal{O}(1/\epsilon)$ convergence rate of Algorothm \ref{Tab:algo_simplified} hails directly from Theorem 1 of \cite{chambolle2010}.
-\begin{remark}
-  Note that the convergence rate of $\mathcal{O}(1/\epsilon)$ cannot be improved in the framework of \cite{chambolle2010}, since neither $G$ nor $H$ is \textit{uniformly convex}.
-\end{remark}
+  Note that the convergence rate of $\mathcal{O}(1/\epsilon)$ cannot be improved in the framework of \cite{chambolle2010}, since neither $G_1$ nor $G_2$ is \textit{uniformly convex}.
+However, it's possible to do over-relaxation and inertial iterates...
 
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[G_2]
   \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for finding a Nash $\epsilon$-equilibrium for a sequential two-person zero-sum game with imcomplete information and perfect recall}
@@
 
-\begin{remark}
-It's possible to do over-relaxation and inertial iterates...
-\end{remark}
+\section{Practical considerations: Exploiting the structure of the payoff matrix}
+In each iteration of Algorithm \ref{Tab:algo_simplified}, most of the time is spent
+pre-multiplying vectors by $A$ and $A^T$.
+For \textit{flop}-type Poker games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em}, $A$ (and thus $A^T$ too) has a rich structure.
+For example, in Rhode Island Hold'em, the payoff matrix $A$ can be written as block-diagonal matrix whose blocks are sums of Kronecker products of much smaller sparse matrices \cite{hoda2010smoothing} $F_1$, $B_1$, $F_2$, $B_2$, $F_3$, $B_3$, $S$, and $W$.
+Viz
+
+\begin{equation}
+  A = \begin{bmatrix}A_1\hspace{2em}\\\hspace{1em}A_2\hspace{1em}\\\hspace{2em}A_3\end{bmatrix}
+\label{eq:factor_A}
+\end{equation}
+where,
+\begin{equation}
+A_1 = F_1 \otimes B_1, \hspace{1em} A_1 = F_2 \otimes B_2, \hspace{1em} A_3 = F_3 \otimes B_3 + S \otimes W
+\end{equation}
+
+The matrices $F_i$ correspond to sequences of moves in round $i$ which end in a \textit{fold} action, and $S$ to the sequences which end in a \textit{showdown}.
+$B_i$ encodes the betting structure of round $i$, while $W$ encodes the wind/lose/draw information determined by ranking the players' hands at showdown.
+As reported in \cite{hoda2010smoothing}, the dimensions of $B_1$, $B_2$, and $B_3$ are $13 \times 13$, $205 \times 205$, and $1774 \times 1774$, respectively.
+By
+contrast, the matrix $A$ is $883741 \times 883741$. Furthermore, the matrices $F_i$, $B_i$,
+$S$, and $W$ are themselves sparse, which allows one to use the compressed row storage data structure that only stores nonzero entries (for example \textit{scipy.sparse.csr\_matrix}, in the Python programming language).
+
+Such a representation of the payoff matrix $A$ trivializes matvec operations involving $A$ or $A^T$.
+Of course, one can always write the payoff matrix $A$ of a flop-type Poker game in a form-similary to \eqref{eq:factor_A}, applying appropriate permutations to the enumeration of the players's sequences.
 
 \section{Results}
-\paragraph{Simulated game: matrix game on simplexes}
-Any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a 
-As in \textbf{nesterov, c-p, etc.}, we generate a $1000 \times 1000$ random matrix whose entries are uniformly identically distributed in the closed interval $[-1, 1]$.
+To access the practical quality of the proposed algorithm, we experimented it on real and simulated games. The results are presented here.
+
+\subsection{Simulated game: matrix game on simplexes}
+Any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a \textit{matrix game}.
+The strategy profile of player $k$ is a simplex; this simplex can be written in the form \eqref{eq:polytope} by taking $E_k := [1, 1, ..., 1] \in \mathbb{R}^{1 \times n_k}$ and $e_k = 1$.
+Thus every matrix game on simplexes can be seen as a sequential game.
+
+Now, as in \textbf{nesterov, c-p, etc.}, we generate a $1000 \times 1000$ random matrix whose entries are uniformly identically distributed in the closed interval $[-1, 1]$.
 See Figure \ref{Tab:sim_dgap_curve}.
@@
 
-\paragraph{Real-world game: Kuhn 3-card Poker}
-For this game, the sequence-form representation is given by (not showing zero entries)\\
-$A = \left[\begin{array}{ccccccccccccc}
-  &   &   &   &   &   &   &   &   &   &   &   &  \\
-  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
-  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
-  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
-  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
-  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
-  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
-  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
-  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
-  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
-  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
-  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
-  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
-\end{array}\right]$,\\
-$E_1 = \left[\begin{array}{ccccccccccccc}
-1 &   &   &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
--1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
-  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
-  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
-  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
-\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
-and $E_2 = \left[\begin{array}{ccccccccccccc}
-1 &   &   &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
--1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
--1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
-\end{array}\right]$.\\
-
-\paragraph{Solution}
-The pair $(x^*, y^*)$ of realization plans given by\\
+\subsection{Real-world game: Kuhn 3-card Poker}
+The sequence-form representation of this simplified Poker variant was given in subsection \ref{sec:kuhn_sf}. The pair $(x^*, y^*)$ of realization plans given by
 $x^* = [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T$ and
@@
 Indeed,  $E_1x^* - e_1 = [4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T$ and $E_2y^* - e_2 = [-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6}, 2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7}]^T$.
-Finally, $x^*TAy^* = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by Kuhn in his 1954 paper.
+Finally, $x^*TAy^* = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by H.
+W.
+Kuhn in his 1950 paper \cite{kuhn}.
 
@@
 These figures validates the theoritically established $\mathcal{O}(1/\epsilon)$ convergence rate of the Algorithm.
+
+The results of the experiments presented here are not benchmarks comparing our algorithm to other algorithms, though it would be nice to do such benchmarks in a future work.
 
@@
 %% where the $C_k$ are arbitrary convex sets for which the euclidean projections $\Pi_{C_k}$ can be effectively computed.
-%% % \paragraph{Example: Computing best response strategies}
+%% % \subsection{Example: Computing best response strategies}
 
@@
 %%     \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{l_1}}{minimize}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{l_2}}{maximize}
-%%            {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}
+%%            {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G_1(y, v) - G_2(x, u)}
 %%            \label{eq:unconstrained_gen_pb}
@@
 %%       %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + l_1) \times (n_1 + l_2)}\\
-%%       G: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow [-\infty, +\infty], (y, v) \mapsto i_{C_2}(y) + e_1^Tv\\
-%%       H: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow [-\infty, +\infty], (x, u) \mapsto i_{C_1}(x) + e_2^Tu
+%%       G_1: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow [-\infty, +\infty], (y, v) \mapsto i_{C_2}(y) + e_1^Tv\\
+%%       G_2: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow [-\infty, +\infty], (x, u) \mapsto i_{C_1}(x) + e_2^Tu
 %%     \end{split}
@@
 
-%%   Moreover, $G$ and $H$ are \textit{p.c.l.s.c} and their proximal operators are given by
+%%   Moreover, $G_1$ and $G_2$ are \textit{p.c.l.s.c} and their proximal operators are given by
 %%   \begin{equation}
@@
 %%     \begin{split}
-%%       \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\\
+%%       \text{prox}_{\tau G_1} : \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\\
 %%       (y, v) &\mapsto (\Pi_{C_2}(y), v - \tau e_1)\\
@@
 
-%% %\paragraph{$\mathcal{O}(1/\epsilon)$ primal-dual algorithm for general problems}
+%% %\subsection{$\mathcal{O}(1/\epsilon)$ primal-dual algorithm for general problems}
 %% Analogous to Algorithm \ref{Tab:algo_simplified}, we obtain Algorithm \ref{Tab:algo} for solving the Nash equilibrium problem \ref{eq:primal_pb} with the general strategy profiles $Q_k$ defined in \eqref{eq:q_gen}.
@@
 
-%% \begin{algorithm}[H]
+%% \begin{algorithm}[G_2yy]
 %%   \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:primal_pb}, with general strategy profiles as defined in \eqref{eq:q_gen}}
@@
 \section{Conclusion}
+For the first time, we have applied a primal-dual algorithm to the problem of computing Nash equilibria for two-person zer-sum sequential games with imcomplete information (like Texas Hold'em, etc.) Our algorithm is simple to implement, with a very low constant cost per iteration, and enjoys a rigorous convergence theory with a proven $\mathcal{O}(1/\epsilon)$ convergence equilibrium in terms of basic operations (matvec products, clipping, etc.), to a Nash $\epsilon$-equilibrium of the game...
+
 \medskip \noindent
-\textbf{Acknowledgments:}
+% \textbf{Acknowledgments:}
 \small

### 2015-01-11 nips2015.tex
ENH: getting ready for arxiv

@@
 \subsection{From extensive-form to sequence-form representation}
-For each information set $h$ of player $k$, $\sigma_h$ (unique and well-defined, by the  is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players.
+For each information set $h$ of player $k$, denote by $\sigma_h$  the sequence of choices ((unique and well-defined, by the the ongoing perfect-recall asumption) from the root node, to --any node of-- $h$, ignoring the choices of the other players.
 \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined.

### 2015-01-11 nips2015.tex
more typos

--- 2015-01-11 nips2015.tex
@@
 \subsection{From extensive-form to sequence-form representation}
-For each information set $h$ of player $k$, $\sigma_h$ (unique and well-defined, by the  is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players.
+For each information set $h$ of player $k$, denote by $\sigma_h$  the sequence of choices from the root node, to $h$ (i.e to any node in $h$), ignoring the choices of the other players.
 \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined.
@@
 The polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}.
-Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
+Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioral-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
 \begin{equation}
@@
 
-From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.
+From this definition, it is clear that each behavioral-strategy is equivalent to a mixed-strategy.
 

### 2015-01-22 nips2015.tex
better tex

@@
 \usepackage{qtree}
-
+\usepackage{natbib}
 \usepackage{graphicx}
@@
 \begin{abstract}
-We present a simple primal-dual algorithm with a low cost per iteration, for computing Nash $\epsilon$-equilibria for two-person zero-sum sequential games like Texas Hold'em Poker, which converges --in duality gap-- after $\mathcal{O}(1/\epsilon)$ basic iterations (i.e iterations only involving basic operations like matvec, clipping, etc., and no calls to external oracles).
+We present a simple primal-dual algorithm with a low cost per iteration, for computing Nash $\epsilon$-equilibria for two-person zero-sum sequential games with imcomplete information and perfect-recall like Texas Hold'em Poker, which converges after $\mathcal{O}(1/\epsilon)$ basic iterations (i.e iterations only involving basic operations like matvec, clipping, etc., and no calls to external first-order oracles, etc.).
 %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall.
-The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}
+The applicability to the latter kind of games is thanks to the sequen e-form representation von Stengel's \cite{von1996efficient}
 Our algorithm derives from the general primal-dual algorithm developed
 % by Chambolle and Pock
-in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria since the strategy profiles (polytopes) of players are so complex that it is not possible
+in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to compute Nash equilibria for the games considered here since the strategy profiles (polytopes) of players are so complex that it is not possible
 % (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
@@
  projections (the proximal operators) thereupon.
-Our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme, without any additional overhead.
-The resulting algorithm is simple, only involving matrix-vector multiplications
-% (without any matrix inversions, etc.)
-and nonnegative clipping.
-% (taking point-wise max of a vector and 0)
+Our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent problem which is amendable to the primal-dual scheme, without any additional overhead.
+The resulting algorithm is simple (less than 10 lines of code), only involving matvec (matrix-vector multiplication) and clipping.
 The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}.
-Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing}, our algorithm has a cheap and constant cost per iteration.
+Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap and constant cost per iteration.
 As proof of concept, we apply our algorithm to solve Kuhn 3-card Poker \cite{kuhn}.
@@
 \label{sec:intro}
-For sequential games with imcomplete information and perfect recall like Texas Hold'em Poker, von Stengel and co-workers have developed the \textit{sequence-form} representation (see \cite{von1996efficient} and references therewithin), whose size is linear in the size of the game tree, in contrast with the \textit{strategic-form} representation which is exponential.
+A game-theoretic aproach to playing games strategically optimally consists in computing Nash-equilibria (infact, approximations thereof) offline, and playing one's part of the equilibrium online.
+This technique is the driving-force behind solution concepts like CFR \cite{lanctot2009monte}, $\text{CFR}^{+}$, and other variants, which have recently found profound success in Poker: equilibria are computed offline (with tremendous computation resources, and the component optimal strategies are played on line by a bot, without any a posteriori computation).
+However, solving for equilibria remains a mathematical and computational challenge, especially in sequential games with imperfect information.
+Under the assumption of \textit{perfect recall}, \cite{von1996efficient} and co-workers have developed the \textit{sequence-form} representation, whose size is linear in the size of the game tree, in contrast with the \textit{strategic-form} representation which is exponential.
 The goal of this paper is to develop a fast and simple primal-dual algorithm for computing  Nash $\epsilon$-equilibria for such games, using this representation.
 
-\subsection{Context}
+\subsection{Background}
 In \cite{von1996efficient, vonequilibrium}, it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}, E_1 \in \mathbb{R}^{l_1 \times n_1}, E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to pairs $(x, y)$ of \textit{realization plans} which solve the primal LCP (Linear Constrained Programming) problem
@@
     & \underset{y,p}{\text{minimize}}
-    & & e_1^Tp \\
+    & & p^Te_1 \\
     & \text{subject to}
@@
     & \underset{x,q}{\text{maximize}}
-    & & -e_2^Tq \\
+    & & -q^Te_2 \\
     & \text{subject to}
@@
 
-with \textit{duality gap} given by\footnote{The last inequality being due to \textit{week duality}.}
+with \textit{duality gap} given by\footnote{The last inequality being due to \textit{weak duality}.}
 \begin{equation}
-  \mathcal{G}(p, q) := e_1^Tp - (-e_2^Tq) = e_1^Tp + e_2^Tq \geq 0
+  \mathcal{G}(p, q) := p^Te_1 - (-q^Te_2) = p^Te_1 + q^Te_2 \geq 0
   \label{eq:dgap}
@@
 $A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and $e_k$ is a vector of the form $[1, 0, ..., 0]$.
-In this representation (called the \textit{sequence-form}), the strategy profile of player $k$ is the polytope
+In this so-called \textit{sequence-form} representation (see section \ref{sec:rep} for details), the strategy profile of player $k$ is the polytope
 \begin{equation}
@@
 
-It was also shown (for example, Theorem 3.14 of \cite{vonequilibrium}) that a $(x, y)$ is a solution to the primal-dual problem \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff there exist vectors $p$ and $q$ such that
+It was also shown (for example, Theorem 3.14 of \cite{vonequilibrium}) that a $(x, y)$ is a solution to the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff there exist vectors $p$ and $q$ such that
 \begin{equation}
@@
 
-Moreover, in this case \textit{strong duality} holds and the value of the game equals $e_1^Tp = -e_2^Tq$; thus the duality gap $\mathcal{G}(p, q)$ defined in \eqref{eq:dgap} vanishes.
+Moreover, in this case \textit{strong duality} holds and the value of the game equals $p^Te_1 = -q^Te_2$; thus the duality gap $\mathcal{G}(p, q)$ defined in \eqref{eq:dgap} vanishes.
 
@@
 %% \item $i_C$: \quad indicator function of a convex set $C$;
-%% % \item $\Pi_C$: \quad euclidean projection operator onto a convex set $C$;
+%% % \item $\Pi_C$: \quad euclidean projection onto a convex set $C$;
 %% \item $\|K\|_2$: \quad spectral norm of a matrix $K$
@@
 %% $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
-%% %% We will assume that the convex sets $C_k$ are simple enough so that the eucliean projection operators $\Pi_{C_k}$ can be cheaply computed.
+%% %% We will assume that the convex sets $C_k$ are simple enough so that the eucliean projections $\Pi_{C_k}$ can be cheaply computed.
 %% Typically, $C_k = \mathbb{R}^{l_k}_+ := \{x \in \mathbb{R}^n|x_k \ge 0\}$, the \textit{the nonnegative orthant}, and encodes a nonnegativity constraint.
@@
 \begin{definition}(\textbf{Nash $\epsilon$-equilibria})
-Given a margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists admissible vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} satisfying
+Given a margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists dual vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} satisfying
 \begin{equation}
@@
 
-The goal of this article is to device a simple algorithm which produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations%We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation.
+The goal of this article is to device a simple algorithm which produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations.
+%We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation.
 Then we state the Nash equilibrium problem for the sequence-form representation.
@@
 Section \ref{sec:notation} features useful notions of convex optimization (proximal operators, convex conjugates, etc.).
-In section \ref{sec:algo} we derive the proposed algorithm for solving this problem and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.
+In section \ref{sec:algo} we derive the proposed algorithm for producing a NAsh $\epsilon$-equilibrium and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.
 We conclude with a demonstration on Kuhn 3-card Poker \cite{kuhn}.
@@
 A complete overview of the subject can be found in the pioneering work \cite{von1996efficient}.
-\subsection{Recap: Extensive-form representation} The game tree $\mathcal{T}$ is defined as follows.
+
+\subsection{The Game tree}
+The game tree $\mathcal{T}$ is defined as follows.
 There are three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}.
@@
 The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops.
-%% The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
+%% The sequence-form is similar to the \textit{strategic-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
 At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node.
@@
 
-A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts.
-The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.
-
-\subsection{From extensive-form to sequence-form representation}
+\subsection{Player sequences}
 For each information set $h$ of player $k$, denote by $\sigma_h$  the sequence of choices from the root node, to $h$ (i.e to any node in $h$), ignoring the choices of the other players.
@@
 
-Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$, and their \textit{mixed-strategies} are randomizations on these pure-strategies.
-In sequence-form, the strategy profile of player $k \ge 1$ is the polytope of $n_k$-dimensional nonnegative vectors $z$ (a realization plan) satisfying
+\subsection{Pure strategies, mixed strategies, realization plans}
+Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$ (i.e the prescription of a move $c \in C_h$ from each information set $h \in \mathcal{I}_k$), and their \textit{mixed-strategies} are randomizations on these pure-strategies.
+A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts.
+The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.
+
+The strategy profile of player $k$ is then the set of $n_k$-dimensional vectors $z$ satisfying
 % Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
@@
   z \geq 0,\hspace{1em}z(\emptyset) = 1,\hspace{1em}
-    z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
+    z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0, \hspace{1em} \forall h \in \mathcal{I}_k
   \label{eq:lin}
@@
 These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
-where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$.
-The polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}.
+where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$, and so the polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}.
+
+\subsection{Behavioral strategies}
 Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioral-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
@@
 
+\subsection{Payoff matrix}
 The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
 \begin{equation}
-    A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
+    A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \hspace{1em} \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
   \end{equation}
@@
 
+\subsection{What matters}
 The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form and the LCP problems correspond to the Nash \textit{minimax} problem for such games.
@@
 
-\section{Related work}
-\label{sec:related_work}
-\paragraph{Smoothing methods}
-In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique \cite{nesterov2005excessive} was used to to solve the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form
-
-\begin{equation}
-  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in Q_1}{\text{maximize}}\text{ }x^TAy
-  \label{eq:gilpin}
-\end{equation}
-
-They authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate (which derives from the general EGT theory) for the outer-most iteration loop, though the cost of an iteration is presumably heavy since it entails computing a $softmax$ at each iteration.
-
-In \cite{gilpinfirst}, a modified verson of the technqiues of \cite{hoda2010smoothing} was developed.
-The authors proved a $\mathcal{O}\left(\left(\|A\| / \delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in terms of the number of calls made to a first-order oracle (for example, Nesterov's optimal gradient \cite{nesterov1983}).
-Here $\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a \textit{condition number} for the given game.
-It should be noted however that
-\begin{itemize}
-\item Though the authors in \cite{gilpinfirst} proved that $\delta > 0$ always, this constant can be arbitrarily small.\item The reported linear convergence rate is not in terms of basic operations (addition, multiplication, matvec, clipping, etc.), but in terms of number of calls to a first-order oracle.
-%% Thus the algorithm developed in \cite{gilpinfirst} doesn't have linear convergence rate in terms of fundamental operations (addition, multiplication, matvec, clipping, etc.).
-  \item Of course, the existence of a linear algorithm for solving \eqref{eq:gilpin} is improbable, as the usual strong-convexity conditions are absent.
-\end{itemize}
-
-\paragraph{CounterFactual Regret minimization}
-More recently, the primal-dual algorithm was applied to matrix games (on simplexes) in \cite{chambolle2014ergodic}.
-Sampling techniques like the CFR (CounterFactual Regret minimization) and its many variants \cite{MartinZinkevichNIPS2007, lanctot2009monte} are also becoming popular...
-
 \section{Useful convex analysis}
 \label{sec:notation}
-We will need the following notations in the sequel. Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
-the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros and $1_{m,n}$ denotes the $m$-by-$n$ matrix of ones.
-%% $\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_k \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegative orthant}.
+We will need the following notations in the sequel. The passionate reader should refer to the classic \cite{rockafellar1997convex} for a more elaborate presentation.
 
+\subsection{Linear algebra, nonnegative clipping, indicator functions, euclidean projection}
+Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
+the space of all $m$-by-$n$ real matrices, and $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
+$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq 0\}$ is the nonnegative $n$-dimensional orthant.
 For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
-$(x)_+$ denotes its point-wise maximum with 0. Note that $(x)_+ \in \mathbb{R}^n_+$.
+$(x)_+$ denotes its point-wise maximum with 0, an operation referred to a \textit{nonnegative-clipping}. Note that $(x)_+ \in \mathbb{R}^n_+$.
 For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$,
@@
 
-Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection operator} onto $C$, denoted $\Pi_C$, is the function
+Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection} onto $C$, denoted $\Pi_C$, is the function
 $\Pi: \mathbb{R}^n \mapsto C$ which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closest to $x$. Precisely,
@@
 
+\subsection{Convex conjugates, proximal operators}
 Let $f : \mathbb{R}^n \rightarrow [-\infty, +\infty]$ be a \textit{proper convex lower semi-continous function}
@@
 \begin{equation}
-  x \mapsto f^*(x) := \underset{z \in \mathbb{R}^n}{\text{max}}\text{ }z^Tx - f(x)
+  x \mapsto f^*(x) := \underset{z \in \mathbb{R}^n}{\text{max}}\text{ }z^Tx - f(z)
 \end{equation}
@@
 One easily verifies that $f^{**} = f$.
-
 Given $\tau > 0$, the \textit{proximal operator} of $f$ of rank
@@
 It is easy to see that if $f$ is the indicator function of a convex set $C$, then $\text{prox}_{\tau f} = \Pi_C, \forall \tau > 0$. In this sense, proximal operators can be seen
-as a generalization of euclidean projection operators.
+as a generalization of euclidean projections.
+The passionate reader will find more on proximal operators and optimization techniques based (forward-backward, etc.) on them in \cite{combettes2011proximal}.
+
+\section{Related work}
+\label{sec:related_work}
+\subsection{Interior-point methods}
+...
+
+\subsection{Smoothing methods}
+In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique \cite{nesterov2005excessive} was used to to solve the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form
+
+\begin{equation}
+  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in Q_1}{\text{maximize}}\text{ }x^TAy
+  \label{eq:gilpin}
+\end{equation}
+
+They authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate (which derives from the general EGT theory) for the outer-most iteration loop, though the cost of an iteration is presumably heavy since it entails computing a $softmax$ at each iteration.
+
+In \cite{gilpinfirst}, a modified verson of the technqiues in \cite{hoda2010smoothing} was developed.
+The authors proved a $\mathcal{O}\left(\left(\|A\| / \delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in terms of the number of calls made to a first-order oracle (for example, Nesterov's optimal gradient \cite{nesterov1983}).
+Here $\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a certain \textit{condition number} for the given game.
+It should be noted however that though the authors in \cite{gilpinfirst} proved that $\delta > 0$ always, this constant can be arbitrarily small.
+Most importantly, the reported linear convergence rate is not in terms of basic operations (addition, multiplication, matvec, clipping, etc.), but in terms of the number of calls to a first-order oracle.
+Of course, the existence of a linear algorithm for solving \eqref{eq:gilpin} is improbable, as the usual strong-convexity conditions are absent.
+
+%% It should be noted that the EGT and its precursors have had considerable success in the signal processing communities, as can be seen in \cite{NestaCandès, eduard, etc.} and the references therein.
+
+\subsection{CounterFactual Regret minimization}
+More recently, the primal-dual algorithm was applied to matrix games (on simplexes) in \cite{chambolle2014ergodic}.
+Sampling techniques like the CFR (CounterFactual Regret minimization) and its many variants \cite{MartinZinkevichNIPS2007, lanctot2009monte} are also becoming popular...
 
@@
 
-\subsection{Reformulating the problem}
-It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing the euclidean projections $\Pi_{Q_k}$.
+\subsection{Unconstrained minimax reformulation of the problem}
+It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing\footnote{However, this computation can be done iteratively using the algorithm in proposition 4.2 of \cite{combettes2010dualization}, for example.} the euclidean projections $\Pi_{Q_k}$.
 Theorem \ref{thm:pd} provides a trick to effectively evade this difficulty.
@@
   \begin{equation}
-    \underset{y, p}{minimize}\text{ }\underset{x, q}{maximize}
+    \underset{y, p}{\text{minimize}}\text{ }\underset{x, q}{\text{maximize}}
            {\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} + G_2(y, p) - G_2(x, q)}
@@
   \begin{equation}
-    \left .
-    \begin{split}
     K :=
@@
       \end{array}
-        \right] \in \mathbb{R}^{(n_1 + l_2) \times (n_2 + l_1)} \\
-      %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + l_1) \times (n_1 + l_2)}\\
-      G_1: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow [0, +\infty], (y, p) \mapsto i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tp\\
-      G_2: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow [0, +\infty], (x, q) \mapsto i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tq
-    \end{split}
-    \right\}
+      \right] \in \mathbb{R}^{(n_1 + l_2) \times (n_2 + l_1)}
+\end{equation}
+
+and the p.c.l.s.c functions $G_1: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow (-\infty, +\infty]$ and $G_2: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ are defined by
+  \begin{equation}
+      G_1(y, p) := i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1, \hspace{1em} G_2(x, q) := i_{\mathbb{R}^{n_1}_+}(x) + q^Te_2
     \label{eq:things}
@@
 \begin{proof}
-  The LCP problem \eqref{eq:primal_pb} simplified as follows
-\begin{equation}
+The optimal value, say $v$, in the dual LCP problem \eqref{eq:primal_pb} can be computed as 
+\begin{eqnarray*}
   \begin{aligned}
-    \underset{y,p}{\text{min}}\text{ }e_1^Tp + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2) + i_{\mathbb{R}^{n_2}_+}(y)\\
-    = \underset{y,p}{\text{min}}\text{ }G_1(y,p) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e2)
+    v &= \underset{y,p}{\text{min}}\text{ }i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1 + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
+    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e2)\\
+    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x \geq 0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) + \underset{q}{\text{max}}\text{ }q^T(E_2y - e_2)\\
+    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x, q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y - i_{\mathbb{R}^{n_1}_+}(x) - q^Te_2\\
+    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x,q}{\text{max}}\text{ }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} - G_2(x, q) \\
+      &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
   \end{aligned}
   \label{eq:a}
-\end{equation}
+\end{eqnarray*}
 
-Now, one computes
-\begin{equation}
-  \begin{split}
-    G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right) &= \underset{x,q}{\text{max}}\text{ }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} - G_2(x, q) \\
-      &= \underset{x, q}{\text{max}}\text{ }x^T(Ay - E_1^Tp) - i_{\mathbb{R}^{n_1}_+}(x) + q^TE_2y - e_2^Tq\\
-      &= \underset{x \geq 0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) + \underset{q}{\text{max}}\text{ }q^T(E_2y - e_2)\\
-      &= i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)
-  \end{split}
-  \label{eq:b}
-\end{equation}
-Combining equations \eqref{eq:a} and \eqref{eq:b}, it follows that the LCP problem \eqref{eq:primal_pb} can be written as 
+Thus the LCP problem \eqref{eq:primal_pb} can be written as 
 \begin{equation}
@@
 \begin{equation}
-  \underset{x,q}{\text{minimize}}\text{ }-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right) - G_2(x, q)\
+  \underset{x,q}{\text{maximize}}\text{ }-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right) - G_2(x, q)
 \end{equation}
 
-But these last two equations are simply the primal and dual formulations of the saddle-point problem \eqref{eq:unconstrained_pb}, and we are done.
+But these last two equations are simply the primal and dual formulations respectively, of the saddle-point problem \eqref{eq:unconstrained_pb}, and we are done.
 
@@
 
-The rest of this section is concerned with applying Algorithm 39 of \cite{chambolle2010} to solve problem
-\eqref{eq:unconstrained_pb} and therefore by Theorem \ref{thm:pd}, the Nash equilibrium problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb}.
+%% The rest of this section is concerned with applying Algorithm 39 of \cite{chambolle2010} to solve problem
+%% \eqref{eq:unconstrained_pb} and therefore by Theorem \ref{thm:pd}, the Nash equilibrium problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb}.
 
-\subsection{The algorithm proper}
+\subsection{Derivation of the algorithm}
 In order to apply Algorithm 39 of \cite{chambolle2010}, we need the proximal operators of
@@
 
-Indeed both $G_1$ and $F$ are separable sums of the indicator function of a convex set, whose prox is simply the euclidean projection operator onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox, at rank $\tau$, is simply $z \mapsto z - \tau a$.
+Indeed both $G_1$ and $F$ are separable sums of the indicator function of a convex set, whose prox is simply the euclidean projection onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox, at rank $\tau$, is simply $z \mapsto z - \tau a$.
 
-Applying Algorithm 39 of \cite{chambolle2010} with $F := G_2^*$
- to problem \eqref{eq:unconstrained_pb}, we obtain Algorithm \ref{Tab:algo_simplified} for solving the original problem \eqref{eq:primal_pb}.
+Applying Algorithm 39 of \cite{chambolle2010} to problem \eqref{eq:unconstrained_pb}, we obtain Algorithm \ref{Tab:algo_simplified} for solving the original problem \eqref{eq:primal_pb}.
 The $\mathcal{O}(1/\epsilon)$ convergence rate of Algorothm \ref{Tab:algo_simplified} hails directly from Theorem 1 of \cite{chambolle2010}.
+
 Note that the convergence rate of $\mathcal{O}(1/\epsilon)$ cannot be improved in the framework of \cite{chambolle2010}, since neither $G_1$ nor $G_2$ is \textit{uniformly convex}.
@@
 %$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$
-$|e_1^Tp^{(k)} + e_2^Tq^{(k)}| \geq \epsilon$}{
+$|p^Te_1^{(k)} + q^Te_2^{(k)}| > \epsilon$}{
     \begin{eqnarray*}
@@
       \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
-      \tilde{q}^{(k+1)} &\leftarrow& 2q^{(k+1)} - q^{(k)}\\
+      \tilde{p}^{(k+1)} &\leftarrow& 2p^{(k+1)} - p^{(k)}\\
       k &\leftarrow& k + 1
@@
 Such a representation of the payoff matrix $A$ trivializes matvec operations involving $A$ or $A^T$.
-Of course, one can always write the payoff matrix $A$ of a flop-type Poker game in a form-similary to \eqref{eq:factor_A}, applying appropriate permutations to the enumeration of the players's sequences.
+Of course, one can always write the payoff matrix $A$ of a flop-type Poker game in a form similary to \eqref{eq:factor_A} by applying appropriate permutations to the enumeration of the players's sequences.
 
@@
 Now, as in \textbf{nesterov, c-p, etc.}, we generate a $1000 \times 1000$ random matrix whose entries are uniformly identically distributed in the closed interval $[-1, 1]$.
-See Figure \ref{Tab:sim_dgap_curve}.
+See Figure \ref{Tab:sim_dgap_curve}...
 
@@
 
+\begin{remark}
 The results of the experiments presented here are not benchmarks comparing our algorithm to other algorithms, though it would be nice to do such benchmarks in a future work.
+\end{remark}
 
@@
 %% %$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$
-%% $|e_1^Tp^{(k)} - e_2^Tq^{(k)}| \geq \epsilon$}{
+%% $|p^Te_1^{(k)} - q^Te_2^{(k)}| \geq \epsilon$}{
 %%     \begin{eqnarray*}
@@
 \section{Conclusion}
-For the first time, we have applied a primal-dual algorithm to the problem of computing Nash equilibria for two-person zer-sum sequential games with imcomplete information (like Texas Hold'em, etc.) Our algorithm is simple to implement, with a very low constant cost per iteration, and enjoys a rigorous convergence theory with a proven $\mathcal{O}(1/\epsilon)$ convergence equilibrium in terms of basic operations (matvec products, clipping, etc.), to a Nash $\epsilon$-equilibrium of the game...
+For the first time, we have applied a primal-dual algorithm to the problem of computing Nash equilibria for two-person zero-sum sequential games with imcomplete information (like Texas Hold'em, etc.).
+Our algorithm is simple to implement, with a very low constant cost per iteration, and enjoys a rigorous convergence theory with a proven $\mathcal{O}(1/\epsilon)$ convergence in terms of basic operations (matvec products, clipping, etc.), to a Nash $\epsilon$-equilibrium of the game...
 
 \medskip \noindent
-% \textbf{Acknowledgments:}
+\textbf{About the author:} I'm a first-year PhD student in Computer Science at Universit\'e de Parix XI.
+My thesis focuses on novel techniques for optimization on Lie groups (of diffeomorphisms), and other structured manifolds, the aim being to obtain better algorithms for nonlinear registration of fMRI brain images and enhance the charting of human functional connectomes.
+
+\textbf{Acknowledgments:} ...
 \small
-\bibliographystyle{ieeetr}
+\bibliographystyle{agsm}
+% \bibliographystyle{abbrvnat}
 \bibliography{bib}

### 2015-01-22 primal_dual.py

@@ -162,7 +162,7 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
         x *= tau
         x += c
         x = proj_C1(x)
-        q = (E2.dot(ytilde) - e2)
+        q = E2.dot(ytilde) - e2
         q *= tau
         q += d
 

### 2015-01-22 simple.py

@@ -949,7 +949,7 @@ if __name__ == "__main__":
         plt.loglog(np.abs(dgaps), label="Primal-Dual", linewidth=4)
         plt.xlabel("$k$", fontsize=25)
         plt.ylabel(
-            "Duality gap $|e_1^Tp^{(k)} + e_2^Tq^{(k)}|$",
+            "Duality gap $|e_1^Tp^{(k)} + e_2^Tq^{(k)}|$ after $k$ iterations",
             fontsize=25)
         plt.legend(loc="best", prop=dict(size=25))
         plt.tick_params(axis='both', which='major', labelsize=20)

### 2015-01-22 nips2015.tex
more refs

@@
 However, solving for equilibria remains a mathematical and computational challenge, especially in sequential games with imperfect information.
-Under the assumption of \textit{perfect recall}, \cite{von1996efficient} and co-workers have developed the \textit{sequence-form} representation, whose size is linear in the size of the game tree, in contrast with the \textit{strategic-form} representation which is exponential.
-The goal of this paper is to develop a fast and simple primal-dual algorithm for computing  Nash $\epsilon$-equilibria for such games, using this representation.
+This paper proposes an algorithm for solving for such equilibria approximately, in a sense which will be made clear shortly.
 
-\subsection{Background}
-In \cite{von1996efficient, vonequilibrium}, it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}, E_1 \in \mathbb{R}^{l_1 \times n_1}, E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to pairs $(x, y)$ of \textit{realization plans} which solve the primal LCP (Linear Constrained Programming) problem
+\subsection{Context}
+The sequence-form for two-person zero-sum games was introduced in \cite{koller1992complexity}, and the theory was further developed in \cite{von1996efficient, vonequilibrium}, where it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}, E_1 \in \mathbb{R}^{l_1 \times n_1}, E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to pairs $(x, y)$ of \textit{realization plans} which solve the primal LCP (Linear Constrained Programming) problem
 \begin{equation}
@@
 
-It was also shown (for example, Theorem 3.14 of \cite{vonequilibrium}) that a $(x, y)$ is a solution to the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff there exist vectors $p$ and $q$ such that
+It was also shown (see Theorem 3.14 of \cite{vonequilibrium}) that a $(x, y)$ is a solution to the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff there exist vectors $p$ and $q$ such that
 \begin{equation}
@@
 \section{Related work}
-\label{sec:related_work}
-\subsection{Interior-point methods}
-...
-
-\subsection{Smoothing methods}
 In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique \cite{nesterov2005excessive} was used to to solve the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form
@@
 
-\subsection{CounterFactual Regret minimization}
-More recently, the primal-dual algorithm was applied to matrix games (on simplexes) in \cite{chambolle2014ergodic}.
-Sampling techniques like the CFR (CounterFactual Regret minimization) and its many variants \cite{MartinZinkevichNIPS2007, lanctot2009monte} are also becoming popular...
+Sampling techniques like the CFR (CounterFactual Regret minimization) and its many variants \cite{MartinZinkevichNIPS2007, lanctot2009monte, Bowling09012015} are also becoming popular.
+
+More recently, \cite{chambolle2014ergodic} employs the primal-dual algorithm was applied to matrix games on simplexes.
+It should be stressed that such matrix games are considerably simpler than the games considered here.
+Indeed, the authors in \cite{chambolle2014ergodic} use the fact that computing the euclidean projection of a point unto a simplex can be done in linear time \cite{duchi2008efficient}, in contrast to the polytopes $Q_k$ defined in \eqref{eq:polytope} for which no such efficient algorithm is known nor is likely to exist.
+Note that computing the euclidean projection of a point unto the polytope $Q_k$ can still be done iteratively using the algorithm in proposition 4.2 of \cite{combettes2010dualization}, for example.
+However, the authors didn't provide a convergence rate for their algorithm, and as with any nested iterative scheme, one would have to solve this sub-problem with finer and finer precision.
 
@@
 \subsection{Unconstrained minimax reformulation of the problem}
-It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing\footnote{However, this computation can be done iteratively using the algorithm in proposition 4.2 of \cite{combettes2010dualization}, for example.} the euclidean projections $\Pi_{Q_k}$.
+It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing the euclidean projections $\Pi_{Q_k}$.
 Theorem \ref{thm:pd} provides a trick to effectively evade this difficulty.
@@
 The $\mathcal{O}(1/\epsilon)$ convergence rate of Algorothm \ref{Tab:algo_simplified} hails directly from Theorem 1 of \cite{chambolle2010}.
-
-Note that the convergence rate of $\mathcal{O}(1/\epsilon)$ cannot be improved in the framework of \cite{chambolle2010}, since neither $G_1$ nor $G_2$ is \textit{uniformly convex}.
-However, it's possible to do over-relaxation and inertial iterates...
+Note however that this convergence rate cannot be improved in the framework of \cite{chambolle2010}, since neither $G_1$ nor $G_2$ is \textit{uniformly convex}.
 

### 2015-01-25 nips2015.tex
better .tex

@@
-\documentclass{article} % For LaTeX2e
-\usepackage{nips14submit_e,times}
+\documentclass[12pt]{article}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{color}
+
+%% \documentclass{article} % For LaTeX2e
+%% \usepackage{nips14submit_e,times}
 \usepackage{hyperref}
@@
 
-\title{Primal-dual algorithm for computing Nash equilibria in
+\title{\bf Primal-dual algorithm for computing Nash equilibria in
 % two-person zero-sum
@@
 \begin{abstract}
-We present a simple primal-dual algorithm with a low cost per iteration, for computing Nash $\epsilon$-equilibria for two-person zero-sum sequential games with imcomplete information and perfect-recall like Texas Hold'em Poker, which converges after $\mathcal{O}(1/\epsilon)$ basic iterations (i.e iterations only involving basic operations like matvec, clipping, etc., and no calls to external first-order oracles, etc.).
+We present a simple primal-dual algorithm with a low cost per iteration for computing Nash $\epsilon$-equilibria in two-person zero-sum sequential games with imcomplete information and perfect-recall (like Texas Hold'em Poker), which converges after $\mathcal{O}(1/\epsilon)$ basic iterations (i.e iterations only involving basic operations like matvec, clipping, etc., and no calls to external first-order oracles, etc.).
 %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall.
@@
 % by Chambolle and Pock
-in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to compute Nash equilibria for the games considered here since the strategy profiles (polytopes) of players are so complex that it is not possible
+in \cite{chambolle2010, chambolle2014ergodic}.
+It should be noted that the latter primal-dual algorithm is not directly applicable to compute Nash equilibria for the afore-mentioned games considered here since the strategy profiles (polytopes) of players are so complex that it is not possible
 % (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
@@
  projections (the proximal operators) thereupon.
-Our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent problem which is amendable to the primal-dual scheme, without any additional overhead.
-The resulting algorithm is simple (less than 10 lines of code), only involving matvec (matrix-vector multiplication) and clipping.
-The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}.
+The core of our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point convex-convex problem which is amendable to the primal-dual scheme (i.e all proximal operators can be computed in closed-form).
 Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap and constant cost per iteration.
@@
 \begin{remark}  
-  Even though problem \eqref{eq:primal_pb} is in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
+It should be noted that even though problem \eqref{eq:primal_pb} is in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
 \end{remark}
@@
 Solving problem \eqref{eq:primal_pb} exactly is impossible in practice, and such a precision doesn't have any fundamental advantage.
-Instead, it is customary compute so-called Nash $\epsilon$-equlibria
+Instead, it is customary compute so-called Nash $\epsilon$-equlibria.
 
@@
 \subsection{Outline of the article}
-In section \ref{sec:rep} we briefly review the sequence-form representation.
+ Section \ref{sec:notation} exposes useful notions of convex optimization (proximal operators, convex conjugates, etc.) which will be crucial for the sequel.
 In section \ref{sec:related_work}, we give a brief overview of existing methods for computing Nash $\epsilon$-equilibria.
-Section \ref{sec:notation} features useful notions of convex optimization (proximal operators, convex conjugates, etc.).
 In section \ref{sec:algo} we derive the proposed algorithm for producing a NAsh $\epsilon$-equilibrium and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.
-We conclude with a demonstration on Kuhn 3-card Poker \cite{kuhn}.
+Section \ref{sec:results} presents practical results obtained both on simulated matrix games and the Kuhn 3-card Poker \cite{kuhn}.
 
@@
 
-\section{The sequence-form representation}
-\label{sec:rep}
-In this section, we briefly recall the sequence-form representation of sequential games with imcomplete information and perfect recall.
+%% \section{The sequence-form representation}
+%% \label{sec:rep}
+%% In this section, we briefly recall the sequence-form representation of sequential games with imcomplete information and perfect recall.
 A complete overview of the subject can be found in the pioneering work \cite{von1996efficient}.
 
-\subsection{The Game tree}
-The game tree $\mathcal{T}$ is defined as follows.
+%% \subsection{The Game tree}
+%% The game tree $\mathcal{T}$ is defined as follows.
 There are three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}.
@@
 Nodes of the game tree $\mathcal{T}$ are identified with states of the game, and actions taken by players correspond to edges of $\mathcal{T}$.
-The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops.
+%% The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops.
 %% The sequence-form is similar to the \textit{strategic-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
-At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node.
+%% At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node.
 This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts.
@@
 
-$a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
-receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
-The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
-We will assume implicitly that each (non-chance) player is rational.
+%% $a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
+%% receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
+%% The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
+%% We will assume implicitly that each (non-chance) player is rational.
 
-\subsection{Player sequences}
-For each information set $h$ of player $k$, denote by $\sigma_h$  the sequence of choices from the root node, to $h$ (i.e to any node in $h$), ignoring the choices of the other players.
+%% \subsection{Player sequences}
+%% For each information set $h$ of player $k$, denote by $\sigma_h$  the sequence of choices from the root node, to $h$ (i.e to any node in $h$), ignoring the choices of the other players.
 \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined.
@@
 The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by
-\begin{equation}
-\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
-\end{equation}
-Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish.
+%% \begin{equation}
+%% \mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
+%% \end{equation}
+%% Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish.
 $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
-$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.
+%% $\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.
 
-\subsection{Pure strategies, mixed strategies, realization plans}
-Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$ (i.e the prescription of a move $c \in C_h$ from each information set $h \in \mathcal{I}_k$), and their \textit{mixed-strategies} are randomizations on these pure-strategies.
+%% \subsection{Pure strategies, mixed strategies, realization plans}
+%% Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$ (i.e the prescription of a move $c \in C_h$ from each information set $h \in \mathcal{I}_k$), and their \textit{mixed-strategies} are randomizations on these pure-strategies.
 A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts.
@@
 
-The strategy profile of player $k$ is then the set of $n_k$-dimensional vectors $z$ satisfying
-% Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
-\begin{equation}
-  z \geq 0,\hspace{1em}z(\emptyset) = 1,\hspace{1em}
-    z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0, \hspace{1em} \forall h \in \mathcal{I}_k
-  \label{eq:lin}
-\end{equation}
+%% The strategy profile of player $k$ is then the set of $n_k$-dimensional vectors $z$ satisfying
+%% % Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
+%% \begin{equation}
+%%   z \geq 0,\hspace{1em}z(\emptyset) = 1,\hspace{1em}
+%%     z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0, \hspace{1em} \forall h \in \mathcal{I}_k
+%%   \label{eq:lin}
+%% \end{equation}
 
-These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
-where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$, and so the polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}.
+%% These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
+%% where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$, and so the polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}.
 
-\subsection{Behavioral strategies}
-Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioral-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
-\begin{equation}
-  \beta_k(h, c) := \begin{cases}
-    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
-    0, &\mbox{Otherwise}.
-  \end{cases}
-\end{equation}
+%% \subsection{Behavioral strategies}
+%% Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioral-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
+%% \begin{equation}
+%%   \beta_k(h, c) := \begin{cases}
+%%     z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
+%%     0, &\mbox{Otherwise}.
+%%   \end{cases}
+%% \end{equation}
 
-From this definition, it is clear that each behavioral-strategy is equivalent to a mixed-strategy.
+%% From this definition, it is clear that each behavioral-strategy is equivalent to a mixed-strategy.
 
-\subsection{Payoff matrix}
-The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
-\begin{equation}
-    A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \hspace{1em} \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
-  \end{equation}
+%% \subsection{Payoff matrix}
+%% The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
+%% \begin{equation}
+%%     A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \hspace{1em} \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
+%%   \end{equation}
 
-If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
+%% If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
 
-\subsection{What matters}
-The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form and the LCP problems correspond to the Nash \textit{minimax} problem for such games.
-However, since are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.
+%% \subsection{In summary}
+%% The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form and the LCP problems correspond to the Nash \textit{minimax} problem for such games.
+However, since we are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.
 
-\subsection{Example: Sequence-form representation of Kuhn Poker}
-\label{sec:kuhn_sf}
-The Kuhn 3-card Poker \cite{kuhn} has sequence-form specification given by (not showing zero entries)\\
-$A = \left[\begin{array}{ccccccccccccc}
-  &   &   &   &   &   &   &   &   &   &   &   &  \\
-  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
-  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
-  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
-  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
-  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
-  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
-  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
-  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
-  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
-  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
-  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
-  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
-\end{array}\right]$,\\
-$E_1 = \left[\begin{array}{ccccccccccccc}
-1 &   &   &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
--1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
-  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
-  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
-  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
-\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
-and $E_2 = \left[\begin{array}{ccccccccccccc}
-1 &   &   &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
--1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
--1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
-\end{array}\right]$.\\
+%% \subsection{Example: Sequence-form representation of Kuhn Poker}
+%% \label{sec:kuhn_sf}
+%% The Kuhn 3-card Poker \cite{kuhn} has sequence-form specification given by (not showing zero entries)\\
+%% $A = \left[\begin{array}{ccccccccccccc}
+%%   &   &   &   &   &   &   &   &   &   &   &   &  \\
+%%   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
+%%   &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
+%%   &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
+%%   &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
+%%   &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
+%%   &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
+%%   &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
+%%   & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
+%%   &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
+%%   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
+%%   &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
+%%   & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
+%% \end{array}\right]$,\\
+%% $E_1 = \left[\begin{array}{ccccccccccccc}
+%% 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+%% -1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
+%% -1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
+%% -1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
+%%   & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
+%%   &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
+%%   &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
+%% \end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
+%% and $E_2 = \left[\begin{array}{ccccccccccccc}
+%% 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+%% -1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
+%% -1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
+%% -1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
+%% -1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
+%% -1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
+%% -1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
+%% \end{array}\right]$.\\
 
@@
 \label{sec:notation}
-We will need the following notations in the sequel. The passionate reader should refer to the classic \cite{rockafellar1997convex} for a more elaborate presentation.
+We will need the following notations in the sequel.
+The passionate reader should refer to the classic \cite{rockafellar1997convex} for a more elaborate presentation.
+This section can be omitted without loss of continuity.
 
@@
 For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
-$(x)_+$ denotes its point-wise maximum with 0, an operation referred to a \textit{nonnegative-clipping}. Note that $(x)_+ \in \mathbb{R}^n_+$.
-For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$,
+$(x)_+:=\text{max}(0, x)$ is the point-wise maximum of $x$ with 0.
+$(.)_+$ is the well-known (multi-dimensional) \textit{ramp} function.For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$.
+The \textit{spectral norm} of a matrix $K$,
 denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).
@@
 \section{Related work}
-In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique \cite{nesterov2005excessive} was used to to solve the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form
+\label{sec:related_work}
+We present a selection of algorithms that is representative of the efforts that have been made in the literature to compute Nash $\epsilon$-equilibria for two-person zero-sum games with imcomplete information like Texas Hold'em Poker, etc.
+
+In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used to to solve the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form
 
@@
 \end{equation}
-
-They authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate (which derives from the general EGT theory) for the outer-most iteration loop, though the cost of an iteration is presumably heavy since it entails computing a $softmax$ at each iteration.
+The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate (which derives from the general EGT theory) for the outer-most iteration loop, though the cost of an iteration is presumably heavy since it entails computing a $softmax$ at each iteration.
 
@@
 Here $\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a certain \textit{condition number} for the given game.
-It should be noted however that though the authors in \cite{gilpinfirst} proved that $\delta > 0$ always, this constant can be arbitrarily small.
-Most importantly, the reported linear convergence rate is not in terms of basic operations (addition, multiplication, matvec, clipping, etc.), but in terms of the number of calls to a first-order oracle.
+It should be noted however that
+\begin{itemize}
+\item[--] Though the authors in \cite{gilpinfirst} proved that $\delta > 0$ always, this constant can be arbitrarily small.
+\item[--] Most importantly, the reported linear convergence rate is not in terms of basic operations (addition, multiplication, matvec, clipping, etc.), but in terms of the number of calls to a first-order oracle.
 Of course, the existence of a linear algorithm for solving \eqref{eq:gilpin} is improbable, as the usual strong-convexity conditions are absent.
+\end{itemize}
 
@@
 
-Sampling techniques like the CFR (CounterFactual Regret minimization) and its many variants \cite{MartinZinkevichNIPS2007, lanctot2009monte, Bowling09012015} are also becoming popular.
-
-More recently, \cite{chambolle2014ergodic} employs the primal-dual algorithm was applied to matrix games on simplexes.
+The primal-dual algorithm first developed in \cite{chambolle2010}, was proposed \cite{chambolle2014ergodic} to solve matrix games on simplexes.
 It should be stressed that such matrix games are considerably simpler than the games considered here.
@@
 However, the authors didn't provide a convergence rate for their algorithm, and as with any nested iterative scheme, one would have to solve this sub-problem with finer and finer precision.
+
+Sampling techniques like the CFR (CounterFactual Regret minimization) and its many variants \cite{MartinZinkevichNIPS2007, lanctot2009monte, Bowling09012015} are also becoming popular.
 
@@
 It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing the euclidean projections $\Pi_{Q_k}$.
-Theorem \ref{thm:pd} provides a trick to effectively evade this difficulty.
+Theorem \ref{thm:pd} provides a trick to effectively evade this difficulty, by re-writting the problem into an equivalent saddle-point convex-concave problem for which the associated proximal operators are simple.
 
@@
 
-and the p.c.l.s.c functions $G_1: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow (-\infty, +\infty]$ and $G_2: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ are defined by
+and the p.c.l.s.c functions $G_1: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow (-\infty, +\infty]$ and \\$G_2: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ are defined by
   \begin{equation}
@@
 
-\subsection{Derivation of the algorithm}
+\subsection{Derivation of the algorithm and its convergence rate}
 In order to apply Algorithm 39 of \cite{chambolle2010}, we need the proximal operators of
@@
   $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
-  \While{
+  \Repeat{
 %$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$
-$|p^Te_1^{(k)} + q^Te_2^{(k)}| > \epsilon$}{
+$|p^Te_1^{(k)} + q^Te_2^{(k)}| \le \epsilon$}{
     \begin{eqnarray*}
@@
 
-\section{Practical considerations: Exploiting the structure of the payoff matrix}
+\section{Exploiting the structure of the payoff matrix $A$}
 In each iteration of Algorithm \ref{Tab:algo_simplified}, most of the time is spent
@@
 \section{Results}
+\label{sec:results}
 To access the practical quality of the proposed algorithm, we experimented it on real and simulated games. The results are presented here.
@@
 Thus every matrix game on simplexes can be seen as a sequential game.
-
 Now, as in \textbf{nesterov, c-p, etc.}, we generate a $1000 \times 1000$ random matrix whose entries are uniformly identically distributed in the closed interval $[-1, 1]$.
@@
   \includegraphics[width=1\linewidth]{simplex_NE.pdf}
-  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} random $1000 \times 1000$ matrix game (on simplexes)}
+  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} random $1000 \times 1000$ matrix game (on simplexes).
+  \textbf{Top}: Duality gap. \textbf{Bottom}: Value of game.
+   The $\mathcal{O}(1/\epsilon)$ convergence rate of the Algorithm is clear from the curves.}
   \label{Tab:sim_dgap_curve}
@@
 \subsection{Real-world game: Kuhn 3-card Poker}
-The sequence-form representation of this simplified Poker variant was given in subsection \ref{sec:kuhn_sf}. The pair $(x^*, y^*)$ of realization plans given by
-$x^* = [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T$ and
-$y^* = [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash $10^{-4}$-equlibrium.
-computed by Algorithm  \ref{Tab:algo_simplified}.
-The convergence curve is shown in Fig \ref{Tab:dgap_curve}.
+The sequence-form representation of this simplified Poker is given by (not showing zero entries)\\
+$A = \left[\begin{array}{ccccccccccccc}
+  &   &   &   &   &   &   &   &   &   &   &   &  \\
+  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
+  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
+  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
+  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
+  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
+  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
+  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
+  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
+  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
+  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
+  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
+  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
+\end{array}\right]$,\\
+$E_1 = \left[\begin{array}{ccccccccccccc}
+1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
+-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
+  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
+  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
+  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
+\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
+and $E_2 = \left[\begin{array}{ccccccccccccc}
+1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
+-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
+-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
+\end{array}\right]$.\\
+
+The pair $(x^*, y^*)$ of realization plans given by $x^* = [1, 0.759, 0.759, 0, 0.241, \\
+1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T$ and $y^* = [1, 1, 0, 0.667, 0.333, 0.667, \\
+0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash $10^{-4}$-equlibrium computed by Algorithm  \ref{Tab:algo_simplified}.
+The convergence curves are shown in Fig \ref{Tab:dgap_curve}.
 One easy checks that this equilibrium is feasible.
@@
 Kuhn in his 1950 paper \cite{kuhn}.
-
 The evolution of the dual gap and the expected value of the game across iterations is shown in Figure \ref{Tab:dgap_curve}.
@@
   \includegraphics[width=1\linewidth]{Kuhn3112_NE.pdf}
-  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} on Kuhn 3-card Poker}
+  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} on Kuhn 3-card Poker.
+  \textbf{Top}: Duality gap. \textbf{Bottom}: Value of game.
+   The $\mathcal{O}(1/\epsilon)$ convergence rate of the Algorithm is clear from the curves.}
   \label{Tab:dgap_curve}
@@
 \medskip \noindent
-\textbf{About the author:} I'm a first-year PhD student in Computer Science at Universit\'e de Parix XI.
+%% \paragraph{About the author:} I'm a first-year PhD student in Computer Science at Universit\'e de Parix XI.
 My thesis focuses on novel techniques for optimization on Lie groups (of diffeomorphisms), and other structured manifolds, the aim being to obtain better algorithms for nonlinear registration of fMRI brain images and enhance the charting of human functional connectomes.
 
-\textbf{Acknowledgments:} ...
+%% \paragraph{Acknowledgments:} ...
 \small

### 2015-02-16 nips2015.tex
wip

@@
 \documentclass[12pt]{article}
-\usepackage{amsfonts}
 \usepackage{amssymb}
@@
 \usepackage{amsmath,amsfonts,amsthm}
+\usepackage[sc, osf]{mathpazo}  %% for nice looking formulae, etc.
 \usepackage{qtree}
@@
 %\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
+
+\usepackage[section]{placeins}
 
@@
 \\
-Parietal team, Inria Saclay Ile-de-France\\
-Saclay, France\\
-\textit{email}: firstname.lastname@inria.fr}
+Parietal team, Inria Saclay Ile-de-France, Saclay, France\\
+\textit{email}: elvis.dohmatob@inria.fr}
 
@@
 
+\providecommand{\keywords}[1]{\textbf{\textit{Index terms---}} #1}
+
 %\nipsfinalcopy % Uncomment for camera-ready version
@@
 \begin{abstract}
-We present a simple primal-dual algorithm with a low cost per iteration for computing Nash $\epsilon$-equilibria in two-person zero-sum sequential games with imcomplete information and perfect-recall (like Texas Hold'em Poker), which converges after $\mathcal{O}(1/\epsilon)$ basic iterations (i.e iterations only involving basic operations like matvec, clipping, etc., and no calls to external first-order oracles, etc.).
+We present a simple primal-dual algorithm with a low cost per iteration for computing Nash $\epsilon$-equilibria in two-person zero-sum sequential games with imcomplete information and perfect recall (like Texas Hold'em Poker), which converges after $\mathcal{O}(1/\epsilon)$ basic iterations
+(i.e iterations involving no
+%o only involving basic operations like matvec, clipping, etc., and no
+calls to external first-order oracles, etc.).
 %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall.
@@
 in \cite{chambolle2010, chambolle2014ergodic}.
-It should be noted that the latter primal-dual algorithm is not directly applicable to compute Nash equilibria for the afore-mentioned games considered here since the strategy profiles (polytopes) of players are so complex that it is not possible
+It should be noted that the latter primal-dual algorithm is not directly applicable to compute Nash equilibria for the aforementioned games considered here since the strategy profiles of players are polyhedra, so complex that it is not possible
 % (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
- to analytically compute
-% (i.e using non-iterative procedures, etc.)
+ to effectively compute % (i.e using non-iterative procedures, etc.)
 euclidean
@@
  projections (the proximal operators) thereupon.
-The core of our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point convex-convex problem which is amendable to the primal-dual scheme (i.e all proximal operators can be computed in closed-form).
+The core of our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point problem which is amenable to the primal-dual scheme.
 Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap and constant cost per iteration.
-As proof of concept, we apply our algorithm to solve Kuhn 3-card Poker \cite{kuhn}.
+As an application, we apply our algorithm to solve Kuhn 3-card Poker \cite{kuhn}.
 %% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
@@
 
+\keywords{sequential game; imcomplete information; perfect recall; sequence-form; Nash equilibrium; primal-dual algoithm; convex-optimization}
+
 \section{Introduction}
 \label{sec:intro}
-A game-theoretic aproach to playing games strategically optimally consists in computing Nash-equilibria (infact, approximations thereof) offline, and playing one's part of the equilibrium online.
-This technique is the driving-force behind solution concepts like CFR \cite{lanctot2009monte}, $\text{CFR}^{+}$, and other variants, which have recently found profound success in Poker: equilibria are computed offline (with tremendous computation resources, and the component optimal strategies are played on line by a bot, without any a posteriori computation).
-However, solving for equilibria remains a mathematical and computational challenge, especially in sequential games with imperfect information.
-This paper proposes an algorithm for solving for such equilibria approximately, in a sense which will be made clear shortly.
+A game-theoretic approach to playing games strategically optimally consists in computing Nash-equilibria (infact, approximations thereof) offline, and playing one's part of the equilibrium online.
+This technique is the driving-force behind solution concepts like CFR (\textbf{TODO: add Z.'s ref first!!!}) \cite{lanctot2009monte}, $\text{CFR}^{+}$ \textbf{TODO: add ref!!!}, and other variants, which have recently had profound success in Poker.
+However, solving games for equilibria remains a mathematical and computational challenge, especially in sequential games with imperfect information.
+This paper proposes a simple and fast algorithm for solving for such equilibria approximately, in a sense which will be made clear shortly.
 
-\subsection{Context}
-The sequence-form for two-person zero-sum games was introduced in \cite{koller1992complexity}, and the theory was further developed in \cite{von1996efficient, vonequilibrium}, where it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}, E_1 \in \mathbb{R}^{l_1 \times n_1}, E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to pairs $(x, y)$ of \textit{realization plans} which solve the primal LCP (Linear Constrained Programming) problem
+\subsection{Some notation}
+Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
+the space of all $m$-by-$n$ real matrices, and $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
+$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq 0\}$ is the nonnegative $n$-dimensional \textit{orthant}.
+The components of a vector $z \in \mathbb{R}^,$ will be denoted $z_0$, $z_1$, ..., $z_{n-1}$.
+The notation ``$z \ge 0$'' means that all the components of $z$ are nonnegative.
+For a vector $z = (z_0, z_1, ..., z_{n-1}) \in \mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
+$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with 0.
+For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$.
+The operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp} function.
+
+The \textit{spectral norm} of a matrix $K$, denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).
+
+\subsection{The problem}
+The sequence-form for two-person zero-sum games was introduced in \cite{koller1992complexity}, and the theory was further developed in \cite{von1996efficient, vonequilibrium}, where it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to pairs $(x, y)$ of \textit{realization plans} which solve the primal LCP (Linear Constrained Programming) problem
 \begin{equation}
@@
     & \underset{y,p}{\text{minimize}}
-    & & p^Te_1 \\
+    & & p_0 \\
     & \text{subject to}
-    & & -Ay + E_1^Tp \geq 0,\\
-    &&& E_2y = e_2,\\
-    &&& y \ge 0
+    &&-Ay + E_1^Tp \geq 0,\\
+    &&&\hspace{4em}E_2y = e_2,\\
+    &&&\hspace{5em} y \ge 0.
   \end{aligned}
@@
     & \underset{x,q}{\text{maximize}}
-    & & -q^Te_2 \\
+    && -q_0 \\
     & \text{subject to}
-    & & -A^Tx + E_2^Tq \leq 0,\\
-    &&& E_1x = e_1,\\
-    &&& x \ge 0
+    && -A^Tx - E_2^Tq \leq 0,\\
+    &&&\hspace{4.5em} E_1x = e_1,\\
+    &&&\hspace{5.5em} x \ge 0.
   \end{aligned}
@@
 \end{equation}
-
-with \textit{duality gap} given by\footnote{The last inequality being due to \textit{weak duality}.}
+The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$ and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual variables. 
+$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and $e_k$ is a vector of the form $[1, 0, ..., 0]$.
+In this so-called \textit{sequence-form} representation, the strategy profile of player $k$ is the polyhedron
 \begin{equation}
-  \mathcal{G}(p, q) := p^Te_1 - (-q^Te_2) = p^Te_1 + q^Te_2 \geq 0
+  Q_k := \{z \in \mathbb{R}^n_+ |\text{ }E_kz = e_k\}
+\label{eq:polyhedron}
+\end{equation}
+Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and $e_2$.
+At a feasible point $(x, y, p, q)$, the \textit{duality gap} $\mathcal{G}(x, y, p, q)$ of primal-dual pair of problems is given by\footnote{The last inequality being due to \textit{weak duality}.}
+\begin{equation}
+  0 \le \mathcal{G}(x, y, p, q) := p_0 - (-q_0) = p_0 + q_0
   \label{eq:dgap}
 \end{equation}
-
-$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and $e_k$ is a vector of the form $[1, 0, ..., 0]$.
-In this so-called \textit{sequence-form} representation (see section \ref{sec:rep} for details), the strategy profile of player $k$ is the polytope
+Define the following closed convex sets
 \begin{equation}
-  Q_k := \{z \ge 0\text{ }|\text{ }E_kz = e_k\} \subseteq \mathbb{R}^{n_k}
-\label{eq:polytope}
+  \begin{aligned}
+  \Sigma_1 &:= \{(y, p) \in \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\text{ }|\text{ } -Ay + E_1^Tp \ge 0, E_2y = e_2, y \ge 0\}\\
+  \Sigma_2 &:= \{(x, q) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}\text{ }|\text{ } -A^Tx - E_2^Tq \le 0, E_1x = e_1, x \ge 0\}
+  \end{aligned}
+  \label{eq:feasibility}
 \end{equation}
-
-It was also shown (see Theorem 3.14 of \cite{vonequilibrium}) that a $(x, y)$ is a solution to the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff there exist vectors $p$ and $q$ such that
-\begin{equation}
-  \begin{split}
-    E_1x = e_1,\text{ }x \geq 0,\hspace{1em} E_2y = e_2,\text{ }y \geq 0\\
-    -Ay + E_1^Tp \geq 0,\hspace{1em}-A^Tx + E_2^Tq \leq 0
-    \end{split}
-\end{equation}
-
-Moreover, in this case \textit{strong duality} holds and the value of the game equals $p^Te_1 = -q^Te_2$; thus the duality gap $\mathcal{G}(p, q)$ defined in \eqref{eq:dgap} vanishes.
+It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair $(x, y)$ is a solution to the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} if (and only if) there exist vectors $p$ and $q$ such that $(y, p) \in \Sigma_1$ and $(x, q) \in \Sigma_2$.
+Thus the problem of finding a Nash equilibrium is equivalent to the problem of finding a point in the cartesian product $\Sigma_1 \times \Sigma_2$.
+Moreover, at equilibria, \textit{strong duality} holds and the value of the game equals $p_0 = -q_0$, i.e the duality gap $\mathcal{G}(x, y, p, q)$ defined in \eqref{eq:dgap} vanishes at equilibria.
 
@@
 \begin{remark}  
-It should be noted that even though problem \eqref{eq:primal_pb} is in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
+It should be noted that even though problem \eqref{eq:primal_pb} is in theory, amenable to classical tools like LCP (\textit{Linear Constraint Programming}), the class of games considered here (sequential games with imcomplete information) are exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
 \end{remark}
 
-% For the purpose of completeness we will cover the sequence-form representation in \ref{sec:rep}.
-
-%% Though \textit{Nash equilibrium} has become a novel way for solving two-person zero-sum games, the problem of computing Nash equilibria for large-scale two-person zero-sum games is still largely unsolved.
-Even though this problem is, in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle.
-%% We will be needing the following notation: %%  The reader should lookup any standard textbook
-%% %% (for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions.
-%% Viz,
-%% \begin{itemize}
-%% \item $\mathbb{R}^n$: $n$-dimensional real vector space;
-%% \item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$n$ real matrices;
-%% \item $0_{m,n}$: $m$-by-$n$ matrix of zeros;
-%% \item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
-%% \item $\mathbb{R}^n_+$: \quad $\{x \in \mathbb{R}^n|x = (x)_+\}$, the $n$-dimensional nonnegative orthant 
-%% \item $i_C$: \quad indicator function of a convex set $C$;
-%% % \item $\Pi_C$: \quad euclidean projection onto a convex set $C$;
-%% \item $\|K\|_2$: \quad spectral norm of a matrix $K$
-%% % \item $F^*$: the convex conjugate of a convex function $F$.
-%% %% \item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
-%% %% \item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
-%% \end{itemize}
-
-%% \section{Statement of the problem}
-%% The Nash equilibrium problem for a two-person zero-sum sequential game with imcomplete information and perfect recall is a the saddle-point problem
-%% \begin{equation}
-%%   \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
-%%   \label{eq:primal_pb}
-%% \end{equation}
-
-%% where player $k$'s \textit{strategy profile} $Q_k$ is the polytope
-%% \begin{equation}
-%%   Q_k := \{z \in \mathbb{R}^{n_k}| E_kz = e_k\text{ and } z_j \ge 0 \text{ }\forall j\}
-%% \end{equation}
-%% for %% some convex subset $C_k$ of a euclidean space $\mathbb{R}^{n_k}$, and 
-%% some $l_k$-by-$n_k$ matrix $E_k$ and $l_k$-dimensional vector $e_k$. $A$ is the \textit{payoff matrix} from player 1's perspective of the game: if player 1 players strategy
-%% $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
-%% %% We will assume that the convex sets $C_k$ are simple enough so that the eucliean projections $\Pi_{C_k}$ can be cheaply computed.
-%% Typically, $C_k = \mathbb{R}^{l_k}_+ := \{x \in \mathbb{R}^n|x_k \ge 0\}$, the \textit{the nonnegative orthant}, and encodes a nonnegativity constraint.
-%% in this case, $\Pi_{C_k}(z) \equiv (z)_+$ as seen in subsection \ref{sec:notation}.
-%% As usual, the ``minimax'' notation in problem \eqref{eq:primal_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
-%% \begin{equation}
-%%   x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
-%% \end{equation}
-%% Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
-%% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
-
-%% We can distinguish two categories of such games, in terms of (non-)simultaneity of play.
-%% \subsection{Simultaneous two-person zero-sum games}
-%% \label{subsec:example_games}
-%% Here, the Nash equilibrium problem takes the form \eqref{eq:primal_pb} with $l_k = 1$, $C_k = \mathbb{R}^{l_k}_+$, $E_k = 1_{1, n_k}$,
-%%   and $e_k = 1$, so that $Q_k$ is simply the probabability $n_k$-simplex $\Delta_{n_k}$. Each point in $\Delta_{n_k}$ corresponds to a \textit{mixed-strategy} for player $j$,
-%% and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_k}$).
-
-%% \subsection{Two-person zero-sum sequential games with imcomplete information and perfect recall}
-%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:primal_pb}.
-
-%% We recall that in the sequence-form representation of such games,  $E_k$ is a matrix whose
-%% entries are $-1$, $0$, or $+1$, and $e_k := (1, 0, 0, ..., 0)$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
-%% encode linear constraints player 1's (resp. player 2's)  ``admissible'' \textit{realization plans} $x$ (resp. $y$).
-
-%% \subsection{Example of Nash equilibirum}
-%% As an illustration, the pair $(x^*, y^*)$ given by
-%% $x^* = [1, .478, .522, .174, .826]^T$ and
-%% $y^* = [1, 1/2, 1/2]^T$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
-%% $A = \left[\begin{array}{ccc}
-%%   &   &  \\
-%%   &   &  \\
-%%   & 1 & -1\\
-%%   & -2 & 4\\
-%% 1 &   &  
-%% \end{array}\right]$, $E_1 = \left[\begin{array}{ccccc}
-%%   1 &   &   &   &  \\
-%%   -1 & 1 & 1 &   &  \\
-%%   -1 &   &   & 1 & 1
-%% \end{array}\right]$,
-%% $E_2 = \left[\begin{array}{ccc}
-%%   1 &   &  \\
-%%   -1 & 1 & 1
-%% \end{array}\right]$, $e_1 = [1, 0, 0]^T$, and $e_2 = [1, 0]^T$.
-
-\subsection{Statement of the problem}
-Solving problem \eqref{eq:primal_pb} exactly is impossible in practice, and such a precision doesn't have any fundamental advantage.
+Solving problem \eqref{eq:primal_pb} exactly is impossible in practice \textbf{Cite Koller!!!}, and such a precision doesn't have any fundamental advantage.
 Instead, it is customary compute so-called Nash $\epsilon$-equlibria.
@@
 \begin{definition}(\textbf{Nash $\epsilon$-equilibria})
-Given a margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists dual vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} satisfying
+Given a small margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists dual vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} such that the duality gap at $(x^*, y^*, p^*, q^*)$ doesn't exceed $\epsilon$.
+That is,
 \begin{equation}
-  0 \le \mathcal{G}(p^*, q^*) \le \epsilon
+  0 \le \mathcal{G}(x^*, y^*, p^*, q^*) \le \epsilon
 \label{eq:approx_pb}
@@
 
+\subsection{Precise statement of the problem}
 The goal of this article is to device a simple algorithm which produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations.
@@
 \subsection{Outline of the article}
- Section \ref{sec:notation} exposes useful notions of convex optimization (proximal operators, convex conjugates, etc.) which will be crucial for the sequel.
+The next section features concepts from convex-analysis which will be used without further explanation.
 In section \ref{sec:related_work}, we give a brief overview of existing methods for computing Nash $\epsilon$-equilibria.
-In section \ref{sec:algo} we derive the proposed algorithm for producing a NAsh $\epsilon$-equilibrium and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.
+In section \ref{sec:algo} we derive the proposed algorithm for producing a Nash $\epsilon$-equilibrium and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.
 Section \ref{sec:results} presents practical results obtained both on simulated matrix games and the Kuhn 3-card Poker \cite{kuhn}.
 
-%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:primal_pb}.
-
-%% \section{The sequence-form representation}
-%% \label{sec:rep}
-%% In this section, we briefly recall the sequence-form representation of sequential games with imcomplete information and perfect recall.
-A complete overview of the subject can be found in the pioneering work \cite{von1996efficient}.
-
-%% \subsection{The Game tree}
-%% The game tree $\mathcal{T}$ is defined as follows.
-There are three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}.
-All three players are treated symmetrically.
-Nodes of the game tree $\mathcal{T}$ are identified with states of the game, and actions taken by players correspond to edges of $\mathcal{T}$.
-%% The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops.
-%% The sequence-form is similar to the \textit{strategic-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
-%% At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node.
-This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts.
-Due to imcompleted information, each player's nodes are grouped into equivalent classes of \textit{strategically indistinguishable} nodes called \textit{information sets}; $\mathcal{I}_k$ is the set of all information sets of player $k$.
-If each information set is a singleton, then the game reduces to a game complete information.
-
-%% $a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
-%% receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
-%% The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
-%% We will assume implicitly that each (non-chance) player is rational.
-
-%% \subsection{Player sequences}
-%% For each information set $h$ of player $k$, denote by $\sigma_h$  the sequence of choices from the root node, to $h$ (i.e to any node in $h$), ignoring the choices of the other players.
-\textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined.
-$C_h$ is the set of choices at $h$.
-The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by
-%% \begin{equation}
-%% \mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
-%% \end{equation}
-%% Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish.
-$\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
-%% $\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.
-
-%% \subsection{Pure strategies, mixed strategies, realization plans}
-%% Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$ (i.e the prescription of a move $c \in C_h$ from each information set $h \in \mathcal{I}_k$), and their \textit{mixed-strategies} are randomizations on these pure-strategies.
-A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts.
-The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.
-
-%% The strategy profile of player $k$ is then the set of $n_k$-dimensional vectors $z$ satisfying
-%% % Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
-%% \begin{equation}
-%%   z \geq 0,\hspace{1em}z(\emptyset) = 1,\hspace{1em}
-%%     z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0, \hspace{1em} \forall h \in \mathcal{I}_k
-%%   \label{eq:lin}
-%% \end{equation}
-
-%% These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
-%% where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$, and so the polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}.
-
-%% \subsection{Behavioral strategies}
-%% Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioral-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
-%% \begin{equation}
-%%   \beta_k(h, c) := \begin{cases}
-%%     z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
-%%     0, &\mbox{Otherwise}.
-%%   \end{cases}
-%% \end{equation}
-
-%% From this definition, it is clear that each behavioral-strategy is equivalent to a mixed-strategy.
-
-%% \subsection{Payoff matrix}
-%% The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
-%% \begin{equation}
-%%     A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \hspace{1em} \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
-%%   \end{equation}
-
-%% If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
-
-%% \subsection{In summary}
-%% The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form and the LCP problems correspond to the Nash \textit{minimax} problem for such games.
-However, since we are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.
-
-%% \subsection{Example: Sequence-form representation of Kuhn Poker}
-%% \label{sec:kuhn_sf}
-%% The Kuhn 3-card Poker \cite{kuhn} has sequence-form specification given by (not showing zero entries)\\
-%% $A = \left[\begin{array}{ccccccccccccc}
-%%   &   &   &   &   &   &   &   &   &   &   &   &  \\
-%%   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
-%%   &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
-%%   &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
-%%   &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
-%%   &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
-%%   &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
-%%   &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
-%%   & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
-%%   &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
-%%   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
-%%   &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
-%%   & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
-%% \end{array}\right]$,\\
-%% $E_1 = \left[\begin{array}{ccccccccccccc}
-%% 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-%% -1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
-%% -1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
-%% -1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
-%%   & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
-%%   &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
-%%   &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
-%% \end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
-%% and $E_2 = \left[\begin{array}{ccccccccccccc}
-%% 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-%% -1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
-%% -1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
-%% -1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
-%% -1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
-%% -1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
-%% -1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
-%% \end{array}\right]$.\\
-
-\section{Useful convex analysis}
+\section{Useful convex-analysis}
 \label{sec:notation}
-We will need the following notations in the sequel.
-The passionate reader should refer to the classic \cite{rockafellar1997convex} for a more elaborate presentation.
-This section can be omitted without loss of continuity.
-
-\subsection{Linear algebra, nonnegative clipping, indicator functions, euclidean projection}
-Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
-the space of all $m$-by-$n$ real matrices, and $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
-$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq 0\}$ is the nonnegative $n$-dimensional orthant.
-For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
-$(x)_+:=\text{max}(0, x)$ is the point-wise maximum of $x$ with 0.
-$(.)_+$ is the well-known (multi-dimensional) \textit{ramp} function.For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$.
-The \textit{spectral norm} of a matrix $K$,
-denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).
-
+We will need the following notations and concepts from convex-analysis in the sequel.
 Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
@@
   \end{equation}
-
 Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection} onto $C$, denoted $\Pi_C$, is the function
@@
 
-\subsection{Convex conjugates, proximal operators}
 Let $f : \mathbb{R}^n \rightarrow [-\infty, +\infty]$ be a \textit{proper convex lower semi-continous function}
@@
 as a generalization of euclidean projections.
-The passionate reader will find more on proximal operators and optimization techniques based (forward-backward, etc.) on them in \cite{combettes2011proximal}.
+
+The passionate reader should refer to \cite{rockafellar1997convex, combettes2011proximal} for a more elaborate exposition of convex-analytical concepts and their use in optimization.
 
@@
 \label{sec:related_work}
+\textbf{TODO: add note about interior-point methods!!!}
+
 We present a selection of algorithms that is representative of the efforts that have been made in the literature to compute Nash $\epsilon$-equilibria for two-person zero-sum games with imcomplete information like Texas Hold'em Poker, etc.
@@
 
-In \cite{gilpinfirst}, a modified verson of the technqiues in \cite{hoda2010smoothing} was developed.
-The authors proved a $\mathcal{O}\left(\left(\|A\| / \delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in terms of the number of calls made to a first-order oracle (for example, Nesterov's optimal gradient \cite{nesterov1983}).
-Here $\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a certain \textit{condition number} for the given game.
+\cite{gilpinfirst} proposed a modified verson of the technqiues in \cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| / \delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in terms of the number of calls made to a first-order oracle (for example, Nesterov's optimal gradient \cite{nesterov1983}).
+Here $\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a certain \textit{condition number} for the game.
 It should be noted however that
 \begin{itemize}
-\item[--] Though the authors in \cite{gilpinfirst} proved that $\delta > 0$ always, this constant can be arbitrarily small.
-\item[--] Most importantly, the reported linear convergence rate is not in terms of basic operations (addition, multiplication, matvec, clipping, etc.), but in terms of the number of calls to a first-order oracle.
+\item[--] though \cite{gilpinfirst} proved that we always have $\delta > 0$, this constant can be arbitrarily small; and most importantly,
+\item[--] the reported linear convergence rate is not in terms of basic operations (addition, multiplication, matvec, clipping, etc.), but in terms of the number of calls to a first-order oracle.
 Of course, the existence of a linear algorithm for solving \eqref{eq:gilpin} is improbable, as the usual strong-convexity conditions are absent.
@@
 
-The primal-dual algorithm first developed in \cite{chambolle2010}, was proposed \cite{chambolle2014ergodic} to solve matrix games on simplexes.
+The primal-dual algorithm first developed in \cite{chambolle2010} was proposed \cite{chambolle2014ergodic} in to solve matrix games on simplexes.
 It should be stressed that such matrix games are considerably simpler than the games considered here.
-Indeed, the authors in \cite{chambolle2014ergodic} use the fact that computing the euclidean projection of a point unto a simplex can be done in linear time \cite{duchi2008efficient}, in contrast to the polytopes $Q_k$ defined in \eqref{eq:polytope} for which no such efficient algorithm is known nor is likely to exist.
-Note that computing the euclidean projection of a point unto the polytope $Q_k$ can still be done iteratively using the algorithm in proposition 4.2 of \cite{combettes2010dualization}, for example.
-However, the authors didn't provide a convergence rate for their algorithm, and as with any nested iterative scheme, one would have to solve this sub-problem with finer and finer precision.
+Indeed, the authors in \cite{chambolle2014ergodic} use the fact that computing the euclidean projection of a point unto a simplex can be done in linear time as in \cite{duchi2008efficient}.
+In contrast, no such efficient algorithm is known nor is likely to exist for the polyhedra $Q_k$ defined in \eqref{eq:polyhedron}, the strategy profiles for players in the games considered here.
+It should however be noted that such this projection can still be done iteratively using, for example, the algorithm in proposition 4.2 of \cite{combettes2010dualization}, for example.
+Unfortunately, the authors didn't provide a convergence rate for their algorithm, and as with any nested iterative scheme, one would have to solve this sub-problem with finer and finer precision.
 
-Sampling techniques like the CFR (CounterFactual Regret minimization) and its many variants \cite{MartinZinkevichNIPS2007, lanctot2009monte, Bowling09012015} are also becoming popular.
+Sampling techniques like the CFR (CounterFactual Regret minimization) and its many variants \cite{MartinZinkevichNIPS2007, lanctot2009monte, Bowling09012015} have also become state-of-the-art.
 
-\section{The proposed algorithm}
+\section{Our main contribution}
 \label{sec:algo}
 We now present our main contribution, namely an $\mathcal{O}(1/\epsilon)$ primal-dual algorithm for computing Nash $\epsilon$-equilibria for sequential two-person zero-sum games with imcomplete information and perfect recall.
-The algorithm is obtained from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}.
+%% The algorithm is obtained from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}.
 
-\subsection{Unconstrained minimax reformulation of the problem}
-It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing the euclidean projections $\Pi_{Q_k}$.
+\subsection{Reformulation of the problem}
+It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing the euclidean projections $\Pi_{Q_k}$ (the proximal operators).
 Theorem \ref{thm:pd} provides a trick to effectively evade this difficulty, by re-writting the problem into an equivalent saddle-point convex-concave problem for which the associated proximal operators are simple.
@@
 
-  where
+  where the $(n_1 + l_2)$-by-$(n_2 + l_1)$ matrix $K$ is defined by
   \begin{equation}
@@
       \end{array}
-      \right] \in \mathbb{R}^{(n_1 + l_2) \times (n_2 + l_1)}
+      \right]
 \end{equation}
@@
   \begin{equation}
-      G_1(y, p) := i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1, \hspace{1em} G_2(x, q) := i_{\mathbb{R}^{n_1}_+}(x) + q^Te_2
+      G_1(y, p) := i_{\mathbb{R}^{n_2}_+}(y) + p_0, \hspace{1em} G_2(x, q) := i_{\mathbb{R}^{n_1}_+}(x) + q_0
     \label{eq:things}
@@
 \begin{proof}
-The optimal value, say $v$, in the dual LCP problem \eqref{eq:primal_pb} can be computed as 
+Recall the definition of the feasibility sets $\Sigma_i$ from equation \eqref{eq:feasibility}.
+The optimal value in the dual LCP problem \eqref{eq:primal_pb} can be computed as 
 \begin{eqnarray*}
   \begin{aligned}
-    v &= \underset{y,p}{\text{min}}\text{ }i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1 + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
+    p_0^* &= \text{min}\{p_0\text{ }|\text{ } (y, p) \in \Sigma_1, p = (p_0, p_1, ..., q_{l_1-1})\}\\
+    &= \underset{y,p}{\text{min}}\text{ }i_{\mathbb{R}^{n_2}_+}(y) + p_0 + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
     &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e2)\\
@@
     &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x, q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y - i_{\mathbb{R}^{n_1}_+}(x) - q^Te_2\\
+    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x, q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y - (i_{\mathbb{R}^{n_1}_+}(x) + q_0)\\
     &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x,q}{\text{max}}\text{ }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} - G_2(x, q) \\
@@
 \end{eqnarray*}
-
 Thus the LCP problem \eqref{eq:primal_pb} can be written as 
@@
 \end{equation}
-
-By a similarly calculation, one shows that the LCP problem \eqref{eq:dual_pb} is equivalent to
+Similarly, the optimal value in the dual LCP problem \eqref{eq:dual_pb} writes
+\begin{eqnarray*}
+  \begin{aligned}
+ -q_0^* &= \text{max}\{-q_0\text{ }|\text{ } (x, q) \in \Sigma_2, q = (q_0, q_1, ..., q_{l_2-1})\}\\
+    &= \underset{x,q}{\text{max}}\text{ }-(i_{\mathbb{R}^{n_1}_+}(x) + q_0) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) - i_{\{0\}}(E_1x - e_1)\\
+    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q) - \underset{y \geq 0}{\text{max}}\text{ }y^T(-A^Tx + E_2^Tq) - \underset{p}{\text{max}}\text{ }p^T(E_1x-e_1)\\
+    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q) -\underset{y,p}{\text{max}}\text{ }-(y^TA^Tx -p^TE_1x + y^TE_2^Tp)-(i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1)\\
+    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q)-\underset{y,p}{\text{max}}\text{ }-
+ \begin{bmatrix}y\\p\end{bmatrix}K^T\begin{bmatrix}x\\q\end{bmatrix}-G_1(y,p)\\
+   &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q)-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right)
+  \end{aligned}
+\end{eqnarray*}
+Thus the LCP problem \eqref{eq:dual_pb} is equivalent to
 \begin{equation}
@@
 
-\subsection{Derivation of the algorithm and its convergence rate}
+\subsection{The proposed algorithm and its $\mathcal{O}(1/\epsilon)$ convergence}
+According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCP problems \eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the saddle-point problem \eqref{eq:unconstrained_pb}.
 In order to apply Algorithm 39 of \cite{chambolle2010}, we need the proximal operators of
@@
   \end{equation}
-
 Indeed both $G_1$ and $F$ are separable sums of the indicator function of a convex set, whose prox is simply the euclidean projection onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox, at rank $\tau$, is simply $z \mapsto z - \tau a$.
-
-Applying Algorithm 39 of \cite{chambolle2010} to problem \eqref{eq:unconstrained_pb}, we obtain Algorithm \ref{Tab:algo_simplified} for solving the original problem \eqref{eq:primal_pb}.
-The $\mathcal{O}(1/\epsilon)$ convergence rate of Algorothm \ref{Tab:algo_simplified} hails directly from Theorem 1 of \cite{chambolle2010}.
-Note however that this convergence rate cannot be improved in the framework of \cite{chambolle2010}, since neither $G_1$ nor $G_2$ is \textit{uniformly convex}.
-
+Applying Algorithm 39 of \cite{chambolle2010} to problem \eqref{eq:unconstrained_pb}, we obtain Algorithm \ref{Tab:algo_simplified}.
+It's $\mathcal{O}(1/\epsilon)$ convergence rate is immediate.
+Indeed,
 %% \subsection{Special case: $C_k = \mathbb{R}^{n_k}_+$} As discussed in subsection \ref{subsec:example_games},
@@
 %$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$
-$|p^Te_1^{(k)} + q^Te_2^{(k)}| \le \epsilon$}{
+$|p_0^{(k)} + q_0^{(k)}| \le \epsilon$}{
     \begin{eqnarray*}
@@
 \end{algorithm}
+\begin{theorem}
+  \label{thm:conv}
+  Algorithm \ref{Tab:algo_simplified} produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations.
+\end{theorem}
 
-\section{Exploiting the structure of the payoff matrix $A$}
+\begin{proof}
+This follows directly from Theorem 1 of \cite{chambolle2010}, and from the equivalence establised in Theorem \ref{thm:pd} above.
+\end{proof}
+
+\begin{remark}
+Note however that this convergence rate cannot be improved in the framework of \cite{chambolle2010}, since neither $G_1$ nor $G_2$ is \textit{uniformly convex}.
+\end{remark}
+
+\section{Efficient computation of $Ay$ and $A^Tx$}
 In each iteration of Algorithm \ref{Tab:algo_simplified}, most of the time is spent
@@
 
+\begin{remark}
+The results presented here are not meant to be benchmarks comparing our algorithm to other algorithms, but should rather be seen as proof-of-concept which experimentally  validates the rigorously extablished results in section \ref{sec:algo}.
+
+\end{remark}
+
 \subsection{Simulated game: matrix game on simplexes}
 Any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a \textit{matrix game}.
-The strategy profile of player $k$ is a simplex; this simplex can be written in the form \eqref{eq:polytope} by taking $E_k := [1, 1, ..., 1] \in \mathbb{R}^{1 \times n_k}$ and $e_k = 1$.
+The strategy profile of player $k$ is a simplex; this simplex can be written in the form \eqref{eq:polyhedron} by taking $E_k := [1, 1, ..., 1] \in \mathbb{R}^{1 \times n_k}$ and $e_k = 1$.
 Thus every matrix game on simplexes can be seen as a sequential game.
@@
   \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} random $1000 \times 1000$ matrix game (on simplexes).
-  \textbf{Top}: Duality gap. \textbf{Bottom}: Value of game.
-   The $\mathcal{O}(1/\epsilon)$ convergence rate of the Algorithm is clear from the curves.}
+  \textbf{Top}: Duality gap. \textbf{Bottom}: Value of game.}
   \label{Tab:sim_dgap_curve}
@@
 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T$ and $y^* = [1, 1, 0, 0.667, 0.333, 0.667, \\
-0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash $10^{-4}$-equlibrium computed by Algorithm  \ref{Tab:algo_simplified}.
+0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of Algorithm  \ref{Tab:algo_simplified}.
 The convergence curves are shown in Fig \ref{Tab:dgap_curve}.
@@
 The evolution of the dual gap and the expected value of the game across iterations is shown in Figure \ref{Tab:dgap_curve}.
-These figures validates the theoritically established $\mathcal{O}(1/\epsilon)$ convergence rate of the Algorithm.
-
-\begin{remark}
-The results of the experiments presented here are not benchmarks comparing our algorithm to other algorithms, though it would be nice to do such benchmarks in a future work.
-\end{remark}
+These figures validate the theoritically established $\mathcal{O}(1/\epsilon)$ convergence rate of the Algorithm.
 
@@
   \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} on Kuhn 3-card Poker.
-  \textbf{Top}: Duality gap. \textbf{Bottom}: Value of game.
-   The $\mathcal{O}(1/\epsilon)$ convergence rate of the Algorithm is clear from the curves.}
+  \textbf{Top}: Duality gap. \textbf{Bottom}: Value of game.}
   \label{Tab:dgap_curve}
@@
 \section{Conclusion}
-For the first time, we have applied a primal-dual algorithm to the problem of computing Nash equilibria for two-person zero-sum sequential games with imcomplete information (like Texas Hold'em, etc.).
-Our algorithm is simple to implement, with a very low constant cost per iteration, and enjoys a rigorous convergence theory with a proven $\mathcal{O}(1/\epsilon)$ convergence in terms of basic operations (matvec products, clipping, etc.), to a Nash $\epsilon$-equilibrium of the game...
+Making use of the sequence-form representation \cite{koller1992complexity, von1996efficient, vonequilibrium}, we have deviced a primal-dual algorithm for computing Nash equilibria in two-person zero-sum sequential games with imcomplete information (like Texas Hold'em, etc.).
+Our algorithm is simple to implement, with a very low constant cost per iteration, and enjoys a rigorous convergence theory with a proven $\mathcal{O}(1/\epsilon)$ convergence in terms of basic operations (matvec products, clipping, etc.), to a Nash $\epsilon$-equilibrium of the game.
+The core of our contribution (summarized in Theorems \ref{thm:pd} and \ref{thm:conv}) was to show that a reformulation of the Nash equilibrium problem for sequential games with imcomplete information lends the problem directly accessible to primal-dual framework \cite{chambolle2010, chambolle2014ergodic}.
+
+Equilibrium problems are saddle-point convex-concave problems, and as such a natural choice for an algorithm would be in the family of primal-dual algorithms.
+The author believes such primal-dual schemes will gain more attention in the algorithmic game theory community in future.
 
@@
 
-%% \paragraph{Acknowledgments:} ...
+\paragraph{Acknowledgments:} ...
 \small

### 2015-02-16 primal_dual.py

@@ -56,7 +56,7 @@ def evil(L, r, z, proj_C=lambda v: np.maximum(v, 0.), L_norm=None,
 
 def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
                    proj_C2=lambda y: np.maximum(y, 0.), init=None,
-                   tol=1e-8, max_iter=10000, inertia=None, rho=None,
+                   tol=1e-8, max_iter=1000, inertia=None, rho=None,
                    good_init=False):
     """Primal-Dual algorithm for computing Nash equlibrium for two-person
     zero-sum game with payoff matrix A and contraint sets

### 2015-02-16 simple.py

@@ -918,7 +918,8 @@ if __name__ == "__main__":
             E2, e2 = game.constraints[2]
             A = game.payoff_matrix
             args = (A, E1, E2, e1, e2)
-            x, y, values, dgaps = primal_dual_ne(A, E1, E2, e1, e2)
+            x, y, values, dgaps = primal_dual_ne(A, E1, E2, e1, e2,
+                                                 max_iter=2000)
         print
         print "Nash Equilibrium:"
         print "x* = ", x
@@ -934,7 +935,7 @@ if __name__ == "__main__":
                         "-1 / 18" if isinstance(game, Kuhn3112) else
                         ("-1 / 4" if isinstance(game, SimplifiedPoker)
                          else "%.2e" % value)), linewidth=4, color="k")
-        plt.xlabel("$k$", fontsize=25)
+        plt.xlabel("$k$ (iteration count)", fontsize=25)
         plt.ylabel("value of game after $k$ iterations", fontsize=25)
         plt.legend(loc="best", prop=dict(size=25))
         # plt.title("%s: Sequence-form NE computation" % (
@@ -947,7 +948,7 @@ if __name__ == "__main__":
         plt.loglog(1. / np.arange(1, len(dgaps) + 1),
                    label="$\\mathcal{O}(1/k)$", linewidth=4, color="k")
         plt.loglog(np.abs(dgaps), label="Primal-Dual", linewidth=4)
-        plt.xlabel("$k$", fontsize=25)
+        plt.xlabel("$k$ (iteration count)", fontsize=25)
         plt.ylabel(
             "Duality gap $|e_1^Tp^{(k)} + e_2^Tq^{(k)}|$ after $k$ iterations",
             fontsize=25)

### 2015-02-19 nips2015.tex
wip

@@
 
+%% prevent figures, algorithms, etc., floating across subsections
 \usepackage[section]{placeins}
+\makeatletter
+\AtBeginDocument{%
+  \expandafter\renewcommand\expandafter\subsection\expandafter{%
+    \expandafter\@fb@secFB\subsection
+  }%
+}
+\makeatother
 
@@
 in \cite{chambolle2010, chambolle2014ergodic}.
-It should be noted that the latter primal-dual algorithm is not directly applicable to compute Nash equilibria for the aforementioned games considered here since the strategy profiles of players are polyhedra, so complex that it is not possible
+It should be noted that the latter primal-dual algorithm is not directly applicable to compute Nash equilibria for the aforementioned games considered here since the strategy profiles of players (polyhedra) are so complex that it is not possible
 % (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
@@
 Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap and constant cost per iteration.
-As an application, we apply our algorithm to solve Kuhn 3-card Poker \cite{kuhn}.
+As an application, we apply our algorithm to solve Kuhn 3-card Poker.
 %% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
@@
 \subsection{Some notation}
-Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
-the space of all $m$-by-$n$ real matrices, and $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
+Let $m$ and $n$ be positive integers.
 $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq 0\}$ is the nonnegative $n$-dimensional \textit{orthant}.
-The components of a vector $z \in \mathbb{R}^,$ will be denoted $z_0$, $z_1$, ..., $z_{n-1}$.
+The components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$).
 The notation ``$z \ge 0$'' means that all the components of $z$ are nonnegative.
 For a vector $z = (z_0, z_1, ..., z_{n-1}) \in \mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
-$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with 0.
+$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$.
 For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$.
@@
 
-The \textit{spectral norm} of a matrix $K$, denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).
+$\mathbb{R}^{m \times n}$ denotes the space of all $m$-by-$n$ real matrices, and $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
+Given a matrix $A \in \mathbb{R}^{m \times n}$, its entries will be donoted $A_{i,j}$ so that
+\[
+A :=\left[
+\begin{array}{cccc}
+A_{0,0} & A_{0,1} & \cdots & A_{0,n-1} \\
+A_{1,0} & A_{1,1} & \cdots & A_{1,n-1} \\
+\vdots & \vdots & \ddots & \vdots\\
+A_{m-1,0} & A_{m-1,1} & \cdots & A_{m-1,n-1}
+\end{array}\right]
+\]
+The \textit{spectral norm} of a matrix $A$, denoted $\|A\|$, is defined to be the largest \textit{singular value} of $A$, i.e the largest \textit{eigen-value} of $A^TA$ (or equivalently, of $AA^T$).
 
@@
 The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$ and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual variables. 
-$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and $e_k$ is a vector of the form $[1, 0, ..., 0]$.
+$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form $[1, 0, ..., 0]$.
 In this so-called \textit{sequence-form} representation, the strategy profile of player $k$ is the polyhedron
@@
 Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and $e_2$.
-At a feasible point $(x, y, p, q)$, the \textit{duality gap} $\mathcal{G}(x, y, p, q)$ of primal-dual pair of problems is given by\footnote{The last inequality being due to \textit{weak duality}.}
+At a feasible point $(y, p, x, q)$, the \textit{duality gap} $\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCP problems is given by\footnote{The inequality being due to \textit{weak duality}.}
 \begin{equation}
-  0 \le \mathcal{G}(x, y, p, q) := p_0 - (-q_0) = p_0 + q_0
+  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0
   \label{eq:dgap}
@@
 Thus the problem of finding a Nash equilibrium is equivalent to the problem of finding a point in the cartesian product $\Sigma_1 \times \Sigma_2$.
-Moreover, at equilibria, \textit{strong duality} holds and the value of the game equals $p_0 = -q_0$, i.e the duality gap $\mathcal{G}(x, y, p, q)$ defined in \eqref{eq:dgap} vanishes at equilibria.
+Moreover, at equilibria, \textit{strong duality} holds and the value of the game equals $p_0 = -q_0$, i.e the duality gap $\mathcal{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at equilibria.
 
@@
 \begin{remark}  
-It should be noted that even though problem \eqref{eq:primal_pb} is in theory, amenable to classical tools like LCP (\textit{Linear Constraint Programming}), the class of games considered here (sequential games with imcomplete information) are exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
+It should be noted that for the the class of games considered here (sequential games with imcomplete information), the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger than what state-of-the-art LCP solvers can handle.
+See \cite{hoda2010smoothing}.
 \end{remark}
 
-Solving problem \eqref{eq:primal_pb} exactly is impossible in practice \textbf{Cite Koller!!!}, and such a precision doesn't have any fundamental advantage.
+Solving the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly is impossible in practice \textbf{Cite Koller!!!}, and such a precision doesn't have any fundamental advantage.
 Instead, it is customary compute so-called Nash $\epsilon$-equlibria.
@@
 \begin{definition}(\textbf{Nash $\epsilon$-equilibria})
-Given a small margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists dual vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} such that the duality gap at $(x^*, y^*, p^*, q^*)$ doesn't exceed $\epsilon$.
+Given a small margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists dual vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} such that the duality gap at $(y^*, p^*, x^*, q^*)$ doesn't exceed $\epsilon$.
 That is,
 \begin{equation}
-  0 \le \mathcal{G}(x^*, y^*, p^*, q^*) \le \epsilon
+  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon
 \label{eq:approx_pb}
@@
 \end{equation}
-For example, the euclidean projections onto the nonnegative orthant and the closed unit-disk $\bar{\Delta}$
+As an example, the euclidean projections onto the nonnegative orthant and the closed unit-disk $\bar{\Delta}$
 % := \{x|\|x\| \le 1\}$
@@
 
-Let $f : \mathbb{R}^n \rightarrow [-\infty, +\infty]$ be a \textit{proper convex lower semi-continous function}
-(\textit{p.c.l.s.c} for short). The \textit{convex conjugate} of $f$ is the function $f^*: \mathbb{R}^n \rightarrow [-\infty, +\infty]$ is defined by
+Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a \textit{proper} (meaning that it is not identically $\infty$) convex function.
+%% \textit{proper convex lower semi-continous function}
+%% (\textit{p.c.l.s.c} for short).
+The \textit{convex conjugate} of $f$ is the function $f^*: \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by
 \begin{equation}
@@
 \end{equation}
+For example, $i_{\mathbb{R}^{n}_+}^*(x) \equiv i_{\mathbb{R}^{n}_+}(-x)$; $(a^Tx)^* \equiv i_{\{0\}}(x - a)$; and $(\frac{1}{2}\|x\|^2)^* \equiv \frac{1}{2}\|x\|^2$.
+One easily verifies that $f^{**} = f$, if $f$ is \textit{lower semi-continuous}.
+The \textit{domain} of $f$ is defined by
+\begin{equation}
+dom f := \{x \in \mathbb{R}^n | f(x) < \infty\}
+\end{equation}
+If $dom f = \mathbb{R}^{n}$, then we say $f$ has \textit{full domain}.
+Note that if $x \mapsto \dfrac{f(x)}{\|x\|}$ is unbounded, then $f^*$ has full domain.
 
-For example $i_{\mathbb{R}^{n}_+}^*(x) \equiv i_{\mathbb{R}^{n}_+}(-x)$; $(a^Tx)^* \equiv i_{\{0\}}(x - a)$; and $(\frac{1}{2}\|x\|^2)^* \equiv \frac{1}{2}\|x\|^2$.
-One easily verifies that $f^{**} = f$.
-Given $\tau > 0$, the \textit{proximal operator} of $f$ of rank
+Let $f$ be as above. Given $\tau > 0$, the \textit{proximal operator} of $f$, at rank
 $\tau$, denoted $\text{prox}_{\tau f}$, is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
@@
 \end{equation}
-
 It is easy to see that if $f$ is the indicator function of a convex set $C$, then $\text{prox}_{\tau f} = \Pi_C, \forall \tau > 0$. In this sense, proximal operators can be seen
@@
 \end{equation}
-
 But these last two equations are simply the primal and dual formulations respectively, of the saddle-point problem \eqref{eq:unconstrained_pb}, and we are done.
@@
 According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCP problems \eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the saddle-point problem \eqref{eq:unconstrained_pb}.
-In order to apply Algorithm 39 of \cite{chambolle2010}, we need the proximal operators of
-$G_1$ and $G_2$. Now, both functions are \textit{p.c.l.s.c} and their proximal operators are given by
+In order to apply Algorithm 39 of \cite{chambolle2010}, we need formulae for the proximal operators of
+$G_1$ and $G_2$.
+Now, either of $G_1$ and $G_2$ is a separable sum of the indicator function of a convex set, whose prox is simply the euclidean projection onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox is simply $z \mapsto z - \tau a$.
+Thus,  one computes their respective proximal operators $\text{prox}_{\tau G_1} : \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}$, $\text{prox}_{\sigma G_2}: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}$ as
   \begin{equation}
-    \left .
-    \begin{split}
-      \text{prox}_{\tau G_1} : \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\\
-      (y, p) &\mapsto ((y)_+, p - \tau e_1)\\
-    \end{split}
-    \right\}
+    \text{prox}_{\tau G_1}(y, p) = ((y)_+, p - \tau e_1), \hspace{1em} \text{prox}_{\sigma G_2}(x, q) = ((x)_+, q - \sigma e_2)
   \end{equation}
 
-  and
-  \begin{equation}
-    \left .
-    \begin{split}
-      \text{prox}_{\sigma G_2}: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}\\
-      (x, q) &\mapsto ((x)_+, q - \sigma e_2)
-    \end{split}
-    \right\}
-  \end{equation}
-Indeed both $G_1$ and $F$ are separable sums of the indicator function of a convex set, whose prox is simply the euclidean projection onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox, at rank $\tau$, is simply $z \mapsto z - \tau a$.
-Applying Algorithm 39 of \cite{chambolle2010} to problem \eqref{eq:unconstrained_pb}, we obtain Algorithm \ref{Tab:algo_simplified}.
-It's $\mathcal{O}(1/\epsilon)$ convergence rate is immediate.
+Finally, applying Algorithm 39 of \cite{chambolle2010} to problem \eqref{eq:unconstrained_pb} we obtain Algorithm \ref{Tab:algo_simplified}.
+Its $\mathcal{O}(1/\epsilon)$ convergence rate in terms of the duality gap is immediate.
 Indeed,
@@
 
-\section{Efficient computation of $Ay$ and $A^Tx$}
+\subsection{Efficient computation of $Ay$ and $A^Tx$}
 In each iteration of Algorithm \ref{Tab:algo_simplified}, most of the time is spent
 pre-multiplying vectors by $A$ and $A^T$.
-For \textit{flop}-type Poker games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em}, $A$ (and thus $A^T$ too) has a rich structure.
-For example, in Rhode Island Hold'em, the payoff matrix $A$ can be written as block-diagonal matrix whose blocks are sums of Kronecker products of much smaller sparse matrices \cite{hoda2010smoothing} $F_1$, $B_1$, $F_2$, $B_2$, $F_3$, $B_3$, $S$, and $W$.
-Viz
+For \textit{flop}-type Poker games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em}, $A$ (and thus $A^T$ too) has a rich block-diagnoal structure which can be carefully exploited.
+
+\begin{definition}(Kronecker product)
+Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
 
 \begin{equation}
-  A = \begin{bmatrix}A_1\hspace{2em}\\\hspace{1em}A_2\hspace{1em}\\\hspace{2em}A_3\end{bmatrix}
+F \otimes B:=\left[
+\begin{array}{cccc}
+F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
+F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
+\vdots & \vdots & \ddots & \vdots\\
+F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
+\end{array}\right] \in \mathbb{R}^{mr \times ns}
+\end{equation}
+\end{definition}
+
+One notes that $(F \otimes B)^T = F^T \otimes B^T$.
+$F \otimes B$ can be very much larger than both $F$ and $B$ in dimensions.
+For example, if $r = n = r = s = 1000$, so that $F$ and $B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a $10^6$-by-$10^6$ matrix!
+Fortunately, given a vector $x \in \mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$ without forming $F \otimes B$.
+Indeed, let $y := (F \otimes B)x$.
+We rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1, ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of $s$ elements of $x$ read from left to right.
+Similarly, rewrite $y$ as as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$.
+Then one easily verfies that $Y$ is the matrix product of the ``small'' matrices $B$, $X$, and $F^T$, i.e
+\begin{equation}
+  \label{eq:kron_matvec}
+  Y = BXF^T
+\end{equation}
+
+Now, in Texas Hold'em for example, the payoff matrix $A$ can be written as block-diagonal matrix whose blocks are sums of Kronecker products of much smaller sparse matrices as follows
+
+\begin{equation}
+  A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2 \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
 \label{eq:factor_A}
 \end{equation}
-where,
-\begin{equation}
-A_1 = F_1 \otimes B_1, \hspace{1em} A_1 = F_2 \otimes B_2, \hspace{1em} A_3 = F_3 \otimes B_3 + S \otimes W
-\end{equation}
-
+See \cite{hoda2010smoothing}.
 The matrices $F_i$ correspond to sequences of moves in round $i$ which end in a \textit{fold} action, and $S$ to the sequences which end in a \textit{showdown}.
 $B_i$ encodes the betting structure of round $i$, while $W$ encodes the wind/lose/draw information determined by ranking the players' hands at showdown.
-As reported in \cite{hoda2010smoothing}, the dimensions of $B_1$, $B_2$, and $B_3$ are $13 \times 13$, $205 \times 205$, and $1774 \times 1774$, respectively.
-By
-contrast, the matrix $A$ is $883741 \times 883741$. Furthermore, the matrices $F_i$, $B_i$,
+The component matrices $F_i$, $B_i$, $S$, and $W$ are small enough to be explictly represented whereas it is infeasible to explicitly represent A.
+Furthermore, the matrices $F_i$, $B_i$,
 $S$, and $W$ are themselves sparse, which allows one to use the compressed row storage data structure that only stores nonzero entries (for example \textit{scipy.sparse.csr\_matrix}, in the Python programming language).
 
-Such a representation of the payoff matrix $A$ trivializes matvec operations involving $A$ or $A^T$.
+Such a representation of the payoff matrix $A$ trivializes matvec operations involving $A$ or $A^T$ (thanks to equation \eqref{eq:kron_matvec} above, applied to their diagonal blocks and exploiting the sparsity of these blocks themselves).
 Of course, one can always write the payoff matrix $A$ of a flop-type Poker game in a form similary to \eqref{eq:factor_A} by applying appropriate permutations to the enumeration of the players's sequences.
@@
 \begin{figure}
-  \includegraphics[width=1\linewidth]{simplex_dgap.pdf}
-  \includegraphics[width=1\linewidth]{simplex_NE.pdf}
+  \includegraphics[width=.56\linewidth]{simplex_dgap.pdf}
+  \includegraphics[width=.56\linewidth]{simplex_NE.pdf}
   \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} random $1000 \times 1000$ matrix game (on simplexes).
-  \textbf{Top}: Duality gap. \textbf{Bottom}: Value of game.}
+  \textbf{Left}: Duality gap. \textbf{Right}: Value of game.}
   \label{Tab:sim_dgap_curve}
@@
 \subsection{Real-world game: Kuhn 3-card Poker}
-The sequence-form representation of this simplified Poker is given by (not showing zero entries)\\
-$A = \left[\begin{array}{ccccccccccccc}
+The sequence-form representation of this simplified Poker variant \cite{kuhn} is given by (not showing zero entries)\\
+$E_1 = \left[\begin{array}{ccccccccccccc}
+1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
+-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
+  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
+  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
+  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
+\end{array}\right] \in \mathbb{R}^{7 \times 13}$,\\
+$E_2 = \left[\begin{array}{ccccccccccccc}
+1 &   &   &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
+-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
+-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
+-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
+-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
+\end{array}\right] \in \mathbb{R}^{7 \times 13}$, \\ $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T \in \mathbb{R}^7$, and $A = \\\left[\begin{array}{ccccccccccccc}
   &   &   &   &   &   &   &   &   &   &   &   &  \\
@@
   & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
-\end{array}\right]$,\\
-$E_1 = \left[\begin{array}{ccccccccccccc}
-1 &   &   &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
--1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
-  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
-  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
-  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
-\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
-and $E_2 = \left[\begin{array}{ccccccccccccc}
-1 &   &   &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
--1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
--1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
-\end{array}\right]$.\\
-
-The pair $(x^*, y^*)$ of realization plans given by $x^* = [1, 0.759, 0.759, 0, 0.241, \\
-1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T$ and $y^* = [1, 1, 0, 0.667, 0.333, 0.667, \\
-0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of Algorithm  \ref{Tab:algo_simplified}.
+\end{array}\right]$.
+The pair $(x^*, y^*) \in \mathbb{R}^{13} \times \mathbb{R}^{13}$ of realization plans given by
+\begin{eqnarray*}
+  \begin{split}
+    x^* &= [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T,\\
+    y^* &= [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T
+    \end{split}
+\end{eqnarray*}
+is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of Algorithm  \ref{Tab:algo_simplified}.
 The convergence curves are shown in Fig \ref{Tab:dgap_curve}.
 One easy checks that this equilibrium is feasible.
-Indeed,  $E_1x^* - e_1 = [4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T$ and $E_2y^* - e_2 = [-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6}, 2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7}]^T$.
-Finally, $x^*TAy^* = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by H.
-W.
-Kuhn in his 1950 paper \cite{kuhn}.
+Indeed,
+\begin{eqnarray*}
+  \begin{split}
+    E_1x^* - e_1 = [&4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, \\&
+      -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T
+    \end{split}
+\end{eqnarray*}
+and
+
+\begin{eqnarray*}
+  \begin{split}
+    E_2y^* - e_2 = [&-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6},\\
+      &2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7}]^T
+    \end{split}
+\end{eqnarray*}
+Finally, ${x^*}^TAy^* = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}.
 The evolution of the dual gap and the expected value of the game across iterations is shown in Figure \ref{Tab:dgap_curve}.
@@
 \begin{figure}
-  \includegraphics[width=1\linewidth]{Kuhn3112_dgap.pdf}
-  \includegraphics[width=1\linewidth]{Kuhn3112_NE.pdf}
+  \includegraphics[width=.56\linewidth]{Kuhn3112_dgap.pdf}
+  \includegraphics[width=.56\linewidth]{Kuhn3112_NE.pdf}
   \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} on Kuhn 3-card Poker.
-  \textbf{Top}: Duality gap. \textbf{Bottom}: Value of game.}
+  \textbf{Left}: Duality gap. \textbf{Right}: Value of game.}
   \label{Tab:dgap_curve}
@@
 Equilibrium problems are saddle-point convex-concave problems, and as such a natural choice for an algorithm would be in the family of primal-dual algorithms.
-The author believes such primal-dual schemes will gain more attention in the algorithmic game theory community in future.
+The author believes such primal-dual schemes will receive more attention in the algorithmic game theory community in future.
 

### 2015-02-19 simple.py

@@ -927,20 +927,23 @@ if __name__ == "__main__":
 
         # plot evoluation of game value
         plt.figure(figsize=(13.5, 10))
-        plt.semilogx(values, linewidth=4)
+        ax = plt.subplot("111")
+        ax.semilogx(values, linewidth=4)
         value = values[-1]
-        plt.axhline(-1. / 18. if isinstance(game, Kuhn3112) else value,
-                    linestyle="--",
-                    label="true value of the game: $%s$" % (
-                        "-1 / 18" if isinstance(game, Kuhn3112) else
-                        ("-1 / 4" if isinstance(game, SimplifiedPoker)
-                         else "%.2e" % value)), linewidth=4, color="k")
-        plt.xlabel("$k$ (iteration count)", fontsize=25)
-        plt.ylabel("value of game after $k$ iterations", fontsize=25)
-        plt.legend(loc="best", prop=dict(size=25))
+        ax.axhline(-1. / 18. if isinstance(game, Kuhn3112) else value,
+                   linestyle="--",
+                   label="true value of the game: $%s$" % (
+                       "-1 / 18" if isinstance(game, Kuhn3112) else
+                       ("-1 / 4" if isinstance(game, SimplifiedPoker)
+                    else "%.2e" % value)), linewidth=4, color="k")
+        ax.set_xlabel("$k$ (iteration count)", fontsize=30)
+        ax.set_ylabel("value of game after $k$ iterations", fontsize=30)
+        plt.legend(loc="best", prop=dict(size=30))
         # plt.title("%s: Sequence-form NE computation" % (
         #         game.__class__.__name__))
-        plt.tick_params(axis='both', which='major', labelsize=20)
+        plt.tick_params(axis='both', which='major', labelsize=35)
+        ax.ticklabel_format(axis="y", style="sci")
+        plt.tight_layout()
         plt.savefig("%s_NE.pdf" % name)
 
         # plot evolution of gual gap
@@ -948,12 +951,12 @@ if __name__ == "__main__":
         plt.loglog(1. / np.arange(1, len(dgaps) + 1),
                    label="$\\mathcal{O}(1/k)$", linewidth=4, color="k")
         plt.loglog(np.abs(dgaps), label="Primal-Dual", linewidth=4)
-        plt.xlabel("$k$ (iteration count)", fontsize=25)
[…]

### 2015-05-30 nips2015.tex
ENH: better figs

@@
-\documentclass[12pt]{article}
-\usepackage{amssymb}
-\usepackage{color}
-
-%% \documentclass{article} % For LaTeX2e
-%% \usepackage{nips14submit_e,times}
-\usepackage{hyperref}
+\documentclass{article} % For LaTeX2e
+\usepackage{nips14submit_e}%,times}
+%\usepackage{hyperref}
 \usepackage{url}
 \usepackage{amsmath,amsfonts,amsthm}
-\usepackage[sc, osf]{mathpazo}  %% for nice looking formulae, etc.
-\usepackage{qtree}
-\usepackage{natbib}
+\usepackage{bbm}
+\usepackage{algorithm,algorithmic}
 \usepackage{graphicx}
-%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
+\usepackage{bm}
+\usepackage{bbm}
+\usepackage[titletoc]{appendix}
 
-%% prevent figures, algorithms, etc., floating across subsections
-\usepackage[section]{placeins}
-\makeatletter
-\AtBeginDocument{%
-  \expandafter\renewcommand\expandafter\subsection\expandafter{%
-    \expandafter\@fb@secFB\subsection
-  }%
-}
-\makeatother
+%\usepackage[section]{placeins}
+\usepackage{subfigure}
 
-\usepackage{bm}
 \def\B#1{\bm{#1}}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\renewcommand{\labelitemi}{--}
+
+\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
+
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{remark}{Remark}
+\newtheorem{fact}{Fact}
+
+\DeclareMathOperator{\proj}{proj}
+\DeclareMathOperator{\prox}{Prox}
 
@@
 
-\newcommand{\fix}{\marginpar{FIX}}
-\newcommand{\new}{\marginpar{NEW}}
- \DeclareMathOperator{\prox}{prox}
-\DeclareMathOperator{\im}{im}
-
-\newtheorem{remark}{Remark}
-
-\def \lb {{\langle}} \def \rb {{\rangle}}
-\newcommand{\fro}[1]{\|#1\|_2}
-\newcommand{\theHalgorithm}{\arabic{algorithm}}
-
-\newcommand{\argmin}{\mathop{\mathrm{argmin}}}
-
-\usepackage{hyperref}
-
-\usepackage[ruled,vlined]{algorithm2e}
-\usepackage{framed}
-\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{definition}[theorem]{Definition}
-
-\providecommand{\keywords}[1]{\textbf{\textit{Index terms---}} #1}
-
 %\nipsfinalcopy % Uncomment for camera-ready version
@@
 \begin{abstract}
-We present a simple primal-dual algorithm with a low cost per iteration for computing Nash $\epsilon$-equilibria in two-person zero-sum sequential games with imcomplete information and perfect recall (like Texas Hold'em Poker), which converges after $\mathcal{O}(1/\epsilon)$ basic iterations
-(i.e iterations involving no
-%o only involving basic operations like matvec, clipping, etc., and no
-calls to external first-order oracles, etc.).
-%% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall.
-The applicability to the latter kind of games is thanks to the sequen e-form representation von Stengel's \cite{von1996efficient}
-Our algorithm derives from the general primal-dual algorithm developed
+We present a simple primal-dual algorithm
+%with low costs per iteration,
+for computing Nash-equilibria in two-person zero-sum sequential games
+with imcomplete information and perfect recall (like Texas Hold'em
+Poker). This primal-dual algorithm derives from the general
+primal-dual algorithm developed
 % by Chambolle and Pock
-in \cite{chambolle2010, chambolle2014ergodic}.
-It should be noted that the latter primal-dual algorithm is not directly applicable to compute Nash equilibria for the aforementioned games considered here since the strategy profiles of players (polyhedra) are so complex that it is not possible
-% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
+in \cite{chambolle2010,chambolle2014ergodic}. It should be noted that
+the latter primal-dual algorithm is not directly applicable to compute
+Nash equilibria for the aforementioned games considered here since the
+strategy profiles of players (polyhedra) are so complex that it is not
+possible
+% (for example, simplexes for simultaneous games, and intersections of
+% hyperplanes and nonnegative orthants, for sequential games)
  to effectively compute % (i.e using non-iterative procedures, etc.)
@@
  projections (the proximal operators) thereupon.
-The core of our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point problem which is amenable to the primal-dual scheme.
-Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap and constant cost per iteration.
+The core of our technique is to rewrite the equilibrium problem as an
+equivalent saddle-point problem for which the proximal operators can
+be computed analytically.
+ %% dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point problem which is amenable to the primal-dual scheme.
+Our algorithm only performs basic iterations
+(i.e iterations involving no
+% only involving basic operations like matvec, clipping, etc., and no
+calls to external first-order oracles, etc.).
+Our algorithm is applicable to a broad class of two-person zero-sum
+games including simultaneous games and sequential games with
+imcomplete information and perfect recall. The applicability to the
+latter kind of games is thanks to the sequence-form representation von
+Stengel's \cite{von1996efficient}
+%% Unlike the EGT (Excessive Gap Technique) recently used in
+%% \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap
+%% and constant cost per iteration.
 As an application, we apply our algorithm to solve Kuhn 3-card Poker.
@@
 
-\keywords{sequential game; imcomplete information; perfect recall; sequence-form; Nash equilibrium; primal-dual algoithm; convex-optimization}
+\textbf{keywords}: sequential game; imcomplete information; perfect
+recall; sequence-form; Nash equilibrium; primal-dual algoithm;
+split-feasibility problem; convex-optimization
 
@@
 \label{sec:intro}
-A game-theoretic approach to playing games strategically optimally consists in computing Nash-equilibria (infact, approximations thereof) offline, and playing one's part of the equilibrium online.
-This technique is the driving-force behind solution concepts like CFR (\textbf{TODO: add Z.'s ref first!!!}) \cite{lanctot2009monte}, $\text{CFR}^{+}$ \textbf{TODO: add ref!!!}, and other variants, which have recently had profound success in Poker.
-However, solving games for equilibria remains a mathematical and computational challenge, especially in sequential games with imperfect information.
-This paper proposes a simple and fast algorithm for solving for such equilibria approximately, in a sense which will be made clear shortly.
+A game-theoretic approach to playing games strategically optimally
+consists in computing Nash-equilibria (infact, approximations thereof)
+offline, and playing one's part of the equilibrium online. This
+technique is the driving-force behind solution concepts like CFR
+(\textbf{TODO: add Z.'s ref first!!!}) \cite{lanctot2009monte},
+$\text{CFR}^{+}$ \textbf{TODO: add ref!!!}, and other variants, which
+have recently had profound success in Poker. However, solving games
+for equilibria remains a mathematical and computational challenge,
+especially in sequential games with imperfect information. This paper
+proposes a simple and fast algorithm for solving for such equilibria
+approximately, in a sense which will be made clear shortly.
 
-\subsection{Some notation}
+\subsection{Some notation and terminology}
 Let $m$ and $n$ be positive integers.
-$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq 0\}$ is the nonnegative $n$-dimensional \textit{orthant}.
-The components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$).
-The notation ``$z \ge 0$'' means that all the components of $z$ are nonnegative.
-For a vector $z = (z_0, z_1, ..., z_{n-1}) \in \mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
-$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$.
-For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$.
-The operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp} function.
+$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
+0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
+components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
+$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
+notation ``$z \ge 0$'' means that all the components of $z$ are
+nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
+\mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
+%% by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
+$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
+maximum of $z$ with $0$.
+%% For example, $((-2, \pi))_+ = (max(-2, 0),
+%% max(\pi, 0)) = (0, \pi)$.
+The operator $(.)_+$ is the well-known
+(multi-dimensional) \textit{ramp} function.
+$\mathbb{R}^{m \times n}$ denotes the space of all $m$-by-$n$ real
+matrices, $I_m$ denotes the $m$-by-$m$ identity matrix, and $0_{m,n}$
+denotes the $m$-by-$n$ matrix of zeros.
 
-$\mathbb{R}^{m \times n}$ denotes the space of all $m$-by-$n$ real matrices, and $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
-Given a matrix $A \in \mathbb{R}^{m \times n}$, its entries will be donoted $A_{i,j}$ so that
-\[
-A :=\left[
-\begin{array}{cccc}
-A_{0,0} & A_{0,1} & \cdots & A_{0,n-1} \\
-A_{1,0} & A_{1,1} & \cdots & A_{1,n-1} \\
-\vdots & \vdots & \ddots & \vdots\\
-A_{m-1,0} & A_{m-1,1} & \cdots & A_{m-1,n-1}
-\end{array}\right]
-\]
-The \textit{spectral norm} of a matrix $A$, denoted $\|A\|$, is defined to be the largest \textit{singular value} of $A$, i.e the largest \textit{eigen-value} of $A^TA$ (or equivalently, of $AA^T$).
+Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
+  norm}, denoted $\|A\|$, is
+ defined to be the largest \textit{singular value} of $A$, i.e the
+ largest \textit{eigen-value} of $A^TA$ (or equivalently, of $AA^T$).
 
-\subsection{The problem}
-The sequence-form for two-person zero-sum games was introduced in \cite{koller1992complexity}, and the theory was further developed in \cite{von1996efficient, vonequilibrium}, where it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to pairs $(x, y)$ of \textit{realization plans} which solve the primal LCP (Linear Constrained Programming) problem
+Given a subset $C$ of $\mathbb{R}^n$,
+$i_C$ denotes its \textit{indicator function} defined by $i_C(x) = 0$
+if $ x \in C$; $i_c(x) = \infty$ otherwise.
+
+Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
+  \textit{proper} (meaning that it is not identically $\infty$) convex
+  function.
+%% \textit{proper convex lower semi-continous function}
+%% (\textit{p.c.l.s.c} for short).
+The \textit{convex conjugate} of $f$ is the function $f^*:
+\mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
+  \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
+Given $\tau > 0$, the \textit{proximal operator}
+of $f$ at rank $\tau$, denoted $\prox_{\tau f}$, is the
+function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
+unique) solution of the problem $\underset{z \in
+  \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)$.
+
+The interested reader should refer to
+\cite{rockafellar1997convex,combettes2011proximal} for a more
+elaborate exposition of convex-analytical concepts and their use in
+optimization.
+
+\subsection{Statement of the problem}
+The sequence-form for two-person zero-sum games was introduced in
+\cite{koller1992complexity}, and the theory was further developed in
+\cite{von1996efficient,vonequilibrium}, where it was established that
+for sequential two-person zero-sum games with imcomplete information
+and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1
+  \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in
+\mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1},
+e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are
+all linear in the size of the game tree (number of states in the game)
+and such that Nash equilibria correspond to pairs $(x, y)$ of
+\textit{realization plans} which solve the primal LCP
 \begin{equation}
   \begin{aligned}
-    & \underset{y,p}{\text{minimize}}
-    & & p_0 \\
-    & \text{subject to}
-    &&-Ay + E_1^Tp \geq 0,\\
-    &&&\hspace{4em}E_2y = e_2,\\
-    &&&\hspace{5em} y \ge 0.
+     \text{minimize }p_0, \hspace{.5em}\text{ subject to }(y,p) \in
+     \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}, -Ay +
+    E_1^Tp \geq 0, E_2y = e_2, y \ge 0.
   \end{aligned}
@@
 
-and the dual LCP problem
+and the dual LCP
 \begin{equation}
   \begin{aligned}
-    & \underset{x,q}{\text{maximize}}
-    && -q_0 \\
-    & \text{subject to}
-    && -A^Tx - E_2^Tq \leq 0,\\
-    &&&\hspace{4.5em} E_1x = e_1,\\
-    &&&\hspace{5.5em} x \ge 0.
+    \text{maximize}-q_0,\hspace{.5em}\text{subject to }(y,q) \in
+    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, -A^Tx - E_2^Tq \leq 0,
+    E_1x = e_1, x \ge 0.
   \end{aligned}
@@
 \end{equation}
-The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$ and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual variables. 
-$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form $[1, 0, ..., 0]$.
-In this so-called \textit{sequence-form} representation, the strategy profile of player $k$ is the polyhedron
+The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
+and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
+variables. 
+$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
+entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
+$[1, 0, ..., 0]$. In this so-called \textit{sequence-form}
+representation, the strategy profile of player $k$ is the polyhedron
 \begin{equation}
@@
 \end{equation}
-Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and $e_2$.
-At a feasible point $(y, p, x, q)$, the \textit{duality gap} $\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCP problems is given by\footnote{The inequality being due to \textit{weak duality}.}
+Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and
+$e_2$. At a feasible point $(y, p, x, q)$, the \textit{duality gap}
+$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
+by\footnote{The inequality being due to \textit{weak duality}.}
 \begin{equation}
@@
 \end{equation}
-Define the following closed convex sets
+
+%\subsection{Characterization of equilibria}
+It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
+$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
+LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
+equilibrium for the game)  if and only if there exist vectors $p$ and
+$q$ such that
 \begin{equation}
-  \begin{aligned}
-  \Sigma_1 &:= \{(y, p) \in \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\text{ }|\text{ } -Ay + E_1^Tp \ge 0, E_2y = e_2, y \ge 0\}\\
-  \Sigma_2 &:= \{(x, q) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}\text{ }|\text{ } -A^Tx - E_2^Tq \le 0, E_1x = e_1, x \ge 0\}
-  \end{aligned}
+\hspace{.25em} -Ay + E_1^Tp \ge 0, \hspace{.5em}A^Tx + E_2^Tq \ge
+0, \hspace{.25em} x^T(-Ay + E_1^Tp) = 0, \hspace{.25em} y^T(A^Tx +
+E_2^Tq) = 0.
 \label{eq:feasibility}
 \end{equation}
-It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair $(x, y)$ is a solution to the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} if (and only if) there exist vectors $p$ and $q$ such that $(y, p) \in \Sigma_1$ and $(x, q) \in \Sigma_2$.
-Thus the problem of finding a Nash equilibrium is equivalent to the problem of finding a point in the cartesian product $\Sigma_1 \times \Sigma_2$.
+
 Moreover, at equilibria, \textit{strong duality} holds and the value of the game equals $p_0 = -q_0$, i.e the duality gap $\mathcal{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at equilibria.
@@
 \begin{remark}  
-It should be noted that for the the class of games considered here (sequential games with imcomplete information), the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger than what state-of-the-art LCP solvers can handle.
+It should be noted that for the the class of games considered here (sequential games with imcomplete information), the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger than what state-of-the-art LCP solvers can handle.
 See \cite{hoda2010smoothing}.
@@
 
-Solving the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly is impossible in practice \textbf{Cite Koller!!!}, and such a precision doesn't have any fundamental advantage.
+Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly is impossible in practice \textbf{Cite Koller!!!}, and such a precision doesn't have any fundamental advantage.
 Instead, it is customary compute so-called Nash $\epsilon$-equlibria.
@@
 \subsection{Outline of the article}
-The next section features concepts from convex-analysis which will be used without further explanation.
-In section \ref{sec:related_work}, we give a brief overview of existing methods for computing Nash $\epsilon$-equilibria.
-In section \ref{sec:algo} we derive the proposed algorithm for producing a Nash $\epsilon$-equilibrium and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.
-Section \ref{sec:results} presents practical results obtained both on simulated matrix games and the Kuhn 3-card Poker \cite{kuhn}.
-
-\section{Useful convex-analysis}
-\label{sec:notation}
-We will need the following notations and concepts from convex-analysis in the sequel.
-Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
-\begin{equation}
-  i_C(x) = \begin{cases}
-    0, &\mbox{if } x \in C\\
-    +\infty, &\mbox{otherwise}.
-    \end{cases}
-  \end{equation}
-Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection} onto $C$, denoted $\Pi_C$, is the function
-$\Pi: \mathbb{R}^n \mapsto C$ which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closest to $x$. Precisely,
-\begin{equation}
-  \Pi_C(x) := \underset{c \in C}{argimin}\text{ }\|c - x\|^2
-\end{equation}
-As an example, the euclidean projections onto the nonnegative orthant and the closed unit-disk $\bar{\Delta}$
-% := \{x|\|x\| \le 1\}$
-are $\Pi_{\mathbb{R}^n_+}(x) \equiv (x)_+$ and $\Pi_{\bar{\Delta}}(z) \equiv \dfrac{z}{max(\|z\|, 1)}$ respectively.
-
-Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a \textit{proper} (meaning that it is not identically $\infty$) convex function.
-%% \textit{proper convex lower semi-continous function}
-%% (\textit{p.c.l.s.c} for short).
-The \textit{convex conjugate} of $f$ is the function $f^*: \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by
-\begin{equation}
-  x \mapsto f^*(x) := \underset{z \in \mathbb{R}^n}{\text{max}}\text{ }z^Tx - f(z)
-\end{equation}
-For example, $i_{\mathbb{R}^{n}_+}^*(x) \equiv i_{\mathbb{R}^{n}_+}(-x)$; $(a^Tx)^* \equiv i_{\{0\}}(x - a)$; and $(\frac{1}{2}\|x\|^2)^* \equiv \frac{1}{2}\|x\|^2$.
-One easily verifies that $f^{**} = f$, if $f$ is \textit{lower semi-continuous}.
-The \textit{domain} of $f$ is defined by
-\begin{equation}
-dom f := \{x \in \mathbb{R}^n | f(x) < \infty\}
-\end{equation}
-If $dom f = \mathbb{R}^{n}$, then we say $f$ has \textit{full domain}.
-Note that if $x \mapsto \dfrac{f(x)}{\|x\|}$ is unbounded, then $f^*$ has full domain.
-
-Let $f$ be as above. Given $\tau > 0$, the \textit{proximal operator} of $f$, at rank
-$\tau$, denoted $\text{prox}_{\tau f}$, is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
-unique) solution of the problem
-\begin{equation}
-  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
-\end{equation}
-It is easy to see that if $f$ is the indicator function of a convex set $C$, then $\text{prox}_{\tau f} = \Pi_C, \forall \tau > 0$. In this sense, proximal operators can be seen
-as a generalization of euclidean projections.
-
-The passionate reader should refer to \cite{rockafellar1997convex, combettes2011proximal} for a more elaborate exposition of convex-analytical concepts and their use in optimization.
+We develop a $\mathcal{O}(1/\epsilon)$ primal-dual algorithm for computing Nash
+$\epsilon$-equilibria for sequential two-person zero-sum games with
+imcomplete information and perfect recall.
 
@@
 
-In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used to to solve the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form
+In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used to to solve the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form
 
@@
 
-The primal-dual algorithm first developed in \cite{chambolle2010} was proposed \cite{chambolle2014ergodic} in to solve matrix games on simplexes.
-It should be stressed that such matrix games are considerably simpler than the games considered here.
-Indeed, the authors in \cite{chambolle2014ergodic} use the fact that computing the euclidean projection of a point unto a simplex can be done in linear time as in \cite{duchi2008efficient}.
-In contrast, no such efficient algorithm is known nor is likely to exist for the polyhedra $Q_k$ defined in \eqref{eq:polyhedron}, the strategy profiles for players in the games considered here.
-It should however be noted that such this projection can still be done iteratively using, for example, the algorithm in proposition 4.2 of \cite{combettes2010dualization}, for example.
-Unfortunately, the authors didn't provide a convergence rate for their algorithm, and as with any nested iterative scheme, one would have to solve this sub-problem with finer and finer precision.
+The primal-dual algorithm first developed in \cite{chambolle2010} was
+proposed \cite{chambolle2014ergodic} in to solve matrix games on
+simplexes. It should be stressed that such matrix games are
+considerably simpler than the games considered here. Indeed, the
+authors in \cite{chambolle2014ergodic} use the fact that computing the
+euclidean projection of a point unto a simplex can be done in linear
+time as in \cite{duchi2008efficient}. In contrast, no such efficient
+algorithm is known nor is likely to exist for the polyhedra $Q_k$
+defined in \eqref{eq:polyhedron}, the strategy profiles for players in
+the games considered here. It should however be noted that such this
+projection can still be done iteratively using, for example, the
+algorithm in proposition 4.2 of \cite{combettes2010dualization} or any
+CQ algorithm (since this projection sub-problem, is, in fact a
+\textit{split-feasibility problem}), for example. Unfortunately, as
+with any nested iterative scheme, one would have to solve this
+sub-problem with finer and finer precision.
 
-Sampling techniques like the CFR (CounterFactual Regret minimization) and its many variants \cite{MartinZinkevichNIPS2007, lanctot2009monte, Bowling09012015} have also become state-of-the-art.
+Sampling techniques like the CFR (CounterFactual Regret minimization)
+and its many variants
+\cite{MartinZinkevichNIPS2007,lanctot2009monte,Bowling09012015} have
+also become state-of-the-art.
 
-\section{Our main contribution}
+\section{Our contributions}
 \label{sec:algo}
-We now present our main contribution, namely an $\mathcal{O}(1/\epsilon)$ primal-dual algorithm for computing Nash $\epsilon$-equilibria for sequential two-person zero-sum games with imcomplete information and perfect recall.
-%% The algorithm is obtained from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}.
-
-\subsection{Reformulation of the problem}
-It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing the euclidean projections $\Pi_{Q_k}$ (the proximal operators).
-Theorem \ref{thm:pd} provides a trick to effectively evade this difficulty, by re-writting the problem into an equivalent saddle-point convex-concave problem for which the associated proximal operators are simple.
+\subsection{Primal-dual algorithm}
+It should be noted that the difficulty of applying the general
+primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to
+problem \eqref{eq:primal_pb} lies in the difficulty of effectively
+computing the euclidean projections $\proj_{Q_k}$ (which are the
+proximal operators here). Theorem \ref{thm:pd} provides a trick to
+effectively evade this difficulty, by re-writting the problem into an
+equivalent saddle-point convex-concave problem for which the
+associated proximal operators are simple.
 
 \begin{theorem}
-  The Nash equilibrium LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} can be re-written in the saddle-point convex-concove form
+  The Nash equilibrium LCPs \eqref{eq:primal_pb} and
+  \eqref{eq:dual_pb} are equivalent to the following convex-concave
+  saddle-point problems
 
@@
     \left[
-      \begin{array}{c|c}
-        A & -E_1^T \\ \hline
+      \begin{array}{cc}
+        A & -E_1^T \\
         E_2 & 0_{l_2, l_1}
@@
 \begin{proof}
-Recall the definition of the feasibility sets $\Sigma_i$ from equation \eqref{eq:feasibility}.
-The optimal value in the dual LCP problem \eqref{eq:primal_pb} can be computed as 
+Define the following closed convex sets
 \begin{eqnarray*}
   \begin{aligned}
-    p_0^* &= \text{min}\{p_0\text{ }|\text{ } (y, p) \in \Sigma_1, p = (p_0, p_1, ..., q_{l_1-1})\}\\
-    &= \underset{y,p}{\text{min}}\text{ }i_{\mathbb{R}^{n_2}_+}(y) + p_0 + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
-    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e2)\\
-    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x \geq 0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) + \underset{q}{\text{max}}\text{ }q^T(E_2y - e_2)\\
-    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x, q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y - i_{\mathbb{R}^{n_1}_+}(x) - q^Te_2\\
-    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x, q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y - (i_{\mathbb{R}^{n_1}_+}(x) + q_0)\\
-    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x,q}{\text{max}}\text{ }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} - G_2(x, q) \\
-      &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
+  \Sigma_2 &:= \{(y, p) \in \mathbb{R}^{n_2} \times
+  \mathbb{R}^{l_1}\text{ }|\text{ } -Ay + E_1^Tp \ge 0, E_2y = e_2, y
+  \ge 0\}\\
+  \Sigma_1 &:= \{(x, q) \in \mathbb{R}^{n_1} \times
+  \mathbb{R}^{l_2}\text{ }|\text{ } -A^Tx - E_2^Tq \le 0, E_1x = e_1,
+  x \ge 0\}
+  \end{aligned}
+\end{eqnarray*}
+The optimal value in the dual LCP \eqref{eq:primal_pb} can be computed as 
+\begin{eqnarray*}
+  \begin{aligned}
+    p_0^* &= \text{min}\{p_0\text{ }|\text{ } (y, p) \in \Sigma_2, p =
+    (p_0, p_1, ..., q_{l_1-1})\}\\
+    &= \underset{y,p}{\text{min}}\text{ }p_0 +
+    i_{\mathbb{R}^{n_2}_+}(y) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) +
+    i_{\{0\}}(E_2y - e_2)\\
+    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) +
+    i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
+    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x \geq
+      0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) +
+    \underset{q}{\text{max}}\text{ }q^T(E_2y - e_2)\\
+    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x,
+      q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y -
+    i_{\mathbb{R}^{n_1}_+}(x) - q^Te_2\\
+    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x,
+      q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y -
+    (i_{\mathbb{R}^{n_1}_+}(x) + q_0)\\
+    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) +
+    \underset{x,q}{\text{max}}\text{
+    }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix}
+      - G_2(x, q) = \underset{y,p}{\text{min}}\text{ }G_1(y,p) +
+      G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
   \end{aligned}
@@
 \end{eqnarray*}
-Thus the LCP problem \eqref{eq:primal_pb} can be written as 
+Thus the LCP \eqref{eq:primal_pb} can be written as 
 \begin{equation}
-  \underset{y,p}{\text{minimize}}\text{ }G_1(y,p) + G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
+  \underset{y,p}{\text{minimize}}\text{ }G_1(y,p) +
+  G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
 \end{equation}
-Similarly, the optimal value in the dual LCP problem \eqref{eq:dual_pb} writes
+Similarly, the optimal value in the dual LCP \eqref{eq:dual_pb} writes
 \begin{eqnarray*}
   \begin{aligned}
- -q_0^* &= \text{max}\{-q_0\text{ }|\text{ } (x, q) \in \Sigma_2, q = (q_0, q_1, ..., q_{l_2-1})\}\\
-    &= \underset{x,q}{\text{max}}\text{ }-(i_{\mathbb{R}^{n_1}_+}(x) + q_0) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) - i_{\{0\}}(E_1x - e_1)\\
-    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q) - \underset{y \geq 0}{\text{max}}\text{ }y^T(-A^Tx + E_2^Tq) - \underset{p}{\text{max}}\text{ }p^T(E_1x-e_1)\\
-    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q) -\underset{y,p}{\text{max}}\text{ }-(y^TA^Tx -p^TE_1x + y^TE_2^Tp)-(i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1)\\
-    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q)-\underset{y,p}{\text{max}}\text{ }-
- \begin{bmatrix}y\\p\end{bmatrix}K^T\begin{bmatrix}x\\q\end{bmatrix}-G_1(y,p)\\
-   &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q)-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right)
+ -q_0^* &= \text{max}\{-q_0\text{ }|\text{ } (x, q) \in \Sigma_1, q =
+ (q_0, q_1, ..., q_{l_2-1})\}\\
+    &= \underset{x,q}{\text{max}}\text{ }-q_0 -
+ i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
+ i_{\{0\}}(E_1x - e_1)\\
+    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q) - \underset{y \geq
+   0}{\text{max}}\text{ }y^T(-A^Tx - E_2^Tq) -
+ \underset{p}{\text{max}}\text{ }p^T(E_1x-e_1)\\
+    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q)
+ -\underset{y,p}{\text{max}}\text{ }-(y^TA^Tx -p^TE_1x +
+ y^TE_2^Tq)-(i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1)\\
+    &= \underset{x,q}{\text{max}}\text{ }-G_2(x,
+ q)-\underset{y,p}{\text{max}}\text{ }-
+ \begin{bmatrix}y\\p\end{bmatrix}K^T\begin{bmatrix}x\\q\end{bmatrix}-G_1(y,p)
+   = \underset{x,q}{\text{max}}\text{ }-G_2(x,
+   q)-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right),
   \end{aligned}
 \end{eqnarray*}
-Thus the LCP problem \eqref{eq:dual_pb} is equivalent to
+and so the the LCP \eqref{eq:dual_pb} is equivalent to
 \begin{equation}
-  \underset{x,q}{\text{maximize}}\text{ }-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right) - G_2(x, q)
+  \underset{x,q}{\text{maximize}}\text{
+  }-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right) - G_2(x, q)
 \end{equation}
-But these last two equations are simply the primal and dual formulations respectively, of the saddle-point problem \eqref{eq:unconstrained_pb}, and we are done.
+But these last two equations are simply the primal and dual
+formulations respectively, of the saddle-point problem
+\eqref{eq:unconstrained_pb}, and we are done.
 
@@
 
-\subsection{The proposed algorithm and its $\mathcal{O}(1/\epsilon)$ convergence}
-According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCP problems \eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the saddle-point problem \eqref{eq:unconstrained_pb}.
-In order to apply Algorithm 39 of \cite{chambolle2010}, we need formulae for the proximal operators of
-$G_1$ and $G_2$.
-Now, either of $G_1$ and $G_2$ is a separable sum of the indicator function of a convex set, whose prox is simply the euclidean projection onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox is simply $z \mapsto z - \tau a$.
-Thus,  one computes their respective proximal operators $\text{prox}_{\tau G_1} : \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}$, $\text{prox}_{\sigma G_2}: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}$ as
+% \subsection{The proposed algorithm and its $\mathcal{O}(1/\epsilon)$
+% convergence}
+
+\paragraph{In summary.}
+According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCPs
+\eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the
+saddle-point problem \eqref{eq:unconstrained_pb}.
+In order to apply Algorithm 39 of \cite{chambolle2010}, we need
+formulae for the proximal operators of
+$G_1$ and $G_2$. Now, either of $G_1$ and $G_2$ is a separable sum of
+the indicator function of a convex set, whose prox is simply the
+euclidean projection onto the set,  and a linear transformation $z
+\mapsto a^Tz$ whose prox is simply $z \mapsto z - \tau a$. Thus,  one
+computes their respective proximal operators $\prox_{\tau G_1} :
+\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow \mathbb{R}^{n_2}
+\times \mathbb{R}^{l_1}$, $\prox_{\sigma G_2}: \mathbb{R}^{n_1} \times
+\mathbb{R}^{l_2} \rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}$
+as
+
   \begin{equation}
-    \text{prox}_{\tau G_1}(y, p) = ((y)_+, p - \tau e_1), \hspace{1em} \text{prox}_{\sigma G_2}(x, q) = ((x)_+, q - \sigma e_2)
+    \prox_{\tau G_1}(y, p) = ((y)_+, p - \tau e_1), \hspace{1em}
+    \prox_{\sigma G_2}(x, q) = ((x)_+, q - \sigma e_2)
   \end{equation}
@@
 %% information and perfect recall admits the formulation \eqref{eq:primal_pb}, with $C_k = \mathbb{R}^{n_k}_+$ (coding for nonnegativity constraints).
-%% In such situations, $\Pi_{C_k}(z) \equiv (z)_+$ as already mentioned in \ref{sec:notation}, and Algorithm \ref{Tab:algo} reduces to the simpler Algorithm \ref{Tab:algo_simplified}.
+%% In such situations, $\proj_{C_k}(z) \equiv (z)_+$ as already mentioned in \ref{sec:notation}, and Algorithm \ref{Tab:algo} reduces to the simpler Algorithm \ref{Tab:algo_simplified}.
 
 \begin{algorithm}[G_2]
-  \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for finding a Nash $\epsilon$-equilibrium for a sequential two-person zero-sum game with imcomplete information and perfect recall}
-  \KwIn{sequence-form specification of the game: $(A, E_1, E_2, e_1, e_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
-  $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, $e_1 \in \mathbb{R}^{l_1}$, $e_2 \in \mathbb{R}^{l_2}$}
-  \KwOut{Nash $\epsilon-$equilibrium pair $(x^{(k)}$, $y^{(k)})$ of realization plans}
-  \textbf{Precompute}: $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
-  \textbf{Initialize}:
-  $x^{(0)} \in \mathbb{R}^{n_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $p \in \mathbb{R}^{l_1}$; $q^{(0)} \in \mathbb{R}^{l_2}$; 
-  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
-  \Repeat{
-%$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$
-$|p_0^{(k)} + q_0^{(k)}| \le \epsilon$}{
-    \begin{eqnarray*}
-      x^{(k+1)} &\leftarrow& \left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{p}^{(k)}\right)\right)_+\\
-      q^{(k+1)} &\leftarrow& q^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
-      y^{(k+1)} &\leftarrow& \left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tq^{(k + 1)}\right)\right)_+\\
-      p^{(k+1)} &\leftarrow& p^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
-      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
-      \tilde{p}^{(k+1)} &\leftarrow& 2p^{(k+1)} - p^{(k)}\\
-      k &\leftarrow& k + 1
-    \end{eqnarray*}
-  }
+%%   \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for finding a Nash $\epsilon$-equilibrium for a sequential two-person zero-sum game with imcomplete information and perfect recall}
+%%   \KwIn{sequence-form specification of the game: $(A, E_1, E_2, e_1, e_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
+%%   $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, $e_1 \in \mathbb{R}^{l_1}$, $e_2 \in \mathbb{R}^{l_2}$}
+%%   \KwOut{Nash $\epsilon-$equilibrium pair $(x^{(k)}$, $y^{(k)})$ of realization plans}
+%%   \textbf{Precompute}: $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
+%%   \textbf{Initialize}:
+%%   $x^{(0)} \in \mathbb{R}^{n_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $p \in \mathbb{R}^{l_1}$; $q^{(0)} \in \mathbb{R}^{l_2}$; 
+%%   $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
+%%   \Repeat{
+%% %$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$
+%% $|p_0^{(k)} + q_0^{(k)}| \le \epsilon$}{
+%%     \begin{eqnarray*}
+%%       x^{(k+1)} &\leftarrow& \left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{p}^{(k)}\right)\right)_+\\
+%%       q^{(k+1)} &\leftarrow& q^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
+%%       y^{(k+1)} &\leftarrow& \left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tq^{(k + 1)}\right)\right)_+\\
+%%       p^{(k+1)} &\leftarrow& p^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
+%%       \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
+%%       \tilde{p}^{(k+1)} &\leftarrow& 2p^{(k+1)} - p^{(k)}\\
+%%       k &\leftarrow& k + 1
+%%     \end{eqnarray*}
+%%   }
   \label{Tab:algo_simplified}
 \end{algorithm}
+
 \begin{theorem}
@@
 This follows directly from Theorem 1 of \cite{chambolle2010}, and from the equivalence establised in Theorem \ref{thm:pd} above.
+\qed
 \end{proof}
@@
 
+%% \subsection{CQ algorithm for solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb}}
+%% In this section, we will reformulate the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} as a \textit{multi-set split-feasibility problem (MSSFP)} which is amenable to the CQ algorithm.
+
+%% Now, let $\mathcal{H}_1$ and $\mathcal{H}_2$ denote the finite-dimensional Hilbert spaces $\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \times \mathbb{R}^{n_2}$ and $\mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \times \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}$ respectively, and consider the following multi-set split-feasibility problem:
+%% \begin{eqnarray}
+%%   \text{Find }(y, p, u, x, q, v) \in \cap_{k=0}^{2}C_k \text{ such that }  L(y, p, u, x, q, v) \in Q
+%%   \label{eq:sf_pb}
+%% \end{eqnarray}
+%% where:
+%% \begin{itemize}
+%%   \item $L: \mathcal{H}_1 \rightarrow \mathcal{H}_2$  is the finite-dimensional (thus bounded) linear operator defined by its matrix
+%% \begin{eqnarray}
+%%   \begin{split}
+%%   L(y, p, u, x, q, v) &:= \left[
+%%     \begin{array}{cccccc}
+%%       -A & E_1^T & -I_{n_1} & 0_{n_1,n_1} & 0_{n_1, l_2} & 0_{n_1, n_2}\\ % \hline
+%%       E_2 & 0_{l_2, l_1} & 0_{l_2, n_1} & 0_{l_2, n_1} & 0_{l_2, l_2} & 0_{l_2, n_2}\\ %\hline
+%%       0_{n_2, n_2} & 0_{n_2, l_1} & 0_{n_2, n_1} & A^T & E_2^T & -I_{n_2}\\ %\hline
+%%       0_{l_1, n_2} & 0_{l_1, l_1} & 0_{l_1, n_1} & E_1 & 0_{l_1, l_2} & 0_{l_1, n_2} 
+%%       \end{array}
+%%     \right]\begin{bmatrix}y\\p\\u\\x\\q\\v\end{bmatrix}\\
+%%     &= (-Ay + E_1^T - u, E_2y, A^Tx + E_2^Tq - v, E_1x)
+%%   \end{split}
+%% \end{eqnarray}
+
+%% \item the closed convex set $Q \subseteq \mathcal{H}_2$ is the singleton
+%% \begin{equation}
+%%   Q := \{e\}, \hspace{.5em} e:=(0_{n_1}, e_2, 0_{n_2}, e_1)
+%% \end{equation}
+
+%% \item the closed sets $C_k$ are of the form
+%% \begin{eqnarray}
+%%   \begin{split}
+%%     C_0 &:= \{(y, p, u, x, q, v) \in \mathcal{H}_1| y \ge 0, u\ge 0, x \ge 0, v\ge0\},\\
+%%   C_1 &:= \{(y, p, u, x, q, v) \in \mathcal{H}_1 |c_1(y, p, u, x, q, v) := y^Tv\le 0\},\\
+%%   C_2 &:= \{(y, p, u, x, q, v) \in \mathcal{H}_1 |c_2(y, p, u, x, q, v) := x^Tu\le 0\}
+%%   \end{split}
+%%   \label{eq:Ck}
+%% \end{eqnarray}
+%% \end{itemize}
+
+%% Note that $C_0$ is convex, whilst the functions $c_k$ are $(S, r)$-subdifferentiable with $S := \{0\}$ and $r = 1$.
+%% Before exploiting the developments sofar in this section, let's begin with a Lemma.
+%% \begin{lemma}
+%% If a hextupule $(y, p, u, x, q, v) \in C$ solves the MSSFP \eqref{eq:sf_pb}, then the pair $(x, y) \in Q_1 \times Q_2$ of realization plans is a Nash equilibrium.
+%% \end{lemma}
+%% \begin{proof}
+%% Simply introduce auxiliary variables $u := -Ay + E_1^Tq$ and $v = A^Tx + E_2^Tq$ in \eqref{eq:feasibility} and note that if $(y,p,u,x,q,v) \in \cap_{k=0}^{2}C_k$ and $L(y,p,u,x,q,v) \in Q$, then $y\ge0$, $u\ge0$, $x\ge0$, $v\ge0$, $E_2y- e_2 = 0$, $E_1x-e_1=0$, $-Ay + E_1^Tp - u=0$, $A^Tx + E_2^Tq - v = 0$, $y^Tv = 0$, and $x^Tu = 0$, which are precisely the conditions in \eqref{eq:feasibility}.
+\qed
+
+%% \end{proof}
+
+%% Now, observe that $C$ is the set of minimizers of the convex function
+%% \begin{equation}
+%% f(y, p, u, x, q, v) := \sum_{j=0}^{n_1-1}{h(x_j, u_j)} + \sum_{j=0}^{n_2-1}{h(y_j, v_j)},
+%% \end{equation}
+%% where the continuous convex function $h$ is defined by
+%% \begin{eqnarray}
+%%   h(a, b) = \frac{1}{2}\begin{cases}
+%%     a^2, &\mbox{if } a \ge (b)_+\\
+%%     b^2, &\mbox{if } b \ge (a)_+\\
+%%     0, &\mbox{if } max(a, b) \le 0.
+%%   \end{cases}
+%%    \label{eq:h_func}
+%% \end{eqnarray}
+%% We'll be needing the following Lemma concerning the prox of $h$.
+
+%% \begin{figure}
+%%   \includegraphics[width=1.\linewidth]{h.png}
+%%   \caption{Graph of the function $h$ defined in equation \eqref{eq:h_func}}
+%% \end{figure}
+%% \begin{lemma}
+%% \begin{eqnarray}
+%%   \prox_{\lambda h}(a, b) = \underset{(\theta, \zeta) \in \{(a_1, b_1), (a_2, b_2), (a_3, b_3)\}}{argmin}{h(\theta, \zeta)}
+%% \end{eqnarray}
+%% where
+%% \begin{eqnarray*}
+%% \begin{split}
+%% (a_1, b_1) &:= 
+%% %\proj_{U_{\sqrt{1 + \lambda}}}((a/\sqrt{1 + \lambda}, b)) = 
+%%   \begin{cases}
+%%     \left(a, b\right), &\mbox{if } a \ge \sqrt{1+\lambda}(b)_+\\
+%%     (0,0), &\mbox{if } 0 \le b \le -\sqrt{1+\lambda}a\\
+%%     (0, b), &\mbox{if } max(a, b) \le 0\\
+%%     \dfrac{\sqrt{1+\lambda}a+b}{2 + \lambda}(\sqrt{1 + \lambda}, 1), &\mbox{otherwise}
+%%   \end{cases}\\
+%% (a_2, b_2) &:= 
+%% %\proj_{U_{\sqrt{1 + \lambda}}}((a/\sqrt{1 + \lambda}, b)) = 
+%%   \begin{cases}
+%%     \left(a, b\right), &\mbox{if } b \ge \sqrt{1+\lambda}(a)_+\\
+%%     (0,0), &\mbox{if } 0 \le a \le -\sqrt{1+\lambda}b\\
+%%     (a, 0), &\mbox{if } max(a, b) \le 0\\
+%%     \dfrac{a + \sqrt{1+\lambda}b}{2 + \lambda}(1,\sqrt{1 + \lambda}), &\mbox{otherwise}
+%%   \end{cases}\\
+%% (a_3, b_3) &:=
+%% %\proj_{W_{\sqrt{1 + \lambda}}}((a, b)) = 
+%% -((-a)_+, (-b)_+)
+%% \end{split}
+%%   \end{eqnarray*}
+%% \end{lemma}
 \subsection{Efficient computation of $Ay$ and $A^Tx$}
-In each iteration of Algorithm \ref{Tab:algo_simplified}, most of the time is spent
-pre-multiplying vectors by $A$ and $A^T$.
-For \textit{flop}-type Poker games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em}, $A$ (and thus $A^T$ too) has a rich block-diagnoal structure which can be carefully exploited.
+In Algorithms \ref{Tab:algo_simplified} most of the time is spent
+pre-multiplying vectors by $A$ and $A^T$. For \textit{flop}-type Poker
+games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
+$A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
+but has a rich block-diagnoal structure which can be carefully
+exploited, as was done in \cite{hoda2010smoothing}.
 
 \begin{definition}(Kronecker product)
-Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
+Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
+  s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
 
@@
 
-Such a representation of the payoff matrix $A$ trivializes matvec operations involving $A$ or $A^T$ (thanks to equation \eqref{eq:kron_matvec} above, applied to their diagonal blocks and exploiting the sparsity of these blocks themselves).
+Such a representation of the payoff matrix $A$ trivializes matvec operations involving $A$ or $A^T$ (thanks to formula \eqref{eq:kron_matvec} above, applied to their diagonal blocks and exploiting the sparsity of these blocks themselves).
 Of course, one can always write the payoff matrix $A$ of a flop-type Poker game in a form similary to \eqref{eq:factor_A} by applying appropriate permutations to the enumeration of the players's sequences.
@@
 \label{sec:results}
-To access the practical quality of the proposed algorithm, we experimented it on real and simulated games. The results are presented here.
+To access the practical quality of the proposed algorithm, we
+experimented it on real and simulated matrix games.
 
-\begin{remark}
-The results presented here are not meant to be benchmarks comparing our algorithm to other algorithms, but should rather be seen as proof-of-concept which experimentally  validates the rigorously extablished results in section \ref{sec:algo}.
+\begin{figure}[!htpb]
+  \includegraphics[width=.34\linewidth]{simplex_dgap.pdf}
+  \hspace{-1em}
+  \includegraphics[width=.34\linewidth]{SimplifiedPoker_dgap.pdf}
+  \hspace{-.8em}
+  \includegraphics[width=.34\linewidth]{Kuhn3112_dgap.pdf}
+  \hspace{-1.3em}
+  \includegraphics[width=.35\linewidth]{simplex_NE.pdf}
+  \hspace{-.8em}
+  \includegraphics[width=.34\linewidth]{SimplifiedPoker_NE.pdf}
+  \hspace{-1.3em}
+  \includegraphics[width=.34\linewidth]{Kuhn3112_NE.pdf}
+  \caption{Convergence curves of Algorithm
+    \ref{Tab:algo_simplified}. \textbf{Left column}: Random $1000
+    \times 1000$ matrix game on simplexes. \textbf{Middle column}:
+    Simplified poker. \textbf{Right column}: Kuhn 3-card
+    Poker. \textbf{Top row}: convergence in terms of ergodic
+    duality-gap. \textbf{Bottom row}: Convergence in terms of value of
+    game.}
+  \label{Tab:dgap_curve}
+\end{figure}
 
-\end{remark}
+%% \begin{remark}
+%% The results presented here are not meant to be benchmarks comparing
+%% our algorithm to other algorithms, but should rather be seen as
+%% proof-of-concept which experimentally  validates the rigorously
+%% extablished results in section \ref{sec:algo}.
+% \end{remark}
 
 \subsection{Simulated game: matrix game on simplexes}
-Any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a \textit{matrix game}.
-The strategy profile of player $k$ is a simplex; this simplex can be written in the form \eqref{eq:polyhedron} by taking $E_k := [1, 1, ..., 1] \in \mathbb{R}^{1 \times n_k}$ and $e_k = 1$.
-Thus every matrix game on simplexes can be seen as a sequential game.
-Now, as in \textbf{nesterov, c-p, etc.}, we generate a $1000 \times 1000$ random matrix whose entries are uniformly identically distributed in the closed interval $[-1, 1]$.
-See Figure \ref{Tab:sim_dgap_curve}...
-
-\begin{figure}
-  \includegraphics[width=.56\linewidth]{simplex_dgap.pdf}
-  \includegraphics[width=.56\linewidth]{simplex_NE.pdf}
-  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} random $1000 \times 1000$ matrix game (on simplexes).
-  \textbf{Left}: Duality gap. \textbf{Right}: Value of game.}
-  \label{Tab:sim_dgap_curve}
-\end{figure}
+Any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a
+\textit{matrix game}. The strategy profile of player $k$ is a simplex;
+this simplex can be written in the form \eqref{eq:polyhedron} by
+taking $E_k := [1, 1, ..., 1] \in \mathbb{R}^{1 \times n_k}$ and $e_k
+= 1$. Thus every matrix game on simplexes can be seen as a sequential
+game. Now, as in \textbf{nesterov, c-p, etc.}, we generate a $1000
+\times 1000$ random matrix whose entries are uniformly identically
+distributed in the closed interval $[-1, 1]$. See Figure \ref{Tab:sim_dgap_curve}...
 
 \subsection{Real-world game: Kuhn 3-card Poker}
-The sequence-form representation of this simplified Poker variant \cite{kuhn} is given by (not showing zero entries)\\
+The sequence-form representation of this simplified Poker variant
+\cite{kuhn} is given by (not showing zero entries)\\
+
 $E_1 = \left[\begin{array}{ccccccccccccc}
@@
   &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
-\end{array}\right] \in \mathbb{R}^{7 \times 13}$,\\
+\end{array}\right] \in \mathbb{R}^{7 \times 13}$,
 $E_2 = \left[\begin{array}{ccccccccccccc}
@@
 -1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
-\end{array}\right] \in \mathbb{R}^{7 \times 13}$, \\ $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T \in \mathbb{R}^7$, and $A = \\\left[\begin{array}{ccccccccccccc}
+\end{array}\right] \in \mathbb{R}^{7 \times 13}$, $e_1 = e_2 = [1, 0,
+  0, 0, 0, 0, 0]^T \in \mathbb{R}^7$, and $A =
+\\\left[\begin{array}{ccccccccccccc}
+
   &   &   &   &   &   &   &   &   &   &   &   &  \\
@@
   & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
-\end{array}\right]$.
-The pair $(x^*, y^*) \in \mathbb{R}^{13} \times \mathbb{R}^{13}$ of realization plans given by
+\end{array}\right] \in \mathbb{R}^{13 \times 13}$.\\
+The pair $(x^*, y^*) \in \mathbb{R}^{13} \times \mathbb{R}^{13}$ of
+realization plans given by
+
 \begin{eqnarray*}
   \begin{split}
-    x^* &= [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T,\\
+    x^* &= [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0,
+      0.275, 0.725]^T,\\
     y^* &= [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T
@@
 \end{eqnarray*}
-is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of Algorithm  \ref{Tab:algo_simplified}.
-The convergence curves are shown in Fig \ref{Tab:dgap_curve}.
-One easy checks that this equilibrium is feasible.
-Indeed,
+is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of
+Algorithm  \ref{Tab:algo_simplified}. The convergence curves are shown
+in Fig \ref{Tab:dgap_curve}. One easy checks that this equilibrium is
+feasible. Indeed,
+
 \begin{eqnarray*}
   \begin{split}
-    E_1x^* - e_1 = [&4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, \\&
+    E_1x^* - e_1 = [&4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67
+      \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, \\&
       -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T
@@
   \begin{split}
-    E_2y^* - e_2 = [&-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6},\\
-      &2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7}]^T
+    E_2y^* - e_2 = [&-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29
+      \times 10^{-6}, -1.50 \times 10^{-6},\\
+      &2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times
+      10^{-7}]^T
     \end{split}
 \end{eqnarray*}
-Finally, ${x^*}^TAy^* = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}.
-The evolution of the dual gap and the expected value of the game across iterations is shown in Figure \ref{Tab:dgap_curve}.
-These figures validate the theoritically established $\mathcal{O}(1/\epsilon)$ convergence rate of the Algorithm.
-
-\begin{figure}
-  \includegraphics[width=.56\linewidth]{Kuhn3112_dgap.pdf}
-  \includegraphics[width=.56\linewidth]{Kuhn3112_NE.pdf}
-  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} on Kuhn 3-card Poker.
-  \textbf{Left}: Duality gap. \textbf{Right}: Value of game.}
-  \label{Tab:dgap_curve}
-\end{figure}
-
-%% \section{Extending to games with more general strategy profiles}
-%% \label{sec:algo_gen}
-%% Notice tha in \eqref{eq:poly}, the strategy profile of player $k$ can be factored as
-%% \begin{equation}
-%%   Q_k := \{z \in \mathbb{R}^{n_k}_+| E_kz = e_k\text\}
-%% \end{equation}
-
-%% The framework presented sofar only demanded we be able to efficiently compute euclidean projections onto the nonnegative orthant $\mathbb{R}^{n_k}_+$, namely nonnegative clipping.
-This opens perspectives to envisage general two-person zero sum games for which the players' strategy profiles are of the form
-%% \begin{equation}
-%%   Q_k := \{z \in C_k| E_kz = e_k\text\}
-%%   \label{eq:q_gen}
-%% \end{equation}
-%% where the $C_k$ are arbitrary convex sets for which the euclidean projections $\Pi_{C_k}$ can be effectively computed.
-%% % \subsection{Example: Computing best response strategies}
-
-%% As a motivating example, suppose Alice knows a priori that Bob is playing a given realization plan $y_0 \in Q_2$ (for example, take $y_0 = [1, 0, ..., 0]^T \in \mathbb{R}^{n_2}$).
-Alice seeks a \textit{best response strategy}, namely a strategy $x^* \in Q_1$ such that
-%% \begin{equation}
-%%   x^TAy_0 \le {x^*}^TAy_0,\text{ } \forall x \in Q_1
-%% \end{equation}
-
-%% One observes that this problem is an instance of problem \eqref{eq:primal_pb} with
-%% $Q_2 = \{y_0\} = \{z \in C_2| E_2z = e_2\text\}$ and $C_2 = \{y_0\}$. Of course the euclidean projection on $C_2$ is simply the constant map $y \mapsto y_0$.
-
-%% As another motivating example, suppose we know the support ...
-
-%% Indeed we have the following generalization of Theorem \ref{thm:pd} for Nash equilibrium problems in which the strategy  profiles have the generic form \eqref{eq:q_gen}.
-%% \begin{theorem}
-%%   The Nash equilibrium problem \eqref{eq:primal_pb} with strategy profiles given by  equation \eqref{eq:q_gen}, can be re-written in the equivalent unconstrained form
-
-%%   \begin{equation}
-%%     \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{l_1}}{minimize}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{l_2}}{maximize}
-%%            {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G_1(y, v) - G_2(x, u)}
-%%            \label{eq:unconstrained_gen_pb}
-%%   \end{equation}
-
-%%   where $v \in \mathbb{R}^{l_1}$ and $u \in \mathbb{R}^{l_2}$ are auxiliary variables and 
-%%   \begin{equation}
-%%     \left .
-%%     \begin{split}
-%%       K :=
-%%       \left[
-%%         \begin{array}{c|c}
-%%           A & -E_1^T \\ \hline
-%%           E_2 & 0_{l_2, l_1}
-%%         \end{array}
-%%         \right] \in \mathbb{R}^{(n_1 + l_2) \times (n_2 + l_1)} \\
-%%       %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + l_1) \times (n_1 + l_2)}\\
-%%       G_1: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow [-\infty, +\infty], (y, v) \mapsto i_{C_2}(y) + e_1^Tv\\
-%%       G_2: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow [-\infty, +\infty], (x, u) \mapsto i_{C_1}(x) + e_2^Tu
-%%     \end{split}
-%%     \right\}
-%%     \label{eq:things}
-%%   \end{equation}
-
-%%   Moreover, $G_1$ and $G_2$ are \textit{p.c.l.s.c} and their proximal operators are given by
-%%   \begin{equation}
-%%     \left .
-%%     \begin{split}
-%%       \text{prox}_{\tau G_1} : \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\\
-%%       (y, v) &\mapsto (\Pi_{C_2}(y), v - \tau e_1)\\
-%%     \end{split}
-%%     \right\}
-%%   \end{equation}
-
-%%   and
-%%   \begin{equation}
-%%     \left .
-%%     \begin{split}
-%%       \text{prox}_{\sigma F}: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}\\
-%%       (x, u) &\mapsto (\Pi_{C_1}(x), u - \sigma e_2)
-%%     \end{split}
-%%     \right\}
-%%   \end{equation}
-%%   \label{thm:pd_gen}
-%% \end{theorem}
-
-%% \begin{proof}
-%% Totally analogous to the proof of Theorem \ref{thm:pd} with $\mathbb{R}^{n_k}_+$ replaced with $C_k$,
-%% $i_{\mathbb{R}^{n_k}_+}$ replaced with $i_{C_k}$, and $\Pi_{\mathbb{R}^{n_k}_+}$ (nonnegative clipping) replaced with $\Pi_{C_k}$.
-%% \end{proof}
-
-%% %\subsection{$\mathcal{O}(1/\epsilon)$ primal-dual algorithm for general problems}
-%% Analogous to Algorithm \ref{Tab:algo_simplified}, we obtain Algorithm \ref{Tab:algo} for solving the Nash equilibrium problem \ref{eq:primal_pb} with the general strategy profiles $Q_k$ defined in \eqref{eq:q_gen}.
-Just like Algorithm \ref{Tab:algo_simplified}, Algorithm \ref{Tab:algo} has a $\mathcal{O}(1/\epsilon)$ convergence rate.
-
-%% \begin{algorithm}[G_2yy]
-%%   \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:primal_pb}, with general strategy profiles as defined in \eqref{eq:q_gen}}
-%%   \KwIn{specification of a game $(A, E_1, E_2, e_1, e_2, C_1, C_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
-%%       $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, $e_1 \in \mathbb{R}^{l_1}$, $e_2 \in \mathbb{R}^{l_2}$, each $C_k$ is a convex subset of $\mathbb{R}^{n_k}$, as in the definition of the strategy profiles $Q_k$ in equation \eqref{eq:q_gen}}
-%%   \KwOut{Nash $\epsilon-$equilibrium pair $x^{(k)}$, $y^{(k)}$}
-%%   \textbf{Precompute}: $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
-%%   \textbf{Initialize}:
-%%   $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{l_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{l_2}$; 
-%%   $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
-%%   \While{
-%% %$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$
-%% $|p^Te_1^{(k)} - q^Te_2^{(k)}| \geq \epsilon$}{
-%%     \begin{eqnarray*}
-%%       x^{(k+1)} &\leftarrow& \Pi_{C_1}\left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)\\
-%%       u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
-%%       y^{(k+1)} &\leftarrow& \Pi_{C_2}\left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)\\
-%%       v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
-%%       \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
-%%       \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
-%%       k &\leftarrow& k + 1
-%%     \end{eqnarray*}
-%%   }
-%%   \label{Tab:algo}
-%% \end{algorithm}
+Finally, one checks that
+\begin{eqnarray*}
+  {x^*}^TAy^* = -0.055593685705289997,
+\end{eqnarray*}
+ which agrees to 4 d.p with the value of $-1 / 18$ computed
+ analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. The
+ evolution of the dual gap and the expected value of the game across
+ iterations is shown in Figure \ref{Tab:dgap_curve}. These figures
+ validate the theoritically established $\mathcal{O}(1/\epsilon)$
+ convergence rate of the Algorithm.
 
 \section{Conclusion}
-Making use of the sequence-form representation \cite{koller1992complexity, von1996efficient, vonequilibrium}, we have deviced a primal-dual algorithm for computing Nash equilibria in two-person zero-sum sequential games with imcomplete information (like Texas Hold'em, etc.).
-Our algorithm is simple to implement, with a very low constant cost per iteration, and enjoys a rigorous convergence theory with a proven $\mathcal{O}(1/\epsilon)$ convergence in terms of basic operations (matvec products, clipping, etc.), to a Nash $\epsilon$-equilibrium of the game.
-The core of our contribution (summarized in Theorems \ref{thm:pd} and \ref{thm:conv}) was to show that a reformulation of the Nash equilibrium problem for sequential games with imcomplete information lends the problem directly accessible to primal-dual framework \cite{chambolle2010, chambolle2014ergodic}.
+Making use of the sequence-form representation
+\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
+deviced a primal-dual algorithm for computing Nash equilibria in
+two-person zero-sum sequential games with imcomplete information (like
+Texas Hold'em, etc.). Our algorithm is simple to implement, with a
+very low constant cost per iteration, and enjoys a rigorous
+convergence theory with a proven $\mathcal{O}(1/\epsilon)$ convergence
+in terms of basic operations (matvec products, clipping, etc.), to a
+Nash $\epsilon$-equilibrium of the game. The core of our contribution
+(summarized in Theorems \ref{thm:pd} and \ref{thm:conv}) was to show
+that a reformulation of the Nash equilibrium problem for sequential
+games with imcomplete information lends the problem directly
+accessible to primal-dual framework
+\cite{chambolle2010,chambolle2014ergodic}.
 
-Equilibrium problems are saddle-point convex-concave problems, and as such a natural choice for an algorithm would be in the family of primal-dual algorithms.
-The author believes such primal-dual schemes will receive more attention in the algorithmic game theory community in future.
+Equilibrium problems are saddle-point convex-concave problems, and as
+such a natural choice for an algorithm would be in the family of
+primal-dual algorithms. The author believes such primal-dual schemes
+will receive more attention in the algorithmic game theory community
+in future.
 
@@
 \small
-\bibliographystyle{agsm}
-% \bibliographystyle{abbrvnat}
+\bibliographystyle{splncs03}
 \bibliography{bib}

### 2015-05-30 primal_dual.py

@@ -15,6 +15,7 @@ def power(A, p, max_iter=100, **kwargs):
     for _ in xrange(max_iter):
         b = A(b, **kwargs)
         d = sqrt(np.dot(b, b))
+        print d
         if d == 0:
             return d
         b /= d
@@ -187,7 +188,7 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
             print "\tConverged after %i iterations." % (k + 1)
             break
 
-    return x, y, values, dgaps
+    return x, y, p, q, values, dgaps
 
 
 def primal_dual_sg_ne(A, **kwargs):

### 2015-05-30 simple.py

@@ -4,8 +4,17 @@ import re
 from nose.tools import assert_equal, assert_true
 import networkx as nx
 import numpy as np
+import matplotlib
 import matplotlib.pyplot as plt
-from primal_dual import primal_dual_ne, primal_dual_sg_ne
+from sklearn.utils import check_random_state
+# from primal_dual import primal_dual_ne, primal_dual_sg_ne
+from tseng_bd import primal_dual_ne, primal_dual_sg_ne
+
+# matplotlib confs
+matplotlib.rcParams['text.latex.preamble'] = ['\\boldmath']
+matplotlib.rc('font', family='serif', serif='cm10')
+matplotlib.rc('text', usetex=True)
+plt.rc('font', size=50)  # make the power in sci notation bigger
 
 
 class Game(object):
@@ -680,7 +689,7 @@ class NashPlayer(Player):
         E, e = self.game.constraints[1]
         F, f = self.game.constraints[2]
         A = self.game.payoff_matrix
-        x, y, _ = primal_dual_ne(A, E, F, e, f)
+        x, y, _, _, _, _, _ = primal_dual_ne(A, E, F, e, f)
         self.rplan = np.array([x, y][self.player - 1])
 
     def choice(self, choices):
@@ -905,12 +914,16 @@ def test_nash_player():
 
 
 if __name__ == "__main__":
-    for game_cls in [SimplifiedPoker, Kuhn3112, "simplex"][1:]:
+    rng = check_random_state(42)
+    max_iter = 10000
+    game_clses = ["simplex", SimplifiedPoker, Kuhn3112]
+    for cnt, game_cls in enumerate(game_clses):
         if game_cls == "simplex":
             game = None
             name = game_cls
-            A = np.random.uniform(-1, 1, size=(1000, 1000))
-            x, y, values, dgaps = primal_dual_sg_ne(A)
+            A = rng.uniform(-1, 1, size=(1000, 1000))
+            x, y, p, q, init, values, dgaps = primal_dual_sg_ne(
+                A, max_iter=max_iter)
         else:
             game = game_cls()
             name = game.__class__.__name__
@@ -918,45 +931,61 @@ if __name__ == "__main__":
             E2, e2 = game.constraints[2]
             A = game.payoff_matrix
             args = (A, E1, E2, e1, e2)
-            x, y, values, dgaps = primal_dual_ne(A, E1, E2, e1, e2,
-                                                 max_iter=2000)
[…]

### 2015-05-31 nips2015.tex
ENH: wrote about T-BD algorithm and proposed a new theorem

@@
 \documentclass{article} % For LaTeX2e
-\usepackage{nips14submit_e}%,times}
+\usepackage{nips14submit_e,times}
 %\usepackage{hyperref}
@@
 \usepackage{bbm}
-\usepackage{algorithm,algorithmic}
+\usepackage{algorithm,algorithmicx}
 \usepackage{graphicx}
@@
 \usepackage[titletoc]{appendix}
+
+\usepackage{algpseudocode}
+\usepackage{pifont}
 
@@
 
+\DeclareMathOperator{\dom}{dom}
 \DeclareMathOperator{\proj}{proj}
-\DeclareMathOperator{\prox}{Prox}
+\DeclareMathOperator{\prox}{prox}
 
@@
   \begin{aligned}
-     \text{minimize }p_0, \hspace{.5em}\text{ subject to }(y,p) \in
+     \text{minimize }e_1^Tp, \hspace{.5em}\text{ subject to }(y,p) \in
      \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}, -Ay +
@@
   \begin{aligned}
-    \text{maximize}-q_0,\hspace{.5em}\text{subject to }(y,q) \in
+    \text{maximize}-e_2^Tq,\hspace{.5em}\text{subject to }(y,q) \in
     \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, -A^Tx - E_2^Tq \leq 0,
@@
 \label{sec:algo}
-\subsection{Primal-dual algorithm}
-It should be noted that the difficulty of applying the general
-primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to
-problem \eqref{eq:primal_pb} lies in the difficulty of effectively
-computing the euclidean projections $\proj_{Q_k}$ (which are the
-proximal operators here). Theorem \ref{thm:pd} provides a trick to
-effectively evade this difficulty, by re-writting the problem into an
-equivalent saddle-point convex-concave problem for which the
-associated proximal operators are simple.
+\subsection{Reformulation as a Generalized Saddle-point Problem (GSP)}
+One cannot directly attack the LCPs \eqref{eq:primal_pb} and
+\eqref{eq:dual_pb} via a traditional primal-dual algorithm
+(for example \cite{chambolle2010,chambolle2014ergodic}) because
+computing the euclidean projections $\proj_{Q_k}$ is very difficult
+(in fact, such subproblems would have to be solved
+iteratively\footnote{An ``exception to the rule'' is the case where
+  the $Q_k's$ are simplexes, so that the projections can be computed
+  exactly using \cite{duchi2008efficient}.}). Also,
+the primal-dual gap might explode even at ``nearly feasible'' points,
+leaving a primal-dual algorithm with no clear on whether progress is
+being made or not. So need to way to
+\begin{itemize}
+\item avoid having to compute the projections $\proj_{Q_k}$, and
+\item cope  with infinite primal-dual gaps.
+\end{itemize}
 
+In the next theorem, we show that the said LCP problems can be
+conveniently written as a \textit{Generalized Saddle-point Problem
+  (GSP)} in the sense of \cite{he2013accelerating}.
 \begin{theorem}
-  The Nash equilibrium LCPs \eqref{eq:primal_pb} and
-  \eqref{eq:dual_pb} are equivalent to the following convex-concave
-  saddle-point problems
+Define two proper closed convex functions
+  \begin{eqnarray}
+    \left.
+    \begin{aligned}
+      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
+      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
+        i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tp\\
+        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
+        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
+          i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tq.
+    \end{aligned}
+    \right\}
+    \label{eq:things}
+  \end{eqnarray}
 
-  \begin{equation}
-    \underset{y, p}{\text{minimize}}\text{ }\underset{x, q}{\text{maximize}}
-           {\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} + G_2(y, p) - G_2(x, q)}
-           \label{eq:unconstrained_pb}
-  \end{equation}
-
-  where the $(n_1 + l_2)$-by-$(n_2 + l_1)$ matrix $K$ is defined by
+Also, define two bilinear forms $\Psi_1$, $\Psi_2: \mathbb{R}^{n_2}
+\times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
+\mathbb{R}^{l_2} \rightarrow \mathbb{R}$ by letting
   \begin{equation}
@@
         \end{array}
-      \right]
+        \right],\hspace{.5em}
+    \Psi_1(y, p, x, q)
+    := \begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix}, \hspace{.5em}
+      \Psi_2(y, p, x, q) := -\Psi_1(y, p, x, q).
 \end{equation}
 
-and the p.c.l.s.c functions $G_1: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow (-\infty, +\infty]$ and \\$G_2: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ are defined by
-  \begin{equation}
-      G_1(y, p) := i_{\mathbb{R}^{n_2}_+}(y) + p_0, \hspace{1em} G_2(x, q) := i_{\mathbb{R}^{n_1}_+}(x) + q_0
-    \label{eq:things}
-  \end{equation}
+Finally, define the functions $\hat{\Psi}_1$, $\hat{\Psi}_2:
+\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}
+\times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ by
+\begin{eqnarray}
+  \left.
+  \begin{aligned}
+    \hat{\Psi}_1(y, p, x, q) &:=
+    \Psi_1(y, p, x, q)+ g_1(y, p) \text{ if }y \ge 0, \hat{\Psi}_1(y,
+    p, x, q) := \infty \text{ otherwise}\\
+    \hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(y, p) \text{ if
+    }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ otherwise}.
+  \end{aligned}
+  \right\}
+\end{eqnarray}
 
-  %% Moreover, if $\mathcal{G_1}'$ denotes the dual-gap function of problem $\eqref{eq:unconstrained_pb}$ and as before, $\mathcal{G_1}$ denotes the dual-gap function of problem \eqref{eq:primal_pb}, then we have the bound
-  %% \begin{equation}
-  %%   \mathcal{G_1}(x, y) \le \mathcal{G_1}'(x, u, y, v), \forall (x, u, y, v) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \times \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}
-  %%   \end{equation}
+Consider the GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$)
+  \begin{eqnarray}
+    \left.
+    \begin{aligned}
+      \text{Find }(y^*,p^*, x^*, q^*) \in \mathbb{R}^{n_2}_+
+  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}_+ \times
+  \mathbb{R}^{l_2}\text{ such that }\hat{\Psi}_1(y^*, p^*, x^*, q^*) \le \hat{\Psi}_1(y, p, x^*, q^*)
+      \text{ and }\\
+      \hspace{.5em}\hat{\Psi}_2(y^*, p^*, x^*, q^*) \le
+      \hat{\Psi}_2(y^*, p^*, x, q)
+        \forall (y,p, x, q) \in \mathbb{R}^{n_2}_+
+      \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}_+ \times
+      \mathbb{R}^{l_2}.
+    \end{aligned}
+    \right\}
+    \label{eq:unconstrained_pb}
+  \end{eqnarray}
+  \label{thm:pd}
 
+  Then a quadruplet $(y^*,p^*, x^*, q^*) \in \mathbb{R}^{n_2}
+  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
+  \mathbb{R}^{l_2}$ solves the Nash equilibrium LCPs
+  \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff it solves
+  GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
   \label{thm:pd}
@@
 
-%% Theorem \ref{thm:pd}, can be interpreted as follows: 2 players $x$ (player 1)  and $y$ (player 2) go heads-on in a zero-sum game with payoff matrix $A$.
-Their strategy, profiles are $Q_1$ and $Q_2$ respectively, meaning that if player $j$ players a strategy which is outside $Q_k$ then they are panalized by inflicting an infinite loss yupon them.
-To remedy this, they recruit assistants $u$ and $v$, whose sole goal is to preven the ...
 \begin{proof}
-Define the following closed convex sets
+Define $S_1 := \dom(g_1) = \mathbb{R}^{n_2}_+ \times \mathbb{R}^{l_1}$
+and $S_2 := \dom(g_2) = 
+\mathbb{R}^{n_1}_+ \times \mathbb{R}^{l_2}$. Noting that the
+equilibria of the LCPs \eqref{eq:primal_pb},
+\eqref{eq:dual_pb}, and the equilibria of GSP($\Psi_1$, $\Psi_2$,
+$g_1$, $g_2$) are contained in $S_1 \times S_2$, it suffices to show
+that at any point $(y, p, x, q) \in S_1 \times S_2$, the duality
+primal-dual gap between the primal LCP \eqref{eq:primal_pb} and the
+dual LCP \eqref{eq:dual_pb} equals the primal-dual gap of
+GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
+
+Indeed, the unconstrained objective in \eqref{eq:primal_pb}, say
+$a(x,y)$, can be written as
 \begin{eqnarray*}
   \begin{aligned}
-  \Sigma_2 &:= \{(y, p) \in \mathbb{R}^{n_2} \times
-  \mathbb{R}^{l_1}\text{ }|\text{ } -Ay + E_1^Tp \ge 0, E_2y = e_2, y
-  \ge 0\}\\
-  \Sigma_1 &:= \{(x, q) \in \mathbb{R}^{n_1} \times
-  \mathbb{R}^{l_2}\text{ }|\text{ } -A^Tx - E_2^Tq \le 0, E_1x = e_1,
-  x \ge 0\}
-  \end{aligned}
-\end{eqnarray*}
-The optimal value in the dual LCP \eqref{eq:primal_pb} can be computed as 
-\begin{eqnarray*}
-  \begin{aligned}
-    p_0^* &= \text{min}\{p_0\text{ }|\text{ } (y, p) \in \Sigma_2, p =
-    (p_0, p_1, ..., q_{l_1-1})\}\\
-    &= \underset{y,p}{\text{min}}\text{ }p_0 +
+    a(y,p) &= e_1^Tp +
     i_{\mathbb{R}^{n_2}_+}(y) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) +
     i_{\{0\}}(E_2y - e_2)\\
-    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) +
+    &= g_1(y,p) +
     i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
-    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x \geq
-      0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) +
-    \underset{q}{\text{max}}\text{ }q^T(E_2y - e_2)\\
-    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x,
-      q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y -
-    i_{\mathbb{R}^{n_1}_+}(x) - q^Te_2\\
-    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x,
-      q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y -
-    (i_{\mathbb{R}^{n_1}_+}(x) + q_0)\\
-    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) +
-    \underset{x,q}{\text{max}}\text{
-    }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix}
-      - G_2(x, q) = \underset{y,p}{\text{min}}\text{ }G_1(y,p) +
-      G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
+    &= g_1(y,p) + \underset{x' \geq
+      0}{\text{max}}\text{ }x'^T(Ay - E_1^Tp) +
+    \underset{q'}{\text{max}}\text{ }q'^T(E_2y - e_2)\\
+    &= g_1(y,p) + \underset{x',
+      q'}{\text{max}}\text{ }x'^TAy - x^TE_1^Tp + q'^TE_2y -
+    (i_{\mathbb{R}^{n_1}_+}(x') + e_2^Tq)\\
+    &= g_1(y,p)
+      - \underset{x',q'}{\text{min}}\text{ }\Psi_2(y, p, x', q') + g_2(x',
+      q') = g_1(y,p) -\phi_2(y,p),
   \end{aligned}
@@
 \end{eqnarray*}
-Thus the LCP \eqref{eq:primal_pb} can be written as 
-\begin{equation}
-  \underset{y,p}{\text{minimize}}\text{ }G_1(y,p) +
-  G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
-\end{equation}
-Similarly, the optimal value in the dual LCP \eqref{eq:dual_pb} writes
+
+where $\phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
+}\hat{\Psi}_2(y, p, x', q') \in [-\infty, +\infty)$.
+Similarly, the unconstrained objective, say
+$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
 \begin{eqnarray*}
   \begin{aligned}
- -q_0^* &= \text{max}\{-q_0\text{ }|\text{ } (x, q) \in \Sigma_1, q =
- (q_0, q_1, ..., q_{l_2-1})\}\\
-    &= \underset{x,q}{\text{max}}\text{ }-q_0 -
- i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
- i_{\{0\}}(E_1x - e_1)\\
-    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q) - \underset{y \geq
-   0}{\text{max}}\text{ }y^T(-A^Tx - E_2^Tq) -
- \underset{p}{\text{max}}\text{ }p^T(E_1x-e_1)\\
-    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q)
- -\underset{y,p}{\text{max}}\text{ }-(y^TA^Tx -p^TE_1x +
- y^TE_2^Tq)-(i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1)\\
-    &= \underset{x,q}{\text{max}}\text{ }-G_2(x,
- q)-\underset{y,p}{\text{max}}\text{ }-
- \begin{bmatrix}y\\p\end{bmatrix}K^T\begin{bmatrix}x\\q\end{bmatrix}-G_1(y,p)
-   = \underset{x,q}{\text{max}}\text{ }-G_2(x,
-   q)-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right),
+ b(x, q) &= 
+ -i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
+ i_{\{0\}}(e_1 - E_1x)\\
+    &= -g_2(x, q) + \underset{y' \geq
+   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
+ \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
+    &= -g_2(x, q)
+ +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
+ g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
    \end{aligned}
 \end{eqnarray*}
-and so the the LCP \eqref{eq:dual_pb} is equivalent to
-\begin{equation}
-  \underset{x,q}{\text{maximize}}\text{
-  }-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right) - G_2(x, q)
-\end{equation}
-But these last two equations are simply the primal and dual
-formulations respectively, of the saddle-point problem
-\eqref{eq:unconstrained_pb}, and we are done.
+where $\phi_1(x, q) :=
+\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) \in
+         [-\infty, +\infty)$.
+Thus, one can compute the primal-dual gap between primal LCP
+\eqref{eq:primal_pb} and dual LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
+\begin{eqnarray*}
+  \begin{split}
+  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
+  q) \\
+  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
+  q) + g_2(x, q) - \phi_1(x, q)\\
+  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
+  q) - \phi_2(y, p)\\
+  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
+  g_1, g_2) \text{ at }(y, p, x, q),
+  \end{split}
+\end{eqnarray*}
+where the second equality follows from the fact that $\Psi_1 + \Psi_2
+:= 0$.
 
@@
 %%   \begin{split}
-%%     \underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{l_2}}{max}\text{ }\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y'\\v'\end{bmatrix} + G_1(y', v') - G_2(x, u)
+%%     \underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{l_2}}{max}\text{ }\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y'\\v'\end{bmatrix} + g_1(y', v') - g_2(x, u)
 %%       &= \underset{x \in \mathbb{R}^{n_1}_+, u \in \mathbb{R}^{l_2}}{max}\text{ }x^TAy' - v'^T(E_1x - e_1) + u^T(E_2y' - e_2)\\
@@
 %%   \begin{split}
-%%     \underset{y \in \mathbb{R}^{n_2}, v \in \mathbb{R}^{l_1}}{min}\text{ }\begin{bmatrix}x'\\u'\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G_1(y, v) - G_2(x', u')
+%%     \underset{y \in \mathbb{R}^{n_2}, v \in \mathbb{R}^{l_1}}{min}\text{ }\begin{bmatrix}x'\\u'\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + g_1(y, v) - g_2(x', u')
 %%       &= \underset{y \in \mathbb{R}^{n_2}_+, v \in \mathbb{R}^{l_1}}{min}\text{ }x'^TAy - v^T(E_1x' - e_1) + u'^T(E_2y - e_2)\\
@@
 
-\paragraph{In summary.}
-According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCPs
-\eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the
-saddle-point problem \eqref{eq:unconstrained_pb}.
-In order to apply Algorithm 39 of \cite{chambolle2010}, we need
-formulae for the proximal operators of
-$G_1$ and $G_2$. Now, either of $G_1$ and $G_2$ is a separable sum of
+\section{The algorithm}
+%% According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCPs
+%% \eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the
+%% saddle-point problem \eqref{eq:unconstrained_pb}. An attractive method
+%% for such a saddle-point problem would be a primal-dual scheme, like
+%% that developed in \cite[Algorithm 39]{chambolle2010}. 
+%% Usually, to use a primal-dual algorithm, one needs a measure of the
+%% ``quality'' of the current iterates as regards being the solution of
+%% the saddle-point problem. A natural measure of this fittness is the
+%% primal-dual gap, which measures defection from strong-duality.
+%% However, the primal-dual gap in \eqref{eq:unconstrained_pb} can be
+%% unbounded even at near feasible points.  is well-suited for
+
+Consider the following algorithm
+\begin{algorithm}
+\caption{Primal-dual algorithm for computing approximate Nash
+  Equilbria in two-person zero-sum games with imcomplete information
+  and perfect recall}
+\label{Tab:algo}
+\begin{algorithmic}[1]
+\State  $\lambda \leftarrow 1/\|K\|$,
+%% $y^{(0)} \leftarrow 0_{n_2}$,
+%% $p^{(0)} \leftarrow 0_{l_1}$, $x^{(0)} \leftarrow 0_{n_1}$, $q^{(0)}
+%% \leftarrow 0_{l_2}$,
+$k \leftarrow 0$
+\While{$\|\tilde{\epsilon}^{a}_k\| \ge \rho$ or $\|\tilde{v}^{a}_k\| \ge \epsilon$}
+\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
+E_2^Tq^{(k)}))_+$
+\State  \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
+\lambda(e_1-E_1x^{(k)})$
+\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
+E_1^Tp^{(k+1)}))_+$
+\State  \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} +
+\lambda(E_2y^{(k+1)}-e_2)$
+\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda
+(A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
+\State $p^{(k+1)} \leftarrow p^{(k+1)} - \lambda E_1(x^{(k+1)}-x^{(k)})$
+\State $k \leftarrow k + 1$
+\EndWhile
+\end{algorithmic}
+\end{algorithm}
+
+\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
+Let $d_0$ be the euclidean distance between the starting point
+$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ Algorithm \ref{Tab:algo} and the
+set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
+Then given any $\epsilon > 0$ and $\rho > 0$, we have the ergodic
+error bounds
+\begin{eqnarray}
+\|\tilde{\epsilon}^{a}_k\| \le \rho\text{ and }\|\tilde{v}^{a}_k\| \le
+\epsilon, \forall k \ge 2d_0\|K\|max(5d_0/\rho, 1/\epsilon).
+\end{eqnarray}
+
+Thus the iterates $(y^{(k)},p^{(k)},x^{(k)},q^{(k)})$ generated by
+Algorithm \ref{Tab:algo} converge ergodically to a
+$(\rho,\epsilon)$-Nash Equilibrium for the GSP \eqref{eq:unconstrained_pb}
+in no more than $2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ steps.
+\end{theorem}
+
+\begin{proof}
+Note that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$ clearly satisfies
+assumptions B.1, B.2, B.3, B.5, and B.6 of \cite{he2013accelerating}
+with $L_{xx} = L_{yy} = 0$ and $L_{xy} = L_{yx} = \|K\|$. Now,
+either of $g_1$ and $g_2$ is a separable sum of
 the indicator function of a convex set, whose prox is simply the
@@
 \mapsto a^Tz$ whose prox is simply $z \mapsto z - \tau a$. Thus,  one
-computes their respective proximal operators $\prox_{\tau G_1} :
+computes their respective proximal operators $\prox_{\tau g_1} :
 \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow \mathbb{R}^{n_2}
-\times \mathbb{R}^{l_1}$, $\prox_{\sigma G_2}: \mathbb{R}^{n_1} \times
+\times \mathbb{R}^{l_1}$, $\prox_{\sigma g_2}: \mathbb{R}^{n_1} \times
 \mathbb{R}^{l_2} \rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}$
-as
-
-  \begin{equation}
-    \prox_{\tau G_1}(y, p) = ((y)_+, p - \tau e_1), \hspace{1em}
-    \prox_{\sigma G_2}(x, q) = ((x)_+, q - \sigma e_2)
-  \end{equation}
-
-Finally, applying Algorithm 39 of \cite{chambolle2010} to problem \eqref{eq:unconstrained_pb} we obtain Algorithm \ref{Tab:algo_simplified}.
-Its $\mathcal{O}(1/\epsilon)$ convergence rate in terms of the duality gap is immediate.
-Indeed,
-%% \subsection{Special case: $C_k = \mathbb{R}^{n_k}_+$} As discussed in subsection \ref{subsec:example_games},
-%% the Nash equilibrium problem for two-person zero-sum simultaneous games and two-person zero-sum sequential games with imcomplete
-%% information and perfect recall admits the formulation \eqref{eq:primal_pb}, with $C_k = \mathbb{R}^{n_k}_+$ (coding for nonnegativity constraints).
-%% In such situations, $\proj_{C_k}(z) \equiv (z)_+$ as already mentioned in \ref{sec:notation}, and Algorithm \ref{Tab:algo} reduces to the simpler Algorithm \ref{Tab:algo_simplified}.
-
-\begin{algorithm}[G_2]
-%%   \caption{$\mathcal{O}(1/\epsilon)$ Primal-dual algorithm for finding a Nash $\epsilon$-equilibrium for a sequential two-person zero-sum game with imcomplete information and perfect recall}
-%%   \KwIn{sequence-form specification of the game: $(A, E_1, E_2, e_1, e_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
-%%   $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, $e_1 \in \mathbb{R}^{l_1}$, $e_2 \in \mathbb{R}^{l_2}$}
-%%   \KwOut{Nash $\epsilon-$equilibrium pair $(x^{(k)}$, $y^{(k)})$ of realization plans}
-%%   \textbf{Precompute}: $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
-%%   \textbf{Initialize}:
-%%   $x^{(0)} \in \mathbb{R}^{n_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $p \in \mathbb{R}^{l_1}$; $q^{(0)} \in \mathbb{R}^{l_2}$; 
-%%   $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$ (for example take $\tau = \sigma = .99/\|K\|$); $k = 0$.\\
-%%   \Repeat{
-%% %$\dfrac{\| x^{(k+1)} - x^{(k)}\|^2 + \|v^{(k+1)}- v^{(k)}\|^2}{\sigma} + \dfrac{\|y^{(k+1)}- y^{(k)}\|^2 + \|u^{(k+1)}- u^{(k)}\|^2}{\tau} < \epsilon$
-%% $|p_0^{(k)} + q_0^{(k)}| \le \epsilon$}{
-%%     \begin{eqnarray*}
-%%       x^{(k+1)} &\leftarrow& \left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{p}^{(k)}\right)\right)_+\\
-%%       q^{(k+1)} &\leftarrow& q^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
-%%       y^{(k+1)} &\leftarrow& \left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tq^{(k + 1)}\right)\right)_+\\
-%%       p^{(k+1)} &\leftarrow& p^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
-%%       \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
-%%       \tilde{p}^{(k+1)} &\leftarrow& 2p^{(k+1)} - p^{(k)}\\
-%%       k &\leftarrow& k + 1
-%%     \end{eqnarray*}
-%%   }
-  \label{Tab:algo_simplified}
-\end{algorithm}
-
-\begin{theorem}
-  \label{thm:conv}
-  Algorithm \ref{Tab:algo_simplified} produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations.
-\end{theorem}
-
-\begin{proof}
-This follows directly from Theorem 1 of \cite{chambolle2010}, and from the equivalence establised in Theorem \ref{thm:pd} above.
-\qed
+$\prox_{\lambda g_1}(y, p) = ((y)_+, p - \lambda e_1)$ and $\prox_{\lambda
+  g_2}(x, q) = ((x)_+, q - \lambda e_2)$. Algorithm \ref{Tab:algo} is
+then obtained from \cite[Algorithm
+  T-BD]{he2013accelerating}, applied on the GSP \eqref{eq:unconstrained_pb}
+ with the choice of parameters $\sigma = 1 \in (0, 1]$, $\sigma_x =
+         \sigma_y = 0 \in [0, \sigma)$,
+ $\lambda_{xy} := \frac{\sqrt{(\sigma^2 - \sigma_x^2)(\sigma^2 -
+               \sigma_y^2)}}{\sigma L_{xy}} = \sigma / \|K\| =
+           1/\|K\|$, $\lambda = \lambda_{xy} \in (0,
+           \lambda_{xy}]$. The convergence result then follows from
+         \cite[Theorem 4.2]{he2013accelerating}.
 \end{proof}
-
-\begin{remark}
-Note however that this convergence rate cannot be improved in the framework of \cite{chambolle2010}, since neither $G_1$ nor $G_2$ is \textit{uniformly convex}.
-\end{remark}
-
-%% \subsection{CQ algorithm for solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb}}
-%% In this section, we will reformulate the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} as a \textit{multi-set split-feasibility problem (MSSFP)} which is amenable to the CQ algorithm.
-
-%% Now, let $\mathcal{H}_1$ and $\mathcal{H}_2$ denote the finite-dimensional Hilbert spaces $\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \times \mathbb{R}^{n_2}$ and $\mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \times \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}$ respectively, and consider the following multi-set split-feasibility problem:
-%% \begin{eqnarray}
-%%   \text{Find }(y, p, u, x, q, v) \in \cap_{k=0}^{2}C_k \text{ such that }  L(y, p, u, x, q, v) \in Q
-%%   \label{eq:sf_pb}
-%% \end{eqnarray}
-%% where:
-%% \begin{itemize}
-%%   \item $L: \mathcal{H}_1 \rightarrow \mathcal{H}_2$  is the finite-dimensional (thus bounded) linear operator defined by its matrix
-%% \begin{eqnarray}
-%%   \begin{split}
-%%   L(y, p, u, x, q, v) &:= \left[
-%%     \begin{array}{cccccc}
-%%       -A & E_1^T & -I_{n_1} & 0_{n_1,n_1} & 0_{n_1, l_2} & 0_{n_1, n_2}\\ % \hline
-%%       E_2 & 0_{l_2, l_1} & 0_{l_2, n_1} & 0_{l_2, n_1} & 0_{l_2, l_2} & 0_{l_2, n_2}\\ %\hline
-%%       0_{n_2, n_2} & 0_{n_2, l_1} & 0_{n_2, n_1} & A^T & E_2^T & -I_{n_2}\\ %\hline
-%%       0_{l_1, n_2} & 0_{l_1, l_1} & 0_{l_1, n_1} & E_1 & 0_{l_1, l_2} & 0_{l_1, n_2} 
-%%       \end{array}
-%%     \right]\begin{bmatrix}y\\p\\u\\x\\q\\v\end{bmatrix}\\
-%%     &= (-Ay + E_1^T - u, E_2y, A^Tx + E_2^Tq - v, E_1x)
-%%   \end{split}
-%% \end{eqnarray}
-
-%% \item the closed convex set $Q \subseteq \mathcal{H}_2$ is the singleton
-%% \begin{equation}
-%%   Q := \{e\}, \hspace{.5em} e:=(0_{n_1}, e_2, 0_{n_2}, e_1)
-%% \end{equation}
-
-%% \item the closed sets $C_k$ are of the form
-%% \begin{eqnarray}
-%%   \begin{split}
-%%     C_0 &:= \{(y, p, u, x, q, v) \in \mathcal{H}_1| y \ge 0, u\ge 0, x \ge 0, v\ge0\},\\
-%%   C_1 &:= \{(y, p, u, x, q, v) \in \mathcal{H}_1 |c_1(y, p, u, x, q, v) := y^Tv\le 0\},\\
-%%   C_2 &:= \{(y, p, u, x, q, v) \in \mathcal{H}_1 |c_2(y, p, u, x, q, v) := x^Tu\le 0\}
-%%   \end{split}
-%%   \label{eq:Ck}
-%% \end{eqnarray}
-%% \end{itemize}
-
-%% Note that $C_0$ is convex, whilst the functions $c_k$ are $(S, r)$-subdifferentiable with $S := \{0\}$ and $r = 1$.
-%% Before exploiting the developments sofar in this section, let's begin with a Lemma.
-%% \begin{lemma}
-%% If a hextupule $(y, p, u, x, q, v) \in C$ solves the MSSFP \eqref{eq:sf_pb}, then the pair $(x, y) \in Q_1 \times Q_2$ of realization plans is a Nash equilibrium.
-%% \end{lemma}
-%% \begin{proof}
-%% Simply introduce auxiliary variables $u := -Ay + E_1^Tq$ and $v = A^Tx + E_2^Tq$ in \eqref{eq:feasibility} and note that if $(y,p,u,x,q,v) \in \cap_{k=0}^{2}C_k$ and $L(y,p,u,x,q,v) \in Q$, then $y\ge0$, $u\ge0$, $x\ge0$, $v\ge0$, $E_2y- e_2 = 0$, $E_1x-e_1=0$, $-Ay + E_1^Tp - u=0$, $A^Tx + E_2^Tq - v = 0$, $y^Tv = 0$, and $x^Tu = 0$, which are precisely the conditions in \eqref{eq:feasibility}.
-\qed
-
-%% \end{proof}
-
-%% Now, observe that $C$ is the set of minimizers of the convex function
-%% \begin{equation}
-%% f(y, p, u, x, q, v) := \sum_{j=0}^{n_1-1}{h(x_j, u_j)} + \sum_{j=0}^{n_2-1}{h(y_j, v_j)},
-%% \end{equation}
-%% where the continuous convex function $h$ is defined by
-%% \begin{eqnarray}
-%%   h(a, b) = \frac{1}{2}\begin{cases}
-%%     a^2, &\mbox{if } a \ge (b)_+\\
-%%     b^2, &\mbox{if } b \ge (a)_+\\
-%%     0, &\mbox{if } max(a, b) \le 0.
-%%   \end{cases}
-%%    \label{eq:h_func}
-%% \end{eqnarray}
-%% We'll be needing the following Lemma concerning the prox of $h$.
-
-%% \begin{figure}
-%%   \includegraphics[width=1.\linewidth]{h.png}
-%%   \caption{Graph of the function $h$ defined in equation \eqref{eq:h_func}}
-%% \end{figure}
-%% \begin{lemma}
-%% \begin{eqnarray}
-%%   \prox_{\lambda h}(a, b) = \underset{(\theta, \zeta) \in \{(a_1, b_1), (a_2, b_2), (a_3, b_3)\}}{argmin}{h(\theta, \zeta)}
-%% \end{eqnarray}
-%% where
-%% \begin{eqnarray*}
-%% \begin{split}
-%% (a_1, b_1) &:= 
-%% %\proj_{U_{\sqrt{1 + \lambda}}}((a/\sqrt{1 + \lambda}, b)) = 
-%%   \begin{cases}
-%%     \left(a, b\right), &\mbox{if } a \ge \sqrt{1+\lambda}(b)_+\\
-%%     (0,0), &\mbox{if } 0 \le b \le -\sqrt{1+\lambda}a\\
-%%     (0, b), &\mbox{if } max(a, b) \le 0\\
-%%     \dfrac{\sqrt{1+\lambda}a+b}{2 + \lambda}(\sqrt{1 + \lambda}, 1), &\mbox{otherwise}
-%%   \end{cases}\\
-%% (a_2, b_2) &:= 
-%% %\proj_{U_{\sqrt{1 + \lambda}}}((a/\sqrt{1 + \lambda}, b)) = 
-%%   \begin{cases}
-%%     \left(a, b\right), &\mbox{if } b \ge \sqrt{1+\lambda}(a)_+\\
-%%     (0,0), &\mbox{if } 0 \le a \le -\sqrt{1+\lambda}b\\
-%%     (a, 0), &\mbox{if } max(a, b) \le 0\\
-%%     \dfrac{a + \sqrt{1+\lambda}b}{2 + \lambda}(1,\sqrt{1 + \lambda}), &\mbox{otherwise}
-%%   \end{cases}\\
-%% (a_3, b_3) &:=
-%% %\proj_{W_{\sqrt{1 + \lambda}}}((a, b)) = 
-%% -((-a)_+, (-b)_+)
-%% \end{split}
-%%   \end{eqnarray*}
-%% \end{lemma}
-\subsection{Efficient computation of $Ay$ and $A^Tx$}
-In Algorithms \ref{Tab:algo_simplified} most of the time is spent
+\subsection{Practical considerations: Efficient computation of $Ay$ and $A^Tx$.}
+In Algorithms \ref{Tab:algo} most of the time is spent
 pre-multiplying vectors by $A$ and $A^T$. For \textit{flop}-type Poker
@@
 
-\section{Results}
+\section{Experimantal results}
 \label{sec:results}
@@
   \caption{Convergence curves of Algorithm
-    \ref{Tab:algo_simplified}. \textbf{Left column}: Random $1000
+    \ref{Tab:algo}. \textbf{Left column}: Random $1000
     \times 1000$ matrix game on simplexes. \textbf{Middle column}:
@@
     Poker. \textbf{Top row}: convergence in terms of ergodic
-    duality-gap. \textbf{Bottom row}: Convergence in terms of value of
-    game.}
+    primal-dual gap. \textbf{Bottom row}: Convergence in terms of
+    value of game.}
   \label{Tab:dgap_curve}
@@
 
-\subsection{Simulated game: matrix game on simplexes}
+\paragraph{Simulated game: matrix game on simplexes.}
 Any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a
@@
 
-\subsection{Real-world game: Kuhn 3-card Poker}
+\paragraph{Real-world game: Kuhn 3-card Poker.}
 The sequence-form representation of this simplified Poker variant
@@
 is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of
-Algorithm  \ref{Tab:algo_simplified}. The convergence curves are shown
+Algorithm  \ref{Tab:algo}. The convergence curves are shown
 in Fig \ref{Tab:dgap_curve}. One easy checks that this equilibrium is

### 2015-05-31 simple.py

@@ -956,18 +956,16 @@ if __name__ == "__main__":
         m = float(m)
         m = "" if m >= 0 else "-"
         e = re.sub("\-0*", "-", e)
-        value_ = "%s10^{%s}" % (m, e)
+        kwargs = {}
+        plt.xlabel("\\textbf{$k$ (iteration count)}", fontsize=50)
+        if cnt == 0:
+            kwargs["label"] = "$\\langle x^*,Ay^*\\rangle$"
+            ax.set_ylabel(("\\textbf{$\\langle x^{(k)}, Ay^{(k)} "
+                           "\\rangle$"), fontsize=50)
         ax.axhline(
             -1. / 18. if isinstance(game, Kuhn3112) else value,
             linestyle="--", dashes=(10, 10), color="k",
-            label="$\\langle x^*,Ay^*\\rangle$ = $%s$" % (
-                "-1 / 18}" if isinstance(game, Kuhn3112) else
-                ("-1 / 4" if isinstance(game, SimplifiedPoker)
-                 else value_)), linewidth=4)
-        plt.xlabel("\\textbf{$k$ (iteration count)}", fontsize=50)
-        if cnt == 0:
-            ax.set_ylabel(("\\textbf{$\\langle x^{(k)}, Ay^{(k)} "
-                           "\\rangle$"), fontsize=50)
+            linewidth=4, **kwargs)
         plt.legend(loc="best", prop=dict(size=45), handlelength=1.5)
         ax.ticklabel_format(axis="y", style="sci", scilimits=(0., 0.))
         ax.tick_params(axis='both', which='major', labelsize=50)

### 2015-05-31 nips2015.tex
ENH: more

@@
 \begin{algorithmic}[1]
+\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
+\in \mathbb{R}^{n_2}
+  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
+  \mathbb{R}^{l_2}$
+\Ensure $(\rho, \epsilon)$-Nash equilibrium
+$(\tilde{y},\tilde{p},\tilde{x},\tilde{q}) \in S_1 \times S_2$ for
+the GSP \eqref{eq:unconstrained_pb}.
 \State  $\lambda \leftarrow 1/\|K\|$,
@@
 
-Thus the iterates $(y^{(k)},p^{(k)},x^{(k)},q^{(k)})$ generated by
-Algorithm \ref{Tab:algo} converge ergodically to a
-$(\rho,\epsilon)$-Nash Equilibrium for the GSP \eqref{eq:unconstrained_pb}
-in no more than $2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ steps.
+Thus Algorithm \ref{Tab:algo} outputs an $(\rho,\epsilon)$-Nash
+Equilibrium for the GSP \eqref{eq:unconstrained_pb}
+in at most $2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ iterations.
 \end{theorem}

### 2015-05-31 nips2015.tex
ENH: more

@@
 Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and
-$e_2$. At a feasible point $(y, p, x, q)$, the \textit{duality gap}
+$e_2$. At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
 $\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
@@
 
-Moreover, at equilibria, \textit{strong duality} holds and the value of the game equals $p_0 = -q_0$, i.e the duality gap $\mathcal{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at equilibria.
+Moreover, at equilibria, \textit{strong duality} holds and the value of the game equals $p_0 = -q_0$, i.e the primal-dual gap $\mathcal{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at equilibria.
 
@@
 \begin{definition}(\textbf{Nash $\epsilon$-equilibria})
-Given a small margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists dual vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} such that the duality gap at $(y^*, p^*, x^*, q^*)$ doesn't exceed $\epsilon$.
-That is,
+Given a $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
+a pair $(x^*, y^*)$ of realization plans such that there exists dual
+vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
+\eqref{eq:dual_pb} such that the primal-dual gap at $(y^*, p^*, x^*, q^*)$
+doesn't exceed $\epsilon$. That is,
+
 \begin{equation}
@@
 
-\subsection{Precise statement of the problem}
-The goal of this article is to device a simple algorithm which produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations.
-%We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation.
-Then we state the Nash equilibrium problem for the sequence-form representation.
-Then in
+\begin{definition}(\textbf{Nash $(\rho,\epsilon)$-equilibria})
+Given $\rho > 0$ and $\epsilon > 0$, a Nash $(\rho,\epsilon$)-equilibrium is
+a pair $(x^*, y^*)$ of realization plans such that there exists dual
+vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
+\eqref{eq:dual_pb} such that ...
+
+\begin{equation}
+  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon
+\label{eq:approx_pb}
+\end{equation}
+\end{definition}
 
@@
 
-\section{Our contributions}
-\label{sec:algo}
-\subsection{Reformulation as a Generalized Saddle-point Problem (GSP)}
+\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
+\label{sec:gsp}
 One cannot directly attack the LCPs \eqref{eq:primal_pb} and
@@
 \section{The algorithm}
+\label{sec:algo}
+
 %% According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCPs

### 2015-06-01 nips2015.tex
ENH: more

@@
 
-\subsection{Some notation and terminology}
+\subsection{Notation and terminology}
 Let $m$ and $n$ be positive integers.
@@
 if $ x \in C$; $i_c(x) = \infty$ otherwise.
-
-Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
-  \textit{proper} (meaning that it is not identically $\infty$) convex
+Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a convex
   function.
+The \textit{effective domain} of $f$, denoted $\dom(f)$ is defined as
+$\dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$. If $\dom(f) \ne
+\emptyset$ then we say $f$ is \textit{proper}.
 %% \textit{proper convex lower semi-continous function}
 %% (\textit{p.c.l.s.c} for short).
-The \textit{convex conjugate} of $f$ is the function $f^*:
-\mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
-  \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
+%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
+%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
+%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
 Given $\tau > 0$, the \textit{proximal operator}
@@
 function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
-unique) solution of the problem $\underset{z \in
-  \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)$.
+unique) minimizer of the $1$-strongly convex function $\mathbb{R}^n
+\rightarrow (-\infty,+\infty]$, $z\mapsto \frac{1}{2}\|z - x\|^2 +
+  \tau f(z)$.
 
@@
 
-\begin{definition}(\textbf{Nash $\epsilon$-equilibria})
-Given a $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
+\begin{definition}[\textbf{Nash $\epsilon$-equilibria}]
+Given $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
 a pair $(x^*, y^*)$ of realization plans such that there exists dual
@@
 
-\begin{definition}(\textbf{Nash $(\rho,\epsilon)$-equilibria})
+\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
 Given $\rho > 0$ and $\epsilon > 0$, a Nash $(\rho,\epsilon$)-equilibrium is
@@
 \eqref{eq:dual_pb} such that ...
-
-\begin{equation}
-  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon
-\label{eq:approx_pb}
-\end{equation}
 \end{definition}
@@
 \subsection{Outline of the article}
-We develop a $\mathcal{O}(1/\epsilon)$ primal-dual algorithm for computing Nash
-$\epsilon$-equilibria for sequential two-person zero-sum games with
-imcomplete information and perfect recall.
+We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
+algorithm for computing Nash $(\rho, \epsilon$)-equilibria for
+sequential two-person zero-sum games with imcomplete information and
+perfect recall.
 
@@
 
-We present a selection of algorithms that is representative of the efforts that have been made in the literature to compute Nash $\epsilon$-equilibria for two-person zero-sum games with imcomplete information like Texas Hold'em Poker, etc.
+We present a selection of algorithms that is representative of the
+efforts that have been made in the literature to compute Nash
+$\epsilon$-equilibria for two-person zero-sum games with imcomplete
+information like Texas Hold'em Poker, etc.
 
-In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used to to solve the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form
+In \cite{hoda2010smoothing}, a nested iterative procedure using the
+Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used to
+to solve the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the
+following equivalent saddle-point form
 
 \begin{equation}
-  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in Q_1}{\text{maximize}}\text{ }x^TAy
+  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
+    Q_1}{\text{maximize}}\text{ }x^TAy
   \label{eq:gilpin}
 \end{equation}
-The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate (which derives from the general EGT theory) for the outer-most iteration loop, though the cost of an iteration is presumably heavy since it entails computing a $softmax$ at each iteration.
+The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
+(which derives from the general EGT theory) for the outer-most
+iteration loop, though the cost of an iteration is presumably heavy
+since it entails computing a $softmax$ at each iteration.
 
-\cite{gilpinfirst} proposed a modified verson of the technqiues in \cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| / \delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in terms of the number of calls made to a first-order oracle (for example, Nesterov's optimal gradient \cite{nesterov1983}).
-Here $\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a certain \textit{condition number} for the game.
-It should be noted however that
+\cite{gilpinfirst} proposed a modified verson of the technqiues in
+\cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
+\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in
+terms of the number of calls made to a first-order oracle (for
+example, Nesterov's optimal gradient \cite{nesterov1983}). Here
+$\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a certain
+\textit{condition number} for the game. It should be noted however that
 \begin{itemize}
-\item[--] though \cite{gilpinfirst} proved that we always have $\delta > 0$, this constant can be arbitrarily small; and most importantly,
-\item[--] the reported linear convergence rate is not in terms of basic operations (addition, multiplication, matvec, clipping, etc.), but in terms of the number of calls to a first-order oracle.
-Of course, the existence of a linear algorithm for solving \eqref{eq:gilpin} is improbable, as the usual strong-convexity conditions are absent.
+\item[--] though \cite{gilpinfirst} proved that we always have $\delta
+  > 0$, this constant can be arbitrarily small; and most importantly,
+\item[--] the reported linear convergence rate is not in terms of
+  basic operations (addition, multiplication, matvec, clipping, etc.),
+  but in terms of the number of calls to a first-order oracle. Of
+  course, the existence of a linear algorithm for solving
+  \eqref{eq:gilpin} is improbable, as the usual strong-convexity
+  conditions are absent.
+
 \end{itemize}
 
-%% It should be noted that the EGT and its precursors have had considerable success in the signal processing communities, as can be seen in \cite{NestaCandès, eduard, etc.} and the references therein.
+%% It should be noted that the EGT and its precursors have had
+%% considerable success in the signal processing communities, as can
+%% be seen in \cite{NestaCandès, eduard, etc.} and the references
+%% therein.
 

### 2015-06-07 nips2015.tex
big refactor

@@
-\documentclass{article} % For LaTeX2e
-\usepackage{nips14submit_e,times}
+\documentclass[envcountsame]{llncs} % For LaTeX2e
+%\usepackage{mathpazo}
+%\usepackage{nips14submit_e,times}
 %\usepackage{hyperref}
 \usepackage{url}
-\usepackage{amsmath,amsfonts,amsthm}
+\usepackage{amsmath,amsfonts}%,amsthm}
 \usepackage{bbm}
@@
 %\usepackage[section]{placeins}
-\usepackage{subfigure}
+\usepackage[FIGTOPCAP]{subfigure}
 
@@
 
-\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
 
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{remark}{Remark}
+%\newtheorem{proposition}[theorem]{Proposition}
+%% \newtheorem{corollary}[theorem]{Corollary}
+%% \newtheorem{definition}[theorem]{Definition}
+%\newtheorem{remark}{Remark}
 \newtheorem{fact}{Fact}
@@
 
-\author{
-Elvis DOHMATOB
-\\
-Parietal team, Inria Saclay Ile-de-France, Saclay, France\\
-\textit{email}: elvis.dohmatob@inria.fr}
-
-\title{\bf Primal-dual algorithm for computing Nash equilibria in
-% two-person zero-sum
-sequential games with imcomplete information
-% with imcomplete information and perfect recall
+\title{\bf A simple algorithm for computing approximate Nash equilibria in
+  two-person zero-sum games with imcomplete information}
+\author{Elvis DOHMATOB\\\email{elvis.dohmatob@inria.fr}}
+\institute{
+Parietal team, Inria Saclay Ile-de-France, Saclay, France
 }
@@
 %with low costs per iteration,
-for computing Nash-equilibria in two-person zero-sum sequential games
-with imcomplete information and perfect recall (like Texas Hold'em
-Poker). This primal-dual algorithm derives from the general
-primal-dual algorithm developed
-% by Chambolle and Pock
-in \cite{chambolle2010,chambolle2014ergodic}. It should be noted that
-the latter primal-dual algorithm is not directly applicable to compute
-Nash equilibria for the aforementioned games considered here since the
-strategy profiles of players (polyhedra) are so complex that it is not
-possible
-% (for example, simplexes for simultaneous games, and intersections of
-% hyperplanes and nonnegative orthants, for sequential games)
- to effectively compute % (i.e using non-iterative procedures, etc.)
-euclidean
-% (metric)%
- projections (the proximal operators) thereupon.
-The core of our technique is to rewrite the equilibrium problem as an
-equivalent saddle-point problem for which the proximal operators can
-be computed analytically.
- %% dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point problem which is amenable to the primal-dual scheme.
+for computing approximate Nash equilibria in two-person zero-sum
+sequential games with imcomplete information and perfect recall (like
+Texas Hold'em Poker).
 Our algorithm only performs basic iterations
@@
 % only involving basic operations like matvec, clipping, etc., and no
-calls to external first-order oracles, etc.).
-Our algorithm is applicable to a broad class of two-person zero-sum
+calls to external first-order oracles, etc.) and is applicable to a
+broad class of two-person zero-sum
 games including simultaneous games and sequential games with
@@
 latter kind of games is thanks to the sequence-form representation von
-Stengel's \cite{von1996efficient}
+Stengel's \cite{von1996efficient}.
 %% Unlike the EGT (Excessive Gap Technique) recently used in
@@
 
-\subsection{Notation and terminology}
+\paragraph{\textbf{Notation and terminology.}}
 Let $m$ and $n$ be positive integers.
@@
 
-\subsection{Statement of the problem}
+\paragraph{\textbf{Statement of the problem.}}
 The sequence-form for two-person zero-sum games was introduced in
@@
     \text{maximize}-e_2^Tq,\hspace{.5em}\text{subject to }(y,q) \in
-    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, -A^Tx - E_2^Tq \leq 0,
+    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, A^Tx + E_2^Tq \geq 0,
     E_1x = e_1, x \ge 0.
@@
 \begin{equation}
-  Q_k := \{z \in \mathbb{R}^n_+ |\text{ }E_kz = e_k\}
+  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\}
 \label{eq:polyhedron}
@@
 
-\subsection{Outline of the article}
+\paragraph{\textbf{Our contribution.}}
 We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
@@
 projection can still be done iteratively using, for example, the
-algorithm in proposition 4.2 of \cite{combettes2010dualization} or any
-CQ algorithm (since this projection sub-problem, is, in fact a
-\textit{split-feasibility problem}), for example. Unfortunately, as
+algorithm in proposition 4.2 of \cite{combettes2010dualization}%%  or any
+%% CQ algorithm (since this projection sub-problem, is, in fact a
+%% \textit{split-feasibility problem}), for example
+. Unfortunately, as
 with any nested iterative scheme, one would have to solve this
@@
     \Psi_1(y, p, x, q)+ g_1(y, p) \text{ if }y \ge 0, \hat{\Psi}_1(y,
-    p, x, q) := \infty \text{ otherwise}\\
+    p, x, q) := \infty \text{ else}\\
     \hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(y, p) \text{ if
-    }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ otherwise}.
+    }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ else}.
   \end{aligned}
@@
 
-Consider the GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$)
+Define the sets $S_1 := \mathbb{R}^{n_2}_+ \times \mathbb{R}^{l_1}$ and $S_2 :=
+\mathbb{R}^{n_1}_+ \times \mathbb{R}^{l_2}$ and consider the
+GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$): Find $(y^*,p^*, x^*, q^*) \in
+S_1 \times S_2$ such that
 \begin{eqnarray}
@@
   \begin{aligned}
-      \text{Find }(y^*,p^*, x^*, q^*) \in \mathbb{R}^{n_2}_+
-  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}_+ \times
-  \mathbb{R}^{l_2}\text{ such that }\hat{\Psi}_1(y^*, p^*, x^*, q^*) \le \hat{\Psi}_1(y, p, x^*, q^*)
-      \text{ and }\\
-      \hspace{.5em}\hat{\Psi}_2(y^*, p^*, x^*, q^*) \le
-      \hat{\Psi}_2(y^*, p^*, x, q)
-        \forall (y,p, x, q) \in \mathbb{R}^{n_2}_+
-      \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}_+ \times
-      \mathbb{R}^{l_2}.
+    \hat{\Psi}_1(y^*, p^*, x^*, q^*) \le \hat{\Psi}_1(y, &p, x^*,
+    q^*),\hspace{.5em} \hspace{.5em}\hat{\Psi}_2(y^*, p^*, x^*, q^*)
+    \le \hat{\Psi}_2(y^*, p^*, x, q)\\
+    &\forall (y,p, x, q) \in S_1 \times S_2.
   \end{aligned}
@@
 \begin{proof}
-Define $S_1 := \dom(g_1) = \mathbb{R}^{n_2}_+ \times \mathbb{R}^{l_1}$
-and $S_2 := \dom(g_2) = 
-\mathbb{R}^{n_1}_+ \times \mathbb{R}^{l_2}$. Noting that the
-equilibria of the LCPs \eqref{eq:primal_pb},
-\eqref{eq:dual_pb}, and the equilibria of GSP($\Psi_1$, $\Psi_2$,
-$g_1$, $g_2$) are contained in $S_1 \times S_2$, it suffices to show
-that at any point $(y, p, x, q) \in S_1 \times S_2$, the duality
-primal-dual gap between the primal LCP \eqref{eq:primal_pb} and the
-dual LCP \eqref{eq:dual_pb} equals the primal-dual gap of
-GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
-
+Note that $\dom(g_1) = S_1$ and $\dom(g_2) = S_2$ and observe that the
+equilibria of the LCPs \eqref{eq:primal_pb}, \eqref{eq:dual_pb}, and
+the equilibria of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$) are contained
+in $S_1 \times S_2$, it suffices to show that at any point $(y, p, x,
+q) \in S_1 \times S_2$, the duality primal-dual gap between the primal
+LCP \eqref{eq:primal_pb} and the dual LCP \eqref{eq:dual_pb} equals
+the primal-dual gap of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
 Indeed, the unconstrained objective in \eqref{eq:primal_pb}, say
-$a(x,y)$, can be written as
+$a(x,y)$, can be computed as
 \begin{eqnarray*}
@@
 
-where $\phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
-}\hat{\Psi}_2(y, p, x', q') \in [-\infty, +\infty)$.
+where $-\infty \le \phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
+}\hat{\Psi}_2(y, p, x', q') < +\infty$.
 Similarly, the unconstrained objective, say
@@
 \end{eqnarray*}
-where $\phi_1(x, q) :=
-\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) \in
-         [-\infty, +\infty)$.
+where $-\infty \le \phi_1(x, q) :=
+\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) < +\infty$.
 Thus, one can compute the primal-dual gap between primal LCP
@@
   \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
-  \mathbb{R}^{l_2}$
-\Ensure $(\rho, \epsilon)$-Nash equilibrium
+  \mathbb{R}^{l_2}$.
+\Ensure A Nash $(\rho, \epsilon)$-equilibrium
 $(\tilde{y},\tilde{p},\tilde{x},\tilde{q}) \in S_1 \times S_2$ for
@@
 Let $d_0$ be the euclidean distance between the starting point
-$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ Algorithm \ref{Tab:algo} and the
+$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the
 set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
@@
   T-BD]{he2013accelerating}, applied on the GSP \eqref{eq:unconstrained_pb}
- with the choice of parameters $\sigma = 1 \in (0, 1]$, $\sigma_x =
+ with the choice of parameters: $\sigma = 1 \in (0, 1]$, $\sigma_x =
          \sigma_y = 0 \in [0, \sigma)$,
@@
                \sigma_y^2)}}{\sigma L_{xy}} = \sigma / \|K\| =
-           1/\|K\|$, $\lambda = \lambda_{xy} \in (0,
+           1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
            \lambda_{xy}]$. The convergence result then follows from
@@
 \begin{figure}[!htpb]
-  \includegraphics[width=.34\linewidth]{simplex_dgap.pdf}
+  \subfigure[Matrix game on simplices]{
+    \includegraphics[width=.33\linewidth]{simplex_dgap.pdf}
+  }
+  \hspace{-2em}
+  \subfigure[Simplified Poker]{
+    \includegraphics[width=.33\linewidth]{SimplifiedPoker_dgap.pdf}
+  }
+  \hspace{-2em}
+  \subfigure[Kuhn 3-card Poker]{
+    \includegraphics[width=.33\linewidth]{Kuhn3112_dgap.pdf}
+  }
+  \vspace{-1em}
   \hspace{-1em}
-  \includegraphics[width=.34\linewidth]{SimplifiedPoker_dgap.pdf}
-  \hspace{-.8em}
-  \includegraphics[width=.34\linewidth]{Kuhn3112_dgap.pdf}
-  \hspace{-1.3em}
-  \includegraphics[width=.35\linewidth]{simplex_NE.pdf}
-  \hspace{-.8em}
-  \includegraphics[width=.34\linewidth]{SimplifiedPoker_NE.pdf}
-  \hspace{-1.3em}
-  \includegraphics[width=.34\linewidth]{Kuhn3112_NE.pdf}
+  \includegraphics[width=.34\linewidth]{simplex_NE.pdf}
+  \hspace{-1em}
+  \includegraphics[width=.33\linewidth]{SimplifiedPoker_NE.pdf}
+  \hspace{-1em}
+  \includegraphics[width=.33\linewidth]{Kuhn3112_NE.pdf}
   \caption{Convergence curves of Algorithm
-    \ref{Tab:algo}. \textbf{Left column}: Random $1000
-    \times 1000$ matrix game on simplexes. \textbf{Middle column}:
-    Simplified poker. \textbf{Right column}: Kuhn 3-card
-    Poker. \textbf{Top row}: convergence in terms of ergodic
+    \ref{Tab:algo}. \textbf{Top row}: convergence in terms of ergodic
     primal-dual gap. \textbf{Bottom row}: Convergence in terms of
@@
 
-%% \begin{remark}
-%% The results presented here are not meant to be benchmarks comparing
-%% our algorithm to other algorithms, but should rather be seen as
-%% proof-of-concept which experimentally  validates the rigorously
-%% extablished results in section \ref{sec:algo}.
-% \end{remark}
-
-\paragraph{Simulated game: matrix game on simplexes.}
+\paragraph{\textbf{Simulated game: matrix game on simplexes.}}
 Any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a
@@
 
-\paragraph{Real-world game: Kuhn 3-card Poker.}
+\paragraph{\textbf{Real-world game: Kuhn 3-card Poker.}}
 The sequence-form representation of this simplified Poker variant

### 2015-06-07 primal_dual.py

@@ -1,64 +1,21 @@
-# Primal-Dual algorithm for computing Nash equilibria in two-person
-# zero-sum games.
-#
-# author: DOHMATOB Elvis
+"""
+Primal-Dual algorithm for computing Nash equilibria in two-person
+zero-sum games.
 
-import warnings
+"""
+# author: Elvis Dohmatob <gmdopp@gmail.com>
+
 from math import sqrt
 import numpy as np
 from scipy import linalg
 
-
-def power(A, p, max_iter=100, **kwargs):
-    """Power iteration to estimate spectral radius of a linear operator."""
-    b = np.random.randn(p)
-    for _ in xrange(max_iter):
-        b = A(b, **kwargs)
-        d = sqrt(np.dot(b, b))
-        print d
-        if d == 0:
-            return d
-        b /= d
-    lambd = np.dot(b, A(b, **kwargs))
-    lambd /= np.dot(b, b)
-    return lambd
-
-
-def evil(L, r, z, proj_C=lambda v: np.maximum(v, 0.), L_norm=None,
-         max_iter=100, verbose=1, tol=1e-4):
-    """Projects the point z onto the intersection of the polyhedron "Lx=r"
-    and the convex set C.
-
-    References
-    ----------
-    P. Combettes et al, "Dualization of Signal Recovery Problems", p.17
-    """
-    if L_norm is None:
-        L_norm = linalg.svdvals(L)[0]
-    gamma = .99 / L_norm ** 2
-    v = np.zeros(L.shape[0])
-    x = np.zeros(L.shape[1])
-    salt = 1e-4
-    for k in xrange(max_iter):
-        old_x = x.copy()
-        x = proj_C(z - L.T.dot(v)) + salt
-        v += gamma * (L.dot(x) - r + salt)
-        salt *= .5  # we want: \sum_{k}{salt_k} < \infty
-        error = sqrt(((x - old_x) ** 2).sum())
-        if verbose:
-            print "\tIteration %03i/%03i: x=%s, error=%5.2e" % (
-                k + 1, max_iter, x, error)
-        if error < tol and 1:
-            if verbose:
-                print "\tConverged after %i iterations." % (k + 1)
-            break
-    return x
+# norm of the concatenation of vectors
+_norm = lambda *args: sqrt(np.sum(np.concatenate(args) ** 2))
 
 
 def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
[…]

### 2015-06-07 simple.py

@@ -7,8 +7,7 @@ import numpy as np
 import matplotlib
 import matplotlib.pyplot as plt
 from sklearn.utils import check_random_state
-# from primal_dual import primal_dual_ne, primal_dual_sg_ne
-from tseng_bd import primal_dual_ne, primal_dual_sg_ne
+from primal_dual import primal_dual_ne, primal_dual_sg_ne
 
 # matplotlib confs
 matplotlib.rcParams['text.latex.preamble'] = ['\\boldmath']
@@ -964,7 +963,7 @@ if __name__ == "__main__":
                            "\\rangle$"), fontsize=50)
         ax.axhline(
             -1. / 18. if isinstance(game, Kuhn3112) else value,
-            linestyle="--", dashes=(10, 10), color="k",
+            linestyle="--", dashes=(20, 10), color="r",
             linewidth=4, **kwargs)
         plt.legend(loc="best", prop=dict(size=45), handlelength=1.5)
         ax.ticklabel_format(axis="y", style="sci", scilimits=(0., 0.))
@@ -976,8 +975,8 @@ if __name__ == "__main__":
         plt.figure(figsize=(13.5, 10))
         plt.grid("on")
         plt.loglog(cst / np.arange(1, len(dgaps) + 1), linestyle="--",
-                   dashes=(10, 10), label="$\\mathcal{O}(1/k)$", linewidth=4,
-                   color="k")
+                   dashes=(20, 10), label="$\\mathcal{O}(1/k)$", linewidth=4,
+                   color="r")
         plt.loglog(np.abs(dgaps), label="\\textbf{Algorithm 1}", linewidth=4)
         if cnt == 0:
             plt.ylabel("\\textbf{$||\\tilde{v}^{a}_k||$}", fontsize=50)

### 2015-06-07 tseng_bd.py

@@ -50,53 +50,3 @@ def tseng_bd(K, prox_g1, prox_g2, init=None, max_iter=1000,
     init["w"] = w.copy()
     init["z"] = z.copy()
     return w, z, init, np.array(gaps)
-
-
-def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
-                   proj_C2=lambda y: np.maximum(y, 0.), init=None, tol=1e-10,
-                   max_iter=10000):
-    """Primal-Dual algorithm for computing Nash equlibrium for two-person
-    zero-sum game with payoff matrix A and contraint sets
-
-        Qj := {z in Cj | Ejz = ej}
-
-    The formal problem is:
-
-        minimize maximize <x, Ay>
-        y in Q2  x in Q1
-    """
-    n1, n2 = A.shape
-    k1, k2 = E1.shape[0], E2.shape[0]
-    zeros = np.zeros((k2, k1))
-    K = np.vstack((np.hstack((A, -E1.T)), np.hstack((E2, zeros))))
-    values = []
-
-    def prox_g1(w, lambd):
-        w[:n2] = proj_C2(w[:n2])
-        w[n2:] -= lambd * e1
-        return w
-
-    def prox_g2(z, lambd):
-        z[:n1] = proj_C1(z[:n1])
-        z[n1:] -= lambd * e2
-        return z
-
-    def callback(variables):
-        y = variables["w"][:n2]
-        x = variables["z"][:n1]
-        value = x.dot(A.dot(y))
-        values.append(value)
-
-    w, z, init, gaps = tseng_bd(K, prox_g1, prox_g2, max_iter=max_iter,
-                                init=init, tol=tol, callback=callback)
-    y, p = w[:n2], w[n2:]
-    x, q = z[:n1], z[n1:]
-    return x, y, p, q, init, values, gaps
-
-
-def primal_dual_sg_ne(A, **kwargs):
-    n1, n2 = A.shape
-    E1 = np.ones((1, n1))
-    E2 = np.ones((1, n2))
-    e1 = e2 = 1.
-    return primal_dual_ne(A, E1, E2, e1, e2, **kwargs)

### 2015-06-07 nips2015.tex
getting down to business (WINE conf is coming)

@@
-\documentclass[envcountsame]{llncs} % For LaTeX2e
-%\usepackage{mathpazo}
-%\usepackage{nips14submit_e,times}
-%\usepackage{hyperref}
+\documentclass[envcountsame]{llncs}
 \usepackage{url}
-\usepackage{amsmath,amsfonts}%,amsthm}
+\usepackage{amsmath,amsfonts}
 \usepackage{bbm}
@@
 \usepackage[titletoc]{appendix}
-
 \usepackage{algpseudocode}
 \usepackage{pifont}
-
-%\usepackage[section]{placeins}
 \usepackage[FIGTOPCAP]{subfigure}
 
-\def\B#1{\bm{#1}}
-%\def\B#1{\mathbf{#1}}
-\def\trans{\mathsf{T}}
-
-%\renewcommand{\labelitemi}{--}
-
-%\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
-
-%\newtheorem{proposition}[theorem]{Proposition}
-%% \newtheorem{corollary}[theorem]{Corollary}
-%% \newtheorem{definition}[theorem]{Definition}
-%\newtheorem{remark}{Remark}
 \newtheorem{fact}{Fact}
-
 \DeclareMathOperator{\dom}{dom}
@@
   \hspace{-2em}
-  \subfigure[Simplified Poker]{
+  \subfigure[Toy Poker]{
     \includegraphics[width=.33\linewidth]{SimplifiedPoker_dgap.pdf}
@@
   \caption{Convergence curves of Algorithm
-    \ref{Tab:algo}. \textbf{Top row}: convergence in terms of ergodic
-    primal-dual gap. \textbf{Bottom row}: Convergence in terms of
+    \ref{Tab:algo}. \textbf{Top row}: Evolution of ergodic
+    primal-dual gap. \textbf{Bottom row}: Evolution of
     value of game.}
@@
 
-\paragraph{\textbf{Simulated game: matrix game on simplexes.}}
+\paragraph{\textbf{Matrix game on simplexes.}}
 Any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a
@@
 \times 1000$ random matrix whose entries are uniformly identically
-distributed in the closed interval $[-1, 1]$. See Figure \ref{Tab:sim_dgap_curve}...
+distributed in the closed interval $[-1, 1]$.
 
-\paragraph{\textbf{Real-world game: Kuhn 3-card Poker.}}
-The sequence-form representation of this simplified Poker variant
-\cite{kuhn} is given by (not showing zero entries)\\
+\paragraph{\textbf{Toy Poker game.}}
+The has $n_1 = n_2 = 5$ and $l_1 = l_2 = 3$. Its sequence-form
+representation is given by (showing only nonzero entries):\\
 
-$E_1 = \left[\begin{array}{ccccccccccccc}
-1 &   &   &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
--1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
-  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
-  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
-  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
-\end{array}\right] \in \mathbb{R}^{7 \times 13}$,
-$E_2 = \left[\begin{array}{ccccccccccccc}
-1 &   &   &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
--1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
--1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
--1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
--1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
-\end{array}\right] \in \mathbb{R}^{7 \times 13}$, $e_1 = e_2 = [1, 0,
-  0, 0, 0, 0, 0]^T \in \mathbb{R}^7$, and $A =
-\\\left[\begin{array}{ccccccccccccc}
+ $E_1(0,0) = E_1(1,1) =
+E_1(1,2) = E_1(2,3) = E_1(2,4) = \textbf{1}$,
+$E_1(1,0) = E_1(2,0) = \textbf{-1}$;\\
 
-  &   &   &   &   &   &   &   &   &   &   &   &  \\
-  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
-  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
-  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
-  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
-  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
-  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
-  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
-  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
-  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
-  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
-  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
-  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
-\end{array}\right] \in \mathbb{R}^{13 \times 13}$.\\
+$E_2(0,0) = E_2(1,1) = E_2(1,2) = E_2(2,3) = E_2(2,4) = \textbf{1}$,
+$E_2(1,0) = E_2(2,0) = \textbf{-1}$; and\\
+
+$A(2,0) = A(4,0) = \textbf{-0.5}$, $A(1,3) = \textbf{1}$, $A(3,1) =
+\textbf{-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = \textbf{0.25}$.
+
+\paragraph{\textbf{Kuhn 3-card Poker.}}
+The game has $n_1 = n_2 = 13$ and $l_1 = l_2 = 7$, and its
+sequence-form is given by:\\
+
+$E_1(0,0) = E_1(1,9) = E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
+E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
+E_1(6,11) = \textbf{1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
+E_1(5,5) = E_1(6,9) = \textbf{-1}$;\\
+
+$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
+E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
+E_2(6,4) = \textbf{1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
+E_2(5,0) = E_2(6,0) = \textbf{-1}$; and\\
+
+$A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
+\textbf{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
+A(6,4) = A(6,12) = A(10,4) = A(10,8) = \textbf{-0.166667}$, $A(7,4) =
+A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = \textbf{0.333333}$,
+$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
+A(12,1) = A(12,5) = \textbf{0.166667}$.\\
+
 The pair $(x^*, y^*) \in \mathbb{R}^{13} \times \mathbb{R}^{13}$ of
@@
 \begin{eqnarray*}
-  {x^*}^TAy^* = -0.055593685705289997,
+  {x^*}^TAy^* = \textbf{-0.05555},
 \end{eqnarray*}
- which agrees to 4 d.p with the value of $-1 / 18$ computed
+ which agrees to 5 d.p with the value of $-1 / 18$ computed
  analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. The
  evolution of the dual gap and the expected value of the game across
- iterations is shown in Figure \ref{Tab:dgap_curve}. These figures
- validate the theoritically established $\mathcal{O}(1/\epsilon)$
- convergence rate of the Algorithm.
+ iterations is shown in Figure \ref{Tab:dgap_curve}.
 
@@
 very low constant cost per iteration, and enjoys a rigorous
-convergence theory with a proven $\mathcal{O}(1/\epsilon)$ convergence
+convergence theory with a proven $\mathcal{O}(1/min(\rho,\epsilon))$ convergence
 in terms of basic operations (matvec products, clipping, etc.), to a
-Nash $\epsilon$-equilibrium of the game. The core of our contribution
-(summarized in Theorems \ref{thm:pd} and \ref{thm:conv}) was to show
-that a reformulation of the Nash equilibrium problem for sequential
-games with imcomplete information lends the problem directly
-accessible to primal-dual framework
-\cite{chambolle2010,chambolle2014ergodic}.
+Nash $(\rho,\epsilon$-equilibrium of the game.
 
@@
 
-\paragraph{Acknowledgments:} ...
 \small

### 2015-06-07 primal_dual.py

@@ -32,8 +32,8 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
     # misc
     if init is None: init = {}
     n1, n2 = A.shape
-    k1, k2 = E1.shape[0], E2.shape[0]
-    zeros = np.zeros((k2, k1))
+    l1, l2 = E1.shape[0], E2.shape[0]
+    zeros = np.zeros((l2, l1))
     if "norm_K" in init: norm_K = init["norm_K"]
     else:
         # XXX use power iteration to compute ||K||
@@ -42,9 +42,9 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
     sigma = init.get("sigma", 1.)
     lambd = init.get("lambd", .9 * sigma / norm_K)
     y = init.get("x", np.zeros(n2))
-    p = init.get("p", np.zeros(k1))
+    p = init.get("p", np.zeros(l1))
     x = init.get("x", np.zeros(n1))
-    q = init.get("q", np.zeros(k2))
+    q = init.get("q", np.zeros(l2))
     delta_y_sum = np.zeros_like(y)
     delta_p_sum = np.zeros_like(p)
     delta_x_sum = np.zeros_like(x)

### 2015-06-07 simple.py

@@ -16,6 +16,21 @@ matplotlib.rc('text', usetex=True)
 plt.rc('font', size=50)  # make the power in sci notation bigger
 
 
+def _matrix2texstr(A, name="A", exclude=None):
+    if exclude is None: exclude = []
+    vals = dict((val, []) for val in np.unique(A))
+    for val in exclude: del vals[val]
+    for v, u in vals.items():
+        for i in range(A.shape[0]):
+            for j in range(A.shape[1]):
+                if A[i, j] == v: u.append((i, j))
+    out = []
+    for v, u in vals.items():
+        out.append("$" + " = ".join(["%s(%i,%i)" % (name, i, j)
+                                     for (i, j) in u] + ["\\textbf{%g}$" % v]))
+    return ", ".join(out)
+
+
 class Game(object):
     """Sequence-form representaion of two-person zero-sum games with perfect
     recall and imcomplete information (like Poker, love, war, diplomacy, etc.)
@@ -473,7 +488,11 @@ class Game(object):
         nx.draw_networkx_edge_labels(self.tree, pos,
                                      edge_labels=self.edge_labels)
 
-        # plt.axis("off")
+    def matrices2texstrs(self):
+        return [
+            _matrix2texstr(self.constraints[1][0], exclude=[0.], name="E_1"),
+            _matrix2texstr(self.constraints[1][0], exclude=[0.], name="E_2"),
+            _matrix2texstr(self.payoff_matrix, exclude=[0.], name="A")]
 
 
 class Kuhn3112(Game):

### 2015-06-07 nips2015.tex
more

@@
 \end{proof}
-\subsection{Practical considerations: Efficient computation of $Ay$ and $A^Tx$.}
+\subsection{Practical considerations}
+\paragraph{\textbf{Efficient computation of $Ay$ and $A^Tx$.}}
 In Algorithms \ref{Tab:algo} most of the time is spent
@@
 One notes that $(F \otimes B)^T = F^T \otimes B^T$.
-$F \otimes B$ can be very much larger than both $F$ and $B$ in dimensions.
-For example, if $r = n = r = s = 1000$, so that $F$ and $B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a $10^6$-by-$10^6$ matrix!
-Fortunately, given a vector $x \in \mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$ without forming $F \otimes B$.
-Indeed, let $y := (F \otimes B)x$.
-We rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1, ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of $s$ elements of $x$ read from left to right.
-Similarly, rewrite $y$ as as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$.
-Then one easily verfies that $Y$ is the matrix product of the ``small'' matrices $B$, $X$, and $F^T$, i.e
+$F \otimes B$ can be very much larger than both $F$ and $B$ in
+dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
+$B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
+$10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
+\mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
+without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
+rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
+  ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
+$s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
+as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
+easily verfies that $Y$ is the matrix product of the ``small''
+matrices $B$, $X$, and $F^T$, i.e
+
 \begin{equation}
@@
 
-Now, in Texas Hold'em for example, the payoff matrix $A$ can be written as block-diagonal matrix whose blocks are sums of Kronecker products of much smaller sparse matrices as follows
+Now, in Texas Hold'em for example, the payoff matrix $A$ can be
+written as block-diagonal matrix whose blocks are sums of Kronecker
+products of much smaller sparse matrices as follows
 
 \begin{equation}
-  A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2 \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
+  A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
+    \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
+    B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
 \label{eq:factor_A}
 \end{equation}
-See \cite{hoda2010smoothing}.
-The matrices $F_i$ correspond to sequences of moves in round $i$ which end in a \textit{fold} action, and $S$ to the sequences which end in a \textit{showdown}.
-$B_i$ encodes the betting structure of round $i$, while $W$ encodes the wind/lose/draw information determined by ranking the players' hands at showdown.
-The component matrices $F_i$, $B_i$, $S$, and $W$ are small enough to be explictly represented whereas it is infeasible to explicitly represent A.
-Furthermore, the matrices $F_i$, $B_i$,
-$S$, and $W$ are themselves sparse, which allows one to use the compressed row storage data structure that only stores nonzero entries (for example \textit{scipy.sparse.csr\_matrix}, in the Python programming language).
+See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
+sequences of moves in round $i$ which end in a \textit{fold} action,
+and $S$ to the sequences which end in a \textit{showdown}. $B_i$
+encodes the betting structure of round $i$, while $W$ encodes the
+wind/lose/draw information determined by ranking the players' hands at
+showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
+enough to be explictly represented whereas it is infeasible to
+explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
+$S$, and $W$ are themselves sparse, which allows one to use the
+compressed row storage data structure that only stores nonzero entries
+(for example \textit{scipy.sparse.csr\_matrix}, in the Python
+programming language).
 
-Such a representation of the payoff matrix $A$ trivializes matvec operations involving $A$ or $A^T$ (thanks to formula \eqref{eq:kron_matvec} above, applied to their diagonal blocks and exploiting the sparsity of these blocks themselves).
-Of course, one can always write the payoff matrix $A$ of a flop-type Poker game in a form similary to \eqref{eq:factor_A} by applying appropriate permutations to the enumeration of the players's sequences.
+Such a representation of the payoff matrix $A$ trivializes matvec
+operations involving $A$ or $A^T$ (thanks to formula
+\eqref{eq:kron_matvec} above, applied to their diagonal blocks and
+exploiting the sparsity of these blocks themselves). Of course, one
+can always write the payoff matrix $A$ of a flop-type Poker game in a
+form similary to \eqref{eq:factor_A} by applying appropriate
+permutations to the enumeration of the players's sequences.
+
+\paragraph{\textbf{Computing $\|K\|$.}} Power iteration (Perron-Frobenius)...
 

### 2015-06-07 nips2015.tex
more

@@
 \begin{abstract}
-We present a simple primal-dual algorithm
-%with low costs per iteration,
-for computing approximate Nash equilibria in two-person zero-sum
-sequential games with imcomplete information and perfect recall (like
-Texas Hold'em Poker).
-Our algorithm only performs basic iterations
-(i.e iterations involving no
-% only involving basic operations like matvec, clipping, etc., and no
-calls to external first-order oracles, etc.) and is applicable to a
-broad class of two-person zero-sum
-games including simultaneous games and sequential games with
-imcomplete information and perfect recall. The applicability to the
-latter kind of games is thanks to the sequence-form representation von
-Stengel's \cite{von1996efficient}.
-%% Unlike the EGT (Excessive Gap Technique) recently used in
-%% \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap
-%% and constant cost per iteration.
-As an application, we apply our algorithm to solve Kuhn 3-card Poker.
-%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
+We present a simple primal-dual algorithm for computing approximate
+Nash equilibria in two-person zero-sum sequential games with
+imcomplete information and perfect recall (like Texas Hold'em
+Poker). Our algorithm only performs basic iterations (i.e iterations
+involving no calls to external first-order oracles, etc.) and is
+applicable to a broad class of two-person zero-sum games including
+simultaneous games and sequential games with imcomplete information
+and perfect recall. The applicability to the latter kind of games is
+thanks to the sequence-form representation
+\cite{koller1992complexity}. As an application, we apply our algorithm
+to solve Kuhn 3-card Poker.
 \end{abstract}
@@
 \cite{koller1992complexity}, and the theory was further developed in
-\cite{von1996efficient,vonequilibrium}, where it was established that
-for sequential two-person zero-sum games with imcomplete information
-and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1
+\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
+established that for sequential two-person zero-sum games with
+imcomplete information and perfect recall, there exist sparse matrices
+$A \in \mathbb{R}^{n_1
   \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in
@@
 \label{sec:algo}
+\textbf{XXX TODO: Define the ergodic variables $\tilde{v}^a$ and
+  $\tilde{\epsilon}^a$, ...}
 
-%% According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCPs
-%% \eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the
-%% saddle-point problem \eqref{eq:unconstrained_pb}. An attractive method
-%% for such a saddle-point problem would be a primal-dual scheme, like
-%% that developed in \cite[Algorithm 39]{chambolle2010}. 
-%% Usually, to use a primal-dual algorithm, one needs a measure of the
-%% ``quality'' of the current iterates as regards being the solution of
-%% the saddle-point problem. A natural measure of this fittness is the
-%% primal-dual gap, which measures defection from strong-duality.
-%% However, the primal-dual gap in \eqref{eq:unconstrained_pb} can be
-%% unbounded even at near feasible points.  is well-suited for
-
-Consider the following algorithm
+Consider the following algorithm for solving the GSP \eqref{eq:unconstrained_pb}
 \begin{algorithm}

### 2015-06-07 primal_dual.py

@@ -70,6 +70,7 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
         delta_x = x - old_x
         delta_q = q - old_q
         y -= lambd * (A.T.dot(delta_x) + E2.T.dot(delta_q))
+        p += lambd * E1.dot(delta_x)
 
         # compute game value and primal-dual gap at current iterates
         value = x.dot(A.dot(y))

### 2015-06-07 nips2015.tex
BF: sign error in algo
ENHs
glitches

@@
 in $S_1 \times S_2$, it suffices to show that at any point $(y, p, x,
-q) \in S_1 \times S_2$, the duality primal-dual gap between the primal
+q) \in S_1 \times S_2$, the primal-dual gap between the primal
 LCP \eqref{eq:primal_pb} and the dual LCP \eqref{eq:dual_pb} equals
@@
 (A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
-\State $p^{(k+1)} \leftarrow p^{(k+1)} - \lambda E_1(x^{(k+1)}-x^{(k)})$
+\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1(x^{(k+1)}-x^{(k)})$
 \State $k \leftarrow k + 1$
@@
 \paragraph{\textbf{Toy Poker game.}}
-The has $n_1 = n_2 = 5$ and $l_1 = l_2 = 3$. Its sequence-form
-representation is given by (showing only nonzero entries):\\
+The sequence-form representation for this Toy Poker game is given by
+(showing only nonzero entries):\\
 
- $E_1(0,0) = E_1(1,1) =
+$E_1 \in \mathbb{E}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
 E_1(1,2) = E_1(2,3) = E_1(2,4) = \textbf{1}$,
-$E_1(1,0) = E_1(2,0) = \textbf{-1}$;\\
+$E_1(1,0) = E_1(2,0) = \textbf{-1}$; \\
 
-$E_2(0,0) = E_2(1,1) = E_2(1,2) = E_2(2,3) = E_2(2,4) = \textbf{1}$,
-$E_2(1,0) = E_2(2,0) = \textbf{-1}$; and\\
+$E_2 \in \mathbb{E}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
+= E_2(2,3) = E_2(2,4) = \textbf{1}$, $E_2(1,0) = E_2(2,0) =
+\textbf{-1}$; and \\
 
-$A(2,0) = A(4,0) = \textbf{-0.5}$, $A(1,3) = \textbf{1}$, $A(3,1) =
+$A \in \mathbb{E}^{5 \times 5}$ with $A(2,0) =
+A(4,0) = \textbf{-0.5}$, $A(1,3) = \textbf{1}$, $A(3,1) =
 \textbf{-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = \textbf{0.25}$.
@@
 
-$E_1(0,0) = E_1(1,9) = E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
+$E_1 \in \mathbb{E}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
+E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
 E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
 E_1(6,11) = \textbf{1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
-E_1(5,5) = E_1(6,9) = \textbf{-1}$;\\
+E_1(5,5) = E_1(6,9) = \textbf{-1}$; \\
 
+ $E_2 \in \mathbb{E}^{7 \times 13}$
 $E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
@@
 E_2(6,4) = \textbf{1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
-E_2(5,0) = E_2(6,0) = \textbf{-1}$; and\\
+E_2(5,0) = E_2(6,0) = \textbf{-1}$; and \\
 
-$A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
+ $A \in \mathbb{E}^{13 \times
+  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
 \textbf{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =

### 2015-06-07 nips2015.tex
more theory

@@
 
-\title{\bf A simple algorithm for computing approximate Nash equilibria in
-  two-person zero-sum games with imcomplete information}
+\title{\bf A simple and efficient algorithm for computing approximate
+  Nash equilibria in two-person zero-sum games with imcomplete
+  information\smallskip\hrule\hrule}
 \author{Elvis DOHMATOB\\\email{elvis.dohmatob@inria.fr}}
@@
 simultaneous games and sequential games with imcomplete information
-and perfect recall. The applicability to the latter kind of games is
-thanks to the sequence-form representation
-\cite{koller1992complexity}. As an application, we apply our algorithm
-to solve Kuhn 3-card Poker.
+and perfect recall. The number of iterations need to produce a Nash
+equilibrium with a given precision is inversely proportion to the
+precision. The applicability to the latter kind of games is thanks to
+the sequence-form representation \cite{koller1992complexity}. As
+proof-of-concept, we apply our algorithm to solve Kuhn 3-card Poker.
 \end{abstract}
@@
 \textbf{keywords}: sequential game; imcomplete information; perfect
-recall; sequence-form; Nash equilibrium; primal-dual algoithm;
-split-feasibility problem; convex-optimization
+recall; sequence-form; approximate Nash equilibrium; primal-dual
+algoithm; convex-optimization
 
@@
 \label{sec:intro}
+\paragraph{\textbf{Context.}}
 A game-theoretic approach to playing games strategically optimally
@@
 denotes the $m$-by-$n$ matrix of zeros.
-
 Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
@@
  defined to be the largest \textit{singular value} of $A$, i.e the
- largest \textit{eigen-value} of $A^TA$ (or equivalently, of $AA^T$).
+ largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).
 
 Given a subset $C$ of $\mathbb{R}^n$,
-$i_C$ denotes its \textit{indicator function} defined by $i_C(x) = 0$
-if $ x \in C$; $i_c(x) = \infty$ otherwise.
+$i_C$ denotes its \textit{indicator function} defined by
+\begin{eqnarray}
+  i_C(x) = 0, \text{ if } x \in C;\hspace{.3em} i_c(x) = \infty\text{
+    otherwise.}
+\end{eqnarray}
+
 Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a convex
@@
 The \textit{effective domain} of $f$, denoted $\dom(f)$ is defined as
-$\dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$. If $\dom(f) \ne
-\emptyset$ then we say $f$ is \textit{proper}.
+\begin{eqnarray}
+  \dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
+\end{eqnarray}
+ If $\dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
 %% \textit{proper convex lower semi-continous function}
@@
 %%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
-Given $\tau > 0$, the \textit{proximal operator}
-of $f$ at rank $\tau$, denoted $\prox_{\tau f}$, is the
-function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
-unique) minimizer of the $1$-strongly convex function $\mathbb{R}^n
-\rightarrow (-\infty,+\infty]$, $z\mapsto \frac{1}{2}\|z - x\|^2 +
-  \tau f(z)$.
+Given $\tau > 0$, the function
+\begin{eqnarray}
+  \prox_{\tau f}: \mathbb{R}^n \rightarrow \mathbb{R}^n,\hspace{.5em}x
+  \mapsto \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
+  - x\|^2 + \tau f(z),
+\end{eqnarray}
 
+is called the \textit{proximal operator} of $f$ at rank $\tau$.
 The interested reader should refer to
@@
 \end{equation}
-\end{definition}
-
-\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
-Given $\rho > 0$ and $\epsilon > 0$, a Nash $(\rho,\epsilon$)-equilibrium is
-a pair $(x^*, y^*)$ of realization plans such that there exists dual
-vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
-\eqref{eq:dual_pb} such that ...
+\label{thm:approx_nash}
 \end{definition}
@@
 We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
-algorithm for computing Nash $(\rho, \epsilon$)-equilibria for
+algorithm for computing Nash $(\rho, \epsilon$)-equilibria (in a sense
+to be made clear later) for
 sequential two-person zero-sum games with imcomplete information and
@@
     p, x, q) := \infty \text{ else}\\
-    \hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(y, p) \text{ if
+    \hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(x, q) \text{ if
     }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ else}.
@@
 := 0$.
+\qed
 
@@
 
-\section{The algorithm}
+\section{The proposed algorithm}
 \label{sec:algo}
+In this section we derive the algorithm which is the main object of
+this manuscript.
+
+\subsection{Relaxing the conditions for equilibrium}
+Let us first introduce the notion of $\epsilon$-subgradients. The idea
+is to replace the usual optimality characterization ``$x$ optimal iff
+$0 \in \partial f(x)$'' with ``$x$ approx optimal iff $0 \in
+\partial_\epsilon f(x)$''. In fact, letting $\epsilon \rightarrow 0^+$,
+$\partial f(x) = \partial_{0^+}f(x)$ will coincide with
+subgradient of $f$ at $x$, namely $\{h\in X | f(z) \ge f(x) + \langle
+h, z - x\rangle \forall z \in X\}$.
+
+\begin{definition}[$\epsilon$-subgradient]
+Given a scalar $\epsilon > 0$ and a function $f:X \subseteq \mathbb{R}^n
+\rightarrow [-\infty,+\infty]$, the $\epsilon$-subgradient of $f$ the
+set-valued function
+\begin{eqnarray}
+\partial_\epsilon f: X \mapsto 2^X, \hspace{.5em} x \mapsto \{h\in X |
+f(z) + \epsilon \ge f(x) + \langle h, z - x\rangle \forall z \in X\}.
+\end{eqnarray}
+\end{definition}
+
+%% Since won't typically be able to compute a feasible point in $Q_1 \in
+%% Q_2$ (due to the equality constraints $E_kz = e_k$), we will consider
+%% an approximate equilibrium concept which takes in to account the
+%% distance from the set of equilibria. Viz,
+
+\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
+Given $\rho > 0$ and $\epsilon > 0$, a Nash
+$(\rho,\epsilon$)-equilibrium is a pair $(x^*, y^*)$ of realization
+plans such that there exists dual vectors $p^*$ and $q^*$ and a
+pertubation vector $v^*$ for which
+\begin{eqnarray}
+\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
+\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
+  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
+\end{eqnarray}
+\end{definition}
+
+The above definition is a generalization of the notion of Nash
+equilibria in the sense that
+\begin{itemize}
+\item Exact Nash equilibria correspond to Nash $(0^+,0^+)$-equilibria.
+\item Nash $\epsilon$-equilibria (in the sense of Definition
+  \ref{thm:approx_nash}) correspond to Nash $(0^+,\epsilon)$-equilibria.
+\end{itemize}
+
+%\paragraph{\textbf{Plan of attack.}}
 \textbf{XXX TODO: Define the ergodic variables $\tilde{v}^a$ and
@@
 
-Consider the following algorithm for solving the GSP \eqref{eq:unconstrained_pb}
+\subsection{The algorithm proper and its convergence rate}
+Consider the following algorithm for solving the GSP
+\eqref{eq:unconstrained_pb}
 \begin{algorithm}
@@
 with $L_{xx} = L_{yy} = 0$ and $L_{xy} = L_{yx} = \|K\|$. Now,
-either of $g_1$ and $g_2$ is a separable sum of
-the indicator function of a convex set, whose prox is simply the
-euclidean projection onto the set,  and a linear transformation $z
-\mapsto a^Tz$ whose prox is simply $z \mapsto z - \tau a$. Thus,  one
-computes their respective proximal operators $\prox_{\tau g_1} :
-\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow \mathbb{R}^{n_2}
-\times \mathbb{R}^{l_1}$, $\prox_{\sigma g_2}: \mathbb{R}^{n_1} \times
-\mathbb{R}^{l_2} \rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}$
-$\prox_{\lambda g_1}(y, p) = ((y)_+, p - \lambda e_1)$ and $\prox_{\lambda
-  g_2}(x, q) = ((x)_+, q - \lambda e_2)$. Algorithm \ref{Tab:algo} is
-then obtained from \cite[Algorithm
-  T-BD]{he2013accelerating}, applied on the GSP \eqref{eq:unconstrained_pb}
- with the choice of parameters: $\sigma = 1 \in (0, 1]$, $\sigma_x =
-         \sigma_y = 0 \in [0, \sigma)$,
+one easily computes the proximal operators $g_1$ and $g_2$ as
+\begin{eqnarray*}
+  \prox_{\lambda g_1}(y, p) \equiv ((y)_+, p - \lambda
+  e_1),\hspace{.5em} \prox_{\lambda g_2}(x, q) \equiv ((x)_+, q -
+  \lambda e_2).
+  \end{eqnarray*}
+
+Algorithm \ref{Tab:algo} is then obtained from \cite[Algorithm
+  T-BD]{he2013accelerating}, applied on the GSP
+\eqref{eq:unconstrained_pb} with the choice of parameters: $\sigma = 1
+\in (0, 1]$, $\sigma_x = \sigma_y = 0 \in [0, \sigma)$,
     $\lambda_{xy} := \frac{\sqrt{(\sigma^2 - \sigma_x^2)(\sigma^2 -
@@
     1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
-           \lambda_{xy}]$. The convergence result then follows from
+    \lambda_{xy}]$. The convergence result follows immediately from
   \cite[Theorem 4.2]{he2013accelerating}.
+  \qed
 \end{proof}
+
 \subsection{Practical considerations}

### 2015-06-07 simple.py

@@ -982,7 +982,7 @@ if __name__ == "__main__":
                            "\\rangle$"), fontsize=50)
         ax.axhline(
             -1. / 18. if isinstance(game, Kuhn3112) else value,
-            linestyle="--", dashes=(20, 10), color="r",
+            linestyle="--", dashes=(30, 10), color="b",
             linewidth=4, **kwargs)
         plt.legend(loc="best", prop=dict(size=45), handlelength=1.5)
         ax.ticklabel_format(axis="y", style="sci", scilimits=(0., 0.))
@@ -994,8 +994,8 @@ if __name__ == "__main__":
         plt.figure(figsize=(13.5, 10))
         plt.grid("on")
         plt.loglog(cst / np.arange(1, len(dgaps) + 1), linestyle="--",
-                   dashes=(20, 10), label="$\\mathcal{O}(1/k)$", linewidth=4,
-                   color="r")
+                   dashes=(30, 10), label="$\\mathcal{O}(1/k)$", linewidth=4,
+                   color="b")
         plt.loglog(np.abs(dgaps), label="\\textbf{Algorithm 1}", linewidth=4)
         if cnt == 0:
             plt.ylabel("\\textbf{$||\\tilde{v}^{a}_k||$}", fontsize=50)

### 2015-06-07 nips2015.tex
llcn2e conf files
bug
glitches + fixups

@@
-\documentclass[envcountsame]{llncs}
+\documentclass[envcountsame]{llcns2e/llncs}
 \usepackage{url}
@@
 
-\title{\bf A simple and efficient algorithm for computing approximate
+\title{\hrule\hrule\bigskip\bigskip A simple and efficient algorithm for computing approximate
   Nash equilibria in two-person zero-sum games with imcomplete
-  information\smallskip\hrule\hrule}
+  information}
 \author{Elvis DOHMATOB\\\email{elvis.dohmatob@inria.fr}}
@@
 imcomplete information and perfect recall (like Texas Hold'em
-Poker). Our algorithm only performs basic iterations (i.e iterations
+Poker) based on the notion of enlarged subgradients.
+Our algorithm only performs basic iterations (i.e iterations
 involving no calls to external first-order oracles, etc.) and is
@@
 recall; sequence-form; approximate Nash equilibrium; primal-dual
-algoithm; convex-optimization
+algoithm; convex-optimization; enlarged subgradient
 
@@
 \begin{equation}
-  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\}
+  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\}.
 \label{eq:polyhedron}
@@
 \begin{equation}
-  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0
+  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0.
   \label{eq:dgap}
@@
 
-Moreover, at equilibria, \textit{strong duality} holds and the value of the game equals $p_0 = -q_0$, i.e the primal-dual gap $\mathcal{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at equilibria.
+Moreover, at equilibria, \textit{strong duality} holds and the value
+of the game equals $p_0 = -q_0$, i.e the primal-dual gap
+$\mathcal{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at
+equilibria.
 
@@
 \begin{equation}
-  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon
+  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon.
 \label{eq:approx_pb}
@@
   \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
-    Q_1}{\text{maximize}}\text{ }x^TAy
+    Q_1}{\text{maximize}}\text{ }x^TAy.
   \label{eq:gilpin}
@@
 \begin{itemize}
-\item avoid having to compute the projections $\proj_{Q_k}$, and
+\item avoid having to compute the projections $\proj_{Q_k}$,
+\item have control over how far we are from the set of equilibria,
 \item cope  with infinite primal-dual gaps.
@@
 \small
-\bibliographystyle{splncs03}
+\bibliographystyle{llcns2e/splncs03}
 \bibliography{bib}

### 2015-06-07 nips2015.tex
more

@@
 \label{sec:intro}
-\paragraph{\textbf{Context.}}
 A game-theoretic approach to playing games strategically optimally
@@
 
-\paragraph{\textbf{Notation and terminology.}}
+\subsection{Notation and terminology}
+\paragraph{\textbf{General notions.}}
 Let $m$ and $n$ be positive integers.
@@
 
+\paragraph{\textbf{Convex analysis.}}
 Given a subset $C$ of $\mathbb{R}^n$,
@@
 %%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
-Given $\tau > 0$, the function
+The \textit{subgradient} of $f$ is the set-valued function
+\begin{eqnarray}
+\partial f: X \mapsto 2^X, \hspace{.5em} x \mapsto \{h\in X |
+f(z)  \ge f(x) + \langle h, z - x\rangle \forall z \in X\}.
+\end{eqnarray}
+Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
+in case $f$ is differentiable at $x$. Given $\tau > 0$, the function
 \begin{eqnarray}
@@
 
-\paragraph{\textbf{Statement of the problem.}}
+\subsection{Statement of the problem}
 The sequence-form for two-person zero-sum games was introduced in
@@
 
-\paragraph{\textbf{Our contribution.}}
+\subsection{Our contribution}
 We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
-algorithm for computing Nash $(\rho, \epsilon$)-equilibria (in a sense
-to be made clear later) for
+algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\rho,
+  \epsilon$)-equilibria (in a sense to be made clear later) for
   sequential two-person zero-sum games with imcomplete information and
@@
 Given a scalar $\epsilon > 0$ and a function $f:X \subseteq \mathbb{R}^n
-\rightarrow [-\infty,+\infty]$, the $\epsilon$-subgradient of $f$ the
-set-valued function
+\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
+$\epsilon$-subgradient, for short) of $f$ the set-valued function
 \begin{eqnarray}
@@
 \in (0, 1]$, $\sigma_x = \sigma_y = 0 \in [0, \sigma)$,
-    $\lambda_{xy} := \frac{\sqrt{(\sigma^2 - \sigma_x^2)(\sigma^2 -
-        \sigma_y^2)}}{\sigma L_{xy}} = \sigma / \|K\| =
+    $\lambda_{xy} := \frac{1}{\sigma L_{xy}}\sqrt{(\sigma^2 -
+        \sigma_x^2)(\sigma^2 - \sigma_y^2)} = \sigma / \|K\| =
       1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,

### 2015-06-07 nips2015.tex
more

@@
 $\partial f(x) = \partial_{0^+}f(x)$ will coincide with
-subgradient of $f$ at $x$, namely $\{h\in X | f(z) \ge f(x) + \langle
-h, z - x\rangle \forall z \in X\}$.
+subgradient of $f$ at $x$.
 

### 2015-06-07 nips2015.tex
glitches + fixups

@@
 \begin{eqnarray}
-\partial f: X \mapsto 2^X, \hspace{.5em} x \mapsto \{h\in X |
-f(z)  \ge f(x) + \langle h, z - x\rangle \forall z \in X\}.
+\partial f: X \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
+\{h\in \mathbb{R}^n | f(z)  \ge f(x) + \langle h, z - x\rangle \forall
+z \in X\}.
 \end{eqnarray}
@@
 algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\rho,
-  \epsilon$)-equilibria (in a sense to be made clear later) for
+  \epsilon$)-equilibria (in a sense to be made clear later in
+  Definition \ref{thm:cool_notion}) for
   sequential two-person zero-sum games with imcomplete information and
@@
 \subsection{Relaxing the conditions for equilibrium}
-Let us first introduce the notion of $\epsilon$-subgradients. The idea
-is to replace the usual optimality characterization ``$x$ optimal iff
-$0 \in \partial f(x)$'' with ``$x$ approx optimal iff $0 \in
-\partial_\epsilon f(x)$''. In fact, letting $\epsilon \rightarrow 0^+$,
-$\partial f(x) = \partial_{0^+}f(x)$ will coincide with
-subgradient of $f$ at $x$.
+Let us first introduce the notion of $\epsilon$-subgradients.
 
@@
 \begin{eqnarray}
-\partial_\epsilon f: X \mapsto 2^X, \hspace{.5em} x \mapsto \{h\in X |
-f(z) + \epsilon \ge f(x) + \langle h, z - x\rangle \forall z \in X\}.
+\partial_\epsilon f: X \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x
+\mapsto \{h \in \mathbb{R}^n | f(z) + \epsilon \ge f(x) + \langle h, z
+- x\rangle \forall z \in X\}.
 \end{eqnarray}
 \end{definition}
+
+The idea is to replace the usual necessary condition ``$0 \in \partial
+f(x)$'' for the optimality of $x$ with ``$v \in \partial_\epsilon
+f(x)$, for some small perturbation vector $v$''. In fact, it is easy
+to see that, for each $x \in X$, $(\partial_\epsilon f(x))_{\epsilon >
+  0}$ is a decreasing sequence of sets which converges to $\partial
+f(x)$.
+
+Henceforth, the notion of approximate Nash equilibria will be
+understood in the following sense.
 
@@
 \end{eqnarray}
+\label{thm:cool_notion}
 \end{definition}

### 2015-06-07 nips2015.tex
glitches + fixups

@@
 
-\begin{definition}[$\epsilon$-subgradient]
+\begin{definition}[$\epsilon$-subgradient \cite{he2013accelerating}]
 Given a scalar $\epsilon > 0$ and a function $f:X \subseteq \mathbb{R}^n
@@
 
-\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
+\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}
+    \cite{he2013accelerating}]
 Given $\rho > 0$ and $\epsilon > 0$, a Nash

### 2015-06-07 nips2015.tex
giving credits

--- 2015-06-07 nips2015.tex
@@
 \subsection{Relaxing the conditions for equilibrium}
-Let us first introduce the notion of $\epsilon$-subgradients.
+Let us first introduce the notion of $\epsilon$-subgradients
+\cite{he2013accelerating}.
 
@@
 Henceforth, the notion of approximate Nash equilibria will be
-understood in the following sense.
+understood in the following sense, which was first introduced in
+\cite{he2013accelerating}.
 

### 2015-06-07 nips2015.tex
more ENHs on algo tex

@@
 
-The idea is to replace the usual necessary condition ``$0 \in \partial
-f(x)$'' for the optimality of $x$ with ``$v \in \partial_\epsilon
-f(x)$, for some small perturbation vector $v$''. In fact, it is easy
-to see that, for each $x \in X$, $(\partial_\epsilon f(x))_{\epsilon >
-  0}$ is a decreasing sequence of sets which converges to $\partial
-f(x)$.
+The idea behind $\epsilon$-subgradients is the following: given a
+function $f$ which we wish to minimize, replace the usual necessary
+condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
+weaker condition ``$\exists v \in \partial_\epsilon f(x)$, for some small
+perturbation vector $v$''. In fact, it is easy to see that, for each
+$x \in X$, $(\partial_\epsilon f(x))_{\epsilon > 0}$ is a decreasing
+sequence of sets which converges to $\partial f(x)$.
 
-Henceforth, the notion of approximate Nash equilibria will be
-understood in the following sense, which was first introduced in
-\cite{he2013accelerating}.
-
-%% Since won't typically be able to compute a feasible point in $Q_1 \in
-%% Q_2$ (due to the equality constraints $E_kz = e_k$), we will consider
-%% an approximate equilibrium concept which takes in to account the
-%% distance from the set of equilibria. Viz,
+This approximation concept for subgradients yields the following
+concept of approximate Nash equlibria (adapted from
+\cite{he2013accelerating}).
 
@@
 Given $\rho > 0$ and $\epsilon > 0$, a Nash
-$(\rho,\epsilon$)-equilibrium is a pair $(x^*, y^*)$ of realization
-plans such that there exists dual vectors $p^*$ and $q^*$ and a
-pertubation vector $v^*$ for which
+$(\rho,\epsilon$)-equilibrium for the GSP \eqref{eq:unconstrained_pb}
+is any quadruplet $(x^*, y^*, x^*, q^*)$ for which
+there exists a perturbation vector $v^*$ such that
 \begin{eqnarray}
@@
 \end{eqnarray}
+
+Such a vector $v^*$ is called a Nash $\epsilon$-residual at $(x^*,
+y^*, x^*, q^*)$.
 \label{thm:cool_notion}
@@
 \end{itemize}
-
-%\paragraph{\textbf{Plan of attack.}}
-\textbf{XXX TODO: Define the ergodic variables $\tilde{v}^a$ and
-  $\tilde{\epsilon}^a$, ...}
 
@@
 the GSP \eqref{eq:unconstrained_pb}.
-\State  $\lambda \leftarrow 1/\|K\|$,
-%% $y^{(0)} \leftarrow 0_{n_2}$,
-%% $p^{(0)} \leftarrow 0_{l_1}$, $x^{(0)} \leftarrow 0_{n_1}$, $q^{(0)}
-%% \leftarrow 0_{l_2}$,
-$k \leftarrow 0$
-\While{$\|\tilde{\epsilon}^{a}_k\| \ge \rho$ or $\|\tilde{v}^{a}_k\| \ge \epsilon$}
+\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$,
+$\tilde{v}_a^{(0)} \leftarrow 0$, $k \leftarrow 0$
+\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \rho$ or
+  $\|\tilde{v}_{a}^{(k)}\| \ge \epsilon$}
 \State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
@@
 (A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
-\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1(x^{(k+1)}-x^{(k)})$
+\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda
+E_1(x^{(k+1)}-x^{(k)})$
+\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k} +
+\frac{1}{\lambda}(y^{(k+1)}-y^{(k)},p^{(k+1)}-p^{(k)},x^{(k+1)}-x^{(k)},q^{(k+1)}-q^{(k)})$
+\State $\tilde{v}_a^{(k+1)} \leftarrow \frac{1}{k + 1}v_a^{(k+1)}$
 \State $k \leftarrow k + 1$
@@
 set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
-Then given any $\epsilon > 0$ and $\rho > 0$, we have the ergodic
-error bounds
+Then given any $\epsilon > 0$ and $\rho > 0$, there exists and index
+$k_0 \le 2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ such that the following
+error bounds hold:
 \begin{eqnarray}
-\|\tilde{\epsilon}^{a}_k\| \le \rho\text{ and }\|\tilde{v}^{a}_k\| \le
-\epsilon, \forall k \ge 2d_0\|K\|max(5d_0/\rho, 1/\epsilon).
+\|\tilde{\epsilon}^{a}_{k_0}\| \le \rho\text{ and }\|\tilde{v}^{a}_{k_0}\| \le
+\epsilon.
 \end{eqnarray}

### 2015-06-07 nips2015.tex
glitches + fixups
refactor algorithm listing in tex

@@
 The above definition is a generalization of the notion of Nash
-equilibria in the sense that
+equilibria since:
 \begin{itemize}
@@
 
-\subsection{The algorithm proper and its convergence rate}
+\subsection{Algorithm and convergence rate}
 Consider the following algorithm for solving the GSP
@@
 \Ensure A Nash $(\rho, \epsilon)$-equilibrium
-$(\tilde{y},\tilde{p},\tilde{x},\tilde{q}) \in S_1 \times S_2$ for
+$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
 the GSP \eqref{eq:unconstrained_pb}.
-\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$,
-$\tilde{v}_a^{(0)} \leftarrow 0$, $k \leftarrow 0$
-\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \rho$ or
-  $\|\tilde{v}_{a}^{(k)}\| \ge \epsilon$}
+\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k \leftarrow 0$
+\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \epsilon$ or
+  $\|{v}_{a}^{(k)}\|/k \ge \rho$}
 \State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
 E_2^Tq^{(k)}))_+$
-\State  \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
+\State  $p^{(k+1)} \leftarrow p^{(k)} -
 \lambda(e_1-E_1x^{(k)})$
@@
 E_1^Tp^{(k+1)}))_+$
-\State  \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} +
-\lambda(E_2y^{(k+1)}-e_2)$
-\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda
-(A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
-\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda
-E_1(x^{(k+1)}-x^{(k)})$
-\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k} +
-\frac{1}{\lambda}(y^{(k+1)}-y^{(k)},p^{(k+1)}-p^{(k)},x^{(k+1)}-x^{(k)},q^{(k+1)}-q^{(k)})$
-\State $\tilde{v}_a^{(k+1)} \leftarrow \frac{1}{k + 1}v_a^{(k+1)}$
+\State $\Delta x^{(k+1)} \leftarrow x^{(k+1)}-x^{(k)}$
+\State $\Delta q^{(k+1)} \leftarrow q^{(k+1)}-q^{(k)}$
+\State  $q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
+\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
++ E_2^T\Delta q^{(k+1)})$
+\State $\Delta y^{(k+1)} \leftarrow y^{(k+1)}-y^{(k)}$
+\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$
+\State $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
+\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} + \frac{1}{\lambda}(\Delta
+y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
 \State $k \leftarrow k + 1$
@@
 \begin{eqnarray}
-\|\tilde{\epsilon}^{a}_{k_0}\| \le \rho\text{ and }\|\tilde{v}^{a}_{k_0}\| \le
-\epsilon.
+\|\tilde{v}_a^{k_0}\| \le \rho \text{ and }
+\|\tilde{\epsilon}_a^{k_0}\| \le \epsilon
 \end{eqnarray}
 
+where $\tilde{v}_a^{(k_0)} := v_a^{(k_0)}/k_0$.
 Thus Algorithm \ref{Tab:algo} outputs an $(\rho,\epsilon)$-Nash
-Equilibrium for the GSP \eqref{eq:unconstrained_pb}
+equilibrium for the GSP \eqref{eq:unconstrained_pb}
 in at most $2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ iterations.
@@
 
-$E_1 \in \mathbb{E}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
+$E_1 \in \mathbb{R}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
 E_1(1,2) = E_1(2,3) = E_1(2,4) = \textbf{1}$,
@@
 
-$E_2 \in \mathbb{E}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
+$E_2 \in \mathbb{R}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
 = E_2(2,3) = E_2(2,4) = \textbf{1}$, $E_2(1,0) = E_2(2,0) =
@@
 
-$A \in \mathbb{E}^{5 \times 5}$ with $A(2,0) =
+$A \in \mathbb{R}^{5 \times 5}$ with $A(2,0) =
 A(4,0) = \textbf{-0.5}$, $A(1,3) = \textbf{1}$, $A(3,1) =
@@
 
-$E_1 \in \mathbb{E}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
+$E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
 E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
@@
 
- $E_2 \in \mathbb{E}^{7 \times 13}$
+ $E_2 \in \mathbb{R}^{7 \times 13}$
 $E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
@@
 
- $A \in \mathbb{E}^{13 \times
+ $A \in \mathbb{R}^{13 \times
   13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =

### 2015-06-22 nips2015.tex
fixups + more

@@
 \usepackage{url}
+%\usepackage{times}
 \usepackage{amsmath,amsfonts}
@@
 \maketitle
-
-\begin{abstract}
-We present a simple primal-dual algorithm for computing approximate
-Nash equilibria in two-person zero-sum sequential games with
-imcomplete information and perfect recall (like Texas Hold'em
-Poker) based on the notion of enlarged subgradients.
-Our algorithm only performs basic iterations (i.e iterations
-involving no calls to external first-order oracles, etc.) and is
-applicable to a broad class of two-person zero-sum games including
-simultaneous games and sequential games with imcomplete information
-and perfect recall. The number of iterations need to produce a Nash
-equilibrium with a given precision is inversely proportion to the
-precision. The applicability to the latter kind of games is thanks to
-the sequence-form representation \cite{koller1992complexity}. As
-proof-of-concept, we apply our algorithm to solve Kuhn 3-card Poker.
+\begin{abstract}We present a simple primal-dual algorithm for
+  computing approximate Nash equilibria in two-person zero-sum
+  sequential games with  imcomplete information and perfect recall
+  (like Texas Hold'em Poker) based on the notion of enlarged
+  subgradients. Our algorithm only performs basic iterations (i.e
+  iterations involving no calls to external first-order oracles, etc.)
+  and is applicable to a broad class of two-person zero-sum games
+  including simultaneous games and sequential games with imcomplete
+  information and perfect recall. The applicability to the latter kind
+  of games is thanks to the sequence-form representation
+  \cite{koller1992complexity} which allows us to encode any such game
+  as a matrix game with polyhedral strategy profiles, the size of the
+  representation being linear in ... The number of iterations needed
+  to produce a Nash equilibrium with a given precision is inversely
+  proportional to the desired precision. As proof-of-concept, we apply our
+  algorithm to solve Kuhn 3-card Poker.
 \end{abstract}
@@
 nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
-\mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
-%% by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
+\mathbb{R}^n$, $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
+by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
 $(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
-maximum of $z$ with $0$.
-%% For example, $((-2, \pi))_+ = (max(-2, 0),
-%% max(\pi, 0)) = (0, \pi)$.
+maximum of $z$ with $0$. For example, $((-2, \pi))_+ = (max(-2, 0),
+max(\pi, 0)) = (0, \pi)$.
 The operator $(.)_+$ is the well-known
 (multi-dimensional) \textit{ramp} function.
-$\mathbb{R}^{m \times n}$ denotes the space of all $m$-by-$n$ real
-matrices, $I_m$ denotes the $m$-by-$m$ identity matrix, and $0_{m,n}$
-denotes the $m$-by-$n$ matrix of zeros.
 Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
@@
 \begin{eqnarray}
-  i_C(x) = 0, \text{ if } x \in C;\hspace{.3em} i_c(x) = \infty\text{
+  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
     otherwise.}
 \end{eqnarray}
-
 Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a convex
@@
 \begin{eqnarray}
-\partial f: X \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
-\{h\in \mathbb{R}^n | f(z)  \ge f(x) + \langle h, z - x\rangle \forall
-z \in X\}.
+\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
+\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
+z \in \mathbb{R}^n\}.
 \end{eqnarray}
 Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
-in case $f$ is differentiable at $x$. Given $\tau > 0$, the function
+in case $f$ is differentiable at $x$. If $f$ is convex, its
+\textit{proximal operator} the function defined by
 \begin{eqnarray}
-  \prox_{\tau f}: \mathbb{R}^n \rightarrow \mathbb{R}^n,\hspace{.5em}x
+  \prox_f: \mathbb{R}^n \rightarrow \mathbb{R}^n,\hspace{.5em}x
   \mapsto \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
-  - x\|^2 + \tau f(z),
+  - x\|^2 + f(z),
+\end{eqnarray}
+For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
+$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
+operators generalize orthongal projectors. One also has the useful
+characterization
+\begin{eqnarray}
+  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
 \end{eqnarray}
 
-is called the \textit{proximal operator} of $f$ at rank $\tau$.
 The interested reader should refer to
-\cite{rockafellar1997convex,combettes2011proximal} for a more
-elaborate exposition of convex-analytical concepts and their use in
-optimization.
+\cite{combettes2011proximal} for
+a more elaborate exposition of proximal operators and their
+use in modern convex-optimization.
 
@@
 \item avoid having to compute the projections $\proj_{Q_k}$,
-\item have control over how far we are from the set of equilibria,
-\item cope  with infinite primal-dual gaps.
+\item have control over how far we are from the set of equilibria and
+  avoid infinite (and thus non-informative) primal-dual gaps
 \end{itemize}
@@
         (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
-          i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tq.
+          i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tq
     \end{aligned}
@@
 
-Also, define two bilinear forms $\Psi_1$, $\Psi_2: \mathbb{R}^{n_2}
+Also define two bilinear forms $\Psi_1$, $\Psi_2: \mathbb{R}^{n_2}
 \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
@@
           A & -E_1^T \\
-          E_2 & 0_{l_2, l_1}
+          E_2 & 0
         \end{array}
@@
 \underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) < +\infty$.
-Thus, one can compute the primal-dual gap between primal LCP
-\eqref{eq:primal_pb} and dual LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
+Thus, one can compute the primal-dual gap between the primal LCP
+\eqref{eq:primal_pb} and dual the LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
 \begin{eqnarray*}
@@
 \label{sec:algo}
-In this section we derive the algorithm which is the main object of
-this manuscript.
-
 \subsection{Relaxing the conditions for equilibrium}
@@
 \cite{he2013accelerating}.
-
 \begin{definition}[$\epsilon$-subgradient]
-Given a scalar $\epsilon > 0$ and a function $f:X \subseteq \mathbb{R}^n
+Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
 \rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
-$\epsilon$-subgradient, for short) of $f$ the set-valued function
+$\epsilon$-subgradient, for short) of $f$ is the set-valued function
 \begin{eqnarray}
-\partial_\epsilon f: X \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x
-\mapsto \{h \in \mathbb{R}^n | f(z) + \epsilon \ge f(x) + \langle h, z
-- x\rangle \forall z \in X\}.
+\partial_\epsilon f: \mathbb{R}^n \rightarrow
+2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
+\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
+\mathbb{R}^n\}.
 \end{eqnarray}
@@
 
-The idea behind $\epsilon$-subgradients is the following: given a
-function $f$ which we wish to minimize, replace the usual necessary
+The idea behind $\epsilon$-subgradients is the following. Say we wish
+to minimize the function $f$. Replace the usual necessary
 condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
-weaker condition ``$\exists v \in \partial_\epsilon f(x)$, for some small
-perturbation vector $v$''. In fact, it is easy to see that, for each
-$x \in X$, $(\partial_\epsilon f(x))_{\epsilon > 0}$ is a decreasing
-sequence of sets which converges to $\partial f(x)$.
-
+weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
+small vector $v$''. In fact, it is easy to see that, for each
+point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
+  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
 This approximation concept for subgradients yields the following
@@
 \subsection{Algorithm and convergence rate}
-Consider the following algorithm for solving the GSP
-\eqref{eq:unconstrained_pb}
+We now derive the algorithm derive the algorithm which is the main object of
+this manuscript.
+
 \begin{algorithm}
+\label{Tab:algo}
 \caption{Primal-dual algorithm for computing approximate Nash
@@
   and perfect recall}
-\label{Tab:algo}
 \begin{algorithmic}[1]
@@
 the GSP \eqref{eq:unconstrained_pb}.
-\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k \leftarrow 0$
+\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
+\leftarrow 0$
 \While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \epsilon$ or
@@
 \State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
-E_1^Tp^{(k+1)}))_+$
-\State $\Delta x^{(k+1)} \leftarrow x^{(k+1)}-x^{(k)}$
-\State $\Delta q^{(k+1)} \leftarrow q^{(k+1)}-q^{(k)}$
-\State  $q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
+E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
+x^{(k+1)}-x^{(k)}$
+\State $\Delta q^{(k+1)} \leftarrow
+q^{(k+1)}-q^{(k)}$, \hspace{.5em}$q^{(k+1)}
+\leftarrow q^{(k)} + \Delta q^{(k+1)}$
 \State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
-+ E_2^T\Delta q^{(k+1)})$
-\State $\Delta y^{(k+1)} \leftarrow y^{(k+1)}-y^{(k)}$
-\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$
-\State $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
-\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} + \frac{1}{\lambda}(\Delta
++ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
+y^{(k+1)}-y^{(k)}$
+\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
+\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
+\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
+\frac{1}{\lambda}(\Delta
 y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
@@
 set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
-Then given any $\epsilon > 0$ and $\rho > 0$, there exists and index
+Then given any $\epsilon > 0$ and $\rho > 0$, there exists an index
 $k_0 \le 2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ such that the following
@@
 one easily computes the proximal operators $g_1$ and $g_2$ as
-\begin{eqnarray*}
+\begin{eqnarray}
   \prox_{\lambda g_1}(y, p) \equiv ((y)_+, p - \lambda
@@
   \lambda e_2).
-  \end{eqnarray*}
+  \end{eqnarray}
 

### 2015-06-22 primal_dual.py

@@ -36,7 +36,7 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
     zeros = np.zeros((l2, l1))
     if "norm_K" in init: norm_K = init["norm_K"]
     else:
-        # XXX use power iteration to compute ||K||
+        # XXX use power iteration to compute ||K||^2
         K = np.vstack((np.hstack((A, -E1.T)), np.hstack((E2, zeros))))
         norm_K = linalg.norm(K, 2)
     sigma = init.get("sigma", 1.)
@@ -58,18 +58,27 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
         old_y = y.copy()
         old_p = p.copy()
         old_x = x.copy()
-        old_q = q.copy()
 
-        # update iterates
+        # y update
         y -= lambd * (A.T.dot(x) + E2.T.dot(q))
         y = proj_C2(y)
+
+        # p update
         p -= lambd * (e1 - E1.dot(x))
+
+        # x updata
         x += lambd * (A.dot(y) - E1.T.dot(p))
         x = proj_C1(x)
-        q += lambd * (E2.dot(y) - e2)
         delta_x = x - old_x
-        delta_q = q - old_q
+
+        # q update
+        delta_q = lambd * (E2.dot(y) - e2)
+        q += delta_q
+
+        # u update (again)
         y -= lambd * (A.T.dot(delta_x) + E2.T.dot(delta_q))
+
+        # p update (again)
         p += lambd * E1.dot(delta_x)
 
         # compute game value and primal-dual gap at current iterates

### 2015-06-22 simple.py

@@ -9,12 +9,6 @@ import matplotlib.pyplot as plt
 from sklearn.utils import check_random_state
 from primal_dual import primal_dual_ne, primal_dual_sg_ne
 
-# matplotlib confs
-matplotlib.rcParams['text.latex.preamble'] = ['\\boldmath']
-matplotlib.rc('font', family='serif', serif='cm10')
-matplotlib.rc('text', usetex=True)
-plt.rc('font', size=50)  # make the power in sci notation bigger
-
 
 def _matrix2texstr(A, name="A", exclude=None):
     if exclude is None: exclude = []
@@ -932,6 +926,12 @@ def test_nash_player():
 
 
 if __name__ == "__main__":
+    # matplotlib confs
+    matplotlib.rcParams['text.latex.preamble'] = ['\\boldmath']
+    matplotlib.rc('font', family='serif', serif='cm10')
+    matplotlib.rc('text', usetex=True)
+    plt.rc('font', size=50)  # make the power in sci notation bigger
+
     rng = check_random_state(42)
     max_iter = 10000
     game_clses = ["simplex", SimplifiedPoker, Kuhn3112]

### 2015-06-24 nips2015.tex
affiliation

@@
-\documentclass[envcountsame]{llcns2e/llncs}
+\documentclass{article} % For LaTeX2e
+\usepackage{nips14submit_e}
+%\documentclass[envcountsame]{llcns2e/llncs}
 \usepackage{url}
-%\usepackage{times}
-\usepackage{amsmath,amsfonts}
+\usepackage{times}
+\usepackage{amsmath,amsfonts, amsthm}
 \usepackage{bbm}
@@
 
+\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
+
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{remark}{Remark}
 \newtheorem{fact}{Fact}
+
 \DeclareMathOperator{\dom}{dom}
@@
 
-\title{\hrule\hrule\bigskip\bigskip A simple and efficient algorithm for computing approximate
+\title{
+  %\hrule\hrule\bigskip\bigskip
+  A simple and efficient algorithm for computing approximate
   Nash equilibria in two-person zero-sum games with imcomplete
   information}
-\author{Elvis DOHMATOB\\\email{elvis.dohmatob@inria.fr}}
-\institute{
-Parietal team, Inria Saclay Ile-de-France, Saclay, France
+\author{Elvis DOHMATOB
+\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
+\\\texttt{firstname.lastname@inria.fr}
 }
@@
 \paragraph{\textbf{General notions.}}
+Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
+of all subsets of $X$, or equivalently the set of all binary
+functions on $X$.
+
 Let $m$ and $n$ be positive integers.
@@
 (multi-dimensional) \textit{ramp} function.
+
 Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
@@
 := 0$.
-\qed
 
@@
   \cite[Theorem 4.2]{he2013accelerating}.
-  \qed
 \end{proof}
@@
  evolution of the dual gap and the expected value of the game across
- iterations is shown in Figure \ref{Tab:dgap_curve}.
+ iterations are shown in Figure \ref{Tab:dgap_curve}.
 

### 2015-06-24 sequential_form.py

@@ -1,71 +1,480 @@
-"""
-Sequential form of games (in the sense of Benhard Von Stengel et al.).
-"""
+def _matrix2texstr(A, name="A", exclude=None):
+    if exclude is None: exclude = []
+    vals = dict((val, []) for val in np.unique(A))
+    for val in exclude: del vals[val]
+    for v, u in vals.items():
+        for i in range(A.shape[0]):
+            for j in range(A.shape[1]):
+                if A[i, j] == v: u.append((i, j))
+    out = []
+    for v, u in vals.items():
+        out.append("$" + " = ".join(["%s(%i,%i)" % (name, i, j)
+                                     for (i, j) in u] + ["\\textbf{%g}$" % v]))
+    return ", ".join(out)
 
-# Author: DOHMATOB Elvis <gmdopp@gmail.com>
-
-import numpy as np
 
 
-class Player(object):
-    def __init__(self, seqs, info):
-        self.seqs = seqs
-        self.info = info
-        self.E = None
-        self.e = None
+class Game(object):
+    """Sequence-form representaion of two-person zero-sum games with perfect
+    recall and imcomplete information (like Poker, love, war, diplomacy, etc.)
 
-    def compute_constraints(self):
+    Terminology
+    -----------
+
+    Game Tree (normal-form definition)
+    ==================================
+    There are 3 players, namely: the "chance" player (player 0, aka nature),
+    Alice (player 0), and Bob (player 2), and the "mute" (player 3) all four
+    treated symmetrically. Each player p has a set of moves (aka, choices,
+    actions, etc.) denoted by an alphabet A_p. For clarity of the discussion,
+    we assume that the set of moves of any two distinct players are disjoint.
+    Furthermore, player 3 (mute) has no moves, i.e A_3 = {}, hence her name.
+
+    The game tree T (from Alice's perspective) is defined as follows.
+    T has a set V(T) of nodes (aka vertices) and a set E(T) of edges.
+    Each node v belongs to a single player, p(v), called "the player to act
+    at v"; p(v) := 3 if v is a leaf node. At node v, the player p(v) has a set
+    C(v) \subset A_p of possible moves. For each player p \in [0, 1, 2],
+    the set of all nodes at which p acts is called the nodes of p,
+    denoted V_p(T). Thus v(0), v(1), and v(2) form a partition of V(T).
+
+    There are two kinds of nodes: the leafs L(T), at which the game must
[…]

### 2015-06-24 simple.py

@@ -2,491 +2,12 @@
 
 import re
 from nose.tools import assert_equal, assert_true
-import networkx as nx
 import numpy as np
 import matplotlib
 import matplotlib.pyplot as plt
 from sklearn.utils import check_random_state
+from sequence_form import Game
 from primal_dual import primal_dual_ne, primal_dual_sg_ne
-
-
-def _matrix2texstr(A, name="A", exclude=None):
-    if exclude is None: exclude = []
-    vals = dict((val, []) for val in np.unique(A))
-    for val in exclude: del vals[val]
-    for v, u in vals.items():
-        for i in range(A.shape[0]):
-            for j in range(A.shape[1]):
-                if A[i, j] == v: u.append((i, j))
-    out = []
-    for v, u in vals.items():
-        out.append("$" + " = ".join(["%s(%i,%i)" % (name, i, j)
-                                     for (i, j) in u] + ["\\textbf{%g}$" % v]))
-    return ", ".join(out)
-
-
-class Game(object):
-    """Sequence-form representaion of two-person zero-sum games with perfect
-    recall and imcomplete information (like Poker, love, war, diplomacy, etc.)
-
-    Terminology
-    -----------
-
-    Game Tree (normal-form definition)
-    ==================================
-    There are 3 players, namely: the "chance" player (player 0, aka nature),
-    Alice (player 0), and Bob (player 2), and the "mute" (player 3) all four
-    treated symmetrically. Each player p has a set of moves (aka, choices,
-    actions, etc.) denoted by an alphabet A_p. For clarity of the discussion,
-    we assume that the set of moves of any two distinct players are disjoint.
-    Furthermore, player 3 (mute) has no moves, i.e A_3 = {}, hence her name.
-
-    The game tree T (from Alice's perspective) is defined as follows.
-    T has a set V(T) of nodes (aka vertices) and a set E(T) of edges.
-    Each node v belongs to a single player, p(v), called "the player to act
-    at v"; p(v) := 3 if v is a leaf node. At node v, the player p(v) has a set
-    C(v) \subset A_p of possible moves. For each player p \in [0, 1, 2],
-    the set of all nodes at which p acts is called the nodes of p,
-    denoted V_p(T). Thus v(0), v(1), and v(2) form a partition of V(T).
-
-    There are two kinds of nodes: the leafs L(T), at which the game must
-    end and decision nodes D(T), at which the player to act must make a move.
[…]

### 2015-06-24 nips2015.tex
refactor .tex

@@
   A simple and efficient algorithm for computing approximate
-  Nash equilibria in two-person zero-sum games with imcomplete
+  Nash equilibria in two-person zero-sum sequential games with imcomplete
   information}
@@
 
+Let us introduce the notion of $\epsilon$-subgradients
+\cite{he2013accelerating}.
+
+\begin{definition}[$\epsilon$-subgradient]
+Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
+\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
+$\epsilon$-subgradient, for short) of $f$ is the set-valued function
+\begin{eqnarray}
+\partial_\epsilon f: \mathbb{R}^n \rightarrow
+2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
+\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
+\mathbb{R}^n\}.
+\end{eqnarray}
+\end{definition}
+
+The idea behind $\epsilon$-subgradients is the following. Say we wish
+to minimize the function $f$. Replace the usual necessary
+condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
+weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
+small vector $v$''. In fact, it is easy to see that, for each
+point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
+  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
+This approximation concept for subgradients yields the following
+concept of approximate Nash equlibria (adapted from
+\cite{he2013accelerating}).
+
+\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
+Given $\rho > 0$ and $\epsilon > 0$, a Nash
+$(\rho,\epsilon$)-equilibrium for the GSP \eqref{eq:unconstrained_pb}
+is any quadruplet $(x^*, y^*, x^*, q^*)$ for which
+there exists a perturbation vector $v^*$ such that
+\begin{eqnarray}
+\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
+\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
+  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
+\end{eqnarray}
+
+Such a vector $v^*$ is called a Nash $\epsilon$-residual at $(x^*,
+y^*, x^*, q^*)$.
+\label{thm:cool_notion}
+\end{definition}
+
+The above definition is a generalization of the notion of Nash
+equilibria since:
+\begin{itemize}
+\item Exact Nash equilibria correspond to Nash $(0^+,0^+)$-equilibria.
+\item Nash $\epsilon$-equilibria (in the sense of Definition
+  \ref{thm:approx_nash}) correspond to Nash $(0^+,\epsilon)$-equilibria.
+\end{itemize}
+
 \subsection{Our contribution}
@@
 algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\rho,
-  \epsilon$)-equilibria (in a sense to be made clear later in
-  Definition \ref{thm:cool_notion}) for
-  sequential two-person zero-sum games with imcomplete information and
-  perfect recall.
+  \epsilon$)-equilibria for sequential two-person zero-sum games with
+  imcomplete information and perfect recall.
 
@@
 \label{sec:algo}
-\subsection{Relaxing the conditions for equilibrium}
-Let us first introduce the notion of $\epsilon$-subgradients
-\cite{he2013accelerating}.
-\begin{definition}[$\epsilon$-subgradient]
-Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
-\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
-$\epsilon$-subgradient, for short) of $f$ is the set-valued function
-\begin{eqnarray}
-\partial_\epsilon f: \mathbb{R}^n \rightarrow
-2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
-\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
-\mathbb{R}^n\}.
-\end{eqnarray}
-\end{definition}
-
-The idea behind $\epsilon$-subgradients is the following. Say we wish
-to minimize the function $f$. Replace the usual necessary
-condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
-weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
-small vector $v$''. In fact, it is easy to see that, for each
-point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
-  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
-This approximation concept for subgradients yields the following
-concept of approximate Nash equlibria (adapted from
-\cite{he2013accelerating}).
-
-\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
-Given $\rho > 0$ and $\epsilon > 0$, a Nash
-$(\rho,\epsilon$)-equilibrium for the GSP \eqref{eq:unconstrained_pb}
-is any quadruplet $(x^*, y^*, x^*, q^*)$ for which
-there exists a perturbation vector $v^*$ such that
-\begin{eqnarray}
-\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
-\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
-  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
-\end{eqnarray}
-
-Such a vector $v^*$ is called a Nash $\epsilon$-residual at $(x^*,
-y^*, x^*, q^*)$.
-\label{thm:cool_notion}
-\end{definition}
-
-The above definition is a generalization of the notion of Nash
-equilibria since:
-\begin{itemize}
-\item Exact Nash equilibria correspond to Nash $(0^+,0^+)$-equilibria.
-\item Nash $\epsilon$-equilibria (in the sense of Definition
-  \ref{thm:approx_nash}) correspond to Nash $(0^+,\epsilon)$-equilibria.
-\end{itemize}
-
 \subsection{Algorithm and convergence rate}

### 2015-06-25 nips2015.tex
refactor .tex
fixup algo label
fixups + more

@@
 \begin{algorithm}
-\label{Tab:algo}
 \caption{Primal-dual algorithm for computing approximate Nash
@@
   and perfect recall}
+\label{Tab:algo}
 \begin{algorithmic}[1]
@@
 \begin{proof}
-Note that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$ clearly satisfies
-assumptions B.1, B.2, B.3, B.5, and B.6 of \cite{he2013accelerating}
-with $L_{xx} = L_{yy} = 0$ and $L_{xy} = L_{yx} = \|K\|$. Now,
-one easily computes the proximal operators $g_1$ and $g_2$ as
-\begin{eqnarray}
+It is clear to see that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$
+satisfies assumptions B.1, B.2, B.3, B.5, and B.6 of
+\cite{he2013accelerating} with $L_{xx} = L_{yy} = 0$ and $L_{xy} =
+L_{yx} = \|K\|$. Now, one easily computes the proximal operators $g_1$
+and $g_2$ as
+\begin{eqnarray*}
   \prox_{\lambda g_1}(y, p) \equiv ((y)_+, p - \lambda
@@
   \lambda e_2).
-  \end{eqnarray}
+  \end{eqnarray*}
 
@@
 $E_1 \in \mathbb{R}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
-E_1(1,2) = E_1(2,3) = E_1(2,4) = \textbf{1}$,
-$E_1(1,0) = E_1(2,0) = \textbf{-1}$; \\
+E_1(1,2) = E_1(2,3) = E_1(2,4) = {1}$,
+$E_1(1,0) = E_1(2,0) = {-1}$; \\
 
 $E_2 \in \mathbb{R}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
-= E_2(2,3) = E_2(2,4) = \textbf{1}$, $E_2(1,0) = E_2(2,0) =
-\textbf{-1}$; and \\
+= E_2(2,3) = E_2(2,4) = {1}$, $E_2(1,0) = E_2(2,0) =
+{-1}$; and \\
 
 $A \in \mathbb{R}^{5 \times 5}$ with $A(2,0) =
-A(4,0) = \textbf{-0.5}$, $A(1,3) = \textbf{1}$, $A(3,1) =
-\textbf{-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = \textbf{0.25}$.
+A(4,0) = {-0.5}$, $A(1,3) = {1}$, $A(3,1) =
+{-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = {0.25}$.
 
-\paragraph{\textbf{Kuhn 3-card Poker.}}
+\paragraph{{Kuhn 3-card Poker.}}
 The game has $n_1 = n_2 = 13$ and $l_1 = l_2 = 7$, and its
@@
 E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
-E_1(6,11) = \textbf{1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
-E_1(5,5) = E_1(6,9) = \textbf{-1}$; \\
+E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
+E_1(5,5) = E_1(6,9) = {-1}$; \\
 
- $E_2 \in \mathbb{R}^{7 \times 13}$
+ $E_2 \in \mathbb{R}^{7 \times 13}$ with
 $E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
 E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
-E_2(6,4) = \textbf{1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
-E_2(5,0) = E_2(6,0) = \textbf{-1}$; and \\
+E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
+E_2(5,0) = E_2(6,0) = {-1}$; and \\
 
@@
   13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
-\textbf{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
-A(6,4) = A(6,12) = A(10,4) = A(10,8) = \textbf{-0.166667}$, $A(7,4) =
-A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = \textbf{0.333333}$,
+{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
+A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
+A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
 $A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
-A(12,1) = A(12,5) = \textbf{0.166667}$.\\
+A(12,1) = A(12,5) = {0.166667}$.\\
 
@@
 \begin{eqnarray*}
-  {x^*}^TAy^* = \textbf{-0.05555},
+  {x^*}^TAy^* = {-0.05555},
 \end{eqnarray*}
@@
 Nash $(\rho,\epsilon$-equilibrium of the game.
-
 Equilibrium problems are saddle-point convex-concave problems, and as

### 2015-06-25 primal_dual.py

@@ -94,8 +94,8 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
 
         # invoke callback
         if callback: callback(locals())
-        print "Iter %03i/%03i: value=%g, gap=%.2e" % (k + 1, max_iter,
-                                                      value, gap)
+        print ("Iter %03i/%03i: game value = %g, primal-dual gap (perturbed) ="
+               " %.2e") % (k + 1, max_iter, value, gap)
 
         # check convergence
         if gap < tol:

### 2015-06-25 nips2015.tex
fixups + more

@@
 \begin{itemize}
-\item avoid having to compute the projections $\proj_{Q_k}$,
-\item have control over how far we are from the set of equilibria and
+\item[--] avoid having to compute the projections $\proj_{Q_k}$,
+\item[--] have control over how far we are from the set of equilibria and
   avoid infinite (and thus non-informative) primal-dual gaps

### 2015-06-25 nips2015.tex
fixups + more

@@
 \item[--] have control over how far we are from the set of equilibria and
-  avoid infinite (and thus non-informative) primal-dual gaps
+  avoid infinite (and thus non-informative) primal-dual gaps.
 \end{itemize}
@@
 in terms of basic operations (matvec products, clipping, etc.), to a
-Nash $(\rho,\epsilon$-equilibrium of the game.
+Nash $(\rho,\epsilon)$-equilibrium of the game.
+
 Equilibrium problems are saddle-point convex-concave problems, and as
-such a natural choice for an algorithm would be in the family of
-primal-dual algorithms. The author believes such primal-dual schemes
-will receive more attention in the algorithmic game theory community
-in future.
+such a natural choice for algorithms for solving them would be in the
+family of primal-dual algorithms. The author believes such primal-dual
+schemes will receive more attention in the algorithmic game theory
+community in future.
 

### 2015-07-03 nips2015.tex
more crisis + fixes: we're ok

@@
 $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
-0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
-components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
-$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
-notation ``$z \ge 0$'' means that all the components of $z$ are
+0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  Given two
+vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
+$\langle z, w\rangle$ The components of $z \in \mathbb{R}^n$ will be
+denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
+not $1$). The notation ``$z \ge 0$'' means that all the components of $z$ are
 nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
 \mathbb{R}^n$, $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
-by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
+by $\|z\| := \sqrt{\langle z, z\rangle} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
 $(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
@@
 \end{eqnarray}
-Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a convex
-  function.
-The \textit{effective domain} of $f$, denoted $\dom(f)$ is defined as
+At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
+etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
+  convex function. The \textit{effective domain} of $f$, denoted
+  $\dom(f)$ is defined as
 \begin{eqnarray}
@@
   \begin{aligned}
-     \text{minimize }e_1^Tp, \hspace{.5em}\text{ subject to }(y,p) \in
+     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{ subject to }(y,p) \in
      \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}, -Ay +
@@
   \begin{aligned}
-    \text{maximize}-e_2^Tq,\hspace{.5em}\text{subject to }(y,q) \in
+    \text{maximize}-\langle e_2, q\rangle,\hspace{.5em}\text{subject to }(y,q) \in
     \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, A^Tx + E_2^Tq \geq 0,
@@
 \end{equation}
-Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and
+Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle = q_0$ by definition of $e_1$ and
 $e_2$. At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
@@
 \hspace{.25em} -Ay + E_1^Tp \ge 0, \hspace{.5em}A^Tx + E_2^Tq \ge
-0, \hspace{.25em} x^T(-Ay + E_1^Tp) = 0, \hspace{.25em} y^T(A^Tx +
-E_2^Tq) = 0.
+0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0, \hspace{.25em}
+\langle y, A^Tx  + E_2^Tq\rangle = 0.
 \label{eq:feasibility}
@@
 to solve the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the
-following equivalent saddle-point form
+following equivalent saddle-point form\footnote{Note that in
+  \cite{hoda2010smoothing}, the roles of $x$ and $y$ are swapped.}
 
@@
   \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
-    Q_1}{\text{maximize}}\text{ }x^TAy.
+    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle
   \label{eq:gilpin}
@@
 \delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in
-terms of the number of calls made to a first-order oracle (for
-example, Nesterov's optimal gradient \cite{nesterov1983}). Here
-$\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a certain
-\textit{condition number} for the game. It should be noted however that
+terms of the number of calls made to a first-order oracle. Here
+$\delta = \delta(A, E_1, E_2, e_1, e_2) > 0$ is a certain
+\textit{condition number} for the game. Their ingenious idea was to
+show that \eqref{eq:gilpin} can futher be written in the form\\
+\[\mathrm{maximize}\{G(x, y):=G(x, y) :=
+max\{\langle x, Av\rangle - \langle u, Ay\rangle |
+(u,v) \in Q_1 \times Q_2|(x,y) \in Q_1 \times Q_2\},
+\]
+and then show that if $\mathcal{E}$ is the set of Nash equilibria for
+the game, then  there exists a scalar
+$\delta > 0$ such that $distance((x, y), \mathcal{E}) \le \dfrac{G(x, y)}{\delta}$,
+for any pair of realization plans $(x, y) \in Q_1 \times Q_2$. Their
+algorithm is then to apply Nesterov smoothing with a geometrically
+decreasing sequence of tolerance levels on primal-dual gap function $G$.
+It should be noted however that
 \begin{itemize}
-\item[--] though \cite{gilpinfirst} proved that we always have $\delta
-  > 0$, this constant can be arbitrarily small; and most importantly,
-\item[--] the reported linear convergence rate is not in terms of
+\item[--] Though \cite{gilpinfirst} proved that we always have $\delta
+  > 0$, this constant can be arbitrarily small; and most importantly.
+\item[--] The reported linear convergence rate is not in terms of
   basic operations (addition, multiplication, matvec, clipping, etc.),
-  but in terms of the number of calls to a first-order oracle. Of
-  course, the existence of a linear algorithm for solving
-  \eqref{eq:gilpin} is improbable, as the usual strong-convexity
-  conditions are absent.
+  but in terms of the number of calls to a first-order oracle. For
+  example the projections $\proj_{Q_k}$ are applied at each iteration.%%  Of
+  %% course, the existence of a linear algorithm for solving
+  %% \eqref{eq:gilpin} is improbable, as the usual strong-convexity
+  %% conditions are absent.
 
@@
       (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
-        i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tp\\
+        i_{\mathbb{R}^{n_2}_+}(y) + \langle e_1,p\rangle\\
         g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
         (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
-          i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tq
+          i_{\mathbb{R}^{n_1}_+}(x) + \langle e_2, q\rangle
     \end{aligned}
@@
 \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
-\mathbb{R}^{l_2} \rightarrow \mathbb{R}$ by letting
+\mathbb{R}^{l_2} \rightarrow \mathbb{R}$ with $\Psi_2 = -\Psi_1$ by letting
   \begin{equation}
@@
     \Psi_1(y, p, x, q)
-    := \begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix}, \hspace{.5em}
-      \Psi_2(y, p, x, q) := -\Psi_1(y, p, x, q).
+    := \left\langle \begin{bmatrix}x\\q\end{bmatrix},
+      K\begin{bmatrix}y\\p\end{bmatrix}\right\rangle.
 \end{equation}
@@
   \begin{aligned}
-    a(y,p) &= e_1^Tp +
-    i_{\mathbb{R}^{n_2}_+}(y) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) +
-    i_{\{0\}}(E_2y - e_2)\\
-    &= g_1(y,p) +
-    i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
+    a(y,p) &= \langle e_1,p\rangle + i_{y\ge 0} + i_{-Ay + E_1^Tp \ge 0} +
+    i_{E_2y = e_2}\\
     &= g_1(y,p) + \underset{x' \geq
-      0}{\text{max}}\text{ }x'^T(Ay - E_1^Tp) +
-    \underset{q'}{\text{max}}\text{ }q'^T(E_2y - e_2)\\
+      0}{\text{max}}\text{ }\langle x',Ay - E_1^Tp\rangle +
+    \underset{q'}{\text{max}}\text{ }\langle q',E_2y - e_2\rangle\\
     &= g_1(y,p) + \underset{x',
-      q'}{\text{max}}\text{ }x'^TAy - x^TE_1^Tp + q'^TE_2y -
-    (i_{\mathbb{R}^{n_1}_+}(x') + e_2^Tq)\\
+      q'}{\text{max}}\text{ }\langle x',Ay\rangle - \langle x',
+    E_1^Tp\rangle + \langle q',E_2y\rangle -
+    (i_{x' \ge 0} + \langle e_2,q\rangle)\\
     &= g_1(y,p)
@@
  b(x, q) &= 
- -i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
- i_{\{0\}}(e_1 - E_1x)\\
+-\langle q, e_2\rangle -i_{x \ge 0} - i_{A^Tx+E_2^Tq \ge 0} -
+ i_{E_1x = e_1}\\
     &= -g_2(x, q) + \underset{y' \geq
-   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
- \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
+   0}{\text{min}}\text{ }\langle y', A^Tx + E_2^Tq\rangle +
+ \underset{p'}{\text{min}}\text{ }\langle p', e_1-E_1x\rangle\\
     &= -g_2(x, q)
@@
 \State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
-E_2^Tq^{(k)}))_+$
-\State  $p^{(k+1)} \leftarrow p^{(k)} -
+E_2^Tq^{(k)}))_+$, \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
 \lambda(e_1-E_1x^{(k)})$
@@
 x^{(k+1)}-x^{(k)}$
-\State $\Delta q^{(k+1)} \leftarrow
-q^{(k+1)}-q^{(k)}$, \hspace{.5em}$q^{(k+1)}
-\leftarrow q^{(k)} + \Delta q^{(k+1)}$
+\State $\Delta q^{(k+1)} \leftarrow \lambda (E_2y -
+e_2)$, \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
 \State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}

### 2015-07-03 primal_dual.py

@@ -14,8 +14,8 @@ _norm = lambda *args: sqrt(np.sum(np.concatenate(args) ** 2))
 
 
 def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
-                   proj_C2=lambda y: np.maximum(y, 0.), init=None, tol=1e-10,
-                   max_iter=10000, callback=None):
+                   proj_C2=lambda y: np.maximum(y, 0.), init=None,
+                   epsilon=1e-10, max_iter=10000, callback=None):
     """Primal-Dual algorithm for computing Nash equlibrium for two-person
     zero-sum game with payoff matrix A and contraint sets
 
@@ -23,8 +23,12 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
 
     The formal problem is:
 
-        minimize maximize <x, Ay>
-        y in Q2  x in Q1
+        minimmize maximize <x, Ay>
+         x in Q1   y in Q2
+
+    Notes
+    -----
+    \epsilon really stands for \rho in the paper.
 
     Returns
     -------
@@ -41,7 +45,7 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
         norm_K = linalg.norm(K, 2)
     sigma = init.get("sigma", 1.)
     lambd = init.get("lambd", .9 * sigma / norm_K)
-    y = init.get("x", np.zeros(n2))
+    y = init.get("y", np.zeros(n2))
     p = init.get("p", np.zeros(l1))
     x = init.get("x", np.zeros(n1))
     q = init.get("q", np.zeros(l2))
@@ -93,13 +97,13 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
         gaps.append(gap)
 
         # invoke callback
-        if callback: callback(locals())
+        if callback and callback(locals()): break
         print ("Iter %03i/%03i: game value = %g, primal-dual gap (perturbed) ="
                " %.2e") % (k + 1, max_iter, value, gap)
 
         # check convergence
-        if gap < tol:
-            print "Converged (gap < gap tol = %.2e)." % tol
+        if gap < epsilon:
+            print "Converged (gap < gap epsilon = %.2e)." % epsilon
             break
[…]

### 2015-07-03 simple.py

@@ -455,7 +455,7 @@ if __name__ == "__main__":
 
     rng = check_random_state(42)
     max_iter = 10000
-    game_clses = ["simplex", SimplifiedPoker, Kuhn3112]
+    game_clses = ["simplex", SimplifiedPoker, Kuhn3112][1:2]
     for cnt, game_cls in enumerate(game_clses):
         if game_cls == "simplex":
             game = None

### 2015-07-03 nips2015.tex
added code for nesterov smoothing and gilpin's first order scheme

@@
 
-\DeclareMathOperator{\dom}{dom}
 \DeclareMathOperator{\proj}{proj}
@@
   convex function. The \textit{effective domain} of $f$, denoted
-  $\dom(f)$ is defined as
+  $dom(f)$ is defined as
 \begin{eqnarray}
-  \dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
+  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
 \end{eqnarray}
- If $\dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
+ If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
 %% \textit{proper convex lower semi-continous function}
@@
   \begin{aligned}
-     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{ subject to }(y,p) \in
-     \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}, -Ay +
-    E_1^Tp \geq 0, E_2y = e_2, y \ge 0.
+     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{ subject to: }(y,p) \in
+     \mathbb{R}^{n_2} \times \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay +
+    E_1^Tp \geq 0.
   \end{aligned}
@@
   \begin{aligned}
-    \text{maximize}-\langle e_2, q\rangle,\hspace{.5em}\text{subject to }(y,q) \in
-    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, A^Tx + E_2^Tq \geq 0,
-    E_1x = e_1, x \ge 0.
+    \text{maximize}-\langle e_2, q\rangle,\hspace{.5em}\text{subject to: }(x,q) \in
+    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2},  x \ge 0, E_1x = e_1, A^Tx + E_2^Tq \geq 0.
   \end{aligned}
@@
 (which derives from the general EGT theory) for the outer-most
-iteration loop, though the cost of an iteration is presumably heavy
-since it entails computing a $softmax$ at each iteration.
+iteration loop.
 
@@
 \textit{condition number} for the game. Their ingenious idea was to
-show that \eqref{eq:gilpin} can futher be written in the form\\
-\[\mathrm{maximize}\{G(x, y):=G(x, y) :=
+show that \eqref{eq:gilpin} can futher be written in the form
+\[\mathrm{maximize}\{G(x, y):=
 max\{\langle x, Av\rangle - \langle u, Ay\rangle |
@@
 \]
-and then show that if $\mathcal{E}$ is the set of Nash equilibria for
-the game, then  there exists a scalar
-$\delta > 0$ such that $distance((x, y), \mathcal{E}) \le \dfrac{G(x, y)}{\delta}$,
+and then show there exists a scalar
+$\delta > 0$ such that ``distance between $(x, y)$ and the set of
+equilibria'' $\le \dfrac{G(x, y)}{\delta}$,
 for any pair of realization plans $(x, y) \in Q_1 \times Q_2$. Their
-algorithm is then to apply Nesterov smoothing with a geometrically
-decreasing sequence of tolerance levels on primal-dual gap function $G$.
-It should be noted however that
+algorithm is then derived by iteratively applying Nesterov smoothing
+with a geometrically decreasing sequence of tolerance levels on
+primal-dual gap function $G$. It should be noted however that
 \begin{itemize}
@@
 \begin{proof}
-Note that $\dom(g_1) = S_1$ and $\dom(g_2) = S_2$ and observe that the
-equilibria of the LCPs \eqref{eq:primal_pb}, \eqref{eq:dual_pb}, and
+Note that $dom(g_1) = S_1$ and $dom(g_2) = S_2$ and observe that since the
+equilibria of the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb}, and
 the equilibria of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$) are contained

### 2015-07-03 nesterov.py

@@ -1,0 +1,254 @@
+"""
+Solving matrix games via Nesterov smoothing. Quick-and-dirty code!
+"""
+# Author: Elvis DOHMATOB <elvis.dohmatob@inria.fr>
+
+from math import sqrt
+import numpy as np
+from scipy import linalg
+
+
+def proj_simplex(v, z=1.):
+    """Projects v unto the simplex {x >= 0, x_0 + x_1 + ... x_n = z}.
+
+    The method is John Duchi's O (n log n) Algorithm 1.
+    """
+    # deterministic O(n log n)
+    u = np.sort(v)[::-1]  # sort v in increasing order
+    aux = (np.cumsum(u) - z) / np.arange(1., len(v) + 1.)
+    return np.maximum(v - aux[np.nonzero(u > aux)[0][-1]], 0.)
+
+
+def test_proj_simplex():
+    v = np.array([1.1, 0., 0.])
+    np.testing.assert_array_equal(proj_simplex(v), [1., 0., 0.])
+
+    v = np.array([0., 0., 0.])
+    np.testing.assert_array_equal(proj_simplex(v), [1. / 3, 1. / 3, 1. / 3])
+
+
+def nesterov_ne(A, c=None, b=None, epsilon=1e-3, max_iter=np.inf,
+                dynamic_mu=False, mu_init=1e-2, mu_factor=.9):
+    """Computes an approx Nash equilibrium for matrix game via Nesterov
+    smoothing [1].
+
+    Formally, the problem is
+
+        minimize maximize <Ax, u> + <c, x> + <b, u>,
+        u in S_2 x in Q_1
+
+    where Q_j is player j's simplex.
+
+    Parameters
+    ----------
+    A: ndarray, shape (m, n)
+        Payoff matrix.
+
+    c: ndarray, shape (n,), optional (default None)
+        <c, x> is added to the payoff function <Ax, u>.
+
+    b: ndarray, shape (n,), optional (default None)
+        <b, u> is added to the payoff function <Ax, u>
+
+    epsilon: positive float, optional (default 1e-3)
+        Tolerance on primal-dual gap.
+
+    max_iter: int, optional (default np.inf)
+        Maximum number of iterations to run. If no value is specified,
+        then it is inferred using Nesterov's formulae.
+
+    dynamic_mu: boolean, optional (default False)
+        If true, then the smoothing parameter mu will be set dynamically.
+
+    mu_init: positive float, optional (default 1e-2)
+        Initial value for the smoothing parameter mu.
+
[…]

### 2015-07-03 primal_dual.py

@@ -15,7 +15,7 @@ _norm = lambda *args: sqrt(np.sum(np.concatenate(args) ** 2))
 
 def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
                    proj_C2=lambda y: np.maximum(y, 0.), init=None,
-                   epsilon=1e-10, max_iter=10000, callback=None):
+                   epsilon=1e-4, max_iter=10000, callback=None):
     """Primal-Dual algorithm for computing Nash equlibrium for two-person
     zero-sum game with payoff matrix A and contraint sets
 
@@ -118,7 +118,7 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
     return x, y, p, q, init, values, gaps
 
 
-def primal_dual_sg_ne(A, epsilon=1e-4, **kwargs):
+def primal_dual_sg_ne(A, epsilon=1e-4, strict=True, **kwargs):
     n1, n2 = A.shape
     E1 = np.ones((1, n1))
     E2 = np.ones((1, n2))
@@ -133,12 +133,14 @@ def primal_dual_sg_ne(A, epsilon=1e-4, **kwargs):
     gaps = []
 
     def cb(variables):
-        gap = A.T.dot(variables["x"]).max() - A.dot(variables["y"]).min()
+        gap = A.dot(variables["y"]).max() - A.T.dot(variables["x"]).min()
         gap = abs(gap)  # maybe gap < 0 in case we aren't on the feasible set
         print gap
         gaps.append(gap)
-        return gap < epsilon
+        return strict and gap < epsilon
 
-    x, y, _, _, _, values, _ = primal_dual_ne(A, E1, E2, e1, e2, callback=cb,
-                                              epsilon=epsilon, **kwargs)
-    return x, y, values, gaps
+    x, y, p, q, init, values, gaps_ = primal_dual_ne(
+        A, E1, E2, e1, e2, callback=cb, epsilon=epsilon, **kwargs)
+
+    if strict: return x, y, values, gaps
+    else: return x, y, p, q, init, values, gaps_

### 2015-07-03 simple.py

@@ -455,14 +455,14 @@ if __name__ == "__main__":
 
     rng = check_random_state(42)
     max_iter = 10000
-    game_clses = ["simplex", SimplifiedPoker, Kuhn3112][1:2]
+    game_clses = ["simplex", SimplifiedPoker, Kuhn3112]
     for cnt, game_cls in enumerate(game_clses):
         if game_cls == "simplex":
             game = None
             name = game_cls
-            A = rng.uniform(-1, 1, size=(1000, 1000))
+            A = rng.uniform(-1, 1, size=(100, 100))
             x, y, p, q, init, values, dgaps = primal_dual_sg_ne(
-                A, max_iter=max_iter)
+                A, max_iter=max_iter, strict=False)
         else:
             game = game_cls()
             name = game.__class__.__name__
@@ -471,7 +471,7 @@ if __name__ == "__main__":
             A = game.payoff_matrix
             args = (A, E1, E2, e1, e2)
             x, y, p, q, init, values, dgaps = primal_dual_ne(A, E1, E2, e1, e2,
-                                                             max_iter=max_iter)
+                                                          max_iter=max_iter)
 
         # estimate constant in bound (4.1) of Yunlong He's Theorem 3.5
         aux = np.concatenate((y, p, x, q))

### 2015-07-04 nips2015.tex
fixups

@@
 vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
-$\langle z, w\rangle$ The components of $z \in \mathbb{R}^n$ will be
+$\langle z, w\rangle := \sum_{j}z_jw_j$ The components of $z \in \mathbb{R}^n$ will be
 denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
@@
 \mathbb{R}^n$, $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
-by $\|z\| := \sqrt{\langle z, z\rangle} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
+by $\|z\| := \sqrt{\langle z, z\rangle}$.
 $(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
@@
 entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
-$[1, 0, ..., 0]$. In this so-called \textit{sequence-form}
+$(1, 0, ..., 0)$. In this so-called \textit{sequence-form}
 representation, the strategy profile of player $k$ is the polyhedron
@@
 \end{equation}
-Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle = q_0$ by definition of $e_1$ and
-$e_2$. At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
+%% Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle = q_0$ by definition of $e_1$ and
+%% $e_2$. 
+At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
 $\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
@@
 \begin{equation}
-  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0.
+  0 \le \mathcal{G}(y, p, x, q) := \langle e_1, p\rangle - (\langle
+  e_2, q\rangle) = \langle e_1, p\rangle + \langle
+  e_2, q\rangle = G(x, y),
   \label{eq:dgap}
 \end{equation}
+where
+\begin{eqnarray}
+G(x, y) :=
+\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
+(u,v) \in Q_1 \times Q_2\}.
+\label{eq:xy_gap}
+\end{eqnarray}
 
@@
 \begin{remark}  
-It should be noted that for the the class of games considered here (sequential games with imcomplete information), the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger than what state-of-the-art LCP solvers can handle.
-See \cite{hoda2010smoothing}.
+It should be noted that for the the class of games considered here
+(sequential games with imcomplete information), the LCPs
+\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
+than what state-of-the-art LCP solvers can handle. See
+\cite{hoda2010smoothing}.
+
 \end{remark}
 
-Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly is impossible in practice \textbf{Cite Koller!!!}, and such a precision doesn't have any fundamental advantage.
-Instead, it is customary compute so-called Nash $\epsilon$-equlibria.
+Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
+is impossible in practice \textbf{Cite Koller!!!}, and such a
+precision doesn't have any fundamental advantage. Instead, it is
+customary compute so-called Nash $\epsilon$-equlibria.
 
@@
 $\delta = \delta(A, E_1, E_2, e_1, e_2) > 0$ is a certain
-\textit{condition number} for the game. Their ingenious idea was to
-show that \eqref{eq:gilpin} can futher be written in the form
-\[\mathrm{maximize}\{G(x, y):=
-max\{\langle x, Av\rangle - \langle u, Ay\rangle |
-(u,v) \in Q_1 \times Q_2|(x,y) \in Q_1 \times Q_2\},
-\]
+\textit{condition number} for the game. The crux of their technique was to
+observe that \eqref{eq:gilpin} can further be written a the minimization of
+the primal-dual gap function $G(x, y)$ (defined in \eqref{eq:xy_gap})
+for the game\footnote{The minimizers of $G$ are precisely the
+  equilibria of the game.}, viz
+\begin{eqnarray}
+\mathrm{maximize}\{G(x,y)|(x,y) \in Q_1 \times Q_2\},
+\end{eqnarray}
 and then show there exists a scalar
-$\delta > 0$ such that ``distance between $(x, y)$ and the set of
-equilibria'' $\le \dfrac{G(x, y)}{\delta}$,
-for any pair of realization plans $(x, y) \in Q_1 \times Q_2$. Their
-algorithm is then derived by iteratively applying Nesterov smoothing
-with a geometrically decreasing sequence of tolerance levels on
+$\delta > 0$ such that for any pair of realization plans $(x, y) \in Q_1 \times Q_2$,
+\begin{eqnarray}
+\text{``distance between }(x, y)\text{ and the set of
+equilibria'' } \le G(x, y)/\delta.
+\end{eqnarray}
+Their
+algorithm is then derived by iteratively applying Nesterov smoothing \cite{nesterov2005a}
+with a geometrically decreasing sequence of tolerance levels
+$\epsilon_{n+1} = \epsilon_n / \gamma$ (with $\gamma > 1$)  on
 primal-dual gap function $G$. It should be noted however that
 \begin{itemize}
-\item[--] Though \cite{gilpinfirst} proved that we always have $\delta
-  > 0$, this constant can be arbitrarily small; and most importantly.
+\item[--] The constant $\delta > 0$ can be arbitrarily small, and so
+  the factor $\|A\| / \delta$ in the $\mathcal{O}\left(\left(\|A\| /
+\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate can
+be arbitrarily large.
 \item[--] The reported linear convergence rate is not in terms of
@@
       (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
-        i_{\mathbb{R}^{n_2}_+}(y) + \langle e_1,p\rangle\\
+        i_{y \ge 0} + \langle e_1,p\rangle\\
         g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
         (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
-          i_{\mathbb{R}^{n_1}_+}(x) + \langle e_2, q\rangle
+          i_{x \ge 0} + \langle e_2, q\rangle
     \end{aligned}
@@
     \Psi_1(y, p, x, q)+ g_1(y, p) \text{ if }y \ge 0, \hat{\Psi}_1(y,
-    p, x, q) := \infty \text{ else}\\
+    p, x, q) := \infty \text{ otherwise}\\
     \hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(x, q) \text{ if
-    }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ else}.
+    }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ otherwise}.
   \end{aligned}
@@
       - \underset{x',q'}{\text{min}}\text{ }\Psi_2(y, p, x', q') + g_2(x',
-      q') = g_1(y,p) -\phi_2(y,p),
+      q') = g_1(y,p)
+      - \underbrace{\underset{x',q'}{\text{min}}\text{
+        }\hat{\Psi}_2(y, p, x', q')}_{\phi_2(y,p)},
   \end{aligned}
@@
 
-where $-\infty \le \phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
-}\hat{\Psi}_2(y, p, x', q') < +\infty$.
 Similarly, the unconstrained objective, say
@@
     &= -g_2(x, q)
- +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
- g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
+ +\underset{y',p'}{\text{min}}\text{ }\Psi_1(y', p', x, q) +
+ g_1(y', p') = -g_2(x, q)
+ +\underbrace{\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p',
+   x, q)}_{\phi_1(x, q)}.
    \end{aligned}
 \end{eqnarray*}
-where $-\infty \le \phi_1(x, q) :=
-\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) < +\infty$.
-Thus, one can compute the primal-dual gap between the primal LCP
+Thus, noting that $-\infty \le \phi_1(x, q), \phi_2(y, p), < +\infty$,
+one can compute the primal-dual gap between the primal LCP
 \eqref{eq:primal_pb} and dual the LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as

### 2015-07-04 nips2015.tex
fixups

@@
 $\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
-operators generalize orthongal projectors. One also has the useful
+operators generalize orthogonal projectors. One also has the useful
 characterization
@@
 
-The interested reader should refer to
-\cite{combettes2011proximal} for
+The interested reader should refer to \cite{combettes2011proximal} for
 a more elaborate exposition of proximal operators and their
@@
 imcomplete information and perfect recall, there exist sparse matrices
-$A \in \mathbb{R}^{n_1
-  \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in
-\mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1},
-e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are
-all linear in the size of the game tree (number of states in the game)
-and such that Nash equilibria correspond to pairs $(x, y)$ of
-\textit{realization plans} which solve the primal LCP
+$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
+  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
+\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
+$l_1$, and $l_2$ are all linear in the size of the game tree (number
+of states in the game) and such that Nash equilibria correspond to
+pairs $(x, y)$ of \textit{realization plans} which solve the primal
+LCP
 \begin{equation}
   \begin{aligned}
-     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{ subject to: }(y,p) \in
-     \mathbb{R}^{n_2} \times \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay +
-    E_1^Tp \geq 0.
+     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
+       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
+     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
   \end{aligned}
@@
   \begin{aligned}
-    \text{maximize}-\langle e_2, q\rangle,\hspace{.5em}\text{subject to: }(x,q) \in
-    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2},  x \ge 0, E_1x = e_1, A^Tx + E_2^Tq \geq 0.
+    \text{maximize}-\langle e_2, q\rangle,\hspace{.5em}\text{subject
+      to: }(x,q) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2},  x \ge
+    0, E_1x = e_1, A^Tx + E_2^Tq \geq 0.
   \end{aligned}
@@
 \end{equation}
-%% Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle = q_0$ by definition of $e_1$ and
+
+Note that the LCPs above have the equivalent saddle point formulation
+\begin{equation}
+  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
+    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle
+  \label{eq:gilpin}
+\end{equation}
+
+%% Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle
+%% = q_0$ by definition of $e_1$ and
 %% $e_2$. 
@@
 \begin{remark}  
-It should be noted that for the the class of games considered here
+It should be noted that for the class of games considered here
 (sequential games with imcomplete information), the LCPs
@@
 Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used to
-to solve the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the
-following equivalent saddle-point form\footnote{Note that in
-  \cite{hoda2010smoothing}, the roles of $x$ and $y$ are swapped.}
-
-\begin{equation}
-  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
-    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle
-  \label{eq:gilpin}
-\end{equation}
+to solve the equilibrium problem \eqref{eq:gilpin}.
 The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
@@
 with a geometrically decreasing sequence of tolerance levels
-$\epsilon_{n+1} = \epsilon_n / \gamma$ (with $\gamma > 1$)  on
-primal-dual gap function $G$. It should be noted however that
+$\epsilon_{n+1} = \epsilon_n / \gamma$ (with $\gamma > 1$)  $G$. It
+should be noted however that
 \begin{itemize}
@@
     := \left\langle \begin{bmatrix}x\\q\end{bmatrix},
-      K\begin{bmatrix}y\\p\end{bmatrix}\right\rangle.
+      K\begin{bmatrix}y\\p\end{bmatrix}\right\rangle = \langle x,
+      Ay\rangle -\langle x, E_1^Tp\rangle + \langle q, E_2y\rangle.
 \end{equation}
@@
 
-\begin{definition}(Kronecker product)
-Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
-  s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
+%% \begin{definition}(Kronecker product)
+%% Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
+%%   s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
 
-\begin{equation}
-F \otimes B:=\left[
-\begin{array}{cccc}
-F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
-F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
-\vdots & \vdots & \ddots & \vdots\\
-F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
-\end{array}\right] \in \mathbb{R}^{mr \times ns}
-\end{equation}
-\end{definition}
+%% \begin{equation}
+%% F \otimes B:=\left[
+%% \begin{array}{cccc}
+%% F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
+%% F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
+%% \vdots & \vdots & \ddots & \vdots\\
+%% F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
+%% \end{array}\right] \in \mathbb{R}^{mr \times ns}
+%% \end{equation}
+%% \end{definition}
 
-One notes that $(F \otimes B)^T = F^T \otimes B^T$.
-$F \otimes B$ can be very much larger than both $F$ and $B$ in
-dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
-$B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
-$10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
-\mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
-without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
-rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
-  ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
-$s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
-as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
-easily verfies that $Y$ is the matrix product of the ``small''
-matrices $B$, $X$, and $F^T$, i.e
+%% One notes that $(F \otimes B)^T = F^T \otimes B^T$.
+%% $F \otimes B$ can be very much larger than both $F$ and $B$ in
+%% dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
+%% $B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
+%% $10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
+%% \mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
+%% without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
+%% rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
+%%   ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
+%% $s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
+%% as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
+%% easily verfies that $Y$ is the matrix product of the ``small''
+%% matrices $B$, $X$, and $F^T$, i.e
 
-\begin{equation}
-  \label{eq:kron_matvec}
-  Y = BXF^T
-\end{equation}
+%% \begin{equation}
+%%   \label{eq:kron_matvec}
+%%   Y = BXF^T
+%% \end{equation}
 
-Now, in Texas Hold'em for example, the payoff matrix $A$ can be
-written as block-diagonal matrix whose blocks are sums of Kronecker
-products of much smaller sparse matrices as follows
+%% Now, in Texas Hold'em for example, the payoff matrix $A$ can be
+%% written as block-diagonal matrix whose blocks are sums of Kronecker
+%% products of much smaller sparse matrices as follows
 
-\begin{equation}
-  A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
-    \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
-    B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
-\label{eq:factor_A}
-\end{equation}
-See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
-sequences of moves in round $i$ which end in a \textit{fold} action,
-and $S$ to the sequences which end in a \textit{showdown}. $B_i$
-encodes the betting structure of round $i$, while $W$ encodes the
-wind/lose/draw information determined by ranking the players' hands at
-showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
-enough to be explictly represented whereas it is infeasible to
-explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
-$S$, and $W$ are themselves sparse, which allows one to use the
-compressed row storage data structure that only stores nonzero entries
-(for example \textit{scipy.sparse.csr\_matrix}, in the Python
-programming language).
+%% \begin{equation}
+%%   A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
+%%     \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
+%%     B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
+%% \label{eq:factor_A}
+%% \end{equation}
+%% See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
+%% sequences of moves in round $i$ which end in a \textit{fold} action,
+%% and $S$ to the sequences which end in a \textit{showdown}. $B_i$
+%% encodes the betting structure of round $i$, while $W$ encodes the
+%% wind/lose/draw information determined by ranking the players' hands at
+%% showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
+%% enough to be explictly represented whereas it is infeasible to
+%% explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
+%% $S$, and $W$ are themselves sparse, which allows one to use the
+%% compressed row storage data structure that only stores nonzero entries
+%% (for example \textit{scipy.sparse.csr\_matrix}, in the Python
+%% programming language).
 
-Such a representation of the payoff matrix $A$ trivializes matvec
-operations involving $A$ or $A^T$ (thanks to formula
-\eqref{eq:kron_matvec} above, applied to their diagonal blocks and
-exploiting the sparsity of these blocks themselves). Of course, one
-can always write the payoff matrix $A$ of a flop-type Poker game in a
-form similary to \eqref{eq:factor_A} by applying appropriate
-permutations to the enumeration of the players's sequences.
+%% Such a representation of the payoff matrix $A$ trivializes matvec
+%% operations involving $A$ or $A^T$ (thanks to formula
+%% \eqref{eq:kron_matvec} above, applied to their diagonal blocks and
+%% exploiting the sparsity of these blocks themselves). Of course, one
+%% can always write the payoff matrix $A$ of a flop-type Poker game in a
+%% form similary to \eqref{eq:factor_A} by applying appropriate
+%% permutations to the enumeration of the players's sequences.
 

### 2015-07-04 nesterov.py

@@ -148,11 +148,11 @@ def gilpin_ne(A, epsilon=1e-4, max_iter=np.inf):
 
     The formal problem is:
 
-         minimize maximize <x, Ay>,
+         minimize maximize <y, Ax>,
          y in Q_2   x in Q_1
 
     """
-
+    A = A.T  # make compatible with nesterov_ne
     m, n = A.shape
     R = np.vstack((np.hstack((np.zeros((m, m)), -A)),
                    np.hstack((A.T, np.zeros((n, n))))))
@@ -230,25 +230,38 @@ def gilpin_ne(A, epsilon=1e-4, max_iter=np.inf):
     return x, y, values, gaps
 
 if __name__ == "__main__":
+    # matplotlib confs
+    import matplotlib
     import matplotlib.pyplot as plt
+    matplotlib.rcParams['text.latex.preamble'] = ['\\boldmath']
+    matplotlib.rc('font', family='serif', serif='cm10')
+    matplotlib.rc('text', usetex=True)
+    plt.rc('font', size=50)  # make the power in sci notation bigger
+
     from primal_dual import primal_dual_sg_ne
     rng = np.random.RandomState(42)
     A = np.array([[-2., 3.], [3, -4]])
     A = rng.randn(10, 10)
-    plt.figure(figsize=(13.5, 7))
-    ax1 = plt.subplot2grid((1, 2), (0, 0))
+    plt.figure(figsize=(17, 13))
+    ax1 = plt.subplot("111")
     plt.grid("on")
-    ax2 = plt.subplot2grid((1, 2), (0, 1))
+    plt.figure(figsize=(17, 13))
+    ax2 = plt.subplot("111")
     plt.grid("on")
-    for solver in ["primal_dual_sg", "nesterov", "gilpin"]:
-        x, u, values, gaps = eval("%s_ne" % solver)(A, epsilon=1e-4,
-                                                    max_iter=10000)
-        plt.grid("on")
-        ax1.loglog(gaps, label=solver)
-        ax1.set_xlabel("$k$")
-        ax1.set_ylabel("primal-dual gap")
-        ax2.semilogx(values, label=solver)
-        ax2.set_xlabel("$k$")
-        ax2.set_ylabel("game value")
-    plt.legend(loc="best")
+    for solver in ["primal-dual sg", "nesterov", "gilpin"]:
+        x, u, values, gaps = eval("%s_ne" % solver.replace(" ", "_").replace(
[…]

### 2015-07-10 paper.tex
refactors + fixups + some XXX removal

--- 2014-08-13 paper.tex
@@
-\documentclass[a4paper,9pt,journal]{IEEEtran}
-\usepackage{graphicx} \usepackage[cmex10]{amsmath}
-\usepackage{amssymb} \usepackage{fancybox} \usepackage{alltt}
-\usepackage{soul} \usepackage{color} \usepackage{verbatim}
-\usepackage{xcolor} \usepackage{colortbl,hhline}
-\usepackage[ruled,vlined]{algorithm2e} \usepackage{framed}
-\usepackage{amsthm} \usepackage{fancyref}
-\usepackage{amsmath,amsfonts,amssymb, amsthm} \usepackage{textcomp}
-
-\newtheorem{remark}{Remark}
-
-\def \lb {{\langle}} \def \rb {{\rangle}}
-\newcommand{\fro}[1]{\|#1\|_2}
-\newcommand{\theHalgorithm}{\arabic{algorithm}}
-
-\newcommand{\argmin}{\mathop{\mathrm{argmin}}}
-
-\usepackage{hyperref}
+\documentclass{article} % For LaTeX2e
+\usepackage{nips14submit_e}
+%\documentclass[envcountsame]{llcns2e/llncs}
+\usepackage{url}
+\usepackage{times}
+\usepackage{amsmath,amsfonts, amsthm}
+\usepackage{bbm}
+\usepackage{algorithm,algorithmicx}
+\usepackage{graphicx}
+\usepackage{bm}
+\usepackage{bbm}
+\usepackage[titletoc]{appendix}
+\usepackage{algpseudocode}
+\usepackage{pifont}
+\usepackage[FIGTOPCAP]{subfigure}
 
 \newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
+
 \newtheorem{proposition}[theorem]{Proposition}
@@
 \newtheorem{definition}[theorem]{Definition}
+\newtheorem{remark}{Remark}
+\newtheorem{fact}{Fact}
 
-\newcommand{\prox}{\textrm{pr ox} } \newcommand{\grad}{\textrm{grad} }
-\newcommand{\dive}{\textrm{div} }
+\DeclareMathOperator{\proj}{proj}
+\DeclareMathOperator{\prox}{prox}
 
-\pagenumbering{gobble}
+\title{
+  %\hrule\hrule\bigskip\bigskip
+  A simple and efficient algorithm for computing approximate
+  Nash equilibria in two-person zero-sum sequential games with imcomplete
+  information}
+\author{Elvis DOHMATOB
+\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
+\\\texttt{firstname.lastname@inria.fr}
+}
+
+% The \author macro works with any number of authors. There are two commands
+% used to separate the names and addresses of multiple authors: \And and \AND.
+%
+% Using \And between authors leaves it to \LaTeX{} to determine where to break
+% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
+% puts 3 of 4 authors names on the first line, and the last on the second
+% line, try using \AND instead of \And before the third author name.
+
+%\nipsfinalcopy % Uncomment for camera-ready version
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{document}
-%\onecolumn
-\title{A fast primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum sequential games}
-
-\author{\IEEEauthorblockN{Elvis D. DOHMATOB}}
 
 \maketitle
-
-\begin{abstract}
-% LESS THAN 200 WORDS !!!!!
-% 
-% While medical imaging typically provides massive amounts of
-% data, the extraction of relevant information in a given
-% applicative context remains a difficult challenge.
-% XXX : don't call it SPM but just "predictive regions or predictive
-% maps"
-In this manuscript, we consider the problem of computing a best response against an opponent's realization plan in two-person sequential games.
-The proposed algorithm for solving the corresponding contrained convex-optimization problem, derives from the primal-dual scheme of A. Chambolle and T. Pock.
-Our algorithm is simple: all resolvent operators can be effectively computed in closed-form, using only elementary algebraic operations.
-%%  and is orders of magnitude more efficient than state-of-the-art algorithms like those based on Linear Programming, Interior-Point methods,
-%% and more recently, the Nesterov Excessive Gap Technique.
-% By way of example, we conclude by exhibiting results on Texas Hold'em Poker.
+\begin{abstract}We present a simple primal-dual algorithm for
+  computing approximate Nash equilibria in two-person zero-sum
+  sequential games with  imcomplete information and perfect recall
+  (like Texas Hold'em Poker) based on the notion of enlarged
+  subgradients. Our algorithm only performs basic iterations (i.e
+  iterations involving no calls to external first-order oracles, etc.)
+  and is applicable to a broad class of two-person zero-sum games
+  including simultaneous games and sequential games with imcomplete
+  information and perfect recall. The applicability to the latter kind
+  of games is thanks to the sequence-form representation
+  \cite{koller1992complexity} which allows us to encode any such game
+  as a matrix game with polyhedral strategy profiles, the size of the
+  representation being linear in ... The number of iterations needed
+  to produce a Nash equilibrium with a given precision is inversely
+  proportional to the desired precision. As proof-of-concept, we apply our
+  algorithm to solve Kuhn 3-card Poker.
 \end{abstract}
 
-\begin{IEEEkeywords}
-  game theory; two-person sequential game; Nash equilibria; best response; convex-optimization; contraint; primal-dual scheme
-\end{IEEEkeywords}
+\textbf{keywords}: sequential game; imcomplete information; perfect
+recall; sequence-form; approximate Nash equilibrium; primal-dual
+algoithm; convex-optimization; enlarged subgradient
 
 \section{Introduction}
-%\label{sec:intro}
-\subsection{Notation and Terminology}
-To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
-(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,
+\label{sec:intro}
+A game-theoretic approach to playing games strategically optimally
+consists in computing Nash-equilibria (infact, approximations thereof)
+offline, and playing one's part of the equilibrium online. This
+technique is the driving-force behind solution concepts like CFR
+\cite{zinkevich2008regret,lanctot2009monte},
+$\text{CFR}^{+}$ \textbf{TODO: add ref!!!}, and other variants, which
+have recently had profound success in Poker. However, solving games
+for equilibria remains a mathematical and computational challenge,
+especially in sequential games with imperfect information. This paper
+proposes a simple and fast algorithm for solving for such equilibria
+approximately, in a sense which will be made clear shortly.
+
+\subsection{Notation and terminology}
+\paragraph{\textbf{General notions.}}
+Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
+of all subsets of $X$, or equivalently the set of all binary
+functions on $X$.
+
+Let $m$ and $n$ be positive integers.
+$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
+0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  Given two
+vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
+$\langle z, w\rangle := \sum_{j}z_jw_j$ The components of $z \in \mathbb{R}^n$ will be
+denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
+not $1$). The notation ``$z \ge 0$'' means that all the components of $z$ are
+nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
+\mathbb{R}^n$, $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
+by $\|z\| := \sqrt{\langle z, z\rangle}$.
+$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
+maximum of $z$ with $0$. For example, $((-2, \pi))_+ = (max(-2, 0),
+max(\pi, 0)) = (0, \pi)$.
+The operator $(.)_+$ is the well-known
+(multi-dimensional) \textit{ramp} function.
+
+Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
+  norm}, denoted $\|A\|$, is
+ defined to be the largest \textit{singular value} of $A$, i.e the
+ largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).
+
+\paragraph{\textbf{Convex analysis.}}
+Given a subset $C$ of $\mathbb{R}^n$,
+$i_C$ denotes its \textit{indicator function} defined by
+\begin{eqnarray}
+  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
+    otherwise.}
+\end{eqnarray}
+At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
+etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
+  convex function. The \textit{effective domain} of $f$, denoted
+  $dom(f)$, is defined as
+\begin{eqnarray}
+  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
+\end{eqnarray}
+ If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
+%% \textit{proper convex lower semi-continous function}
+%% (\textit{p.c.l.s.c} for short).
+%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
+%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
+%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
+The \textit{subgradient} of $f$ is the set-valued function
+\begin{eqnarray}
+\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
+\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
+z \in \mathbb{R}^n\}.
+\end{eqnarray}
+Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
+in case $f$ is differentiable at $x$. If $f$ is convex, its
+\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
+\rightarrow \mathbb{R}^n$ defined by
+\begin{eqnarray}
+  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
+  - x\|^2 + f(z).
+\end{eqnarray}
+For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
+$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
+operators generalize orthogonal projectors. One also has the useful
+characterization
+\begin{eqnarray}
+  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
+\end{eqnarray}
+
+The interested reader should refer to \cite{combettes2011proximal} for
+a more elaborate exposition of proximal operators and their
+use in modern convex-optimization.
+
+\subsection{Statement of the problem}
+The sequence-form for two-person zero-sum games was introduced in
+\cite{koller1992complexity}, and the theory was further developed in
+\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
+established that for sequential two-person zero-sum games with
+imcomplete information and perfect recall, there exist sparse matrices
+$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
+  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
+\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
+$l_1$, and $l_2$ are all linear in the size of the game tree (number
+of states in the game) and such that Nash equilibria correspond to
+pairs $(x, y)$ of \textit{realization plans} which solve the primal
+LCP
+\begin{equation}
+  \begin{aligned}
+     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
+       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
+     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
+  \end{aligned}
+  \label{eq:primal_pb}
+\end{equation}
+
+and the dual LCP
+\begin{equation}
+  \begin{aligned}
+    \text{maximize}-\langle e_2, q\rangle,\hspace{.5em}\text{subject
+      to: }(x,q) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2},  x \ge
+    0, E_1x = e_1, A^Tx + E_2^Tq \geq 0.
+  \end{aligned}
+  \label{eq:dual_pb}
+\end{equation}
+The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
+and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
+variables. 
+$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
+entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
+$(1, 0, ..., 0)$. In this so-called \textit{sequence-form}
+representation, the strategy profile of player $k$ is the polyhedron
+\begin{equation}
+  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\}.
+\label{eq:polyhedron}
+\end{equation}
+
+Note that the LCPs above have the equivalent saddle point formulation
+\begin{equation}
+  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
+    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle
+  \label{eq:gilpin}
+\end{equation}
+
+%% Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle
+%% = q_0$ by definition of $e_1$ and
+%% $e_2$. 
+At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
+$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
+by\footnote{The inequality being due to \textit{weak duality}.}
+\begin{equation}
+  0 \le \mathcal{G}(y, p, x, q) := \langle e_1, p\rangle - (\langle
+  e_2, q\rangle) = \langle e_1, p\rangle + \langle
+  e_2, q\rangle = G(x, y),
+  \label{eq:dgap}
+\end{equation}
+where
+\begin{eqnarray}
+G(x, y) :=
+\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
+(u,v) \in Q_1 \times Q_2\}.
+\label{eq:xy_gap}
+\end{eqnarray}
+
+%\subsection{Characterization of equilibria}
+It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
+$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
+LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
+equilibrium for the game)  if and only if there exist vectors $p$ and
+$q$ such that
+\begin{equation}
+\hspace{.25em} -Ay + E_1^Tp \ge 0, \hspace{.5em}A^Tx + E_2^Tq \ge
+0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0, \hspace{.25em}
+\langle y, A^Tx  + E_2^Tq\rangle = 0.
+\label{eq:feasibility}
+\end{equation}
+
+Moreover, at equilibria, \textit{strong duality} holds and the value
+of the game equals $p_0 = -q_0$, i.e the primal-dual gap
+$\mathcal{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at
+equilibria.
+
+%% As usual, the ``minimax'' notation in problem \eqref{eq:primal_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution if (and only if)
+%% \begin{equation}
+%%   x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
+%% \label{eq:nash_ineq}
+%% \end{equation}
+%% Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
+%% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
+
+\begin{remark}  
+It should be noted that for the class of games considered here
+(sequential games with imcomplete information), the LCPs
+\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
+than what state-of-the-art LCP solvers can handle. See
+\cite{hoda2010smoothing}.
+
+\end{remark}
+
+Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
+is impossible in practice \textbf{Cite Koller!!!}, and such a
+precision doesn't have any fundamental advantage. Instead, it is
+customary compute so-called Nash $\epsilon$-equlibria.
+
+\begin{definition}[\textbf{Nash $\epsilon$-equilibria}]
+Given $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
+a pair $(x^*, y^*)$ of realization plans such that there exists dual
+vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
+\eqref{eq:dual_pb} such that the primal-dual gap at $(y^*, p^*, x^*, q^*)$
+doesn't exceed $\epsilon$. That is,
+
+\begin{equation}
+  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon.
+\label{eq:approx_pb}
+\end{equation}
+\label{thm:approx_nash}
+\end{definition}
+
+Let us introduce the notion of $\epsilon$-subgradients
+\cite{he2013accelerating}.
+
+\begin{definition}[$\epsilon$-subgradient]
+Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
+\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
+$\epsilon$-subgradient, for short) of $f$ is the set-valued function
+\begin{eqnarray}
+\partial_\epsilon f: \mathbb{R}^n \rightarrow
+2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
+\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
+\mathbb{R}^n\}.
+\end{eqnarray}
+\end{definition}
+
+The idea behind $\epsilon$-subgradients is the following. Say we wish
+to minimize the function $f$. Replace the usual necessary
+condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
+weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
+small vector $v$''. In fact, it is easy to see that, for each
+point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
+  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
+This approximation concept for subgradients yields the following
+concept of approximate Nash equlibria (adapted from
+\cite{he2013accelerating}).
+
+\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
+Given $\rho > 0$ and $\epsilon > 0$, a Nash
+$(\rho,\epsilon$)-equilibrium for the GSP \eqref{eq:unconstrained_pb}
+is any quadruplet $(x^*, y^*, x^*, q^*)$ for which
+there exists a perturbation vector $v^*$ such that
+\begin{eqnarray}
+\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
+\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
+  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
+\end{eqnarray}
+
+Such a vector $v^*$ is called a Nash $\epsilon$-residual at $(x^*,
+y^*, x^*, q^*)$.
+\label{thm:cool_notion}
+\end{definition}
+
+The above definition is a generalization of the notion of Nash
+equilibria since:
 \begin{itemize}
-\item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$p$ real matrices;
-\item $E^{-1}(U)$: \quad pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
-namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
-\item $A^T$: \quad transpose of a matrix $A$;
-\item $\begin{bmatrix}A\\B\end{bmatrix}$: \quad vertical stacking of two matrices $A$ and $B$;
-\item $v_j$: \quad $j$th component of  a vector $v$;
-\item $u^Tv$: \quad dot product of two vectors $u$ and $v$;
-\item $\mathbb{R}^n_+$: \quad the $n$-dimensional nonnegative orthant;
-\item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
-\item $i_C$: \quad indicator function of a convex set $C$;
-\item $\Pi_C$: \quad euclidean projector onto a convex set $C$;
-\item $\|K\|_2$: \quad matrix 2-norm of a matrix $K$;
-\item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
-\item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
-\item $(1 + \sigma \partial f)^{-1}$: resolvent (a.k.a proximal) operator of a \textit{l.s.c.p.c} function $f$, for a given stepsize $\sigma > 0$
+\item Exact Nash equilibria correspond to Nash $(0^+,0^+)$-equilibria.
+\item Nash $\epsilon$-equilibria (in the sense of Definition
+  \ref{thm:approx_nash}) correspond to Nash $(0^+,\epsilon)$-equilibria.
 \end{itemize}
 
-\subsection{Statement of the problem}
-Consider a two-person sequential game\footnote{In a sequential game, players take turns in play, one after the other,
-as opposed to simultaneous play.} in \textit{sequential-form} (See for example, \cite{von1996efficient}
-and \cite{koller1996efficient} 
-for theory on sequential-form representation), and let $A \in \mathbb{R}^{m,n}$ be our payoff matrix.
-We will be referring to the other player as ``the opponent''. We are interested in the problem of
-finding a best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$, given a fixed
-behavioral strategy $y_0$ for the opponent, where $E$ is a sparse $p$-by-$n$ matrix whose
-entries are $-1$, $0$, or $+1$, and $(1, 0, 0, ..., 0) =: e \in \mathbb{R}^p$. Recall that $E$
-and $e$ encode linear constraints on our ``admissible'' realization plans\footnote{In games
-in sequential form, the terms ``strategy'' and ``realization plan'' mean thesame thing.} $x$,
-in the sequential form representation of the game. In the language of convex-optimization,
-one can readily give the following saddle-point formulation for this problem. Viz,
-
-\begin{equation}
-  \underset{x \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})}{min}\text{ }-y_0^TAx
-  \label{eq:opt_pb}
-\end{equation}
-
-\begin{definition}
-A solution $x^*$ to problem \eqref{eq:opt_pb} is called a \textit{best response} strategy against
-the opponent's fixed strategy $y_0$.
-\end{definition}
-
-\begin{remark}
-Of course $y_0$ is not necessarily an optimal strategy for the opponent. In case it is, the pair $(x^*, y_0)$
-is a Nash equilibrium for the game.
-\end{remark}
-
-\begin{remark}
-  In practice, $A$, $E$, and $F$ are very sparse.
-%% : $A$ will be sparse because a concrete sequential game will
-%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
-%% combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
-%% $E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
-%% zig-zag between only a limited number of the player's information sets so that a move at an information set will
-%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
-This sparsity should be thoroughly exploited\footnote{For example when
-multiplying vectors with these matrices.} by a solver for problem \eqref{eq:opt_pb}.
-\end{remark}
-
-In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}.
-We elaborate our proposed algorithm in section \ref{sec:algo}.
+\subsection{Our contribution}
+We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
+algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\rho,
+  \epsilon$)-equilibria for sequential two-person zero-sum games with
+  imcomplete information and perfect recall.
 
@@
 \label{sec:related_work}
+\textbf{TODO: add note about interior-point methods!!!}
 
-Pending...
+We present a selection of algorithms that is representative of the
+efforts that have been made in the literature to compute Nash
+$\epsilon$-equilibria for two-person zero-sum games with imcomplete
+information like Texas Hold'em Poker, etc.
+
+In \cite{hoda2010smoothing}, a nested iterative procedure using the
+Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used to
+to solve the equilibrium problem \eqref{eq:gilpin}.
+The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
+(which derives from the general EGT theory) for the outer-most
+iteration loop.
+
+\cite{gilpinfirst} proposed a modified verson of the technqiues in
+\cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
+\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in
+terms of the number of calls made to a first-order oracle. Here
+$\delta = \delta(A, E_1, E_2, e_1, e_2) > 0$ is a certain
+\textit{condition number} for the game. The crux of their technique was to
+observe that \eqref{eq:gilpin} can further be written a the minimization of
+the primal-dual gap function $G(x, y)$ (defined in \eqref{eq:xy_gap})
+for the game\footnote{The minimizers of $G$ are precisely the
+  equilibria of the game.}, viz
+\begin{eqnarray}
+\mathrm{maximize}\{G(x,y)|(x,y) \in Q_1 \times Q_2\},
+\end{eqnarray}
+and then show there exists a scalar
+$\delta > 0$ such that for any pair of realization plans $(x, y) \in Q_1 \times Q_2$,
+\begin{eqnarray}
+\text{``distance between }(x, y)\text{ and the set of
+equilibria'' } \le G(x, y)/\delta.
+\end{eqnarray}
+Their
+algorithm is then derived by iteratively applying Nesterov smoothing \cite{nesterov2005a}
+with a geometrically decreasing sequence of tolerance levels
+$\epsilon_{n+1} = \epsilon_n / \gamma$ (with $\gamma > 1$)  $G$. It
+should be noted however that
+\begin{itemize}
+\item[--] The constant $\delta > 0$ can be arbitrarily small, and so
+  the factor $\|A\| / \delta$ in the $\mathcal{O}\left(\left(\|A\| /
+\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate can
+be arbitrarily large.
+\item[--] The reported linear convergence rate is not in terms of
+  basic operations (addition, multiplication, matvec, clipping, etc.),
+  but in terms of the number of calls to a first-order oracle. For
+  example the projections $\proj_{Q_k}$ are applied at each iteration.%%  Of
+  %% course, the existence of a linear algorithm for solving
+  %% \eqref{eq:gilpin} is improbable, as the usual strong-convexity
+  %% conditions are absent.
+
+\end{itemize}
+
+%% It should be noted that the EGT and its precursors have had
+%% considerable success in the signal processing communities, as can
+%% be seen in \cite{NestaCandès, eduard, etc.} and the references
+%% therein.
+
+The primal-dual algorithm first developed in \cite{chambolle2010} was
+proposed \cite{chambolle2014ergodic} in to solve matrix games on
+simplexes. It should be stressed that such matrix games are
+considerably simpler than the games considered here. Indeed, the
+authors in \cite{chambolle2014ergodic} use the fact that computing the
+euclidean projection of a point unto a simplex can be done in linear
+time as in \cite{duchi2008efficient}. In contrast, no such efficient
+algorithm is known nor is likely to exist for the polyhedra $Q_k$
+defined in \eqref{eq:polyhedron}, the strategy profiles for players in
+the games considered here. It should however be noted that such this
+projection can still be done iteratively using, for example, the
+algorithm in proposition 4.2 of \cite{combettes2010dualization}%%  or any
+%% CQ algorithm (since this projection sub-problem, is, in fact a
+%% \textit{split-feasibility problem}), for example
+. Unfortunately, as
+with any nested iterative scheme, one would have to solve this
+sub-problem with finer and finer precision.
+
+Sampling techniques like the CFR (CounterFactual Regret minimization)
+and its many variants
+\cite{MartinZinkevichNIPS2007,lanctot2009monte,Bowling09012015} have
+also become state-of-the-art.
+
+\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
+\label{sec:gsp}
+One cannot directly attack the LCPs \eqref{eq:primal_pb} and
+\eqref{eq:dual_pb} via a traditional primal-dual algorithm
+(for example \cite{chambolle2010,chambolle2014ergodic}) because
+computing the euclidean projections $\proj_{Q_k}$ is very difficult
+(in fact, such subproblems would have to be solved
+iteratively\footnote{An ``exception to the rule'' is the case where
+  the $Q_k's$ are simplexes, so that the projections can be computed
+  exactly using \cite{duchi2008efficient}.}). Also,
+the primal-dual gap might explode even at ``nearly feasible'' points,
+leaving a primal-dual algorithm with no clear on whether progress is
+being made or not. So need to way to
+\begin{itemize}
+\item[--] avoid having to compute the projections $\proj_{Q_k}$,
+\item[--] have control over how far we are from the set of equilibria and
+  avoid infinite (and thus non-informative) primal-dual gaps.
+\end{itemize}
+
+In the next theorem, we show that the said LCP problems can be
+conveniently written as a \textit{Generalized Saddle-point Problem
+  (GSP)} in the sense of \cite{he2013accelerating}.
+\begin{theorem}
+Define two proper closed convex functions
+  \begin{eqnarray}
+    \left.
+    \begin{aligned}
+      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
+      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
+        i_{y \ge 0} + \langle e_1,p\rangle\\
+        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
+        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
+          i_{x \ge 0} + \langle e_2, q\rangle
+    \end{aligned}
+    \right\}
+    \label{eq:things}
+  \end{eqnarray}
+
+Also define two bilinear forms $\Psi_1$, $\Psi_2: \mathbb{R}^{n_2}
+\times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
+\mathbb{R}^{l_2} \rightarrow \mathbb{R}$ with $\Psi_2 = -\Psi_1$ by letting
+  \begin{equation}
+      K :=
+      \left[
+        \begin{array}{cc}
+          A & -E_1^T \\
+          E_2 & 0
+        \end{array}
+        \right],\hspace{.5em}
+    \Psi_1(y, p, x, q)
+    := \left\langle \begin{bmatrix}x\\q\end{bmatrix},
+      K\begin{bmatrix}y\\p\end{bmatrix}\right\rangle = \langle x,
+      Ay\rangle -\langle x, E_1^Tp\rangle + \langle q, E_2y\rangle,
+\end{equation}
+
+and, define the functions $\hat{\Psi}_1$, $\hat{\Psi}_2:
+\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}
+\times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ by
+\begin{eqnarray}
+  \left.
+  \begin{aligned}
+    \hat{\Psi}_1(y, p, x, q) &:=
+    \Psi_1(y, p, x, q)+ g_1(y, p) \text{ if }y \ge 0, \hat{\Psi}_1(y,
+    p, x, q) := \infty \text{ otherwise}\\
+    \hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(x, q) \text{ if
+    }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ otherwise}.
+  \end{aligned}
+  \right\}
+\end{eqnarray}
+
+Finally, define the sets $S_1 := \mathbb{R}^{n_2}_+ \times \mathbb{R}^{l_1}$ and $S_2 :=
+\mathbb{R}^{n_1}_+ \times \mathbb{R}^{l_2}$ and consider the
+GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$): Find a quadruplet $(y^*,p^*, x^*, q^*) \in
+S_1 \times S_2$ such that
+\begin{eqnarray}
+    \hat{\Psi}_1(y^*, p^*, x^*, q^*) \le \hat{\Psi}_1(y, p, x^*,
+    q^*) \text{ and }\hat{\Psi}_2(y^*, p^*, x^*, q^*)
+    \le \hat{\Psi}_2(y^*, p^*, x, q) \forall (y,p, x, q) \in S_1
+    \times S_2.
+  \label{eq:unconstrained_pb}
+\end{eqnarray}
+\label{thm:pd}
+
+Then a quadruplet $(y^*,p^*, x^*, q^*) \in \mathbb{R}^{n_2}
+  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
+  \mathbb{R}^{l_2}$ solves the Nash equilibrium LCPs
+  \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff it solves
+  GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
+  \label{thm:pd}
+\end{theorem}
+
+\begin{proof}
+Note that $dom(g_1) = S_1$ and $dom(g_2) = S_2$ and observe that since the
+equilibria of the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb}, and
+the equilibria of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$) are contained
+in $S_1 \times S_2$, it suffices to show that at any point $(y, p, x,
+q) \in S_1 \times S_2$, the primal-dual gap between the primal
+LCP \eqref{eq:primal_pb} and the dual LCP \eqref{eq:dual_pb} equals
+the primal-dual gap of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
+Indeed, the unconstrained objective in \eqref{eq:primal_pb}, say
+$a(x,y)$, can be computed as
+\begin{eqnarray*}
+  \begin{aligned}
+    a(y,p) &= \langle e_1,p\rangle + i_{y\ge 0} + i_{-Ay + E_1^Tp \ge 0} +
+    i_{E_2y = e_2}\\
+    &= g_1(y,p) + \underset{x' \geq
+      0}{\text{max}}\text{ }\langle x',Ay - E_1^Tp\rangle +
+    \underset{q'}{\text{max}}\text{ }\langle q',E_2y - e_2\rangle\\
+    &= g_1(y,p) + \underset{x',
+      q'}{\text{max}}\text{ }\langle x',Ay\rangle - \langle x',
+    E_1^Tp\rangle + \langle q',E_2y\rangle -
+    (i_{x' \ge 0} + \langle e_2,q\rangle)\\
+    &= g_1(y,p)
+      - \underset{x',q'}{\text{min}}\text{ }\Psi_2(y, p, x', q') + g_2(x',
+      q') = g_1(y,p)
+      - \underbrace{\underset{x',q'}{\text{min}}\text{
+        }\hat{\Psi}_2(y, p, x', q')}_{\phi_2(y,p)},
+  \end{aligned}
+  \label{eq:a}
+\end{eqnarray*}
+
+Similarly, the unconstrained objective, say
+$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
+\begin{eqnarray*}
+  \begin{aligned}
+ b(x, q) &= 
+-\langle q, e_2\rangle -i_{x \ge 0} - i_{A^Tx+E_2^Tq \ge 0} -
+ i_{E_1x = e_1}\\
+ &= -g_2(x, q) + \underset{y' \geq
+   0}{\text{min}}\text{ }\langle y', A^Tx + E_2^Tq\rangle +
+ \underset{p'}{\text{min}}\text{ }\langle p', e_1-E_1x\rangle\\
+    &= -g_2(x, q)
+ +\underset{y',p'}{\text{min}}\text{ }\Psi_1(y', p', x, q) +
+ g_1(y', p') = -g_2(x, q)
+ +\underbrace{\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p',
+   x, q)}_{\phi_1(x, q)}.
+   \end{aligned}
+\end{eqnarray*}
+Thus, noting that $-\infty \le \phi_1(x, q), \phi_2(y, p), < +\infty$,
+one computes the primal-dual gap between the primal LCP
+\eqref{eq:primal_pb} and dual the LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
+\begin{eqnarray*}
+  \begin{split}
+  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
+  q) \\
+  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
+  q) + g_2(x, q) - \phi_1(x, q)\\
+  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
+  q) - \phi_2(y, p)\\
+  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
+  g_1, g_2) \text{ at }(y, p, x, q),
+  \end{split}
+\end{eqnarray*}
+where the second equality follows from the fact that $\Psi_1 + \Psi_2
+:= 0$.
+\end{proof}
+
+By Theorem \ref{thm:pd}, solviing for a Nash equilibrium for
+the game is equivalent to solving the GSP
+\eqref{eq:unconstrained_pb}, which as it turns out, is simpler
+conceptually. The rest of the paper will be devoted to
+developing an algorithm for solving the latter.
+
+% \subsection{The proposed algorithm and its $\mathcal{O}(1/\epsilon)$
+% convergence}
 
@@
 \label{sec:algo}
-In this section we present the algorithm which is the purpose of this paper, namely an algorithm
-for solving \eqref{eq:opt_pb}. Our algorithm (Alg.\ref{Tab:algo}) is a use-case of
-the generic primal-dual algorithm of A. Chambolle and T. Pock, namely Algorithm 1 of \cite{chambolle2010}.
+We now derive the algorithm derive the algorithm which is the main object of
+this manuscript.
 
-\subsection{Derivation of the algorithm}
-First observe that (1) can be re-written in the form:
-\begin{equation}
-  \underset{x \in \mathbb{R}^n}{min}\text{ }{f(-Ax) + g(x)}
-\end{equation}
-where:\\
-\begin{equation}
-  \left.
-  \begin{aligned}
-    g := i_{E^{-1}(\{e\})} + i_{\mathbb{R}_{+}^m}\\
-    f: z \mapsto y_0^Tz
-    \end{aligned}
-  \right\}
-\end{equation}
-
-Finally, the primal-dual formulation of this problem (which can be easily obtained using
-\textit{Fenchel-Rockafellar duality}, for example) is:
-\begin{equation}
-  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m}{max}\text{ }{y^T(-A)x_0 + g(x) - f^*(y)}
-\end{equation}
-
-Now, let's observe that $i_{E^{-1}(\{e\})}(x) = \underset{\zeta \in \mathbb{R}^p}{max}\text{ }\zeta^T(e - Ex)$, and so one can re-write (2) as:
-\begin{equation}
-  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m, \zeta \in \mathbb{R}^p}{max}\text{ }
-  \begin{bmatrix}y\\\zeta\end{bmatrix}^TKx + G(x) - F^*(y, \zeta)
-  \label{eq:pd_opt}
-\end{equation}
-where we've defined:
-\begin{equation}
-  \left.
-  \begin{aligned}
-    K := -\begin{bmatrix}A\\E\end{bmatrix}\\
-    G := g - i_{E^{-1}(\{b\})} = i_{\mathbb{R}_{+}^n}\\
-    F^*: (y, \zeta) \mapsto (f^*(y) - \zeta^Te) = (i_{\{y_0\}}(y) - e^T\zeta)
-  \end{aligned}
-  \right\}
-\end{equation}
-
-Furthermore, one easily checks that $F^*$ and $G$ are \textit{l.s.c.p.c} with resolvent
-(a.k.a \textit{proximity}) operators given by the simple formulae:
-\begin{equation}
-  \left.
-  \begin{aligned}
-    (1 + \tau \partial G)^{-1} = \Pi_{\mathbb{R}_+^n}: x \mapsto (x)_+\\
-    (1 + \sigma \partial F^*)^{-1}: (y, \zeta) \mapsto (y_0, \zeta + \sigma e)
-  \end{aligned}
-  \right\}
-\end{equation}
-
-Using these ingredients, we derive the primal-dual algorithm given in Alg.\ref{Tab:algo}, 
-for solving \eqref{eq:pd_opt}, and thus \eqref{eq:opt_pb}.
-
-\begin{remark}
-Equation \eqref{eq:pd_opt} is in the form of equation (2) in \cite{chambolle2010} if we take $X := \mathbb{R}^n$ and
-$Y := \mathbb{R}^m \times \mathbb{R}^p$.
-\end{remark}
-
-\begin{remark}
-Neither $G$ nor $F^*$ is strongly convex and so Alg.\ref{Tab:algo} cannot be accelerated in the sense of algorithm 39 of \cite{chambolle2010}.
-\end{remark}
-
-\begin{algorithm}[htb]
-  \caption{Primal-dual algorithm for computing best response against opponent's fixed realization plan $y_0$}
-  \textbf{Given} Tolerance $\epsilon > 0$.\\
-  \textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
-  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
-  \textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
-  \Repeat{
-    $\frac{\|x^{(k+1)} - x^{(k)}\|^2_2}{2\tau} + \frac{\|\zeta^{(k+1)} - \zeta^{(k)}\|^2_2}{2\sigma} < \epsilon$}{
-    \begin{eqnarray*}
-      \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
-      x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
-      \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
-      k &\leftarrow& k + 1
-    \end{eqnarray*}
-  } \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
+\subsection{Algorithm and convergence rate}
+\begin{algorithm}
+\caption{Primal-dual algorithm for computing approximate Nash
+  Equilbria in two-person zero-sum games with imcomplete information
+  and perfect recall}
 \label{Tab:algo}
+\begin{algorithmic}[1]
+\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
+\in \mathbb{R}^{n_2}
+  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
+  \mathbb{R}^{l_2}$.
+\Ensure A Nash $(\rho, \epsilon)$-equilibrium
+$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
+the GSP \eqref{eq:unconstrained_pb}.
+\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
+\leftarrow 0$
+\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \epsilon$ or
+  $\|{v}_{a}^{(k)}\|/k \ge \rho$}
+\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
+E_2^Tq^{(k)}))_+$, \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
+\lambda(e_1-E_1x^{(k)})$
+\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
+E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
+x^{(k+1)}-x^{(k)}$
+\State $\Delta q^{(k+1)} \leftarrow \lambda (E_2y -
+e_2)$, \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
+\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
++ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
+y^{(k+1)}-y^{(k)}$
+\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
+\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
+\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
+\frac{1}{\lambda}(\Delta
+y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
+\State $k \leftarrow k + 1$
+\EndWhile
+\end{algorithmic}
 \end{algorithm}
 
-\subsection{Convergence analysis of the algorithm}
-Pending...
+\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
+Let $d_0$ be the euclidean distance between the starting point
+$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the
+set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
+Then given any $\epsilon > 0$ and $\rho > 0$, there exists an index
+$k_0 \le 2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ such that the following
+error bounds hold:
+\begin{eqnarray}
+\|\tilde{v}_a^{k_0}\| \le \rho \text{ and }
+\|\tilde{\epsilon}_a^{k_0}\| \le \epsilon
+\end{eqnarray}
 
-\begin{remark}
-The derivation above reveals that in equation \eqref{eq:opt_pb} above, if the constraint ``$x \ge 0$'' is replaced by
-a constraint ``$x \in C$'' (thus obtaining a new problem) where $C$ is a convex set
-%% onto which euclidean projections
-%% can be easily computed (for example, a probability simplex)
-, then we simply need to replace the operator ``$(.)_+$''
-with ``$\Pi_C$'' in the equations to obtain a corresponding algorithm. Of course, this is because $i_C^* = \Pi_C$.
-\end{remark}
+where $\tilde{v}_a^{(k_0)} := v_a^{(k_0)}/k_0$.
+Thus Algorithm \ref{Tab:algo} outputs an $(\rho,\epsilon)$-Nash
+equilibrium for the GSP \eqref{eq:unconstrained_pb}
+in at most $2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ iterations.
+\end{theorem}
+
+\begin{proof}
+It is clear to see that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$
+satisfies assumptions B.1, B.2, B.3, B.5, and B.6 of
+\cite{he2013accelerating} with $L_{xx} = L_{yy} = 0$ and $L_{xy} =
+L_{yx} = \|K\|$. Now, one easily computes the proximal operators $g_1$
+and $g_2$ as
+\begin{eqnarray*}
+  \prox_{\lambda g_1}(y, p) \equiv ((y)_+, p - \lambda
+  e_1),\hspace{.5em} \prox_{\lambda g_2}(x, q) \equiv ((x)_+, q -
+  \lambda e_2).
+  \end{eqnarray*}
+
+Algorithm \ref{Tab:algo} is then obtained from \cite[Algorithm
+  T-BD]{he2013accelerating}, applied on the GSP
+\eqref{eq:unconstrained_pb} with the choice of parameters: $\sigma = 1
+\in (0, 1]$, $\sigma_x = \sigma_y = 0 \in [0, \sigma)$,
+    $\lambda_{xy} := \frac{1}{\sigma L_{xy}}\sqrt{(\sigma^2 -
+        \sigma_x^2)(\sigma^2 - \sigma_y^2)} = \sigma / \|K\| =
+      1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
+      \lambda_{xy}]$. The convergence result follows immediately from
+  \cite[Theorem 4.2]{he2013accelerating}.
+\end{proof}
+
+\subsection{Practical considerations}
+\paragraph{\textbf{Efficient computation of $Ay$ and $A^Tx$.}}
+In Algorithms \ref{Tab:algo} most of the time is spent
+pre-multiplying vectors by $A$ and $A^T$. For \textit{flop}-type Poker
+games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
+$A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
+but has a rich block-diagnoal structure which can be carefully
+exploited, as was done in \cite{hoda2010smoothing}.
+
+%% \begin{definition}(Kronecker product)
+%% Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
+%%   s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
+
+%% \begin{equation}
+%% F \otimes B:=\left[
+%% \begin{array}{cccc}
+%% F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
+%% F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
+%% \vdots & \vdots & \ddots & \vdots\\
+%% F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
+%% \end{array}\right] \in \mathbb{R}^{mr \times ns}
+%% \end{equation}
+%% \end{definition}
+
+%% One notes that $(F \otimes B)^T = F^T \otimes B^T$.
+%% $F \otimes B$ can be very much larger than both $F$ and $B$ in
+%% dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
+%% $B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
+%% $10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
+%% \mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
+%% without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
+%% rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
+%%   ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
+%% $s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
+%% as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
+%% easily verfies that $Y$ is the matrix product of the ``small''
+%% matrices $B$, $X$, and $F^T$, i.e
+
+%% \begin{equation}
+%%   \label{eq:kron_matvec}
+%%   Y = BXF^T
+%% \end{equation}
+
+%% Now, in Texas Hold'em for example, the payoff matrix $A$ can be
+%% written as block-diagonal matrix whose blocks are sums of Kronecker
+%% products of much smaller sparse matrices as follows
+
+%% \begin{equation}
+%%   A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
+%%     \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
+%%     B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
+%% \label{eq:factor_A}
+%% \end{equation}
+%% See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
+%% sequences of moves in round $i$ which end in a \textit{fold} action,
+%% and $S$ to the sequences which end in a \textit{showdown}. $B_i$
+%% encodes the betting structure of round $i$, while $W$ encodes the
+%% wind/lose/draw information determined by ranking the players' hands at
+%% showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
+%% enough to be explictly represented whereas it is infeasible to
+%% explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
+%% $S$, and $W$ are themselves sparse, which allows one to use the
+%% compressed row storage data structure that only stores nonzero entries
+%% (for example \textit{scipy.sparse.csr\_matrix}, in the Python
+%% programming language).
+
+%% Such a representation of the payoff matrix $A$ trivializes matvec
+%% operations involving $A$ or $A^T$ (thanks to formula
+%% \eqref{eq:kron_matvec} above, applied to their diagonal blocks and
+%% exploiting the sparsity of these blocks themselves). Of course, one
+%% can always write the payoff matrix $A$ of a flop-type Poker game in a
+%% form similary to \eqref{eq:factor_A} by applying appropriate
+%% permutations to the enumeration of the players's sequences.
+
+\paragraph{\textbf{Computing $\|K\|$.}} Power iteration (Perron-Frobenius)...
+
+\section{Experimantal results}
+\label{sec:results}
+To access the practical quality of the proposed algorithm, we
+experimented it on real and simulated matrix games.
+
+\begin{figure}[!htpb]
+  \subfigure[Matrix game on simplices]{
+    \includegraphics[width=.33\linewidth]{simplex_dgap.pdf}
+  }
+  \hspace{-2em}
+  \subfigure[Toy Poker]{
+    \includegraphics[width=.33\linewidth]{SimplifiedPoker_dgap.pdf}
+  }
+  \hspace{-2em}
+  \subfigure[Kuhn 3-card Poker]{
+    \includegraphics[width=.33\linewidth]{Kuhn3112_dgap.pdf}
+  }
+  \vspace{-1em}
+  \hspace{-1em}
+  \includegraphics[width=.34\linewidth]{simplex_NE.pdf}
+  \hspace{-1em}
+  \includegraphics[width=.33\linewidth]{SimplifiedPoker_NE.pdf}
+  \hspace{-1em}
+  \includegraphics[width=.33\linewidth]{Kuhn3112_NE.pdf}
+  \caption{Convergence curves of Algorithm
+    \ref{Tab:algo}. \textbf{Top row}: Evolution of ergodic
+    primal-dual gap. \textbf{Bottom row}: Evolution of
+    value of game.}
+  \label{Tab:dgap_curve}
+\end{figure}
+
+\paragraph{\textbf{Matrix game on simplexes.}}
+Any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a
+\textit{matrix game}. The strategy profile of player $k$ is a simplex;
+this simplex can be written in the form \eqref{eq:polyhedron} by
+taking $E_k := [1, 1, ..., 1] \in \mathbb{R}^{1 \times n_k}$ and $e_k
+= 1$. Thus every matrix game on simplexes can be seen as a sequential
+game. Now, as in \textbf{nesterov, c-p, etc.}, we generate a $1000
+\times 1000$ random matrix whose entries are uniformly identically
+distributed in the closed interval $[-1, 1]$.
+
+\paragraph{\textbf{Toy Poker game.}}
+The sequence-form representation for this Toy Poker game is given by
+(showing only nonzero entries):\\
+
+$E_1 \in \mathbb{R}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
+E_1(1,2) = E_1(2,3) = E_1(2,4) = {1}$,
+$E_1(1,0) = E_1(2,0) = {-1}$; \\
+
+$E_2 \in \mathbb{R}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
+= E_2(2,3) = E_2(2,4) = {1}$, $E_2(1,0) = E_2(2,0) =
+{-1}$; and \\
+
+$A \in \mathbb{R}^{5 \times 5}$ with $A(2,0) =
+A(4,0) = {-0.5}$, $A(1,3) = {1}$, $A(3,1) =
+{-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = {0.25}$.
+
+\paragraph{{Kuhn 3-card Poker.}}
+The game has $n_1 = n_2 = 13$ and $l_1 = l_2 = 7$, and its
+sequence-form is given by:\\
+
+$E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
+E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
+E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
+E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
+E_1(5,5) = E_1(6,9) = {-1}$; \\
+
+ $E_2 \in \mathbb{R}^{7 \times 13}$ with
+$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
+E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
+E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
+E_2(5,0) = E_2(6,0) = {-1}$; and \\
+
+ $A \in \mathbb{R}^{13 \times
+  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
+{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
+A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
+A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
+$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
+A(12,1) = A(12,5) = {0.166667}$.\\
+
+The pair $(x^*, y^*) \in \mathbb{R}^{13} \times \mathbb{R}^{13}$ of
+realization plans given by
+
+\begin{eqnarray*}
+  \begin{split}
+    x^* &= [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0,
+      0.275, 0.725]^T,\\
+    y^* &= [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T
+    \end{split}
+\end{eqnarray*}
+is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of
+Algorithm  \ref{Tab:algo}. The convergence curves are shown
+in Fig \ref{Tab:dgap_curve}. One easy checks that this equilibrium is
+feasible. Indeed,
+
+\begin{eqnarray*}
+  \begin{split}
+    E_1x^* - e_1 = [&4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67
+      \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, \\&
+      -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T
+    \end{split}
+\end{eqnarray*}
+and
+
+\begin{eqnarray*}
+  \begin{split}
+    E_2y^* - e_2 = [&-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29
+      \times 10^{-6}, -1.50 \times 10^{-6},\\
+      &2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times
+      10^{-7}]^T
+    \end{split}
+\end{eqnarray*}
+Finally, one checks that
+\begin{eqnarray*}
+  {x^*}^TAy^* = {-0.05555},
+\end{eqnarray*}
+ which agrees to 5 d.p with the value of $-1 / 18$ computed
+ analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. The
+ evolution of the dual gap and the expected value of the game across
+ iterations are shown in Figure \ref{Tab:dgap_curve}.
+
+\section{Conclusion}
+Making use of the sequence-form representation
+\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
+deviced a primal-dual algorithm for computing Nash equilibria in
+two-person zero-sum sequential games with imcomplete information (like
+Texas Hold'em, etc.). Our algorithm is simple to implement, with a
+very low constant cost per iteration, and enjoys a rigorous
+convergence theory with a proven $\mathcal{O}(1/min(\rho,\epsilon))$ convergence
+in terms of basic operations (matvec products, clipping, etc.), to a
+Nash $(\rho,\epsilon)$-equilibrium of the game.
+
+Equilibrium problems are saddle-point convex-concave problems, and as
+such a natural choice for algorithms for solving them would be in the
+family of primal-dual algorithms. The author believes such primal-dual
+schemes will receive more attention in the algorithmic game theory
+community in future.
 
 \medskip \noindent
-\textbf{Acknowledgments:}
-Pending...
+%% \paragraph{About the author:} I'm a first-year PhD student in Computer Science at Universit\'e de Parix XI.
+My thesis focuses on novel techniques for optimization on Lie groups (of diffeomorphisms), and other structured manifolds, the aim being to obtain better algorithms for nonlinear registration of fMRI brain images and enhance the charting of human functional connectomes.
 
-% ==========
-% = biblio =
-% ==========
-% {\small
-\bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv.bib,agt.bib}
+\small
+\bibliographystyle{llcns2e/splncs03}
+\bibliography{bib}
+
 \end{document}
-
-%
-%

### 2015-07-10 paper_old.tex
refactors + fixups + some XXX removal

\documentclass[a4paper,9pt,journal]{IEEEtran}
\usepackage{graphicx} \usepackage[cmex10]{amsmath}
\usepackage{amssymb} \usepackage{fancybox} \usepackage{alltt}
\usepackage{soul} \usepackage{color} \usepackage{verbatim}
\usepackage{xcolor} \usepackage{colortbl,hhline}
\usepackage[ruled,vlined]{algorithm2e} \usepackage{framed}
\usepackage{amsthm} \usepackage{fancyref}
\usepackage{amsmath,amsfonts,amssymb, amsthm} \usepackage{textcomp}

\newtheorem{remark}{Remark}

\def \lb {{\langle}} \def \rb {{\rangle}}
\newcommand{\fro}[1]{\|#1\|_2}
\newcommand{\theHalgorithm}{\arabic{algorithm}}

\newcommand{\argmin}{\mathop{\mathrm{argmin}}}

\usepackage{hyperref}

\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}

\newcommand{\prox}{\textrm{pr ox} } \newcommand{\grad}{\textrm{grad} }
\newcommand{\dive}{\textrm{div} }

\pagenumbering{gobble}

\begin{document}
\onecolumn
\title{Computing Nash equilibria and best response strategies in two-person zero-sum sequential games}

\author{\IEEEauthorblockN{Elvis D. DOHMATOB}}

\maketitle

\begin{abstract}
% LESS THAN 200 WORDS !!!!!
% 
% While medical imaging typically provides massive amounts of
% data, the extraction of relevant information in a given
% applicative context remains a difficult challenge.
% XXX : don't call it SPM but just "predictive regions or predictive
% maps"
In this manuscript, we consider the problem of computing a best response against an opponent's realization plan in two-person sequential games.
The proposed algorithm for solving the corresponding contrained convex-optimization problem, derives from the primal-dual scheme of A. Chambolle and T. Pock.
Our algorithm is simple: all resolvent operators can be effectively computed in closed-form, using only elementary algebraic operations.
%%  and is orders of magnitude more efficient than state-of-the-art algorithms like those based on Linear Programming, Interior-Point methods,
%% and more recently, the Nesterov Excessive Gap Technique.
% By way of example, we conclude by exhibiting results on Texas Hold'em Poker.
\end{abstract}

\begin{IEEEkeywords}
  game theory; two-person sequential game; Nash equilibria; best response; convex-optimization; contraint; primal-dual scheme
\end{IEEEkeywords}

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,
\begin{itemize}
\item $\mathcal{P}(S)$: \quad set of all the subsets of $S$;
\item $\mathcal{P}_k(S)$: \quad set of all the subsets of $S$ which have exactly $k$ elements;
\item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$p$ real matrices;
\item $E^{-1}(U)$: \quad pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$;
\item $A^T$: \quad transpose of a matrix $A$;
\item $\begin{bmatrix}A\\B\end{bmatrix}$: \quad vertical stacking of two matrices $A$ and $B$;
\item $v_j$: \quad $j$th component of  a vector $v$;
\item $u^Tv$: \quad dot product of two vectors $u$ and $v$;
\item $\mathbb{R}^n_+$: \quad the $n$-dimensional nonnegative orthant;
\item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
\item $i_C$: \quad indicator function of a convex set $C$;
\item $\Pi_C$: \quad euclidean projector onto a convex set $C$;
\item $\|K\|_2$: \quad matrix 2-norm of a matrix $K$;
\item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
\item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
\item $(1 + \sigma \partial f)^{-1}$: resolvent (a.k.a proximal) operator of a \textit{l.s.c.p.c} function $f$, for a given stepsize $\sigma > 0$
\end{itemize}

\subsection{Generating the Texas Hold'em Poker game tree}
Let $a := (a_1, a_2, a_3, a_4) \in 
\mathbb{R}\times\mathbb{R}\times\mathbb{R}^2\times\mathbb{R}^2$ hold the accounting info, where:
\begin{itemize}
\item $a_1\in\mathbb{R}$ is the running bet size,
\item $a_2\in\mathbb{R}$ is the running total amount in the pot,
\item $a_3\in\mathbb{R}^2$ is a vector showing what each player has put into the pot sofar, and
\item $a_4\in\mathbb{R}^2$ is a vector showing running capital of each player.
\end{itemize}
Let $ok(a, L)$ be a flag which is true iff the bet size $a_1$ has not exceeded the limit $L$ and each player's running credit is nonnegative.
For any round $t\in\mathbb{N}$, let $p(t)$ be the player to begin and $\Sigma(t)$ be the set of all signals that can be emitted by the chance player.
\definition{
A signal is simply any part of the information needed at shutdown to score the player's hands.
}
\remark{
An emitted signal can be fully observable (for example, community cards), or only partially observable (for example when private / hole / pocket cards are delt, players can only see their own hole cards given to them; they can't see another player's hole cards).
}

\begin{equation}
  \gamma(t, T, a, L) = \begin{cases} 
    \mathcal{P}_1(\Sigma(t)), &\mbox{if } (t < T) \land ok(a, L) \land (p(t) = 0);\\
            {\{\textbf{F}_{p(t)}\} \cup \textbf{C}_{p(t)}\gamma(t + 1, T, a, L) \cup \textbf{K}_{p(t)}\lambda(t, T, g(a, \textbf{K}_{p(t)}), L)},&\mbox{if } (t < T) \land ok(a, L) \land (p(t) > 0);\\
            \emptyset, &\mbox{if } t \ge T \lor \neg ok(a, L) .\end{cases}
\end{equation}
where the auxiliary function $\lambda$ is defined by:
\begin{equation}
  \left.
  \begin{aligned}
    \lambda(t, T, a, L) := \cup_{n=0}^\infty\alpha_1^{(n)}(t, T, a, L) \cup \cup_{n=0}^\infty\alpha_2^{(n)}(t, T, a, L)\\
    \alpha_1^{(n)}(t, T, a, L) := (\textbf{R}_{p(t)'}\textbf{R}_{p(t)})^n\mathcal{P}_1(\{\textbf{F}_{p(t)'}, \textbf{K}_{p(t)'}\})\gamma(t + 1, T, g(a, (\textbf{R}_{p(t)'}\textbf{R}_{p(t)})^n\mathcal{P}_1(\{\textbf{F}_{p(t)'}, \textbf{K}_{p(t)'}\})), L)\\
    \alpha_2^{(n)}(t, T, a, L) := (\textbf{R}_{p(t)'}\textbf{R}_{p(t)})^n\textbf{R}_{p(t)'}\mathcal{P}_1(\{\textbf{F}_{p(t)}, \textbf{K}_{p(t)}\})\gamma(t + 1, T, g(a, (\textbf{R}_{p(t)'}\textbf{R}_{p(t)})^n\textbf{R}_{p(t)'}\mathcal{P}_1(\{\textbf{F}_{p(t)}, \textbf{K}_{p(t)}\})), L)
    %% \lambda_{1}(t, T, a, L) := \cup_{n=0}^\infty\alpha_1^{(n)}(t, T, a, L)\\
    %% \lambda_{2}(t, T, a) := \cup_{n=0}^\infty\\
    \end{aligned}
  \right\}
\end{equation}

\subsection{Statement of the problem}
Consider a two-person sequential game\footnote{In a sequential game, players take turns in play, one after the other,
as opposed to simultaneous play.} in \textit{sequential-form} (See for example, \cite{von1996efficient}
and \cite{koller1996efficient} 
for theory on sequential-form representation), and let $A \in \mathbb{R}^{m,n}$ be our payoff matrix.
We will be referring to the other player as ``the opponent''. We are interested in the problem of
finding a best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$, given a fixed
behavioral strategy $y_0$ for the opponent, where $E$ is a sparse $p$-by-$n$ matrix whose
entries are $-1$, $0$, or $+1$, and $(1, 0, 0, ..., 0) =: e \in \mathbb{R}^p$. Recall that $E$
and $e$ encode linear constraints on our ``admissible'' realization plans\footnote{In games
in sequential form, the terms ``strategy'' and ``realization plan'' mean thesame thing.} $x$,
in the sequential form representation of the game. In the language of convex-optimization,
one can readily give the following saddle-point formulation for this problem. Viz,

\begin{equation}
  \underset{x \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})}{min}\text{ }-y_0^TAx
  \label{eq:opt_pb}
\end{equation}

\begin{definition}
A solution $x^*$ to problem \eqref{eq:opt_pb} is called a \textit{best response} strategy against
the opponent's fixed strategy $y_0$.
\end{definition}

\begin{remark}
Of course $y_0$ is not necessarily an optimal strategy for the opponent. In case it is, the pair $(x^*, y_0)$
is a Nash equilibrium for the game.
\end{remark}

\begin{remark}
  In practice, $A$, $E$, and $F$ are very sparse.
%% : $A$ will be sparse because a concrete sequential game will
%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
%% combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
%% $E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
%% zig-zag between only a limited number of the player's information sets so that a move at an information set will
%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
This sparsity should be thoroughly exploited\footnote{For example when
multiplying vectors with these matrices.} by a solver for problem \eqref{eq:opt_pb}.
\end{remark}

In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}.
We elaborate our proposed algorithm in section \ref{sec:algo}.

\section{Related work}
\label{sec:related_work}

Pending...

\section{The proposed algorithm}
\label{sec:algo}
In this section we present the algorithm which is the purpose of this paper, namely an algorithm
for solving \eqref{eq:opt_pb}. Our algorithm (Alg.\ref{Tab:algo}) is a use-case of
the generic primal-dual algorithm of A. Chambolle and T. Pock, namely Algorithm 1 of \cite{chambolle2010}.

\subsection{Derivation of the algorithm}
First observe that (1) can be re-written in the form:
\begin{equation}
  \underset{x \in \mathbb{R}^n}{min}\text{ }{f(-Ax) + g(x)}
\end{equation}
where:\\
\begin{equation}
  \left.
  \begin{aligned}
    g := i_{E^{-1}(\{e\})} + i_{\mathbb{R}_{+}^m}\\
    f: z \mapsto y_0^Tz
    \end{aligned}
  \right\}
\end{equation}

Finally, the primal-dual formulation of this problem (which can be easily obtained using
\textit{Fenchel-Rockafellar duality}, for example) is:
\begin{equation}
  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m}{max}\text{ }{y^T(-A)x_0 + g(x) - f^*(y)}
\end{equation}

Now, let's observe that $i_{E^{-1}(\{e\})}(x) = \underset{\zeta \in \mathbb{R}^p}{max}\text{ }\zeta^T(e - Ex)$, and so one can re-write (2) as:
\begin{equation}
  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m, \zeta \in \mathbb{R}^p}{max}\text{ }
  \begin{bmatrix}y\\\zeta\end{bmatrix}^TKx + G(x) - F^*(y, \zeta)
  \label{eq:pd_opt}
\end{equation}
where we've defined:
\begin{equation}
  \left.
  \begin{aligned}
    K := -\begin{bmatrix}A\\E\end{bmatrix}\\
    G := g - i_{E^{-1}(\{b\})} = i_{\mathbb{R}_{+}^n}\\
    F^*: (y, \zeta) \mapsto (f^*(y) - \zeta^Te) = (i_{\{y_0\}}(y) - e^T\zeta)
  \end{aligned}
  \right\}
\end{equation}

Furthermore, one easily checks that $F^*$ and $G$ are \textit{l.s.c.p.c} with resolvent
(a.k.a \textit{proximity}) operators given by the simple formulae:
\begin{equation}
  \left.
  \begin{aligned}
    (1 + \tau \partial G)^{-1} = \Pi_{\mathbb{R}_+^n}: x \mapsto (x)_+\\
    (1 + \sigma \partial F^*)^{-1}: (y, \zeta) \mapsto (y_0, \zeta + \sigma e)
  \end{aligned}
  \right\}
\end{equation}

Using these ingredients, we derive the primal-dual algorithm given in Alg.\ref{Tab:algo}, 
for solving \eqref{eq:pd_opt}, and thus \eqref{eq:opt_pb}.

\begin{remark}
Equation \eqref{eq:pd_opt} is in the form of equation (2) in \cite{chambolle2010} if we take $X := \mathbb{R}^n$ and
$Y := \mathbb{R}^m \times \mathbb{R}^p$.
\end{remark}

\begin{remark}
Neither $G$ nor $F^*$ is strongly convex and so Alg.\ref{Tab:algo} cannot be accelerated in the sense of algorithm 39 of \cite{chambolle2010}.
\end{remark}

\begin{algorithm}[htb]
  \caption{Primal-dual algorithm for computing best response against opponent's fixed realization plan $y_0$}
  \textbf{Given} Tolerance $\epsilon > 0$.\\
  \textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
  \textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
  \Repeat{
    $\frac{\|x^{(k+1)} - x^{(k)}\|^2_2}{2\tau} + \frac{\|\zeta^{(k+1)} - \zeta^{(k)}\|^2_2}{2\sigma} < \epsilon$}{
    \begin{eqnarray*}
      \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
      x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
      \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
      k &\leftarrow& k + 1
    \end{eqnarray*}
  } \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
  \label{Tab:algo}
\end{algorithm}

\subsection{Convergence analysis of the algorithm}
Pending...

\begin{remark}
The derivation above reveals that in equation \eqref{eq:opt_pb} above, if the constraint ``$x \ge 0$'' is replaced by
a constraint ``$x \in C$'' (thus obtaining a new problem) where $C$ is a convex set
%% onto which euclidean projections
%% can be easily computed (for example, a probability simplex)
, then we simply need to replace the operator ``$(.)_+$''
with ``$\Pi_C$'' in the equations to obtain a corresponding algorithm. Of course, this is because $i_C^* = \Pi_C$.
\end{remark}

\medskip \noindent
\textbf{Acknowledgments:}
Pending...

% ==========
% = biblio =
% ==========
% {\small
\bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv.bib,agt.bib}
\end{document}

%
%

### 2015-07-10 simple.py

@@ -9,6 +9,8 @@ from sklearn.utils import check_random_state
 from sequence_form import Game
 from primal_dual import primal_dual_ne, primal_dual_sg_ne
 
+RNG = np.random.choice
+
 
 class Kuhn3112(Game):
     """Kuhn's 3-card Poker: http://en.wikipedia.org/wiki/Kuhn_poker"""
@@ -167,8 +169,6 @@ class Player(object):
     def choice(self, choices):
         """Invoked to make a choice from given list of choices.
 
-        XXX Use local rng!
-
         Parameters
         ----------
         start : string
@@ -182,7 +182,7 @@ class Player(object):
         c : string
             The made choice.
         """
-        return np.random.choice(choices, size=1)[0]
+        return RNG.choice(choices)
 
     def observe(self, player, choice):
         """Observe given player make a move, and memorize it."""

### 2015-07-11 paper.tex
citation for NP-hardness of our fundamental problem

@@
 Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
-is impossible in practice \textbf{Cite Koller!!!}, and such a
-precision doesn't have any fundamental advantage. Instead, it is
+is impossible in practice (indeed, this system of problems is NP-hard
+\cite{koller1992complexity}) and such a
+precision doesn't have any fundamental practical advantage. Instead, it is
 customary compute so-called Nash $\epsilon$-equlibria.

### 2015-07-11 nesterov.py

@@ -241,14 +241,14 @@ if __name__ == "__main__":
     from primal_dual import primal_dual_sg_ne
     rng = np.random.RandomState(42)
     A = np.array([[-2., 3.], [3, -4]])
-    A = rng.randn(500, 500)
+    A = rng.randn(100, 100)
     fig1 = plt.figure(figsize=(17, 13))
     ax1 = plt.subplot("111")
     plt.grid("on")
     fig2 = plt.figure(figsize=(17, 13))
     ax2 = plt.subplot("111")
     plt.grid("on")
-    for solver in ["primal-dual sg", "nesterov", "gilpin"]:
+    for solver in ["primal-dual sg", "nesterov", "gilpin"][:1]:
         x, u, values, gaps = eval("%s_ne" % solver.replace(" ", "_").replace(
             "-", "_"))(A, epsilon=1e-4, max_iter=100000)
         ax1.loglog(gaps, label="\\textbf{%s}" % solver, linewidth=4)

### 2015-07-12 paper.tex
more

@@
 of all subsets of $X$, or equivalently the set of all binary
-functions on $X$.
-
-Let $m$ and $n$ be positive integers.
+functions on $X$. Let $m$ and $n$ be positive integers. Given two
+vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
+$\langle z, w\rangle := \sum_{j}z_jw_j$. The components of $z$ will be
+denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
+not $1$). The notation ``$z \ge 0$'' means that all the components of
+$z$ are nonnegative.
 $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
-0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  Given two
-vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
-$\langle z, w\rangle := \sum_{j}z_jw_j$ The components of $z \in \mathbb{R}^n$ will be
-denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
-not $1$). The notation ``$z \ge 0$'' means that all the components of $z$ are
-nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
-\mathbb{R}^n$, $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
-by $\|z\| := \sqrt{\langle z, z\rangle}$.
-$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
-maximum of $z$ with $0$. For example, $((-2, \pi))_+ = (max(-2, 0),
-max(\pi, 0)) = (0, \pi)$.
-The operator $(.)_+$ is the well-known
-(multi-dimensional) \textit{ramp} function.
-
+0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  $\|z\|$ denotes the
+$2$-\textit{norm} of $z$ defined by $\|z\| := \sqrt{\langle z,
+  z\rangle}$. $(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the
+point-wise maximum of $z$ with $0$. For example, $((-2, \pi))_+ =
+(max(-2, 0), max(\pi, 0)) = (0, \pi)$. The operator $(.)_+$ is the
+well-known (multi-dimensional) \textit{ramp} function. The
+$n$-simplex denoted $\Delta_n$, is defined by $\Delta_n := \{z \in
+\mathbb{R}^n_+|z_0 + z_1 + ... z_{n - 1} = 1\}$.
 Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
@@
 $\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
-operators generalize orthogonal projectors. One also has the useful
-characterization
+operators generalize orthogonal projectors. For example
+$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
+(z)_+$. One also has the useful characterization
 \begin{eqnarray}
@@
 $(1, 0, ..., 0)$. In this so-called \textit{sequence-form}
-representation, the strategy profile of player $k$ is the polyhedron
+representation, the strategy profile of player $k$ is the convex polyhedron
 \begin{equation}
@@
 At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
-$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
+$\tilde{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
 by\footnote{The inequality being due to \textit{weak duality}.}
 \begin{equation}
-  0 \le \mathcal{G}(y, p, x, q) := \langle e_1, p\rangle - (\langle
+  0 \le \tilde{G}(y, p, x, q) := \langle e_1, p\rangle - (\langle
   e_2, q\rangle) = \langle e_1, p\rangle + \langle
@@
 of the game equals $p_0 = -q_0$, i.e the primal-dual gap
-$\mathcal{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at
+$\tilde{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at
 equilibria.
@@
 \begin{equation}
-  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon.
+  0 \le \tilde{G}(y^*, p^*, x^*, q^*) \le \epsilon.
 \label{eq:approx_pb}
@@
 \partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
-  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
+  \hat{\Psi}_2(y^*, p^*, ., .)](y^*,p^*,x^*,q^*).
 \end{eqnarray}
@@
 
+\paragraph{Matrix games on simplexes.} It should be noted that any
+matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
+  game with payoff matrix $A$, for which each player's strategy
+profile is a simplex; this simplex can be written in the form
+\eqref{eq:polyhedron} by taking $E_k := (1, 1, ..., 1) \in
+\mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
+matrix game on simplexes can be seen as a sequential game.  Thus the
+results presented in this manuscript can be trivially applied such
+games in particular. Here, the polyhedral strategy profiles $Q_k$
+defined in \eqref{eq:polyhedron} reduce to simplexes $\Delta_{n_k}$,
+and the primal-dual gap function $G(x,y)$ writes $G(x, y) =
+\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
+\Delta_{n_1} \times \Delta_{n_2}\} = \underset{0 \le j <
+  n_1}{\text{max }}(Ay)_j - \underset{0 \le i < n_2}{\text{min
+}}(A^Tx)_i$.
+
 \subsection{Our contribution}
@@
 \label{sec:related_work}
-\textbf{TODO: add note about interior-point methods!!!}
-
 We present a selection of algorithms that is representative of the
@@
 \begin{eqnarray}
-\mathrm{maximize}\{G(x,y)|(x,y) \in Q_1 \times Q_2\},
+\mathrm{minimize}\{G(x,y)|(x,y) \in Q_1 \times Q_2\},
 \end{eqnarray}
@@
 \delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate can
-be arbitrarily large.
+be arbitrarily large for ill-conditioned games.
 \item[--] The reported linear convergence rate is not in terms of
@@
   but in terms of the number of calls to a first-order oracle. For
-  example the projections $\proj_{Q_k}$ are applied at each iteration.%%  Of
+  example the complicated projections $\proj_{Q_k}$ are applied at each iteration.%%  Of
   %% course, the existence of a linear algorithm for solving
@@
 
-\section{The proposed algorithm}
+\section{The proposed primal-dual algorithm}
 \label{sec:algo}
@@
 L_{yx} = \|K\|$. Now, one easily computes the proximal operators $g_1$
-and $g_2$ as
-\begin{eqnarray*}
+and $g_2$ in closed-form as
+\begin{eqnarray}
   \prox_{\lambda g_1}(y, p) \equiv ((y)_+, p - \lambda
@@
 \paragraph{\textbf{Matrix game on simplexes.}}
-Any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a
-\textit{matrix game}. The strategy profile of player $k$ is a simplex;
-this simplex can be written in the form \eqref{eq:polyhedron} by
-taking $E_k := [1, 1, ..., 1] \in \mathbb{R}^{1 \times n_k}$ and $e_k
-= 1$. Thus every matrix game on simplexes can be seen as a sequential
-game. Now, as in \textbf{nesterov, c-p, etc.}, we generate a $1000
+As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
 \times 1000$ random matrix whose entries are uniformly identically

### 2015-07-12 nesterov.py

@@ -241,14 +241,14 @@ if __name__ == "__main__":
     from primal_dual import primal_dual_sg_ne
     rng = np.random.RandomState(42)
     A = np.array([[-2., 3.], [3, -4]])
-    A = rng.randn(100, 100)
+    A = rng.randn(20, 10)
     fig1 = plt.figure(figsize=(17, 13))
     ax1 = plt.subplot("111")
     plt.grid("on")
     fig2 = plt.figure(figsize=(17, 13))
     ax2 = plt.subplot("111")
     plt.grid("on")
-    for solver in ["primal-dual sg", "nesterov", "gilpin"][:1]:
+    for solver in ["nesterov", "gilpin", "primal-dual sg"]:
         x, u, values, gaps = eval("%s_ne" % solver.replace(" ", "_").replace(
             "-", "_"))(A, epsilon=1e-4, max_iter=100000)
         ax1.loglog(gaps, label="\\textbf{%s}" % solver, linewidth=4)

### 2015-07-14 paper.tex
fixups + typos

@@
 by\footnote{The inequality being due to \textit{weak duality}.}
-\begin{equation}
-  0 \le \tilde{G}(y, p, x, q) := \langle e_1, p\rangle - (\langle
+\begin{eqnarray}
+  \begin{split}
+  0 \le \tilde{G}(y, p, x, q) &:= \langle e_1, p\rangle - (\langle
   e_2, q\rangle) = \langle e_1, p\rangle + \langle
-  e_2, q\rangle = G(x, y),
+  e_2, q\rangle\\
+  &= G(x, y) := \mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
+(u,v) \in Q_1 \times Q_2\}.
+\end{split}
   \label{eq:dgap}
-\end{equation}
-where
-\begin{eqnarray}
-G(x, y) :=
-\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
-(u,v) \in Q_1 \times Q_2\}.
-\label{eq:xy_gap}
 \end{eqnarray}
@@
 observe that \eqref{eq:gilpin} can further be written a the minimization of
-the primal-dual gap function $G(x, y)$ (defined in \eqref{eq:xy_gap})
+the primal-dual gap function $G(x, y)$ (defined in \eqref{eq:dgap})
 for the game\footnote{The minimizers of $G$ are precisely the
@@
 \cite{he2013accelerating} with $L_{xx} = L_{yy} = 0$ and $L_{xy} =
-L_{yx} = \|K\|$. Now, one easily computes the proximal operators $g_1$
-and $g_2$ in closed-form as
-\begin{eqnarray}
-  \prox_{\lambda g_1}(y, p) \equiv ((y)_+, p - \lambda
-  e_1),\hspace{.5em} \prox_{\lambda g_2}(x, q) \equiv ((x)_+, q -
-  \lambda e_2).
-  \end{eqnarray}
-
-Algorithm \ref{Tab:algo} is then obtained from \cite[Algorithm
+L_{yx} = \|K\|$. Now, one easily computes the proximal operator of
+$g_j$ in closed-form as $\prox_{\lambda g_j}(z, v) \equiv ((z)_+,
+v - \lambda e_j)$. With all these ingredients in place, Algorithm
+\ref{Tab:algo} is then obtained from \cite[Algorithm
   T-BD]{he2013accelerating}, applied on the GSP

### 2015-07-14 nesterov.py

@@ -238,7 +238,7 @@ if __name__ == "__main__":
     matplotlib.rc('text', usetex=True)
     plt.rc('font', size=50)  # make the power in sci notation bigger
 
-    from primal_dual import primal_dual_sg_ne
+    from primal_dual import primal_dual_sg_ne as elvis_ne
     rng = np.random.RandomState(42)
     A = np.array([[-2., 3.], [3, -4]])
     A = rng.randn(20, 10)
@@ -248,7 +248,7 @@ if __name__ == "__main__":
     fig2 = plt.figure(figsize=(17, 13))
     ax2 = plt.subplot("111")
     plt.grid("on")
-    for solver in ["nesterov", "gilpin", "primal-dual sg"]:
+    for solver in ["nesterov", "gilpin", "elvis"]:
         x, u, values, gaps = eval("%s_ne" % solver.replace(" ", "_").replace(
             "-", "_"))(A, epsilon=1e-4, max_iter=100000)
         ax1.loglog(gaps, label="\\textbf{%s}" % solver, linewidth=4)

### 2015-07-19 paper.tex
getting ready for submission

@@
 \textbf{keywords}: sequential game; imcomplete information; perfect
-recall; sequence-form; approximate Nash equilibrium; primal-dual
-algoithm; convex-optimization; enlarged subgradient
+recall; approximate Nash equilibrium; primal-dual
+algoithm; convex-optimization
 
@@
 
-\subsection{Notation and terminology}
+\subsection{Notation, terminology, and some aspects of modern convex analysis}
 \paragraph{\textbf{General notions.}}
@@
 
-\paragraph{\textbf{Convex analysis.}}
+\paragraph{\textbf{Modern convex analysis.}}
 Given a subset $C$ of $\mathbb{R}^n$,
@@
 
-\subsection{Statement of the problem}
+\subsection{Nash-equilibrium concepts and statement of the problem}
+\subsubsection{Preliminaries}
 The sequence-form for two-person zero-sum games was introduced in
@@
 
-%\subsection{Characterization of equilibria}
 It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
@@
 
+\subsubsection{A note about matrix games on simplexes.} It should be
+noted
+that any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
+  game with payoff matrix $A$, for which each player's strategy
+profile is a simplex; this simplex can be written in the form
+\eqref{eq:polyhedron} by taking $E_k := (1, 1, ..., 1) \in
+\mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
+matrix game on simplexes can be seen as a sequential game.  Thus the
+results presented in this manuscript can be trivially applied such
+games in particular. Here, the polyhedral strategy profiles $Q_k$
+defined in \eqref{eq:polyhedron} reduce to simplexes $\Delta_{n_k}$,
+and the primal-dual gap function $G(x,y)$ writes
+\begin{eqnarray}G(x, y) =
+\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
+\Delta_{n_1} \times \Delta_{n_2}\} = \underset{0 \le j <
+  n_1}{\text{max }}(Ay)_j - \underset{0 \le i < n_2}{\text{min
+}}(A^Tx)_i.
+\end{eqnarray}
+
 %% As usual, the ``minimax'' notation in problem \eqref{eq:primal_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution if (and only if)
@@
 
-\begin{remark}  
-It should be noted that for the class of games considered here
-(sequential games with imcomplete information), the LCPs
-\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
-than what state-of-the-art LCP solvers can handle. See
-\cite{hoda2010smoothing}.
-
-\end{remark}
-
+\subsubsection{Approximate feasibility and optimality}
 Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
 is impossible in practice (indeed, this system of problems is NP-hard
-\cite{koller1992complexity}) and such a
-precision doesn't have any fundamental practical advantage. Instead, it is
-customary compute so-called Nash $\epsilon$-equlibria.
+\cite{koller1992complexity}) and such a precision doesn't have any
+fundamental practical advantage. Instead, it is customary compute
+``approximate'' Nash equilibria.
 
@@
 
-Let us introduce the notion of $\epsilon$-subgradients
+Let us now, introduce the notion of $\epsilon$-subgradients
 \cite{he2013accelerating}.
@@
 
-\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
-Given $\rho > 0$ and $\epsilon > 0$, a Nash
-$(\rho,\epsilon$)-equilibrium for the GSP \eqref{eq:unconstrained_pb}
+\begin{definition}[\textbf{Nash $(\epsilon_1,\epsilon_2)$-equilibria}]
+Given tolerance levels $\epsilon_1, \epsilon_2 > 0$, a Nash
+$(\epsilon_1,\epsilon_2)$-equilibrium for the GSP \eqref{eq:unconstrained_pb}
 is any quadruplet $(x^*, y^*, x^*, q^*)$ for which
@@
 \begin{eqnarray}
-\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
-\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
+\|v^*\| \le \epsilon_1 \text{ and}\hspace{.5em} v^* \in
+\partial_{\epsilon_2}[\hat{\Psi}_1(., ., x^*, q^*) +
   \hat{\Psi}_2(y^*, p^*, ., .)](y^*,p^*,x^*,q^*).
@@
 \begin{itemize}
-\item Exact Nash equilibria correspond to Nash $(0^+,0^+)$-equilibria.
+\item Exact Nash equilibria correspond to Nash $(0,0)$-equilibria.
 \item Nash $\epsilon$-equilibria (in the sense of Definition
-  \ref{thm:approx_nash}) correspond to Nash $(0^+,\epsilon)$-equilibria.
+  \ref{thm:approx_nash}) correspond to Nash $(0,\epsilon)$-equilibria.
 \end{itemize}
 
-\paragraph{Matrix games on simplexes.} It should be noted that any
-matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
-  game with payoff matrix $A$, for which each player's strategy
-profile is a simplex; this simplex can be written in the form
-\eqref{eq:polyhedron} by taking $E_k := (1, 1, ..., 1) \in
-\mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
-matrix game on simplexes can be seen as a sequential game.  Thus the
-results presented in this manuscript can be trivially applied such
-games in particular. Here, the polyhedral strategy profiles $Q_k$
-defined in \eqref{eq:polyhedron} reduce to simplexes $\Delta_{n_k}$,
-and the primal-dual gap function $G(x,y)$ writes $G(x, y) =
-\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
-\Delta_{n_1} \times \Delta_{n_2}\} = \underset{0 \le j <
-  n_1}{\text{max }}(Ay)_j - \underset{0 \le i < n_2}{\text{min
-}}(A^Tx)_i$.
-
 \subsection{Our contribution}
-We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
-algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\rho,
-  \epsilon$)-equilibria for sequential two-person zero-sum games with
+We develop a $\mathcal{O}(1/\epsilon)$ primal-dual
+algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\epsilon,
+  0)$-equilibria in sequential two-person zero-sum games with
   imcomplete information and perfect recall.
@@
 also become state-of-the-art.
+
+Finally, let us note that for the class of games considered here
+(sequential games with imcomplete information), the LCPs
+\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
+than what state-of-the-art LCP and interior-point solvers can
+handle. See for example \cite{hoda2010smoothing}.
 
@@
   \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff it solves
-  GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
+  GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$). In order words, GSP($\Psi_1$,
+  $\Psi_2$, $g_1$, $g_2$) is equivalent to the Nash equilibrium LCPs
+  \eqref{eq:primal_pb} and \eqref{eq:dual_pb}.
   \label{thm:pd}
@@
       - \underbrace{\underset{x',q'}{\text{min}}\text{
-        }\hat{\Psi}_2(y, p, x', q')}_{\phi_2(y,p)},
+        }\hat{\Psi}_2(y, p, x', q')}_{\phi_2(y,p)}\\
+      &= g_1(y, p) - \phi_2(y, p).
   \end{aligned}
@@
  +\underbrace{\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p',
-   x, q)}_{\phi_1(x, q)}.
+   x, q)}_{\phi_1(x, q)}\\
+ &= -g_2(x, q) + \phi_1(x, q). 
    \end{aligned}
 \end{eqnarray*}
-Thus, noting that $-\infty \le \phi_1(x, q), \phi_2(y, p), < +\infty$,
+Thus, noting that $-\infty \le \phi_1(x, q), \phi_2(y, p), < +\infty$
+(so that all the operations below are valid),
 one computes the primal-dual gap between the primal LCP
@@
 \end{eqnarray*}
-where the second equality follows from the fact that $\Psi_1 + \Psi_2
+where the second equality follows from the zero-sum condition $\Psi_1 + \Psi_2
 := 0$.
@@
 \begin{algorithmic}[1]
-\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
+\Require $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
 \in \mathbb{R}^{n_2}
@@
 \leftarrow 0$
-\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \epsilon$ or
-  $\|{v}_{a}^{(k)}\|/k \ge \rho$}
+\While{$\|{v}_{a}^{(k)}\|/k \ge \epsilon$}
 \State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
@@
 
-\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
+\begin{theorem}[Ergodic $\mathcal{O}(1/\epsilon)$ convergence]
 Let $d_0$ be the euclidean distance between the starting point
@@
 set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
-Then given any $\epsilon > 0$ and $\rho > 0$, there exists an index
-$k_0 \le 2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ such that the following
-error bounds hold:
+Then given any $\epsilon > 0$, there exists an index
+$k_0 \le \frac{2d_0\|K\|}{\epsilon}$ such that after $k_0$ iterations
+the algorithm produces the following a quadruplet
+$(y^{k_0},p^{k_0},x^{k_0},q^{k_0})$ and a vector $v^{k_0}$ such that
 \begin{eqnarray}
-\|\tilde{v}_a^{k_0}\| \le \rho \text{ and }
-\|\tilde{\epsilon}_a^{k_0}\| \le \epsilon
+\|v^{k_0}\| \le \epsilon \text{ and}\hspace{.5em} v^{k_0} \in
+\partial[\hat{\Psi}_1(., ., x^{k_0}, q^{k_0}) +
+  \hat{\Psi}_2(y^{k_0}, p^{k_0}, ., .)](y^{k_0},p^{k_0},x^{k_0},q^{k_0}).
 \end{eqnarray}
 
-where $\tilde{v}_a^{(k_0)} := v_a^{(k_0)}/k_0$.
-Thus Algorithm \ref{Tab:algo} outputs an $(\rho,\epsilon)$-Nash
+Thus Algorithm \ref{Tab:algo} outputs an $(\epsilon,0)$-Nash
 equilibrium for the GSP \eqref{eq:unconstrained_pb}
-in at most $2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ iterations.
+in at most $\frac{2d_0\|K\|}{\epsilon}$ iterations.
 \end{theorem}
@@
 
-\section{Conclusion}
+\section{Concluding remarks}
 Making use of the sequence-form representation
@@
 Nash $(\rho,\epsilon)$-equilibrium of the game.
-
 Equilibrium problems are saddle-point convex-concave problems, and as
@@
 
-\medskip \noindent
-%% \paragraph{About the author:} I'm a first-year PhD student in Computer Science at Universit\'e de Parix XI.
-My thesis focuses on novel techniques for optimization on Lie groups (of diffeomorphisms), and other structured manifolds, the aim being to obtain better algorithms for nonlinear registration of fMRI brain images and enhance the charting of human functional connectomes.
+%% \paragraph{About the author:} I'm a first-year PhD student in Computer
+%% Science at Universit\'e de Parix XI. My thesis focuses on novel
+%% techniques for optimization on Lie groups (of diffeomorphisms), and
+%% other structured manifolds, the aim being to obtain better algorithms
+%% for nonlinear registration of fMRI brain images and enhance the
+%% charting of human functional connectomes.
 
-\small
+\pagebreak
 \bibliographystyle{llcns2e/splncs03}

### 2015-07-22 paper.tex
fixups

@@
   basic operations (addition, multiplication, matvec, clipping, etc.),
-  but in terms of the number of calls to a first-order oracle. For
-  example the complicated projections $\proj_{Q_k}$ are applied at each iteration.%%  Of
+  but in terms of the number of calls to a first-order oracle. Most
+  notably, the complicated projections $\proj_{Q_k}$ are applied at
+  each iteration.%%  Of
   %% course, the existence of a linear algorithm for solving
@@
 projection can still be done iteratively using, for example, the
-algorithm in proposition 4.2 of \cite{combettes2010dualization}%%  or any
-%% CQ algorithm (since this projection sub-problem, is, in fact a
-%% \textit{split-feasibility problem}), for example
-. Unfortunately, as
+algorithm in proposition 4.2 of \cite{combettes2010dualization} or the
+algorithms developed in \cite{tran2015splitting}. Unfortunately, as
 with any nested iterative scheme, one would have to solve this
@@
 \label{sec:algo}
-We now derive the algorithm derive the algorithm which is the main object of
-this manuscript.
+We now derive and establish the theoretical properties of the
+algorithm which is the main object of this manuscript.
 
@@
   \mathbb{R}^{l_2}$.
-\Ensure A Nash $(\rho, \epsilon)$-equilibrium
+\Ensure A Nash $(\epsilon,0)$-equilibrium
 $({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
@@
 very low constant cost per iteration, and enjoys a rigorous
-convergence theory with a proven $\mathcal{O}(1/min(\rho,\epsilon))$ convergence
+convergence theory with a proven $\mathcal{O}(1/\epsilon)$ convergence
 in terms of basic operations (matvec products, clipping, etc.), to a
-Nash $(\rho,\epsilon)$-equilibrium of the game.
+Nash $(\epsilon,0)$-equilibrium of the game.
 Equilibrium problems are saddle-point convex-concave problems, and as

### 2015-07-22 primal_dual.py

@@ -13,6 +13,7 @@ from scipy import linalg
 _norm = lambda *args: sqrt(np.sum(np.concatenate(args) ** 2))
 
 
+@profile
 def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
                    proj_C2=lambda y: np.maximum(y, 0.), init=None,
                    epsilon=1e-4, max_iter=10000, callback=None):

### 2015-07-22 sequential_form.py

@@ -1,3 +1,6 @@
+import numpy as np
+
+
 def _matrix2texstr(A, name="A", exclude=None):
     if exclude is None: exclude = []
     vals = dict((val, []) for val in np.unique(A))

### 2015-07-23 paper.tex
major changes

@@
   sequential games with  imcomplete information and perfect recall
-  (like Texas Hold'em Poker) based on the notion of enlarged
-  subgradients. Our algorithm only performs basic iterations (i.e
-  iterations involving no calls to external first-order oracles, etc.)
+  (like Texas Hold'em Poker). Our algorithm only performs basic
+  iterations (i.e iterations involving no calls to external
+  first-order oracles, etc.)
   and is applicable to a broad class of two-person zero-sum games
@@
   \cite{koller1992complexity} which allows us to encode any such game
-  as a matrix game with polyhedral strategy profiles, the size of the
-  representation being linear in ... The number of iterations needed
-  to produce a Nash equilibrium with a given precision is inversely
-  proportional to the desired precision. As proof-of-concept, we apply our
-  algorithm to solve Kuhn 3-card Poker.
+  as a matrix game with polyhedral strategy profiles. We prove that
+  the number of iterations needed to produce a Nash equilibrium with a
+  given precision is inversely proportional to the desired
+  precision. We also present experimental results on simulated and
+  real games (Kuhn poker).
 \end{abstract}
@@
 consists in computing Nash-equilibria (infact, approximations thereof)
-offline, and playing one's part of the equilibrium online. This
+offline, and playing one's part (an optimal \textit{behavioral}
+strategy) of the equilibrium online. This
 technique is the driving-force behind solution concepts like CFR
 \cite{zinkevich2008regret,lanctot2009monte},
-$\text{CFR}^{+}$ \textbf{TODO: add ref!!!}, and other variants, which
+$\text{CFR}^{+}$ \cite{tammelin14} and other variants, etc., which
 have recently had profound success in Poker. However, solving games
@@
 
-\subsection{Notation, terminology, and some aspects of modern convex analysis}
-\paragraph{\textbf{General notions.}}
+\subsection{Notation and terminology}
 Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
@@
 $n$-simplex denoted $\Delta_n$, is defined by $\Delta_n := \{z \in
-\mathbb{R}^n_+|z_0 + z_1 + ... z_{n - 1} = 1\}$.
+\mathbb{R}^n_+|\sum_j z_j = 1\}$.
 Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
@@
 
-\paragraph{\textbf{Modern convex analysis.}}
-Given a subset $C$ of $\mathbb{R}^n$,
-$i_C$ denotes its \textit{indicator function} defined by
-\begin{eqnarray}
-  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
-    otherwise.}
-\end{eqnarray}
-At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
-etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
-  convex function. The \textit{effective domain} of $f$, denoted
-  $dom(f)$, is defined as
-\begin{eqnarray}
-  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
-\end{eqnarray}
- If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
-%% \textit{proper convex lower semi-continous function}
-%% (\textit{p.c.l.s.c} for short).
-%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
-%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
-%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
-The \textit{subgradient} of $f$ is the set-valued function
-\begin{eqnarray}
-\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
-\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
-z \in \mathbb{R}^n\}.
-\end{eqnarray}
-Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
-in case $f$ is differentiable at $x$. If $f$ is convex, its
-\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
-\rightarrow \mathbb{R}^n$ defined by
-\begin{eqnarray}
-  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
-  - x\|^2 + f(z).
-\end{eqnarray}
-For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
-$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
-operators generalize orthogonal projectors. For example
-$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
-(z)_+$. One also has the useful characterization
-\begin{eqnarray}
-  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
-\end{eqnarray}
-
-The interested reader should refer to \cite{combettes2011proximal} for
-a more elaborate exposition of proximal operators and their
-use in modern convex-optimization.
-
 \subsection{Nash-equilibrium concepts and statement of the problem}
-\subsubsection{Preliminaries}
 The sequence-form for two-person zero-sum games was introduced in
@@
 
-\subsubsection{A note about matrix games on simplexes.} It should be
+Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
+is impossible in practice (indeed, this system of problems is NP-hard
+\cite{koller1992complexity}) and such a precision doesn't have any
+fundamental practical advantage. Instead, it is customary compute
+``approximate'' Nash equilibria. A popular notion of approximate
+equilibria is the following:
+
+\begin{definition}[\textbf{Nash $\epsilon$-equilibria}]
+Given $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
+a pair $(x^*, y^*)$ of realization plans such that there exists dual
+vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
+\eqref{eq:dual_pb} such that the primal-dual gap at $(y^*, p^*, x^*, q^*)$
+doesn't exceed $\epsilon$. That is,
+
+\begin{equation}
+  0 \le \tilde{G}(y^*, p^*, x^*, q^*) \le \epsilon.
+\label{eq:approx_pb}
+\end{equation}
+\label{thm:approx_nash}
+\end{definition}
+
+\paragraph{Our contribution.}
+Developing on an alternative notion of approximate equilibria
+homologuous to that presented in Definition \ref{thm:approx_nash}, we
+device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
+computing approximate Nash equilibria in sequential two-person
+zero-sum games with imcomplete information and perfect recall. We also
+prove that the number of iterations required by the algorithm to
+produce an approximation equilibrium to a precision $\epsilon$ is
+$\mathcal{O}(1/\epsilon)$.
+
+\paragraph{A note about matrix games on simplexes.} It should be
 noted
@@
 %% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
-
-\subsubsection{Approximate feasibility and optimality}
-Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
-is impossible in practice (indeed, this system of problems is NP-hard
-\cite{koller1992complexity}) and such a precision doesn't have any
-fundamental practical advantage. Instead, it is customary compute
-``approximate'' Nash equilibria.
-
-\begin{definition}[\textbf{Nash $\epsilon$-equilibria}]
-Given $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
-a pair $(x^*, y^*)$ of realization plans such that there exists dual
-vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
-\eqref{eq:dual_pb} such that the primal-dual gap at $(y^*, p^*, x^*, q^*)$
-doesn't exceed $\epsilon$. That is,
-
-\begin{equation}
-  0 \le \tilde{G}(y^*, p^*, x^*, q^*) \le \epsilon.
-\label{eq:approx_pb}
-\end{equation}
-\label{thm:approx_nash}
-\end{definition}
-
-Let us now, introduce the notion of $\epsilon$-subgradients
-\cite{he2013accelerating}.
-
-\begin{definition}[$\epsilon$-subgradient]
-Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
-\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
-$\epsilon$-subgradient, for short) of $f$ is the set-valued function
-\begin{eqnarray}
-\partial_\epsilon f: \mathbb{R}^n \rightarrow
-2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
-\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
-\mathbb{R}^n\}.
-\end{eqnarray}
-\end{definition}
-
-The idea behind $\epsilon$-subgradients is the following. Say we wish
-to minimize the function $f$. Replace the usual necessary
-condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
-weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
-small vector $v$''. In fact, it is easy to see that, for each
-point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
-  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
-This approximation concept for subgradients yields the following
-concept of approximate Nash equlibria (adapted from
-\cite{he2013accelerating}).
-
-\begin{definition}[\textbf{Nash $(\epsilon_1,\epsilon_2)$-equilibria}]
-Given tolerance levels $\epsilon_1, \epsilon_2 > 0$, a Nash
-$(\epsilon_1,\epsilon_2)$-equilibrium for the GSP \eqref{eq:unconstrained_pb}
-is any quadruplet $(x^*, y^*, x^*, q^*)$ for which
-there exists a perturbation vector $v^*$ such that
-\begin{eqnarray}
-\|v^*\| \le \epsilon_1 \text{ and}\hspace{.5em} v^* \in
-\partial_{\epsilon_2}[\hat{\Psi}_1(., ., x^*, q^*) +
-  \hat{\Psi}_2(y^*, p^*, ., .)](y^*,p^*,x^*,q^*).
-\end{eqnarray}
-
-Such a vector $v^*$ is called a Nash $\epsilon$-residual at $(x^*,
-y^*, x^*, q^*)$.
-\label{thm:cool_notion}
-\end{definition}
-
-The above definition is a generalization of the notion of Nash
-equilibria since:
-\begin{itemize}
-\item Exact Nash equilibria correspond to Nash $(0,0)$-equilibria.
-\item Nash $\epsilon$-equilibria (in the sense of Definition
-  \ref{thm:approx_nash}) correspond to Nash $(0,\epsilon)$-equilibria.
-\end{itemize}
-
-\subsection{Our contribution}
-We develop a $\mathcal{O}(1/\epsilon)$ primal-dual
-algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\epsilon,
-  0)$-equilibria in sequential two-person zero-sum games with
-  imcomplete information and perfect recall.
 
@@
 
+\section{A more amenable notion of approximate equilibrium}
+\subsection{Interlude: Proximal calculus}
+Let us introduce some notions in modern convex analysis which will be
+useful in what follows. Given a subset $C$ of $\mathbb{R}^n$,
+$i_C$ denotes its \textit{indicator function} defined by
+\begin{eqnarray}
+  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
+    otherwise.}
+\end{eqnarray}
+At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
+etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
+  convex function. The \textit{effective domain} of $f$, denoted
+  $dom(f)$, is defined as
+\begin{eqnarray}
+  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
+\end{eqnarray}
+ If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
+%% \textit{proper convex lower semi-continous function}
+%% (\textit{p.c.l.s.c} for short).
+%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
+%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
+%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
+The \textit{subgradient} of $f$ is the set-valued function
+\begin{eqnarray}
+\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
+\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
+z \in \mathbb{R}^n\}.
+\end{eqnarray}
+Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
+in case $f$ is differentiable at $x$. If $f$ is convex, its
+\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
+\rightarrow \mathbb{R}^n$ defined by
+\begin{eqnarray}
+  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
+  - x\|^2 + f(z).
+\end{eqnarray}
+For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
+$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
+operators generalize orthogonal projectors. For example
+$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
+(z)_+$. One also has the useful characterization
+\begin{eqnarray}
+  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
+\end{eqnarray}
+
+The interested reader should refer to \cite{combettes2011proximal} for
+a more elaborate exposition of proximal operators and their
+use in modern convex-optimization.
+
+Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
+\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
+$\epsilon$-subgradient, for short) of $f$ is the set-valued function
+\begin{eqnarray}
+\partial_\epsilon f: \mathbb{R}^n \rightarrow
+2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
+\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
+\mathbb{R}^n\}.
+\end{eqnarray}
+
+The idea behind $\epsilon$-subgradients is the following. Say we wish
+to minimize the function $f$. Replace the usual necessary
+condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
+weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
+small vector $v$''. In fact, it is easy to see that, for each
+point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
+  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
+
+This approximation concept for subgradients yields the following
+concept of approximate Nash equlibria (adapted from
+\cite{he2013accelerating}).
+
+\begin{definition}[\textbf{Nash $(\epsilon_1,\epsilon_2)$-equilibria}]
+Given tolerance levels $\epsilon_1, \epsilon_2 > 0$, a Nash
+$(\epsilon_1,\epsilon_2)$-equilibrium for the GSP \eqref{eq:unconstrained_pb}
+is any quadruplet $(x^*, y^*, x^*, q^*)$ for which
+there exists a perturbation vector $v^*$ such that
+\begin{eqnarray}
+\|v^*\| \le \epsilon_1 \text{ and}\hspace{.5em} v^* \in
+\partial_{\epsilon_2}[\hat{\Psi}_1(., ., x^*, q^*) +
+  \hat{\Psi}_2(y^*, p^*, ., .)](y^*,p^*,x^*,q^*).
+\end{eqnarray}
+
+Such a vector $v^*$ is called a Nash $\epsilon$-residual at $(x^*,
+y^*, x^*, q^*)$.
+\label{thm:cool_notion}
+\end{definition}
+
+The above definition is a generalization of the notion of Nash
+equilibria since:
+\begin{itemize}
+\item Exact Nash equilibria correspond to Nash $(0,0)$-equilibria.
+\item Nash $\epsilon$-equilibria (in the sense of Definition
+  \ref{thm:approx_nash}) correspond to Nash $(0,\epsilon)$-equilibria.
+\end{itemize}
+
 \section{The proposed primal-dual algorithm}
@@
 In Algorithms \ref{Tab:algo} most of the time is spent
-pre-multiplying vectors by $A$ and $A^T$. For \textit{flop}-type Poker
+pre-multiplying vectors by $A$ and $A^T$. For \textit{flop-type} poker
 games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
-$A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
+$A$ (and thus $A^T$ too)  is very big (up $10^{100}$ rows and columns!)
 but has a rich block-diagnoal structure which can be carefully
@@
 
-\section{Experimantal results}
+\section{Experimental results}
 \label{sec:results}
 To access the practical quality of the proposed algorithm, we
-experimented it on real and simulated matrix games.
+experimented it on real games.
+
+\subsection{Basic test-bed: Matrix games on simplexes}
+As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
+\times 1000$ random matrix whose entries are uniformly identically
+distributed in the closed interval $[-1, 1]$.
 
 \begin{figure}[!htpb]
-  \subfigure[Matrix game on simplices]{
-    \includegraphics[width=.33\linewidth]{simplex_dgap.pdf}
+  \subfigure[Matrix game on simplexes]{
+    \includegraphics[width=.33\linewidth]{0.pdf}
   }
@@
   \hspace{-1em}
-  \includegraphics[width=.34\linewidth]{simplex_NE.pdf}
+  \includegraphics[width=.34\linewidth]{1.pdf}
   \hspace{-1em}
@@
 
-\paragraph{\textbf{Matrix game on simplexes.}}
-As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
-\times 1000$ random matrix whose entries are uniformly identically
-distributed in the closed interval $[-1, 1]$.
+\subsection{Sequential games with imcomplete information}
+\paragraph{\textbf{Toy Poker game...}}
+%% The sequence-form representation for this Toy Poker game is given by
+%% (showing only nonzero entries):\\
 
-\paragraph{\textbf{Toy Poker game.}}
-The sequence-form representation for this Toy Poker game is given by
-(showing only nonzero entries):\\
+%% $E_1 \in \mathbb{R}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
+%% E_1(1,2) = E_1(2,3) = E_1(2,4) = {1}$,
+%% $E_1(1,0) = E_1(2,0) = {-1}$; \\
 
-$E_1 \in \mathbb{R}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
-E_1(1,2) = E_1(2,3) = E_1(2,4) = {1}$,
-$E_1(1,0) = E_1(2,0) = {-1}$; \\
+%% $E_2 \in \mathbb{R}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
+%% = E_2(2,3) = E_2(2,4) = {1}$, $E_2(1,0) = E_2(2,0) =
+%% {-1}$; and \\
 
-$E_2 \in \mathbb{R}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
-= E_2(2,3) = E_2(2,4) = {1}$, $E_2(1,0) = E_2(2,0) =
-{-1}$; and \\
+%% $A \in \mathbb{R}^{5 \times 5}$ with $A(2,0) =
+%% A(4,0) = {-0.5}$, $A(1,3) = {1}$, $A(3,1) =
+%% {-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = {0.25}$.
 
-$A \in \mathbb{R}^{5 \times 5}$ with $A(2,0) =
-A(4,0) = {-0.5}$, $A(1,3) = {1}$, $A(3,1) =
-{-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = {0.25}$.
+\paragraph{{Kuhn 3-card Poker}} is a simplified form of poker
+developed by Harold W. Kuhn. It is a zero sum two player game. The
+deck includes only three playing cards, for example a King, Queen, and
+Jack. One card is dealt to each player, then the first player must bet
+or pass, then the second player may bet or pass. If any player chooses
+to bet the opposing player must bet as well ("call") in order to stay
+in the round. After both players pass or bet the player with the
+highest card wins the pot. Kuhn demonstrated that there are many game
+theoretic optimal strategies for the first player in this game, but
+only one for the second player, and that, when played optimally, the
+first player should expect to lose at a rate of −1/18 per hand. The
+sequence-form representation of the game has $n_1 = n_2 = 13$
+sequences and $l_1 = l_2 = 7$ information
+sets per player. More details (payoff matrix, etc.) are provided in
+the supp. mats. %% , and its
+%% sequence-form is given by:\\
 
-\paragraph{{Kuhn 3-card Poker.}}
-The game has $n_1 = n_2 = 13$ and $l_1 = l_2 = 7$, and its
-sequence-form is given by:\\
+%% $E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
+%% E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
+%% E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
+%% E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
+%% E_1(5,5) = E_1(6,9) = {-1}$; \\
 
-$E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
-E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
-E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
-E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
-E_1(5,5) = E_1(6,9) = {-1}$; \\
+%%  $E_2 \in \mathbb{R}^{7 \times 13}$ with
+%% $E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
+%% E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
+%% E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
+%% E_2(5,0) = E_2(6,0) = {-1}$; and \\
 
- $E_2 \in \mathbb{R}^{7 \times 13}$ with
-$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
-E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
-E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
-E_2(5,0) = E_2(6,0) = {-1}$; and \\
-
- $A \in \mathbb{R}^{13 \times
-  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
-{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
-A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
-A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
-$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
-A(12,1) = A(12,5) = {0.166667}$.\\
+%%  $A \in \mathbb{R}^{13 \times
+%%   13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
+%% {-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
+%% A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
+%% A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
+%% $A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
+%% A(12,1) = A(12,5) = {0.166667}$.\\
 

### 2015-07-23 nesterov.py

@@ -229,6 +229,8 @@ def gilpin_ne(A, epsilon=1e-4, max_iter=np.inf):
 
     return x, y, values, gaps
 
+_cap = lambda name: name[0].upper() + name[1:].lower()
+
 if __name__ == "__main__":
     # matplotlib confs
     import matplotlib
@@ -238,32 +240,34 @@ if __name__ == "__main__":
     matplotlib.rc('text', usetex=True)
     plt.rc('font', size=50)  # make the power in sci notation bigger
 
-    from primal_dual import primal_dual_sg_ne as elvis_ne
+    from primal_dual import primal_dual_sg_ne as alg_1_ne
     rng = np.random.RandomState(42)
     A = np.array([[-2., 3.], [3, -4]])
-    A = rng.randn(20, 10)
-    fig1 = plt.figure(figsize=(17, 13))
+    A = rng.randn(50, 50)
+    fig1 = plt.figure(figsize=(13.5, 10))
     ax1 = plt.subplot("111")
     plt.grid("on")
-    fig2 = plt.figure(figsize=(17, 13))
+    fig2 = plt.figure(figsize=(13.5, 10))
     ax2 = plt.subplot("111")
     plt.grid("on")
-    for solver in ["nesterov", "gilpin", "elvis"]:
+    for solver in ["alg 1", "gilpin", "nesterov"]:
         x, u, values, gaps = eval("%s_ne" % solver.replace(" ", "_").replace(
             "-", "_"))(A, epsilon=1e-4, max_iter=100000)
-        ax1.loglog(gaps, label="\\textbf{%s}" % solver, linewidth=4)
-        ax1.set_xlabel("\\textbf{$k$}", fontsize=50)
+        ax1.loglog(gaps, label="\\textbf{%s}" % _cap(solver), linewidth=6)
         ax1.set_ylabel("\\textbf{primal-dual gap}", fontsize=50)
-
-        ax2.semilogx(values, label="\\textbf{%s}" % solver, linewidth=4)
-        ax2.set_xlabel("\\textbf{$k$}", fontsize=50)
+        if solver == "alg 1":
+            ax1.loglog(1. / np.arange(1, len(gaps) + 1), linestyle="--",
+                       dashes=(20, 10), label="$\\mathcal{O}(1/k)$",
+                       linewidth=6, color="k")
+        ax2.semilogx(values, label="\\textbf{%s}" % _cap(solver), linewidth=6)
[…]

### 2015-07-23 primal_dual.py

@@ -13,7 +13,6 @@ from scipy import linalg
 _norm = lambda *args: sqrt(np.sum(np.concatenate(args) ** 2))
 
 
-@profile
 def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
                    proj_C2=lambda y: np.maximum(y, 0.), init=None,
                    epsilon=1e-4, max_iter=10000, callback=None):

### 2015-07-23 sequence_form.py

@@ -1,3 +1,6 @@
+import re
+import networkx as nx
+import matplotlib.pyplot as plt
 import numpy as np
 
 

### 2015-07-23 simple.py

@@ -455,17 +455,17 @@ if __name__ == "__main__":
 
     rng = check_random_state(42)
     max_iter = 10000
-    game_clses = ["simplex", SimplifiedPoker, Kuhn3112]
+    game_clses = ["simplex", SimplifiedPoker, Kuhn3112][1:]
     for cnt, game_cls in enumerate(game_clses):
         if game_cls == "simplex":
             game = None
             name = game_cls
-            A = rng.uniform(-1, 1, size=(100, 100))
+            A = rng.uniform(-1, 1, size=(50, 50))
             x, y, p, q, init, values, dgaps = primal_dual_sg_ne(
                 A, max_iter=max_iter, strict=False)
         else:
             game = game_cls()
-            name = game.__class__.__name__
+            name = game_cls.__name__
             E1, e1 = game.constraints[1]
             E2, e2 = game.constraints[2]
             A = game.payoff_matrix
@@ -489,22 +489,13 @@ if __name__ == "__main__":
         plt.figure(figsize=(13.5, 10))
         ax = plt.subplot("111")
         plt.grid("on")
-        ax.semilogx(values, linewidth=4)
+        ax.semilogx(values, linewidth=6, label="\\textbf{Alg 1}")
         value_ = "%.0e" % value
         m, e = re.search("(.+?)e(.+)", value_).groups()
         m = float(m)
         m = "" if m >= 0 else "-"
         e = re.sub("\-0*", "-", e)
-        kwargs = {}
         plt.xlabel("\\textbf{$k$ (iteration count)}", fontsize=50)
-        if cnt == 0:
-            kwargs["label"] = "$\\langle x^*,Ay^*\\rangle$"
-            ax.set_ylabel(("\\textbf{$\\langle x^{(k)}, Ay^{(k)} "
-                           "\\rangle$"), fontsize=50)
-        ax.axhline(
-            -1. / 18. if isinstance(game, Kuhn3112) else value,
-            linestyle="--", dashes=(30, 10), color="b",
-            linewidth=4, **kwargs)
         plt.legend(loc="best", prop=dict(size=45), handlelength=1.5)
         ax.ticklabel_format(axis="y", style="sci", scilimits=(0., 0.))
         ax.tick_params(axis='both', which='major', labelsize=50)
@@ -515,12 +506,11 @@ if __name__ == "__main__":
         plt.figure(figsize=(13.5, 10))
[…]

### 2015-07-23 paper.tex
typo
ENH: ready for first arXiv upload

@@
 \subsection{Nash-equilibrium concepts and statement of the problem}
-The sequence-form for two-person zero-sum games was introduced in
+The sequence-form representation for two-person zero-sum games with
+imcomplete information was introduced in
 \cite{koller1992complexity}, and the theory was further developed in
 \cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
-established that for sequential two-person zero-sum games with
-imcomplete information and perfect recall, there exist sparse matrices
+established that for such games, there exist sparse matrices
 $A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
@@
 pairs $(x, y)$ of \textit{realization plans} which solve the primal
-LCP
+LCP (Linear Convex Program)
 \begin{equation}
@@
   \begin{split}
-  0 \le \tilde{G}(y, p, x, q) &:= \langle e_1, p\rangle - (\langle
+  0 \le \tilde{G}(y, p, x, q) &:= \langle e_1, p\rangle - (-\langle
   e_2, q\rangle) = \langle e_1, p\rangle + \langle
@@
 
-\paragraph{Our contribution.}
-Developing on an alternative notion of approximate equilibria
-homologuous to that presented in Definition \ref{thm:approx_nash}, we
-device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
-computing approximate Nash equilibria in sequential two-person
-zero-sum games with imcomplete information and perfect recall. We also
-prove that the number of iterations required by the algorithm to
-produce an approximation equilibrium to a precision $\epsilon$ is
-$\mathcal{O}(1/\epsilon)$.
-
 \paragraph{A note about matrix games on simplexes.} It should be
@@
 %% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
+
+\subsection{Our contribution}
+One cannot directly attack the LCPs \eqref{eq:primal_pb} and
+\eqref{eq:dual_pb} via a traditional primal-dual algorithm
+(for example \cite{chambolle2010,chambolle2014ergodic}) because
+computing the euclidean projections $\proj_{Q_k}$ is very difficult
+(in fact, such subproblems would have to be solved
+iteratively\footnote{An ``exception to the rule'' is the case where
+  the $Q_k's$ are simplexes, so that the projections can be computed
+  exactly using \cite{duchi2008efficient}.}). Also,
+the primal-dual gap might explode even at ``nearly feasible'' points,
+leaving a primal-dual algorithm with no clear indication whatsoever,
+on whether progress is being made or not. So need to way to
+\begin{itemize}
+\item[--] avoid having to compute the projections $\proj_{Q_k}$,
+\item[--] have control over how far we are from the set of equilibria and
+  avoid infinite (and thus non-informative) primal-dual gaps.
+\end{itemize}
+
+Developing on an alternative notion of approximate equilibria (see
+Definition \ref{thm:cool_notion})
+homologuous to that presented in Definition \ref{thm:approx_nash}, we
+device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
+computing approximate Nash equilibria in sequential two-person
+zero-sum games with imcomplete information and perfect recall. We also
+prove (Theorem \ref{thm:pd})
+that the number of iterations required by the algorithm to
+produce an approximation equilibrium to a precision $\epsilon$ is
+$\mathcal{O}(1/\epsilon)$.%%  The source of approximation in our scheme
+%% is that we explicitly control how close we are to the feasible set
+%% $Q_1 \times Q_2$.
 
@@
 
-\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
+\section{Our contributions}
+\subsection{Reformulation as a Generalized Saddle-point Problem (GSP)}
 \label{sec:gsp}
-One cannot directly attack the LCPs \eqref{eq:primal_pb} and
-\eqref{eq:dual_pb} via a traditional primal-dual algorithm
-(for example \cite{chambolle2010,chambolle2014ergodic}) because
-computing the euclidean projections $\proj_{Q_k}$ is very difficult
-(in fact, such subproblems would have to be solved
-iteratively\footnote{An ``exception to the rule'' is the case where
-  the $Q_k's$ are simplexes, so that the projections can be computed
-  exactly using \cite{duchi2008efficient}.}). Also,
-the primal-dual gap might explode even at ``nearly feasible'' points,
-leaving a primal-dual algorithm with no clear on whether progress is
-being made or not. So need to way to
-\begin{itemize}
-\item[--] avoid having to compute the projections $\proj_{Q_k}$,
-\item[--] have control over how far we are from the set of equilibria and
-  avoid infinite (and thus non-informative) primal-dual gaps.
-\end{itemize}
-
 In the next theorem, we show that the said LCP problems can be
@@
 
-\section{A more amenable notion of approximate equilibrium}
-\subsection{Interlude: Proximal calculus}
-Let us introduce some notions in modern convex analysis which will be
+\subsection{A more amenable notion of approximate equilibria}
+\subsubsection{Interlude: Proximal calculus}
+Let us introduce some notions from modern convex analysis which will be
 useful in what follows. Given a subset $C$ of $\mathbb{R}^n$,
@@
 
-Such a vector $v^*$ is called a Nash $\epsilon$-residual at $(x^*,
+Such a vector $v^*$ is called a Nash $(\epsilon_1, \epsilon_2)$-residual at $(x^*,
 y^*, x^*, q^*)$.
@@
 
-\section{The proposed primal-dual algorithm}
+\subsection{The proposed primal-dual algorithm}
 \label{sec:algo}
@@
 
-\subsection{Algorithm and convergence rate}
 \begin{algorithm}
@@
 but has a rich block-diagnoal structure which can be carefully
-exploited, as was done in \cite{hoda2010smoothing}.
+exploited, as was done in \cite{hoda2010smoothing}. For the purpose of
+completeness, we explain the details of the tricks used in
+\cite{hoda2010smoothing} for speeding up the computation of these
+matvec products.
 
-%% \begin{definition}(Kronecker product)
-%% Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
-%%   s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
+\begin{definition}(Kronecker product)
+Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
+  s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
 
-%% \begin{equation}
-%% F \otimes B:=\left[
-%% \begin{array}{cccc}
-%% F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
-%% F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
-%% \vdots & \vdots & \ddots & \vdots\\
-%% F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
-%% \end{array}\right] \in \mathbb{R}^{mr \times ns}
-%% \end{equation}
-%% \end{definition}
+\begin{equation}
+F \otimes B:=\left[
+\begin{array}{cccc}
+F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
+F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
+\vdots & \vdots & \ddots & \vdots\\
+F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
+\end{array}\right] \in \mathbb{R}^{mr \times ns}
+\end{equation}
+\end{definition}
 
-%% One notes that $(F \otimes B)^T = F^T \otimes B^T$.
-%% $F \otimes B$ can be very much larger than both $F$ and $B$ in
-%% dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
-%% $B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
-%% $10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
-%% \mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
-%% without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
-%% rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
-%%   ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
-%% $s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
-%% as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
-%% easily verfies that $Y$ is the matrix product of the ``small''
-%% matrices $B$, $X$, and $F^T$, i.e
+One notes that $(F \otimes B)^T = F^T \otimes B^T$.
+$F \otimes B$ can be very much larger than both $F$ and $B$ in
+dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
+$B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
+$10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
+\mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
+without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
+rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
+  ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
+$s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
+as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
+easily verfies that $Y$ is the matrix product of the ``small''
+matrices $B$, $X$, and $F^T$, i.e
 
-%% \begin{equation}
-%%   \label{eq:kron_matvec}
-%%   Y = BXF^T
-%% \end{equation}
+\begin{equation}
+  \label{eq:kron_matvec}
+  Y = BXF^T
+\end{equation}
 
-%% Now, in Texas Hold'em for example, the payoff matrix $A$ can be
-%% written as block-diagonal matrix whose blocks are sums of Kronecker
-%% products of much smaller sparse matrices as follows
+Now, in Texas Hold'em for example, the payoff matrix $A$ can be
+written as block-diagonal matrix whose blocks are sums of Kronecker
+products of much smaller sparse matrices as follows
 
-%% \begin{equation}
-%%   A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
-%%     \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
-%%     B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
-%% \label{eq:factor_A}
-%% \end{equation}
-%% See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
-%% sequences of moves in round $i$ which end in a \textit{fold} action,
-%% and $S$ to the sequences which end in a \textit{showdown}. $B_i$
-%% encodes the betting structure of round $i$, while $W$ encodes the
-%% wind/lose/draw information determined by ranking the players' hands at
-%% showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
-%% enough to be explictly represented whereas it is infeasible to
-%% explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
-%% $S$, and $W$ are themselves sparse, which allows one to use the
-%% compressed row storage data structure that only stores nonzero entries
-%% (for example \textit{scipy.sparse.csr\_matrix}, in the Python
-%% programming language).
+\begin{equation}
+  A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
+    \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
+    B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
+\label{eq:factor_A}
+\end{equation}
+See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
+sequences of moves in round $i$ which end in a \textit{fold} action,
+and $S$ to the sequences which end in a \textit{showdown}. $B_i$
+encodes the betting structure of round $i$, while $W$ encodes the
+wind/lose/draw information determined by ranking the players' hands at
+showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
+enough to be explictly represented whereas it is infeasible to
+explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
+$S$, and $W$ are themselves sparse, which allows one to use the
+compressed row storage data structure that only stores nonzero entries
+(for example \textit{scipy.sparse.csr\_matrix}, in the Python
+programming language).
 
-%% Such a representation of the payoff matrix $A$ trivializes matvec
-%% operations involving $A$ or $A^T$ (thanks to formula
-%% \eqref{eq:kron_matvec} above, applied to their diagonal blocks and
-%% exploiting the sparsity of these blocks themselves). Of course, one
-%% can always write the payoff matrix $A$ of a flop-type Poker game in a
-%% form similary to \eqref{eq:factor_A} by applying appropriate
-%% permutations to the enumeration of the players's sequences.
+Such a representation of the payoff matrix $A$ trivializes matvec
+operations involving $A$ or $A^T$ (thanks to formula
+\eqref{eq:kron_matvec} above, applied to their diagonal blocks and
+exploiting the sparsity of these blocks themselves). Of course, one
+can always write the payoff matrix $A$ of a flop-type Poker game in a
+form similary to \eqref{eq:factor_A} by applying appropriate
+permutations to the enumeration of the players's sequences.
 
-\paragraph{\textbf{Computing $\|K\|$.}} Power iteration (Perron-Frobenius)...
+\paragraph{\textbf{Computing $\|K\|$.}}
+Also the 2-norm $\|K\|$ of the linear operator $K$, can be efficiently
+computed using the power iteration (Perron-Frobenius).
 
@@
 To access the practical quality of the proposed algorithm, we
-experimented it on real games.
-
-\subsection{Basic test-bed: Matrix games on simplexes}
+tested it on simulated and real games.
+\paragraph{Basic test-bed: Matrix games on simplexes.}
 As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
 \times 1000$ random matrix whose entries are uniformly identically
-distributed in the closed interval $[-1, 1]$.
+distributed in the closed interval $[-1, 1]$. We compared our proposed
+Algorithm \ref{Tab:algo} with Nesterov's \cite{nesterov2005a} and Gilpin's et
+al. \cite{gilpinfirst}. The results of the benchmarks are shown in
+Figure \ref{Tab:dgap_curve}\textit{(a)}...
 
@@
   \subfigure[Matrix game on simplexes]{
-    \includegraphics[width=.33\linewidth]{0.pdf}
+    \includegraphics[width=.5\linewidth]{0.pdf}
   }
-  \hspace{-2em}
-  \subfigure[Toy Poker]{
-    \includegraphics[width=.33\linewidth]{SimplifiedPoker_dgap.pdf}
-  }
+  %% \hspace{-2em}
+  %% \subfigure[Toy Poker]{
+  %%   \includegraphics[width=.5\linewidth]{SimplifiedPoker_dgap.pdf}
+  %% }
   \hspace{-2em}
   \subfigure[Kuhn 3-card Poker]{
-    \includegraphics[width=.33\linewidth]{Kuhn3112_dgap.pdf}
+    \includegraphics[width=.5\linewidth]{Kuhn3112_dgap.pdf}
   }
   \vspace{-1em}
+  \hspace{-2em}
+  \includegraphics[width=.5\linewidth]{1.pdf}
+  %% \hspace{-1em}
+  %% \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
   \hspace{-1em}
-  \includegraphics[width=.34\linewidth]{1.pdf}
-  \hspace{-1em}
-  \includegraphics[width=.33\linewidth]{SimplifiedPoker_NE.pdf}
-  \hspace{-1em}
-  \includegraphics[width=.33\linewidth]{Kuhn3112_NE.pdf}
+  \includegraphics[width=.5\linewidth]{Kuhn3112_NE.pdf}
   \caption{Convergence curves of Algorithm
@@
 
-\subsection{Sequential games with imcomplete information}
-\paragraph{\textbf{Toy Poker game...}}
-%% The sequence-form representation for this Toy Poker game is given by
-%% (showing only nonzero entries):\\
-
-%% $E_1 \in \mathbb{R}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
-%% E_1(1,2) = E_1(2,3) = E_1(2,4) = {1}$,
-%% $E_1(1,0) = E_1(2,0) = {-1}$; \\
-
-%% $E_2 \in \mathbb{R}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
-%% = E_2(2,3) = E_2(2,4) = {1}$, $E_2(1,0) = E_2(2,0) =
-%% {-1}$; and \\
-
-%% $A \in \mathbb{R}^{5 \times 5}$ with $A(2,0) =
-%% A(4,0) = {-0.5}$, $A(1,3) = {1}$, $A(3,1) =
-%% {-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = {0.25}$.
-
-\paragraph{{Kuhn 3-card Poker}} is a simplified form of poker
-developed by Harold W. Kuhn. It is a zero sum two player game. The
+\paragraph{Experiments on sequential games with imcomplete information: Kuhn 3-card
+  poker.} This game is a simplified form of poker
+developed by Harold W. Kuhn. It is a two-person zero-sum game which is
+simply enough to serve as an example but contains all the complexity
+traits of a imcomplete information sequential game. The
 deck includes only three playing cards, for example a King, Queen, and
@@
 in the round. After both players pass or bet the player with the
-highest card wins the pot. Kuhn demonstrated that there are many game
-theoretic optimal strategies for the first player in this game, but
-only one for the second player, and that, when played optimally, the
-first player should expect to lose at a rate of −1/18 per hand. The
+highest card wins the pot. The
 sequence-form representation of the game has $n_1 = n_2 = 13$
 sequences and $l_1 = l_2 = 7$ information
-sets per player. More details (payoff matrix, etc.) are provided in
-the supp. mats. %% , and its
+sets per player. The pair $(x^*, y^*) \in \mathbb{R}^{13} \times
+\mathbb{R}^{13}$ of realization plans given by
+\begin{eqnarray*}
+  \begin{split}
+    x^* &= [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0,
+      0.275, 0.725]^T,\\
+    y^* &= [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T
+    \end{split}
+\end{eqnarray*}
+is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of
+Algorithm  \ref{Tab:algo}. The convergence curves are shown
+in Fig \ref{Tab:dgap_curve}. One easy checks that this equilibrium is
+feasible. Indeed, $E_1x^* - e_1 = [4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67
+      \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5},
+      -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T$
+and
+$E_2y^* - e_2 = [-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29
+  \times 10^{-6}, -1.50 \times 10^{-6},
+      2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times
+      10^{-7}]^T$.
+Finally, one checks that ${x^*}^TAy^* = {-0.05555}$,
+ which agrees to 5 d.p with the value of $-1 / 18$ computed
+ analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. The
+ evolution of the dual gap and the expected value of the game across
+ iterations are shown in Figure \ref{Tab:dgap_curve}.
+More details (payoff matrix, etc.) are provided in
+the supplementary materials...
+
+\section{Concluding remarks}
+Making use of the sequence-form representation
+\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
+deviced a simple and efficient primal-dual algorithm for computing
+Nash equilibria in two-person zero-sum sequential games with
+imcomplete information (like Texas Hold'em, etc.). Our algorithm is
+simple to implement, with a very low constant cost per iteration, and
+enjoys a rigorous convergence theory with a proven
+$\mathcal{O}(1/\epsilon)$ convergence in terms of basic operations
+(matvec products, clipping, etc.), to a Nash
+$(\epsilon,0)$-equilibrium of the game. Equilibrium problems are
+saddle-point convex-concave problems, and as
+such a natural choice for algorithms for solving them would be in the
+family of primal-dual algorithms. We believe such primal-dual
+schemes will receive more attention in the algorithmic game theory
+community in future.
+
+The author's implementation of the proposed algorithm is available
+upon request.
+
+%% \paragraph{About the author:} I'm a first-year PhD student in Computer
+%% Science at Universit\'e de Parix XI. My thesis focuses on novel
+%% techniques for optimization on Lie groups (of diffeomorphisms), and
+%% other structured manifolds, the aim being to obtain better algorithms
+%% for nonlinear registration of fMRI brain images and enhance the
+%% charting of human functional connectomes.
+%\pagebreak
+\bibliographystyle{llcns2e/splncs03}
+\bibliography{bib}
+
+\section{Supplementary materials}
+...
+ %% , and its
 %% sequence-form is given by:\\
@@
 
-The pair $(x^*, y^*) \in \mathbb{R}^{13} \times \mathbb{R}^{13}$ of
-realization plans given by
+%\paragraph{\textbf{Toy Poker game...}}
+%% The sequence-form representation for this Toy Poker game is given by
+%% (showing only nonzero entries):\\
 
-\begin{eqnarray*}
-  \begin{split}
-    x^* &= [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0,
-      0.275, 0.725]^T,\\
-    y^* &= [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T
-    \end{split}
-\end{eqnarray*}
-is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of
-Algorithm  \ref{Tab:algo}. The convergence curves are shown
-in Fig \ref{Tab:dgap_curve}. One easy checks that this equilibrium is
-feasible. Indeed,
+%% $E_1 \in \mathbb{R}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
+%% E_1(1,2) = E_1(2,3) = E_1(2,4) = {1}$,
+%% $E_1(1,0) = E_1(2,0) = {-1}$; \\
 
-\begin{eqnarray*}
-  \begin{split}
-    E_1x^* - e_1 = [&4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67
-      \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, \\&
-      -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T
-    \end{split}
-\end{eqnarray*}
-and
+%% $E_2 \in \mathbb{R}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
+%% = E_2(2,3) = E_2(2,4) = {1}$, $E_2(1,0) = E_2(2,0) =
+%% {-1}$; and \\
 
-\begin{eqnarray*}
-  \begin{split}
-    E_2y^* - e_2 = [&-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29
-      \times 10^{-6}, -1.50 \times 10^{-6},\\
-      &2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times
-      10^{-7}]^T
-    \end{split}
-\end{eqnarray*}
-Finally, one checks that
-\begin{eqnarray*}
-  {x^*}^TAy^* = {-0.05555},
-\end{eqnarray*}
- which agrees to 5 d.p with the value of $-1 / 18$ computed
- analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. The
- evolution of the dual gap and the expected value of the game across
- iterations are shown in Figure \ref{Tab:dgap_curve}.
-
-\section{Concluding remarks}
-Making use of the sequence-form representation
-\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
-deviced a primal-dual algorithm for computing Nash equilibria in
-two-person zero-sum sequential games with imcomplete information (like
-Texas Hold'em, etc.). Our algorithm is simple to implement, with a
-very low constant cost per iteration, and enjoys a rigorous
-convergence theory with a proven $\mathcal{O}(1/\epsilon)$ convergence
-in terms of basic operations (matvec products, clipping, etc.), to a
-Nash $(\epsilon,0)$-equilibrium of the game.
-Equilibrium problems are saddle-point convex-concave problems, and as
-such a natural choice for algorithms for solving them would be in the
-family of primal-dual algorithms. The author believes such primal-dual
-schemes will receive more attention in the algorithmic game theory
-community in future.
-
-%% \paragraph{About the author:} I'm a first-year PhD student in Computer
-%% Science at Universit\'e de Parix XI. My thesis focuses on novel
-%% techniques for optimization on Lie groups (of diffeomorphisms), and
-%% other structured manifolds, the aim being to obtain better algorithms
-%% for nonlinear registration of fMRI brain images and enhance the
-%% charting of human functional connectomes.
-
-\pagebreak
-\bibliographystyle{llcns2e/splncs03}
-\bibliography{bib}
+%% $A \in \mathbb{R}^{5 \times 5}$ with $A(2,0) =
+%% A(4,0) = {-0.5}$, $A(1,3) = {1}$, $A(3,1) =
+%% {-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = {0.25}$.
 

### 2015-07-23 paper.tex
ENH: ready for first arXiv upload

@@
 
+\subsubsection{Yet another notion of approximate equilibrium}
 Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
@@
 \section{Supplementary materials}
-...
- %% , and its
-%% sequence-form is given by:\\
+\paragraph{Sequence-form representation for Kuhn 3-card poker:}
+$E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
+E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
+E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
+E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
+E_1(5,5) = E_1(6,9) = {-1}$; \\
 
-%% $E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
-%% E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
-%% E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
-%% E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
-%% E_1(5,5) = E_1(6,9) = {-1}$; \\
+ $E_2 \in \mathbb{R}^{7 \times 13}$ with
+$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
+E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
+E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
+E_2(5,0) = E_2(6,0) = {-1}$; and \\
 
-%%  $E_2 \in \mathbb{R}^{7 \times 13}$ with
-%% $E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
-%% E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
-%% E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
-%% E_2(5,0) = E_2(6,0) = {-1}$; and \\
-
-%%  $A \in \mathbb{R}^{13 \times
-%%   13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
-%% {-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
-%% A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
-%% A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
-%% $A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
-%% A(12,1) = A(12,5) = {0.166667}$.\\
+ $A \in \mathbb{R}^{13 \times
+  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
+{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
+A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
+A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
+$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
+A(12,1) = A(12,5) = {0.166667}$.\\
 

### 2015-07-23 paper.tex
supp mat section populated

@@
 \section{Supplementary materials}
-\paragraph{Sequence-form representation for Kuhn 3-card poker:}
+\subsection{Sequence-form representation for Kuhn 3-card poker}
 $E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =

### 2015-07-23 paper.tex
fixups

@@
-\documentclass{article} % For LaTeX2e
-\usepackage{nips14submit_e}
+\documentclass{article} % For LaTeX2e\usepackage{nips14submit_e}
 %\documentclass[envcountsame]{llcns2e/llncs}
@@
     primal-dual gap. \textbf{Bottom row}: Evolution of
-    value of game.}
+    value of game...}
   \label{Tab:dgap_curve}
@@
  which agrees to 5 d.p with the value of $-1 / 18$ computed
- analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. The
- evolution of the dual gap and the expected value of the game across
- iterations are shown in Figure \ref{Tab:dgap_curve}.
-More details (payoff matrix, etc.) are provided in
-the supplementary materials...
+ analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. More
+ details (payoff matrix, etc.) are provided in the supplementary
+ materials. The  evolution of the dual gap and the expected value of
+ the game across iterations are shown in Figure \ref{Tab:dgap_curve}.
+We have not benchmarked this against the algorithms proposed in
+\cite{nesterov2005a} and Gilpin's et al. \cite{gilpinfirst} because
+implementing them for such games would require us to compute the
+complicated projections $\prox_{Q_k}$.  We recall that
+avoiding these projections was one of the goals of the present
+manuscript.
 
@@
 imcomplete information (like Texas Hold'em, etc.). Our algorithm is
-simple to implement, with a very low constant cost per iteration, and
+simple to implement, with a low constant cost per iteration, and
 enjoys a rigorous convergence theory with a proven

### 2015-07-23 nesterov.py

@@ -243,7 +243,7 @@ if __name__ == "__main__":
     from primal_dual import primal_dual_sg_ne as alg_1_ne
     rng = np.random.RandomState(42)
     A = np.array([[-2., 3.], [3, -4]])
-    A = rng.randn(50, 50)
+    A = rng.randn(1000, 1000)
     fig1 = plt.figure(figsize=(13.5, 10))
     ax1 = plt.subplot("111")
     plt.grid("on")

### 2015-07-24 paper.tex
cosmetics
wip

--- 2015-07-23 paper.tex
@@
   the number of iterations needed to produce a Nash equilibrium with a
-  given precision is inversely proportional to the desired
+  given precision is inversely proportional to the
   precision. We also present experimental results on simulated and
@@
 \subsection{Nash-equilibrium concepts and statement of the problem}
-The sequence-form representation for two-person zero-sum games with
-imcomplete information was introduced in
+The sequence-form for two-person zero-sum games was introduced in
 \cite{koller1992complexity}, and the theory was further developed in
 \cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
-established that for such games, there exist sparse matrices
+established that for sequential two-person zero-sum games with
+imcomplete information and perfect recall, there exist sparse matrices
 $A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
@@
 pairs $(x, y)$ of \textit{realization plans} which solve the primal
-LCP (Linear Convex Program)
+LCP
 \begin{equation}
@@
 
+\paragraph{Our contribution.}
+Developing on a homologuous and alternative notion of approximate equilibria
+, we device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
+computing approximate Nash equilibria in sequential two-person
+zero-sum games with imcomplete information and perfect recall. We also
+prove that the number of iterations required by the algorithm to
+produce an approximation equilibrium to a precision $\epsilon$ is
+$\mathcal{O}(1/\epsilon)$.
+
 \paragraph{A note about matrix games on simplexes.} It should be
@@
 %% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
-
-\subsection{Our contribution}
-One cannot directly attack the LCPs \eqref{eq:primal_pb} and
-\eqref{eq:dual_pb} via a traditional primal-dual algorithm
-(for example \cite{chambolle2010,chambolle2014ergodic}) because
-computing the euclidean projections $\proj_{Q_k}$ is very difficult
-(in fact, such subproblems would have to be solved
-iteratively\footnote{An ``exception to the rule'' is the case where
-  the $Q_k's$ are simplexes, so that the projections can be computed
-  exactly using \cite{duchi2008efficient}.}). Also,
-the primal-dual gap might explode even at ``nearly feasible'' points,
-leaving a primal-dual algorithm with no clear indication whatsoever,
-on whether progress is being made or not. So need to way to
-\begin{itemize}
-\item[--] avoid having to compute the projections $\proj_{Q_k}$,
-\item[--] have control over how far we are from the set of equilibria and
-  avoid infinite (and thus non-informative) primal-dual gaps.
-\end{itemize}
-
-Developing on an alternative notion of approximate equilibria (see
-Definition \ref{thm:cool_notion})
-homologuous to that presented in Definition \ref{thm:approx_nash}, we
-device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
-computing approximate Nash equilibria in sequential two-person
-zero-sum games with imcomplete information and perfect recall. We also
-prove (Theorem \ref{thm:pd})
-that the number of iterations required by the algorithm to
-produce an approximation equilibrium to a precision $\epsilon$ is
-$\mathcal{O}(1/\epsilon)$.%%  The source of approximation in our scheme
-%% is that we explicitly control how close we are to the feasible set
-%% $Q_1 \times Q_2$.
 
@@
 
-\section{Our contributions}
-\subsection{Reformulation as a Generalized Saddle-point Problem (GSP)}
+\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
 \label{sec:gsp}
+One cannot directly attack the LCPs \eqref{eq:primal_pb} and
+\eqref{eq:dual_pb} via a traditional primal-dual algorithm
+(for example \cite{chambolle2010,chambolle2014ergodic}) because
+computing the euclidean projections $\proj_{Q_k}$ is very difficult
+(in fact, such subproblems would have to be solved
+iteratively\footnote{An ``exception to the rule'' is the case where
+  the $Q_k's$ are simplexes, so that the projections can be computed
+  exactly using \cite{duchi2008efficient}.}). Also,
+the primal-dual gap might explode even at ``nearly feasible'' points,
+leaving a primal-dual algorithm with no clear on whether progress is
+being made or not. So need to way to
+\begin{itemize}
+\item[--] avoid having to compute the projections $\proj_{Q_k}$,
+\item[--] have control over how far we are from the set of equilibria and
+  avoid infinite (and thus non-informative) primal-dual gaps.
+\end{itemize}
+
 In the next theorem, we show that the said LCP problems can be
@@
 
-\subsection{A more amenable notion of approximate equilibria}
-\subsubsection{Interlude: Proximal calculus}
-Let us introduce some notions from modern convex analysis which will be
+\section{A more amenable notion of approximate equilibrium}
+\subsection{Interlude: Proximal calculus}
+Let us introduce some notions in modern convex analysis which will be
 useful in what follows. Given a subset $C$ of $\mathbb{R}^n$,
@@
 
-\subsubsection{Yet another notion of approximate equilibrium}
 Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
@@
 
-Such a vector $v^*$ is called a Nash $(\epsilon_1, \epsilon_2)$-residual at $(x^*,
+Such a vector $v^*$ is called a Nash $\epsilon$-residual at $(x^*,
 y^*, x^*, q^*)$.
@@
 
-\subsection{The proposed primal-dual algorithm}
+\section{The proposed primal-dual algorithm}
 \label{sec:algo}
@@
 
+\subsection{Algorithm and convergence rate}
 \begin{algorithm}
@@
 but has a rich block-diagnoal structure which can be carefully
-exploited, as was done in \cite{hoda2010smoothing}. For the purpose of
-completeness, we explain the details of the tricks used in
-\cite{hoda2010smoothing} for speeding up the computation of these
-matvec products.
+exploited, as was done in \cite{hoda2010smoothing}.
 
-\begin{definition}(Kronecker product)
-Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
-  s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
+%% \begin{definition}(Kronecker product)
+%% Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
+%%   s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
 
-\begin{equation}
-F \otimes B:=\left[
-\begin{array}{cccc}
-F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
-F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
-\vdots & \vdots & \ddots & \vdots\\
-F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
-\end{array}\right] \in \mathbb{R}^{mr \times ns}
-\end{equation}
-\end{definition}
+%% \begin{equation}
+%% F \otimes B:=\left[
+%% \begin{array}{cccc}
+%% F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
+%% F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
+%% \vdots & \vdots & \ddots & \vdots\\
+%% F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
+%% \end{array}\right] \in \mathbb{R}^{mr \times ns}
+%% \end{equation}
+%% \end{definition}
 
-One notes that $(F \otimes B)^T = F^T \otimes B^T$.
-$F \otimes B$ can be very much larger than both $F$ and $B$ in
-dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
-$B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
-$10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
-\mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
-without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
-rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
-  ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
-$s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
-as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
-easily verfies that $Y$ is the matrix product of the ``small''
-matrices $B$, $X$, and $F^T$, i.e
+%% One notes that $(F \otimes B)^T = F^T \otimes B^T$.
+%% $F \otimes B$ can be very much larger than both $F$ and $B$ in
+%% dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
+%% $B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
+%% $10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
+%% \mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
+%% without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
+%% rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
+%%   ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
+%% $s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
+%% as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
+%% easily verfies that $Y$ is the matrix product of the ``small''
+%% matrices $B$, $X$, and $F^T$, i.e
 
-\begin{equation}
-  \label{eq:kron_matvec}
-  Y = BXF^T
-\end{equation}
+%% \begin{equation}
+%%   \label{eq:kron_matvec}
+%%   Y = BXF^T
+%% \end{equation}
 
-Now, in Texas Hold'em for example, the payoff matrix $A$ can be
-written as block-diagonal matrix whose blocks are sums of Kronecker
-products of much smaller sparse matrices as follows
+%% Now, in Texas Hold'em for example, the payoff matrix $A$ can be
+%% written as block-diagonal matrix whose blocks are sums of Kronecker
+%% products of much smaller sparse matrices as follows
 
-\begin{equation}
-  A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
-    \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
-    B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
-\label{eq:factor_A}
-\end{equation}
-See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
-sequences of moves in round $i$ which end in a \textit{fold} action,
-and $S$ to the sequences which end in a \textit{showdown}. $B_i$
-encodes the betting structure of round $i$, while $W$ encodes the
-wind/lose/draw information determined by ranking the players' hands at
-showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
-enough to be explictly represented whereas it is infeasible to
-explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
-$S$, and $W$ are themselves sparse, which allows one to use the
-compressed row storage data structure that only stores nonzero entries
-(for example \textit{scipy.sparse.csr\_matrix}, in the Python
-programming language).
+%% \begin{equation}
+%%   A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
+%%     \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
+%%     B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
+%% \label{eq:factor_A}
+%% \end{equation}
+%% See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
+%% sequences of moves in round $i$ which end in a \textit{fold} action,
+%% and $S$ to the sequences which end in a \textit{showdown}. $B_i$
+%% encodes the betting structure of round $i$, while $W$ encodes the
+%% wind/lose/draw information determined by ranking the players' hands at
+%% showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
+%% enough to be explictly represented whereas it is infeasible to
+%% explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
+%% $S$, and $W$ are themselves sparse, which allows one to use the
+%% compressed row storage data structure that only stores nonzero entries
+%% (for example \textit{scipy.sparse.csr\_matrix}, in the Python
+%% programming language).
 
-Such a representation of the payoff matrix $A$ trivializes matvec
-operations involving $A$ or $A^T$ (thanks to formula
-\eqref{eq:kron_matvec} above, applied to their diagonal blocks and
-exploiting the sparsity of these blocks themselves). Of course, one
-can always write the payoff matrix $A$ of a flop-type Poker game in a
-form similary to \eqref{eq:factor_A} by applying appropriate
-permutations to the enumeration of the players's sequences.
+%% Such a representation of the payoff matrix $A$ trivializes matvec
+%% operations involving $A$ or $A^T$ (thanks to formula
+%% \eqref{eq:kron_matvec} above, applied to their diagonal blocks and
+%% exploiting the sparsity of these blocks themselves). Of course, one
+%% can always write the payoff matrix $A$ of a flop-type Poker game in a
+%% form similary to \eqref{eq:factor_A} by applying appropriate
+%% permutations to the enumeration of the players's sequences.
 
-\paragraph{\textbf{Computing $\|K\|$.}}
-Also the 2-norm $\|K\|$ of the linear operator $K$, can be efficiently
-computed using the power iteration (Perron-Frobenius).
+\paragraph{\textbf{Computing $\|K\|$.}} Power iteration (Perron-Frobenius)...
 
@@
 To access the practical quality of the proposed algorithm, we
-tested it on simulated and real games.
-\paragraph{Basic test-bed: Matrix games on simplexes.}
+experimented it on real games.
+
+\subsection{Basic test-bed: Matrix games on simplexes}
 As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
 \times 1000$ random matrix whose entries are uniformly identically
-distributed in the closed interval $[-1, 1]$. We compared our proposed
-Algorithm \ref{Tab:algo} with Nesterov's \cite{nesterov2005a} and Gilpin's et
-al. \cite{gilpinfirst}. The results of the benchmarks are shown in
-Figure \ref{Tab:dgap_curve}\textit{(a)}...
+distributed in the closed interval $[-1, 1]$.
 
@@
   \subfigure[Matrix game on simplexes]{
-    \includegraphics[width=.5\linewidth]{0.pdf}
+    \includegraphics[width=.33\linewidth]{0.pdf}
   }
-  %% \hspace{-2em}
-  %% \subfigure[Toy Poker]{
-  %%   \includegraphics[width=.5\linewidth]{SimplifiedPoker_dgap.pdf}
-  %% }
+  \hspace{-2em}
+  \subfigure[Toy Poker]{
+    \includegraphics[width=.33\linewidth]{SimplifiedPoker_dgap.pdf}
+  }
   \hspace{-2em}
   \subfigure[Kuhn 3-card Poker]{
-    \includegraphics[width=.5\linewidth]{Kuhn3112_dgap.pdf}
+    \includegraphics[width=.33\linewidth]{Kuhn3112_dgap.pdf}
   }
   \vspace{-1em}
-  \hspace{-2em}
-  \includegraphics[width=.5\linewidth]{1.pdf}
-  %% \hspace{-1em}
-  %% \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
   \hspace{-1em}
-  \includegraphics[width=.5\linewidth]{Kuhn3112_NE.pdf}
+  \includegraphics[width=.34\linewidth]{1.pdf}
+  \hspace{-1em}
+  \includegraphics[width=.33\linewidth]{SimplifiedPoker_NE.pdf}
+  \hspace{-1em}
+  \includegraphics[width=.33\linewidth]{Kuhn3112_NE.pdf}
   \caption{Convergence curves of Algorithm
@@
 
-\paragraph{Experiments on sequential games with imcomplete information: Kuhn 3-card
-  poker.} This game is a simplified form of poker
-developed by Harold W. Kuhn. It is a two-person zero-sum game which is
-simply enough to serve as an example but contains all the complexity
-traits of a imcomplete information sequential game. The
-deck includes only three playing cards, for example a King, Queen, and
-Jack. One card is dealt to each player, then the first player must bet
-or pass, then the second player may bet or pass. If any player chooses
-to bet the opposing player must bet as well ("call") in order to stay
-in the round. After both players pass or bet the player with the
-highest card wins the pot. The
-sequence-form representation of the game has $n_1 = n_2 = 13$
-sequences and $l_1 = l_2 = 7$ information
-sets per player. The pair $(x^*, y^*) \in \mathbb{R}^{13} \times
-\mathbb{R}^{13}$ of realization plans given by
-\begin{eqnarray*}
-  \begin{split}
-    x^* &= [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0,
-      0.275, 0.725]^T,\\
-    y^* &= [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T
-    \end{split}
-\end{eqnarray*}
-is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of
-Algorithm  \ref{Tab:algo}. The convergence curves are shown
-in Fig \ref{Tab:dgap_curve}. One easy checks that this equilibrium is
-feasible. Indeed, $E_1x^* - e_1 = [4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67
-      \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5},
-      -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T$
-and
-$E_2y^* - e_2 = [-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29
-  \times 10^{-6}, -1.50 \times 10^{-6},
-      2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times
-      10^{-7}]^T$.
-Finally, one checks that ${x^*}^TAy^* = {-0.05555}$,
- which agrees to 5 d.p with the value of $-1 / 18$ computed
- analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. The
- evolution of the dual gap and the expected value of the game across
- iterations are shown in Figure \ref{Tab:dgap_curve}.
-More details (payoff matrix, etc.) are provided in
-the supplementary materials...
-
-\section{Concluding remarks}
-Making use of the sequence-form representation
-\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
-deviced a simple and efficient primal-dual algorithm for computing
-Nash equilibria in two-person zero-sum sequential games with
-imcomplete information (like Texas Hold'em, etc.). Our algorithm is
-simple to implement, with a very low constant cost per iteration, and
-enjoys a rigorous convergence theory with a proven
-$\mathcal{O}(1/\epsilon)$ convergence in terms of basic operations
-(matvec products, clipping, etc.), to a Nash
-$(\epsilon,0)$-equilibrium of the game. Equilibrium problems are
-saddle-point convex-concave problems, and as
-such a natural choice for algorithms for solving them would be in the
-family of primal-dual algorithms. We believe such primal-dual
-schemes will receive more attention in the algorithmic game theory
-community in future.
-
-The author's implementation of the proposed algorithm is available
-upon request.
-
-%% \paragraph{About the author:} I'm a first-year PhD student in Computer
-%% Science at Universit\'e de Parix XI. My thesis focuses on novel
-%% techniques for optimization on Lie groups (of diffeomorphisms), and
-%% other structured manifolds, the aim being to obtain better algorithms
-%% for nonlinear registration of fMRI brain images and enhance the
-%% charting of human functional connectomes.
-%\pagebreak
-\bibliographystyle{llcns2e/splncs03}
-\bibliography{bib}
-
-\section{Supplementary materials}
-\subsection{Sequence-form representation for Kuhn 3-card poker}
-$E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
-E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
-E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
-E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
-E_1(5,5) = E_1(6,9) = {-1}$; \\
-
- $E_2 \in \mathbb{R}^{7 \times 13}$ with
-$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
-E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
-E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
-E_2(5,0) = E_2(6,0) = {-1}$; and \\
-
- $A \in \mathbb{R}^{13 \times
-  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
-{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
-A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
-A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
-$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
-A(12,1) = A(12,5) = {0.166667}$.\\
-
-%\paragraph{\textbf{Toy Poker game...}}
+\subsection{Sequential games with imcomplete information}
+\paragraph{\textbf{Toy Poker game...}}
 %% The sequence-form representation for this Toy Poker game is given by
@@
 
+\paragraph{{Kuhn 3-card Poker}} is a simplified form of poker
+developed by Harold W. Kuhn. It is a zero sum two player game. The
+deck includes only three playing cards, for example a King, Queen, and
+Jack. One card is dealt to each player, then the first player must bet
+or pass, then the second player may bet or pass. If any player chooses
+to bet the opposing player must bet as well ("call") in order to stay
+in the round. After both players pass or bet the player with the
+highest card wins the pot. Kuhn demonstrated that there are many game
+theoretic optimal strategies for the first player in this game, but
+only one for the second player, and that, when played optimally, the
+first player should expect to lose at a rate of −1/18 per hand. The
+sequence-form representation of the game has $n_1 = n_2 = 13$
+sequences and $l_1 = l_2 = 7$ information
+sets per player. More details (payoff matrix, etc.) are provided in
+the supp. mats. %% , and its
+%% sequence-form is given by:\\
+
+%% $E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
+%% E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
+%% E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
+%% E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
+%% E_1(5,5) = E_1(6,9) = {-1}$; \\
+
+%%  $E_2 \in \mathbb{R}^{7 \times 13}$ with
+%% $E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
+%% E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
+%% E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
+%% E_2(5,0) = E_2(6,0) = {-1}$; and \\
+
+%%  $A \in \mathbb{R}^{13 \times
+%%   13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
+%% {-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
+%% A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
+%% A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
+%% $A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
+%% A(12,1) = A(12,5) = {0.166667}$.\\
+
+The pair $(x^*, y^*) \in \mathbb{R}^{13} \times \mathbb{R}^{13}$ of
+realization plans given by
+
+\begin{eqnarray*}
+  \begin{split}
+    x^* &= [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0,
+      0.275, 0.725]^T,\\
+    y^* &= [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T
+    \end{split}
+\end{eqnarray*}
+is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of
+Algorithm  \ref{Tab:algo}. The convergence curves are shown
+in Fig \ref{Tab:dgap_curve}. One easy checks that this equilibrium is
+feasible. Indeed,
+
+\begin{eqnarray*}
+  \begin{split}
+    E_1x^* - e_1 = [&4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67
+      \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, \\&
+      -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T
+    \end{split}
+\end{eqnarray*}
+and
+
+\begin{eqnarray*}
+  \begin{split}
+    E_2y^* - e_2 = [&-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29
+      \times 10^{-6}, -1.50 \times 10^{-6},\\
+      &2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times
+      10^{-7}]^T
+    \end{split}
+\end{eqnarray*}
+Finally, one checks that
+\begin{eqnarray*}
+  {x^*}^TAy^* = {-0.05555},
+\end{eqnarray*}
+ which agrees to 5 d.p with the value of $-1 / 18$ computed
+ analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. The
+ evolution of the dual gap and the expected value of the game across
+ iterations are shown in Figure \ref{Tab:dgap_curve}.
+
+\section{Concluding remarks}
+Making use of the sequence-form representation
+\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
+deviced a primal-dual algorithm for computing Nash equilibria in
+two-person zero-sum sequential games with imcomplete information (like
+Texas Hold'em, etc.). Our algorithm is simple to implement, with a
+very low constant cost per iteration, and enjoys a rigorous
+convergence theory with a proven $\mathcal{O}(1/\epsilon)$ convergence
+in terms of basic operations (matvec products, clipping, etc.), to a
+Nash $(\epsilon,0)$-equilibrium of the game.
+Equilibrium problems are saddle-point convex-concave problems, and as
+such a natural choice for algorithms for solving them would be in the
+family of primal-dual algorithms. The author believes such primal-dual
+schemes will receive more attention in the algorithmic game theory
+community in future.
+
+%% \paragraph{About the author:} I'm a first-year PhD student in Computer
+%% Science at Universit\'e de Parix XI. My thesis focuses on novel
+%% techniques for optimization on Lie groups (of diffeomorphisms), and
+%% other structured manifolds, the aim being to obtain better algorithms
+%% for nonlinear registration of fMRI brain images and enhance the
+%% charting of human functional connectomes.
+
+\pagebreak
+\bibliographystyle{llcns2e/splncs03}
+\bibliography{bib}
+
 \end{document}

### 2015-07-24 paper.tex
fixups

--- 2015-07-23 paper.tex
@@
-\documentclass{article} % For LaTeX2e\usepackage{nips14submit_e}
-%\documentclass[envcountsame]{llcns2e/llncs}
+\documentclass{article} % For LaTeX2e
+\usepackage{nips14submit_e}
 \usepackage{url}
@@
 \times 1000$ random matrix whose entries are uniformly identically
-distributed in the closed interval $[-1, 1]$. We compared our proposed
+distributed in the closed interval $[-1, 1]$. We compare our proposed
 Algorithm \ref{Tab:algo} with Nesterov's \cite{nesterov2005a} and Gilpin's et
@@
 sequences and $l_1 = l_2 = 7$ information
-sets per player. The pair $(x^*, y^*) \in \mathbb{R}^{13} \times
+sets per player. More
+ details (payoff matrix, etc.) are provided in the supplementary
+ materials. The pair $(x^*, y^*) \in \mathbb{R}^{13} \times
 \mathbb{R}^{13}$ of realization plans given by
@@
  which agrees to 5 d.p with the value of $-1 / 18$ computed
- analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. More
- details (payoff matrix, etc.) are provided in the supplementary
- materials. The  evolution of the dual gap and the expected value of
+ analytically by H. W. Kuhn in his 1950 paper \cite{kuhn}. The
+ evolution of the dual gap and the expected value of
  the game across iterations are shown in Figure \ref{Tab:dgap_curve}.
@@
 complicated projections $\prox_{Q_k}$.  We recall that
-avoiding these projections was one of the goals of the present
-manuscript.
+avoiding these projections was one of the goals of the manuscript.
 

### 2015-07-24 paper.tex
more

@@
 }}(A^Tx)_i.
+\label{eq:mg_pd}
 \end{eqnarray}
@@
     primal-dual gap. \textbf{Bottom row}: Evolution of
-    value of game...}
+    value of game. In \textit{(a)}, one can see the linear (i.e
+    exponential) of the algorithm in \cite{gilpinfirst}, inbetween
+    consecutive breakpoints on the $\epsilon$ grid. The duality gaps
+    are computed according to formula \eqref{eq:mg_pd}. The
+    first-order smoothing algorithm from \cite{nesterov2005a} jitters around as the
+    iterations go on because even the smoothed problem becomes heavily
+    ill-conditioned near solutions. On the other hand, our propsed
+    algorithm seems to beat both of the aforementioned algorithms, and
+  its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly verified.}
   \label{Tab:dgap_curve}
@@
 sequences and $l_1 = l_2 = 7$ information
-sets per player. More
- details (payoff matrix, etc.) are provided in the supplementary
- materials. The pair $(x^*, y^*) \in \mathbb{R}^{13} \times
-\mathbb{R}^{13}$ of realization plans given by
+sets per player. The sequence-form of the game is given by\\\\
+$E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
+E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
+E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
+E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
+E_1(5,5) = E_1(6,9) = {-1}$; $E_2 \in \mathbb{R}^{7 \times 13}$ with
+$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
+E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
+E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
+E_2(5,0) = E_2(6,0) = {-1}$; and $A \in \mathbb{R}^{13 \times
+  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
+{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
+A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
+A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
+$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
+A(12,1) = A(12,5) = {0.166667}$.\\
+
+The pair of vectors $(x^*, y^*) \in \mathbb{R}^{13 + 13}$ plans given by
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-is a Nash $10^{-4}$-equlibrium computed in 1500 iterations of
+is a Nash $(10^{-4},0)$-equlibrium computed in 1500 iterations of
 Algorithm  \ref{Tab:algo}. The convergence curves are shown
 in Fig \ref{Tab:dgap_curve}. One easy checks that this equilibrium is
-feasible. Indeed, $E_1x^* - e_1 = [4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67
+feasible. Indeed, one computes \\\\
+$E_1x^* - e_1 = [4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67
       \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5},
@@
       2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times
-      10^{-7}]^T$.
+      10^{-7}]^T$.\\\\
 Finally, one checks that ${x^*}^TAy^* = {-0.05555}$,
@@
 
-\section{Supplementary materials}
-\subsection{Sequence-form representation for Kuhn 3-card poker}
-$E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
-E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
-E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
-E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
-E_1(5,5) = E_1(6,9) = {-1}$; \\
-
- $E_2 \in \mathbb{R}^{7 \times 13}$ with
-$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
-E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
-E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
-E_2(5,0) = E_2(6,0) = {-1}$; and \\
-
- $A \in \mathbb{R}^{13 \times
-  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
-{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
-A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
-A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
-$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
-A(12,1) = A(12,5) = {0.166667}$.\\
-
 %\paragraph{\textbf{Toy Poker game...}}

### 2015-07-24 paper.tex
fixups + change font

@@
 \usepackage{url}
-\usepackage{times}
+\usepackage{sans}
 \usepackage{amsmath,amsfonts, amsthm}
@@
   A simple and efficient algorithm for computing approximate
-  Nash equilibria in two-person zero-sum sequential games with imcomplete
+  Nash equilibria in sequential games with imcomplete
   information}
-\author{Elvis DOHMATOB
-\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
+\author{Elvis DOHMATOB%, Gael VAROQUAUX, Bertrand THIRION
+\\\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
 \\\texttt{firstname.lastname@inria.fr}
@@
 \cite{koller1992complexity}, and the theory was further developed in
-\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
+\cite{koller1994fast,von1996efficient,vonequilibrium} where it was
 established that for such games, there exist sparse matrices
@@
 \mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
-\Delta_{n_1} \times \Delta_{n_2}\} = \underset{0 \le j <
-  n_1}{\text{max }}(Ay)_j - \underset{0 \le i < n_2}{\text{min
-}}(A^Tx)_i.
+\Delta_{n_1} \times \Delta_{n_2}\} = \underset{0 \le i <
+  n_1}{\text{max }}(Ay)_i - \underset{0 \le j < n_2}{\text{min
+}}(A^Tx)_j.
 \label{eq:mg_pd}
@@
   exactly using \cite{duchi2008efficient}.}). Also,
-the primal-dual gap might explode even at ``nearly feasible'' points,
+the primal-dual gap might explode nearly the set of feasible points,
 leaving a primal-dual algorithm with no clear indication whatsoever,
@@
 
-\section{Our contributions}
-\subsection{Reformulation as a Generalized Saddle-point Problem (GSP)}
+\section{Methods}
+\subsection{The Generalized Saddle-point Problem (GSP) connection}
 \label{sec:gsp}
-In the next theorem, we show that the said LCP problems can be
+In the next theorem, we show that the LCPs \eqref{eq:primal_pb}
+and \eqref{eq:dual_pb} can be
 conveniently written as a \textit{Generalized Saddle-point Problem
@@
 GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$): Find a quadruplet $(y^*,p^*, x^*, q^*) \in
-S_1 \times S_2$ such that
+S_1 \times S_2$ such that $\forall (y,p, x, q) \in S_1
+    \times S_2$, it holds that
 \begin{eqnarray}
@@
     q^*) \text{ and }\hat{\Psi}_2(y^*, p^*, x^*, q^*)
-    \le \hat{\Psi}_2(y^*, p^*, x, q) \forall (y,p, x, q) \in S_1
-    \times S_2.
+    \le \hat{\Psi}_2(y^*, p^*, x, q).
   \label{eq:unconstrained_pb}
@@
 
-Then a quadruplet $(y^*,p^*, x^*, q^*) \in \mathbb{R}^{n_2}
+Then GSP($\Psi_1$,
+  $\Psi_2$, $g_1$, $g_2$) is equivalent to the Nash equilibrium LCPs
+  \eqref{eq:primal_pb} and \eqref{eq:dual_pb}, i.e
+a quadruplet $(y^*,p^*, x^*, q^*) \in \mathbb{R}^{n_2}
   \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
@@
   \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff it solves
-  GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$). In order words, GSP($\Psi_1$,
-  $\Psi_2$, $g_1$, $g_2$) is equivalent to the Nash equilibrium LCPs
-  \eqref{eq:primal_pb} and \eqref{eq:dual_pb}.
+  GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$). 
   \label{thm:pd}
@@
 
-\subsection{A more amenable notion of approximate equilibria}
-\subsubsection{Interlude: Proximal calculus}
-Let us introduce some notions from modern convex analysis which will be
-useful in what follows. Given a subset $C$ of $\mathbb{R}^n$,
-$i_C$ denotes its \textit{indicator function} defined by
+\subsection{Interlude: Proximal calculus}
+Let us introduce some powerful modern convex-analytical notions which will be
+essential in the sequel.
+Given a subset $C$ of
+$\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined
+by
 \begin{eqnarray}
@@
 At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
-etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
-  convex function. The \textit{effective domain} of $f$, denoted
+etc.). For example, we will write $i_{z \ge 0}$ for
+$i_{\mathbb{R}^n_+}(z)$, etc. Let $f : \mathbb{R}^n \rightarrow
+(-\infty, +\infty]$ be a
+  convex function. The \textit{orthogonal projector} onto $C$, is the
+  ``closes-point function''
+
+  \begin{eqnarray}
+    \proj_C: \mathbb{R}^n \rightarrow C, x \mapsto \underset{z \in
+      C}{\text{argmin }}\frac{1}{2}\|z-x\|^2.
+\end{eqnarray}
+
+The \textit{effective domain} of $f$, denoted
   $dom(f)$, is defined as
@@
 \end{eqnarray}
+Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
+should) be thought of as performing an \textit{implicit} gradient step
+of size $\gamma$.
 
-The interested reader should refer to \cite{combettes2011proximal} for
-a more elaborate exposition of proximal operators and their
-use in modern convex-optimization.
+The interested reader should refer to \cite{combettes2011proximal} and
+the references therewithing, for a more elaborate exposition on
+proximal calculus and its use in modern convex-optimization.
 
-\subsubsection{Yet another notion of approximate equilibrium}
+\subsection{A more comfortable notion of approximate Nash equilibrium}
 Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
@@
 
-\subsection{The proposed primal-dual algorithm}
+\subsection{The proposed algorithm}
 \label{sec:algo}
@@
 \subsection{Practical considerations}
-\paragraph{\textbf{Efficient computation of $Ay$ and $A^Tx$.}}
-In Algorithms \ref{Tab:algo} most of the time is spent
+\paragraph{\textbf{\textit(a) Efficient computation of $Ay$ and $A^Tx$.}}
+In Algorithms \ref{Tab:algo}, most of the time is spent
 pre-multiplying vectors by $A$ and $A^T$. For \textit{flop-type} poker
@@
 
-\paragraph{\textbf{Computing $\|K\|$.}}
+\paragraph{\textit(b) Computing $\|K\|$.}
 Also the 2-norm $\|K\|$ of the linear operator $K$, can be efficiently
@@
 tested it on simulated and real games.
-\paragraph{Basic test-bed: Matrix games on simplexes.}
-As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
-\times 1000$ random matrix whose entries are uniformly identically
-distributed in the closed interval $[-1, 1]$. We compare our proposed
-Algorithm \ref{Tab:algo} with Nesterov's \cite{nesterov2005a} and Gilpin's et
-al. \cite{gilpinfirst}. The results of the benchmarks are shown in
-Figure \ref{Tab:dgap_curve}\textit{(a)}...
-
-\begin{figure}[!htpb]
-  \subfigure[Matrix game on simplexes]{
-    \includegraphics[width=.5\linewidth]{0.pdf}
-  }
-  %% \hspace{-2em}
-  %% \subfigure[Toy Poker]{
-  %%   \includegraphics[width=.5\linewidth]{SimplifiedPoker_dgap.pdf}
-  %% }
-  \hspace{-2em}
-  \subfigure[Kuhn 3-card Poker]{
-    \includegraphics[width=.5\linewidth]{Kuhn3112_dgap.pdf}
-  }
-  \vspace{-1em}
-  \hspace{-2em}
-  \includegraphics[width=.5\linewidth]{1.pdf}
-  %% \hspace{-1em}
-  %% \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
-  \hspace{-1em}
-  \includegraphics[width=.5\linewidth]{Kuhn3112_NE.pdf}
-  \caption{Convergence curves of Algorithm
-    \ref{Tab:algo}. \textbf{Top row}: Evolution of ergodic
-    primal-dual gap. \textbf{Bottom row}: Evolution of
-    value of game. In \textit{(a)}, one can see the linear (i.e
-    exponential) of the algorithm in \cite{gilpinfirst}, inbetween
-    consecutive breakpoints on the $\epsilon$ grid. The duality gaps
-    are computed according to formula \eqref{eq:mg_pd}. The
-    first-order smoothing algorithm from \cite{nesterov2005a} jitters around as the
-    iterations go on because even the smoothed problem becomes heavily
-    ill-conditioned near solutions. On the other hand, our propsed
-    algorithm seems to beat both of the aforementioned algorithms, and
-  its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly verified.}
-  \label{Tab:dgap_curve}
-\end{figure}
-
-\paragraph{Experiments on sequential games with imcomplete information: Kuhn 3-card
+\paragraph{\textit(a) Experiments on sequential games with imcomplete
+  information: Kuhn 3-card
   poker.} This game is a simplified form of poker
@@
 \cite{nesterov2005a} and Gilpin's et al. \cite{gilpinfirst} because
-implementing them for such games would require us to compute the
-complicated projections $\prox_{Q_k}$.  We recall that
+implementing them from scratch for such games would require us to
+compute the complicated projections $\prox_{Q_k}$.  We recall that
 avoiding these projections was one of the goals of the manuscript.
+
+\paragraph{\textit(b) Basic test-bed: Matrix games on simplexes.}
+As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
+\times 1000$ random matrix whose entries are uniformly identically
+distributed in the closed interval $[-1, 1]$. We compare our proposed
+Algorithm \ref{Tab:algo} with Nesterov's \cite{nesterov2005a} and
+Gilpin's et al. \cite{gilpinfirst}. The results of the benchmarks are
+shown in Figure \ref{Tab:dgap_curve}\textit{(a)}.
+
+\begin{figure}[!htpb]
+  \subfigure[$10^3 \times 10^3$ matrix game on simplexes]{
+    \includegraphics[width=.5\linewidth]{0.pdf}
+  }
+  %% \hspace{-2em}
+  %% \subfigure[Toy Poker]{
+  %%   \includegraphics[width=.5\linewidth]{SimplifiedPoker_dgap.pdf}
+  %% }
+  \hspace{-2em}
+  \subfigure[Kuhn 3-card poker]{
+    \includegraphics[width=.5\linewidth]{Kuhn3112_dgap.pdf}
+  }
+  \vspace{-1em}
+  \hspace{-.5em}
+  \includegraphics[width=.5\linewidth]{1.pdf}
+  %% \hspace{-1em}
+  %% \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
+  %\hspace{.5em}
+  \includegraphics[width=.49\linewidth]{Kuhn3112_NE.pdf}
+  \caption{Convergence curves of Algorithm
+    \ref{Tab:algo}. In \textit{(a)}, the duality gaps
+    are computed according to formula \eqref{eq:mg_pd}. One can see
+    the linear (i.e exponential) behavior of the algorithm in
+    \cite{gilpinfirst}, inbetween consecutive breakpoints on the
+    $\epsilon$ grid (though the rate of exponential growth seems to by
+    quite close to $1$ here). The first-order smoothing algorithm from
+    \cite{nesterov2005a} jitters around as the iterations go on
+    because even the smoothed problem becomes heavily ill-conditioned
+    near solutions. On the other hand, our proposed
+    algorithm seems to beat both of the aforementioned algorithms, and
+  its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly
+  verified empirically.}
+  \label{Tab:dgap_curve}
+\end{figure}
 
@@
 
-The author's implementation of the proposed algorithm is available
-upon request.
+\paragraph{Software.} The authors' implementation of the proposed
+algorithm is available upon request.
 
-%% \paragraph{About the author:} I'm a first-year PhD student in Computer
-%% Science at Universit\'e de Parix XI. My thesis focuses on novel
-%% techniques for optimization on Lie groups (of diffeomorphisms), and
-%% other structured manifolds, the aim being to obtain better algorithms
-%% for nonlinear registration of fMRI brain images and enhance the
-%% charting of human functional connectomes.
+%% \paragraph{About the author:} The first author is first-year PhD
+%% student in Computer Science at Universit\'e de Parix XI. My thesis
+%% focuses on novel techniques for optimization on Lie groups (of
+%% diffeomorphisms), and other structured manifolds, the aim being to
+%% obtain better algorithms for nonlinear registration of fMRI brain
+%% images and enhance the charting of human functional connectomes.
+
 %\pagebreak

### 2015-07-25 paper.tex
first WINE submission

@@
   information}
-\author{Elvis DOHMATOB%, Gael VAROQUAUX, Bertrand THIRION
+\author{Elvis DOHMATOB, Gael VAROQUAUX, Bertrand THIRION
 \\\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
@@
   computing approximate Nash equilibria in two-person zero-sum
-  sequential games with  imcomplete information and perfect recall
+  sequential games with  incomplete information and perfect recall
   (like Texas Hold'em Poker). Our algorithm only performs basic
@@
   and is applicable to a broad class of two-person zero-sum games
-  including simultaneous games and sequential games with imcomplete
+  including simultaneous games and sequential games with incomplete
   information and perfect recall. The applicability to the latter kind
@@
 
-\textbf{keywords}: sequential game; imcomplete information; perfect
+\textbf{keywords}: sequential game; incomplete information; perfect
 recall; approximate Nash equilibrium; primal-dual
-algoithm; convex-optimization
+algorithm; convex-optimization
 
@@
 technique is the driving-force behind solution concepts like CFR
-\cite{zinkevich2008regret,lanctot2009monte},
+\cite{zinkevich2008regret,lanctot2009monte,Bowling09012015},
 $\text{CFR}^{+}$ \cite{tammelin14} and other variants, etc., which
@@
 especially in sequential games with imperfect information. This paper
-proposes a simple and fast algorithm for solving for such equilibria
-approximately, in a sense which will be made clear shortly.
+proposes a simple and efficient algorithm for solving for such
+equilibria approximately, in a sense which will be made clear shortly.
 
@@
 The sequence-form representation for two-person zero-sum games with
-imcomplete information was introduced in
+incomplete information was introduced in
 \cite{koller1992complexity}, and the theory was further developed in
@@
 %% $e_2$. 
-At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
-$\tilde{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
+At a feasible point $(y, p, x, q)$ for the LCPs, the \textit{primal-dual gap}
+$\tilde{G}(y, p, x, q)$ of these primal-dual pair is given
 by\footnote{The inequality being due to \textit{weak duality}.}
@@
 \end{eqnarray}
-
+In \eqref{eq:dgap}, the quantity $G(x, y)$ is nothing but the primal-dual
+gap for the equivalent saddle point problem \eqref{eq:gilpin}.
 It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
@@
 computing approximate Nash equilibria in sequential two-person
-zero-sum games with imcomplete information and perfect recall. We also
+zero-sum games with incomplete information and perfect recall. We also
 prove (Theorem \ref{thm:pd})
@@
 produce an approximation equilibrium to a precision $\epsilon$ is
-$\mathcal{O}(1/\epsilon)$.%%  The source of approximation in our scheme
+$\mathcal{O}(1/\epsilon)$. These contributions will be elaborated in
+section \ref{sec:gsp}. %%  The source of approximation in our scheme
 %% is that we explicitly control how close we are to the feasible set
@@
 efforts that have been made in the literature to compute Nash
-$\epsilon$-equilibria for two-person zero-sum games with imcomplete
+$\epsilon$-equilibria for two-person zero-sum games with incomplete
 information like Texas Hold'em Poker, etc.
+
+First and foremost, let us note that for the class of games considered
+here (sequential games with incomplete information), the LCPs
+\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
+than what state-of-the-art LCP and interior-point solvers can
+handle. See for example \cite{hoda2010smoothing,gilpinfirst}.
 
@@
 
-The primal-dual algorithm first developed in \cite{chambolle2010} was
-proposed \cite{chambolle2014ergodic} in to solve matrix games on
-simplexes. It should be stressed that such matrix games are
+The primal-dual algorithm first developed in \cite{chambolle2010}, was
+proposed can be used to solve matrix games on
+simplexes as was done in \cite{chambolle2014ergodic}, for example.
+It should be stressed that such matrix games are
 considerably simpler than the games considered here. Indeed, the
 authors in \cite{chambolle2014ergodic} use the fact that computing the
-euclidean projection of a point unto a simplex can be done in linear
+euclidean projection of a point onto a simplex can be done in linear
 time as in \cite{duchi2008efficient}. In contrast, no such efficient
@@
 Sampling techniques like the CFR (CounterFactual Regret minimization)
-and its many variants
-\cite{MartinZinkevichNIPS2007,lanctot2009monte,Bowling09012015} have
-also become state-of-the-art.
-
-Finally, let us note that for the class of games considered here
-(sequential games with imcomplete information), the LCPs
-\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
-than what state-of-the-art LCP and interior-point solvers can
-handle. See for example \cite{hoda2010smoothing}.
+\cite{zinkevich2008regret,lanctot2009monte,Bowling09012015} have
+also become state-of-the-art, and are particularly useful in
+many-player games, since convex-analytical methods cannot help much in
+such games.
 
 \section{Methods}
+\label{sec:gsp}
 \subsection{The Generalized Saddle-point Problem (GSP) connection}
-\label{sec:gsp}
 In the next theorem, we show that the LCPs \eqref{eq:primal_pb}
@@
 \caption{Primal-dual algorithm for computing approximate Nash
-  Equilbria in two-person zero-sum games with imcomplete information
+  Equilbria in two-person zero-sum games with incomplete information
   and perfect recall}
@@
 tested it on simulated and real games.
-\paragraph{\textit(a) Experiments on sequential games with imcomplete
+\paragraph{\textit(a) Experiments on sequential games with incomplete
   information: Kuhn 3-card
@@
 simply enough to serve as an example but contains all the complexity
-traits of a imcomplete information sequential game. The
+traits of a incomplete information sequential game. The
 deck includes only three playing cards, for example a King, Queen, and
@@
     near solutions. On the other hand, our proposed
-    algorithm seems to beat both of the aforementioned algorithms, and
+    algorithm beats both of the aforementioned algorithms, and
   its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly
@@
 Nash equilibria in two-person zero-sum sequential games with
-imcomplete information (like Texas Hold'em, etc.). Our algorithm is
+incomplete information (like Texas Hold'em, etc.). Our algorithm is
 simple to implement, with a low constant cost per iteration, and

### 2015-07-25 nesterov.py

@@ -243,7 +243,7 @@ if __name__ == "__main__":
     from primal_dual import primal_dual_sg_ne as alg_1_ne
     rng = np.random.RandomState(42)
     A = np.array([[-2., 3.], [3, -4]])
-    A = rng.randn(1000, 1000)
+    A = rng.randn(100, 100)
     fig1 = plt.figure(figsize=(13.5, 10))
     ax1 = plt.subplot("111")
     plt.grid("on")
@@ -269,5 +269,5 @@ if __name__ == "__main__":
         ax.tick_params(axis='both', which='major', labelsize=50)
         ax.legend(loc="best", prop=dict(size=45), handlelength=1.5)
         plt.tight_layout()
-        plt.savefig("%i.pdf" % i)
+        # plt.savefig("%i.pdf" % i)
     plt.show()

### 2015-07-25 primal_dual.py

@@ -13,6 +13,16 @@ from scipy import linalg
 _norm = lambda *args: sqrt(np.sum(np.concatenate(args) ** 2))
 
 
+def _check_subgradient(f, x, g, n=10):
+    """Checks that g is a sub-gradient of f at x."""
+    from sklearn.utils import check_random_state
+    rng = check_random_state(42)
+    p = len(x)
+    for z in rng.randn(n, p):
+        if f(z) < f(x) + np.dot(g, z - x): return False
+    return True
+
+
 def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
                    proj_C2=lambda y: np.maximum(y, 0.), init=None,
                    epsilon=1e-4, max_iter=10000, callback=None):
@@ -58,6 +68,9 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
 
     # main loop
     for k in range(max_iter):
+        # invoke callback
+        if callback and callback(locals()): break
+
         # save previous iterates
         old_y = y.copy()
         old_p = p.copy()
@@ -96,12 +109,9 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
                     delta_q_sum) / lambd / (k + 1.)
         gaps.append(gap)
 
-        # invoke callback
-        if callback and callback(locals()): break
+        # check convergence
         print ("Iter %03i/%03i: game value = %g, primal-dual gap (perturbed) ="
                " %.2e") % (k + 1, max_iter, value, gap)
-
-        # check convergence
         if gap < epsilon:
             print "Converged (gap < gap epsilon = %.2e)." % epsilon
             break

### 2015-07-25 paper.tex
more

@@
 
-\textbf{keywords}: sequential game; incomplete information; perfect
-recall; approximate Nash equilibrium; primal-dual
-algorithm; convex-optimization
+\textbf{keywords}: algorithmic-game theory; sequential game;
+incomplete information; perfect recall; approximate Nash equilibrium;
+primal-dual algorithm; convex-optimization
 
@@
 L_{yx} = \|K\|$. Now, one easily computes the proximal operator of
-$g_j$ in closed-form as $\prox_{\lambda g_j}(z, v) \equiv ((z)_+,
-v - \lambda e_j)$. With all these ingredients in place, Algorithm
+$g_j$ in closed-form as $\prox_{\lambda g_j}(a, b) \equiv ((a)_+,
+b - \lambda e_j)$. With all these ingredients in place, Algorithm
 \ref{Tab:algo} is then obtained from \cite[Algorithm
@@
 In Algorithms \ref{Tab:algo}, most of the time is spent
-pre-multiplying vectors by $A$ and $A^T$. For \textit{flop-type} poker
+pre-multiplying vectors by $A$ and $A^T$ (precisely 3 such operations
+are done per iteration). For \textit{flop-type} poker
 games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
-$A$ (and thus $A^T$ too)  is very big (up $10^{100}$ rows and columns!)
+$A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
 but has a rich block-diagnoal structure which can be carefully

### 2015-07-25 nesterov.py

@@ -243,14 +243,14 @@ if __name__ == "__main__":
     from primal_dual import primal_dual_sg_ne as alg_1_ne
     rng = np.random.RandomState(42)
     A = np.array([[-2., 3.], [3, -4]])
-    A = rng.randn(100, 100)
+    A = rng.randn(10, 10)
     fig1 = plt.figure(figsize=(13.5, 10))
     ax1 = plt.subplot("111")
     plt.grid("on")
     fig2 = plt.figure(figsize=(13.5, 10))
     ax2 = plt.subplot("111")
     plt.grid("on")
-    for solver in ["alg 1", "gilpin", "nesterov"]:
+    for solver in ["alg 1", "gilpin", "nesterov"][:1]:
         x, u, values, gaps = eval("%s_ne" % solver.replace(" ", "_").replace(
             "-", "_"))(A, epsilon=1e-4, max_iter=100000)
         ax1.loglog(gaps, label="\\textbf{%s}" % _cap(solver), linewidth=6)

### 2015-07-25 primal_dual.py

@@ -5,6 +5,7 @@ zero-sum games.
 """
 # author: Elvis Dohmatob <gmdopp@gmail.com>
 
+import numbers
 from math import sqrt
 import numpy as np
 from scipy import linalg
@@ -19,13 +20,50 @@ def _check_subgradient(f, x, g, n=10):
     rng = check_random_state(42)
     p = len(x)
     for z in rng.randn(n, p):
+        z += x
+        print f(z), f(x) + np.dot(g, z - x)
         if f(z) < f(x) + np.dot(g, z - x): return False
     return True
 
 
+class _GSPEnergy(object):
+    """This object is useful for checking
+    v \in \partial [Phi_1(., ., x_, q_) + Phi_2(y_, p_, ., .)](y_, p_, x_, q_)
+    """
+    def __init__(self, K, e1, e2, y_, p_, x_, q_):
+        self.K = K
+        self.e1 = np.array([e1]) if isinstance(e1, numbers.Number) else e1
+        self.e2 = np.array([e2]) if isinstance(e2, numbers.Number) else e2
+        self.y_ = y_
+        self.p_ = p_
+        self.x_ = x_
+        self.q_ = q_
+        self.l1_ = len(self.e1)
+        self.l2_ = len(self.e2)
+        self.n2_ = K.shape[0] - self.l1_
+        self.n1_ = K.shape[1] - self.l2_
+        self.yp_ = np.concatenate((y_, p_))
+        self.xq_ = np.concatenate((x_, q_))
+
+    def __call__(self, ypxq):
+        yp = ypxq[:self.K.shape[1]]
+        y, p = yp[:self.n2_], yp[self.n2_:]
+        y = np.maximum(0., y)
+        yp = np.concatenate((y, p))
+        xq = ypxq[self.K.shape[1]:]
+        x, q = xq[:self.n1_], xq[self.n1_:]
+        x = np.maximum(0., x)
+        xq = np.concatenate((x, q))
+        if not np.all(y >= 0.) or not np.all(x >= 0.): return np.inf
+        a = self.xq_.dot(self.K.dot(yp)) + self.e1.dot(p)
+        b = -xq.dot(self.K.dot(self.yp_)) + self.e2.dot(q)
+        return a + b
+
+
 def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
                    proj_C2=lambda y: np.maximum(y, 0.), init=None,
[…]

### 2015-07-25 simple.py

@@ -455,7 +455,7 @@ if __name__ == "__main__":
 
     rng = check_random_state(42)
     max_iter = 10000
-    game_clses = ["simplex", SimplifiedPoker, Kuhn3112][1:]
+    game_clses = ["simplex", SimplifiedPoker, Kuhn3112][2:]
     for cnt, game_cls in enumerate(game_clses):
         if game_cls == "simplex":
             game = None

### 2015-07-27 paper.tex
fixups (after arXiv version 1 --still pending, btw)

@@
   information}
-\author{Elvis DOHMATOB, Gael VAROQUAUX, Bertrand THIRION
+\author{Elvis DOHMATOB%, Gael VAROQUAUX, Bertrand THIRION
 \\\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
@@
   sequential games with  incomplete information and perfect recall
-  (like Texas Hold'em Poker). Our algorithm only performs basic
+  (like Texas Hold'em poker). Our algorithm only performs basic
   iterations (i.e iterations involving no calls to external
@@
 $\text{CFR}^{+}$ \cite{tammelin14} and other variants, etc., which
-have recently had profound success in Poker. However, solving games
+have recently had profound success in poker. However, solving games
 for equilibria remains a mathematical and computational challenge,
@@
 denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
-not $1$). The notation ``$z \ge 0$'' means that all the components of
+not $1$). $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ }
+z \geq 0\}$ is the nonnegative $n$th \textit{orthant}.
+The notation ``$z \ge 0$'' means that all the components of
 $z$ are nonnegative.
-$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
-0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  $\|z\|$ denotes the
-$2$-\textit{norm} of $z$ defined by $\|z\| := \sqrt{\langle z,
-  z\rangle}$. $(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the
-point-wise maximum of $z$ with $0$. For example, $((-2, \pi))_+ =
-(max(-2, 0), max(\pi, 0)) = (0, \pi)$. The operator $(.)_+$ is the
-well-known (multi-dimensional) \textit{ramp} function. The
-$n$-simplex denoted $\Delta_n$, is defined by $\Delta_n := \{z \in
-\mathbb{R}^n_+|\sum_j z_j = 1\}$.
+$\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| :=
+\sqrt{\langle z, z\rangle}$. $(z)_+:=\text{max}(0, z) \in
+\mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
+example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
+operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
+function. The $n$-simplex denoted $\Delta_n$, is defined by $\Delta_n
+:= \{z \in \mathbb{R}^n_+|\sum_j z_j = 1\}$.
 Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
@@
   exactly using \cite{duchi2008efficient}.}). Also,
-the primal-dual gap might explode nearly the set of feasible points,
-leaving a primal-dual algorithm with no clear indication whatsoever,
-on whether progress is being made or not. So need to way to
+the primal-dual gap might explode even at points arbitrarily close to
+the set of feasible points, leaving the algorithm with no indication
+whatsoever, on whether progress is being made or not. So need to way to
 \begin{itemize}
@@
 Definition \ref{thm:cool_notion})
-homologuous to that presented in Definition \ref{thm:approx_nash}, we
+homologous to that presented in Definition \ref{thm:approx_nash}, we
 device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
@@
 zero-sum games with incomplete information and perfect recall. We also
-prove (Theorem \ref{thm:pd})
-that the number of iterations required by the algorithm to
-produce an approximation equilibrium to a precision $\epsilon$ is
-$\mathcal{O}(1/\epsilon)$. These contributions will be elaborated in
-section \ref{sec:gsp}. %%  The source of approximation in our scheme
+prove (Theorem \ref{thm:pd}) that --in an ergodic sense-- the number of
+iterations required by the algorithm to produce an approximation
+equilibrium to a precision $\epsilon$ is $\mathcal{O}(1/\epsilon)$,
+with explicit values for the constants involved this worst-case cost.
+These contributions will be elaborated in section \ref{sec:gsp}.
+%%  The source of approximation in our scheme
 %% is that we explicitly control how close we are to the feasible set
@@
 $\epsilon$-equilibria for two-person zero-sum games with incomplete
-information like Texas Hold'em Poker, etc.
-
+information like Texas Hold'em poker, etc.
 First and foremost, let us note that for the class of games considered
@@
 iteration loop.
-
 \cite{gilpinfirst} proposed a modified verson of the technqiues in
@@
 \subsection{Interlude: Proximal calculus}
-Let us introduce some powerful modern convex-analytical notions which will be
-essential in the sequel.
-Given a subset $C$ of
+Let us introduce some basic but powerful modern convex-analytical
+notions which will be essential in the sequel. Given a subset $C$ of
 $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined
@@
 exploiting the sparsity of these blocks themselves). Of course, one
-can always write the payoff matrix $A$ of a flop-type Poker game in a
+can always write the payoff matrix $A$ of a flop-type poker game in a
 form similary to \eqref{eq:factor_A} by applying appropriate
@@
   %% \hspace{-2em}
-  %% \subfigure[Toy Poker]{
+  %% \subfigure[Toy poker]{
   %%   \includegraphics[width=.5\linewidth]{SimplifiedPoker_dgap.pdf}

### 2015-07-28 paper.tex
polyhedron changed to polytope (since bounded provably)

@@
 \usepackage[FIGTOPCAP]{subfigure}
+\usepackage{caption}
 
@@
 \subsection{Nash-equilibrium concepts and statement of the problem}
+
 The sequence-form representation for two-person zero-sum games with
@@
 $A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
-entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
-$(1, 0, ..., 0)$. In this so-called \textit{sequence-form}
-representation, the strategy profile of player $k$ is the convex polyhedron
-\begin{equation}
-  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\}.
-\label{eq:polyhedron}
-\end{equation}
+entries are $-1$, $0$ or $1$, with exactly 1 entry equal -1 per row, and each $e_k$ is a vector of the form
+$(1, 0, ..., 0)$.
 
+\begin{figure}[!h]
+\begin{minipage}{.65\linewidth}
+%\caption*{\textbf{Sparse-Variation.}
 Note that the LCPs above have the equivalent saddle point formulation
@@
   \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
-    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle
+    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle,
   \label{eq:gilpin}
 \end{equation}
-
-%% Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle
-%% = q_0$ by definition of $e_1$ and
-%% $e_2$. 
+where the \textit{convex polytope} (by which we mean a bounded convex
+polyhedron)
+\begin{equation}
+  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\} \subseteq
+  [0, 1]^{n_k}
+\label{eq:polytope}
+\end{equation}
+is the the strategy profile of player $k$ in this representation.
 At a feasible point $(y, p, x, q)$ for the LCPs, the \textit{primal-dual gap}
@@
   \begin{split}
-  0 \le \tilde{G}(y, p, x, q) &:= \langle e_1, p\rangle - (-\langle
+  0 &\le \tilde{G}(y, p, x, q) := \langle e_1, p\rangle - (-\langle
   e_2, q\rangle) = \langle e_1, p\rangle + \langle
@@
 \end{eqnarray}
+%}
+\end{minipage}
+\hspace{.5em}
+\begin{minipage}{.4\linewidth}
+  \includegraphics[width=1\linewidth]{grain4.png}
+  \caption{A convex polytope}
+  \label{fig:roi}
+\end{minipage}
+\end{figure}
+
 In \eqref{eq:dgap}, the quantity $G(x, y)$ is nothing but the primal-dual
@@
 profile is a simplex; this simplex can be written in the form
-\eqref{eq:polyhedron} by taking $E_k := (1, 1, ..., 1) \in
+\eqref{eq:polytope} by taking $E_k := (1, 1, ..., 1) \in
 \mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
@@
 games in particular. Here, the polyhedral strategy profiles $Q_k$
-defined in \eqref{eq:polyhedron} reduce to simplexes $\Delta_{n_k}$,
+defined in \eqref{eq:polytope} reduce to simplexes $\Delta_{n_k}$,
 and the primal-dual gap function $G(x,y)$ writes
@@
 (for example \cite{chambolle2010,chambolle2014ergodic}) because
-computing the euclidean projections $\proj_{Q_k}$ is very difficult
+computing the orthogonal projections $\proj_{Q_k}$ is very difficult
 (in fact, such subproblems would have to be solved
@@
 authors in \cite{chambolle2014ergodic} use the fact that computing the
-euclidean projection of a point onto a simplex can be done in linear
+orthogonal projection of a point onto a simplex can be done in linear
 time as in \cite{duchi2008efficient}. In contrast, no such efficient
 algorithm is known nor is likely to exist for the polyhedra $Q_k$
-defined in \eqref{eq:polyhedron}, the strategy profiles for players in
+defined in \eqref{eq:polytope}, the strategy profiles for players in
 the games considered here. It should however be noted that such this
@@
 \end{eqnarray*}
-where the second equality follows from the zero-sum condition $\Psi_1 + \Psi_2
-:= 0$.
+where the second equality follows from the zero-sum condition $\Psi_1
++ \Psi_2 := 0$.
 \end{proof}
@@
 \eqref{eq:unconstrained_pb}, which as it turns out, is simpler
-conceptually. The rest of the paper will be devoted to
-developing an algorithm for solving the latter.
+conceptually (for example, we no longer need to compute the
+complicated orthogonal projections $\proj_{Q_k}$). The rest of the
+paper will be devoted to developing an algorithm for solving the latter.
 
@@
 \begin{theorem}[Ergodic $\mathcal{O}(1/\epsilon)$ convergence]
-Let $d_0$ be the euclidean distance between the starting point
+Let $d_0$ be the orthogonal distance between the starting point
 $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the

### 2015-07-28 paper.tex
fixups before final arXiv upload (version 1)

@@
   (like Texas Hold'em poker). Our algorithm only performs basic
-  iterations (i.e iterations involving no calls to external
-  first-order oracles, etc.)
+  iterations (i.e matvec multiplications, clipping, etc., and no calls
+  to external first-order oracles, no matrix inversions, etc.)
   and is applicable to a broad class of two-person zero-sum games
@@
   \cite{koller1992complexity} which allows us to encode any such game
-  as a matrix game with polyhedral strategy profiles. We prove that
+  as a matrix game with convex polytopial profiles. We prove that
   the number of iterations needed to produce a Nash equilibrium with a
@@
 $A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
-entries are $-1$, $0$ or $1$, with exactly 1 entry equal -1 per row, and each $e_k$ is a vector of the form
-$(1, 0, ..., 0)$.
+entries are $-1$, $0$ or $1$, with exactly 1 entry per row which
+equals $-1$ except for the first whose whose first entry is $1$ and all
+the others are $0$. Each of the vectors $e_k$ is of the form $(1, 0, ..., 0)$.
 
@@
 \end{equation}
-is the the strategy profile of player $k$ in this representation.
-At a feasible point $(y, p, x, q)$ for the LCPs, the \textit{primal-dual gap}
-$\tilde{G}(y, p, x, q)$ of these primal-dual pair is given
-by\footnote{The inequality being due to \textit{weak duality}.}
+is identified with the strategy profile of player $k$ in the
+sequence-form representation. At a feasible point $(y, p, x, q)$ for
+the LCPs, the \textit{primal-dual gap} $\tilde{G}(y, p, x, q)$ of
+these primal-dual pair is given by\footnote{The inequality being due
+  to \textit{weak duality}.}
 \begin{eqnarray}
@@
 results presented in this manuscript can be trivially applied such
-games in particular. Here, the polyhedral strategy profiles $Q_k$
+games in particular. Here, the polytopial $Q_k$
 defined in \eqref{eq:polytope} reduce to simplexes $\Delta_{n_k}$,
@@
 computing the orthogonal projections $\proj_{Q_k}$ is very difficult
-(in fact, such subproblems would have to be solved
+In fact, such subproblems would have to be solved
 iteratively\footnote{An ``exception to the rule'' is the case where
   the $Q_k's$ are simplexes, so that the projections can be computed
-  exactly using \cite{duchi2008efficient}.}). Also,
+  exactly using \cite{duchi2008efficient}.}. Also,
 the primal-dual gap might explode even at points arbitrarily close to
@@
 \begin{itemize}
-\item[--] avoid having to compute the projections $\proj_{Q_k}$,
-\item[--] have control over how far we are from the set of equilibria and
-  avoid infinite (and thus non-informative) primal-dual gaps.
+\item[(1)] avoid having to compute the projections $\proj_{Q_k}$,
+\item[(2)] have control over how far we are from the set of
+  equilibria and avoid infinite (and thus non-informative) primal-dual
+  gaps.
 \end{itemize}
@@
 homologous to that presented in Definition \ref{thm:approx_nash}, we
-device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
+device a primal-dual algorithm that (Algorithm \ref{Tab:algo}) for
 computing approximate Nash equilibria in sequential two-person
-zero-sum games with incomplete information and perfect recall. We also
+zero-sum games with incomplete information and perfect recall, and
+which satisfies the above crucial requirements (1)--(2). We also
 prove (Theorem \ref{thm:pd}) that --in an ergodic sense-- the number of
@@
 \label{sec:related_work}
-We present a selection of algorithms that is representative of the
+We now present a selection of algorithms that is representative of the
 efforts that have been made in the literature to compute Nash
@@
 In \cite{hoda2010smoothing}, a nested iterative procedure using the
-Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used to
+Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used
 to solve the equilibrium problem \eqref{eq:gilpin}.
@@
 The primal-dual algorithm first developed in \cite{chambolle2010}, was
-proposed can be used to solve matrix games on
-simplexes as was done in \cite{chambolle2014ergodic}, for example.
-It should be stressed that such matrix games are
+proposed in \cite{chambolle2014ergodic} as a way of solving matrix
+games on. It should be stressed that such matrix games on simplexes are
 considerably simpler than the games considered here. Indeed, the
-authors in \cite{chambolle2014ergodic} use the fact that computing the
+authors in \cite{chambolle2014ergodic} used the fact that computing the
 orthogonal projection of a point onto a simplex can be done in linear
 time as in \cite{duchi2008efficient}. In contrast, no such efficient
-algorithm is known nor is likely to exist for the polyhedra $Q_k$
-defined in \eqref{eq:polytope}, the strategy profiles for players in
-the games considered here. It should however be noted that such this
-projection can still be done iteratively using, for example, the
-algorithm in proposition 4.2 of \cite{combettes2010dualization} or the
-algorithms developed in \cite{tran2015splitting}. Unfortunately, as
-with any nested iterative scheme, one would have to solve this
-sub-problem with finer and finer precision.
+algorithm is known nor is likely to exist, for the polytopes $Q_k$
+defined in \eqref{eq:polytope}.%% , the strategy profiles for players in
+%% the games considered here.
+That notwithstanding, such projections can still be done iteratively
+using for example, the algorithm in proposition 4.2 of
+\cite{combettes2010dualization} or the algorithms developed in
+\cite{tran2015splitting}. Unfortunately, as with any nested iterative
+scheme, one would have to solve this sub-problem with finer and finer
+precision.
 
@@
 \begin{proof}
-Note that $dom(g_1) = S_1$ and $dom(g_2) = S_2$ and observe that since the
-equilibria of the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb}, and
-the equilibria of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$) are contained
-in $S_1 \times S_2$, it suffices to show that at any point $(y, p, x,
+It suffices to show that at any point $(y, p, x,
 q) \in S_1 \times S_2$, the primal-dual gap between the primal
@@
 The interested reader should refer to \cite{combettes2011proximal} and
-the references therewithing, for a more elaborate exposition on
+the references therewithin, for a more elaborate exposition on
 proximal calculus and its use in modern convex-optimization.
@@
 \subsection{A more comfortable notion of approximate Nash equilibrium}
+\begin{definition}
   Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
@@
 \end{eqnarray}
-
+\end{definition}
 The idea behind $\epsilon$-subgradients is the following. Say we wish
@@
 \label{sec:algo}
-We now derive and establish the theoretical properties of the
-algorithm which is the main object of this manuscript.
+We now derive the algorithm (Algorithm \ref{Tab:algo}) which is the
+  main object of this
+manuscript, and establish the theoretical properties.
 
@@
 \leftarrow 0$
-\While{$\|{v}_{a}^{(k)}\|/k \ge \epsilon$}
+\While{$\|{v}_{a}^{(k)}\| \ge \epsilon$}
 \State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
@@
 \hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
-\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
-\frac{1}{\lambda}(\Delta
-y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
+\State ${v}_a^{(k+1)} \leftarrow \frac{1}{\lambda}\frac{1}{k+1}(y^{(k+1)} -
+y^{(0)}, p^{(k+1)} - p^{(0)}, x^{(k+1)} - x^{(0)}, q^{(k+1)} - q^{(0)})$ 
 \State $k \leftarrow k + 1$
@@
 the algorithm produces the following a quadruplet
-$(y^{k_0},p^{k_0},x^{k_0},q^{k_0})$ and a vector $v^{k_0}$ such that
+$(y^{k_0},p^{k_0},x^{k_0},q^{k_0})$ and a vector $v_a^{k_0}$ such that
 \begin{eqnarray}
-\|v^{k_0}\| \le \epsilon \text{ and}\hspace{.5em} v^{k_0} \in
+\|v_a^{k_0}\| \le \epsilon \text{ and}\hspace{.5em} v_a^{k_0} \in
 \partial[\hat{\Psi}_1(., ., x^{k_0}, q^{k_0}) +
@@
       1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
-      \lambda_{xy}]$. The convergence result follows immediately from
+      \lambda_{xy}]$. Finally, note that $v_a^{(k+1)}$ as defined in
+  line 8 of Algorithm \ref{Tab:algo} simply correponds to the the
+  average difference in the iterates (this is a teloscopic sum),
+  scaled by $\lambda$. The convergence result follows immediately from
   \cite[Theorem 4.2]{he2013accelerating}.
@@
 developed by Harold W. Kuhn. It is a two-person zero-sum game which is
-simply enough to serve as an example but contains all the complexity
-traits of a incomplete information sequential game. The
-deck includes only three playing cards, for example a King, Queen, and
+simple enough to serve as a proof-of-concept example but contains all
+the complexity traits of a incomplete information sequential game. The
+deck includes only three playing cards: a King, Queen, and
 Jack. One card is dealt to each player, then the first player must bet
@@
 (matvec products, clipping, etc.), to a Nash
-$(\epsilon,0)$-equilibrium of the game. Equilibrium problems are
-saddle-point convex-concave problems, and as
+$(\epsilon,0)$-equilibrium of the game.
+
+Equilibrium problems are saddle-point convex-concave problems, and as
 such a natural choice for algorithms for solving them would be in the

### 2015-07-28 nesterov.py

@@ -250,7 +250,7 @@ if __name__ == "__main__":
     fig2 = plt.figure(figsize=(13.5, 10))
     ax2 = plt.subplot("111")
     plt.grid("on")
-    for solver in ["alg 1", "gilpin", "nesterov"][:1]:
+    for solver in ["alg 1", "gilpin", "nesterov"]:
         x, u, values, gaps = eval("%s_ne" % solver.replace(" ", "_").replace(
             "-", "_"))(A, epsilon=1e-4, max_iter=100000)
         ax1.loglog(gaps, label="\\textbf{%s}" % _cap(solver), linewidth=6)

### 2015-07-28 paper.tex
typo
multiple fixups

@@
   \begin{aligned}
-     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
-       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
-     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
+    \underset{(y,p) \in \mathbb{R}^{n_2} \times
+     \mathbb{R}^{l_1}}{\text{minimize }}\langle e_1,
+    p\rangle \hspace{.5em}\text{
+       subject to: } y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
   \end{aligned}
@@
   \begin{aligned}
-    \text{maximize}-\langle e_2, q\rangle,\hspace{.5em}\text{subject
-      to: }(x,q) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2},  x \ge
+    \underset{(x,q) \in \mathbb{R}^{n_1} \times
+      \mathbb{R}^{l_2}}{\text{maximize }}-\langle e_2,
+    q\rangle\hspace{.5em}\text{subject
+      to: } x \ge
     0, E_1x = e_1, A^Tx + E_2^Tq \geq 0.
@@
 which satisfies the above crucial requirements (1)--(2). We also
-prove (Theorem \ref{thm:pd}) that --in an ergodic sense-- the number of
+prove (Theorem \ref{thm:pd}) that --in an ergodic / Ces\`ario sense-- the number of
 iterations required by the algorithm to produce an approximation
@@
 proposed in \cite{chambolle2014ergodic} as a way of solving matrix
-games on. It should be stressed that such matrix games on simplexes are
-considerably simpler than the games considered here. Indeed, the
-authors in \cite{chambolle2014ergodic} used the fact that computing the
-orthogonal projection of a point onto a simplex can be done in linear
-time as in \cite{duchi2008efficient}. In contrast, no such efficient
-algorithm is known nor is likely to exist, for the polytopes $Q_k$
-defined in \eqref{eq:polytope}.%% , the strategy profiles for players in
-%% the games considered here.
+games on simplexes. It should be stressed that such matrix games on
+simplexes are considerably simpler than the games considered
+here. Indeed, the authors in \cite{chambolle2014ergodic} used the fact
+that computing the orthogonal projection of a point onto a simplex can
+be done in linear time as in \cite{duchi2008efficient}. In contrast,
+no such efficient algorithm is known nor is likely to exist, for the
+polytopes $Q_k$ defined in \eqref{eq:polytope}.%% , the strategy
+%% profiles for players in %% the games considered here.
 That notwithstanding, such projections can still be done iteratively
@@
 conveniently written as a \textit{Generalized Saddle-point Problem
-  (GSP)} in the sense of \cite{he2013accelerating}.
+  (GSP)} in the sense of \cite{he2013accelerating}. The crux of idea
+is to remove the linear constraints in the definitions of the strategy
+polytopes $Q_k$, by modifying the payoff matrix to yield an equivalent
+saddle-point problem.
 \begin{theorem}
@@
 
-and, define the functions $\hat{\Psi}_1$, $\hat{\Psi}_2:
+and define the functions $\hat{\Psi}_1$, $\hat{\Psi}_2:
 \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}
@@
 \begin{algorithmic}[1]
-\Require $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
-\in \mathbb{R}^{n_2}
+\Require $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)}) \in \mathbb{R}^{n_2}
   \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
@@
 the GSP \eqref{eq:unconstrained_pb}.
-\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
+\State  $\lambda \leftarrow 1/\|K\|$, ${v}^{(0)} \leftarrow 0$, $k
 \leftarrow 0$
-\While{$\|{v}_{a}^{(k)}\| \ge \epsilon$}
+\While{ $ k = 0$ or  $\frac{1}{k\lambda}\|v^{(k)}\| \ge \epsilon$}
 \State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
@@
 \hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
-\State ${v}_a^{(k+1)} \leftarrow \frac{1}{\lambda}\frac{1}{k+1}(y^{(k+1)} -
-y^{(0)}, p^{(k+1)} - p^{(0)}, x^{(k+1)} - x^{(0)}, q^{(k+1)} - q^{(0)})$ 
+\State ${v}^{(k+1)} \leftarrow {v}^{(k)} + (\Delta
+y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$ 
 \State $k \leftarrow k + 1$
@@
 
-\begin{theorem}[Ergodic $\mathcal{O}(1/\epsilon)$ convergence]
+\begin{theorem}[Ergodic / Ces\`ario $\mathcal{O}(1/\epsilon)$ convergence]
 Let $d_0$ be the orthogonal distance between the starting point
@@
 the algorithm produces the following a quadruplet
-$(y^{k_0},p^{k_0},x^{k_0},q^{k_0})$ and a vector $v_a^{k_0}$ such that
+$(y^{k_0},p^{k_0},x^{k_0},q^{k_0})$ and a vector $v^{k_0}$ such that
 \begin{eqnarray}
@@
 \partial[\hat{\Psi}_1(., ., x^{k_0}, q^{k_0}) +
-  \hat{\Psi}_2(y^{k_0}, p^{k_0}, ., .)](y^{k_0},p^{k_0},x^{k_0},q^{k_0}).
+  \hat{\Psi}_2(y^{k_0}, p^{k_0}, ., .)](y^{k_0},p^{k_0},x^{k_0},q^{k_0}),
 \end{eqnarray}
-
+where $v_a^{(k_0)} := \frac{1}{k\lambda}v^{(k_0)}$.
 Thus Algorithm \ref{Tab:algo} outputs an $(\epsilon,0)$-Nash
@@
       1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
-      \lambda_{xy}]$. Finally, note that $v_a^{(k+1)}$ as defined in
-  line 8 of Algorithm \ref{Tab:algo} simply correponds to the the
-  average difference in the iterates (this is a teloscopic sum),
-  scaled by $\lambda$. The convergence result follows immediately from
+      \lambda_{xy}]$. The convergence result follows immediately from
   \cite[Theorem 4.2]{he2013accelerating}.

### 2015-08-10 paper.tex
typos + fixups

@@
 
-\subsection{Notation and terminology}
+\paragraph{Notation and terminology.}
 Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
@@
     p\rangle \hspace{.5em}\text{
-       subject to: } y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
+       subject to: } y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0,
   \end{aligned}
@@
 sequence-form representation. At a feasible point $(y, p, x, q)$ for
-the LCPs, the \textit{primal-dual gap} $\tilde{G}(y, p, x, q)$ of
-these primal-dual pair is given by\footnote{The inequality being due
-  to \textit{weak duality}.}
+the LCPs, the \textit{primal-dual gap} $\tilde{G}(y, p, x, q)$ is
+given by\footnote{The first inequality being due to \textit{weak
+    duality}.}
 \begin{eqnarray}
@@
 \begin{minipage}{.4\linewidth}
-  \includegraphics[width=1\linewidth]{grain4.png}
+  \includegraphics[width=1\linewidth]{polytope.png}
   \caption{A convex polytope}
@@
 
-The pair of vectors $(x^*, y^*) \in \mathbb{R}^{13 + 13}$ plans given by
+The pair of vectors $(x^*, y^*) \in \mathbb{R}^{13 + 13}$ given by
 \begin{eqnarray*}
@@
 
-\section{Concluding remarks}
+\section{Concluding remarks and future work}
 Making use of the sequence-form representation

### 2015-08-10 nesterov.py

@@ -15,7 +15,7 @@ def proj_simplex(v, z=1.):
     """
     # deterministic O(n log n)
     u = np.sort(v)[::-1]  # sort v in increasing order
-    aux = (np.cumsum(u) - z) / np.arange(1., len(v) + 1.)
+    aux = (u.cumsum() - z) / np.arange(1., len(v) + 1.)
     return np.maximum(v - aux[np.nonzero(u > aux)[0][-1]], 0.)
 
 

### 2015-08-24 paper.tex
fixups

@@
 \usepackage{url}
-\usepackage{sans}
+\usepackage{times}
 \usepackage{amsmath,amsfonts, amsthm}
@@
   convex function. The \textit{orthogonal projector} onto $C$, is the
-  ``closes-point function''
+  ``closest-point function''
 
@@
 %%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
-The \textit{subgradient} of $f$ is the set-valued function
+The \textit{subdifferential} of $f$ at a point $x \in \mathbb{R}^n$ is
+defined by
 \begin{eqnarray}
-\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
-\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
-z \in \mathbb{R}^n\}.
+\partial f(x) := \{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z -
+x\rangle, \forall z \in \mathbb{R}^n\}.
 \end{eqnarray}
-Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
+Each element of $\partial f(x)$ is called a \textit{subgradient} of $f$
+at $x$. Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
 in case $f$ is differentiable at $x$. If $f$ is convex, its
@@
   Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
-  \rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
-  $\epsilon$-subgradient, for short) of $f$ is the set-valued function
+  \rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subdifferential (or
+  $\epsilon$-subdifferential, for short) of $f$ is the set-valued function
   \begin{eqnarray}
@@
 \end{definition}
-The idea behind $\epsilon$-subgradients is the following. Say we wish
+The idea behind $\epsilon$-subdifferentials is the following. Say we wish
 to minimize the function $f$. Replace the usual necessary
@@
 
-This approximation concept for subgradients yields the following
+This approximation concept for subdifferentials yields the following
 concept of approximate Nash equlibria (adapted from

### 2015-09-26 paper.tex
larger margins
ran aspell on .tex

@@
-\documentclass{article} % For LaTeX2e
-\usepackage{nips14submit_e}
-\usepackage{url}
+% Template for ISBI-2013 paper; to be used with:
+%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
+%          IEEEbib.bst - IEEE bibliography style file.
+% --------------------------------------------------------------------------
+\documentclass[a4paper,9pt]{extarticle}
+\usepackage{spconf,amsmath,amsfonts,amsthm,amssymb,graphicx}
+\usepackage{algorithm,algorithmicx,algpseudocode}
 \usepackage{times}
-\usepackage{amsmath,amsfonts, amsthm}
-\usepackage{bbm}
-\usepackage{algorithm,algorithmicx}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage{bbm}
-\usepackage[titletoc]{appendix}
-\usepackage{algpseudocode}
-\usepackage{pifont}
-\usepackage[FIGTOPCAP]{subfigure}
+\usepackage[font={small}]{caption}
+\usepackage{subfigure}
+\usepackage{wrapfig}
 \usepackage{caption}
+\usepackage{transparent}
+\usepackage{xcolor,colortbl}
+\usepackage{dcolumn}
 
-\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
+%% squeezing
+\linespread{0.85}
+\usepackage[compact]{titlesec}
+%\titlespacing{\section}{0pt}{2ex}{1ex}
+\titlespacing{\subsection}{0pt}{1ex}{0ex}
+\titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}
 
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{definition}[theorem]{Definition}
+%\def\baselinestretch{0.98}
+
+% Example definitions.
+% --------------------
+\def\x{{\mathbf x}}
+\def\L{{\cal L}}
+
+% Title.
+% ------
+\title{ A simple and efficient algorithm for computing approximate
+  Nash equilibria in sequential games with incomplete
+  information}
+
+%
+% Single address.
+% ---------------
+\name{Elvis Dohmatob}
+\address{Parietal Team, INRIA, Universit\'e de Paris-Saclay}
+%
+% For example:
+% ------------
+%\address{School\\
+%	Department\\
+%	Address}
+%
+% Two addresses (uncomment and modify for two-address case).
+% ----------------------------------------------------------
+%\twoauthors
+ %% {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
+ %%        {School A-B\\
+ %%        Department A-B\\
+ %%        Address A-B}
+ %% {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
+ %%        while at ...}}
+ %%        {School C-D\\
+ %%        Department C-D\\
+ %%        Address C-D}
+%
+% More than two addresses
+% -----------------------
+% \name{Author Name$^{\star \dagger}$ \qquad Author Name$^{\star}$ \qquad Author Name$^{\dagger}$}
+%
+% \address{$^{\star}$ Affiliation Number One \\
+%     $^{\dagger}$}Affiliation Number Two
+%
+
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
+\DeclareMathOperator{\proj}{proj}
+\DeclareMathOperator{\soft}{soft}
+\DeclareMathOperator{\prox}{prox}
+\DeclareMathOperator{\Prox}{Prox}
+\DeclareMathOperator{\im}{im}
+\DeclareMathOperator{\rank}{rank}
+\DeclareMathOperator{\supp}{supp}
+
+% macros from michael's .tex
+\DeclareMathOperator{\dist}{dist} % The distance.
+\DeclareMathOperator{\argmin}{argmin}
+\DeclareMathOperator{\argmax}{argmax}
+\DeclareMathOperator{\Id}{Id}
+\DeclareMathOperator{\abs}{abs}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\N}{\mathbb{N}}
+\newtheorem{thm}{Theorem}[section]
+\newtheorem{prop}[thm]{Proposition}
+\newtheorem{lemma}[thm]{Lemma}
+\newtheorem{corollary}[thm]{Corollary}
+\newtheorem{definition}{Definition}
+\newtheorem{theorem}{Theorem}
 \newtheorem{remark}{Remark}
-\newtheorem{fact}{Fact}
-
-\DeclareMathOperator{\proj}{proj}
-\DeclareMathOperator{\prox}{prox}
-
-\title{
-  %\hrule\hrule\bigskip\bigskip
-  A simple and efficient algorithm for computing approximate
-  Nash equilibria in sequential games with imcomplete
-  information}
-\author{Elvis DOHMATOB%, Gael VAROQUAUX, Bertrand THIRION
-\\\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
-\\\texttt{firstname.lastname@inria.fr}
-}
-
-% The \author macro works with any number of authors. There are two commands
-% used to separate the names and addresses of multiple authors: \And and \AND.
-%
-% Using \And between authors leaves it to \LaTeX{} to determine where to break
-% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
-% puts 3 of 4 authors names on the first line, and the last on the second
-% line, try using \AND instead of \And before the third author name.
-
-%\nipsfinalcopy % Uncomment for camera-ready version
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 A game-theoretic approach to playing games strategically optimally
-consists in computing Nash-equilibria (infact, approximations thereof)
+consists of computing Nash-equilibria (in fact, approximations thereof)
 offline, and playing one's part (an optimal \textit{behavioral}
@@
 \cite{zinkevich2008regret,lanctot2009monte,Bowling09012015},
-$\text{CFR}^{+}$ \cite{tammelin14} and other variants, etc., which
+$\text{CFR}^{+}$ \cite{tammelin14} and other variants, which
 have recently had profound success in poker. However, solving games
@@
 
-\paragraph{Notation and terminology.}
+\subsection{Notation and terminology}
 Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
@@
 
-\subsection{Nash-equilibrium concepts and statement of the problem}
+Let us introduce some basic but powerful modern convex-analytical
+notions which will be essential in the sequel. Given a subset $C$ of
+$\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined
+by $i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
+    otherwise}$.
+At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
+etc.). For example, we will write $i_{z \ge 0}$ for
+$i_{\mathbb{R}^n_+}(z)$, etc. Let $f : \mathbb{R}^n \rightarrow
+(-\infty, +\infty]$ be a
+  convex function. The \textit{orthogonal projector} onto $C$, is the
+  ``closest-point function'' $\proj_C: \mathbb{R}^n \rightarrow C, x
+  \mapsto \underset{z \in
+      C}{\text{argmin }}\frac{1}{2}\|z-x\|^2$.
+The \textit{effective domain} of $f$, denoted
+  $dom(f)$, is defined as
+$dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$.
+ If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
+%% \textit{proper convex lower semi-continous function}
+%% (\textit{p.c.l.s.c} for short).
+%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
+%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
+%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
+The \textit{subdifferential} of $f$ at a point $x \in \mathbb{R}^n$ is
+defined by
+$\partial f(x) := \{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z -
+x\rangle, \forall z \in \mathbb{R}^n\}$.
+%% Each element of $\partial f(x)$ is called a \textit{subgradient} of $f$
+%% at $x$. Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
+%% in case $f$ is differentiable at $x$.
+If $f$ is convex, its
+\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
+\rightarrow \mathbb{R}^n$ defined by $\prox_f(x): = \underset{z \in
+  \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
+  - x\|^2 + f(z)$.
+%% For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
+%% $\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
+%% operators generalize orthogonal projectors. For example
+%% $\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
+%% (z)_+$. One also has the useful characterization
+%% \begin{eqnarray}
+%%   p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
+%% \end{eqnarray}
+%% Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
+%% should) be thought of as performing an \textit{implicit} gradient step
+%% of size $\gamma$.
+
+The interested reader should refer to \cite{combettes2011proximal} and
+the references therein, for a more elaborate exposition on
+proximal calculus and its use in modern convex-optimization.
+
+\subsection{Statement of the problem}
 
@@
     p\rangle \hspace{.5em}\text{
-       subject to: } y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0,
+       subject to: } &y \ge 0, E_2y = e_2,\\
+    &-Ay + E_1^Tp \geq 0,
   \end{aligned}
@@
     q\rangle\hspace{.5em}\text{subject
-      to: } x \ge
-    0, E_1x = e_1, A^Tx + E_2^Tq \geq 0.
+      to: } &x \ge
+    0, E_1x = e_1,\\
+    &A^Tx + E_2^Tq \geq 0.
   \end{aligned}
@@
 
-\begin{figure}[!h]
-\begin{minipage}{.65\linewidth}
-%\caption*{\textbf{Sparse-Variation.}
 Note that the LCPs above have the equivalent saddle point formulation
@@
 \end{eqnarray}
-%}
-\end{minipage}
-\hspace{.5em}
-\begin{minipage}{.4\linewidth}
-  \includegraphics[width=1\linewidth]{polytope.png}
-  \caption{A convex polytope}
-  \label{fig:roi}
-\end{minipage}
-\end{figure}
 
@@
 \begin{equation}
-\hspace{.25em} -Ay + E_1^Tp \ge 0, \hspace{.5em}A^Tx + E_2^Tq \ge
-0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0, \hspace{.25em}
-\langle y, A^Tx  + E_2^Tq\rangle = 0.
+\begin{split}
+\hspace{.25em} -Ay + E_1^Tp \ge 0, &\hspace{.5em}A^Tx + E_2^Tq \ge
+0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0,\\
+&\langle y, A^Tx  + E_2^Tq\rangle = 0.
+\end{split}
 \label{eq:feasibility}
@@
 
-\paragraph{A note about matrix games on simplexes.} It should be
-noted
+\begin{remark}
+It should be noted
 that any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
@@
 and the primal-dual gap function $G(x,y)$ writes
-\begin{eqnarray}G(x, y) =
+\begin{eqnarray}
+\begin{split}
+G(x, y) &=
 \mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
-\Delta_{n_1} \times \Delta_{n_2}\} = \underset{0 \le i <
+\Delta_{n_1} \times \Delta_{n_2}\}\\
+&= \underset{0 \le i <
   n_1}{\text{max }}(Ay)_i - \underset{0 \le j < n_2}{\text{min
 }}(A^Tx)_j.
+\end{split}
 \label{eq:mg_pd}
 \end{eqnarray}
+\end{remark}
 
-%% As usual, the ``minimax'' notation in problem \eqref{eq:primal_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution if (and only if)
-%% \begin{equation}
-%%   x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
-%% \label{eq:nash_ineq}
-%% \end{equation}
-%% Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
-%% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.
-
-\subsection{Our contribution}
+\subsection{Quick sketch of our contribution}
 One cannot directly attack the LCPs \eqref{eq:primal_pb} and
@@
 computing the orthogonal projections $\proj_{Q_k}$ is very difficult
-In fact, such subproblems would have to be solved
+In fact, such sub-problems would have to be solved
 iteratively\footnote{An ``exception to the rule'' is the case where
@@
 iteration loop.
-\cite{gilpinfirst} proposed a modified verson of the technqiues in
+\cite{gilpinfirst} proposed a modified version of the techniques in
 \cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
@@
 
-Sampling techniques like the CFR (CounterFactual Regret minimization)
-\cite{zinkevich2008regret,lanctot2009monte,Bowling09012015} have
-also become state-of-the-art, and are particularly useful in
-many-player games, since convex-analytical methods cannot help much in
-such games.
+CFR (CounterFactual Regret minimization) \cite{zinkevich2008regret},
+Monte Carlo CFR \cite{lanctot2009monte}, and CFR+
+\cite{Bowling09012015} have also become state-of-the-art, and are
+particularly useful in many-player games, since convex-analytical
+methods cannot help much in such games.
 
@@
 \begin{equation}
+  \begin{split}  
     K :=
@@
     := \left\langle \begin{bmatrix}x\\q\end{bmatrix},
-      K\begin{bmatrix}y\\p\end{bmatrix}\right\rangle = \langle x,
-      Ay\rangle -\langle x, E_1^Tp\rangle + \langle q, E_2y\rangle,
+      K\begin{bmatrix}y\\p\end{bmatrix}\right\rangle%% \\
+      %% &= \langle x,
+      %% Ay\rangle -\langle x, E_1^Tp\rangle + \langle q, E_2y\rangle,
+\end{split}
 \end{equation}
@@
 \begin{eqnarray}
-  \left.
   \begin{aligned}
-    \hat{\Psi}_1(y, p, x, q) &:=
-    \Psi_1(y, p, x, q)+ g_1(y, p) \text{ if }y \ge 0, \hat{\Psi}_1(y,
-    p, x, q) := \infty \text{ otherwise}\\
-    \hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(x, q) \text{ if
-    }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ otherwise}.
+    \hat{\Psi}_1(y, p, x, q) :=\begin{cases}
+    \Psi_1(y, p, x, q)+ g_1(y, p), &\mbox{ if }y \ge 0,\\
+    +\infty, &\mbox{ otherwise}\end{cases}\\
+    %% &\hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(x, q) \text{ if
+    %% }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ otherwise}.
+    \hat{\Psi}_2(y, p, x, q) :=\begin{cases}
+    \Psi_2(y, p, x, q)+ g_2(y, p), &\mbox{ if }x \ge 0,\\
+    +\infty, &\mbox{ otherwise}\end{cases}
   \end{aligned}
-  \right\}
 \end{eqnarray}
@@
 \begin{eqnarray}
-    \hat{\Psi}_1(y^*, p^*, x^*, q^*) \le \hat{\Psi}_1(y, p, x^*,
-    q^*) \text{ and }\hat{\Psi}_2(y^*, p^*, x^*, q^*)
+  \begin{split}
+    &\hat{\Psi}_1(y^*, p^*, x^*, q^*) \le \hat{\Psi}_1(y, p, x^*,
+    q^*),\\
+    &\hat{\Psi}_2(y^*, p^*, x^*, q^*)
     \le \hat{\Psi}_2(y^*, p^*, x, q).
   \label{eq:unconstrained_pb}
+\end{split}
 \end{eqnarray}
@@
   \begin{aligned}
-    a(y,p) &= \langle e_1,p\rangle + i_{y\ge 0} + i_{-Ay + E_1^Tp \ge 0} +
+    &a(y,p) = \langle e_1,p\rangle + i_{y\ge 0} + i_{-Ay + E_1^Tp \ge 0} +
     i_{E_2y = e_2}\\
@@
       q'}{\text{max}}\text{ }\langle x',Ay\rangle - \langle x',
-    E_1^Tp\rangle + \langle q',E_2y\rangle -
+    E_1^Tp\rangle + \langle q',E_2y\rangle\\
+    &\hspace{10em}-
     (i_{x' \ge 0} + \langle e_2,q\rangle)\\
@@
       - \underset{x',q'}{\text{min}}\text{ }\Psi_2(y, p, x', q') + g_2(x',
-      q') = g_1(y,p)
+      q')\\
+      &= g_1(y,p)
       - \underbrace{\underset{x',q'}{\text{min}}\text{
-        }\hat{\Psi}_2(y, p, x', q')}_{\phi_2(y,p)}\\
-      &= g_1(y, p) - \phi_2(y, p).
+        }\hat{\Psi}_2(y, p, x', q')}_{\phi_2(y,p)}
+      = g_1(y, p) - \phi_2(y, p).
   \end{aligned}
@@
   \begin{aligned}
- b(x, q) &= 
+&b(x, q) = 
 -\langle q, e_2\rangle -i_{x \ge 0} - i_{A^Tx+E_2^Tq \ge 0} -
@@
  +\underset{y',p'}{\text{min}}\text{ }\Psi_1(y', p', x, q) +
- g_1(y', p') = -g_2(x, q)
- +\underbrace{\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p',
-   x, q)}_{\phi_1(x, q)}\\
- &= -g_2(x, q) + \phi_1(x, q). 
+ g_1(y', p')\\
+& = -g_2(x, q) +
+ \underbrace{\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p',
+   x, q)}_{\phi_1(x, q)} = -g_2(x, q) + \phi_1(x, q). 
    \end{aligned}
@@
   \begin{split}
-  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
+    &a(y, p) - b(x, q) = g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
   q) \\
   &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
-  q) + g_2(x, q) - \phi_1(x, q)\\
+  q) + g_2(x, q) \\
+  &\hspace{2em}- \phi_1(x, q)\\
   &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
@@
 
-By Theorem \ref{thm:pd}, solviing for a Nash equilibrium for
+By Theorem \ref{thm:pd}, solving for a Nash equilibrium for
 the game is equivalent to solving the GSP
@@
 
-\subsection{Interlude: Proximal calculus}
-Let us introduce some basic but powerful modern convex-analytical
-notions which will be essential in the sequel. Given a subset $C$ of
-$\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined
-by
-\begin{eqnarray}
-  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
-    otherwise.}
-\end{eqnarray}
-At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
-etc.). For example, we will write $i_{z \ge 0}$ for
-$i_{\mathbb{R}^n_+}(z)$, etc. Let $f : \mathbb{R}^n \rightarrow
-(-\infty, +\infty]$ be a
-  convex function. The \textit{orthogonal projector} onto $C$, is the
-  ``closest-point function''
-
-  \begin{eqnarray}
-    \proj_C: \mathbb{R}^n \rightarrow C, x \mapsto \underset{z \in
-      C}{\text{argmin }}\frac{1}{2}\|z-x\|^2.
-\end{eqnarray}
-
-The \textit{effective domain} of $f$, denoted
-  $dom(f)$, is defined as
-\begin{eqnarray}
-  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
-\end{eqnarray}
- If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
-%% \textit{proper convex lower semi-continous function}
-%% (\textit{p.c.l.s.c} for short).
-%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
-%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
-%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
-The \textit{subdifferential} of $f$ at a point $x \in \mathbb{R}^n$ is
-defined by
-\begin{eqnarray}
-\partial f(x) := \{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z -
-x\rangle, \forall z \in \mathbb{R}^n\}.
-\end{eqnarray}
-Each element of $\partial f(x)$ is called a \textit{subgradient} of $f$
-at $x$. Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
-in case $f$ is differentiable at $x$. If $f$ is convex, its
-\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
-\rightarrow \mathbb{R}^n$ defined by
-\begin{eqnarray}
-  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
-  - x\|^2 + f(z).
-\end{eqnarray}
-For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
-$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
-operators generalize orthogonal projectors. For example
-$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
-(z)_+$. One also has the useful characterization
-\begin{eqnarray}
-  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
-\end{eqnarray}
-Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
-should) be thought of as performing an \textit{implicit} gradient step
-of size $\gamma$.
-
-The interested reader should refer to \cite{combettes2011proximal} and
-the references therewithin, for a more elaborate exposition on
-proximal calculus and its use in modern convex-optimization.
-
 \subsection{A more comfortable notion of approximate Nash equilibrium}
@@
   Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
-  \rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subdifferential (or
-  $\epsilon$-subdifferential, for short) of $f$ is the set-valued function
+  \rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged
+  subdifferential (or
+  $\epsilon$-subdifferential, for short) of $f$ is the set-valued
+  function defined by
   \begin{eqnarray}
-\partial_\epsilon f: \mathbb{R}^n \rightarrow
-2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
+\partial_\epsilon f(x):= \{s \in \mathbb{R}^n | f(z)
 \ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
@@
 there exists a perturbation vector $v^*$ such that
-\begin{eqnarray}
-\|v^*\| \le \epsilon_1 \text{ and}\hspace{.5em} v^* \in
+$\|v^*\| \le \epsilon_1$ and $v^* \in
 \partial_{\epsilon_2}[\hat{\Psi}_1(., ., x^*, q^*) +
-  \hat{\Psi}_2(y^*, p^*, ., .)](y^*,p^*,x^*,q^*).
-\end{eqnarray}
+  \hat{\Psi}_2(y^*, p^*, ., .)](y^*,p^*,x^*,q^*)$.
 
-Such a vector $v^*$ is called a Nash $(\epsilon_1, \epsilon_2)$-residual at $(x^*,
+Such a vector $v^*$ is called a Nash $(\epsilon_1,
+\epsilon_2)$-residual at the point $(x^*,
 y^*, x^*, q^*)$.
@@
 $k_0 \le \frac{2d_0\|K\|}{\epsilon}$ such that after $k_0$ iterations
-the algorithm produces the following a quadruplet
+the algorithm produces a quadruplet
 $(y^{k_0},p^{k_0},x^{k_0},q^{k_0})$ and a vector $v^{k_0}$ such that
-\begin{eqnarray}
-\|v_a^{k_0}\| \le \epsilon \text{ and}\hspace{.5em} v_a^{k_0} \in
+$\|v_a^{k_0}\| \le \epsilon$ and $v_a^{k_0} \in
 \partial[\hat{\Psi}_1(., ., x^{k_0}, q^{k_0}) +
-  \hat{\Psi}_2(y^{k_0}, p^{k_0}, ., .)](y^{k_0},p^{k_0},x^{k_0},q^{k_0}),
-\end{eqnarray}
+  \hat{\Psi}_2(y^{k_0}, p^{k_0}, ., .)](y^{k_0},p^{k_0},x^{k_0},q^{k_0})$,
 where $v_a^{(k_0)} := \frac{1}{k\lambda}v^{(k_0)}$.
@@
 \subsection{Practical considerations}
-\paragraph{\textbf{\textit(a) Efficient computation of $Ay$ and $A^Tx$.}}
+\paragraph*{\textbf{\textit(a) Efficient computation of $Ay$ and $A^Tx$.}}
 In Algorithms \ref{Tab:algo}, most of the time is spent
@@
 $A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
-but has a rich block-diagnoal structure which can be carefully
-exploited, as was done in \cite{hoda2010smoothing}. For the purpose of
-completeness, we explain the details of the tricks used in
-\cite{hoda2010smoothing} for speeding up the computation of these
-matvec products.
+but has a rich block-diagonal structure (each block is itself the
+Kronecker product of smaller matrices) which can be carefully
+exploited, as was done in \cite{hoda2010smoothing}.%%  For the purpose of
+%% completness, we explain the details of the tricks used in
+%% \cite{hoda2010smoothing} for speeding up the computation of these
+%% matvec products.
 
-\begin{definition}(Kronecker product)
-Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
-  s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
+%% \begin{definition}(Kronecker product)
+%% Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
+%%   s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
 
-\begin{equation}
-F \otimes B:=\left[
-\begin{array}{cccc}
-F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
-F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
-\vdots & \vdots & \ddots & \vdots\\
-F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
-\end{array}\right] \in \mathbb{R}^{mr \times ns}
-\end{equation}
-\end{definition}
+%% \begin{equation}
+%% F \otimes B:=\left[
+%% \begin{array}{cccc}
+%% F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
+%% F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
+%% \vdots & \vdots & \ddots & \vdots\\
+%% F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
+%% \end{array}\right] \in \mathbb{R}^{mr \times ns}
+%% \end{equation}
+%% \end{definition}
 
-One notes that $(F \otimes B)^T = F^T \otimes B^T$.
-$F \otimes B$ can be very much larger than both $F$ and $B$ in
-dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
-$B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
-$10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
-\mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
-without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
-rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
-  ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
-$s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
-as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
-easily verfies that $Y$ is the matrix product of the ``small''
-matrices $B$, $X$, and $F^T$, i.e
+%% One notes that $(F \otimes B)^T = F^T \otimes B^T$.
+%% $F \otimes B$ can be very much larger than both $F$ and $B$ in
+%% dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
+%% $B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
+%% $10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
+%% \mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
+%% without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
+%% rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
+%%   ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
+%% $s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
+%% as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
+%% easily verfies that $Y$ is the matrix product of the ``small''
+%% matrices $B$, $X$, and $F^T$, i.e
 
-\begin{equation}
-  \label{eq:kron_matvec}
-  Y = BXF^T
-\end{equation}
+%% \begin{equation}
+%%   \label{eq:kron_matvec}
+%%   Y = BXF^T
+%% \end{equation}
 
-Now, in Texas Hold'em for example, the payoff matrix $A$ can be
-written as block-diagonal matrix whose blocks are sums of Kronecker
-products of much smaller sparse matrices as follows
+%% Now, in Texas Hold'em for example, the payoff matrix $A$ can be
+%% written as block-diagonal matrix whose blocks are sums of Kronecker
+%% products of much smaller sparse matrices as follows
 
-\begin{equation}
-  A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
-    \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
-    B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
-\label{eq:factor_A}
-\end{equation}
-See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
-sequences of moves in round $i$ which end in a \textit{fold} action,
-and $S$ to the sequences which end in a \textit{showdown}. $B_i$
-encodes the betting structure of round $i$, while $W$ encodes the
-wind/lose/draw information determined by ranking the players' hands at
-showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
-enough to be explictly represented whereas it is infeasible to
-explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
-$S$, and $W$ are themselves sparse, which allows one to use the
-compressed row storage data structure that only stores nonzero entries
-(for example \textit{scipy.sparse.csr\_matrix}, in the Python
-programming language).
+%% \begin{equation}
+%%   A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
+%%     \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
+%%     B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
+%% \label{eq:factor_A}
+%% \end{equation}
+%% See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
+%% sequences of moves in round $i$ which end in a \textit{fold} action,
+%% and $S$ to the sequences which end in a \textit{showdown}. $B_i$
+%% encodes the betting structure of round $i$, while $W$ encodes the
+%% wind/lose/draw information determined by ranking the players' hands at
+%% showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
+%% enough to be explictly represented whereas it is infeasible to
+%% explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
+%% $S$, and $W$ are themselves sparse, which allows one to use the
+%% compressed row storage data structure that only stores nonzero entries
+%% (for example \textit{scipy.sparse.csr\_matrix}, in the Python
+%% programming language).
 
-Such a representation of the payoff matrix $A$ trivializes matvec
-operations involving $A$ or $A^T$ (thanks to formula
-\eqref{eq:kron_matvec} above, applied to their diagonal blocks and
-exploiting the sparsity of these blocks themselves). Of course, one
-can always write the payoff matrix $A$ of a flop-type poker game in a
-form similary to \eqref{eq:factor_A} by applying appropriate
-permutations to the enumeration of the players's sequences.
+%% Such a representation of the payoff matrix $A$ trivializes matvec
+%% operations involving $A$ or $A^T$ (thanks to formula
+%% \eqref{eq:kron_matvec} above, applied to their diagonal blocks and
+%% exploiting the sparsity of these blocks themselves). Of course, one
+%% can always write the payoff matrix $A$ of a flop-type poker game in a
+%% form similary to \eqref{eq:factor_A} by applying appropriate
+%% permutations to the enumeration of the players's sequences.
 
-\paragraph{\textit(b) Computing $\|K\|$.}
+\paragraph*{\textit(b) Computing $\|K\|$.}
 Also the 2-norm $\|K\|$ of the linear operator $K$, can be efficiently
@@
 \label{sec:results}
-To access the practical quality of the proposed algorithm, we
+To assess the practical quality of the proposed algorithm, we
 tested it on simulated and real games.
-\paragraph{\textit(a) Experiments on sequential games with incomplete
+\paragraph*{Experiments on sequential games with incomplete
   information: Kuhn 3-card
@@
 in the round. After both players pass or bet the player with the
-highest card wins the pot. The
-sequence-form representation of the game has $n_1 = n_2 = 13$
-sequences and $l_1 = l_2 = 7$ information
-sets per player. The sequence-form of the game is given by\\\\
-$E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
-E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
-E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
-E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
-E_1(5,5) = E_1(6,9) = {-1}$; $E_2 \in \mathbb{R}^{7 \times 13}$ with
-$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
-E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
-E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
-E_2(5,0) = E_2(6,0) = {-1}$; and $A \in \mathbb{R}^{13 \times
-  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
-{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
-A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
-A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
-$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
-A(12,1) = A(12,5) = {0.166667}$.\\
+highest card wins the pot.%%  The
+%% sequence-form representation of the game has $n_1 = n_2 = 13$
+%% sequences and $l_1 = l_2 = 7$ information
+%% sets per player. The sequence-form of the game is given by\\\\
+%% $E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
+%% E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
+%% E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
+%% E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
+%% E_1(5,5) = E_1(6,9) = {-1}$; $E_2 \in \mathbb{R}^{7 \times 13}$ with
+%% $E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
+%% E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
+%% E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
+%% E_2(5,0) = E_2(6,0) = {-1}$; and $A \in \mathbb{R}^{13 \times
+%%   13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
+%% {-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
+%% A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
+%% A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
+%% $A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
+%% A(12,1) = A(12,5) = {0.166667}$.\\
 
@@
   \begin{split}
-    x^* &= [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0,
-      0.275, 0.725]^T,\\
-    y^* &= [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T
+    &x^* = [1, .759, .759, 0, .241, 1, .425, .575, 0, .275, 0,
+      .275, .725]^T,\\
+    &y^* = [1, 1, 0, .667, .333, .667, .333, 1, 0, 0, 1, 0, 1]^T
     \end{split}
 \end{eqnarray*}
-is a Nash $(10^{-4},0)$-equlibrium computed in 1500 iterations of
+is a Nash $(10^{-4},0)$-equilibrium computed in 1500 iterations of
 Algorithm  \ref{Tab:algo}. The convergence curves are shown
@@
 
-\paragraph{\textit(b) Basic test-bed: Matrix games on simplexes.}
+\paragraph*{Basic test-bed: Matrix games on simplexes.}
 As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
@@
 \cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
-deviced a simple and efficient primal-dual algorithm for computing
+devised a simple and efficient primal-dual algorithm for computing
 Nash equilibria in two-person zero-sum sequential games with
@@
 such a natural choice for algorithms for solving them would be in the
-family of primal-dual algorithms. We believe such primal-dual
-schemes will receive more attention in the algorithmic game theory
-community in future.
+family of primal-dual algorithms. %%  We believe such primal-dual
+%% schemes will receive more attention in the algorithmic game theory
+%% community in future.
 
-\paragraph{Software.} The authors' implementation of the proposed
-algorithm is available upon request.
+%% \paragraph{Software.} The authors' implementation of the proposed
+%% algorithm is available upon request.
 

### 2015-09-26 paper.tex
added ieee copyright contract

@@
 % ------
-\title{ A simple and efficient algorithm for computing approximate
-  Nash equilibria in sequential games with incomplete
-  information}
+\title{A SIMPLE AND EFFICIENT ALGORITHM FOR COMPUTING APPROXIMATE
+  NASH-EQUAILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION}
 
@@
 \maketitle
-\begin{abstract}We present a simple primal-dual algorithm for
-  computing approximate Nash equilibria in two-person zero-sum
+\begin{abstract}
+We present a simple primal-dual algorithm for
+  computing approximate Nash-equilibria in two-person zero-sum
   sequential games with  incomplete information and perfect recall
@@
   as a matrix game with convex polytopial profiles. We prove that
-  the number of iterations needed to produce a Nash equilibrium with a
+  the number of iterations needed to produce a Nash-equilibrium with a
   given precision is inversely proportional to the
@@
 
-\textbf{keywords}: algorithmic-game theory; sequential game;
-incomplete information; perfect recall; approximate Nash equilibrium;
-primal-dual algorithm; convex-optimization
+\begin{keywords} algorithmic-game theory, sequential games,
+incomplete information, perfect recall, approximate Nash-equilibrium
+\end{keywords}
 
@@
 $l_1$, and $l_2$ are all linear in the size of the game tree (number
-of states in the game) and such that Nash equilibria correspond to
+of states in the game) and such that Nash-equilibria correspond to
 pairs $(x, y)$ of \textit{realization plans} which solve the primal
@@
 fundamental practical advantage. Instead, it is customary compute
-``approximate'' Nash equilibria. A popular notion of approximate
+``approximate'' Nash-equilibria. A popular notion of approximate
 equilibria is the following:
@@
 device a primal-dual algorithm that (Algorithm \ref{Tab:algo}) for
-computing approximate Nash equilibria in sequential two-person
+computing approximate Nash-equilibria in sequential two-person
 zero-sum games with incomplete information and perfect recall, and
@@
 Then GSP($\Psi_1$,
-  $\Psi_2$, $g_1$, $g_2$) is equivalent to the Nash equilibrium LCPs
+  $\Psi_2$, $g_1$, $g_2$) is equivalent to the Nash-equilibrium LCPs
   \eqref{eq:primal_pb} and \eqref{eq:dual_pb}, i.e
@@
   \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
-  \mathbb{R}^{l_2}$ solves the Nash equilibrium LCPs
+  \mathbb{R}^{l_2}$ solves the Nash-equilibrium LCPs
   \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff it solves
@@
 
-By Theorem \ref{thm:pd}, solving for a Nash equilibrium for
+By Theorem \ref{thm:pd}, solving for a Nash-equilibrium for
 the game is equivalent to solving the GSP
@@
 
-\subsection{A more comfortable notion of approximate Nash equilibrium}
+\subsection{A more comfortable notion of approximate Nash-equilibrium}
 \begin{definition}
@@
 This approximation concept for subdifferentials yields the following
-concept of approximate Nash equlibria (adapted from
+concept of approximate Nash-equlibria (adapted from
 \cite{he2013accelerating}).
@@
 \begin{itemize}
-\item Exact Nash equilibria correspond to Nash $(0,0)$-equilibria.
+\item Exact Nash-equilibria correspond to Nash $(0,0)$-equilibria.
 \item Nash $\epsilon$-equilibria (in the sense of Definition
@@
 devised a simple and efficient primal-dual algorithm for computing
-Nash equilibria in two-person zero-sum sequential games with
+Nash-equilibria in two-person zero-sum sequential games with
 incomplete information (like Texas Hold'em, etc.). Our algorithm is

### 2015-09-26 paper.tex
multiple issues and fixups thereof

@@
   of games is thanks to the sequence-form representation
-  \cite{koller1992complexity} which allows us to encode any such game
+  which allows us to encode any such game
   as a matrix game with convex polytopial profiles. We prove that
@@
   given precision is inversely proportional to the
-  precision. We also present experimental results on simulated and
-  real games (Kuhn poker).
+  precision. By way of demonstration, we also present experimental
+  results on simulated and real games (Kuhn poker).
 \end{abstract}
@@
 \subsection{Notation and terminology}
-Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
-of all subsets of $X$, or equivalently the set of all binary
-functions on $X$. Let $m$ and $n$ be positive integers. Given two
+Let $m$ and $n$ be positive integers. Given two
 vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
@@
 the references therein, for a more elaborate exposition on
-proximal calculus and its use in modern convex-optimization.
+proximal calculus. % and its use in modern convex-optimization.
 
@@
 \cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
-\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in
+\delta\right) \log \left(1 / \epsilon\right)\right)$ convergence rate in
 terms of the number of calls made to a first-order oracle. Here
@@
   the factor $\|A\| / \delta$ in the $\mathcal{O}\left(\left(\|A\| /
-\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate can
+\delta\right) \log\left(1 / \epsilon\right)\right)$ convergence rate can
 be arbitrarily large for ill-conditioned games.
@@
 
-\section{Methods}
+\section{Our contributions}
 \label{sec:gsp}
-\subsection{The Generalized Saddle-point Problem (GSP) connection}
+\subsection{Preliminaries}
 In the next theorem, we show that the LCPs \eqref{eq:primal_pb}
@@
 
-\subsection{A more comfortable notion of approximate Nash-equilibrium}
+\subsection{Yet another notion of approximate Nash-equilibrium}
 \begin{definition}
@@
 \subsection{Practical considerations}
-\paragraph*{\textbf{\textit(a) Efficient computation of $Ay$ and $A^Tx$.}}
+\paragraph*{Efficient computation of $Ay$ and $A^Tx$.}
 In Algorithms \ref{Tab:algo}, most of the time is spent
@@
 
-\paragraph*{\textit(b) Computing $\|K\|$.}
+\paragraph*{Computing $\|K\|$.}
 Also the 2-norm $\|K\|$ of the linear operator $K$, can be efficiently
-computed using the power iteration (Perron-Frobenius).
+computed using the power iteration.
 
@@
 tested it on simulated and real games.
-\paragraph*{Experiments on sequential games with incomplete
-  information: Kuhn 3-card
-  poker.} This game is a simplified form of poker
+\paragraph*{Sequential games with incomplete
+  information: Kuhn poker.} This game is a simplified form of poker
 developed by Harold W. Kuhn. It is a two-person zero-sum game which is
@@
   }
-  \vspace{-1em}
+  %\vspace{-1em}
   \hspace{-.5em}
@@
   its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly
-  verified empirically.}
+  verified empirically. \textit{(b)}: Kuhn poker. In both cases we see
+  that the proved convergence rate for our algorithm is observed.}
   \label{Tab:dgap_curve}
@@
 $(\epsilon,0)$-equilibrium of the game.
-
 Equilibrium problems are saddle-point convex-concave problems, and as
@@
 
-%\pagebreak
-\bibliographystyle{llcns2e/splncs03}
-\bibliography{bib}
-
 %\paragraph{\textbf{Toy Poker game...}}
@@
 
+\pagebreak
+\bibliographystyle{IEEEbib}
+\bibliography{bib}
+
 \end{document}

### 2015-09-26 paper.tex
ran aspell on .tex

@@
 \begin{abstract}
-We present a simple primal-dual algorithm for
-  computing approximate Nash-equilibria in two-person zero-sum
-  sequential games with  incomplete information and perfect recall
-  (like Texas Hold'em poker). Our algorithm only performs basic
-  iterations (i.e matvec multiplications, clipping, etc., and no calls
-  to external first-order oracles, no matrix inversions, etc.)
-  and is applicable to a broad class of two-person zero-sum games
-  including simultaneous games and sequential games with incomplete
-  information and perfect recall. The applicability to the latter kind
-  of games is thanks to the sequence-form representation
-  which allows us to encode any such game
-  as a matrix game with convex polytopial profiles. We prove that
-  the number of iterations needed to produce a Nash-equilibrium with a
-  given precision is inversely proportional to the
-  precision. By way of demonstration, we also present experimental
-  results on simulated and real games (Kuhn poker).
+We present a simple primal-dual algorithm for computing approximate
+Nash equilibria in two-person zero-sum sequential games with
+incomplete information and perfect recall (like Texas Hold'em
+poker). Our algorithm only performs basic iterations (i.e matvec
+multiplications, clipping, etc., and no calls to external first-order
+oracles, no matrix inversions, etc.) and is applicable to a broad
+class of two-person zero-sum games including simultaneous games and
+sequential games with incomplete information and perfect recall. The
+applicability to the latter kind of games is thanks to the
+sequence-form representation which allows us to encode any such game
+as a matrix game with convex polytopial profiles. We prove that the
+number of iterations needed to produce a Nash equilibrium with a given
+precision is inversely proportional to the precision. As
+proof-of-concept, we also present experimental results on simulated
+and real games (Kuhn poker).
 \end{abstract}

### 2015-09-28 paper.tex
glitches + fixups + ENHs

--- 2015-09-26 paper.tex
@@
 %% squeezing
-\linespread{0.85}
+\linespread{0.845}
 \usepackage[compact]{titlesec}
@@
 % ------
-\title{A SIMPLE AND EFFICIENT ALGORITHM FOR COMPUTING APPROXIMATE
+\title{A SIMPLE PRIMAL-DUAL ALGORITHM FOR COMPUTING APPROXIMATE
   NASH-EQUAILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION}
@@
 \name{Elvis Dohmatob}
-\address{Parietal Team, INRIA, Universit\'e de Paris-Saclay}
+\address{Parietal Team, INRIA / CEA, Universit\'e Paris-Saclay}
 %
@@
 \begin{abstract}
-We present a simple primal-dual algorithm for
-  computing approximate Nash-equilibria in two-person zero-sum
-  sequential games with  incomplete information and perfect recall
-  (like Texas Hold'em poker). Our algorithm only performs basic
+We present a simple primal-dual algorithm for computing approximate
+Nash-equilibria in two-person zero-sum sequential games with
+incomplete information and perfect recall (like Texas Hold'em
+Poker). Our algorithm is numerically stable, performs basic
 iterations (i.e matvec multiplications, clipping, etc., and no calls
-  to external first-order oracles, no matrix inversions, etc.)
-  and is applicable to a broad class of two-person zero-sum games
-  including simultaneous games and sequential games with incomplete
-  information and perfect recall. The applicability to the latter kind
-  of games is thanks to the sequence-form representation
-  which allows us to encode any such game
-  as a matrix game with convex polytopial profiles. We prove that
-  the number of iterations needed to produce a Nash-equilibrium with a
-  given precision is inversely proportional to the
-  precision. By way of demonstration, we also present experimental
-  results on simulated and real games (Kuhn poker).
+to external first-order oracles, no matrix inversions, etc.) and is
+applicable to a broad class of two-person zero-sum games including
+simultaneous games and sequential games with incomplete information
+and perfect recall. The
+applicability to the latter kind of games is thanks to the
+sequence-form representation which allows us to encode any such game
+as a matrix game with convex polytopial strategy profiles. We prove
+that the number of iterations needed to produce a Nash-equilibrium
+with a given precision is inversely proportional to the precision. As
+proof-of-concept, we present experimental results on matrix games
+on simplexes and Kuhn Poker.
 \end{abstract}
 
-\begin{keywords} algorithmic-game theory, sequential games,
-incomplete information, perfect recall, approximate Nash-equilibrium
+\begin{keywords} Nash-equilibrium, sequential games,
+  incomplete information, perfect recall, convex optimization
 \end{keywords}
@@
 $\text{CFR}^{+}$ \cite{tammelin14} and other variants, which
-have recently had profound success in poker. However, solving games
+have recently had profound success in Poker. However, solving games
 for equilibria remains a mathematical and computational challenge,
-especially in sequential games with imperfect information. This paper
-proposes a simple and efficient algorithm for solving for such
-equilibria approximately, in a sense which will be made clear shortly.
-
-\subsection{Notation and terminology}
-Let $m$ and $n$ be positive integers. Given two
-vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
-$\langle z, w\rangle := \sum_{j}z_jw_j$. The components of $z$ will be
-denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
-not $1$). $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ }
-z \geq 0\}$ is the nonnegative $n$th \textit{orthant}.
-The notation ``$z \ge 0$'' means that all the components of
-$z$ are nonnegative.
-$\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| :=
-\sqrt{\langle z, z\rangle}$. $(z)_+:=\text{max}(0, z) \in
-\mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
-example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
-operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
-function. The $n$-simplex denoted $\Delta_n$, is defined by $\Delta_n
-:= \{z \in \mathbb{R}^n_+|\sum_j z_j = 1\}$.
-Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
-  norm}, denoted $\|A\|$, is
- defined to be the largest \textit{singular value} of $A$, i.e the
- largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).
-
-Let us introduce some basic but powerful modern convex-analytical
-notions which will be essential in the sequel. Given a subset $C$ of
-$\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined
-by $i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
-    otherwise}$.
-At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
-etc.). For example, we will write $i_{z \ge 0}$ for
-$i_{\mathbb{R}^n_+}(z)$, etc. Let $f : \mathbb{R}^n \rightarrow
-(-\infty, +\infty]$ be a
-  convex function. The \textit{orthogonal projector} onto $C$, is the
-  ``closest-point function'' $\proj_C: \mathbb{R}^n \rightarrow C, x
-  \mapsto \underset{z \in
-      C}{\text{argmin }}\frac{1}{2}\|z-x\|^2$.
-The \textit{effective domain} of $f$, denoted
-  $dom(f)$, is defined as
-$dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$.
- If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
-%% \textit{proper convex lower semi-continous function}
-%% (\textit{p.c.l.s.c} for short).
-%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
-%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
-%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
-The \textit{subdifferential} of $f$ at a point $x \in \mathbb{R}^n$ is
-defined by
-$\partial f(x) := \{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z -
-x\rangle, \forall z \in \mathbb{R}^n\}$.
-%% Each element of $\partial f(x)$ is called a \textit{subgradient} of $f$
-%% at $x$. Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
-%% in case $f$ is differentiable at $x$.
-If $f$ is convex, its
-\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
-\rightarrow \mathbb{R}^n$ defined by $\prox_f(x): = \underset{z \in
-  \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
-  - x\|^2 + f(z)$.
-%% For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
-%% $\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
-%% operators generalize orthogonal projectors. For example
-%% $\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
-%% (z)_+$. One also has the useful characterization
-%% \begin{eqnarray}
-%%   p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
-%% \end{eqnarray}
-%% Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
-%% should) be thought of as performing an \textit{implicit} gradient step
-%% of size $\gamma$.
-
-The interested reader should refer to \cite{combettes2011proximal} and
-the references therein, for a more elaborate exposition on
-proximal calculus. % and its use in modern convex-optimization.
+especially in sequential games with imperfect information. In this
+paper, we propose a simple primal-dual algorithm for solving for such
+equilibria approximately (in a sense to be made precise in Definition
+\ref{thm:cool_notion} below).
 
 \subsection{Statement of the problem}
-
 The sequence-form representation for two-person zero-sum games with
@@
 
-Note that the LCPs above have the equivalent saddle point formulation
+The LCPs above have the equivalent saddle-point formulation
 \begin{equation}
@@
 \begin{equation}
-  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\} \subseteq
+  Q_k := \{z \ge 0 |\text{ }E_kz = e_k\} \subseteq
   [0, 1]^{n_k}
@@
 In \eqref{eq:dgap}, the quantity $G(x, y)$ is nothing but the primal-dual
-gap for the equivalent saddle point problem \eqref{eq:gilpin}.
+gap for the equivalent saddle-point problem \eqref{eq:gilpin}.
 It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
@@
 \end{equation}
-
 Moreover, at equilibria, \textit{strong duality} holds and the value
@@
 $\tilde{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at
-equilibria.
-
-Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
-is impossible in practice (indeed, this system of problems is NP-hard
-\cite{koller1992complexity}) and such a precision doesn't have any
-fundamental practical advantage. Instead, it is customary compute
-``approximate'' Nash-equilibria. A popular notion of approximate
-equilibria is the following:
+equilibria.%%  Solving the LCPs \eqref{eq:primal_pb} and
+%% \eqref{eq:dual_pb} exactly is very practice
+%% \cite{koller1992complexity}) and such a precision doesn't have any
+%% fundamental practical advantage. Instead, it is customary compute
+%% ``approximate'' Nash-equilibria.%%  A now introduce a popular notion of
+%% %% approximate Nash-equilibria:
 
@@
 Given $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
-a pair $(x^*, y^*)$ of realization plans such that there exists dual
+a pair $(x^*, y^*)$ of realization plans for which there exists dual
 vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
@@
 
-\begin{remark}
-It should be noted
+\subsection{Notation and terminology}
+\paragraph*{General.} Let $m$ and $n$ be positive integers.
+The components of a vector $z \in \mathbb{R}^n$ will be
+denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
+not $1$). $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ }
+z \geq 0\}$ is the nonnegative $n$th \textit{orthant}.
+The notation ``$z \ge 0$'' means that all the components of
+$z$ are nonnegative.
+$\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| :=
+\sqrt{\langle z, z\rangle}$. $(z)_+:=\text{max}(0, z) \in
+\mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
+example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
+operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
+function. The $n$-simplex denoted $\Delta_n$, is defined by $\Delta_n
+:= \{z \in \mathbb{R}^n_+|\sum_j z_j = 1\}$.
+Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
+  norm}, denoted $\|A\|$, is
+ defined to be the largest \textit{singular value} of $A$, i.e the
+ largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).
+
+\paragraph*{Convex analysis.} Let us introduce some basic but powerful
+modern convex-analytical
+notions which will be essential in the sequel. Given a subset $C$ of
+$\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined
+by $i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
+    otherwise}$.
+At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
+etc.). For example, we will write $i_{z \ge 0}$ for
+$i_{\mathbb{R}^n_+}(z)$, etc.  The \textit{orthogonal projector} onto $C$, is the
+``closest-point'' map $\proj_C: \mathbb{R}^n \rightarrow C, x
+  \mapsto \underset{z \in
+      C}{\text{argmin }}\frac{1}{2}\|z-x\|^2$.
+Let $f : \mathbb{R}^n \rightarrow
+(-\infty, +\infty]$ be a
+  convex function. The \textit{effective domain} of $f$, denoted
+  $dom(f)$, is defined as
+$dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$.
+ If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
+%% \textit{proper convex lower semi-continous function}
+%% (\textit{p.c.l.s.c} for short).
+%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
+%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
+%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
+The \textit{subdifferential} of $f$ at a point $x \in \mathbb{R}^n$ is
+defined by
+$\partial f(x) := \{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z -
+x\rangle, \forall z \in \mathbb{R}^n\}$.
+%% Each element of $\partial f(x)$ is called a \textit{subgradient} of $f$
+%% at $x$. Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
+%% in case $f$ is differentiable at $x$.
+If $f$ is convex, its
+\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
+\rightarrow \mathbb{R}^n$ defined by $\prox_f(x): = \underset{z \in
+  \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
+  - x\|^2 + f(z)$.
+%% For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
+%% $\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
+%% operators generalize orthogonal projectors. For example
+%% $\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
+%% (z)_+$. One also has the useful characterization
+%% \begin{eqnarray}
+%%   p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
+%% \end{eqnarray}
+%% Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
+%% should) be thought of as performing an \textit{implicit} gradient step
+%% of size $\gamma$.
+
+The interested reader should refer to \cite{combettes2011proximal} and
+the references therein, for a more elaborate exposition on
+proximal calculus. % and its use in modern convex-optimization.
+
+\subsection{A remark concerning matrix games on simplexes.} It should
+be noted
 that any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
@@
 \mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
-matrix game on simplexes can be seen as a sequential game.  Thus the
+matrix game on simplexes can be seen as a sequential game, and so the
 results presented in this manuscript can be trivially applied such
-games in particular. Here, the polytopial $Q_k$
-defined in \eqref{eq:polytope} reduce to simplexes $\Delta_{n_k}$,
-and the primal-dual gap function $G(x,y)$ writes
+games in particular. For this special sub-class of sequential games,
+the primal-dual gap function $G(x,y)$ writes
 \begin{eqnarray}
@@
 \end{eqnarray}
-\end{remark}
 
 \subsection{Quick sketch of our contribution}
-One cannot directly attack the LCPs \eqref{eq:primal_pb} and
-\eqref{eq:dual_pb} via a traditional primal-dual algorithm
-(for example \cite{chambolle2010,chambolle2014ergodic}) because
-computing the orthogonal projections $\proj_{Q_k}$ is very difficult
-In fact, such sub-problems would have to be solved
-iteratively\footnote{An ``exception to the rule'' is the case where
-  the $Q_k's$ are simplexes, so that the projections can be computed
-  exactly using \cite{duchi2008efficient}.}. Also,
-the primal-dual gap might explode even at points arbitrarily close to
-the set of feasible points, leaving the algorithm with no indication
-whatsoever, on whether progress is being made or not. So need to way to
-\begin{itemize}
-\item[(1)] avoid having to compute the projections $\proj_{Q_k}$,
-\item[(2)] have control over how far we are from the set of
-  equilibria and avoid infinite (and thus non-informative) primal-dual
-  gaps.
-\end{itemize}
+%% One cannot directly attack the LCPs
+%% \eqref{eq:primal_pb} and
+%% \eqref{eq:dual_pb} via a traditional primal-dual algorithm
+%% (for example \cite{chambolle2010,chambolle2014ergodic}) because
+%% computing the orthogonal projections $\proj_{Q_k}$ is very difficult
+%% In fact, such sub-problems would have to be solved
+%% iteratively\footnote{An ``exception to the rule'' is the case where
+%%   the $Q_k's$ are simplexes, so that the projections can be computed
+%%   exactly using \cite{duchi2008efficient}.}.
 
@@
 homologous to that presented in Definition \ref{thm:approx_nash}, we
-device a primal-dual algorithm that (Algorithm \ref{Tab:algo}) for
-computing approximate Nash-equilibria in sequential two-person
-zero-sum games with incomplete information and perfect recall, and
-which satisfies the above crucial requirements (1)--(2). We also
-prove (Theorem \ref{thm:pd}) that --in an ergodic / Ces\`ario sense-- the number of
-iterations required by the algorithm to produce an approximation
-equilibrium to a precision $\epsilon$ is $\mathcal{O}(1/\epsilon)$,
-with explicit values for the constants involved this worst-case cost.
-These contributions will be elaborated in section \ref{sec:gsp}.
+device a simple numerically stable primal-dual algorithm that
+(Algorithm \ref{Tab:algo}) for computing approximate Nash-equilibria
+in sequential two-person zero-sum games with incomplete information and
+perfect recall. On, each iteration, the only operations performed by
+our algorithm are of the form $A^Tx$, $Ay$, $E_1^Tp$, $E_2^Tq$, and
+$(x)_+$. We also prove (Theorem \ref{thm:pd}) that --in an ergodic /
+Ces\`ario sense-- the number of iterations required by the algorithm
+to produce an approximation equilibrium to a precision $\epsilon$ is
+$\mathcal{O}(1/\epsilon)$, with explicit values for the constants
+involved this worst-case cost.
 %% The source of approximation in our scheme
@@
 %% $Q_1 \times Q_2$.
+% These contributions will be elaborated in section \ref{sec:gsp}.
 
-\section{Related work}
+\section{Relation to prior work}
 \label{sec:related_work}
@@
 $\epsilon$-equilibria for two-person zero-sum games with incomplete
-information like Texas Hold'em poker, etc.
+information like Texas Hold'em Poker, etc.
 First and foremost, let us note that for the class of games considered
@@
 than what state-of-the-art LCP and interior-point solvers can
-handle. See for example \cite{hoda2010smoothing,gilpinfirst}.
+handle (see for example \cite{hoda2010smoothing,gilpinfirst}).
 
+\subsection{Regret minimization}
+CFR (CounterFactual Regret minimization) \cite{zinkevich2008regret},
+Monte Carlo CFR \cite{lanctot2009monte}, and CFR+
+\cite{Bowling09012015}, by their large popularity, have become the
+definitive state-of-the-art, and are particularly useful in
+many-player games, since convex-analytical methods cannot help much in
+such games. Also, they can be shown to converge to a Nash-equilibrium
+provided each player uses a CFR scheme to play the game
+\cite{zinkevich2008regret}, but generally enjoy a much weaker
+convergence theory. For example, \cite{lanctot2009monte} showed that
+such scheme have a running time of $\mathcal{O}(1/\epsilon^2)$ to
+produce a Nash $\epsilon$-equilibrium.
+
+\subsection{First-order methods}
 In \cite{hoda2010smoothing}, a nested iterative procedure using the
-Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used
+Excessive Gap Technique (EGT) \cite{nesterov2005excessive} (EGT and
+precursors are well-known to the signal-processing community
+\cite{NESTA}) was used
 to solve the equilibrium problem \eqref{eq:gilpin}.
@@
   %% conditions are absent.
+\end{itemize}
+Recently, \cite{kroer2015} proposed accelerations to first-order
+methods for computing Nash-equilibria (including those just
+discussed), by an appropriate choice of the underlying \textit{Bregman
+distance} and the \textit{distance generating function} (essential
+ingredients in EGT-type algorithms). These modifications provably
+gain a constant factor in the worst-case convergence rate of the
+resulting algorithm. %, compared to \textit{vanilla} implementations.
 
-\end{itemize}
-
-%% It should be noted that the EGT and its precursors have had
-%% considerable success in the signal processing communities, as can
-%% be seen in \cite{NestaCandès, eduard, etc.} and the references
-%% therein.
-
+\subsection{Primal-dual algorithms}
 The primal-dual algorithm first developed in \cite{chambolle2010}, was
 proposed in \cite{chambolle2014ergodic} as a way of solving matrix
-games on simplexes. It should be stressed that such matrix games on
+games on simplexes. Notably, such matrix games on
 simplexes are considerably simpler than the games considered
@@
 no such efficient algorithm is known nor is likely to exist, for the
-polytopes $Q_k$ defined in \eqref{eq:polytope}.%% , the strategy
+polytopes $Q_k$ defined in \eqref{eq:polytope}. %% , the strategy
 %% profiles for players in %% the games considered here.
@@
 scheme, one would have to solve this sub-problem with finer and finer
-precision.
+precision, rendering the overall solver impractical.
 
-CFR (CounterFactual Regret minimization) \cite{zinkevich2008regret},
-Monte Carlo CFR \cite{lanctot2009monte}, and CFR+
-\cite{Bowling09012015} have also become state-of-the-art, and are
-particularly useful in many-player games, since convex-analytical
-methods cannot help much in such games.
+ Also, the primal-dual gap might explode even at points arbitrarily
+ close to the set of feasible points, leaving the algorithm with no
+ indication whatsoever, on whether progress is being made or not. So,
+ we need a way to \textit{(1)} avoid having to compute the projections
+$\proj_{Q_k}$, and \textit{(2)} have control over how far we are from
+the set of equilibria and avoid infinite (and thus non-informative)
+primal-dual gaps. Amongst other amendments, this issue was addressed
+in \cite{he2013accelerating}.
 
@@
 is to remove the linear constraints in the definitions of the strategy
-polytopes $Q_k$, by modifying the payoff matrix to yield an equivalent
+polytopes $Q_k$, by augmenting the payoff matrix to yield an equivalent
 saddle-point problem.
@@
   \end{eqnarray}
-
 Also define two bilinear forms $\Psi_1$, $\Psi_2: \mathbb{R}^{n_2}
@@
 \end{equation}
-
 and define the functions $\hat{\Psi}_1$, $\hat{\Psi}_2:
@@
     \hat{\Psi}_2(y, p, x, q) :=\begin{cases}
-    \Psi_2(y, p, x, q)+ g_2(y, p), &\mbox{ if }x \ge 0,\\
+    \Psi_2(y, p, x, q)+ g_2(x, q), &\mbox{ if }x \ge 0,\\
     +\infty, &\mbox{ otherwise}\end{cases}
@@
 \end{eqnarray}
-
-Finally, define the sets $S_1 := \mathbb{R}^{n_2}_+ \times \mathbb{R}^{l_1}$ and $S_2 :=
-\mathbb{R}^{n_1}_+ \times \mathbb{R}^{l_2}$ and consider the
-GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$): Find a quadruplet $(y^*,p^*, x^*, q^*) \in
-S_1 \times S_2$ such that $\forall (y,p, x, q) \in S_1
-    \times S_2$, it holds that
+Finally, define the sets $S_1 := \mathbb{R}^{n_2}_+ \times
+\mathbb{R}^{l_1}$ and $S_2 := \mathbb{R}^{n_1}_+ \times
+\mathbb{R}^{l_2}$, and consider the GSP($\Psi_1$, $\Psi_2$, $g_1$,
+$g_2$): Find a quadruplet $(y^*,p^*, x^*, q^*) \in S_1 \times S_2$,
 \begin{eqnarray}
@@
     &\hat{\Psi}_1(y^*, p^*, x^*, q^*) \le \hat{\Psi}_1(y, p, x^*,
-    q^*),\\
+    q^*),\hspace{1em}and\\
     &\hat{\Psi}_2(y^*, p^*, x^*, q^*)
-    \le \hat{\Psi}_2(y^*, p^*, x, q).
+    \le \hat{\Psi}_2(y^*, p^*, x, q),\hspace{.21em} \forall (y,p, x, q)
+    \in S_1 \times S_2.
   \label{eq:unconstrained_pb}
@@
 \label{thm:pd}
-
 Then GSP($\Psi_1$,
-  $\Psi_2$, $g_1$, $g_2$) is equivalent to the Nash-equilibrium LCPs
+  $\Psi_2$, $g_1$, $g_2$) is equivalent to the LCPs
   \eqref{eq:primal_pb} and \eqref{eq:dual_pb}, i.e
@@
   \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
-  \mathbb{R}^{l_2}$ solves the Nash-equilibrium LCPs
+  \mathbb{R}^{l_2}$ solves the LCPs
   \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff it solves
@@
 \end{eqnarray*}
-
 Similarly, the unconstrained objective, say
@@
 \end{eqnarray*}
-where the second equality follows from the zero-sum condition $\Psi_1
-+ \Psi_2 := 0$.
+where the second equality follows from %% the zero-sum condition 
+$\Psi_1 + \Psi_2 := 0$.
 \end{proof}
@@
 The idea behind $\epsilon$-subdifferentials is the following. Say we wish
-to minimize the function $f$. Replace the usual necessary
+to minimize the function $f$. Replace the usual necessary and sufficient
 condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
@@
   0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
-
 This approximation concept for subdifferentials yields the following
-concept of approximate Nash-equlibria (adapted from
+concept of approximate Nash-equilibria (refer to
 \cite{he2013accelerating}).
@@
   \hat{\Psi}_2(y^*, p^*, ., .)](y^*,p^*,x^*,q^*)$.
-
 Such a vector $v^*$ is called a Nash $(\epsilon_1,
@@
 The above definition is a generalization of the notion of Nash
-equilibria since:
-\begin{itemize}
-\item Exact Nash-equilibria correspond to Nash $(0,0)$-equilibria.
-\item Nash $\epsilon$-equilibria (in the sense of Definition
+equilibria since: \textit{(a)} exact Nash-equilibria correspond to
+Nash $(0,0)$-equilibria, and \textit{(b)} Nash $\epsilon$-equilibria (in the sense of Definition
   \ref{thm:approx_nash}) correspond to Nash $(0,\epsilon)$-equilibria.
-\end{itemize}
 
@@
 \label{sec:algo}
-We now derive the algorithm (Algorithm \ref{Tab:algo}) which is the
-  main object of this
-manuscript, and establish the theoretical properties.
+We now derive the algorithm (Algorithm \ref{Tab:algo}) for computing
+Nash $(\epsilon, 0)$-equilibria and establish its theoretical
+properties. The algorithm emerges as synthesis of Theorem \ref{thm:pd}
+above, and ideas from \cite{he2013accelerating}.
 
 \begin{algorithm}
-\caption{Primal-dual algorithm for computing approximate Nash
-  Equilbria in two-person zero-sum games with incomplete information
-  and perfect recall}
+\caption{Primal-dual algorithm for computing Nash $(\epsilon,
+  0)$-equilibria in two-person zero-sum sequential games}
 \label{Tab:algo}
@@
 the GSP \eqref{eq:unconstrained_pb}.
-\State  $\lambda \leftarrow 1/\|K\|$, ${v}^{(0)} \leftarrow 0$, $k
-\leftarrow 0$
+\State  \textbf{Initialize:} $\lambda \leftarrow 1/\|K\|$, ${v}^{(0)}
+\leftarrow 0$, $k \leftarrow 0$
 \While{ $ k = 0$ or  $\frac{1}{k\lambda}\|v^{(k)}\| \ge \epsilon$}
@@
 \begin{theorem}[Ergodic / Ces\`ario $\mathcal{O}(1/\epsilon)$ convergence]
-Let $d_0$ be the orthogonal distance between the starting point
+Let $d_0$ be the euclidean distance between the starting point
 $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the
@@
 where $v_a^{(k_0)} := \frac{1}{k\lambda}v^{(k_0)}$.
-Thus Algorithm \ref{Tab:algo} outputs an $(\epsilon,0)$-Nash
-equilibrium for the GSP \eqref{eq:unconstrained_pb}
+Thus Algorithm \ref{Tab:algo} outputs a Nash
+$(\epsilon,0)$-equilibrium for the GSP \eqref{eq:unconstrained_pb}
 in at most $\frac{2d_0\|K\|}{\epsilon}$ iterations.
@@
 In Algorithms \ref{Tab:algo}, most of the time is spent
-pre-multiplying vectors by $A$ and $A^T$ (precisely 3 such operations
-are done per iteration). For \textit{flop-type} poker
-games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
+pre-multiplying vectors by $A$ and $A^T$. For \textit{flop-type} Poker
+games like Texas Hold'em and  Rhode Island Hold'em,
 $A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
@@
 Kronecker product of smaller matrices) which can be carefully
-exploited, as was done in \cite{hoda2010smoothing}.%%  For the purpose of
-%% completness, we explain the details of the tricks used in
-%% \cite{hoda2010smoothing} for speeding up the computation of these
-%% matvec products.
-
-%% \begin{definition}(Kronecker product)
-%% Let $F \in \mathbb{R}^{m \times n}$ and $B \in \mathbb{R}^{r \times
-%%   s}$ be matrices. The kronecker product of $F$ and $B$ is defined by
-
-%% \begin{equation}
-%% F \otimes B:=\left[
-%% \begin{array}{cccc}
-%% F_{0,0}B & F_{0,1}B & \cdots & F_{0,n-1}B \\
-%% F_{1,0}B & F_{1,1}B & \cdots & F_{1,n-1}B \\
-%% \vdots & \vdots & \ddots & \vdots\\
-%% F_{m-1,0}B & F_{m-1,1}B & \cdots & F_{m-1,n-1}B 
-%% \end{array}\right] \in \mathbb{R}^{mr \times ns}
-%% \end{equation}
-%% \end{definition}
-
-%% One notes that $(F \otimes B)^T = F^T \otimes B^T$.
-%% $F \otimes B$ can be very much larger than both $F$ and $B$ in
-%% dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
-%% $B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
-%% $10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
-%% \mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
-%% without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
-%% rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
-%%   ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
-%% $s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
-%% as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
-%% easily verfies that $Y$ is the matrix product of the ``small''
-%% matrices $B$, $X$, and $F^T$, i.e
-
-%% \begin{equation}
-%%   \label{eq:kron_matvec}
-%%   Y = BXF^T
-%% \end{equation}
-
-%% Now, in Texas Hold'em for example, the payoff matrix $A$ can be
-%% written as block-diagonal matrix whose blocks are sums of Kronecker
-%% products of much smaller sparse matrices as follows
-
-%% \begin{equation}
-%%   A = \begin{bmatrix}F_1 \otimes B_1\hspace{10em}\\\hspace{3em}F_2
-%%     \otimes B_2\hspace{7em}\\\hspace{6em}F_3 \otimes
-%%     B_3\hspace{4em}\\\hspace{10em}F_4 \otimes B_4 + S \end{bmatrix}
-%% \label{eq:factor_A}
-%% \end{equation}
-%% See \cite{hoda2010smoothing}. The matrices $F_i$ correspond to
-%% sequences of moves in round $i$ which end in a \textit{fold} action,
-%% and $S$ to the sequences which end in a \textit{showdown}. $B_i$
-%% encodes the betting structure of round $i$, while $W$ encodes the
-%% wind/lose/draw information determined by ranking the players' hands at
-%% showdown. The component matrices $F_i$, $B_i$, $S$, and $W$ are small
-%% enough to be explictly represented whereas it is infeasible to
-%% explicitly represent A. Furthermore, the matrices $F_i$, $B_i$,
-%% $S$, and $W$ are themselves sparse, which allows one to use the
-%% compressed row storage data structure that only stores nonzero entries
-%% (for example \textit{scipy.sparse.csr\_matrix}, in the Python
-%% programming language).
-
-%% Such a representation of the payoff matrix $A$ trivializes matvec
-%% operations involving $A$ or $A^T$ (thanks to formula
-%% \eqref{eq:kron_matvec} above, applied to their diagonal blocks and
-%% exploiting the sparsity of these blocks themselves). Of course, one
-%% can always write the payoff matrix $A$ of a flop-type poker game in a
-%% form similary to \eqref{eq:factor_A} by applying appropriate
-%% permutations to the enumeration of the players's sequences.
+exploited, as in \cite{hoda2010smoothing}. Also the sampling
+strategies presented in the recent work \cite{kroer2015} (section 6),
+for generating unbiased estimates of $Ay$ and $A^Tx$ would readily
+convert Algorithm \ref{Tab:algo} into an online and much scalable
+solver.
 
@@
 Also the 2-norm $\|K\|$ of the linear operator $K$, can be efficiently
-computed using the power iteration.
+computed using the power iteration. Results are presented and
+commented in Figure \ref{Tab:dgap_curve}.
 
-\section{Experimental results}
+\section{Numerical experiments results}
 \label{sec:results}
-To assess the practical quality of the proposed algorithm, we
-tested it on simulated and real games.
-\paragraph*{Sequential games with incomplete
-  information: Kuhn poker.} This game is a simplified form of poker
-developed by Harold W. Kuhn. It is a two-person zero-sum game which is
-simple enough to serve as a proof-of-concept example but contains all
-the complexity traits of a incomplete information sequential game. The
-deck includes only three playing cards: a King, Queen, and
-Jack. One card is dealt to each player, then the first player must bet
-or pass, then the second player may bet or pass. If any player chooses
+We now present some proof-of-concept for the algorithm proposed.
+\subsection{Basic test-bed: Matrix games on simplexes}
+As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
+\times 1000$ random matrix whose entries are uniformly identically
+distributed in the closed interval $[-1, 1]$. %%  We compare our proposed
+%% Algorithm \ref{Tab:algo} with Nesterov's \cite{nesterov2005a} and
+%% Gilpin's et al. \cite{gilpinfirst}.
+The results of the experiments are shown in Figure
+\ref{Tab:dgap_curve}\textit{(a)}.
+
+\subsection{Kuhn Poker, a ``toy'' sequential game} This game is a
+simplified form of Poker
+developed by Harold W. Kuhn in \cite{kuhn}. It already contains all
+the complexities (sequentiality, imperfection of information, etc.) of
+a full-blown Poker game like Texas Hold'em, but is simple enough to
+serve as a proof-of-concept for the ideas developed in this
+manuscript. The deck includes only three playing
+cards: a King, Queen, and Jack. One card is dealt to each player, then
+the first player must bet or pass, then the second player may bet or
+pass. If any player chooses
 to bet the opposing player must bet as well ("call") in order to stay
-in the round. After both players pass or bet the player with the
-highest card wins the pot.%%  The
+in the round. After both players pass or bet, the player with the
+highest card wins the pot. %%  The
 %% sequence-form representation of the game has $n_1 = n_2 = 13$
@@
 %% A(12,1) = A(12,5) = {0.166667}$.\\
-
 The pair of vectors $(x^*, y^*) \in \mathbb{R}^{13 + 13}$ given by
@@
  the game across iterations are shown in Figure \ref{Tab:dgap_curve}.
-We have not benchmarked this against the algorithms proposed in
+We have not benchmarked our algorithm against the algorithms proposed in
 \cite{nesterov2005a} and Gilpin's et al. \cite{gilpinfirst} because
@@
 
-\paragraph*{Basic test-bed: Matrix games on simplexes.}
-As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
-\times 1000$ random matrix whose entries are uniformly identically
-distributed in the closed interval $[-1, 1]$. We compare our proposed
-Algorithm \ref{Tab:algo} with Nesterov's \cite{nesterov2005a} and
-Gilpin's et al. \cite{gilpinfirst}. The results of the benchmarks are
-shown in Figure \ref{Tab:dgap_curve}\textit{(a)}.
+The results of the experiments are shown in Figure
+\ref{Tab:dgap_curve}\textit{(b)}.
 
@@
   %% \hspace{-2em}
-  %% \subfigure[Toy poker]{
+  %% \subfigure[Toy Poker]{
   %%   \includegraphics[width=.5\linewidth]{SimplifiedPoker_dgap.pdf}
@@
   \hspace{-2em}
-  \subfigure[Kuhn 3-card poker]{
+  \subfigure[Kuhn 3-card Poker]{
     \includegraphics[width=.5\linewidth]{Kuhn3112_dgap.pdf}
@@
   its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly
-  verified empirically. \textit{(b)}: Kuhn poker. In both cases we see
-  that the proved convergence rate for our algorithm is observed.}
+  verified empirically. \textit{(b)}: Kuhn Poker. In both cases we see
+  that the proved convergence rate for our algorithm is observed. The
+  algorithms of Nesterov and Gilpin are included in the plots only
+  indicatively, since this is not meant to be a benchmark as already
+  explained.}
   \label{Tab:dgap_curve}
@@
 \cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
-devised a simple and efficient primal-dual algorithm for computing
+devised a simple numerically stable primal-dual algorithm for computing
 Nash-equilibria in two-person zero-sum sequential games with
@@
 (matvec products, clipping, etc.), to a Nash
-$(\epsilon,0)$-equilibrium of the game.
-Equilibrium problems are saddle-point convex-concave problems, and as
-such a natural choice for algorithms for solving them would be in the
-family of primal-dual algorithms. %%  We believe such primal-dual
+$(\epsilon,0)$-equilibrium of the game. In future, we plan to run more
+experiments on real Poker games to measure the practical power of the
+proposed algorithm compared to other competed schemes like CFR and
+EGT.
+
+In conclusion, Nash-equilibrium problems are saddle-point
+convex-concave problems, and as such a natural tool
+for tackling them would be proximal primal-dual / operator-splitting
+algorithms. %%  We believe such primal-dual
 %% schemes will receive more attention in the algorithmic game theory

### 2015-10-02 paper.tex
fixups

@@
 %%   exactly using \cite{duchi2008efficient}.}.
-
+We now give a brief overview of our contributions, which will be made
+more elaborate in section \ref{sec:gsp}.
 Developing on an alternative notion of approximate equilibria (see
@@
 $\mathcal{O}(1/\epsilon)$, with explicit values for the constants
-involved this worst-case cost.
+involved.
 %% The source of approximation in our scheme
@@
 \label{sec:related_work}
-We now present a selection of algorithms that is representative of the
+Here, we present a selection of algorithms that is representative of the
 efforts that have been made in the literature to compute Nash
@@
 provided each player uses a CFR scheme to play the game
-\cite{zinkevich2008regret}, but generally enjoy a much weaker
+\cite{zinkevich2008regret}, but have a much weaker
 convergence theory. For example, \cite{lanctot2009monte} showed that
@@
 \mathbb{R}^{l_2}$, and consider the GSP($\Psi_1$, $\Psi_2$, $g_1$,
-$g_2$): Find a quadruplet $(y^*,p^*, x^*, q^*) \in S_1 \times S_2$,
+$g_2$): Find a quadruplet $(y^*,p^*, x^*, q^*) \in S_1 \times S_2$
+such that
 \begin{eqnarray}
@@
 Also the 2-norm $\|K\|$ of the linear operator $K$, can be efficiently
-computed using the power iteration. Results are presented and
-commented in Figure \ref{Tab:dgap_curve}.
+computed using the power iteration.
 
@@
 We now present some proof-of-concept for the algorithm proposed.
+Results are presented and commented in Figure \ref{Tab:dgap_curve}.
 \subsection{Basic test-bed: Matrix games on simplexes}

### 2015-10-15 paper.tex
multiple glitches

@@
 % ------
-\title{A SIMPLE PRIMAL-DUAL ALGORITHM FOR COMPUTING APPROXIMATE
-  NASH-EQUAILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION}
+\title{A SIMPLE NUMERICALLY STABLE PRIMAL-DUAL ALGORITHM FOR COMPUTING
+  NASH-EQUILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION}
 
@@
 incomplete information and perfect recall (like Texas Hold'em
-Poker). Our algorithm is numerically stable, performs basic
+Poker). Our algorithm is numerically stable, performs only basic
 iterations (i.e matvec multiplications, clipping, etc., and no calls
-to external first-order oracles, no matrix inversions, etc.) and is
+to external first-order oracles, no matrix inversions, etc.), and is
 applicable to a broad class of two-person zero-sum games including
 simultaneous games and sequential games with incomplete information
-and perfect recall. The
-applicability to the latter kind of games is thanks to the
-sequence-form representation which allows us to encode any such game
-as a matrix game with convex polytopial strategy profiles. We prove
-that the number of iterations needed to produce a Nash-equilibrium
-with a given precision is inversely proportional to the precision. As
-proof-of-concept, we present experimental results on matrix games
-on simplexes and Kuhn Poker.
+and perfect recall. The applicability to the latter kind of games is
+thanks to the sequence-form representation which allows us to encode
+any such game as a matrix game with convex polytopial strategy
+profiles. We prove that the number of iterations needed to produce a
+Nash-equilibrium with a given precision is inversely proportional to
+the precision. As proof-of-concept, we present experimental results on
+matrix games on simplexes and Kuhn Poker.
 \end{abstract}
@@
 \end{keywords}
-
+%\tableofcontents
 \section{Introduction}
@@
 especially in sequential games with imperfect information. In this
-paper, we propose a simple primal-dual algorithm for solving for such
+paper, we propose (our detailed contributions are sketched in
+subsection \ref{sec:sketch} below and elaborated in section
+\ref{sec:gsp}) a simple primal-dual algorithm for solving for such
 equilibria approximately (in a sense to be made precise in Definition
@@
 \end{equation}
-where the \textit{convex polytope} (by which we mean a bounded convex
-polyhedron)
+where the compact convex polytope
 \begin{equation}
-  Q_k := \{z \ge 0 |\text{ }E_kz = e_k\} \subseteq
+  Q_k := \{z \in \mathbb{R}^{n_k} | z \ge 0, E_kz = e_k\} \subseteq
   [0, 1]^{n_k}
@@
 sequence-form representation. At a feasible point $(y, p, x, q)$ for
-the LCPs, the \textit{primal-dual gap} $\tilde{G}(y, p, x, q)$ is
+the LCPs, the \textit{duality gap} $\tilde{G}(y, p, x, q)$ is
 given by\footnote{The first inequality being due to \textit{weak
@@
 $(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
-LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
-equilibrium for the game)  if and only if there exist vectors $p$ and
-$q$ such that
+LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a
+Nash-equilibrium for the game)  if and only if there exist vectors $p$
+and $q$ such that
 \begin{equation}
@@
 \end{equation}
-Moreover, at equilibria, \textit{strong duality} holds and the value
-of the game equals $p_0 = -q_0$, i.e the primal-dual gap
+Moreover, at equilibria \textit{strong duality} holds and the value
+of the game equals $p_0 = -q_0$, i.e the duality gap
 $\tilde{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at
@@
 vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
-\eqref{eq:dual_pb} such that the primal-dual gap at $(y^*, p^*, x^*, q^*)$
+\eqref{eq:dual_pb} such that the duality gap at $(y^*, p^*, x^*, q^*)$
 doesn't exceed $\epsilon$. That is,
@@
 
-\subsection{Notation and terminology}
-\paragraph*{General.} Let $m$ and $n$ be positive integers.
-The components of a vector $z \in \mathbb{R}^n$ will be
-denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
-not $1$). $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ }
-z \geq 0\}$ is the nonnegative $n$th \textit{orthant}.
-The notation ``$z \ge 0$'' means that all the components of
-$z$ are nonnegative.
-$\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| :=
-\sqrt{\langle z, z\rangle}$. $(z)_+:=\text{max}(0, z) \in
-\mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
-example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
-operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
-function. The $n$-simplex denoted $\Delta_n$, is defined by $\Delta_n
-:= \{z \in \mathbb{R}^n_+|\sum_j z_j = 1\}$.
-Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
-  norm}, denoted $\|A\|$, is
- defined to be the largest \textit{singular value} of $A$, i.e the
- largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).
-
-\paragraph*{Convex analysis.} Let us introduce some basic but powerful
-modern convex-analytical
-notions which will be essential in the sequel. Given a subset $C$ of
-$\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined
-by $i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
-    otherwise}$.
-At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
-etc.). For example, we will write $i_{z \ge 0}$ for
-$i_{\mathbb{R}^n_+}(z)$, etc.  The \textit{orthogonal projector} onto $C$, is the
-``closest-point'' map $\proj_C: \mathbb{R}^n \rightarrow C, x
-  \mapsto \underset{z \in
-      C}{\text{argmin }}\frac{1}{2}\|z-x\|^2$.
-Let $f : \mathbb{R}^n \rightarrow
-(-\infty, +\infty]$ be a
-  convex function. The \textit{effective domain} of $f$, denoted
-  $dom(f)$, is defined as
-$dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$.
- If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
-%% \textit{proper convex lower semi-continous function}
-%% (\textit{p.c.l.s.c} for short).
-%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
-%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
-%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
-The \textit{subdifferential} of $f$ at a point $x \in \mathbb{R}^n$ is
-defined by
-$\partial f(x) := \{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z -
-x\rangle, \forall z \in \mathbb{R}^n\}$.
-%% Each element of $\partial f(x)$ is called a \textit{subgradient} of $f$
-%% at $x$. Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
-%% in case $f$ is differentiable at $x$.
-If $f$ is convex, its
-\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
-\rightarrow \mathbb{R}^n$ defined by $\prox_f(x): = \underset{z \in
-  \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
-  - x\|^2 + f(z)$.
-%% For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
-%% $\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
-%% operators generalize orthogonal projectors. For example
-%% $\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
-%% (z)_+$. One also has the useful characterization
-%% \begin{eqnarray}
-%%   p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
-%% \end{eqnarray}
-%% Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
-%% should) be thought of as performing an \textit{implicit} gradient step
-%% of size $\gamma$.
-
-The interested reader should refer to \cite{combettes2011proximal} and
-the references therein, for a more elaborate exposition on
-proximal calculus. % and its use in modern convex-optimization.
-
-\subsection{A remark concerning matrix games on simplexes.} It should
-be noted
-that any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
-  game with payoff matrix $A$, for which each player's strategy
-profile is a simplex; this simplex can be written in the form
-\eqref{eq:polytope} by taking $E_k := (1, 1, ..., 1) \in
+\subsection{A remark concerning matrix games on simplexes}
+It should be noted that any matrix $A \in \mathbb{R}^{n_1 \times n_2}$
+specifies a matrix game with payoff matrix $A$, for which player $k$'s
+strategy profile is a simplex
+\begin{eqnarray}
+\Delta_{n_k} := \left\{z \in \mathbb{R}^{n_k}|z \ge 0,\sum_j
+z_j = 1\right\}.
+\end{eqnarray}
+This simplex can be written as a compact convex polytope in
+the form \eqref{eq:polytope} by taking $E_k := (1, 1, ..., 1) \in
 \mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
@@
 games in particular. For this special sub-class of sequential games,
-the primal-dual gap function $G(x,y)$ writes
+the duality gap function $G(x,y)$ writes
 \begin{eqnarray}
@@
 \subsection{Quick sketch of our contribution}
+\label{sec:sketch}
 %% One cannot directly attack the LCPs
@@
 our algorithm are of the form $A^Tx$, $Ay$, $E_1^Tp$, $E_2^Tq$, and
-$(x)_+$. We also prove (Theorem \ref{thm:pd}) that --in an ergodic /
-Ces\`ario sense-- the number of iterations required by the algorithm
-to produce an approximation equilibrium to a precision $\epsilon$ is
-$\mathcal{O}(1/\epsilon)$, with explicit values for the constants
-involved.
+$(x)_+ := (\max(0, x_j))_j$. We also prove (Theorem \ref{thm:pd}) that
+--in an ergodic / Ces\`ario sense-- the number of iterations required
+by the algorithm to produce an approximation equilibrium to a
+precision $\epsilon$ is $\mathcal{O}(1/\epsilon)$, with explicit
+values for the constants involved.
 %% The source of approximation in our scheme
@@
 % These contributions will be elaborated in section \ref{sec:gsp}.
+
+\subsection{Notation and terminology}
+\paragraph*{General.} Let $m$ and $n$ be positive integers.
+The components of a vector $z \in \mathbb{R}^n$ will be
+denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
+not $1$). $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ }
+z \geq 0\}$ is the nonnegative $n$th \textit{orthant}.
+$\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| :=
+\sqrt{\langle z, z\rangle}$. %%  $(z)_+:=\text{max}(0, z) \in
+%% \mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
+%% example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
+%% operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
+%% function.
+Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
+  norm}, denoted $\|A\|$, is
+ defined to be the largest \textit{singular value} of $A$, i.e the
+ largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).
+
+\paragraph*{Convex analysis.} %% For our purposes, it will suffice to
+%% know the following basic but powerful modern convex-analytical
+%% concepts. The interested reader should refer to
+%% \cite{combettes2011proximal} and the references therein for a more
+%% elaborate and scholastic exposition on the subject. % and its use in
+%%                                 % modern
+%%                                 % convex-optimization.
+Given a subset $C \subseteq \mathbb{R}^n$, $i_C$ denotes the
+\textit{indicator function} of $C$ defined by $i_C(x) = 0 \text{ if }
+x \in C\text{ and }+\infty\text{ otherwise}$.
+At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
+etc.). For example, we will write $i_{z \ge 0}$ for
+$i_{\mathbb{R}^n_+}(z)$, etc.  The \textit{orthogonal projector} onto
+$C$, is the ``closest-point'' map $\proj_C: \mathbb{R}^n \rightarrow
+C, x \mapsto \underset{z \in C}{\text{argmin }}\frac{1}{2}\|z-x\|^2$.
+Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
+  convex function. The \textit{effective domain} of $f$, denoted
+  $dom(f)$, is defined as
+$dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$.
+ If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
+%% \textit{proper convex lower semi-continous function}
+%% (\textit{p.c.l.s.c} for short).
+%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
+%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
+%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
+The \textit{subdifferential} of $f$ at a point $x \in \mathbb{R}^n$ is
+defined by
+$\partial f(x) := \{v \in \mathbb{R}^n | f(z)  \ge f(x) + \langle v, z -
+x\rangle, \forall z \in \mathbb{R}^n\}$.
+%% Each element of $\partial f(x)$ is called a \textit{subgradient} of $f$
+%% at $x$. Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
+%% in case $f$ is differentiable at $x$.
+If $f$ is convex, its
+\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
+\rightarrow \mathbb{R}^n$ defined by $\prox_f(x): = \underset{z \in
+  \mathbb{R}^n}{\text{argmin }}\frac{1}{2}\|z
+  - x\|^2 + f(z)$.
+%% For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
+%% $\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
+%% operators generalize orthogonal projectors. For example
+%% $\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
+%% (z)_+$. One also has the useful characterization
+%% \begin{eqnarray}
+%%   p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
+%% \end{eqnarray}
+%% Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
+%% should) be thought of as performing an \textit{implicit} gradient step
+%% of size $\gamma$.
+
+We recommend \cite{rockafellar1997convex,combettes2011proximal} for a
+more detailed exposition on convex analysis and its use in
+modern optimization theory and practice.
 
@@
 information like Texas Hold'em Poker, etc.
-First and foremost, let us note that for the class of games considered
+It should be noted that the class of games considered
 here (sequential games with incomplete information), the LCPs
@@
 than what state-of-the-art LCP and interior-point solvers can
-handle (see for example \cite{hoda2010smoothing,gilpinfirst}).
+handle (see \cite{hoda2010smoothing,gilpinfirst}).
 
@@
 convergence theory. For example, \cite{lanctot2009monte} showed that
-such scheme have a running time of $\mathcal{O}(1/\epsilon^2)$ to
-produce a Nash $\epsilon$-equilibrium.
+such schemes have a prohibitive running time of
+$\mathcal{O}(1/\epsilon^2)$ to produce a Nash $\epsilon$-equilibrium.
 
@@
 observe that \eqref{eq:gilpin} can further be written a the minimization of
-the primal-dual gap function $G(x, y)$ (defined in \eqref{eq:dgap})
+the duality gap function $G(x, y)$ (defined in \eqref{eq:dgap})
 for the game\footnote{The minimizers of $G$ are precisely the
@@
 \begin{eqnarray}
-\text{``distance between }(x, y)\text{ and the set of
+\text{``distance between }(x, y)\text{ and set of
 equilibria'' } \le G(x, y)/\delta.
@@
 Their
-algorithm is then derived by iteratively applying Nesterov smoothing \cite{nesterov2005a}
+algorithm is then derived by iteratively applying Nesterov smoothing
+\cite{nesterov2005a}
 with a geometrically decreasing sequence of tolerance levels
-$\epsilon_{n+1} = \epsilon_n / \gamma$ (with $\gamma > 1$)  $G$. It
-should be noted however that
-\begin{itemize}
-\item[--] The constant $\delta > 0$ can be arbitrarily small, and so
-  the factor $\|A\| / \delta$ in the $\mathcal{O}\left(\left(\|A\| /
-\delta\right) \log\left(1 / \epsilon\right)\right)$ convergence rate can
-be arbitrarily large for ill-conditioned games.
-\item[--] The reported linear convergence rate is not in terms of
+$\epsilon_{n+1} = \epsilon_n / \gamma$ (with $\gamma > 1$)
+$G$. However, there are a number of issues, most notably: \textit{(a)}
+The constant $\delta > 0$ can be arbitrarily small, and so the factor
+$\|A\| / \delta$ in the $\mathcal{O}\left(\left(\|A\| / \delta\right)
+\log\left(1 / \epsilon\right)\right)$ convergence rate can be
+arbitrarily large for ill-conditioned games.
+\textit{(b)} The reported linear convergence rate is not in terms of
   basic operations (addition, multiplication, matvec, clipping, etc.),
   but in terms of the number of calls to a first-order oracle. Most
-  notably, the complicated projections $\proj_{Q_k}$ are applied at
-  each iteration.%%  Of
+  notably, projections onto the polytopes $Q_k$ are computed on
+  each iteration, a very hard sub-problem. %%  Of
   %% course, the existence of a linear algorithm for solving
@@
   %% conditions are absent.
-\end{itemize}
+
 Recently, \cite{kroer2015} proposed accelerations to first-order
@@
 ingredients in EGT-type algorithms). These modifications provably
-gain a constant factor in the worst-case convergence rate of the
-resulting algorithm. %, compared to \textit{vanilla} implementations.
+gain a constant factor in the worst-case convergence rate over the
+original algorithm. %, compared to \textit{vanilla} implementations.
 
@@
 scheme, one would have to solve this sub-problem with finer and finer
-precision, rendering the overall solver impractical.
+precision, rendering the overall solver impractical. One can also cite
+\cite{nurminski2008}, in which the authors endeavored an iterative
+projection algorithm onto polytopes in outer representation.
 
- Also, the primal-dual gap might explode even at points arbitrarily
+Other than the difficult projection sub-problem just discussed,
+the duality gap might explode even at points arbitrarily
  close to the set of feasible points, leaving the algorithm with no
- indication whatsoever, on whether progress is being made or not. So,
- we need a way to \textit{(1)} avoid having to compute the projections
-$\proj_{Q_k}$, and \textit{(2)} have control over how far we are from
-the set of equilibria and avoid infinite (and thus non-informative)
-primal-dual gaps. Amongst other amendments, this issue was addressed
-in \cite{he2013accelerating}.
+ indication whatsoever, on whether progress is being made.
+
+%% So, mindful we need a way to \textit{(1)} avoid having to compute the
+%% projections $\proj_{Q_k}$, and \textit{(2)} have control over how far
+%% we are from the set of equilibria and avoid infinite (and thus
+%% non-informative) duality gaps. Amongst other amendments, this
+%% issue was addressed in \cite{he2013accelerating}.
 
@@
 \label{sec:gsp}
-\subsection{Preliminaries}
+\subsection{A Generalized Saddle-point Problem (GSP) equivalent of
+  the Nash-equilibrium LCPs \eqref{eq:primal_pb} and
+  \eqref{eq:dual_pb}}
 In the next theorem, we show that the LCPs \eqref{eq:primal_pb}
 and \eqref{eq:dual_pb} can be
-conveniently written as a \textit{Generalized Saddle-point Problem
-  (GSP)} in the sense of \cite{he2013accelerating}. The crux of idea
-is to remove the linear constraints in the definitions of the strategy
-polytopes $Q_k$, by augmenting the payoff matrix to yield an equivalent
-saddle-point problem.
+conveniently written as a GSP in the sense of
+\cite{he2013accelerating}. The crux of idea is to remove the linear
+constraints in the definitions of the strategy polytopes $Q_k$, by
+augmenting the payoff matrix to yield an equivalent saddle-point
+problem. The result is an equivalent game with unbounded strategy
+profiles (nonnegative orthants) with much simpler geometry.
+We elaborate the construction in the following theorem.
 \begin{theorem}
@@
       \end{array}
-      \right],\hspace{.5em}
+      \right],\hspace{.2em}
     \Psi_1(y, p, x, q)
     := \left\langle \begin{bmatrix}x\\q\end{bmatrix},
-      K\begin{bmatrix}y\\p\end{bmatrix}\right\rangle%% \\
+      K\begin{bmatrix}y\\p\end{bmatrix}\right\rangle, %% \\
       %% &= \langle x,
@@
     \Psi_2(y, p, x, q)+ g_2(x, q), &\mbox{ if }x \ge 0,\\
-    +\infty, &\mbox{ otherwise}\end{cases}
+    +\infty, &\mbox{ otherwise.}\end{cases}
   \end{aligned}
@@
 It suffices to show that at any point $(y, p, x,
-q) \in S_1 \times S_2$, the primal-dual gap between the primal
+q) \in S_1 \times S_2$, the duality gap between the primal
 LCP \eqref{eq:primal_pb} and the dual LCP \eqref{eq:dual_pb} equals
-the primal-dual gap of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
+the duality gap of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
 Indeed, the unconstrained objective in \eqref{eq:primal_pb}, say
@@
 \end{eqnarray*}
-Thus, noting that $-\infty \le \phi_1(x, q), \phi_2(y, p), < +\infty$
+Thus, noting that $-\infty < \phi_1(x, q), \phi_2(y, p) < +\infty$
 (so that all the operations below are valid),
-one computes the primal-dual gap between the primal LCP
+one computes the duality gap between the primal LCP
 \eqref{eq:primal_pb} and dual the LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
@@
   &\hspace{2em}- \phi_1(x, q)\\
-  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
-  q) - \phi_2(y, p)\\
-  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
+  &= \hat{\Psi}_1(y, p, x, q) - \phi_1(x,
+  q) + \hat{\Psi}_2(y, p, x, q) - \phi_2(y, p)\\
+  &= \text{duality gap of GSP}(\Psi_1, \Psi_2,
   g_1, g_2) \text{ at }(y, p, x, q),
@@
 \eqref{eq:unconstrained_pb}, which as it turns out, is simpler
-conceptually (for example, we no longer need to compute the
+conceptually (e.g, we no longer need to compute the
 complicated orthogonal projections $\proj_{Q_k}$). The rest of the
@@
 
-\subsection{Yet another notion of approximate Nash-equilibrium}
+\subsection{The proposed algorithm}
+We now derive the algorithm (Algorithm \ref{Tab:algo}) for computing
+Nash $(\epsilon, 0)$-equilibria and establish its theoretical
+properties. The algorithm, which emerges as a synthesis of Theorem
+\ref{thm:pd} above and ideas from \cite{he2013accelerating},  is
+numerically stable and performs only basic iterations (i.e matvec
+multiplications, clipping, etc., and no calls to external first-order
+oracles, no matrix inversions, etc.).
+\label{sec:algo}
 \begin{definition}
-  Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
-  \rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged
+  Given $\epsilon > 0$ and a function $f:\mathbb{R}^n
+  \rightarrow (-\infty,+\infty]$, the $\epsilon$-enlarged
   subdifferential (or
@@
   \begin{eqnarray}
-\partial_\epsilon f(x):= \{s \in \mathbb{R}^n | f(z)
-\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
+\partial_\epsilon f(x):= \{v \in \mathbb{R}^n | f(z)
+\ge f(x) + \langle v, z - x\rangle - \epsilon,\forall z \in
 \mathbb{R}^n\}.
@@
 The idea behind $\epsilon$-subdifferentials is the following. Say we wish
-to minimize the function $f$. Replace the usual necessary and sufficient
-condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
-weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
-small vector $v$''. In fact, it is easy to see that, for each
-point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
-  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
-This approximation concept for subdifferentials yields the following
-concept of approximate Nash-equilibria (refer to
-\cite{he2013accelerating}).
+to minimize a convex function $f$. Replace the usual
+necessary and sufficient condition ``$0 \in \partial f(x)$'' for the
+optimality of $x$ with the weaker condition ``$\partial_\epsilon f(x)$
+contains a sufficiently small vector $v$''. %%  In fact, it is easy to
+%%  see that, for each
+%% point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
+%%   0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
+This approximation concept for subdifferentials yields yet another notion
+of approximate Nash-equilibrium.
+the following concept of approximate Nash-equilibria (refer to
+\cite{he2013accelerating}), namely
 
@@
 
-The above definition is a generalization of the notion of Nash
-equilibria since: \textit{(a)} exact Nash-equilibria correspond to
-Nash $(0,0)$-equilibria, and \textit{(b)} Nash $\epsilon$-equilibria (in the sense of Definition
+The above definition is a generalization of the notion of
+Nash-equilibria since: \textit{(a)} exact Nash-equilibria correspond
+to Nash $(0,0)$-equilibria, and \textit{(b)} Nash
+$\epsilon$-equilibria (in the sense of Definition
 \ref{thm:approx_nash}) correspond to Nash $(0,\epsilon)$-equilibria.
-
-\subsection{The proposed algorithm}
-\label{sec:algo}
-We now derive the algorithm (Algorithm \ref{Tab:algo}) for computing
-Nash $(\epsilon, 0)$-equilibria and establish its theoretical
-properties. The algorithm emerges as synthesis of Theorem \ref{thm:pd}
-above, and ideas from \cite{he2013accelerating}.
 
@@
   \hat{\Psi}_2(y^{k_0}, p^{k_0}, ., .)](y^{k_0},p^{k_0},x^{k_0},q^{k_0})$,
-where $v_a^{(k_0)} := \frac{1}{k\lambda}v^{(k_0)}$.
+where
+\begin{eqnarray}
+\label{eq:v_a}
+v_a^{(k_0)} := \frac{1}{k\lambda}v^{(k_0)}.
+\end{eqnarray}
 Thus Algorithm \ref{Tab:algo} outputs a Nash
@@
 \begin{proof}
-It is clear to see that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$
+It is clear that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$
 satisfies assumptions B.1, B.2, B.3, B.5, and B.6 of
@@
 \ref{Tab:algo} is then obtained from \cite[Algorithm
-  T-BD]{he2013accelerating}, applied on the GSP
+  T-BD]{he2013accelerating} applied on the GSP
 \eqref{eq:unconstrained_pb} with the choice of parameters: $\sigma = 1
@@
       1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
-      \lambda_{xy}]$. The convergence result follows immediately from
-  \cite[Theorem 4.2]{he2013accelerating}.
+      \lambda_{xy}]$. The convergence result then follows immediately
+  from \cite[Theorem 4.2]{he2013accelerating}.
 \end{proof}
@@
 $A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
-but has a rich block-diagonal structure (each block is itself the
-Kronecker product of smaller matrices) which can be carefully
-exploited, as in \cite{hoda2010smoothing}. Also the sampling
+but is sparse and has a rich block-diagonal structure (each block is
+itself the Kronecker product of smaller matrices) which can be
+carefully exploited, as in \cite{hoda2010smoothing}. Also the sampling
 strategies presented in the recent work \cite{kroer2015} (section 6),
@@
 \paragraph*{Computing $\|K\|$.}
-Also the 2-norm $\|K\|$ of the linear operator $K$, can be efficiently
-computed using the power iteration.
+A major ingredient in the proposed algorithm is $\|K\|$, the $2$-norm
+of the huge matrix $K$. This  can be efficiently computed using the
+power iteration. Also since $\|K\|$ is only used in defining the
+step-size $\lambda := 1/\|K\|$, it may be possible to avoid computing
+$\|K\|$ altogether, and instead use a line-search / backtrack strategy
+(see \cite{o2013adaptive}, e.g) for setting $\lambda$.
+
+\paragraph*{Game abstraction.} For many variants of Poker, there has
+been extensive research in lossy / lossless abstraction techniques (for
+example \cite{gilpin2007} and more recently,
+\cite{sandholm2015abstraction,brown2015hierarchical}), wherein
+strategically equivalent or not-so-different situations in the game
+tree are lumped together. This can drastically reduce the size of the
+state space from a player's perspective, and ultimately, the size of
+the matrices $A$, $E_1$, and $E_2$, without significantly deviating
+much from the true game.
 
@@
 Results are presented and commented in Figure \ref{Tab:dgap_curve}.
+\begin{remark}
+\label{thm:bulletproof}
+We have not benchmarked our algorithm against the algorithms proposed in
+\cite{nesterov2005a} and Gilpin's et al. \cite{gilpinfirst} because
+implementing them from scratch for such games would require us to
+compute the complicated projections $\prox_{Q_k}$. We recall that
+avoiding these projections was one of the goals of the manuscript.
+\end{remark}
 \subsection{Basic test-bed: Matrix games on simplexes}
@@
  the game across iterations are shown in Figure \ref{Tab:dgap_curve}.
-We have not benchmarked our algorithm against the algorithms proposed in
-\cite{nesterov2005a} and Gilpin's et al. \cite{gilpinfirst} because
-implementing them from scratch for such games would require us to
-compute the complicated projections $\prox_{Q_k}$. We recall that
-avoiding these projections was one of the goals of the manuscript.
-
 The results of the experiments are shown in Figure
@@
   \caption{Convergence curves of Algorithm
-    \ref{Tab:algo}. In \textit{(a)}, the duality gaps
+    \ref{Tab:algo}.  We stress that the algorithms of Nesterov
+    \cite{nesterov2005a} and Gilpin \cite{gilpinfirst} are included in
+    the plots only indicatively, since this is not meant to be a
+    benchmark as already explained (Remark \ref{thm:bulletproof}). In
+    \textit{(a)}, the duality gaps
     are computed according to formula \eqref{eq:mg_pd}. One can see
-    the linear (i.e exponential) behavior of the algorithm in
+    the linear (i.e exponentially fast) behavior of the algorithm in
     \cite{gilpinfirst}, inbetween consecutive breakpoints on the
-    $\epsilon$ grid (though the rate of exponential growth seems to by
-    quite close to $1$ here). The first-order smoothing algorithm from
-    \cite{nesterov2005a} jitters around as the iterations go on
-    because even the smoothed problem becomes heavily ill-conditioned
-    near solutions. On the other hand, our proposed
-    algorithm beats both of the aforementioned algorithms, and
-  its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly
-  verified empirically. \textit{(b)}: Kuhn Poker. In both cases we see
-  that the proved convergence rate for our algorithm is observed. The
-  algorithms of Nesterov and Gilpin are included in the plots only
-  indicatively, since this is not meant to be a benchmark as already
-  explained.}
+    $\epsilon$ grid (though the rate of linear convergence seems
+    to by quite close to $1$ here). As expected, the first-order smoothing
+    algorithm labelled ``Nesterov'' \cite{nesterov2005a} jitters
+    around as the iterations go on because even the smoothed problem
+    becomes heavily ill-conditioned
+    near solutions. %% On the other hand, our proposed
+  %%   algorithm beats both of the aforementioned algorithms, and
+  %% its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly
+  %% verified empirically.
+  \textit{(b)}: Kuhn Poker. In the top-right plot, we show the
+  modified duality gap defined in \eqref{eq:v_a} In both cases, we see
+  that the proved convergence rate for our algorithm is empirically
+  observed.}
   \label{Tab:dgap_curve}
@@
 In conclusion, Nash-equilibrium problems are saddle-point
-convex-concave problems, and as such a natural tool
+convex-concave problems, and as such, a natural tool
 for tackling them would be proximal primal-dual / operator-splitting
-algorithms. %%  We believe such primal-dual
-%% schemes will receive more attention in the algorithmic game theory
-%% community in future.
+algorithms, and we believe such methods will receive more attention
+in the algorithmic game theory community in future.
 

### 2015-10-15 primal_dual.py

@@ -131,6 +131,7 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
 
         # p update
         p -= lambd * (e1 - E1.dot(x))
+        print e1 - E1.dot(x)
 
         # x updata
         x += lambd * (A.dot(y) - E1.T.dot(p))

### 2016-02-03 kuhn.py
preparing icml submission

@@ -1,22 +1,6 @@
-import itertools
-import re
-
-
-ALPHABET = "abcdefghijklm"
-
-with open("kuhn.txt", "r") as fd:
-    lines = fd.read().splitlines()
-    fd.close()
-    n_lines = int(lines[0])
-    lines = lines[1:]
-    assert n_lines == len(lines)
-    for line in lines:
-        line = line.split("*")
-        size = int(line[0])
-        line = line[1:]
-        assert size == len(line) - 1
-        if size == 0:
-            n, k = map(int, re.match("\((.+), (.+)\)", line[0]).groups())
-            for cards in itertools.combinations(ALPHABET[:n], k):
-                print cards
-        print size
+rules = []
+for perm, proba in zip([(1, 2), (1, 3), (2, 1), (2, 3), (3, 1), (3, 2)],
+                       [1. / 6] * 6):
+    head = [((perm, proba), 1)]
+    rules.append(([head, ("pass", 2), ("pass", 3)], (1., None),
+                  [head, ("pass", 2), ("bet", 1), (

### 2016-02-03 sequence_form.py

@@ -5,13 +5,16 @@ import numpy as np
 
 
 def _matrix2texstr(A, name="A", exclude=None):
-    if exclude is None: exclude = []
+    if exclude is None:
+        exclude = []
     vals = dict((val, []) for val in np.unique(A))
-    for val in exclude: del vals[val]
+    for val in exclude:
+        del vals[val]
     for v, u in vals.items():
         for i in range(A.shape[0]):
             for j in range(A.shape[1]):
-                if A[i, j] == v: u.append((i, j))
+                if A[i, j] == v:
+                    u.append((i, j))
     out = []
     for v, u in vals.items():
         out.append("$" + " = ".join(["%s(%i,%i)" % (name, i, j)
@@ -19,132 +22,15 @@ def _matrix2texstr(A, name="A", exclude=None):
     return ", ".join(out)
 
 
-
 class Game(object):
-    """Sequence-form representaion of two-person zero-sum games with perfect
-    recall and imcomplete information (like Poker, love, war, diplomacy, etc.)
 
-    Terminology
-    -----------
-
-    Game Tree (normal-form definition)
-    ==================================
-    There are 3 players, namely: the "chance" player (player 0, aka nature),
-    Alice (player 0), and Bob (player 2), and the "mute" (player 3) all four
-    treated symmetrically. Each player p has a set of moves (aka, choices,
-    actions, etc.) denoted by an alphabet A_p. For clarity of the discussion,
-    we assume that the set of moves of any two distinct players are disjoint.
-    Furthermore, player 3 (mute) has no moves, i.e A_3 = {}, hence her name.
-
-    The game tree T (from Alice's perspective) is defined as follows.
-    T has a set V(T) of nodes (aka vertices) and a set E(T) of edges.
-    Each node v belongs to a single player, p(v), called "the player to act
-    at v"; p(v) := 3 if v is a leaf node. At node v, the player p(v) has a set
-    C(v) \subset A_p of possible moves. For each player p \in [0, 1, 2],
-    the set of all nodes at which p acts is called the nodes of p,
-    denoted V_p(T). Thus v(0), v(1), and v(2) form a partition of V(T).
-
-    There are two kinds of nodes: the leafs L(T), at which the game must
-    end and decision nodes D(T), at which the player to act must make a move.
-    L(T) and D(T) are a partition of the node V(T). For example in Poker,
-    a leaf node is reached at countdown, or when a player folds, or when the
-    player runs out of money.
-
[…]

### 2016-02-03 icml/paper.tex
preparing icml submission

--- 2015-10-15 paper.tex
@@
-% Template for ISBI-2013 paper; to be used with:
-%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
-%          IEEEbib.bst - IEEE bibliography style file.
-% --------------------------------------------------------------------------
-\documentclass[a4paper,9pt]{extarticle}
-\usepackage{spconf,amsmath,amsfonts,amsthm,amssymb,graphicx}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%% ICML 2016 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Use the following line _only_ if you're still using LaTeX 2.09.
+%\documentstyle[icml2016,epsf,natbib]{article}
+% If you rely on Latex2e packages, like most moden people use this:
+\documentclass{article}
+
+% use Times
+\usepackage{times}
+% For figures
+\usepackage{graphicx} % more modern
+%\usepackage{epsfig} % less modern
+\usepackage{subfigure}
+
+% For citations
+\usepackage{natbib}
+
+% As of 2011, we use the hyperref package to produce hyperlinks in the
+% resulting PDF.  If this breaks your system, please commend out the
+% following usepackage line and replace \usepackage{icml2016} with
+% \usepackage[nohyperref]{icml2016} above.
+\usepackage{hyperref}
+
+% Packages hyperref and algorithmic misbehave sometimes.  We can fix
+% this with the following command.
+\newcommand{\theHalgorithm}{\arabic{algorithm}}
+
+% Employ the following version of the ``usepackage'' statement for
+% submitting the draft version of the paper for review.  This will set
+% the note in the first column to ``Under review.  Do not distribute.''
+\usepackage[accepted]{icml2016}
+
+% Employ this version of the ``usepackage'' statement after the paper has
+% been accepted, when creating the final version.  This will set the
+% note in the first column to ``Proceedings of the...''
+%\usepackage[accepted]{icml2016}
+
+% The \icmltitle you define below is probably too long as a header.
+% Therefore, a short form for the running title is supplied here:
+
+\usepackage{amsmath,amsfonts,amsthm,amssymb,graphicx}
 \usepackage{algorithm,algorithmicx,algpseudocode}
+\usepackage{amsmath,amsfonts,amsthm,amssymb,graphicx}
 \usepackage{times}
@@
 
-%% squeezing
-\linespread{0.845}
-\usepackage[compact]{titlesec}
-%\titlespacing{\section}{0pt}{2ex}{1ex}
-\titlespacing{\subsection}{0pt}{1ex}{0ex}
-\titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}
-
-%\def\baselinestretch{0.98}
-
-% Example definitions.
-% --------------------
-\def\x{{\mathbf x}}
-\def\L{{\cal L}}
-
-% Title.
-% ------
-\title{A SIMPLE NUMERICALLY STABLE PRIMAL-DUAL ALGORITHM FOR COMPUTING
-  NASH-EQUILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION}
-
-%
-% Single address.
-% ---------------
-\name{Elvis Dohmatob}
-\address{Parietal Team, INRIA / CEA, Universit\'e Paris-Saclay}
-%
-% For example:
-% ------------
-%\address{School\\
-%	Department\\
-%	Address}
-%
-% Two addresses (uncomment and modify for two-address case).
-% ----------------------------------------------------------
-%\twoauthors
- %% {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
- %%        {School A-B\\
- %%        Department A-B\\
- %%        Address A-B}
- %% {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
- %%        while at ...}}
- %%        {School C-D\\
- %%        Department C-D\\
- %%        Address C-D}
-%
-% More than two addresses
-% -----------------------
-% \name{Author Name$^{\star \dagger}$ \qquad Author Name$^{\star}$ \qquad Author Name$^{\dagger}$}
-%
-% \address{$^{\star}$ Affiliation Number One \\
-%     $^{\dagger}$}Affiliation Number Two
-%
+%% %% squeezing
+%% \linespread{0.845}
+%% \usepackage[compact]{titlesec}
+%% %\titlespacing{\section}{0pt}{2ex}{1ex}
+%% \titlespacing{\subsection}{0pt}{1ex}{0ex}
+%% \titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}
 
@@
 \DeclareMathOperator{\supp}{supp}
+\DeclareMathOperator{\dom}{dom}
 
@@
 
+%\def\baselinestretch{0.98}
+
+% Example definitions.
+% --------------------
+\def\x{{\mathbf x}}
+\def\L{{\cal L}}
+
+\icmltitlerunning{A primal-dual algorithm for Nash-equilibria in
+  incomplete information games}
+
 \begin{document}
 
-\maketitle
+\twocolumn[
+\icmltitle{A primal-dual algorithm for Nash-equilibria in incomplete
+  information games}
+
+% It is OKAY to include author information, even for blind
+% submissions: the style file will automatically remove it for you
+% unless you've provided the [accepted] option to the icml2016
+% package.
+\icmlauthor{Elvis Dohmatob}{elvis.dohmatob@inria.fr}
+\icmladdress{Parietal Team, INRIA / CEA, Universit\'e de Paris-Saclay}
+
+% You may provide any keywords that you 
+% find helpful for describing your paper; these are used to populate 
+% the "keywords" metadata in the PDF but will not be shown in the document
+\icmlkeywords{Nash-equilibrium, sequential games,
+  incomplete information, perfect recall, convex optimization}
+
+\vskip 0.3in
+]
+
 \begin{abstract}
@@
 
-\begin{keywords} Nash-equilibrium, sequential games,
-  incomplete information, perfect recall, convex optimization
-\end{keywords}
-%\tableofcontents
 \section{Introduction}
@@
 consists of computing Nash-equilibria (in fact, approximations thereof)
-offline, and playing one's part (an optimal \textit{behavioral}
-strategy) of the equilibrium online. This
-technique is the driving-force behind solution concepts like CFR
+offline, and playing one's part of the equilibrium --an optimal
+\textit{behavioral strategy}-- oneline. This technique is the
+driving-force behind solution concepts like CFR
 \cite{zinkevich2008regret,lanctot2009monte,Bowling09012015},
@@
   \begin{aligned}
-    \underset{(y,p) \in \mathbb{R}^{n_2} \times
-     \mathbb{R}^{l_1}}{\text{minimize }}\langle e_1,
-    p\rangle \hspace{.5em}\text{
-       subject to: } &y \ge 0, E_2y = e_2,\\
-    &-Ay + E_1^Tp \geq 0,
+    &\underset{(y,p) \in \mathbb{R}^{n_2} \times
+     \mathbb{R}^{l_1}}{\text{minimize }}e_1^Tp\\
+    &\text{subject to: } y \ge 0, E_2y = e_2,
+    -Ay + E_1^Tp \geq 0,
   \end{aligned}
@@
   \begin{aligned}
-    \underset{(x,q) \in \mathbb{R}^{n_1} \times
-      \mathbb{R}^{l_2}}{\text{maximize }}-\langle e_2,
-    q\rangle\hspace{.5em}\text{subject
-      to: } &x \ge
-    0, E_1x = e_1,\\
-    &A^Tx + E_2^Tq \geq 0.
+    &\underset{(x,q) \in \mathbb{R}^{n_1} \times
+      \mathbb{R}^{l_2}}{\text{maximize }}-e_2^Tq\\
+    &\text{subject to: } x \ge
+    0, E_1x = e_1, A^Tx + E_2^Tq \geq 0.
   \end{aligned}
@@
 equals $-1$ except for the first whose whose first entry is $1$ and all
-the others are $0$. Each of the vectors $e_k$ is of the form $(1, 0, ..., 0)$.
+the others are $0$. Each of the vectors $e_k$ is of the form $(1, 0,
+..., 0)$.
 
@@
   \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
-    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle,
+    Q_1}{\text{maximize}}\text{ }x^TAy,
   \label{eq:gilpin}
@@
 is identified with the strategy profile of player $k$ in the
-sequence-form representation. At a feasible point $(y, p, x, q)$ for
+sequence-form representation
+\cite{koller1992complexity,koller1994fast,von1996efficient,vonequilibrium}. At
+a feasible point $(y, p, x, q)$ for
 the LCPs, the \textit{duality gap} $\tilde{G}(y, p, x, q)$ is
-given by\footnote{The first inequality being due to \textit{weak
-    duality}.}
+given by\footnote{The inequality being due to \textit{weak duality}.}
 \begin{eqnarray}
   \begin{split}
-  0 &\le \tilde{G}(y, p, x, q) := \langle e_1, p\rangle - (-\langle
-  e_2, q\rangle) = \langle e_1, p\rangle + \langle
-  e_2, q\rangle\\
-  &= G(x, y) := \mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
-(u,v) \in Q_1 \times Q_2\}.
+  \tilde{G}(y, p, x, q) &:= e_1^Tp - (-e_2^Tq) = e_1^Tp + e_2^Tq\\
+  &= \mathrm{max}\{u^TAy - x^TAv| (u,v) \in Q_1 \times Q_2\}\\
+  &=:G(x, y) \ge 0.
 \end{split}
@@
 \hspace{.25em} -Ay + E_1^Tp \ge 0, &\hspace{.5em}A^Tx + E_2^Tq \ge
-0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0,\\
-&\langle y, A^Tx  + E_2^Tq\rangle = 0.
+0, \hspace{.25em} x^T(-Ay + E_1^Tp) = 0,\\
+&y^T(A^Tx  + E_2^Tq) = 0.
 \end{split}
@@
 \begin{eqnarray}
-\Delta_{n_k} := \left\{z \in \mathbb{R}^{n_k}|z \ge 0,\sum_j
+\Delta_{n_k} := \left\{z \in \mathbb{R}^{n_k}|z \ge 0,\sum_{j=1}^{n_k}
 z_j = 1\right\}.
@@
 G(x, y) &=
-\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
+\mathrm{max}\{u^TAy - x^TAv | (u,v) \in
 \Delta_{n_1} \times \Delta_{n_2}\}\\
@@
 \subsection{Notation and terminology}
-\paragraph*{General.} Let $m$ and $n$ be positive integers.
+\paragraph{General.} Let $m$ and $n$ be positive integers.
 The components of a vector $z \in \mathbb{R}^n$ will be
@@
 $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| :=
-\sqrt{\langle z, z\rangle}$. %%  $(z)_+:=\text{max}(0, z) \in
-%% \mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
-%% example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
-%% operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
-%% function.
+\sqrt{z^Tz}$.  $(z)_+:=\text{max}(0, z) \in
+\mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
+example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
+operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
+function.
 Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
@@
 
-\paragraph*{Convex analysis.} %% For our purposes, it will suffice to
-%% know the following basic but powerful modern convex-analytical
-%% concepts. The interested reader should refer to
-%% \cite{combettes2011proximal} and the references therein for a more
-%% elaborate and scholastic exposition on the subject. % and its use in
-%%                                 % modern
-%%                                 % convex-optimization.
+\paragraph{Convex analysis.} In the sequel, we will use the following
+basic but powerful modern convex-analytical
+concepts.
 Given a subset $C \subseteq \mathbb{R}^n$, $i_C$ denotes the
@@
   convex function. The \textit{effective domain} of $f$, denoted
-  $dom(f)$, is defined as
-$dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$.
- If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
+  $\dom f$, is defined as
+$\dom f := \{x \in \mathbb{R}^n | f(x) < +\infty\}$.
+ If $\dom f \ne \emptyset$ then we say $f$ is \textit{proper}.
 %% \textit{proper convex lower semi-continous function}
@@
 defined by
-$\partial f(x) := \{v \in \mathbb{R}^n | f(z)  \ge f(x) + \langle v, z -
-x\rangle, \forall z \in \mathbb{R}^n\}$.
+$\partial f(x) := \{v \in \mathbb{R}^n | f(z)  \ge f(x) + v^T(z -
+x), \forall z \in \mathbb{R}^n\}$.
 %% Each element of $\partial f(x)$ is called a \textit{subgradient} of $f$
@@
 \textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
-\rightarrow \mathbb{R}^n$ defined by $\prox_f(x): = \underset{z \in
+\rightarrow \mathbb{R}^n$ defined by
+\begin{equation}
+ \prox_f(x): = \underset{z \in
   \mathbb{R}^n}{\text{argmin }}\frac{1}{2}\|z
-  - x\|^2 + f(z)$.
-%% For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
-%% $\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
-%% operators generalize orthogonal projectors. For example
-%% $\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
-%% (z)_+$. One also has the useful characterization
-%% \begin{eqnarray}
-%%   p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
-%% \end{eqnarray}
-%% Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
-%% should) be thought of as performing an \textit{implicit} gradient step
-%% of size $\gamma$.
-
-We recommend \cite{rockafellar1997convex,combettes2011proximal} for a
-more detailed exposition on convex analysis and its use in
-modern optimization theory and practice.
-
-\section{Relation to prior work}
+  - x\|^2 + f(z).
+\end{equation}
+For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
+$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
+operators generalize orthogonal projectors. For example
+$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
+(z)_+$. One also has the useful characterization
+\begin{eqnarray}
+  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
+\end{eqnarray}
+Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
+should) be thought of as performing an \textit{implicit} gradient step
+of size $\gamma$.
+
+A more detailed exposition on convex analysis and its use in
+modern optimization theory and practice can be found in
+\cite{rockafellar1997convex,combettes2011proximal}.
+
+\section{Prior work}
 \label{sec:related_work}
@@
 $\delta > 0$ such that for any pair of realization plans $(x, y) \in Q_1 \times Q_2$,
-\begin{eqnarray}
+\begin{eqnarray*}
 \text{``distance between }(x, y)\text{ and set of
 equilibria'' } \le G(x, y)/\delta.
-\end{eqnarray}
+\end{eqnarray*}
 Their
@@
 \label{sec:gsp}
-\subsection{A Generalized Saddle-point Problem (GSP) equivalent of
-  the Nash-equilibrium LCPs \eqref{eq:primal_pb} and
-  \eqref{eq:dual_pb}}
+\subsection{Generalized Saddle-point Problem (GSP) for
+  Nash-equilibrium}
 In the next theorem, we show that the LCPs \eqref{eq:primal_pb}
@@
 conveniently written as a GSP in the sense of
-\cite{he2013accelerating}. The crux of idea is to remove the linear
+\cite{he2013accelerating}. The crux of idea is to ``dualize'' the linear
 constraints in the definitions of the strategy polytopes $Q_k$, by
@@
 Define two proper closed convex functions
-  \begin{eqnarray}
-    \left.
-    \begin{aligned}
+  \begin{eqnarray*}
       g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
       (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
-        i_{y \ge 0} + \langle e_1,p\rangle\\
+        i_{y \ge 0} + e_1^Tp\\
         g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
         (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
-          i_{x \ge 0} + \langle e_2, q\rangle
-    \end{aligned}
-    \right\}
+          i_{x \ge 0} + e_2^Tq
     \label{eq:things}
-  \end{eqnarray}
+  \end{eqnarray*}
 Also define two bilinear forms $\Psi_1$, $\Psi_2: \mathbb{R}^{n_2}
 \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
-\mathbb{R}^{l_2} \rightarrow \mathbb{R}$ with $\Psi_2 = -\Psi_1$ by letting
-\begin{equation}
+\mathbb{R}^{l_2} \rightarrow \mathbb{R}$ by letting
+\begin{eqnarray*}
   \begin{split}  
@@
     \Psi_1(y, p, x, q)
-    := \left\langle \begin{bmatrix}x\\q\end{bmatrix},
-      K\begin{bmatrix}y\\p\end{bmatrix}\right\rangle, %% \\
+    := \begin{bmatrix}x\\q\end{bmatrix}^T
+      K\begin{bmatrix}y\\p\end{bmatrix}, %% \\
       %% &= \langle x,
@@
 \end{split}
-\end{equation}
-and define the functions $\hat{\Psi}_1$, $\hat{\Psi}_2:
+\end{eqnarray*}
+with $\Psi_2 = -\Psi_1$, and define the functions $\hat{\Psi}_1$,
+$\hat{\Psi}_2
 \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}
 \times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ by
-\begin{eqnarray}
-  \begin{aligned}
+\begin{eqnarray*}
     \hat{\Psi}_1(y, p, x, q) :=\begin{cases}
     \Psi_1(y, p, x, q)+ g_1(y, p), &\mbox{ if }y \ge 0,\\
-    +\infty, &\mbox{ otherwise}\end{cases}\\
+    +\infty, &\mbox{ otherwise,}\end{cases}\\
     %% &\hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(x, q) \text{ if
@@
     +\infty, &\mbox{ otherwise.}\end{cases}
-  \end{aligned}
-\end{eqnarray}
+\end{eqnarray*}
 Finally, define the sets $S_1 := \mathbb{R}^{n_2}_+ \times
@@
 $g_2$): Find a quadruplet $(y^*,p^*, x^*, q^*) \in S_1 \times S_2$
-such that
+s.t $\forall (y,p, x, q) \in S_1 \times S_2$, we have
 \begin{eqnarray}
@@
     &\hat{\Psi}_2(y^*, p^*, x^*, q^*)
-    \le \hat{\Psi}_2(y^*, p^*, x, q),\hspace{.21em} \forall (y,p, x, q)
-    \in S_1 \times S_2.
+    \le \hat{\Psi}_2(y^*, p^*, x, q).
   \label{eq:unconstrained_pb}
@@
   \begin{aligned}
-    &a(y,p) = \langle e_1,p\rangle + i_{y\ge 0} + i_{-Ay + E_1^Tp \ge 0} +
+    &a(y,p) = e_1^Tp + i_{y\ge 0} + i_{-Ay + E_1^Tp \ge 0} +
     i_{E_2y = e_2}\\
     &= g_1(y,p) + \underset{x' \geq
-      0}{\text{max}}\text{ }\langle x',Ay - E_1^Tp\rangle +
-    \underset{q'}{\text{max}}\text{ }\langle q',E_2y - e_2\rangle\\
+      0}{\text{max}}\text{ }x'^T(Ay - E_1^Tp) +
+    \underset{q'}{\text{max}}\text{ }q'^T(E_2y - e_2)\\
     &= g_1(y,p) + \underset{x',
-      q'}{\text{max}}\text{ }\langle x',Ay\rangle - \langle x',
-    E_1^Tp\rangle + \langle q',E_2y\rangle\\
+      q'}{\text{max}}\text{ }x'^TAy - x'^T
+    E_1^Tp + q'^TE_2y\\
     &\hspace{10em}-
-    (i_{x' \ge 0} + \langle e_2,q\rangle)\\
+    (i_{x' \ge 0} + e_2^Tq)\\
     &= g_1(y,p)
@@
 &b(x, q) = 
--\langle q, e_2\rangle -i_{x \ge 0} - i_{A^Tx+E_2^Tq \ge 0} -
+-q^Te_2 -i_{x \ge 0} - i_{A^Tx+E_2^Tq \ge 0} -
  i_{E_1x = e_1}\\
  &= -g_2(x, q) + \underset{y' \geq
-   0}{\text{min}}\text{ }\langle y', A^Tx + E_2^Tq\rangle +
- \underset{p'}{\text{min}}\text{ }\langle p', e_1-E_1x\rangle\\
+   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
+ \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
     &= -g_2(x, q)
@@
 \begin{definition}
-  Given $\epsilon > 0$ and a function $f:\mathbb{R}^n
+  Given $\epsilon \ge 0$ and a function $f:\mathbb{R}^n
   \rightarrow (-\infty,+\infty]$, the $\epsilon$-enlarged
@@
   \begin{eqnarray}
+    \begin{split}
     \partial_\epsilon f(x):= \{v \in \mathbb{R}^n | f(z)
-\ge f(x) + \langle v, z - x\rangle - \epsilon,\forall z \in
-\mathbb{R}^n\}.
+    \ge f(x) + &v^T(z - x) - \epsilon,\\
+    &\forall z \in \mathbb{R}^n\}.
+    \end{split}
 \end{eqnarray}
 \end{definition}
-The idea behind $\epsilon$-subdifferentials is the following. Say we wish
-to minimize a convex function $f$. Replace the usual
+Of course, $\partial_0f = \partial f$, the usual notion of
+subdifferential. The idea behind $\epsilon$-subdifferentials is the
+following. Say we wish to minimize a convex function $f$. Replace the usual
 necessary and sufficient condition ``$0 \in \partial f(x)$'' for the
 optimality of $x$ with the weaker condition ``$\partial_\epsilon f(x)$
-contains a sufficiently small vector $v$''. %%  In fact, it is easy to
-%%  see that, for each
-%% point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
-%%   0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
+contains a sufficiently small vector $v$''.  In fact, it is easy to
+ see that, for each
+point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
+  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
 This approximation concept for subdifferentials yields yet another notion
@@
 b - \lambda e_j)$. With all these ingredients in place, Algorithm
-\ref{Tab:algo} is then obtained from \cite[Algorithm
-  T-BD]{he2013accelerating} applied on the GSP
+\ref{Tab:algo} is then obtained from Algorithm
+  T-BD of \cite{he2013accelerating} applied on the GSP
 \eqref{eq:unconstrained_pb} with the choice of parameters: $\sigma = 1
@@
       \lambda_{xy}]$. The convergence result then follows immediately
-  from \cite[Theorem 4.2]{he2013accelerating}.
+  from Theorem 4.2 of \cite{he2013accelerating}.
 \end{proof}
@@
 \subsection{Practical considerations}
-\paragraph*{Efficient computation of $Ay$ and $A^Tx$.}
+\paragraph{Efficient computation of $Ay$ and $A^Tx$.}
 In Algorithms \ref{Tab:algo}, most of the time is spent
@@
 
-\paragraph*{Computing $\|K\|$.}
+\paragraph{Computing $\|K\|$.}
 A major ingredient in the proposed algorithm is $\|K\|$, the $2$-norm
@@
 
-\paragraph*{Game abstraction.} For many variants of Poker, there has
+\paragraph{Game abstraction.} For many variants of Poker, there has
 been extensive research in lossy / lossless abstraction techniques (for
@@
 \end{remark}
-\subsection{Basic test-bed: Matrix games on simplexes}
+\paragraph{\textit{(a)} Basic test-bed: Matrix games on simplexes.}
 As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
@@
 
-\subsection{Kuhn Poker, a ``toy'' sequential game} This game is a
-simplified form of Poker
+\paragraph{\textit{(b)} Kuhn Poker, a ``toy'' incomplete-information
+  sequential game.} This game is a simplified form of Poker
 developed by Harold W. Kuhn in \cite{kuhn}. It already contains all
@@
   \subfigure[$10^3 \times 10^3$ matrix game on simplexes]{
-    \includegraphics[width=.5\linewidth]{0.pdf}
+    \includegraphics[width=.5\linewidth]{../0.pdf}
   }
@@
   \subfigure[Kuhn 3-card Poker]{
-    \includegraphics[width=.5\linewidth]{Kuhn3112_dgap.pdf}
+    \includegraphics[width=.5\linewidth]{../Kuhn3112_dgap.pdf}
   }
@@
   \hspace{-.5em}
-  \includegraphics[width=.5\linewidth]{1.pdf}
+  \includegraphics[width=.5\linewidth]{../1.pdf}
   %% \hspace{-1em}
@@
   %\hspace{.5em}
-  \includegraphics[width=.49\linewidth]{Kuhn3112_NE.pdf}
+  \includegraphics[width=.49\linewidth]{../Kuhn3112_NE.pdf}
   \caption{Convergence curves of Algorithm
@@
     becomes heavily ill-conditioned
-    near solutions. %% On the other hand, our proposed
-  %%   algorithm beats both of the aforementioned algorithms, and
-  %% its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly
-  %% verified empirically.
+    near solutions. On the other hand, our proposed
+    algorithm beats both of the aforementioned algorithms, and
+  its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly
+  verified empirically.
   \textit{(b)}: Kuhn Poker. In the top-right plot, we show the
@@
 
-\section{Concluding remarks and future work}
+\section{Concluding remarks}
 Making use of the sequence-form representation
 \cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
-devised a simple numerically stable primal-dual algorithm for computing
-Nash-equilibria in two-person zero-sum sequential games with
-incomplete information (like Texas Hold'em, etc.). Our algorithm is
-simple to implement, with a low constant cost per iteration, and
-enjoys a rigorous convergence theory with a proven
-$\mathcal{O}(1/\epsilon)$ convergence in terms of basic operations
-(matvec products, clipping, etc.), to a Nash
-$(\epsilon,0)$-equilibrium of the game. In future, we plan to run more
-experiments on real Poker games to measure the practical power of the
-proposed algorithm compared to other competed schemes like CFR and
+proposed an equivalent Generalized Saddle-Point (GSP) formulation to
+the Nash-equilibrium problem for sequential games with incomplete
+information and perfect recall (e.g Texas Hold'em, etc.). Then, we
+have devised a simple numerically stable primal-dual algorithm for
+solving the GSP, and so by equivalence, compute (approximate)
+Nash-equilibria for such games. Our algorithm is simple to implement,
+with a low constant cost per iteration, and enjoys a rigorous
+convergence theory with a proven $\mathcal{O}(1/\epsilon)$ convergence
+in terms of basic operations (matvec products, clipping, etc.), to a
+Nash $(\epsilon,0)$-equilibrium of the game. In future, we plan to run
+more experiments on real Poker games to measure the practical power of
+the proposed algorithm compared to other competed schemes like CFR and
 EGT.
@@
 for tackling them would be proximal primal-dual / operator-splitting
-algorithms, and we believe such methods will receive more attention
+algorithms applied, for example, to the GSP formulation we have
+proposed. We believe such methods will receive more attention
 in the algorithmic game theory community in future.
 
-%% \paragraph{Software.} The authors' implementation of the proposed
-%% algorithm is available upon request.
+\paragraph{Software.} The author's implementation of the proposed
+algorithm is available upon request.
 
@@
 
-\pagebreak
-\bibliographystyle{IEEEbib}
-\bibliography{bib}
+% In the unusual situation where you want a paper to appear in the
+% references without citing it in the main text, use \nocite
+%\nocite{langley00}
+
+\bibliography{../bib}
+\bibliographystyle{icml2016}
 
 \end{document}
+
+% This document was modified from the file originally made available by
+% Pat Langley and Andrea Danyluk for ICML-2K. This version was
+% created by Lise Getoor and Tobias Scheffer, it was slightly modified  
+% from the 2010 version by Thorsten Joachims & Johannes Fuernkranz, 
+% slightly modified from the 2009 version by Kiri Wagstaff and 
+% Sam Roweis's 2008 version, which is slightly modified from 
+% Prasad Tadepalli's 2007 version which is a lightly 
+% changed version of the previous year's version by Andrew Moore, 
+% which was in turn edited from those of Kristian Kersting and 
+% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2016-02-03 chambolle_pock.py

@@ -72,6 +72,23 @@ def chambolle_pock(K, KT, prox_G, prox_Fstar, x0, y0, max_iter=100,
 
     return x, y
 
+
+def cp(A, E1, E2, e1, e2, **kwargs):
+    from chambolle_pock import chambolle_pock
+    n1, n2 = A.shape
+    l1 = len(e1)
+    l2 = len(e2)
+    k = K(A, E1, E2)
+    kt = k.T
+    yp0 = np.zeros(n2 + l1)
+    xq0 = np.zeros(n1 + l2)
+    prox_G = lambda yp, lambd: np.concatenate((np.maximum(yp[:n2], 0.),
+                                               yp[n2:] - lambd * e1))
+    prox_Fstar = lambda xq, lambd: np.concatenate((np.maximum(xq[:n1], 0.),
+                                                   xq[n1:] - lambd * e2))
+    return chambolle_pock(k, kt, prox_G, prox_Fstar, yp0, xq0, **kwargs)
+
+
 if __name__ == "__main__":
 
     """

### 2016-02-03 primal_dual.py

@@ -14,6 +14,25 @@ from scipy import linalg
 _norm = lambda *args: sqrt(np.sum(np.concatenate(args) ** 2))
 
 
+class K(object):
+    def __init__(self, A, E1, E2, L=None):
+        self.A = A
+        self.E1 = E1
+        self.E2 = E2
+        self.n1, self.n2 = A.shape
+        self.l1, self.l2 = E1.shape[0], E2.shape[0]
+        zeros = np.zeros((self.l2, self.l1))
+        self.mat = np.vstack((np.hstack((A, -E1.T)), np.hstack((E2, zeros))))
+        self.L = linalg.norm(self.mat, 2) if L is None else L
+
+    def __call__(self, yp):
+        return self.mat.dot(yp)
+
+    @property
+    def T(self):
+        return K(self.A.T, -self.E2, -self.E1, L=self.L)
+
+
 def _check_subgradient(f, x, g, n=10):
     """Checks that g is a sub-gradient of f at x."""
     from sklearn.utils import check_random_state
@@ -115,6 +134,9 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
     deltas_p = []
     deltas_x = []
     deltas_q = []
+    y_avg = np.zeros_like(y)
+    x_avg = np.zeros_like(x)
+    k = 1
     for k in range(max_iter):
         # invoke callback
         if callback and callback(locals()):
@@ -137,6 +159,7 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
         x += lambd * (A.dot(y) - E1.T.dot(p))
         x = proj_C1(x)
         delta_x = x - old_x
+        x_avg += x
         if check_ergodic:
             deltas_x.append(delta_x)
 
@@ -149,6 +172,7 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
         # u update (again)
         y -= lambd * (A.T.dot(delta_x) + E2.T.dot(delta_q))
         delta_y = y - old_y
+        y_avg += y
         if check_ergodic:
             deltas_y.append(delta_y)
 
@@ -177,6 +201,8 @@ def primal_dual_ne(A, E1, E2, e1, e2, proj_C1=lambda x: np.maximum(x, 0.),
             break
 
     # misc
+    y = y_avg / float(k)
[…]

### 2016-02-03 simple.py

@@ -9,7 +9,10 @@ from sklearn.utils import check_random_state
 from sequence_form import Game
 from primal_dual import primal_dual_ne, primal_dual_sg_ne
 
-RNG = np.random.choice
+
+def _bin(x, n=None):
+    x = map(int, bin(x)[2:])
+    return tuple(((n - len(x)) * [0]) + x)
 
 
 class Kuhn3112(Game):
@@ -137,6 +140,66 @@ class SimplifiedPoker(Game):
                         self.add_labelled_edge(a, y, 3, payoff=payoff)
 
 
+class LogicGatePredictionGame(Game):
+    N_INPUTS = 10
+    BOOK = ["0"]
+
+    def player_choices(self):
+        return {0: "0", 2: "01",
+                1: "".join([str(x) for x in range(2 ** self.N_INPUTS)])}
+
+    def blur(self, choice, *args):
+        return "0"
+
+    def unblur(self, part, player):
+        return "0"
+
+    def call_gate(self, *args):
+        raise NotImplementedError
+
+    def build_tree(self):
+        samples = range(2 ** self.N_INPUTS)
+        self.set_node_info(0, "(/,0)", ["(%s,1)" % choice
+                                        for choice in self.PLAYER_CHOICES[0]])
+        child = self.add_labelled_edge(
+            "(/,0)", "0", 1, choices=["(%s,2)" % c for c in samples])
+        for x in samples:
+            y_true = self.call_gate(*_bin(x, n=self.N_INPUTS)) % 2
+            u = self.add_labelled_edge(child, str(x), 2,
+                                       choices=["(0,3)", "(1,3)"])
+            for y_pred in range(2):
+                self.add_labelled_edge(u, str(y_pred), 3,
+                                       payoff=-1. if y_pred == y_true else 1.)
+
+
+class XorGame(LogicGatePredictionGame):
+    def call_gate(self, *args):
+        return np.sum(args) % 2
+
+
+class AndGame(LogicGatePredictionGame):
+    def call_gate(self, *args):
+        return np.prod(np.array(args) % 2)
+
+
+class OrGame(LogicGatePredictionGame):
+    def call_gate(self, *args):
+        return np.max(args) > 0.
+
+
+class EvilGame(LogicGatePredictionGame):
+
+    def call_gate(self, *args):
+        return np.array(args)[::2].sum().max() > 0.
+
+
+class NotGame(LogicGatePredictionGame):
+    N_INPUTS = 1
+
[…]

### 2016-02-04 icml/paper.tex
more

@@
 % the note in the first column to ``Under review.  Do not distribute.''
-\usepackage[accepted]{icml2016}
+\usepackage{icml2016}
 
@@
 \end{equation}
-The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
-and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
+The vectors $p = (p_0, p_1, \ldots, p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
+and $q = (q_0, q_1, \ldots, q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
 variables. 
@@
 the others are $0$. Each of the vectors $e_k$ is of the form $(1, 0,
-..., 0)$.
+\ldots, 0) \in \mathbb R^{l_k}$.
 
@@
 the LCPs, the \textit{duality gap} $\tilde{G}(y, p, x, q)$ is
-given by\footnote{The inequality being due to \textit{weak duality}.}
+given by\footnote{The inequality is referred to as \textit{weak duality}.}
 \begin{eqnarray}
@@
 \begin{eqnarray}
-\Delta_{n_k} := \left\{z \in \mathbb{R}^{n_k}|z \ge 0,\sum_{j=1}^{n_k}
+\Delta_{n_k} := \left\{z \in \mathbb{R}^{n_k}|z \ge 0,\sum_j
 z_j = 1\right\}.
@@
 This simplex can be written as a compact convex polytope in
-the form \eqref{eq:polytope} by taking $E_k := (1, 1, ..., 1) \in
+the form \eqref{eq:polytope} by taking $E_k := (1, 1, \ldots, 1) \in
 \mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
@@
 The components of a vector $z \in \mathbb{R}^n$ will be
-denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
+denoted $z_0$, $z_1$, \ldots, $z_{n-1}$ (indexing begins from $0$,
 not $1$). $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ }
